### 2020-08-17 1.intro/introduction.tex
add draft converted from thesis

The proliferation of information technology has enabled us to collect and consume huge volumes of data at unprecedented speeds and at very low costs.
This fast and cheap access to data gave rise to fundamentally new ways of pursuing scientific questions.
In contrast with the traditional hypothesis--experiment--analysis cycle where data are collected from the experiments, abundant information are often available before specific questions are even formulated. 
Such information can be used for not just evaluating hypotheses, but also for \emph{generating}, and \emph{selecting} the hypotheses to pursue. 
As a result, {multiple testing} --- where a large number of hypotheses are formulated and screened for their plausibility simultaneously --- has become a staple of modern data-driven studies.

An archetypal example of multiple testing problems is genetic association studies \citep{bush2012genome}.
In genetic association studies, scientists test hypotheses relating each of the hundreds of thousands of genetic marker locations to phenotypic traits of interest;
the goal here is to select the set of most promising genetic markers for subsequent investigation.
Another example of multiple testing problems arise in cybersecurity, where millions of IP addresses are monitored in real time.
In this engineering application, statistics are collected and tests are performed for each IP address, in an attempt to locate the IP addresses with anomalous network activities, so that and malicious traffic and volumetric attacks can be filtered to protect end users of network services \citep{kallitsis2016amon}.

We are motivated by the above examples in particular to study {high-dimensional} multiple testing problems where a large number of hypotheses are tested simultaneously.

% This high multiplicity of tests brings along a multitude of challenges, and has been a subject of extensive study in recent years.

In the rest of the introduction, we shall review the main objectives of high-dimensional multiple testing, elaborate on these objectives in two classes of data models and in the context of the genetic applications, and briefly summarize the contents of this text.

% While many such multiplicities are explicit, where screenings and selections of hypotheses, models, or variables are performed \emph{and} annouced, they may be completely ``silent'', where such selections are performed but not explicitly reported \citep{berry2012multiplicities}.

% This paper seeks to establish some new asymptotic optimality results for common multiple testing procedures, including the Bonferroni procedure and the Benjamini-Hochberg procedure, in high-dimensional chi-square models.

% This dissertation studies in detail the theoretical limits of multiple problems in high-dimensional sparse models

\section{The additive error model}

Consider the canonical signal-plus-noise model where the observation $x$ is a high-dimensional vector in $\R^p$,
\begin{equation} \label{eq:model-additive}
    x(i) = \mu(i) + \epsilon(i), \quad i=1,\ldots,p.
\end{equation}
The signal, $\mu = (\mu(i))_{i=1}^p$, is a vector with $s$ non-zero components supported on the set $S=\{i:\mu(i)\neq 0\}$; the second term $\epsilon$ is a random error vector. 
The goal of high-dimensional statistics is usually two-fold: 
\begin{enumerate}
    \item To detect the presence of non-zero components in $\mu$. That is, to test the global hypothesis $\mu = 0$, which we call the \emph{detection} problem, and
    \item To estimate the support set $S$, which we call the \emph{support recovery} problem.
\end{enumerate}
To illustrate, in the engineering application of cybersecurity, Internet service providers (ISP) routinely collect statistics of network traffic to determine if there are abnormal surges or blackouts.
The data vector $x$ could represent, for example, incoming traffic volumes to each server node that the ISP maintains.
In this case, the vector $\mu$ would be the average traffic volumes when under normal operating conditions, and $\epsilon$'s the fluctuations around these normal levels of traffic.
% The ISPs collect, for example, incoming traffic volumes to each server to determine if there are abnormal surges or blackouts.
The signal detection problem in this context is then equivalent to determining if there are \emph{any} anomalies among all servers, and the support recovery problem is equivalent to \emph{identifying} the servers with anomalies.
Similar questions of signal detection and support recovery are pursued in large-scale microarray experiments, %\citep{dudoit2003multiple}, 
brain imaging and fMRI analysis, %\citep{nichols2003controlling}, 
and numerous other applications.

A common theme in such applications is that the errors are correlated, and that the signal vectors are believed to be sparse: the number of non-zero components in $\mu$ is small compared to the number of test performed --- in the cybersecurity example, while monitoring is performed over a large number of servers, it is often believed that only very few servers will be experiencing problems at any time.
Under such sparsity assumptions, it is natural to ask if and when one can reliably {(1)} detect the signals, and {(2)} recover the support set $S$.
% Further, one would like to characterize the statistical procedures that achieve efficient detection and support recovery, whenever such goals become possible to achieve.
We explore both the \emph{detection} and the \emph{support recovery} problems in this thesis. 
More precisely, we are interested in the theoretical feasibility of both problems, and seek minimal conditions under which these problems can be consistently solved in large dimensions.

\medskip

Model \eqref{eq:model-additive} is simple yet ubiquitous.
Consider the linear model
\begin{equation*}
 Y = X\mu + \xi,
\end{equation*}
where $\mu$ is a $p$-dimensional vector of regression coefficients of interest to be inferred from observations of $X$ and $Y$.
If the design matrix $X$ is of full column rank, then the ordinary least squares (OLS) estimator of $\mu$ can be formed 
\begin{equation} \label{eq:OLS}
    \widehat{\mu} = \left(X'X\right)^{-1}X'Y = \mu + \epsilon,
\end{equation}
where $\epsilon := (X'X)^{-1}X'\xi$.
Hence we recover the generic problem \eqref{eq:model-additive}. 
Signal detection is therefore equivalent to the problem of testing the global null model, and support recovery problem corresponds to the fundamental problem of variable selection.

Note that the components in the observation $x$ (and equivalently, the noise $\epsilon$) in \eqref{eq:model-additive} need not be independent. 
In the linear regression example, even when the components of the noise term $\xi$ are independent, those of the OLS estimator \eqref{eq:OLS} need not be, unless we have an orthogonal design.
Indeed, in practice, independence is the exception rather than the rule.
Therefore a general theory of feasibility must address the role of the error dependence structures in such testing problems, and identify practical procedures that attain the performance limits in independent as well as dependent cases, as soon as the problems become theoretically feasible.

\section{Genome-wide association studies and the chi-square model}
\label{sec:motivation-chisq}

The second data model we analyze is the high-dimensional chi-square model,
\begin{equation} \label{eq:model-chisq}
    %x(i) \distras{\mathrm{ind.}} \chi_\nu^2\left(\lambda(i)\right), \quad i=1,\ldots,p.
    x(i) \sim \chi_\nu^2\left(\lambda(i)\right), \quad i=1,\ldots,p,
\end{equation}
where the data $x(i)$'s follow independent (non-central) chi-square distributions with $\nu$ degrees of freedom and non-centrality parameter $\lambda(i)$.

% While the additive error models are frequently featured in the literature, the chi-square models need some introduction.

Model \eqref{eq:model-chisq} is motivated by large-scale categorical variable screening problems, typified by \ac{GWAS}
% genome-wide association studies (GWAS) 
where millions of genetic factors are examined for their potential influence on phenotypic traits.
% We briefly introduce the scientific background next, to provide some context.

% introduced through the language of GWAS next.
% These categorical covariate screening problems naturally give rise to the high-dimensional chi-square models, introduced through the language of GWAS next.
% 
% Broadly speaking, GWAS aim to discover genetic variations that are linked to traits or diseases of interested, by testing for associations between the subjects' genetic compositions and their phenotypes.
In a GWAS with a case-control design, a total of $n$ subjects are recruited,  consisting of $n_1$ subjects possessing some defined traits, and $n_2$ subjects without the traits serving as controls.
The genetic compositions of the subjects are then examined for variations known as \ac{SNP} at an array of $p$ genomic marker locations, and compared between the case and the control group.
These physical traits are commonly referred to as \emph{phenotypes}, and the genetic variations are known as \emph{genotypes}.

Focusing on one specific genomic location, the counts of observed genotypes, if two variants are present, can be tabulated as follows.
% \begin{table}[ht]
% \centering
\begin{center}
    \begin{tabular}{cccc}
    \hline
    & \multicolumn{2}{c}{Genotype} & \\
    \cline{2-3}
    \# Observations & Variant 1 & Variant 2 & Total by phenotype \\
    \hline
    Cases & $O_{11}$ & $O_{12}$ & $n_1$ \\
    Controls & $O_{21}$ & $O_{22}$ & $n_2$ \\
    \hline
    \end{tabular}
    % \caption{Tabulated counts of genotype-phenotype combinations in a genetic association test.}
\end{center}
% \end{table}
Researchers test for associations between the genotypes and phenotypes using, for example, the Pearson chi-square test with statistic
\begin{equation} \label{eq:chisq-statistic}
    x = \sum_{j=1}^2 \sum_{k=1}^2 \frac{(O_{jk} - E_{jk})^2}{E_{jk}},
\end{equation}
where ${E}_{jk} = (O_{j1}+O_{j2})(O_{1k}+O_{2k})/n$.
% are the expected number of observations under the null.
%E_{jk} = \Big(\sum_{l}O_{jl}\Big)\Big(\sum_{l}O_{lk}\Big)\Big/n.

Under the mild assumption that the counts $O_{jk}$'s follow a multinomial distribution (or a product-binomial distribution, if we decide to condition on one of the marginals), the statistic $x$ in \eqref{eq:chisq-statistic} can be shown to have an approximate $\chi^2(\lambda)$ distribution with $\nu=1$ degree of freedom at large sample sizes (see, e.g., classical results in \citet{ferguson2017course} and
\cite{agresti2018introduction}). 
Independence between the genotypes and phenotypes would imply a non-centrality parameter $\lambda$ value of zero; if dependence exists, we would have a non-zero $\lambda$ where its value depends on the underlying multinomial probabilities.
More generally, if we have a $J$ phenotypes and $K$ genetic variants, assuming a $J\times K$ multinomial distribution, the statistic will follow approximately a $\chi^2_{\nu}(\lambda)$ distribution with $\nu = (J-1)(K-1)$ degrees of freedom, when sample sizes are large.

The same asymptotic distributional approximations also apply to the likelihood ratio statistic, and many other statistics under slightly different modeling assumptions \citep{gao2019upass}.
These association tests are performed at each of the $p$ SNP marker locations throughout the whole genome, and we arrive at $p$ statistics having approximately (non-central) chi-square distributions, $\chi_{\nu(i)}^2\left(\lambda(i)\right)$, for $i=1,\ldots,p$,
% \begin{equation} \label{eq:model-chisquare-approx}
%     x(i) \mathrel{\dot\sim} \chi_{\nu(i)}^2\left(\lambda(i)\right), \quad i=1,\ldots,p,
% \end{equation}
where $\lambda = (\lambda(i))_{i=1}^p$ is the $p$-dimensional non-centrality parameter.
%, with $\lambda(i)=0$ indicating independence of the $i$-th SNP with the outcomes, and $\lambda(i)\neq0$ indicating associations.

Although the number of tested genomic locations $p$ can sometimes exceed $10^5$ or even $10^6$, it is often believed that only a small set of genetic locations have tangible influences on the outcome of the disease or the trait of interest.
Under the stylized assumption of sparsity, $\lambda$ is assumed to have $s$ non-zero components, with $s$ being much smaller than the problem dimension $p$. 
The goal of researchers is again two-fold: (1) to test if $\lambda(i)=0$ for all $i$, and (2) to estimate the set $S=\{i:\lambda(i)\neq 0\}$.
In other words, we look to first determine if there are \emph{any} genetic variations associated with the disease; and if there are associations, we want to locate them.

\medskip

The chi-square model \eqref{eq:model-chisq} also plays an important role in analyzing variable screening problems under omnidirectional alternatives.
A primary example is multiple testing under two-sided alternatives in the additive error model \eqref{eq:model-additive} where the errors $\epsilon$ are assumed to have standard normal distributions.

Under two-sided alternatives, unbiased test procedures call for rejecting the hypothesis $\mu(i)=0$ at locations where observations have large absolute values, or equivalently, large squared values.
Taking squares on both sides of \eqref{eq:model-additive}, and we arrive at Model \eqref{eq:model-chisq} with non-centrality parameters $\lambda(i) = \mu^2(i)$ and degree-of-freedom parameter $\nu =1$.
In this case, the support recovery problem is equivalent to locating the set of observations with mean shifts, $S=\{i:\mu(i)\neq 0\}$, where the mean shifts could take place in both directions.

Therefore, a theory for the chi-square model \eqref{eq:model-chisq} naturally lends itself to the study of two-sided alternatives in the Gaussian additive error model \eqref{eq:model-additive}.
In comparing such results with existing theory on one-sided alternatives, we will be able to quantify if, and how much of a price has to be paid for the additional uncertainty when we have no prior knowledge on the direction of the signals.

% In many applications, of course, restricting ourselves to one-sided tests is unrealistic.
% For example, in fMRI studies, the interest is in \emph{both} regions where average brain activities {increase} and where they {decrease}, when comparing the case group to the controls \citep{narayan2015two}. 
% In the challenging application of anomaly detection on Internet traffic streams, millions of IP addresses need to be scanned in real time to identify \emph{both} volumetric attacks and blackouts \citep{kallitsis2016amon}.
% Indeed, omnidirectional tests are the more natural choice in so-called discovery sciences where little to no prior knowledge is available.

\section{Contents}

Important notions and definitions in high-dimensional testing problems are recalled in Chapter \ref{chap:background}. 
We review related literature as well as key concepts and technical results used in our subsequent analyses.

In Chapter \ref{chap:phase-transitions} we study the sparse signal detection and support recovery problems for the additive error model \eqref{eq:model-additive} when components of the noise term $\epsilon$ are independent standard Gaussian random variables.
In particular, we point out several new \emph{phase transitions} in signal detection problems, and provide a unified account of recently discovered phase transitions in support recovery problems.
These result show that as the dimension $p\to\infty$, the tasks of detecting the existence of signals, or identifying the support set $S$ are either doable or impossible depending on the sparsity and signal sizes of the problems.
We also identify commonly used procedures that attain the performance limits in both detection and support recovery problems.

Both the Gaussianity assumption and the independence assumption are relaxed in Chapter \ref{chap:exact-support-recovery}.
Established are the necessary and sufficient conditions for exact support recovery in the high-dimensional asymptotic regime.
This is a major theoretical contribution of the thesis, solving, and expanding on, open problems in the literature (see \cite{butucea2018variable, gao2018fundamental}).
The analysis of support recovery problem is intimately related to a \emph{concentration of maxima} phenomena in the analysis of extremes.
The latter concept is key to understanding the role played by dependence in the phase transition phenomena of high-dimensional testing problems.
Using this probabilistic concept, we establish minimax optimality results that hold for a very large class of dependence structures.

The dependence condition defined by the concentration of maxima  concepts is further demystified in Chapter \ref{chap:URS} for Gaussian errors.
We offer a complete characterization of the concentration of maxima phenomenon, known as uniform relative stability, in terms of the covariance structures of the Gaussian arrays.
This result may be of independent interest since it relates to the so-called \emph{superconcentration} phenomenon coined by \cite{chatterjee2014superconcentration}.
See also, \cite{gao2018fundamental} and \citet*{kartsioukas2019rate}.

Chapter \ref{chap:GWAS} returns to high-dimensional multiple testing problems, and study the chi-square model \eqref{eq:model-chisq} inspired by the marginal association screening problems.
We establish four new phase-transition-type results in the chi-square model, and illustrate their practical implications in the GWAS application.
Our theory enables us to explain the long-standing empirical observation that small perturbations in the frequency and penetrance of genetic variations lead to drastic changes in the discoverability in genetic association studies.
% We also provide a user-friendly web-based software tool for planning, and reviewing, genome-wide association studies, published in \cite{gao2019upass}.

### 2020-08-17 2.background/2.AGG.tex
add draft converted from thesis

We introduce a fairly general class of distributions known as \ac{AGG} in this section, and state some properties about the tails of the AGG distributions.

\begin{definition} \label{def:AGG}
A distribution $F$ is called asymptotic generalized Gaussian with parameter $\nu>0$ (denoted $\text{AGG}(\nu)$) if
\begin{enumerate}
    \item $F(x)\in(0,1)$ for all $x\in\R$, and \smallskip
    \item $\log{\overline{F}(x)} \sim -\frac{1}{\nu}x^\nu$ and $\log{F(-x)} \sim -\frac{1}{\nu}(-x)^\nu,$ \label{eq:AGG}
\end{enumerate}
where $\overline{F}(x) = 1 - F(x)$ is the survival function, and $a(x)\sim b(x)$ is taken to mean $\lim_{x\to\infty} a(x)/b(x) = 1$.
\end{definition}

The AGG models include, for example, the Gaussian distribution ($\nu = 2$), and the Laplace distribution ($\nu = 1$) as special cases. 
Since the requirement is only placed on the tail behavior, this class encompasses a large variety of light-tailed models, and is commonly used in the literature on high-dimensional testing \citep{cai2007estimation, arias2017distribution}.

% On the other hand, the AGG models are themselves special cases of a more general class of tail models as we will see in Example \ref{exmp:AGG}.
% For simplicity of exposition, however, we shall focus on the $\text{AGG}(\nu)$ distributions, where the quantiles have explicit expressions.

\begin{proposition} \label{prop:quantile}
The $(1/p)$-th upper quantile of $\text{AGG}(\nu)$ is
\begin{equation} \label{eq:AGG-quantiles}
    u_{p} := F^\leftarrow(1-1/p) \sim \left(\nu\log{p}\right)^{1/\nu},\quad \text{as }\;p\to\infty,
\end{equation}
where $F^\leftarrow(q) = \inf_x\{x:F(x)\ge q\},\ q\in (0,1)$.
\end{proposition}
% The proof of Proposition \ref{prop:quantile} can be found in Section \ref{suppsec:AGG} of the supplement \citep{gao2018supplement}.
% We remark here that the family of density is log-concave for $\nu \ge 1$, therefore the oracle procedure is the thresholding procedure (See Section \ref{subsec:oracle}).

% \begin{proposition}[$(1 - 1/p)$-th quantile] \label{prop:quantile}
% Let 
% \begin{equation} \label{eq:quantiles-Appendix}
% u_p = F^{\leftarrow}(1-1/p),    
% \end{equation}
% then,
% \begin{equation}
% \lim_{p\to\infty} \frac{u_p}{\left(\nu\log{p}\right)^{1/\nu}} = 1.
% \end{equation}
% \end{proposition}
% 
\begin{proof}[Proof of Proposition \ref{prop:quantile}]
By definition of AGG, for any $\epsilon>0$, there is a constant $C(\epsilon)$ such that for all $x\ge C$, we have
$$
-\frac{1}{\nu}x^\nu(1+\epsilon) \le \log{\overline{F}(x)} \le -\frac{1}{\nu}x^\nu(1-\epsilon).
$$
Therefore, for all $x < x_l := \left((1+\epsilon)^{-1}\nu\log{p}\right)^{1/\nu}$, we have
\begin{equation} \label{eq:AGG-quantiles-proof-1}
    -\log{p} = -\frac{1}{\nu}x_l^\nu(1+\epsilon) \le \log{\overline{F}(x_l)} \le \log{\overline{F}(x)},
\end{equation}
and for all $x > x_u := \left((1-\epsilon)^{-1}\nu\log{p}\right)^{1/\nu}$, we have
\begin{equation} \label{eq:AGG-quantiles-proof-2}
    \log{\overline{F}(x)} \le \log{\overline{F}(x_u)} \le -\frac{1}{\nu}x_u^\nu(1-\epsilon) = -\log{p}.
\end{equation}
By definition of generalized inverse,
\begin{equation*}
    u_p := F^\leftarrow(1-1/p) = \inf\{x:\overline{F}(x)\le 1/p\} = \inf\{x:\log{\overline{F}(x)} \le -\log{p}\}.
\end{equation*}
We know from relations \eqref{eq:AGG-quantiles-proof-1} and \eqref{eq:AGG-quantiles-proof-2} that 
$$
[x_u, +\infty) \subseteq \{x:\log{\overline{F}(x)} \le -\log{p}\} \subseteq [x_l, +\infty),
$$
and so $x_l\le u_p \le x_u$, and the expression for the quantiles follow.
\end{proof}

### 2020-08-17 2.background/2.RV_and_RS.tex
add draft converted from thesis

The behavior of the maxima of identically distributed random variables has been studied extensively in the literature (see, e.g., \cite{leadbetter2012extremes,resnick2013extreme,embrechts2013modelling,de2007extreme} 
and the references therein). 
% We show in this subsection that the maxima of errors with rapidly varying tails can be bounded above using quantiles of their marginal distribution, regardless of their dependence structure; this was a key step in the proof of Theorem \ref{thm:sufficient}.
The concept of rapid variation plays an important role in the light-tailed case.

\begin{definition}[Rapid variation] \label{def:rapid-variation}
The survival function of a distribution, $\overline{F}(x) = 1 - F(x)$, is said to be rapidly varying if
\begin{equation}\label{e:def:rapid-variation}
\lim_{x\to\infty} \frac{\overline{F}(tx)}{\overline{F}(x)} 
    = \begin{cases}
    0, & t > 1\\
    1, & t = 1\\
    \infty, & 0 < t < 1
\end{cases}.
\end{equation}
\end{definition}

When $F(x)<1$ for all finite $x$, \citet{gnedenko1943distribution} showed that the distribution $F$ has rapidly varying tails if and only if the maxima of independent observations from $F$ are \emph{relatively stable} in the following sense.
\begin{definition}[Relative stability] \label{def:RS}
Let $\epsilon_p = \left(\epsilon_p(i)\right)_{i=1}^p$ be a sequence of random variables with identical marginal distributions $F$. 
Define the sequence $(u_p)_{p=1}^\infty$ to be the $(1-1/p)$-th generalized quantile of $F$, i.e., 
\begin{equation} \label{eq:quantiles}
    u_p = F^\leftarrow(1 - 1/p).
\end{equation}
The triangular array ${\cal E} = \{\epsilon_p, p\in\N\}$ is said to have relatively stable (RS) maxima if
\begin{equation} \label{eq:RS-condition}
    \frac{1}{u_{p}} M_p := \frac{1}{u_{p}} \max_{i=1,\ldots,p} \epsilon_p(i) \xrightarrow{\P} 1,\quad \text{as }\;p\to\infty.
\end{equation}
\end{definition}

In the case of independent and identically distributed $\epsilon_p(i)$'s, \citet{barndorff1963limit} and \citet{resnick1973almost} obtained necessary and sufficient conditions for the \emph{almost sure stability} of maxima, where the convergence in \eqref{eq:RS-condition} holds almost surely.

While relative stability (and almost sure stability) is well-understood in the independent case, the role of dependence has not been fully explored.
We start this investigation with a small refinement of Theorem 2 in \citet{gnedenko1943distribution} valid under arbitrary dependence.

\begin{proposition}[Rapid variation and relative stability] \label{prop:rapid-varying-tails}
Assume that the array ${\cal E}$ consists of identically distributed random 
variables with cumulative distribution function $F$, where $F(x)<1$ for all finite $x>0$. 
\begin{enumerate}
    \item If $F$ has rapidly varying right tail, then for all $\delta>0$,
        \begin{equation} \label{eq:rapid-varying-tails}
            \P\left[\frac{1}{u_p} M_p\le1+\delta\right] \ge 1 - \frac{\overline F((1+\delta)u_p)}{\overline F(u_p)} \to 1.
        \end{equation}
    \item If, in addition, the array ${\cal E}$ has independent entries, then it is relatively stable if and only if $F$ has rapidly varying tail.
    \label{prop:rapid-varying-tails_part-ii}
\end{enumerate}
\end{proposition}

\begin{proof}[Proof of Proposition \ref{prop:rapid-varying-tails}] 
By the union bound and the fact that 
$p\overline F(u_p) \le 1$, we have
\begin{align}\label{e:prop:rapid-varying-tails_part-i-1}
\P [ M_p > (1+\delta)u_p] \le p \overline F((1+\delta)u_p)
 \le \frac{\overline F((1+\delta)u_p)}{\overline F(u_p)}.
\end{align}
In view of \eqref{e:def:rapid-variation} (rapid variation) and the fact that $u_p\to\infty$, as $p\to\infty$, the right-hand side of \eqref{e:prop:rapid-varying-tails_part-i-1} vanishes 
as $p\to\infty$, for all $\delta>0$.  This completes the proof of \eqref{eq:rapid-varying-tails}. Part 2 is a re-statement of the classic result due to Gnedenko in \cite{gnedenko1943distribution}.
\end{proof}

We next demonstrate that Gaussian, Exponential, Laplace, and Gamma distributions all have rapidly varying tails.

% \begin{corollary} \label{cor:AGG-is-RS}
% If $F\in\text{AGG}(\nu)$, $\nu>0$, an independent array ${\cal E}$ is relatively stable. Further, $\text{AGG}(\nu)$ is the only class of model with $u_{p} \sim \left(\nu\log{p}\right)^{1/\nu}$.
% \end{corollary}
% 
% \begin{proof}[Proof of Corollary \ref{cor:AGG-is-URS}]
% By Proposition \ref{prop:rapid-varying-tails}, it is enough to show that in the AGG model,  $\overline{F}$ has rapidly varying tail. 
% By definition of the AGG tails \eqref{def:AGG}, we have
% $$
% \lim_{t\to\infty} \frac{\log{\left(\overline{F}(tx)\Big/\overline{F}(t)\right)}}{-\frac{1}{\nu}t^\nu(x^\n% u-1)} = 1,
% $$
% where the denominator tends to $+\infty$ or $-\infty$ depending on whether $0<x<1$ or $x>1$.
% Therefore, we must have $\overline{F}(tx) / \overline{F}(t)$ converging to $\infty$ or 0 in the correct range of $x$'s; the case where $x=1$ is trivial.
% The last claim follows from the expression for AGG quantiles; see Proposition \ref{prop:quantile}.
% \end{proof}

\begin{example}[Generalized AGG] \label{exmp:AGG}
A distribution is said to have \emph{Generalized AGG} right tail, if $\log{\overline{F}}$ is regularly varying,
\begin{equation} \label{eq:GAGG}
    \log{\overline{F}(x)} = - x^\nu L(x),
\end{equation}
where $\nu>0$ and $L: (0,+\infty)\to(0,+\infty)$ is a slowly varying function. (A function is said to be slowly varying if $\lim_{x\to\infty}L(tx)/L(x) = 1$ for all $t>0$.) Note that the $\text{AGG}(\nu)$ model corresponds to the special case where $L(x)\to 1/\nu$, as $x\to\infty$.

Relation \eqref{eq:rapid-varying-tails} holds for all arrays $\cal E$ with \emph{generalized} AGG marginals; if the entries are independent, the maxima are relatively stable. 
This follows directly from Proposition \ref{prop:rapid-varying-tails}, once we show that $F$ has rapidly varying tail. 
Indeed, by \eqref{eq:GAGG}, we have
$$
\log{\left(\overline{F}(tx)\Big/ \overline{F}(x)\right)} = - L(x)x^\nu\left(t^\nu\frac{L(tx)}{L(x)} - 1\right),
$$
which converges to $-\infty$, 0, and $+\infty$, as $x\to\infty$, when $t>1$, $t=1$, and $t<1$, respectively, since $x^\nu L(x)\to\infty$ as $x\to\infty$ by definition of $L$.
\end{example}

The \ac{AGG} class encompasses a wide variety of rapidly varying tail models such as Gaussian and double exponential distributions. The larger class \eqref{eq:GAGG} is needed, however, for the Gamma distribution.

More generally, distributions with heavier tails (e.g., log-normal) and lighter tails (e.g., Gompertz) outside the generalized AGG class \eqref{eq:GAGG} may also possess rapidly varying tails;
heavy-tailed distributions like the Pareto and t-distributions, on the other hand, do not.
These alternative classes of models are will be introduced when we study the phase transitions in Chapter \ref{chap:exact-support-recovery}. 
%For brevity, we focus here on the $\text{AGG}(\nu)$ models.

### 2020-08-17 2.background/2.asymptotics.tex
add draft converted from thesis

We look to derive useful asymptotic approximations for high dimensional problems, and analyze the afore-mentioned procedures in the regime where the dimensionality of the observations diverge.
Throughout this text, we consider triangular arrays of observations as described in Models \eqref{eq:model-additive} and \eqref{eq:model-chisq}, and study the performance of procedures in the signal detection and support recovery tasks when 
\begin{equation*}
  p\to\infty.
\end{equation*}
The criteria for success and failure in support recovery problems under this high-dimensional asymptotic regime are defined as follows.
\begin{definition} \label{def:exact-recovery-success-failure}
We say a sequence of procedures $\mathcal{R} = \mathcal{R}_p$ succeeds asymptotically in the detection problem (and respectively, exact, exact-approximate, approximate-exact, and approximate support recovery problem) if 
\begin{equation} \label{eq:support-recovery-success}
    \mathrm{risk}^{\mathrm{P}}(\mathcal{R}) \to 0, \quad \text{as}\quad p\to\infty,
\end{equation}
where $\mathrm{P}=\mathrm{D}$ (respectively, $\mathrm{E}$, $\mathrm{EA}$, $\mathrm{AE}$, $\mathrm{A}$).

Conversely, we say the exact support recovery fails asymptotically in the detection problem (and respectively, exact, exact-approximate, approximate-exact, and approximate support recovery problem) if 
\begin{equation} \label{eq:support-recovery-failure}
    \liminf\mathrm{risk}^{\mathrm{P}}(\mathcal{R}) \ge 1, \quad \text{as}\quad p\to\infty,
\end{equation}
where $\mathrm{P}=\mathrm{D}$ (respectively, $\mathrm{E}$, $\mathrm{EA}$, $\mathrm{AE}$, $\mathrm{A}$).
\end{definition}
The choice of the constant 1 in the definition \eqref{eq:support-recovery-failure} allows us to declare failure for trivial testing procedures. 
For example, trivial deterministic procedures that always reject, and ones that always fail to reject, both have statistical risks 1 in either the detection or the support recovery problem.
Similarly, a trivial randomized procedure that reject the nulls uniformly at random also has risk of 1, and is declared as a failure in both problems.

% Similarly, we define the criteria for asymptotic success and failure for approximate support recovery as follows.
% \begin{definition} \label{def:approx-recovery-success-failure}
% We say a sequence of procedures $\mathcal{R} = \mathcal{R}_p$ succeeds asymptotically in the approximate support recovery problem if 
% \begin{equation} \label{eq:approx-recovery-success}
%     \mathrm{risk}^{\mathrm{A}}(\mathcal{R}) \to 0, \quad \text{as}\quad p\to\infty.
% \end{equation}
% We say the approximate support recovery fails asymptotically if 
% \begin{equation} \label{eq:approx-recovery-failure}
%     \liminf\mathrm{risk}^{\mathrm{A}}(\mathcal{R}) \ge 1, \quad \text{as}\quad p\to\infty.
% \end{equation}
% \end{definition}

% The performance of procedures in terms of the criteria in Definition \ref{def:exact-recovery-success-failure} 
% % and \ref{def:approx-recovery-success-failure} 
% will be analyzed in Sections \ref{subsec:exact-support-recovery-boundary} and \ref{subsec:approx-support-recovery-boundary}.

{\bf Signal detection.}
The asymptotic behavior of the statistical risk of signal detection problems \eqref{eq:risk-detection} in high dimensions was first studied in \cite{ingster1998minimax}, where a so-called phase transition phenomena was discovered for sparse additive models \eqref{eq:model-additive} with independent and Gaussian components. 
That is, depending on the signal size and sparsity of the signal $\mu$, the detection risk either vanishes, or has a liminf of 1 when we apply the theoretically optimal \ac{LR} test, as dimensionality of the problem diverges.
The \ac{LR} test, unfortunately, relies on the knowledge of signal sparsity and signal sizes which are often unknown.
The sparsity-and-signal-size-agnostic statistic \ac{HC} was identified to attain such optimal performance limits in sparse Gaussian models in \cite{donoho2004higher}. 
A modified goodness-of-fit test statistic in \citet{zhang2002powerful}, and two statistics based on thresholded-$L_1$ and $L_2$ norms in \cite{zhong2013tests} were also shown to be asymptotically optimal in the detection problem.
Recent studies have also focused on the behavior of detection risk \eqref{eq:risk-detection} in dense and scale mixture models \cite{cai2011optimal}, under general distributional assumptions \citep{cai2014optimal, arias2017distribution1}, as well as when errors are dependent \citep{hall2010innovated}.
A comprehensive review focusing on the role of \ac{HC} in detection problems can be found in \cite{donoho2015special}.
Notwithstanding the extensive literature on the detection problem, performances of simple statistics such as $L_q$ norms \eqref{eq:Lq-norm} and sums \eqref{eq:sum-statistic}, to the best of our knowledge, have only been sparingly documented. 
We gather relevant results in Chapter \ref{chap:phase-transitions}, and make several new reports on the performance of statistics commonly used in practice.

\medskip

{\bf Exact support recovery.}
There is a wealth of literature on the so-called sparsistency (i.e., $\P[\widehat{S} = S]\to 1$ as $p\to\infty$) problem in the regression context. 
Sparsistency problems were pursued, among many others, by \citet{zhao2006model} and \citet{wasserman2009high} in the high-dimensional regression setting (where the number of samples $n\ll p$), and by \citet*{meinshausen2006high} in graphical models.
Although there have been numerous studies on the sufficient conditions for sparsistency, efforts on necessary conditions have been scarce.
Notable exceptions include \cite{wainwright2009information, wainwright2009sharp} and \cite{comminges2012tight} in regression problems.
We refer readers to the recent book by \cite{wainwright2019high} (and in particular, the bibliographical sections of Chapters 7 and 15) for a comprehensive review.

Elaborate asymptotic minimax optimality results under the Hamming loss were derived for methods proposed in \cite{ji2012ups} and \cite{jin2014optimality} for regression problems.
More recently, \cite{butucea2018variable} also obtained similar minimax optimality results for a specific procedure in the Gaussian additive error model \eqref{eq:model-additive} in terms of the expected Hamming loss.

Nevertheless, two important questions remained unanswered.
Namely, precise phase-transition-type results for the exact support recovery risk \eqref{eq:risk-exact} and for the support recovery probability \eqref{eq:risk-prob} 
% --- akin to that obtained in \cite{arias2017distribution} for the approximate support recovery risk \eqref{eq:risk-approximate} --- 
have not been established.
And secondly, performance of commonly used statistical procedures reviewed in Section \ref{sec:statistical-procedures}
in terms of these risk metrics have not been studied.
Resolving these two issues, we show in this text that several well-known FWER-controlling procedures --- including Bonferroni's procedure --- are optimal in the additive error model under both one-sided and two-sided alternatives.
% these results have appeared in \cite{gao2018fundamental} and \cite{gao2019five}

\medskip

{\bf Approximate support recovery.}
Performance limits of FDR-controlling procedures in the support recovery problem have been actively studied in recent years.
The asymptotic optimality of the Benjamini-Hochberg procedure
% in the Gaussian scale mixture model 
was analyzed under decision theoretic frameworks in \cite{genovese2002operating, bogdan2011asymptotic, neuvial2012false}, with main focus on location/scale models. 
In particular, these papers show that the statistical risks of the procedures come close to that of the oracle procedures under suitable asymptotic regimes.
Strategies for dealing with multiple testing under general distributional assumptions can be found in, e.g., \cite{efron2004large}, \cite{storey2007optimal}, and \cite{sun2007oracle}.
The two-sided alternative in the additive error model was featured as the primary example in \cite{sun2007oracle}.

In the additive error model \eqref{eq:model-additive} under independent Gaussian errors and one-sided alternatives \eqref{eq:global-test-one-sided},
\cite{arias2017distribution} showed that a phase transition exists for  the approximate support recovery risk \eqref{eq:risk-approximate}.
The \ac{BH} procedure \cite{benjamini1995controlling}, and the Cand\'es-Barber procedure \cite{barber2015controlling} was identified to be asymptotically optimal. % \citet{rabinovich2017optimal} further established the rate-optimality of both procedures under the same regime.
However, \cite{arias2017distribution}, as all related work so far, assumed the non-nulls to follow a common alternative distribution.
We derive a new phase transitions result that relaxes this assumption on the alternatives in Chapter \ref{chap:phase-transitions}.

\medskip

{\bf Asymmetric statistical risks.}
Although weighted sums of false discovery and non-discovery have been studied in the literature mentioned above, none has considered simultaneous family-wise error control and marginal, location-wise power requirements.
As a result, asymmetric statistical risks such as \eqref{eq:risk-exact-approx} and \eqref{eq:risk-approx-exact} have not been investigated.
As argued in Section \ref{sec:risks}, properties of these asymmetric risks are of important practical concern in applications such as GWAS.
We study the asymptotic behavior of these risks in Chapters \ref{chap:phase-transitions} and \ref{chap:GWAS} of this text.
% ; the results therein have appeared in \cite{gao2019five}.
% these results have appeared in \cite{gao2018fundamental} and \cite{gao2019five}

\medskip

{\bf Chi-square models and GWAS.}
The high-dimensional chi-square model \eqref{eq:model-chisq} seemed to have received little attention in the literature.
While the sparse signal detection problem in the chi-square model has been studied \cite{donoho2004higher}, to the best of our knowledge,  asymptotic limits of the support recovery problems have not been studied.
The chi-squared model and the motivating GWAS application are analyzed in Chapter \ref{chap:GWAS}.
The results obtained therein help us understand the sharp power decay in GWAS that have been long observed \citep{bush2012genome} and recently reviewed and visualized \citep{gao2019upass}.

% Results in Chapter \ref{chap:GWAS} now appear in \cite{gao2019five}.
% We also analyzed asymptotic equivalences of several additional common association tests, and implement power calculations for GWAS in a software tool \cite{gao2019upass}. 
% The software streamlines power analysis with a canonical disease model invariant parametrization, and therefore enables forensics of reported findings in genetic association studies.
% We introduce the software and illustrate its use in the appendix.

### 2020-08-17 2.background/2.risks_relations.tex
add draft converted from thesis

We now elaborate on the relationship between statistical risks, as promised in Section \ref{sec:risks}.
The first lemma concerns the asymptotic relationship between the probability of exact recovery \eqref{eq:risk-prob} and the risk of exact support recovery \eqref{eq:risk-exact}.

\begin{lemma} \label{lemma:risk-exact-recovery-probability}
For any sequence of procedures for support recovery $\mathcal{R} = \mathcal{R}_p$, we have, 
%The probability of exact recovery $\P[\widehat{S} = S]$, and risk of exact support recovery $\mathrm{risk}^{\mathrm{E}}$, defined in \eqref{eq:risk-exact}, are related as follows,
\begin{equation} \label{eq:exact-recovery-implies-risk-0}
    \P[\widehat{S} = S] \to 1 \iff \mathrm{risk}^{\mathrm{E}}(\mathcal{R})\to0,
\end{equation}
and
\begin{equation} \label{eq:failure-recovery-implies-risk-1}
    \P[\widehat{S} = S] \to 0 \implies \liminf\mathrm{risk}^{\mathrm{E}}(\mathcal{R})\ge1,
\end{equation}
as $p\to\infty$. Dependence on $p$ was suppressed for notational convenience.
\end{lemma}

\begin{proof}[Proof of Lemma \ref{lemma:risk-exact-recovery-probability}]
Notice that $\{\widehat{S}=S\}$ implies $\{\widehat{S}\subseteq S\} \cap \{\widehat{S}\supseteq S\}$, therefore we have for every fixed $p$,
\begin{equation} \label{eq:risk-exact-recovery-probability-proof-1}
    \mathrm{risk}^{\mathrm{E}} 
    = 2 - \P[\widehat{S} \subseteq S] - \P[S \subseteq \widehat{S}] \\
    \le 2 - 2\P[\widehat{S}=S].
\end{equation}
On the other hand, since $\{\widehat{S}\neq S\}$ implies $\{\widehat{S}\not\subseteq S\} \cup \{\widehat{S}\not\supseteq S\}$, we have for every fixed $p$,
\begin{equation} \label{eq:risk-exact-recovery-probability-proof-2}
    1 - \P[\widehat{S}=S]
    = \P[\widehat{S}\neq S]
    \le 2 - \P[\widehat{S} \subseteq S] - \P[S \subseteq \widehat{S}]
    = \mathrm{risk}^{\mathrm{E}}. 
\end{equation}
Relation \eqref{eq:exact-recovery-implies-risk-0} follows from \eqref{eq:risk-exact-recovery-probability-proof-1} and \eqref{eq:risk-exact-recovery-probability-proof-2}, and Relation \eqref{eq:failure-recovery-implies-risk-1} from \eqref{eq:risk-exact-recovery-probability-proof-2}.
\end{proof}

By virtue of Lemma \ref{lemma:risk-exact-recovery-probability}, it is sufficient to study the probability of exact support recovery $\P[\widehat{S}=S]$ in place of $\mathrm{risk}^{\mathrm{E}}$, if we are interested in the asymptotic properties of the risk in the sense of \eqref{eq:support-recovery-success} and \eqref{eq:support-recovery-failure}.
% (The converse, discussed in Section \ref{sec:discussions} below, is not true.)

\medskip

Keen readers must have noticed the asymmetry in Relation \eqref{eq:failure-recovery-implies-risk-1} when we discussed the relationship between the exact support recovery risk \eqref{eq:risk-exact} and the probability of exact support recovery \eqref{eq:risk-prob}.

%The converse of \eqref{eq:failure-recovery-implies-risk-1} is not true.
While a trivial procedure that never rejects and a procedure that always rejects both have $\mathrm{risk}^{\mathrm{E}}$ equal to 1, the converse is not true.
For example, it is possible that a procedure selects the true index set $S$ with probability $1/2$, but makes one false inclusion \emph{and} one false omission simultaneously the other half of the time. 
In this case the procedure will have 
$$\mathrm{risk}^{\mathrm{E}} = 1, \quad \text{and} \quad \P[\widehat{S}=S] = 1/2,$$
showing that the converse of Relation \eqref{eq:failure-recovery-implies-risk-1} is in fact false.

The same argument applies to $\mathrm{risk}^{\mathrm{A}}$:
a procedure may select the true index set $S$ with probability $1/2$, but makes enough false inclusions and omissions other half of the time, so that $\mathrm{risk}^{\mathrm{A}}$ is equal to one.
Therefore, although the class of methods with risks equal to or exceeding 1 certainly contains the trivial procedures that we mentioned, they are not necessarily ``useless'' as some researchers have claimed (c.f., \citet{arias2017distribution}, Remark 2).

\medskip

Upper and lower bounds for \ac{FDR} and \ac{FNR} can be immediately derived by replacing the numerators in \eqref{eq:FDR-FNR} with the Hamming loss,
\begin{equation} \label{eq:Hamming-loss-FDR-FNR-bound}
    \E\left[\frac{H(\widehat{S}, S)}{\max\{|\widehat{S}|, |S|, 1\}}\right] 
    \le \mathrm{FDR} + \mathrm{FNR}
    \le \E\left[\frac{H(\widehat{S}, S)}{\max\{\min\{|\widehat{S}|, |S|\}, 1\}}\right].
\end{equation}
Therefore, it is sufficient, but not necessary, that the Hamming loss vanish in order to have vanishing approximate support recovery risks \eqref{eq:risk-approximate}.

\medskip

Turning to the relationship between the probability of exact support recovery \eqref{eq:risk-prob} and Hamming loss \eqref{eq:Hamming-loss}, we point out a natural lower bound of the former using the expectation of the latter,
\begin{equation} \label{eq:Hamming-loss-lower-bound}
    \mathbb{P}[\widehat S = S] 
    \ge 1 - \mathbb{E}[H(\widehat S, S)]
    = 1 - \sum\limits_{i=1}^p\E\left|\mathbbm{1}_{\widehat{S}}(i)- \mathbbm{1}_{S}(i)\right|.
\end{equation}
A key observation in Relation \eqref{eq:Hamming-loss-lower-bound} is that the expected Hamming loss decouples into $p$ terms, and dependence of the estimates $\mathbbm{1}_{\widehat{S}}(i)$ among the $p$ locations no longer plays a role in the sum.
Therefore, studying support recovery problems via the expected Hamming loss is not very informative especially under severe dependence, as the bound \eqref{eq:Hamming-loss-lower-bound} may become {very} loose.
Vanishing Hamming loss is again sufficient, but not necessary for 
$\P[\widehat{S}=S]$ or the exact support recovery risk to fo to zero.
% the probability of exact support recovery --- and hence the exact support recovery risk --- to go to zero.

### 2020-08-17 2.background/2.statistical_procedures.tex
add draft converted from thesis

We review some popular procedures for signal detection and signal support recovery tasks in this section.

{\bf Signal detection.}
One of the commonly used statistics in sparse signal detection problems such as \eqref{eq:global-test-additive} and \eqref{eq:global-test-chisq} are the $L_q$ norms of the observations $x$,
\begin{equation} \label{eq:Lq-norm}
   L_q(x) = \left(\sum_{i=1}^p{|x(i)|^q}\right)^{1/q}.
\end{equation}
Typical choices of $q$ include $q=1, 2$ and $\infty$, where $L_\infty(x)$ is interpreted as the limit of $L_q(x)$ norms as $q\to\infty$, and is equivalent to $\max_{i}|x(i)|$.
Test procedures based on \eqref{eq:Lq-norm} may then be written as $T(\mathcal{R}(x)) = \mathbbm{1}_{(t,+\infty)}(L_q(x))$, where the cutoff $t$ can be chosen to control the Type I error at desired levels.

While \eqref{eq:Lq-norm} measures the deviation of the data from the origin in an omnidirectional manner, statistics that are tailored to the alternatives can be used in the hopes of power improvement if the directions of the alternatives are known.
For example, if we were to test positive mean shifts in the additive error model \eqref{eq:model-additive} in the one-sided alternative,
\begin{equation} \label{eq:global-test-one-sided}
    %\mathcal{H}_0: \mu(i) = 0, \;i=1,\ldots,p,
    %\quad\text{v.s.}\quad 
    \mathcal{H}_1: \mu(i)> 0, \; \text{for some }i\in\{1,\ldots,p\},
\end{equation}
one might consider monitoring the sum (or equivalently, the arithmetic average) of the observations, 
\begin{equation} \label{eq:sum-statistic}
    S(x) := \sum_{i=1}^p{x(i)},
\end{equation}
or the maximum of the observations,
\begin{equation} \label{eq:max-statistic}
    M(x) := \max_{i=1,\ldots,p}{x(i)}.
\end{equation}
Other tests based on the empirical \ac{CDF} are also available.
Assuming the same one-sided alternative, let 
\begin{equation}
    p(i) = 1 - \sup\{F_i(y)\,:\,y<x(i)\}, \quad i = 1,\ldots,p,
\end{equation}
be the p-values of the individual observations, where $F_i$ is the \ac{CDF} of the $i$-th component $x(i)$ under $\mathcal{H}_0$.
We define empirical \ac{CDF} of the p-values as
\begin{equation}
    \widehat{F}_p(t) = 
    \frac{1}{p} \sum_{i=1}^p \mathbbm{1}_{(-\infty, t]}(p(i)).
\end{equation}
Viewed as random elements in the space of c\`adl\`ag functions with the Skorohod $J_1$ topology, the centered and scaled \ac{CDF}s converge weakly to a Brownian bridge,
\begin{equation*}
    \left\{\sqrt{p}\left(\widehat{F}_p(t) - t\right)\right\}_{t\in[0,1]} 
    % \stackrel{J_1}{\longrightarrow} 
    \implies
    \left\{\mathbb{B}(t)\right\}_{t\in[0,1]},
\end{equation*}
under the global null $\mathcal{H}_0$ and mild continuity assumptions on the $F_i$'s \citep{skorokhod1956limit}. 
Therefore, goodness-of-fit statistics such as Kolmogorov-Smirnov distance \citep{smirnov1948table}, Cramer-von Mises-type statistics \citep{cramer1928composition, anderson1952asymptotic} that measure the departure from this limiting behavior can be used for testing $\mathcal{H}_0$ against $\mathcal{H}_1$.
Of particular interest is the \ac{HC} statistic, first proposed by \cite{tukey1976lecture},
\begin{equation*} %\label{eq:HC-statistic}
    HC(x) = 
    \max_{0\le t\le\alpha_0}\frac{\widehat{F}_p(t) - t}{\sqrt{t(1 - t)/p}}.
\end{equation*}

Performance of these statistics in high-dimensional sparse signal detection problems will be reviewed in Section \ref{sec:asymptotics}, and analyzed in Chapter \ref{chap:phase-transitions}.

\medskip

{\bf Signal support recovery.}
In signal support recovery tasks, we shall study the performance of five procedures, all of which belong to the broad class of thresholding procedures.
\begin{definition}[Thresholding procedures]
A thresholding procedure for estimating the support 
$S:=\{i\, :\, \lambda(i)\neq0\}$ is one that takes on the form
\begin{equation} \label{eq:thresholding-procedure}
    \widehat{S} = \left\{i\,|\,x(i) \ge t(x)\right\},
\end{equation}
where the threshold $t(x)$ may depend on the data $x$.
\end{definition}

Examples of thresholding procedures include ones that aim to control FWER \eqref{eq:FWER-FWNR} --- Bonferroni's \cite{dunn1961multiple}, Sid\'ak's \citep{vsidak1967rectangular}, Holm's \citep{holm1979simple}, and Hochberg's procedure \citep{hochberg1988sharper} --- as well as procedures that target FDR \eqref{eq:FDR-FNR}, such as the Benjamini-Hochberg \cite{benjamini1995controlling} and the Cand\'es-Barber procedure \cite{barber2015controlling}.
Indeed, the class of thresholding procedures \eqref{eq:thresholding-procedure} is so general that it contains most (but not all) of the statistical procedures in the multiple testing literature.
% \cite{roquain2011type}.

% \subsection{FWER-controlling procedures}
% \label{subsec:FWER-controlling-procedures}

We review five thresholding procedures, starting with the well-known Bonferroni's procedure which aims at controlling family-wise error rates.
\begin{definition}[Bonferroni's procedure]
Suppose the errors $\epsilon(i)$'s have a common marginal distribution $F$, Bonferroni's procedure with level $\alpha$ is the thresholding procedure that uses the threshold
\begin{equation} \label{eq:Bonferroni-procedure}
    t_p = F^{\leftarrow}(1 - \alpha/p).
\end{equation}
where  $F^{\leftarrow}(u)=\inf{\left\{x:F(x)\ge u\right\}}$ is the generalized inverse function.
\end{definition}
% It is easy to see that the family-wise error rate (FWER) is controlled at level $\alpha$ by applying the union bound, regardless of the error-dependence structure (see e.g.\ Relation \eqref{eq:Bonferroni-FWER-control}, below).
The Bonferroni procedure is deterministic (i.e., non data-dependent), and only depends on the dimension of the problem and the null distribution.
A closely related procedure is Sid\'ak's procedure \citep{vsidak1967rectangular},
which is a more aggressive (and also deterministic) thresholding procedure that uses the threshold
\begin{equation} \label{eq:Sidak-procedure}
    t_p = F^{\leftarrow}((1 - \alpha)^{1/p}).
\end{equation}
% can be shown to control FWER in the case independent errors.

The third procedure, strictly more powerful than Bonferroni's, is the so-called Holm's procedure \citep{holm1979simple}.
On observing the data $x$, its coordinates can be ordered from largest to smallest
$x(i_1) \ge x(i_2)  \ge \ldots \ge x(i_p)$,
where $(i_1, \ldots, i_p)$ is a permutation of $\{1, \ldots, p\}$. 
Denote the order statistics as $x_{[1]}, x_{[2]}, \ldots, x_{[p]}$.
\begin{definition}[Holm's procedure]
Let $i^*$ be the largest index such that
$$
\overline{F}(x_{[i]}) \le \alpha / (p-i+1),\quad \text{for all }\;i\le i^*.
$$
Holm's procedure with level $\alpha$ is the thresholding procedure with threshold
\begin{equation} \label{eq:Holm-procedure}
    t_p(x) = x_{[i^*]}.
\end{equation}
\end{definition}
In contrast to the Bonferroni procedure, Holm's procedure is data-dependent.
% It can be shown that Holm's procedure also controls FWER at $\alpha$ level, regardless of dependence in the data.
A closely related, more aggressive (data-dependent) thresholding procedure is Hochberg's procedure \citep{hochberg1988sharper}
%\begin{definition}[Hochberg's procedure]
%Hochberg's procedure 
which replaces the index $i^*$ in Holm's procedure with the largest index such that
$$
\overline{F}(x_{[i]}) \le \alpha / (p-i+1).
$$
Notice that both Holm's procedure and Hochberg's procedure compare p-values to the same thresholds $\alpha / (p-i+1)$.
However, Holm's procedure only rejects the set of hypotheses whose p-values are all smaller than their respective thresholds.
On the other hand, Hochberg's procedure rejects the set of hypotheses as long as the largest of their p-values fall below its threshold, and therefore, can be more powerful than Holm's procedure. 
%where  $\overline{F}(x)=1-F(x)$ is the survival function.
%\end{definition}

It can be shown that Bonferroni's procedure and Holm's procedure both control FWER at their nominal levels, regardless of dependence in the data \citep{holm1979simple}.
In contrast, Sid\'ak's procedure and Hochberg's procedure control FWER at nominal levels when data are independent \citep{vsidak1967rectangular, hochberg1988sharper}.

Last but not least, we review the \ac{BH} procedure, which aims at controlling \ac{FDR} in \eqref{eq:FDR-FNR}, proposed by  \cite{benjamini1995controlling}.

Recall the order statistics of our observations $x_{[1]} \ge x_{[2]}  \ge \ldots \ge x_{[p]}$.
\begin{definition}[Benjamini-Hochberg's procedure]
Let $i^*$ be the largest index such that
$$
\overline{F}(x_{[i]}) \le \alpha i/p.
$$
The Benjamini-Hochberg procedure with level $\alpha$ is the thresholding procedure with threshold
\begin{equation} \label{eq:BH-procedure}
    t_p(x) = x_{[i^*]},
\end{equation}
\end{definition}
The \ac{BH} procedure is shown to control the FDR at level $\alpha$ when the $x(i)$'s are independent \citep{benjamini1995controlling}.
Variations of the \ac{BH} procedure have been proposed to control the \ac{FDR} under dependent observations \citep{benjamini2001control}.

% We now turn to discuss the framework for anlayzing the asymptotic risks in high dimensions.

Performance of these procedures in high-dimensional sparse signal support recovery problems will be reviewed in Section \ref{sec:asymptotics}, and analyzed in Chapters \ref{chap:phase-transitions}, \ref{chap:exact-support-recovery}, and \ref{chap:GWAS}.

### 2020-08-17 2.background/2.statistical_risks.tex
add draft converted from thesis

We define the statistical risk metrics for signal detection and signal support recovery problems in this section.

{\bf Signal detection.}
Recall that in sparse signal detection problems, our goal is to come up with a procedure, $\mathcal{R}(x)$, such that the null hypothesis is rejected if the data $x$ is deemed incompatible with the null.
In the example of additive error models \eqref{eq:model-additive}, we wish to tell apart two hypotheses
\begin{equation} \label{eq:global-test-additive}
    \mathcal{H}_0: \mu(i) = 0, \;i=1,\ldots,p,
    \quad\text{v.s.}\quad 
    \mathcal{H}_1: \mu(i)\neq 0, \; \text{for some }i\in\{1,\ldots,p\},
\end{equation}
based on the $p$-dimensional observation $x$.
Similarly in the chi-square model \eqref{eq:model-chisq}, we look to test
\begin{equation} \label{eq:global-test-chisq}
    \mathcal{H}_0: \lambda(i) = 0, \;i=1,\ldots,p,
    \quad\text{v.s.}\quad 
    \mathcal{H}_1: \lambda(i)\neq 0, \; \text{for some }i\in\{1,\ldots,p\}.
\end{equation} 
Since the decision is binary, we may write the outcome of the procedure in the form of an indicator function, $T(\mathcal{R}(x))\in\{0,1\}$, where the function $T$ takes on value 1 if the null is to be rejected in favor of the alternative, and 0 if we fail to reject the null. 
The Type I and Type II errors of the procedure, i.e., the probability of wrong decisions under the null hypothesis $\mathcal{H}_0$ and alternative hypothesis $\mathcal{H}_1$, respectively, are defined as 
\begin{equation} \label{eq:type-II-error}
    \alpha(\mathcal{R}) := \P_{\mathcal{H}_0}\left(T(\mathcal{R}(x))=1\right)
    \quad \text{and} \quad
    \beta(\mathcal{R}) := \P_{\mathcal{H}_1}\left(T(\mathcal{R}(x))=0\right).
\end{equation}
The Neyman-Pearson framework of hypothesis testing then seeks tests that minimize the Type II error of the test, while controlling the Type I error of the test at low levels.
We are particularly interested in the sum of the two errors, 
\begin{equation} \label{eq:risk-detection}
    \mathrm{risk}^{\mathrm{D}}(\mathcal{R}) := \alpha(\mathcal{R}) + \beta(\mathcal{R}),
\end{equation}
which shall be referred to as the risk of signal detection (of the procedure $\mathcal{R}$).
It is trivial that a small $\mathrm{risk}^{\mathrm{D}}$ would imply both small Type I and Type II errors of the procedure.

\medskip

{\bf Signal support recovery.}
Turning to support recovery problems, our goal is to design a procedure $\mathcal R$ that produces a set estimate $\widehat{S}$ of the true index set of relevant variables $S$.
% The true index set, of course, depends on the modeling assumptions. 
For example, in the sparse additive error model \eqref{eq:model-additive} we aim to estimate $S=\{i:\mu(i)\neq 0\}$, while in the sparse chi-square model \eqref{eq:model-chisq} the goal is to estimate $S=\{i:\lambda(i)\neq 0\}$.
Formally, one should write $\widehat{S}(\mathcal{R}(x))$ to reflect the dependence of the set estimate on the procedure $\mathcal{R}$ and on the test statistics $x$; 
for notational convenience, we suppress this dependence and simply write $\widehat{S}$.
% in place of $\widehat{S}(\mathcal{R}(x))$

For a given procedure $\mathcal{R}$, the {false discovery rate} (FDR) 
and the {false non-discovery rate} (FNR) of a procedure are defined as
% of the procedure is defined to be the expected fraction of false findings not in the true index set, among the reported discoveries \cite{benjamini1995controlling}. 
% Its counterpart, \emph{false non-discovery rate} (FNR), measuring the power of the procedure, is defined as the expected fraction of missed detection. 
% Mathematically, we define
\begin{equation} \label{eq:FDR-FNR}
    \mathrm{FDR}(\mathcal{R}) := \E\left[\frac{|\widehat{S}\setminus S|}{\max\{|\widehat{S}|,1\}}\right]
    \quad \text{and} \quad
    \mathrm{FNR}(\mathcal{R}) := \E\left[\frac{|S\setminus \widehat{S}|}{\max\{|{S}|,1\}}\right],
\end{equation}
where the maxima in the denominators resolve the possible division-by-0 problem. 
Roughly speaking, FDR measures the expected fraction of false findings, while FNR describes the proportion of Type II errors among the true signals, and reflects the average marginal power of the procedure.

A more stringent criterion for false discovery is the \ac{FWER},
%family-wise error rate (FWER),
% defined to be the probability of reporting at least one finding not contained in the true index set.
and correspondingly, a more stringent criteria for false non-discovery is the \ac{FWNR},
%family-wise non-discovery rate (FWNR), 
i.e.,
% the probability of missing at least one signal in the true index set. That is,
\begin{equation} \label{eq:FWER-FWNR}
    \mathrm{FWER}(\mathcal{R}) := 1 - \P[\widehat{S} \subseteq S]
    \quad \text{and} \quad
    \mathrm{FWNR}(\mathcal{R}) := 1 - \P[S \subseteq \widehat{S}].
\end{equation}

We introduce five different statistical risk metrics, 
each having different asymptotic limits in the support recovery problems as we will see later in this text. 
Following \cite{arias2017distribution}, we define the risk for \emph{approximate} support recovery as
\begin{equation} \label{eq:risk-approximate}
    \mathrm{risk}^{\mathrm{A}}(\mathcal{R}) := \mathrm{FDR}(\mathcal{R}) + \mathrm{FNR}(\mathcal{R}).
\end{equation}
Analogously, we define the risk for \emph{exact} support recovery as
\begin{equation} \label{eq:risk-exact}
    \mathrm{risk}^{\mathrm{E}}(\mathcal{R}) := \mathrm{FWER}(\mathcal{R}) + \mathrm{FWNR}(\mathcal{R}).
\end{equation}
Two closely related measures of success in the exact support recovery risk are the probability of exact recovery, 
\begin{equation} \label{eq:risk-prob}
    \P[\widehat{S} = S] = 1 - \P[\widehat{S} \neq S],
\end{equation}
and the Hamming loss
\begin{equation} \label{eq:Hamming-loss}
    H(\widehat S, S) := \left|\widehat{S}\triangle S\right|
    = \sum\limits_{i=1}^p\left|\mathbbm{1}_{\widehat{S}}(i)- \mathbbm{1}_{S}(i)\right|.
\end{equation}
which counts the number of mismatches between the estimated and true support sets.

The relationship between probability of support recovery $\P[\widehat{S} = S]$, exact support recovery risk $\mathrm{risk}^{\mathrm{E}}$, and the expected Hamming loss $\mathbb{E}[H(\widehat S, S)]$ will be discussed in Section \ref{sec:risks-relations} below.

\medskip

Notice that all risk metrics introduced so far penalize false discoveries and missed signals somewhat symmetrically --- the approximate support recovery risk combines proportions of errors, the exact support recovery risk combines probabilities of errors, and the Hamming loss increments the risk by one regardless of the types of errors made.
In applications, however, attitudes towards Type I and Type II errors are often different.
In the example of GWAS, where the number of candidate locations $p$ could be in the millions, researchers are typically interested in the marginal (location-wise) power of discovery, while exercising stringent (family-wise) false discovery control --- a situation not reflected in the above-mentioned risk metrics.
This asymmetric consideration, and in particular the GWAS application, prompts us to consider risks that weigh both the family-wise error rate and the marginal power of discovery.
One such risk metric is what shall be referred to as the \emph{exact-approximate} support recovery risk
\begin{equation} \label{eq:risk-exact-approx}
    \mathrm{risk}^{\mathrm{EA}}(\mathcal{R}) := \mathrm{FWER}(\mathcal{R}) + \mathrm{FNR}(\mathcal{R}).
\end{equation}
The somewhat cumbersome name and notation are chosen to reflect
the asymmetry in dealing with the two types of errors in support recovery.
Namely, when the risk metric \eqref{eq:risk-exact-approx} vanishes, we have ``exact false discovery control, and approximate false non-discovery control'' asymptotically.

Analogously, we consider the \emph{approximate-exact} support recovery risk
\begin{equation} \label{eq:risk-approx-exact}
    \mathrm{risk}^{\mathrm{AE}}(\mathcal{R}) := \mathrm{FDR}(\mathcal{R}) + \mathrm{FWNR}(\mathcal{R}),
\end{equation}
which places more emphasis on non-discovery control over false discovery.

% These two risks differ in their stringency in controlling false discovery and false non-discovery.
Theoretical limits and performance of procedures in support recovery problems will be studied in terms of the five risk metrics \eqref{eq:risk-approximate}, \eqref{eq:risk-exact}, \eqref{eq:risk-prob}, \eqref{eq:risk-exact-approx} and \eqref{eq:risk-approx-exact}, in Chapters \ref{chap:phase-transitions}, \ref{chap:exact-support-recovery}, and \ref{chap:GWAS}.
We are particularly interested in fundamental limits of signal detection and support recovery problems in terms of these metrics, as well as the optimality of commonly used procedures in high dimensional settings.

% This asymmetry motivates us to study, and discover, two new phase transitions, both in the additive error model \eqref{eq:model-additive} under one-sided alternatives, and in the chi-square model \eqref{eq:model-chisq}.
% The latter, as discussed in Section \ref{subsec:motivation-additive}, entails the additive error model \eqref{eq:model-additive} under two-sided alternatives.
% Further details can be found in Section \ref{subsec:risks} below, after 
% We summarize the main messages of this paper next.

% The third consideration that motivates us is the choice of practically relevant statistical risks.

### 2020-08-17 2.background/background.tex
add draft converted from thesis

We establish the background necessary for the study of sparse signal detection and support recovery problems in this chapter.
Sections \ref{sec:risks} and \ref{sec:statistical-procedures} provide a refresher on the definitions of statistical risks and some commonly used statistical procedures.
Section \ref{sec:asymptotics} describes the asymptotic regime under which we analyze these procedures, and reviews the related literature in high-dimensional statistics.
We discuss in Section \ref{sec:risks-relations} the connections among the risk metrics, and point out some common fallacies.
The remaining sections collect the technical preparations for this text.
Section \ref{suppsec:AGG} defines an important class of error distributions which will be analyzed in detail in later chapters. 
And finally, Section \ref{subsec:RS} introduces the concepts of concentration of maxima, which plays a crucial role in the analysis of high-dimensional support recovery problems.

% prepare the definitions and technical results used in our analyses.

\section{Statistical risks}
\label{sec:risks}
\input{2.background/2.statistical_risks.tex}

\section{Statistical procedures}
\label{sec:statistical-procedures}
\input{2.background/2.statistical_procedures.tex}

\section{Related literature and our contributions}
\label{sec:asymptotics}
\input{2.background/2.asymptotics.tex}

\section{Relationships between the asymptotic risks}
\label{sec:risks-relations}
\input{2.background/2.risks_relations.tex}

\section{The asymptotic generalized Gaussian (AGG) models}
\label{suppsec:AGG}
\input{2.background/2.AGG.tex}

\section{Rapid variation and relative stability}
\label{subsec:RS}
\input{2.background/2.RV_and_RS.tex}

### 2020-08-17 3.phase_transitions/3.BH_monotonicity.tex
add draft converted from thesis

We make a connection between power of the \ac{BH} procedure and the stochastic ordering of distributions under the alternative.
This result, though natural, seems new.

\begin{lemma}[Monotonicity of the BH procedure] \label{lemma:monotonicity-BH-procedure}
Consider $p$ independent observations $x(i)$, $i\in\{1,\ldots,p\}$, where the $(p-s)$ coordinates in the null part have common distribution $F_0$, and the remaining $s$ signals have alternative distributions $F^{i}_j$, $i\in S$, respectively.
Compare the two alternatives $j\in\{1,2\}$, where the distributions in Alternative 2 are stochastically larger than those in Alternative 1, i.e.,
\begin{equation*}
    F^{i}_2(t) \le F^{i}_1(t), \quad \text{for all} \;\; t\in\R, \; \text{and for all} \;\; i\in S.
\end{equation*}
If the BH procedure is applied at the same nominal level of FDR, then the FNR of the \ac{BH} procedure under Alternative 2 is bounded above by the FNR under Alternative 1.
Further, the threshold of the \ac{BH} procedure under Alternative 2 is stochastically smaller than that under Alternative 1.
\end{lemma}

Loosely put, the power of the BH procedure is monotone increasing with respect to the stochastic ordering of the alternatives, yet (the distribution of) the \ac{BH} threshold is monotone decreasing in the distributions of the alternatives.

\begin{proof}[Proof of Lemma \ref{lemma:monotonicity-BH-procedure}]
We first re-express the BH procedure in a different form.
Recall that on observing $x(i)$, $i\in\{1,\ldots,p\}$, the BH procedure is the thresholding procedure with threshold set at $x_{[i^*]}$, where $i^* := \max\{i\,|\,\overline{F_0}(x_{[i]})\le \alpha i/p\}$, and $x_{[1]}\ge\ldots\ge x_{[p]}$ are the order statistics.

Let $\widehat{G}$ denote the left-continuous empirical survival function
\begin{equation} \label{eq:empirical-tail-distribution}
    \widehat{G}(t) = \frac{1}{p}\sum_{i=1}^p\mathbbm{1}\{x(i) \ge t\}.
\end{equation}
By the definition, we know that $\widehat{G}(x_{[i]}) = i/p$.
Therefore, by the definition of $i^*$, we have
\begin{equation*} 
    \overline{F_0}(x_{[i]}) > \alpha\widehat{G}(x_{[i]}) = \alpha i/p \quad \text{for all }i>i^*.
\end{equation*}
Since $\widehat{G}$ is constant on $(x_{[i^*+1]}, x_{[i^*]}]$, the fact that 
$\overline{F_0}(x_{[i^*]}) \le \alpha\widehat{G}(x_{[i^*]})$ and $\overline{F_0}(x_{[i^*+1]}) > \alpha\widehat{G}(x_{[i^*+1]})$ implies that $\alpha\widehat{G}$ and $\overline{F_0}$ must ``intersect'' on the interval by continuity of $F_0$.
We denote this ``intersection'' as
\begin{equation} \label{eq:approx-boundary-proof-tau}
    \tau = \inf\{t\,|\,\overline{F_0}(t)\le\alpha\widehat{G}(t)\}. 
    %= \min\{t\,|\,\overline{F_0}(t)=\alpha\widehat{G}(t)\}.
\end{equation}
Note that $\tau$ cannot be equal to $x_{[i^*+1]}$ since $\overline{F}_0$ is c\`adl\`ag.
Since there is no observation in $[\tau, x_{[i^*]})$, we can write the BH procedure as the thresholding procedure with threshold set at $\tau$.

Now, denote the observations under Alternatives 1 and 2 as $x_1(i)$ and $x_2(i)$.
Since $x_2(i)$ stochastically dominates $x_1(i)$ for all $i\in\{1,\ldots,p\}$, there exists a coupling $(\widetilde{x}_1, \widetilde{x}_2)$ of $x_1$ and $x_2$ such that 
% $\widetilde{x}_1(i) = \widetilde{x}_2(i)$ for $i\in S^c$, and 
$\widetilde{x}_1(i) \le \widetilde{x}_2(i)$ almost surely for all $i$.
We will replace $\widetilde{x}_1$ and $\widetilde{x}_2$ with $x_1$ and $x_2$ in what follows.
Since we will compare the FNR's, i.e., expectations with respect to the marginals of ${x}$'s in the last step, this replacement does not affect the conclusions.
To simplify notation, we still write $x_1$ and $x_2$ in place of $\widetilde{x}_1$ and $\widetilde{x}_2$.

Let $\widehat{G}_k$ be the left-continuous empirical survival function under Alternative $k$, i.e.,
\begin{equation} \label{eq:empirical-survival}
    \widehat{G}_k(t) = \frac{1}{p}\sum_{i=1}^p\mathbbm{1}\{x_k(i) \ge t\}, \quad k\in\{1,2\}.
\end{equation}
We define the BH thresholds $\tau_1$ and $\tau_2$ by replacing $\widehat{G}$ in \eqref{eq:approx-boundary-proof-tau} with $\widehat{G}_1$ and $\widehat{G}_2$, respectively.
Denote the set estimates of signal support $\widehat{S}_k = \{i\,|\,x_k(i)\ge\tau_k\}$ by the BH procedure.
We claim that 
\begin{equation} \label{eq:monotonicity-BH-procedure-thresholds}
    \tau_2 \le \tau_1 \quad \text{with probability } 1.
\end{equation}

Indeed, by definition of the empirical survival function \eqref{eq:empirical-survival} and the fact that $x_1(i) \le x_2(i)$ almost surely for all $i$,  we have $\widehat{G}_1(t) \le \widehat{G}_2(t)$ for all $t$.
Hence, $\overline{F_0}(t)\le\alpha\widehat{G}_1(t)$ implies $\overline{F_0}(t)\le\alpha\widehat{G}_2(t)$, and Relation \eqref{eq:monotonicity-BH-procedure-thresholds} follows from the definition of $\tau$ in \eqref{eq:approx-boundary-proof-tau}.
The claim of stochastic ordering of the \ac{BH} thresholds in Lemma \ref{lemma:monotonicity-BH-procedure} follows from \eqref{eq:monotonicity-BH-procedure-thresholds}.

Finally, when $\tau_2 \le \tau_1$, we have $\tau_2 \le \tau_1 \le x_1(i) \le x_2(i)$ with probability 1 for all $i\in\widehat{S}_1$.
Therefore, it follows that $\widehat{S}_1 \subseteq \widehat{S}_2$ and hence $|S\setminus\widehat{S}_2| \le |S\setminus\widehat{S}_1|$ almost surely. 
The first conclusion in Lemma \ref{lemma:monotonicity-BH-procedure} follows from the last inequality.
\end{proof}

### 2020-08-17 3.phase_transitions/3.Gaussian-distributions.tex
add draft converted from thesis

We recall three facts of Gaussian distributions that will be used in the proofs later.

We first state the relative stability of iid standard Gaussian random variables,
Since the standard Gaussian distribution falls in the class of asymptotically generalized Gaussians (AGG; see Definition \ref{def:AGG}), by Example \ref{exmp:AGG}, we know that the triangular array ${\cal E} = \{\left(\epsilon_p(i)\right)_{i=1}^p, p\in\N\}$ has relatively stable (RS) maxima in the sense of \eqref{eq:RS-condition}, i.e.,
\begin{equation} \label{eq:relative-stability-Gaussian-maxima}
    \frac{1}{u_{p}} \max_{i=1,\ldots,p} \epsilon_p(i) \xrightarrow{\P} 1,\quad \text{as }\;p\to\infty,
\end{equation}
where $u_p$ is the $(1/p)$-th upper quantile as defined in \eqref{eq:AGG-quantiles}.
Similarly, since the array ${\cal E}$ has distributions symmetric around 0, it also has relatively stable minima
\begin{equation} \label{eq:relative-stability-Gaussian-minima}
    \frac{1}{u_{p}} \min_{i=1,\ldots,p} \epsilon_p(i) \xrightarrow{\P} -1,\quad \text{as }\;p\to\infty.
\end{equation}

The second fact is on the well-known bounds for the Mill's ratio of Gaussian tails.
Let $\Phi$ denote the CDF of the standard Gaussian distribution and $\phi$ its density.
One can show that for all $x>0$ we have
\begin{equation} \label{eq:Mills-ratio}
    \frac{x}{1+x^2}\phi(x) \le \overline{\Phi}(x) = 1-\Phi(x) \le \frac{1}{x}\phi(x),
\end{equation}
using e.g., integration by parts.

The third fact is the stochastic monotonicity of the Gaussian location family. 
In fact, for all location families $\{F_\delta(x)\}_\delta$ where $F_\delta(x) = F(x-\delta)$, we have,
\begin{equation} \label{eq:stochastic-monotonicity-Gaussian}
    F_{\delta_1}(t) \ge F_{\delta_2}(t), \quad \text{for all}\quad t\in\mathbb{R}\quad\text{and all}\quad \delta_1 \le \delta_2.
\end{equation}
Relation \eqref{eq:stochastic-monotonicity-Gaussian} holds, of course, when $F$ is the standard Gaussian distribution.

### 2020-08-17 3.phase_transitions/3.Gaussian-support-recovery.tex
add draft converted from thesis

Turning to support recovery problems in the Gaussian error model \eqref{eq:model-additive-Chapter3},
we will analyze the asymptotic performance limits in terms of the risk metrics for exact, exact-approximate, approximate-exact support recovery problems (i.e., \eqref{eq:risk-exact}, \eqref{eq:risk-exact-approx}, and \eqref{eq:risk-approx-exact}, respectively), as well as the probability of support recovery \eqref{eq:risk-prob}. 
We will also review the recent result for exact support recovery risk \eqref{eq:risk-approximate} by \cite{arias2017distribution}, to reveal a rather complete landscape of support recovery problems in high-dimensional Gaussian error models.

We restrict our attention to the class of thresholding procedures in this section.
Specifically, the lower bounds that we develop in Theorems \ref{thm:Gaussian-error-exact-boundary} through \ref{thm:Gaussian-error-approx-exact-boundary} below are only meant to apply to thresholding procedures. 
Although it is intuitively appealing to consider only data-thresholding procedures in multiple testing problems, such procedures are not always optimal in more general settings. 
% Recently, \cite{arias2019detection} showed that thresholding procedures are in fact sub-optimal in the additive models \eqref{eq:model-additive} when errors have heavy (regularly-varying) tails. 
% Gao and Stoev [14] characterized the conditions under which thresholding procedures are optimal in the exact support recovery problem. 
% The optimality of data-thresholding procedures in terms of other statistical risks is an open problem that invites a dedicated investigation in a future study.
The optimality of thresholding procedures and the consequences of this restriction will be treated in Chapter \ref{chap:exact-support-recovery}.

\medskip

A technical ingredient is needed in order to state our main results.
We define a rate at which the nominal levels of FWER or FDR go to zero.
\begin{definition} \label{def:slowly-vanishing}
We say the nominal level of errors $\alpha = \alpha_p$ vanishes slowly, if
\begin{equation} \label{eq:slowly-vanishing-error}
    \alpha\to 0,\quad \text{and} \quad \alpha p^\delta\to\infty \text{  for any } \delta>0.
\end{equation}
\end{definition}
As an example, the sequence of nominal levels $\alpha_p = 1/\log{(p)}$ is slowly vanishing, while the sequence $\alpha_p = 1/\sqrt{p}$ is not.

\subsection{The exact support recovery problem}
\label{subsec:exact-support-recovery-Gaussian}

Our study of the exact support recovery risk \eqref{eq:risk-exact} begins with a brief review of existing results for the Hamming loss \eqref{eq:Hamming-loss}.
Indeed, as discussions in Section \ref{sec:asymptotics} suggest, the latter can be informative of the exact support recovery problems for models with independent components.

Inspired by the phase transition results for the signal detection problem, \cite{ji2012ups}, \citet{genovese2012comparison}, and \cite{jin2014optimality} derived interesting sharp results on support recovery problems in linear models under the Hamming loss $H(\widehat S, S)$.
Specifically, these papers establish minimax-type phase transition results in their respective settings. 
Under the sparsity parametrization in \eqref{eq:signal-sparsity-additive} and assuming equal signal sizes of ${(2r\log{p})^{1/2}}$, Hamming losses were shown to diverge to $+\infty$ when $r$ falls below the threshold
\begin{equation} \label{eq:strong-classification-boundary-Gaussian}
    g(\beta) = (1 + (1 - \beta)^{1/2})^2,
\end{equation}
for any method of support estimation.
Conversely, under orthogonal, or near-orthogonal random designs, if $r>g(\beta)$, they showed that the methods they proposed achieve vanishing Hamming loss.

Very recently, \citet{butucea2018variable}\; studied both asymptotics and non-asymptotics of support recovery problems in the additive noise model \eqref{eq:model-additive-Chapter3} under the assumption of equal signal sizes, using the Hamming loss.
Again, the analysis of asymptotic optimality focused on a newly proposed procedure which is very specific to the Gaussian model.
It is not at all clear if the optimality properties are a consequence of its mysterious construction.

We now show that commonly used and computationally efficient procedures can also be asymptotically optimal in the exact support recovery problem.

\begin{theorem} \label{thm:Gaussian-error-exact-boundary}
Consider the high-dimensional additive error model \eqref{eq:model-additive-Chapter3} under independent standard Gaussian errors, with signal sparsity and size as described in \eqref{eq:signal-sparsity-additive} and \eqref{eq:signal-size-additive}.
The function \eqref{eq:strong-classification-boundary-Gaussian} characterizes the phase transition of the exact support recovery problem.
Specifically, if $\underline{r} > {{g}}(\beta)$, then Bonferroni's, Sid\'ak's, Holm's, and Hochberg's procedures with slowly vanishing  nominal FWER levels (as defined in Definition \ref{def:slowly-vanishing}) all achieve asymptotically exact support recovery in the sense of \eqref{eq:support-recovery-success}.

Conversely, if $\overline{r} < {{g}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, we have $\P[\widehat{S}_p=S_p]\to0$.
Therefore, in view of Lemma \ref{lemma:risk-exact-recovery-probability}, exact support recovery asymptotically fails for all thresholding procedures in the sense of \eqref{eq:support-recovery-failure}.
\end{theorem}

We visualize the result in a $\beta$-$r$ phase diagram in Figure \ref{fig:phase-Gaussian-errors}.

Theorem \ref{thm:Gaussian-error-exact-boundary} is in fact a special case of the more general Theorem \ref{thm:sufficient} which covers dependent and non-Gaussian errors.
We will study the exact support recovery problem in greater detail, and prove the more general version of the Theorem in Chapter \ref{chap:exact-support-recovery}.

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{./figures/phase_diagram_Gaussian_ALL_boundaries.eps}
  \end{center}
   \caption{The phase diagram of support recovery problems for the high-dimensional chi-square model \eqref{eq:model-additive-Chapter3}, illustrating the boundaries of the exact support recovery (FWER + FWNR; top curve; Theorem \ref{thm:Gaussian-error-exact-boundary}), the approximate-exact support recovery (FDR + FWNR; second curve from top; Theorem \ref{thm:Gaussian-error-approx-exact-boundary}), the exact-approximate support recovery (FWER + FNR; horizontal line $r=1$; Theorem \ref{thm:Gaussian-error-exact-approx-boundary}), and the approximate support recovery problems (FDR + FNR; tilted line $r=\beta$; Theorem \ref{thm:Gaussian-error-approx-boundary}). The signal detection problem (Type I + Type II errors of the global test; lower curve) was studied in Donoho and Jin (2004). In each region of the diagram and above, the annotated statistical risk can be made to vanish, as dimension $p$ diverges. Conversely, the risks has liminf at least one.}
   \label{fig:phase-Gaussian-errors}
\end{figure}

\subsection{The approximate support recovery problem}
\label{subsec:approx-support-recovery-Gaussian}

\cite{arias2017distribution} studied the performance of the Benjamini-Hochberg procedure \citep{benjamini1995controlling} and a stripped-down version of the Cand\'es-Barber procedure \citep{barber2015controlling} in approximate support recovery problems when the components of the noise term $\epsilon$ in \eqref{eq:model-additive-Chapter3} have independent and symmetric distributions.
A phase transition phenomenon for the approximate support recovery risk \eqref{eq:risk-approximate} was established in the Gaussian additive error model, where the two aforementioned methods are both shown to be asymptotically optimal.

The analysis therein, however, assumed equal signal sizes for the alternatives.
We generalize the main results of \citet{arias2017distribution} to allow for unequal signal sizes.

\begin{theorem} \label{thm:Gaussian-error-approx-boundary}
In the context of Theorem \ref{thm:Gaussian-error-exact-boundary}, the function 
\begin{equation} \label{eq:approx-boundary-Gaussian}
    h(\beta) = \beta
\end{equation}
characterizes the phase transition of approximate support recovery problem.
Specifically, if $\underline{r} > {h}(\beta)$, then the Benjamini-Hochberg procedure (defined in Section \ref{sec:statistical-procedures}) with slowly vanishing nominal FDR levels (as defined in Definition \ref{def:slowly-vanishing}) achieves asymptotically approximate support recovery in the sense of \eqref{eq:support-recovery-success}.

Conversely, if $\overline{r} < {h}(\beta)$, then approximate support recovery asymptotically fails in the sense of \eqref{eq:support-recovery-failure} for all thresholding procedures.
\end{theorem}

Proof of Theorem \ref{thm:Gaussian-error-approx-boundary} is presented in Section \ref{sec:proofs}. 
The key to proving this generalization is a monotonicity property of the \ac{BH} procedure. 
Namely, the power of the \ac{BH} procedure in terms of FNR monotonically increases for stochastically larger alternatives.
This fact will be formalized in Lemma \ref{lemma:monotonicity-BH-procedure}, and may be of independent interest.

\subsection{The exact-approximate support recovery problem}
\label{subsec:exact-approx-support-recovery-Gaussian}

We now derive two new asymptotic phase transition results for the \emph{asymmetric} statistical risks, \eqref{eq:risk-exact-approx} and \eqref{eq:risk-approx-exact}, in the Gaussian error models.
The next theorem describes the phase transition in the exact-approximate support recovery problem.

\begin{theorem} \label{thm:Gaussian-error-exact-approx-boundary}
In the context of Theorem \ref{thm:Gaussian-error-exact-boundary}, the function 
\begin{equation} \label{eq:exact-approx-boundary-Gaussian}
    \widetilde{g}(\beta) = 1
\end{equation}
characterizes the phase transition of exact-approximate support recovery problem.
Specifically, if $\underline{r} > \widetilde{g}(\beta)$, then the procedures listed in Theorem \ref{thm:Gaussian-error-exact-boundary} with slowly vanishing nominal FWER levels (as defined in Definition \ref{def:slowly-vanishing}) achieve asymptotically exact-approximate support recovery in the sense of \eqref{eq:support-recovery-success}.

Conversely, if $\overline{r} < \widetilde{g}(\beta)$, then for any thresholding procedure $\widehat{S}$, the exact-approximate support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
\end{theorem}

Theorem \ref{thm:Gaussian-error-exact-approx-boundary} is proved in Section \ref{sec:proofs}. 
The phase transition boundary \eqref{eq:exact-approx-boundary-Gaussian} is visualized in Figure \ref{fig:phase-Gaussian-errors}.

\begin{remark}
Boundary \eqref{eq:exact-approx-boundary-Gaussian} was briefly suggested by \citet{arias2017distribution}.
Unfortunately, it was falsely claimed that the boundary characterized the phase transition of the \emph{exact} support recovery problem, and the alleged proof was left as an ``exercise to the reader''.
This exercise was completed in Chapter \ref{chap:exact-support-recovery}, where the correct boundary \eqref{eq:exact-boundary-chisquared} was identified.

Theorem \ref{thm:Gaussian-error-exact-approx-boundary} here shows that the boundary \eqref{eq:exact-approx-boundary-Gaussian} \emph{does} exist, though for the slightly different \emph{exact-approximate} support recovery problem.
As we will see in Section \ref{sec:chisq-boundaries}, the boundary \eqref{eq:exact-approx-boundary-Gaussian} also applies to the exact-approximate support recovery problem in chi-square models \eqref{eq:model-chisq}.
\end{remark}

\subsection{The approximate-exact support recovery problem}
\label{subsec:aprox-exact-support-recovery-Gaussian}

The last phase transition is in terms of the approximate-exact support recovery risk
\eqref{eq:risk-approx-exact}.

\begin{theorem} \label{thm:Gaussian-error-approx-exact-boundary}
In the context of Theorem \ref{thm:Gaussian-error-exact-boundary}, the function 
\begin{equation} \label{eq:approx-exact-boundary-Gaussian}
    \widetilde{h}(\beta) = \left(\sqrt{\beta} + \sqrt{1-\beta}\right)^2
\end{equation}
characterizes the phase transition of approximate-exact support recovery problem.
Specifically, if $\underline{r} > \widetilde{h}(\beta)$, then the Benjamini-Hochberg procedure with slowly vanishing nominal FDR levels (as defined in Definition \ref{def:slowly-vanishing}) achieves asymptotically approximate-exact support recovery in the sense of \eqref{eq:support-recovery-success}.

Conversely, if $\overline{r} < \widetilde{h}(\beta)$, then for any thresholding procedure $\widehat{S}$, the approximate-exact support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
\end{theorem}

Theorem \ref{thm:Gaussian-error-approx-exact-boundary} is proved in Section \ref{sec:proofs}.
The phase transition boundary \eqref{eq:approx-exact-boundary-Gaussian} is visualized in Figure \ref{fig:phase-Gaussian-errors}.

\subsection{Asymptotic power analysis}
\label{subsec:power-analysis}

Theorems \ref{thm:Gaussian-error-exact-boundary} through \ref{thm:Gaussian-error-approx-exact-boundary} allow us to asymptotically quantify the required signals sizes in support recovery problems, as well as in the global hypothesis testing problem in the Gaussian additive error model \eqref{eq:model-additive-Chapter3}. 
Specifically, these results indicate that at all sparsity levels $\beta\in(0,1)$, the difficulties of the problems in terms of the required signal sizes have the following ordering
$$
f(\beta) < h(\beta) < \widetilde{g}(\beta) < \widetilde{h}(\beta) < g(\beta),
$$
as previewed in Figure \ref{fig:phase-Gaussian-errors}.
The ordering aligns with our intuition that the required signal sizes must increase as we move from detection to support recovery problems.
Similarly, more stringent criteria for error control (e.g., FWER compared to FDR) require larger signals.
We can now also compare $\widetilde{g}(\beta)$ and $\widetilde{h}(\beta)$, whose ordering may not be clear from this line of reasoning.

\medskip

Our last comment is on the gap between FDR and FWER under sparsity assumptions. 
Although it is believed that FWER control is sometimes too stringent compared to, say, FDR control in support recovery problems, the fact that all three thresholds (detection, weak, and strong classification) involve the same scaling indicates that the difficulties of the three problems (signal detection, approximate, and exact support recovery) are comparable when signals are very sparse, i.e., when $\beta$ is close to 1.
This is illustrated with the next example.

\begin{example}[Power analysis for variable selection] \label{exmp:gap-when-signal-sparse}
For Gaussian errors (AGG with $\nu = 2$), when $\beta = 3/4$, the signal detection boundary \eqref{eq:detection-boundary-large-signals} says that signals will have to be at least of magnitude $\sqrt{(\log{p})/2}$, 
while approximate support recovery \eqref{eq:approx-boundary-Gaussian} requires signal sizes of at least $\sqrt{3(\log{p})/2}$, 
and exact support recovery \eqref{eq:strong-classification-boundary-Gaussian} calls for signal sizes of at least $\sqrt{9(\log{p})/2}$. 
The required signal sizes increases, but are within the same order of magnitude.

If $m$ independent copies $x_1,\ldots,x_m$ of the observations were made on the same set of $p$ locations, then by taking location-wise averages, $\overline{x}_{m}(j) = \frac{1}{m}\sum_{i=1}^{m} x_i(j)$,
we can reduce error standard deviation, and hence boost the signal-to-noise ratio, by a factor of $\sqrt{m}$.
By the simple calculations above, if $m$ samples are needed to detect (sparse) signals of a certain magnitude, then $3m$ samples will enable approximate support recovery with FDR control, and in fact, $9m$ samples would enable exact support recovery with FWER control.
\end{example}

On the other hand, the gap between FDR and FWER is much larger when signals are dense.
For example, if the signals are only \emph{approximately} sparse, i.e., having a few components above \eqref{eq:strong-classification-boundary-Gaussian} but many smaller components above  \eqref{eq:approx-boundary-Gaussian}, then FDR-controlling procedures will discover substantially larger proportion of signals than FWER-controlling procedures.

Indeed, as $\beta\to0$, the required signal size for approximate support recovery \eqref{eq:approx-boundary-Gaussian} tends to 0, while the required signal size for exact support recovery \eqref{eq:strong-classification-boundary-Gaussian} tends to $4$ in the Gaussian error models.
While Example \ref{exmp:gap-when-signal-sparse} indicates that the exact support recovery is not much more stringent than approximate support recovery when signals are sparse, the gap between required signal sizes widens when signals are dense.

### 2020-08-17 3.phase_transitions/3.global-tests.tex
add draft converted from thesis

The optimality of sparse signal detection was first studied by \citet{ingster1998minimax}, who showed that a phase transition in the $r$-$\beta$ plane exists for the signal detection problem. 
Specifically, assuming equal signal sizes with magnitude $\sqrt{2{r}\log{p}}$, if the signal size $r$ is above a so-called detection boundary,
\begin{equation} \label{eq:detection-boundary-large-signals}
    f(\beta) = 
    \begin{cases}
        \max\{0,\; \beta - 1/2\} & 0 < \beta \le 3/4, \\
        \left(1 - \sqrt{1-\beta}\right)^2 & 3/4 < \beta \le 1,
    \end{cases}
\end{equation} 
then the global null hypothesis $\mu(i)=0$ for all $i=1,\ldots,p$ can be distinguished from the alternative as $p\to\infty$ in the sense of \eqref{eq:support-recovery-success} using the likelihood ratio test; 
otherwise, when signal sizes fall below the boundary, no test can do better than a random guess.
Adaptive tests such as Tukey's \ac{HC} \citep{donoho2004higher} and a modified goodness-of-fit test statistic of \citet{zhang2002powerful} have been identified to attain this performance limit without knowledge of the sparsity and signal sizes. 
% We visualize this boundary $f$ in the upper panel of Figure \ref{fig:phase-diagram-signal-detection}.
It is also known that the max-statistic \eqref{eq:max-statistic} is only efficient when $r>(1+\sqrt{1-\beta})^2$, and is therefore sub-optimal for denser signals where $1/2\le\beta\le 3/4$; see \cite{cai2011optimal}.
In contrast, the sum-of-square-type statistics such as $L_2$ was shown in \cite{fan1996test} to be asymptotically powerless when the $L_2$-norm of the signal $\|\mu\|_2^2$ is $o(\sqrt{p})$, or equivalently, when $\beta>1/2$ in our parametrization.

Notice that the scaling for the signal magnitude $\Delta = \sqrt{2r\log{p}}$ is useful for studying very sparse signals ($\beta>1/2$), but fails to reveal the difficulties of the detection problems when signals are relatively dense ($\beta<1/2$).
Indeed, a different scaling is needed for small but dense signals.
With slight overloading of notation, we parametrize signal sizes as 
\begin{equation} \label{eq:signal-size-small} 
    \underline{\Delta} = p^{\underline{r}}
    \le \mu(i) \le
    \overline{\Delta} = p^{\overline{r}}, \quad \text{for all}\;\;i\in S_p,
\end{equation}
where $\underline{r}$ and $\overline{r}$ are negative constants.
In this scaling for the faint signals, \citet{cai2011optimal} showed that a similar phase transition characterized by the following boundary,
\begin{equation} \label{eq:detection-boundary-small-signals}
    f_s(\beta) = \beta - 1/2, \quad 0 < \beta \le 1/2,
\end{equation} 
exists.
Specifically, if $\overline{r}<f_s(\beta)$, the signal detection fails in the sense of \eqref{eq:support-recovery-failure} regardless of the procedures, while the \ac{HC} statistic continues to attain asymptotically perfect detection when $\underline{r}>f_s(\beta)$. 
We visualize this boundary in the lower panel of Figure \ref{fig:phase-diagram-signal-detection}.

\begin{figure}
      \centering
      \includegraphics[width=0.7\textwidth]{figures/phase_diagram_signal_detection.eps}
      \includegraphics[width=0.7\textwidth]{figures/phase_diagram_signal_detection_vanishing_signals.eps}
      \caption{The phase diagrams of the sparse signal detection problem. 
      Signal size and sparsity are parametrized by $r$ and $\beta$, respectively.
      % Signal sparsity $|S|$ is parametrized by $\beta$. 
      % Signal sizes $\Delta$, parametrized by $r$, increases with dimension $p$ inside the upper panel, and decreases with $p$ inside the power panel.
      The diagrams illustrate the regions where the signal detection problem can be solved asymptotically by some of the commonly used statistics: the maximum ($M$), the sum-of-squares ($L_2$), the sum-of-absolute values ($L_1$), and the sum ($S$).
      In each region of the diagram, the annotated statistics can make the detection risk \eqref{eq:risk-detection} vanish, as dimension $p$ diverges. Conversely, the risks has liminf at least one.
      The detection problem is unsolvable for very sparse and weak signals in the undetectable regions.
      Notice that the $L_1$ and $L_2$ statistics are in fact sub-optimal for all sparsity levels.
      On the other hand, the max-statistic remains powerful for sparse signals ($\beta>1/2$), and is fully efficient when the problem is very sparse ($\beta\ge3/4$).
      The \ac{HC} statistic can detect signals in all configurations in the detectable regions.
      See text and Theorem \ref{thm:detection-optimality}.}
      \label{fig:phase-diagram-signal-detection}
\end{figure}

To the best of our knowledge, performance of simple statistics such as $L_1$, $L_2$ norms, and $S$ in this weak signal setting have not been reported in the literature perhaps due to a perceived lack of novelty.
Our first Theorem investigates the performance of these routine statistics for detecting sparse signals in high-dimensions, and summarizes the known results.

\begin{theorem} \label{thm:detection-optimality}
Consider the signal detection problem in the triangular array of Gaussian error models \eqref{eq:model-additive-Chapter3} where the sparsity is parametrized as in \eqref{eq:signal-sparsity-additive}.
\begin{itemize}
    \item For signals whose sizes are parametrized as in \eqref{eq:signal-size-additive}, the detection problem can be asymptotically solved in the sense of \eqref{eq:support-recovery-success} with $L_2$, $L_1$, or $S$ statistic when $\beta\le 1/2$; on the other hand, these statistics are asymptotically powerless in the sense of \eqref{eq:support-recovery-failure} when $\beta>1/2$.
    \item For small and dense signals whose signal sizes are parametrized as in \eqref{eq:signal-size-small}, the detection problem can be asymptotically solved in the sense of \eqref{eq:support-recovery-success} with $L_2$ or $L_1$ statistic when $\underline{r}>\beta/2-{1}/{4}$; on the other hand, these statistics are asymptotically powerless in the sense of \eqref{eq:support-recovery-failure} when $\overline{r}<\beta/2-{1}/{4}$.
    Further, tests based on the $S$ statistic can succeed asymptotically in the sense of \eqref{eq:support-recovery-success} when $\underline{r}>\beta-1/2$, hence attaining the boundary of detectability in \eqref{eq:detection-boundary-small-signals}.
\end{itemize}
\end{theorem}

Theorem \ref{thm:detection-optimality} is proved in Section \ref{sec:proofs} below.
We visualize the results in Theorem in Figure \ref{fig:phase-diagram-signal-detection}.
It is worth noting that the $\beta$-$r$ parameter regions where $L_1$ and $L_2$ statistics are asymptotically powerful coincide, and these statistics are theoretically suboptimal for both sparse regimes ($\beta>1/2$) and relatively dense regimes ($\beta\le 1/2$).

Ideas have been proposed to combine statistics that are powerful for different alternatives to create adaptive tests that maintain high power for at all sparsity levels.
Such adaptive tests can be constructed, for example, by leveraging the asymptotic independence of the sum- and supremum-type statistics \citep{hsing1995note}. 
Recently, \citet{xu2016adaptive} showed that for dependent observations under mixing and moment conditions, the sum-of-power-type statistics
\begin{equation}
    \widetilde{L}_q(x) = \sum_{i=1}^p x^q(i)
\end{equation} 
with distinct positive integer powers (i.e., $q=1,2,\ldots$) are asymptotically jointly independent, and proposed an adaptive test that monitors the minimium p-value of tests constructed with $\tilde{L}_q$'s.
This idea is further developed in \cite{wu2019adaptive} for generalized linear models and in \cite{he2018asymptotically} with U-statistics.

Optimality properties of such adaptive tests and the optimal choice of the $q$-combinations, however, remain open problems.
\cite{xu2016adaptive} suggested combine $q=1, 2, 3, \ldots, 6$, and  $q=\infty$, based empirical evidence from numerical experiments. 
Theorem \ref{thm:detection-optimality} here implies that, at least for detecting one-sided alternatives, the $\widetilde{L}_2$ statistic (i.e., $L_2$ norm) and the $L_1$ norm are asymptotically dominated by the $\widetilde{L}_1$ statistic (or equivalently, the sum $S$). Therefore it is sufficient to include only the latter in the construction of the adaptive test.

### 2020-08-17 3.phase_transitions/3.proofs-phase-transitions.tex
add draft converted from thesis

We first recall some basic properties of the Gaussian distribution in Section \ref{sec:Gaussian-distributions}.
Section \ref{suppsec:BH-monotonicity} states and proves an interesting property of the \ac{BH} procedure which may be of independent interest.
Results on the signal detection problem (Theorem \ref{thm:detection-optimality}) are proved in Section \ref{subsec:proof-additive-error-detection-boundaries}, and the phase transition results on the support recovery problems (Theorems \ref{thm:Gaussian-error-exact-boundary} through \ref{thm:Gaussian-error-approx-exact-boundary}) are shown in Sections \ref{subsec:proof-additive-error-approx-boundaries} and \ref{subsec:proof-additive-error-mix-boundaries}.

\subsection{Auxiliary facts of Gaussian distributions}
\label{sec:Gaussian-distributions}
\input{3.phase_transitions/3.Gaussian-distributions.tex}

\subsection{Monotonicity of the Benjamini-Hochberg procedure}
\label{suppsec:BH-monotonicity}
\input{3.phase_transitions/3.BH_monotonicity.tex}

\subsection{Proof of Theorem \ref{thm:detection-optimality}}
\label{subsec:proof-additive-error-detection-boundaries}

\begin{proof}[Proof of Theorem \ref{thm:detection-optimality}]
Statements about $L_1$, $L_2$, and sum statistics $S$ in the case of diverging signal sizes \eqref{eq:signal-size-additive} can be found in \cite{fan1996test} and \cite{candes2018lecture}.
We prove here the statements for the case where signals are dense and small, as parametrized in \eqref{eq:signal-size-small}.

We first show that the sum statistic $S$, or equivalently, the simple arithmetic mean attains the sparse signal detection boundary.

Consider the case of vanishing signals as prescribed in \eqref{eq:signal-size-small}, by normality of the summands, we have, 
\begin{equation}
    \frac{1}{\sqrt{p}}\sum_{i=1}^p x(i) \sim 
    \begin{cases}
    \mathrm{N}(0, 1), & \text{under } H_0\\
    \mathrm{N}(p^{(r-\beta)+1/2}, 1), & \text{under }  H_1.
    \end{cases}
\end{equation}
It immediately follows that the two distributions can be distinguished perfectly if $p^{r-(\beta-1/2)}$ diverges, i.e., $r>\beta-1/2$. 
This can be seen by simply setting the rejection region at $(p^{(r-\beta)+1/2}/2,\,+\infty)$ for the scaled statistic $\sum_{i=1}^p x(i)/\sqrt{p} $.
According to the lower bound on the performance limit in detection problems (see Theorem 8 in \cite{cai2011optimal}), we have shown that $S$ attains the optimal detection boundary \eqref{eq:detection-boundary-small-signals}.

We now turn to the $L_2$-norms.
Recall a non-central chi-square random variable $\chi^2_k(\lambda)$ has mean $(k+\lambda)$ and variance $2(k+2\lambda)$.
Since the observations have distributions $\mathrm{N}(0,1)$ under the null and $\mathrm{N}(p^r,1)$ under the alternative, we have $x^2(i)\sim \chi^2_1(0)$ for $i\not\in S$ and $x^2(i)\sim \chi^2_1(p^{2r})$ for $i\in S$.
Therefore, mean and variance of the (centered and scaled) $L_2$ statistics are
\begin{equation}
    \E\left[\frac{1}{\sqrt{p}}\sum_{i=1}^p \left(x(i)^2-1\right)\right] = 
    \begin{cases}
    0, & \text{under } H_0\\
    p^{1-\beta}p^{2r}p^{-1/2} = p^{1/2-\beta+2r} & \text{under } H_1,
    \end{cases}
\end{equation}
and 
\begin{equation}
    \mathrm{Var}\left(\frac{1}{\sqrt{p}}\sum_{i=1}^p \left(x(i)^2-1\right)\right) = 
    \begin{cases}
    \frac{1}{p}2p = 2, & \text{under } H_0\\
    \frac{1}{p}\left(2p+2p^{1-\beta+2r}\right) = 2(1+p^{2r-\beta}) & \text{under } H_1,
    \end{cases}
\end{equation}
respectively.
By the (Lyapunov) central limit theorem, we have
\begin{equation}
    \frac{1}{2p}\sum_{i=1}^p \left(x(i)^2-1\right) \implies \mathrm{N}(0,1),
\end{equation}
under the null, and
\begin{equation}
    \frac{1}{2p}\left(\sum_{i=1}^p \left(x(i)^2-1\right) - p^{1/2-\beta+2r}\right) \implies \mathrm{N}(0,1),
\end{equation}
under the alternative since $p^{2r-\beta}\to0$ for all $r<0$ and $\beta>0$.
Hence, perfect detection with the $L_2$-norm is possible if $p^{1/2-\beta+2r}$ diverges, i.e., $r>\beta/2-1/4$.
On the other hand, if $r<\beta/2-1/4$, the distributions of the (scaled) statistics merge under the null and the alternative. % \fbox{Hellinger distance is scale-invariant (show), detection is impossible}.

The case of $L_1$-norm is treated similarly.
Let $Y=|X|$ where $X\sim|\mathrm{N}(\mu,1)|$. 
Using the expressions for the mean and variance of $Y$ (see, e.g., \cite{tsagris2014folded}),
\begin{align}
    \mu_Y &= \E[Y] = \sqrt{\frac{2}{\pi}}e^{-\mu^2/2} + \mu(1-\Phi(-\mu)), \\
    \sigma_Y^2 &= \mathrm{Var}(Y) = \mu^2 + 1 - \mu^2_Y,
\end{align}
where $\Phi$ is the CDF of a standard normal random variable,
we have, regardless of the value of $\mu$,
\begin{equation} \label{eq:bounded-variance-abs-Gaussian}
    \sigma_Y^2 = \mathrm{Var}(Y) = \E(Y-\E Y)^2 \le \E(X-\E X)^2 = 1,
\end{equation}
where the inequality holds because absolute value is a Lipschitz function with Lipschitz constant 1.

By the central limit theorem, we have,
\begin{equation}
    \frac{1}{\sqrt{p}}\left(\sum_{i=1}^p |x(i)| - \sqrt{\frac{2}{\pi}}\right) \implies \mathrm{N}(0, 1-2/\pi)
\end{equation}
under the null.
On the other hand, when the alternative hypothesis holds, we have
\begin{align*}
    \E \left[ \frac{1}{\sqrt{p}} \left(\sum_{i=1}^p |x(i)| - \sqrt{\frac{2}{\pi}}\right) \right] 
    &= \frac{p^{1-\beta}}{\sqrt{p}}\left[\left(\sqrt{\frac{2}{\pi}}e^{-\mu^2/2} + \mu\left(1-2\Phi(-\mu)\right) \right) - \sqrt{\frac{2}{\pi}} \right] \\
    &= p^{1/2-\beta} \left[\sqrt{\frac{2}{\pi}}\left(e^{-p^{2r}/2} - 1 \right) + p^r\left(1-2\Phi(-\mu)\right) \right] \\
    &= p^{1/2-\beta} \left[\sqrt{\frac{2}{\pi}}\left(-p^{2r}/2 - O(p^{4r})\right) + p^r\left(\sqrt{\frac{2}{\pi}}p^r + O(p^{3r})\right) \right] \\
    &= p^{1/2-\beta} \sqrt{\frac{2}{\pi}} \left(p^{2r}/2 + O(p^{4r}) \right) \\
    &= p^{1/2-\beta+2r} \sqrt{{1}/{2\pi}} + O(p^{1/2-\beta+4r}),
\end{align*}
and 
\begin{align*}
    \mathrm{Var} \left(\frac{1}{\sqrt{p}} \left(\sum_{i=1}^p |x(i)| - \sqrt{\frac{2}{\pi}}\right) \right) 
    & = (1-p^{1-\beta})(1-2/\pi) + p^{1-\beta}\sigma_{Y}^2 \\
    & \to 1-2/\pi,
\end{align*}
by boundedness of $\sigma_{Y}^2$ shown in \eqref{eq:bounded-variance-abs-Gaussian}.
Again, by the (Lyapunov) central limit theorem, we conclude asymptotic normality of the centered and scaled $L_1$-norms under the alternative.
In an entirely analogous argument to the $L_2$-norm case, asymptotically perfect detection can be achieved if $p^{1/2-\beta+2r}$ diverges, i.e., $r>\beta/2-1/4$.
On the other hand, when $r<\beta/2-1/4$, the two hypotheses cannot be told apart by the $L_1$-norms since the distributions of the (scaled) statistics merge under the two hypotheses.
\end{proof}

\subsection{Proof of Theorem \ref{thm:Gaussian-error-approx-boundary}}
\label{subsec:proof-additive-error-approx-boundaries}

We first show the necessary condition. 
That is, when $\overline{r} < \beta$, no thresholding procedure is able to achieve approximate support recovery.
The arguments are similar to that in Theorem 1 of \cite{arias2017distribution}, although we allow for unequal signal sizes.

\begin{proof}[Proof of necessary condition in Theorem \ref{thm:Gaussian-error-approx-boundary}]
Denote the distributions of $\mathrm{N}(0,1)$, $\mathrm{N}(\underline{\Delta}, 1)$, and $\mathrm{N}((\overline{\Delta}, 1)$ as $F_0$, $F_{\underline{a}}$, and $F_{\overline{a}}$ respectively.

% We first show the necessary condition, i.e., when $\overline{r}<\beta$, approximate support recovery cannot be achieved with any thresholding procedure.
% In particular, we show that the liminf of the sum of FDP and NDP is at least 1.

Recall that thresholding procedures are of the form
$$
\widehat{S}_p = \left\{i\,|\,x(i) > t_p(x)\right\}.
$$
Denote $\widehat{S} := \left\{i\,|\,x(i) > t_p(x)\right\}$, and $\widehat{S}(u) := \left\{i\,|\,x(i) > u\right\}$.
For any threshold $u\ge t_p$ we must have $\widehat{S}(u)\subseteq\widehat{S}$, and hence
\begin{equation} \label{eq:approx-boundary-proof-FDP-Gaussian}
    \text{FDP} := \frac{|\widehat{S}\setminus{S}|}{|\widehat{S}|} \ge \frac{|\widehat{S}\setminus{S}|}{|\widehat{S}\cup{S}|} = \frac{|\widehat{S}\setminus{S}|}{|\widehat{S}\setminus{S}| + |S|} \ge
    \frac{|\widehat{S}(u)\setminus{S}|}{|\widehat{S}(u)\setminus{S}| + |S|}.
\end{equation}
On the other hand, for any threshold $u\le t_p$ we must have $\widehat{S}(u)\supseteq\widehat{S}$, and hence
\begin{equation} \label{eq:approx-boundary-proof-NDP-Gaussian}
    \text{NDP} := \frac{|{S}\setminus\widehat{S}|}{|{S}|} \ge 
    \frac{|{S}\setminus\widehat{S}(u)|}{|{S}|}.
\end{equation}
Since either $u\ge t_p$ or  $u\le t_p$ must take place, putting \eqref{eq:approx-boundary-proof-FDP-Gaussian} and \eqref{eq:approx-boundary-proof-NDP-Gaussian} together, we have
\begin{equation} \label{eq:approx-boundary-proof-converse-1-Gaussian}
    \text{FDP} + \text{NDP} 
    \ge \frac{|\widehat{S}(u)\setminus{S}|}{|\widehat{S}(u)\setminus{S}|+|{S}|} \wedge \frac{|{S}\setminus\widehat{S}(u)|}{|{S}|},
\end{equation}
for any $u$.
Therefore it suffices to show that for a suitable choice of $u$, the RHS of \eqref{eq:approx-boundary-proof-converse-1-Gaussian} converges to 1 in probability; the desired conclusion on FDR and FNR follows by the dominated convergence theorem.

Let $t^* = \sqrt{2q\log{p}}$ for some fixed $q$, we obtain an estimate of the tail probability by Mill's ratio \eqref{eq:Mills-ratio}, 
\begin{equation}
    \overline{F_0}(t^*) 
    \sim \frac{1}{t^*}\phi(t^*)
    = \frac{1}{2\sqrt{\pi q\log{p}}} p^{-q}, \label{eq:approx-boundary-proof-null-tail-prob-Gaussian}
\end{equation}
where $a_p\sim b_p$ is taken to mean $a_p/b_p\to 1$.
Observe that $|\widehat{S}(t^*)\setminus{S}|$ has distribution $\text{Binom}(p-s, \overline{F_0}(t^*))$ where $s=|S|$, denote $X = X_p := {|\widehat{S}(t^*)\setminus{S}|}/{|S|}$, and we have 
$$
\mu := \E\left[X\right] = \frac{(p-s)\overline{F_0}(t^*)}{s},
\quad \text{and} \quad
\var\left(X\right) = \frac{(p-s)\overline{F_0}(t^*){F_0}(t^*)}{s^2} \le \mu/s.
$$
Therefore for any $M>0$, we have, by Chebyshev's inequality,
\begin{equation}
    \P\left[X < M\right] 
    \le \P\left[\left|X-\mu\right| > \mu - M\right]
    \le \frac{\mu/s}{(\mu-M)^2}
    = \frac{1/(\mu s)}{(1-M/\mu)^2}. \label{eq:approx-boundary-proof-converse-2-Gaussian}
\end{equation}
Now, from the expression of $\overline{F_0}(t^*)$ in \eqref{eq:approx-boundary-proof-null-tail-prob-Gaussian}, we obtain
$$
\mu = (p^\beta - 1)\overline{F_0}(t^*) \sim \frac{1}{2\sqrt{\pi q\log{p}}} p^{\beta-q}.
$$
Since $\overline{r}<\beta$, we can pick $q$ such that $\overline{r}<q<\beta$. 
In turn, we have $\mu \to\infty$, as $p\to\infty$.
Therefore the last expression in \eqref{eq:approx-boundary-proof-converse-2-Gaussian} converges to 0, and we conclude that $X\to\infty$ in probability, and hence
\begin{equation} \label{eq:approx-boundary-proof-converse-3-Gaussian}
\frac{|\widehat{S}(t^*)\setminus{S}|}{|\widehat{S}(t^*)\setminus{S}|+|{S}|} 
= \frac{X}{X+1} \to 1 \quad \text{in probability}.
\end{equation}

On the other hand, we show that with the same choice of $u = t^*$, we have,
\begin{equation} \label{eq:approx-boundary-proof-converse-4-Gaussian}
    \frac{|{S}\setminus\widehat{S}(t^*)|}{|{S}|}\to 1 \quad \text{in probability}.
\end{equation}
By the stochastic monotonicity of Gaussian location family \eqref{eq:stochastic-monotonicity-Gaussian}, we have the following lower bound for the probability of missed detection for each signal $\mu(i)$, $i\in S$, 
\begin{equation} \label{eq:approx-boundary-proof-converse-5-Gaussian}
    \P[\mathrm{N}(\mu(i), 1) \le t^*] \ge F_{\overline{a}}(t^*).
\end{equation}
Since $|{S}\setminus\widehat{S}(t^*)|$ can be written as the sum of $s$ independent Bernoulli random variables,
\begin{equation*}
    |{S}\setminus\widehat{S}(t^*)| = \sum_{i\in S} \mathbbm{1}_{(-\infty, t^*]}(x(i)),
\end{equation*}
using with \eqref{eq:approx-boundary-proof-converse-5-Gaussian}, we conclude that $|{S}\setminus\widehat{S}(t^*)| \stackrel{\mathrm{d}}{\ge} \text{Binom}(s, {F_{\overline{a}}}(t^*))$.
Finally, we know that ${F_{\overline{a}}}(t^*)$ converges to 1 by our choice of diverging $t^*$, and the necessary condition is shown.
\end{proof}

We now turn to the sufficient condition. 
That is, when $\underline{r} > \beta$, the Benjamini-Hochberg procedure with slowly vanishing FDR levels achieves asymptotic approximate support recovery.

\begin{proof}[Proof of the sufficient condition in Theorem \ref{thm:Gaussian-error-approx-boundary}]
The FDR vanishes by our choice of $\alpha$ and the FDR-controlling property of the BH procedure \citep{benjamini1995controlling}.
It only remains to show that FNR also vanishes.

To do so we compare the FNR under the alternative specified in Theorem \ref{thm:Gaussian-error-approx-boundary} to one with all of the signal sizes equal to $\underline{\Delta}$.
By Lemma \ref{lemma:monotonicity-BH-procedure}, it suffices to show that the FNR under the BH procedure in this setting vanishes.
Let $x(i)$ be vectors of independent observations with $p-s$ nulls having standard Gaussian distributions, and $s$ signals having $\mathrm{N}(\underline{\Delta}, 1)$ distributions.

Denote the null and the alternative distributions as $F_0$ and $F_{a}$ respectively.
Let $\widehat{G}$ denote the empirical survival function as in \eqref{eq:empirical-tail-distribution}.
Define the empirical survival functions for the null part and signal part
\begin{equation} \label{eq:empirical-survival-null-signal-Gaussian}
    \widehat{W}_\text{null}(t) = \frac{1}{p-s}\sum_{i\not\in S}\mathbbm{1}\{x(i) \ge t\},
    \quad
    \widehat{W}_\text{signal}(t) = \frac{1}{s}\sum_{i\in S}\mathbbm{1}\{x(i) \ge t\},
\end{equation}
where $s=|S|$, so that
$$
\widehat{G}(t) = \frac{p-s}{p}\widehat{W}_\text{null}(t) + \frac{s}{p}\widehat{W}_\text{signal}(t).
$$

We need the following result to describe the deviations of the empirical distributions.
\begin{lemma}[Theorem 1 of \citet{eicker1979asymptotic}] \label{lemma:empirical-process}
Let $Z_1,\ldots,Z_k$ be iid with continuous survival function $Q$.
Let $\widehat{Q}_k$ denote their empirical survival function and define 
$\xi_k = \sqrt{2\log{\log{(k)}}/k}$ for $k \ge 3$. 
Then
$$
\frac{1}{\xi_k}\sup_z\frac{|\widehat{Q}_k(z) - Q(z)|}{\sqrt{Q(z)(1 - Q(z))}} \to 1,
$$
in probability as $k \to \infty$.
In particular,
$$
\widehat{Q}_k(z) = Q(z) + O_\P\left(\xi_k\sqrt{Q(z)(1 - Q(z))}\right),
$$
uniformly in z.
\end{lemma}

Apply Lemma \ref{lemma:empirical-process} to the two summands in $\widehat{G}$, we obtain
$\widehat{G}(t) = G(t) + \widehat{R}(t)$,
where 
\begin{equation} \label{eq:empirical-process-mean-Gaussian}
    G(t) = \frac{p-s}{p}\overline{F_0}(t) + \frac{s}{p}\overline{F_a}(t),
\end{equation}
and 
\begin{equation} \label{eq:empirical-process-residual-Gaussian}
    \widehat{R}(t) = O_\P\left(\xi_p\sqrt{\overline{F_0}(t)F_0(t)} + \frac{s}{p}\xi_s\sqrt{\overline{F_a}(t)F_a(t)}\right),
\end{equation}
uniformly in $t$.

Recall (see proof of Lemma \ref{lemma:monotonicity-BH-procedure}) that the BH procedure is the thresholding procedure with threshold set at 
\begin{equation} \label{eq:approx-boundary-proof-tau-Gaussian}
    \tau = \inf\{t\,|\,\overline{F_0}(t)\le\alpha\widehat{G}(t)\}. 
    %= \min\{t\,|\,\overline{F_0}(t)=\alpha\widehat{G}(t)\}.
\end{equation}
The NDP may also be re-written as 
$$
\text{NDP} = \frac{|{S}\setminus\widehat{S}|}{|{S}|} = \frac{1}{s}\sum_{i\in S}\mathbbm{1}\{x(i) < \tau\} = 1 - \widehat{W}_\text{signal}(\tau),
$$
so that it suffices to show that 
\begin{equation} \label{eq:approx-boundary-proof-sufficient-1-Gaussian}
    \widehat{W}_\text{signal}(\tau)\to 1
\end{equation} in probability.
Applying Lemma \ref{lemma:empirical-process} to $\widehat{W}_\text{signal}$, we know that 
$$
\widehat{W}_\text{signal}(\tau) = \overline{F_a}(\tau) + O_\P\left(\xi_s\sqrt{\overline{F_a}(\tau)F_a(\tau)}\right) = \overline{F_a}(\tau) + o_\P(1).
$$
So it suffices to show that $F_a(\tau)\to 0$ in probability.
Now let $t^* = \sqrt{2q\log(p)}$ for some $q$ such that $\beta<q<\underline{r}$.
We have 
\begin{equation} \label{eq:approx-boundary-proof-sufficient-2-Gaussian}
    F_a(t^*) 
    = \Phi(t^* - \underline{\Delta}) 
    = \Phi(\sqrt{2(q - \underline{r})\log{p}}) \to 0. 
\end{equation}
Hence in order to show \eqref{eq:approx-boundary-proof-sufficient-1-Gaussian}, it suffices to show 
\begin{equation} \label{eq:approx-boundary-proof-sufficient-3-Gaussian}
    \P\left[\tau \le t^*\right] \to 1.
\end{equation}
By \eqref{eq:empirical-process-mean-Gaussian}, the mean of the empirical process $\widehat{G}$ evaluated at $t^*$ is
\begin{equation} \label{eq:approx-boundary-proof-sufficient-4-Gaussian}
    G(t^*) = \frac{p-s}{p}\overline{F_0}(t^*) + \frac{s}{p}\overline{F_a}(t^*).
\end{equation}
The first term, using Relation \eqref{eq:approx-boundary-proof-null-tail-prob-Gaussian}, is asymptotic to $p^{-q}L(p)$, where $L(p)$ is the logarithmic term in $p$.
The second term, since $\overline{F_a}(t^*)\to 1$ by Relation \eqref{eq:approx-boundary-proof-sufficient-2-Gaussian}, is asymptotic to $p^{-\beta}$.
Therefore, $G(t^*) \sim p^{-q}L(p) + p^{-\beta} \sim p^{-\beta}$, since 
$p^{\beta-q}L(p)\to0$ where $q>\beta$.

The fluctuation of the empirical process at $t^*$, by Relation \eqref{eq:empirical-process-residual-Gaussian}, is 
\begin{align*}
    \widehat{R}(t^*) 
    &= O_\P\left(\xi_p\sqrt{\overline{F_0}(t^*)F_0(t^*)} + \frac{s}{p}\xi_s\sqrt{\overline{F_a}(t^*)F_a(t^*)}\right)\\
    &= O_\P\left(\xi_p\sqrt{\overline{F_0}(t^*)}\right) + o_\P\left(p^{-\beta}\right).
\end{align*}
By \eqref{eq:approx-boundary-proof-null-tail-prob-Gaussian} and the expression for $\xi_p$, the first term is $O_\P\left(p^{-(q+1)/2}L(p)\right)$ where $L(p)$ is a poly-logarithmic term in $p$.
Since $\beta<\min\{q,1\}$, we have $\beta<(q+1)/2$, and hence $\widehat{R}(t^*) = o_\P(p^{-\beta})$.

Putting the mean and the fluctuation of $\widehat{G}(t^*)$ together, we obtain
$$
\widehat{G}(t^*) = G(t^*) + \widehat{R}(t^*) \sim_\P G(t^*) \sim p^{-\beta},
$$
and therefore, together with \eqref{eq:approx-boundary-proof-null-tail-prob-Gaussian}, we have
$$
\overline{F_0}(t^*)/\widehat{G}(t^*) = p^{\beta-q}L(p)(1+o_{\P}(1)),
$$
which is eventually smaller than the FDR level $\alpha$ by the assumption \eqref{eq:slowly-vanishing-error} and the fact that $\beta<q$.
That is, 
$$
\P\left[\overline{F}_0(t^*) / \widehat{G}(t^*) < \alpha\right] \to 1.
$$
By definition of $\tau$ (recall \eqref{eq:approx-boundary-proof-tau-Gaussian}), this implies that $\tau \le t^*$ with probability tending to 1, and \eqref{eq:approx-boundary-proof-sufficient-3-Gaussian} is shown.
The proof for the sufficient condition is complete.
\end{proof}

\subsection{Proof of Theorems \ref{thm:Gaussian-error-exact-approx-boundary} and \ref{thm:Gaussian-error-approx-exact-boundary}}
\label{subsec:proof-additive-error-mix-boundaries}

Proof of Theorem \ref{thm:Gaussian-error-exact-approx-boundary} uses ideas from the proof of Theorem \ref{thm:Gaussian-error-approx-boundary} and is substantially shorter.

\begin{proof}[Proof of Theorem \ref{thm:Gaussian-error-exact-approx-boundary}]
We first show the sufficient condition. 
Vanishing FWER is guaranteed by the properties of the procedures, and we only need to show that FNR also goes to zero. 
Similar to the proof of Theorem \ref{thm:Gaussian-error-approx-boundary}, it suffices to show that
\begin{equation} \label{eq:additive-error-exact-approx-boundary-proof-sufficient-1}
    \text{NDP} = 1 - \widehat{W}_\text{signal}(t_p) \to 0,
\end{equation}
where $t_p$ is the threshold of Bonferroni's procedure.

Since $\alpha$ vanishes slowly (see Definition \ref{eq:slowly-vanishing-error}), for any $\delta>0$, we have $p^{-\delta}=o(\alpha)$.
Therefore, we have $-\log\alpha\le\delta\log{p}$ for large $p$, and
\begin{equation*} 
    1 \le \limsup_{p\to\infty}\frac{2\log{p} - 2\log{\alpha}}{2\log{p}} \le 1+\delta,
\end{equation*}
for any $\delta>0$.
Therefore, by the expression for normal quantiles, we know that 
$$
t_p=F^\leftarrow(1-\alpha/p)\sim(2\log{p}-2\log{\alpha})^{1/2} \sim(2\log{p})^{1/2}.
$$

Since $\underline{r}>\widetilde{g}(\beta)=1$, we can pick $q$ such that $1<q<\underline{r}$.
Let $t^* = \sqrt{2q\log{p}}$, we know that $t_p<t_p^*$ for large $p$.
Therefore for large $p$, we have
$$
\widehat{W}_\text{signal}(t_p) \ge \widehat{W}_\text{signal}(t^*) \ge \overline{F_a}(t^*) + o_\P(1),
$$
where $\overline{F_a}$ is the survival function of $\mathrm{N}(\sqrt{2\underline{r}\log{p}}, 1)$; the last inequality follows from the stochastic monotonicity of the Gaussian location family \eqref{eq:stochastic-monotonicity-Gaussian}, and Lemma \ref{lemma:empirical-process}.
Indeed, by our choice of $q<\underline{r}$, we obtain
$$
F_a(t^*) = \Phi\left(\sqrt{2(q-\underline{r})\log{p}}\right)\to0,
$$
and \eqref{eq:additive-error-exact-approx-boundary-proof-sufficient-1} is shown. 
This completes the proof of the sufficient condition.

The proof of the necessary condition follows similar structure as in the proof of Theorem \ref{thm:Gaussian-error-approx-boundary}, and uses the lower bound
\begin{equation} \label{eq:additive-error-exact-approx-boundary-proof-necessary-1}
    \mathrm{FWER}(\mathcal{R}) + \mathrm{FNR}(\mathcal{R}) \ge \P\left[\max_{i\in S^c}x(i)>u\right] \wedge \E\left[\frac{|S\setminus \widehat{S}(u)|}{|S|}\right],
\end{equation}
which holds for any arbitrary thresholding procedure $\mathcal{R}$ and arbitrary real $u\in\R$.

By the assumption that $\overline{r}<\widetilde{g}(\beta)=1$, we can pick $q$ such that $\overline{r}<q<1$ and let $u = t^*=\sqrt{2q\log{p}}$ in \eqref{eq:additive-error-exact-approx-boundary-proof-necessary-1}.
By relative stability of iid Gaussian random variables \eqref{eq:relative-stability-Gaussian-maxima}, we have
\begin{equation} \label{eq:additive-error-exact-approx-boundary-proof-necessary-2}
    \P\left[\frac{\max_{i\in S^c} x(i)}{\sqrt{2\log{p}}} > \frac{t^*}{\sqrt{2\log{p}}}\right] \to 1.
\end{equation}
since the first fraction in \eqref{eq:additive-error-exact-approx-boundary-proof-necessary-2} converges to 1, while the second converges to $q<1$.
Therefore, the first term on the right-hand side of \eqref{eq:additive-error-exact-approx-boundary-proof-necessary-1} converges to 1.

On the other hand, by the stochastic monotonicity of Gaussian location family \eqref{eq:stochastic-monotonicity-Gaussian}, the probability of missed detection for each signal is lower bounded by $\P[Z+\mu(i) \le t^*] \ge F_{\overline{a}}(t^*)$, where $Z$ is a standard Gaussian r.v., and $F_{\overline{a}}$ is the cdf of $\mathrm{N}(\sqrt{2\overline{r}\log{p}}, 1)$.
Therefore, $|{S}\setminus\widehat{S}(t^*)| \stackrel{\mathrm{d}}{\ge} \text{Binom}(s, {F_{\overline{a}}}(t^*))$, and it suffices to show that ${F_{\overline{a}}}(t^*)$ converges to 1.
Indeed,
\begin{equation*}
    {F_{\overline{a}}}(t^*) = \Phi(\sqrt{2(q-\overline{r})\log{p}}) \to 1,
\end{equation*}
by our choice of $q>\overline{r}$.
Hence both quantities in the minimum on the right-hand side of \eqref{eq:additive-error-exact-approx-boundary-proof-necessary-1} converge to 1 in the limit, and the necessary condition is shown.
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm:Gaussian-error-approx-exact-boundary}]
We first show the sufficient condition.
Since FDR control is guaranteed by the BH procedure, we only need to show that the FWNR also vanishes, that is,
\begin{equation} \label{eq:approx-exact-boundary-proof-sufficient-1-Gaussian}
    \P\left[\min_{i\in S}x(i) \ge \tau\right] \to 1,
\end{equation}
where $\tau$ is the threshold for the BH procedure.

By the assumption that $\underline{r}>\widetilde{h}(\beta)=(\sqrt{\beta}+\sqrt{1-\beta})^2$, we have $\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{\beta}$, so we can pick $q>0$, such that 
\begin{equation} \label{eq:approx-exact-boundary-proof-sufficient-2-Gaussian}
\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{q}>\sqrt{\beta}.
\end{equation}
We only need to show that with a specific choice of $t^*=\sqrt{2q\log{p}}$ where
\begin{equation} \label{eq:additive-error-approx-exact-boundary-proof-sufficient-1}
\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{q}>\sqrt{\beta},
\end{equation}
we have both
\begin{equation} \label{additive-error-eq:approx-exact-boundary-proof-sufficient-2}
\P\left[\tau\le t^*\right]\to 1,
\end{equation}
and 
\begin{equation} \label{eq:additive-error-approx-exact-boundary-proof-sufficient-3}
    \P\left[\min_{i\in S}x(i) \ge t^* \right] \to 1,
\end{equation}
so that 
\begin{equation*} 
    \P\left[\min_{i\in S}x(i) \ge \tau\right] \ge 
    % \P\left[\min_{i\in S}x(i) \ge t^* \ge \tau\right] \ge
    \P\left[\min_{i\in S}x(i) \ge t^*,\; t^* \ge \tau\right] \to 1.
\end{equation*}

Relation \eqref{additive-error-eq:approx-exact-boundary-proof-sufficient-2} follows in exactly the same way \eqref{eq:approx-boundary-proof-sufficient-3-Gaussian} did on page  \pageref{eq:approx-boundary-proof-sufficient-3-Gaussian}.

Dividing the left-hand-side in Relation \eqref{eq:additive-error-approx-exact-boundary-proof-sufficient-3} by $\sqrt{2\log{p}}$, we have,
\begin{align*}
    \frac{\min_{i\in S}x(i)}{\sqrt{2\log{p}}} 
    &= \frac{\min_{i\in S}\mu(i)+\epsilon(i)}{\sqrt{2\log{p}}} 
    \stackrel{\mathrm{d}}{\ge} \frac{\sqrt{2\underline{r}\log{p}} + \min_{i\in S}\epsilon(i)}{\sqrt{2\log{p}}} \\
    &\to -\sqrt{1-\beta} + \sqrt{\underline{r}},
\end{align*}
where the last convergence follows from the relative stability of iid Gaussians minima \eqref{eq:relative-stability-Gaussian-minima}. 
On the other hand, ${t^*}/{\sqrt{2\log{p}}}=\sqrt{q}<\sqrt{\underline{r}}-\sqrt{1-\beta}$ by our choice of ${q}$, and Relation \eqref{eq:additive-error-approx-exact-boundary-proof-sufficient-3} follows.

The necessary condition follows from the lower bound
\begin{equation} \label{eq:additive-error-approx-exact-boundary-proof-necessary-1}
    \mathrm{FDR}(\mathcal{R}) + \mathrm{FWNR}(\mathcal{R}) \ge \E\left[\frac{|\widehat{S}(u)\setminus S|}{|\widehat{S}(u)\setminus S| + |S|}\right] \wedge 
    \P\left[\min_{i\in S}x(i)<u\right],
\end{equation}
which holds for any thresholding procedure $\mathcal{R}$ and for arbitrary $u\in\R$.
In particular, we show that both terms in the minimum in \eqref{eq:additive-error-approx-exact-boundary-proof-necessary-1} converge to 1 when we set $u=t^*=\sqrt{2q\log{p}}$ where 
\begin{equation}
\sqrt{\overline{r}}-\sqrt{1-\beta}<\sqrt{q}<\sqrt{\beta}.
\end{equation}

On the one hand, we have,
$$
\frac{\min_{i\in S}x(i)}{\sqrt{2\log{p}}} 
\stackrel{\mathrm{d}}{\le} \frac{\min_{i\in S}\epsilon(i)+\sqrt{2\overline{r}\log{p}}}{\sqrt{2\log{p}}} 
\to \sqrt{\overline{r}}-\sqrt{1-\beta},
$$
by relative stability of iid Gaussians \eqref{eq:relative-stability-Gaussian-minima}. On the other hand, ${t^*}/{\sqrt{2\log{p}}}=\sqrt{q}>\sqrt{\underline{r}}-\sqrt{1-\beta}$ by our choice of ${q}$;
this shows that the second term on the right-hand side of \eqref{eq:additive-error-approx-exact-boundary-proof-necessary-1} converges to 1.

Observe that $|\widehat{S}(t^*)\setminus{S}|$ has distribution $\text{Binom}(p-s, \overline{\Phi}(t^*))$, and define $X = X_p := {|\widehat{S}(t^*)\setminus{S}|}/{|S|}$, we obtain,
% On the other hand, define $ = \E[|S\setminus\widehat{S}(t^*)|/|S|]$,
\begin{align*}
    \mu &:= \E[X] = (p^\beta-1)\overline{\Phi}(t^*) 
    \sim (p^\beta-1)\frac{\phi(t^*)}{t^*} \\
    &\sim \frac{1}{\sqrt{2\pi}}\left(2q\log{p}\right)^{-1/2}p^{\beta-q}\to\infty,
\end{align*}
where the divergence follows from our choice of $q<\beta$.
Using again Relations \eqref{eq:approx-boundary-proof-converse-2-Gaussian} and \eqref{eq:approx-boundary-proof-converse-3-Gaussian}, we conclude that the first term on the right-hand side of \eqref{eq:additive-error-approx-exact-boundary-proof-necessary-1} also converges to 1.
This completes the proof of the necessary condition.
\end{proof}

### 2020-08-17 3.phase_transitions/phase_transitions.tex
add draft converted from thesis

We study the fundamental limits of the signal detection and support recovery problems in the location models with independent Gaussian errors in this chapter.
Specifically, we derive the conditions under which the detection and support recovery problems succeed and fail in the sense of \eqref{eq:support-recovery-success} and \eqref{eq:support-recovery-failure}, in the additive error model 
\begin{equation} \label{eq:model-additive-Chapter3}
    x(i) = \mu(i) + \epsilon(i), \quad i=1,\ldots,p,
\end{equation}
where the errors $\epsilon(i)$'s are \ac{iid} standard Gaussians random variables.
We restrict our analysis to models with independent and identically distributed Gaussian errors for the moment.
Both the distributional assumption and the independence assumption will be relaxed in the following chapters.

As laid out in Section \ref{sec:asymptotics}, we work under the asymptotic regime where the problem dimension $p$ diverges to infinity.
Let the signal vectors $\mu = \mu_p$ have 
\begin{equation} \label{eq:signal-sparsity-additive}
    |S_p| = \left\lfloor p^{1-\beta} \right\rfloor, \quad \beta\in(0,1]
\end{equation}
non-zero entries, where $\beta$ parametrizes the problem sparsity.
The closer $\beta$ is to 1, the sparser the support $S$; conversely, when $\beta$ is close to 0, the support is dense with many non-null signals.
We consider one-sided alternatives \eqref{eq:global-test-one-sided}, and parametrize the range of the non-zero (and perhaps unequal) signals with
\begin{equation} \label{eq:signal-size-additive}
    \underline{\Delta} = \sqrt{2\underline{r}\log{p}}
    \le \mu(i) \le
    \overline{\Delta} = \sqrt{2\overline{r}\log{p}}, \quad \text{for all}\;\;i\in S_p,
\end{equation}
for some constants $0<\underline{r}\le\overline{r}\le+\infty$.

% \label{rmk:global-test-boundary}
The parametrization of signal sparsity \eqref{eq:signal-sparsity-additive} and signal sizes \eqref{eq:signal-size-additive} in the Gaussian model was first introduced in \citet{ingster1998minimax}, and later adopted by \cite{hall2010innovated}, \cite{cai2011optimal}, \cite{zhong2013tests}, \cite{cai2014optimal}, \cite{arias2017distribution1}, and numerous others for studying the signal detection problem in Gaussian location-scale models.
Similar scalings of sparsity and signal size are also used in, e.g., \cite{ji2012ups}, \cite{jin2014optimality}, \cite{butucea2018variable} to study the phase transitions of the support recovery problems under Gaussianity assumptions.

\section{Sparse signal detection problems}
\label{sec:global-tests}
\input{3.phase_transitions/3.global-tests.tex}

\section{Sparse signal support recovery problems}
\label{sec:additive-error-model-boundaries}
\input{3.phase_transitions/3.Gaussian-support-recovery.tex}

\section{Proofs}
\label{sec:proofs}
\input{3.phase_transitions/3.proofs-phase-transitions.tex}

### 2020-08-17 4.exact_support_recovery/4.gaps_in_false_discovery_control.tex
add draft converted from thesis

We offer a brief discussion on the statistical implications of Theorem \ref{thm:sufficient} and \ref{thm:necessary}.
Before doing so, we shall first review some related work on sparse signal detection and approximate support recovery.

The problem of sparse signal detection was first studied by \citet*{ingster1998minimax} under independent Gaussian errors.
Specifically, under the parametrization \eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized} (with $\nu=2$), it was shown that the detection problem can be answered perfectly as $p\to\infty$, when signal size $r$ is above a threshold $f(\beta)$, where
\begin{equation} \label{eq:detection-boundary}
f(\beta) = \begin{cases}
\left(1 - \sqrt{1 - \beta}\right)^2 &,\ \beta\ge3/4\\
\beta - 0.5 &,\ 1/2<\beta<3/4.
\end{cases}
\end{equation}
Conversely, when $r<f(\beta)$, we can do no better than random guessing. 
Thus, the function $f(\beta)$ fully characterizes the so-called \emph{detection boundary} of the signal detection problem, and demonstrates a phase-transition phenomenon. 
\citet*{donoho2004higher} showed that the Higher Criticism statistic, originally proposed by Tukey, is a procedure that achieves the detection boundary asymptotically, without prior knowledge of the sparsity and the signal size.

In this context of approximate support recovery, the corresponding concept to type I error is the \emph{False Discovery Proportion} (FDP), defined as $\text{FDP} = |\widehat{S}\setminus S|\big/|\widehat{S}|$ (with \emph{False Discovery Rate} (FDR) being the expectation of FDP), 
and the counterpart of type II error in this context being the \emph{False Non-discovery Proportion} (FNP), defined $\text{NDP} = |S\setminus\widehat{S}|\big/|S|$.
\citet*{haupt2011distilled} showed that for signal size $r > \beta$, the sum of FDP and FNP can be made to vanish as $p\to\infty$; while if $r < \beta$, no thresholding procedure can succeed asymptotically. We shall call this boundary 
\begin{equation} \label{eq:weak-classification-boundary}
    h(\beta) = \beta
\end{equation}
the \emph{weak classification boundary}. Recently, \citet*{arias2017distribution} showed that the Benjamini-Hochberg procedure \citep*{benjamini1995controlling} and the Barber-Cand{\`e}s procedure \citep*{barber2015controlling} are practical procedures that achieve this weak classification boundary.
These procedures are special cases of \emph{thresholding procedures}.

An even more stringent notion of false discovery is the \emph{Family-Wise Error Rate} (FWER), defined as $1 - \mathbb P[\widehat{S} \subseteq S]$, which is probability of falsely reporting any signal not in the support set.
Observe that vanishing FDP and NDP does not imply $\P\left[\widehat{S} = S\right]\to 1$;
the latter, stronger, notion of set consistency requires that the FWER vanish as well.

### 2020-08-17 4.exact_support_recovery/4.heavy-tailed.tex
add draft converted from thesis

We analyze the performance of thresholding estimators under heavy-tailed models in this section, and illustrate its lack of phase transition.
Suppose we have iid errors with Pareto tails in Model \eqref{eq:model-additive}, that is, $\epsilon(i)$'s have common marginal distribution $F$ where
\begin{equation} \label{eq:pareto-tails}
    \overline{F}(x) \sim x^{-\alpha} \quad \text{and} \quad F(-x) \sim x^{-\alpha},    
\end{equation}
as $x\to\infty$. 
It is well-known (see, e.g., Theorem 1.6.2 of \citep{leadbetter2012extremes}) that the maxima of iid Pareto random variables have Frechet-type limits.
Specifically, we have
\begin{equation} \label{eq:Frechet-limit-1}
    \frac{\max_{i\in\{1,\ldots,p\}}\epsilon(i)}{u_p} \implies Y,
\end{equation}
in distribution, where $u_p = F^{\leftarrow}(1-1/p)\sim p^{1/\alpha}$, and $Y$ is a standard $\alpha$-Frechet random variable, i.e.,
\begin{equation*}
    \P[Y\le t] = \exp{\{-t^{-\alpha}\}}, \quad t>0.
\end{equation*}
By symmetry in our assumptions, the same argument applies to the minima as well.

\begin{theorem} \label{thm:heavy-tails}
Let errors in Model \eqref{eq:model-additive} be as described in Relation \eqref{eq:pareto-tails}.
Let the signal have $s = |S| = fp$ non-zero entries, with magnitude $\Delta = rp^{1/\alpha}$, where both $f\in(0,1)$ and $r\in(0,+\infty)$ may depend on $p$, so that no generality is lost.

Under these assumptions, the necessary condition for thresholding procedures $\widehat{S}$ to achieve exact support recovery ($\P[\widehat{S}=S]\to1$) is 
\begin{equation} \label{eq:heavy-tails-exact-recovery}
    \liminf_{p\to\infty} r = \infty.
\end{equation}
Condition \eqref{eq:heavy-tails-exact-recovery} is also sufficient for the oracle thresholding procedure to succeed in the exact support recovery problem.

On the other hand, the necessary and sufficient condition for all thresholding procedures to fail exact support recovery ($\P[\widehat{S}=S]\to0$) is 
$$
\limsup_{p\to\infty} r = 0.
$$
\end{theorem}

In other words, Theorem \ref{thm:heavy-tails} states that there does not exist a non-trivial phase transition for thresholding procedures when errors have (two-sided) $\alpha$-Pareto tails.

\begin{proof}[Proof of Theorem \ref{thm:heavy-tails}]
Recall the oracle thresholding procedure $\widehat{S}^* = \left\{i:x(i) \ge x_{[s]}\right\}$, and the set of all thresholding procedures, denoted 
${\cal S}$ (see Definition \ref{eq:thresholding-procedure}).
The probability of exact support recovery by any thresholding procedure $\widehat{S}\in{\cal S}$ is bounded above by that of $\widehat{S}^*$, that is,
\begin{align}
    \max_{\widehat{S}\in{\cal S}}\P[\widehat{S}=S] 
        &= \P[\widehat{S}^*=S] 
        = \P\Big[\max_{i\in S^c}x(i) \le \min_{i\in S}x(i)\Big] \nonumber \\
        &= \P\Big[\frac{\max_{i\in S^c}x(i)}{u_p} \le \frac{\min_{i\in S}x(i)}{u_p}\Big] \nonumber \\
        &= \P\Big[\frac{M_{S^c}}{u_p} \le \frac{m_S}{u_p} + r_p\Big], \label{eq:heavy-tailed-case-proof-0}
        % &= \P\Big[\underbrace{(1-f)^{1/\alpha}Y^{(1)}}_{=:F_1} + \underbrace{f^{1/\alpha}Y^{(2)}}_{=:F_2} \le r\Big], 
\end{align}
where $M_{S^c} = \max_{i\in S^c}\epsilon(i)$ and $m_S = \min_{i\in S}\epsilon(i)$.
For any $\alpha > 0$, the following elementary relations hold,
\begin{equation*}
    0 < L \le (1-f)^{1/\alpha} + f^{1/\alpha} \le U < \infty, \quad \text{for all} \; f\in(0,1),
\end{equation*}
where $L = \min\left\{1, 2(1/2)^{1/\alpha}\right\}$ and $U = \max\left\{1, 2(1/2)^{1/\alpha}\right\}$.
Therefore we have,
\begin{equation} \label{eq:heavy-tailed-case-proof-1}
    U\max\left\{\frac{M_{S^c}}{u_p}, -\frac{m_S}{u_p}\right\} < r_p
    \implies
    (1-f)^{1/\alpha}\frac{M_{S^c}}{u_p} - f^{1/\alpha}\frac{m_S}{u_p} < r_p,
\end{equation}
and 
\begin{equation} \label{eq:heavy-tailed-case-proof-2}
    L\min\left\{\frac{M_{S^c}}{u_p}, -\frac{m_S}{u_p}\right\} < r_p
    \impliedby
    (1-f)^{1/\alpha}\frac{M_{S^c}}{u_p} - f^{1/\alpha}\frac{m_S}{u_p} < r_p.
\end{equation}
Putting together \eqref{eq:heavy-tailed-case-proof-0}, \eqref{eq:heavy-tailed-case-proof-1}, and \eqref{eq:heavy-tailed-case-proof-2}, we have
\begin{equation} \label{eq:heavy-tailed-case-proof-3}
    \P\Big[\max\left\{\frac{M_{S^c}}{u_p}, -\frac{m_S}{u_p}\right\} < r_p/U\Big]
    \le \P[\widehat{S}^*=S]
    \le \P\Big[\min\left\{\frac{M_{S^c}}{u_p}, -\frac{m_S}{u_p}\right\} < r_p/L\Big].
\end{equation}
We know from the weak convergence result \eqref{eq:Frechet-limit-1} that for any $\epsilon>0$ there is a constant $N$ such that for all $p>N$ we have 
\begin{equation} \label{eq:heavy-tailed-case-proof-3.5}
    \P\Big[\max\left\{\frac{M_{S^c}}{u_p}, -\frac{m_S}{u_p}\right\} < r_p/U\Big]
    \ge \P\Big[\max\left\{Y^{(1)}, Y^{(2)}\right\} < {r_p}/{U}\Big] - \epsilon,
\end{equation}
where $Y^{(1)}$ and $Y^{(2)}$ are independent $\alpha$-Frechet random variables with scale coefficients $(1-f)^{1/\alpha}$ and $f^{1/\alpha}$ respectively.
That is,
\begin{equation*}
    \P[Y^{(1)}\le t] = \exp{\{-(1-f)/t^\alpha\}}, 
    \quad \text{and} \quad
    \P[Y^{(2)}\le t] = \exp{\{-f/t^\alpha\}}.
\end{equation*}
Since the distributional limit in \eqref{eq:heavy-tailed-case-proof-3.5} has a density (with respect to the Lebesgue measure), we know that density is bounded above by a finite constant, say, $K$.
For the same choice of $\epsilon$ as before, we can find a further constant $N'$ such that for all $p>\max\{N, N'\}$ we have 
$$
    \liminf r_p < \epsilon/K + r_p,
$$
so that the right hand side of \eqref{eq:heavy-tailed-case-proof-3.5} is bounded by
\begin{equation} \label{eq:heavy-tailed-case-proof-3.6}
    \P\Big[\max\left\{Y^{(1)}, Y^{(2)}\right\} < {r_p}/{U}\Big] - \epsilon
    \ge \P\Big[\max\left\{Y^{(1)}, Y^{(2)}\right\} < \frac{\liminf r_p}{U}\Big] - 2\epsilon.
\end{equation}
By the arbitrariness in the choice of $\epsilon$, we conclude from \eqref{eq:heavy-tailed-case-proof-3.5} and \eqref{eq:heavy-tailed-case-proof-3.6} that
\begin{equation} \label{eq:heavy-tailed-case-proof-4}
    \liminf \P\Big[\max\left\{\frac{M_{S^c}}{u_p}, -\frac{m_S}{u_p}\right\} < r_p/U\Big]
    \ge \P\Big[\max\left\{Y^{(1)}, Y^{(2)}\right\} < \frac{\liminf r_p}{U}\Big].
\end{equation}
Combining Relations \eqref{eq:heavy-tailed-case-proof-3} and \eqref{eq:heavy-tailed-case-proof-4}, we know that if $\liminf r_p = \infty$, we must have 
$$
    \liminf\P\left[\widehat{S}^*=S\right]
    \ge \P\Big[\max\left\{Y^{(1)}, Y^{(2)}\right\} < \frac{\liminf r_p}{U}\Big] = 1.
$$
Conversely, if $\liminf\P\left[\widehat{S}^*=S\right]<1$, we must have $\liminf r_p < \infty$.

Similarly, we can obtain the upper bound of exact support recovery probability for the optimal thresholding procedure,
\begin{equation} \label{eq:heavy-tailed-case-proof-5}
    \limsup \P\Big[\min\left\{\frac{M_{S^c}}{u_p}, -\frac{m_S}{u_p}\right\} < r_p/L\Big]
    \le \P\Big[\min\left\{Y^{(1)}, Y^{(2)}\right\} < \frac{\limsup r_p}{L}\Big].
\end{equation}
The conclusions of the second part of Theorem \ref{thm:heavy-tails} follow from \eqref{eq:heavy-tailed-case-proof-3} and \eqref{eq:heavy-tailed-case-proof-5}.
\end{proof}

The probability of exact recovery can be approximated if the parameters $r$ and $f$ converge.
The next result follows from a small modification of the arguments in the proof of Theorem \ref{thm:heavy-tails}.

\begin{corollary}
Under the assumptions in Theorem \ref{thm:heavy-tails}, if 
$\lim r = r^*$, and $\lim f = f^*$, for some constant $r^*\ge0$ and $f^*\in[0,1]$, then 
$$
    \lim \P[\widehat{S}^*=S] 
    = \P\Big[(1-f^*)^{1/\alpha}Z_1 + (f^*)^{1/\alpha}Z_2 < {r^*}\Big].
$$
where $Z_1$ and $Z_2$ are independent standard $\alpha$-Frechet random variables, i.e., $\P[Z_i \le t] = \exp{\{-x^{-\alpha}\}}$, $x>0$.
\end{corollary}

\begin{remark}
Of course one might wonder if it would be meaningful to derive a ``phase transition'' under a different parametrization of the signal sizes, say 
\begin{equation} \label{eq:Pareto-parametrization-with-boundary}
    \Delta = p^{r/\alpha}.
\end{equation}
In this case, Theorem \ref{thm:heavy-tails} suggests that a ``phase transition'' takes place at $r=1$.
However, this non-multiplicative parametrization of the signal sizes would make power analysis (like in Example \ref{exmp:gap-when-signal-sparse}) dimension-dependent.

To illustrate, in the case of Gaussian errors with variance 1, if we were interested in small signals of size $\sqrt{2r\log{p}}$, where $r<1$ is below the boundary \eqref{eq:strong-classification-boundary}, then we only need $n > 2/r$ samples to guarantee discovery of their support.
In the Pareto case with parametrization \eqref{eq:Pareto-parametrization-with-boundary}, however, if we were interested in small signals of size $p^{r/\alpha}$, where $r<1$, then the ``boundary'' says that we will need $n > p^{2(1-r)/\alpha}$ samples, which is exponential in the dimension $p$ and quickly diverges.
Recall that the ``boundary'' is really an asymptotic result in $p$. 
Such an approximation in finite dimensions becomes invalid.
\end{remark}

### 2020-08-17 4.exact_support_recovery/4.minimax.tex
add draft converted from thesis

We establish in this section minimax versions of our results from Section \ref{sec:boundary}.
Specifically, if we restrict ourselves to \emph{the class of thresholding procedures} $\cal T$ (defined in \eqref{eq:thresholding-procedure}), then Bonferroni's procedure is minimax optimal, for \emph{any} fixed dependence structures in the URS class.
This is formalized in Corollary \ref{cor:point-wise-minimax} in Section \ref{subsec:point-wise-minimax}.
We refer to this result as \emph{point-wise} minimax, to emphasize the fact that this optimality holds for every \emph{fixed} URS array.

Meanwhile, if we search over \emph{all procedures}, but expand the parameter space to include {all} dependence structures, then a different minimax optimality statement holds for Bonferroni's procedure.
This result, formally stated in Section \ref{subsec:minimax-over-dependence}, is a consequence of our characterization of the finite-sample Bayes optimality of thresholding procedures in Sections \ref{subsec:Bayes-optimality} and \ref{subsec:optimal-procedure-sub-exponential}.
% The result is of independent interest and it is the main contribution of this section.

Finally, we offer some insights into the support recovery problem in the case when errors have heavier-than-exponential tails in Section \ref{subsec:optimal-procedure-super-exponential}.

\subsection{Point-wise minimax optimality}
\label{subsec:point-wise-minimax}

Theorems \ref{thm:sufficient} and \ref{thm:necessary} can be cast in the form of an asymptotic minimax statement. 
% (concealing the gap between sufficient and necessary conditions as pointed out in Remark \ref{rmk:gap-between-sufficient-necessary}).

\begin{corollary}[Point-wise minimax]
\label{cor:point-wise-minimax}
Let $\widehat{S}^{\text{Bonf}}$ be the sequence of Bonferroni's procedure described in Theorem \ref{thm:sufficient}. 
Let also the errors have common $\text{AGG}(\nu)$ distribution $F$ with parameter $\nu>0$, and $\Theta_p^+$ be as defined in \eqref{eq:minimax-signal-config-over}.
If $\underline{r}>g(\beta)$, then we have
\begin{equation} \label{eq:point-wise-minimax-above}
    \limsup_{p\to\infty} \sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P(\widehat{S}^{\text{Bonf}}_p \neq S_p) = 0,
\end{equation}
for arbitrary dependence structure of the error array ${\cal E} = \{\epsilon_p(i)\}_p$.
Let $\cal T$ be the class of thresholding procedures \eqref{eq:thresholding-procedure}. 
If $\underline{r}<g(\beta)$, then we have
\begin{equation} \label{eq:point-wise-minimax-below}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P(\widehat{S}_p \neq S_p) = 1,
\end{equation}
for any error dependence structure such that ${\cal E}\in U(F)$ and ${(-\cal E)}\in U(F)$.
\end{corollary}

\begin{proof}[Proof of Corollary \ref{cor:point-wise-minimax}]
The first conclusion \eqref{eq:point-wise-minimax-above} is a restatement of Theorem \ref{thm:sufficient}.

For the second statement \eqref{eq:point-wise-minimax-below}, since $\underline{r}<g(\beta)$, we can pick a sequence $\mu^*\in\Theta_p^+(\beta, \underline{r})$ such that $|S_p| = \lfloor p^{1-\beta}\rfloor$, with signals having the same signal size $\mu(i)=(2r\log{p})^{1/\nu}$ for all $i\in S_p$, where $\underline{r}<{r}<g(\beta)$.
For this particular choice of $\mu^*$ we have $\mu^*\in\Theta_p^-(\beta, \overline{r})$ where $r<\overline{r}<g(\beta)$,
and according to Theorem \ref{thm:necessary}, we obtain $\lim_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \mathbb P[\widehat{S}_p \neq S_p] = 1$, for all dependence structures in the URS class.
\end{proof}

\begin{remark}
Theorem \ref{thm:necessary} is a stronger result than the traditional minimax claim in Relation \eqref{eq:point-wise-minimax-below}.
Indeed,  \eqref{eq:classification-impossible-dependent} involves an infimum (over the class $\Theta^-_p$) while \eqref{eq:point-wise-minimax-below} has a supremum (over the class $\Theta^+_p$).

On the other hand, Corollary \ref{cor:point-wise-minimax} is more informative than many minimax-type statements, since it applies ``point-wise'' to any fixed error dependence structure in the URS class.
\end{remark}

\begin{remark}
Corollary \ref{cor:point-wise-minimax} echoes Remark \ref{rmk:dependence-assumptions}: for a very large class of dependence structures, we cannot improve upon Bonferroni's procedure in exact support recovery problems (asymptotically), unless we look beyond thresholding procedures.
% There is a limited amount of literature on non-thresholding procedures that utilize the error dependence structures to improve power.
% A notable effort was made by \citet{jin2014optimality}, where the performance (in terms of Hamming loss) of a so-called graphlet screening procedure was studied. 
\end{remark}

% This is an enhancement (in the asymptotic sense) of the minimax results in Section 4.1 of \cite{butucea2018variable}, where the supremum was taken over the dependence structures.

\subsection{Bayes optimality in support recovery problems}
\label{subsec:Bayes-optimality}

In studying support recovery problems (e.g., \citet{arias2017distribution}), restrictions to the thresholding procedures are sometimes justified by arguing that such procedures are the ``reasonable'' choice for estimating the support set.
%  In Theorem \ref{thm:sufficient} we saw that a (FWER-controlling) thresholding procedure is indeed consistent for support recovery. 
% It is natural to ask if it will be sufficient to restrict our attention to only such procedures.
We show in this section that, perhaps surprisingly, for general error models, thresholding procedures are not always optimal, even when the observations are independent.

We shall identify the optimal procedure for support recovery problems under a Bayesian setting with general distributional assumptions (including but not limited to additive models \eqref{eq:model-additive}).
Specifically, we assume that there is an ordered set $P = (i_1,\ldots,i_s)$, $i_i\in\{1,\ldots,p\}$, and $s$ (not necessarily equal) densities $f_{1}, \ldots, f_{s}$, such that the observations indexed by $P$ have corresponding densities. That is,
\begin{equation} \label{eq:signal-distributions-ordered}
x(i_j) \sim f_j, \quad j=1,\ldots,s.
\end{equation}
Let also the rest $(p-s)$ observations have common density $f_0$, i.e., $x(i)\sim f_0$ for $i\not\in S$.
We further assume that the observations $x$ are mutually independent.

We adopt here a Bayesian framework to measure statistical risks. 
Let the ordered support $P=(i_1,\ldots,i_s)$ have prior
\begin{equation} \label{eq:uniform-ordered}
\pi((i_1,\ldots, i_s)) = {(p-s)!}/{p!},
\end{equation}
for all distinct $1\le i_1, \ldots, i_s\le p$.
Consequently, the unordered support $S=\{i_1,\ldots,i_s\}$ is distributed uniformly in the collection of all set of size $s$, with the unordered uniform distribution $\pi^{\text{u}}$. That is, for all for all $S\in\mathcal{S}:=\left\{S\subseteq\{1,\ldots,p\};|S|=s\right\}$, we have 
\begin{equation} \label{eq:uniform}
\pi^{\text{u}}
(\{i_1,\ldots, i_s\}) = \sum_{\sigma}\pi((i_{\sigma(1)},\ldots, i_{\sigma(s)})) = {(p-s)!s!}/{p!},
\end{equation}
where the sum is taken over all permuations of $\{1,2,\ldots,s\}$.

For any fixed configuration $P$, consider the loss function,
$$
\ell(\widehat{S},S) := \P[\widehat{S} \neq S] = \P_{P}[\widehat{S} \neq S],
$$
where the probability is taken over the randomness in the observations only.
The Bayes optimal procedures should minimize 
\begin{equation} \label{eq:Bayes-risk}
    \E_\pi \P[\widehat{S} \neq S],
\end{equation}
where the expectation is taken over the random configurations $P$, with a uniform distribution $\pi$ as specified in \eqref{eq:uniform-ordered}.

% For a sequence of estimators $\widehat{S} = \widehat{S}_p$, the asymptotically optimal procedures are defined to be the ones that minimize the asymptotic Bayes risk,
% \begin{equation} \label{eq:Bayes-risk}
%     R(\widehat{S}) := \limsup_{p\to\infty} \E_{P,{\cal E}} [\ell(\widehat{S},S)] = \limsup_{p\to\infty} \P_{P,{\cal E}}[\widehat{S} \neq S].
% \end{equation}

If, however, the sparsity $s = |S|$ of the problem is known, then a natural estimator for $S$ would be based on the set of top $s$ order statistics.
\begin{definition}[Oracle data thresholding]
We call $\widehat{S}^* = \{i\,|\, x(i)\ge x_{[s]}\}$ the oracle data thresholding procedure, where $x_{[1]} \ge \ldots \ge x_{[p]}$ are the order statistics of $x$.
\end{definition}

The finite-sample optimality of the oracle thresholding procedure $\widehat{S}^*$ is intimately linked with the \emph{monotone likelihood ratio} (MLR) property.
\begin{definition}[Monotone Likelihood Ratio]
A family of positive densities on $\R$, $\{f_\delta, \delta \in U\}$, is said to have the MLR property if, for all $\delta_0, \delta_1\in U\subseteq\R$ such that $\delta_0 < \delta_1$, the likelihood ratio $\left(f_{\delta_1}(x)/f_{\delta_0}(x)\right)$ is an increasing function of $x$.
\end{definition}

Their relationship is summarized in the following lemma.

\begin{proposition} \label{prop:optimal-oracle-procedures}
Let the observations $x(i)$, $i=1,\ldots,p$ be as prescribed as in \eqref{eq:signal-distributions-ordered} through \eqref{eq:uniform-ordered}.
If each of $\{f_0, f_{1}\},\ldots,\{f_0,f_{s}\}$ form an MLR family, then the oracle data thresholding procedure $\widehat{S}^* = \{i\,|\, x(i)\ge x_{[s]}\}$ is finite-sample optimal in terms of Bayes risk $\E_\pi \P[\widehat{S} \neq S]$. That is,
\begin{equation} \label{eq:finite-sample-Bayes-optimal}
    \widehat{S}^* \in \argmin_{\widehat{S}} \E_\pi \P[\widehat{S} \neq S].
\end{equation}
for all $s$ and $p$.
\end{proposition}

The proof of Proposition \ref{prop:optimal-oracle-procedures} is found in Section \ref{suppsec:proofs}.

We emphasize that the oracle thresholding procedures are in fact \emph{finite-sample optimal} in the above Bayesian context.
Further, our setup allows for different alternative distributions, and relaxes the assumptions of \citet{butucea2018variable} when studying distributional generalizations, where the alternatives are assumed to be identically distributed.

It remains to understand when the key MLR property holds. 
We elaborate on this question next.

\subsection{Bayes optimality under sub-exponential errors}
\label{subsec:optimal-procedure-sub-exponential}

Returning to the more concrete signal-plus-noise model \eqref{eq:model-additive}, it turns out that the error tail behavior is what determines the optimality of data thresholding procedures.
In this setting, log-concavity of the error densities is \emph{equivalent} to the MLR property (Lemma \ref{lemma:MLR-log-concavity}). This, in turn, yields the finite-sample optimality of data thresholding procedures (Proposition \ref{prop:log-concave}).

\begin{lemma} \label{lemma:MLR-log-concavity}
Let $\delta$ be the magnitude of the non-zero signals in the signal-plus-noise model \eqref{eq:model-additive} with positive error density $f_0$, and let $f_\delta(x) = f_0(x-\delta)$.
The family $\{f_\delta, \delta \in \R\}$ has the MLR property if and only if the error density $f_0$ is log-concave.
\end{lemma}

\begin{proof}[Proof of Lemma \ref{lemma:MLR-log-concavity}]
Suppose MLR holds, we will show that $f_0(t) = \exp\{\phi(t)\}$ for some concave function $\phi$.
By the assumption of MLR, for any $x_1 < x_2$, setting $\delta_0 = 0$, and $\delta_1 = (x_2 - x_1)/2 > 0$, we have
\begin{equation*}
    \log{\frac{f_{\delta_1}(x_2)}{f_{\delta_0}(x_2)}}
    = \phi\left(\frac{(x_1+x_2)}{2}\right)- \phi(x_2) 
    \ge \phi(x_1)- \phi\left(\frac{(x_1+x_2)}{2}\right) 
    = \log{\frac{f_{\delta_1}(x_1)}{f_{\delta_0}(x_1)}}.
\end{equation*}
This implies that the log-density $\phi(t)$ is midpoint-concave, i.e., for all $x_1$ and $x_2$, we have,
\begin{equation}
    \phi\left(\frac{(x_1+x_2)}{2}\right) 
    \ge \frac{1}{2} \phi(x_1) + \frac{1}{2} \phi(x_2).
\end{equation}
For Lebesgue measurable functions, midpoint concavity is equivalent to concavity by the Sierpinki Theorem (see, e.g., Sec I.3 of \cite{donoghue2014distributions}). This proves the `only-if' part.

For the `if' part, when  $\phi(t) = \log{(f_0(t))}$ is log-concave, then for any $\delta_0 < \delta_1$, and any $x<y$, we have
\begin{equation} \label{eq:concavity-implies-MLR}
    \log{\frac{f_{\delta_1}(y)}{f_{\delta_0}(y)}} - \log{\frac{f_{\delta_1}(x)}{f_{\delta_0}(x)}}
    = \phi(y-\delta_1) - \phi(y-\delta_0) - \phi(x-\delta_1) + \phi(x-\delta_0) \ge 0,
\end{equation}
where the last inequality is a simple consequence of concavity (see Lemma \ref{lemma:four-point-concavity}). This proves the `if' part.
\end{proof}

Proposition \ref{prop:optimal-oracle-procedures} and Lemma \ref{lemma:MLR-log-concavity} yield immediately the following.

\begin{proposition} \label{prop:log-concave}
Consider the additive error model \eqref{eq:model-additive}.
Let the errors $\epsilon$ be independent with common distribution $F$.
Let the signal $\mu$ have $s$ positive entries with magnitudes $0<\delta_1\le\ldots\le\delta_s$, located on $\{1,\ldots,p\}$ as prescribed in \eqref{eq:uniform-ordered}.
If $F$ has a positive, log-concave density $f$, then the oracle thresholding procedure $\widehat{S}^* = \{i\,;\,x(i)\ge x_{[s]}\}$ is finite-sample optimal in terms of Bayes risk in the sense of \eqref{eq:finite-sample-Bayes-optimal}.
\end{proposition} 
Notice that under MLR (or equivalently, log-concavity of the errors in additive models), the oracle thresholding procedure is finite-sample optimal even in the case where the signals have different (positive) sizes.

The assumption of log-concavity of the densities is compatible with the AGG model when $\nu\ge1$, as demonstrated in the next example.

\begin{example} \label{exmp:AGG-logconcave}
The generalized Gaussian density $f(x)\propto \exp\{-|x|^\nu/\nu\}$ is log-concave for all $\nu\ge1$.
Therefore in the additive error model \eqref{eq:model-additive}, according to Proposition \ref{prop:log-concave}, the oracle thresholding procedure is Bayes optimal in the sense of \eqref{eq:finite-sample-Bayes-optimal}.
\end{example}

%(This also explains the $\gamma\ge 1$ condition in Theorem 1 of Arias-Castro and Chen)

Consider the asymptotic Bayes risk as defined in \eqref{eq:Bayes-risk}, the statement for the necessary condition of support recovery, with the help of Proposition \ref{prop:log-concave}, can be strengthened to include all procedures (in the Bayesian context), regardless of whether they are thresholding.

\begin{theorem} \label{thm:necessary-strengthened}
Consider the additive model \eqref{eq:model-additive} where the $\epsilon_p(i)$'s are independent and identically distributed with log-concave densities in the AGG class. 
Let the signals be as prescribed in Proposition \ref{prop:log-concave}.
If the signal sizes fall below the strong classification boundary \eqref{eq:strong-classification-boundary}, i.e. $\overline{r}<g(\beta)$,
then we have
\begin{equation} \label{eq:classification-impossible-Bayes}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi \P[\widehat{S}_p\neq S_p] = 1,
\end{equation}
where the infimum on $\widehat{S}_p$ is taken over all procedures.
\end{theorem}

\begin{proof}[Proof of Theorem \ref{thm:necessary-strengthened}]
When errors are independent with log-concave density, the oracle thresholding procedure $\widehat{S}^*_p$, by Proposition \ref{prop:log-concave}, minimizes the Bayes risk \eqref{eq:Bayes-risk} among \emph{all} procedures. That is,
$$
\liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi\P[\widehat{S}_p\neq S_p]
\ge \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p].
$$
Since $\widehat{S}^*_p$ belongs to the class of all thresholding procedures, we have
\begin{align*}
    \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p] 
    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \E_\pi\P[\widehat{S}_p\neq S_p] \\
    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \inf_{S_p} \P[\widehat{S}_p\neq S_p] = 1,
\end{align*}
when $\overline{r}<g(\beta)$, where the last line follows from Theorem \ref{thm:necessary}.
\end{proof}

% \begin{remark}
% In view of Theorem \ref{thm:necessary-strengthened}, Bonferroni's thresholding procedure $\widehat{S}_p^{\text{Bonf}}$ described in Theorem \ref{thm:sufficient} is an asymptotically minimax procedure over the class of error models $U(F)$.
% That is, in the class of errors with AGG($\nu$) marginals $F$ where $\nu\ge1$, we have
% \begin{equation} \label{eq:minimax}
%     \widehat{S}_p^{\text{Bonf}} \in \argmin_{\widehat{S}_p} \sup_{{\cal E}\in U(F)} R(\widehat{S}_p),
% \end{equation}
% where the minimum is taken over \emph{all} procedures $\widehat{S}$.
% It can be shown that the supremum in the Bayes risk formulation \eqref{eq:minimax}, where $S$ is random and uniformly distributed, can be replaced by a supremum over all possible (deterministic) configurations of support sets.
% This can be done by applying Theorem 1.1 in the supplement of \citep{butucea2018variable}.
% We content ourselves with a Bayesian minimax result here.
% \end{remark}

\subsection{Minimax optimality over all procedures}
\label{subsec:minimax-over-dependence}

% In the previous section we demonstrated the minimax optimality of thresholding procedures, in a point-wise sense over a large class of dependence structure.
Theorem \ref{thm:necessary-strengthened} allows us to state another minimax conclusion --- one in which we search over \emph{all procedures}, by allowing the supremum in the minimax statement to be taken over the dependence structures.

\begin{corollary}
\label{cor:minimax-over-dependence}
Let $D(F)$ be the collection of error arrays with common marginal $F$ as defined in \eqref{eq:common-marginal-distribution} where $F$ is an $\text{AGG}(\nu)$ distribution.
Let also $\widehat{S}^{\text{Bonf}}_p$ be Bonferroni's procedure as described in Theorem \ref{thm:sufficient}.
If $\underline{r}>g(\beta)$, then we have
\begin{equation} \label{eq:minimax-over-dependence-over}
    \limsup_{p\to\infty} \sup_{\substack{\mu\in\Theta_p^+(\beta,\underline{r})\\ {\cal E}\in D(F)}} \P(\widehat{S}^{\text{Bonf}}_p \neq S_p) = 0.
\end{equation}
Further, when $\underline{r}<g(\beta)$, and $F$ has a positive log-concave density $f$, we have
\begin{equation} \label{eq:minimax-over-dependence-under}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \sup_{\substack{\mu\in\Theta_p^+(\beta,\underline{r})\\ {\cal E}\in D(F)}} \P(\widehat{S}_p \neq S_p) = 
    1,
\end{equation}
where the infimum on $\widehat{S}_p$ is taken over all procedures.
\end{corollary}

\begin{remark}
Since the class $\text{AGG}(\nu)$, $\nu\ge1$ contains distributions with log-concave densities (Example \ref{exmp:AGG-logconcave}), the minimax statement \eqref{eq:minimax-over-dependence-under} continues to hold if the supremum is taken over the entire class $F\in\text{AGG}(\nu)$, $\nu\ge1$.
We opted for a more informative formulation which emphasizes the log-concavity condition on the density of $F$.
\end{remark}

\begin{remark}
Corollary \ref{cor:minimax-over-dependence} is no stronger than Corollary \ref{cor:point-wise-minimax}. 
In Corollary \ref{cor:point-wise-minimax} we search over only the class of thresholding procedures, but offer a tight, point-wise lower bound on the asymptotic risk over the class of URS dependence structures.
On the other hand, Corollary \ref{cor:minimax-over-dependence} provides a uniform lower bound for the asymptotic risk over all dependence structures, which may not be tight except in the case of independent errors.
% , and when the errors have nice, log-concave densities.
\end{remark}

\begin{proof}[Proof of Corollary \ref{cor:minimax-over-dependence}]
Relation \eqref{eq:minimax-over-dependence-over} is a re-statement of Remark \ref{rmk:sufficient-strengthened}.

For any distribution $\pi$ (with a slight abuse of notation) over the parameter space $\Theta_p^+\times D(F)$, we have
\begin{equation} \label{eq:minimax-over-dependence-under-proof}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \sup_{\substack{\mu\in\Theta_p^+(\beta, \underline{r})\\ {\cal E}\in D(F)}} \P(\widehat{S}_p \neq S_p) 
\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_{\pi} \P(\widehat{S}_p \neq S_p),
\end{equation}
since the supremum is bounded from below by expectations.
In particular, define $\pi$ to be the uniform distribution over the configurations $\Theta_p^*\times I(f)$, where
\begin{align*}
    \Theta_p^* &=
    \{\mu\in\mathbb{R}^d:\;|S_p|=\lfloor p^{1-\beta}\rfloor,\;\mu(i)=0\;\text{for all }i\not\in S, \;\text{and}\\
    &\quad\quad\mu(i) = (\nu{r}\log{p})^{1/\nu}\;\text{for all }i\in S,\;\text{where}\;\underline{r}<r<g(\beta)\},
\end{align*}
and 
% \begin{align*}
%     I(f)&=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\;\text{are independently and identically distributed}\\
%     &\quad\quad\text{with density}\; f(x)\propto \exp\{-|x|^\nu/\nu\}\}.
% \end{align*}
\begin{equation*}
    I(f)=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\;\text{\ac{iid} with density}\; f(x)\propto \exp\{-|x|^\nu/\nu\}\}.
\end{equation*}

Since the density $f$ of $F$ is log-concave, the distribution of the signal configurations satisfies the conditions in Theorem \ref{thm:necessary-strengthened}.
Thus, the desired conclusion \eqref{eq:minimax-over-dependence-under} follows from Theorem \ref{thm:necessary-strengthened} and \eqref{eq:minimax-over-dependence-under-proof}.
\end{proof}

\subsection{Bayes optimality of likelihood ratio thresholding}
\label{subsec:optimal-procedure-super-exponential}

The following result provides the general form of finite-sample Bayes optimal procedures.
It turns out that in general, \emph{likelihood ratio thresholding} is optimal.

\begin{proposition} \label{prop:likelihood-ratio-thresholding}
Let the observations $x(i)$, $i=1,\ldots,p$ have $s$ signals as prescribed in \eqref{eq:uniform-ordered} having common density $f_a$, and let the rest $(p-s)$ locations have common density $f_0$.
Define the likelihood ratios 
$$
L(i) := {f_a(x(i))}\big/{f_0(x(i))},
$$
and let $L_{[1]} \ge L_{[2]} \ge \ldots \ge L_{[p]}$ be the order statistics of the $L(i)$'s.
Then the procedure $\widehat{S}_{\text{opt}} = \{i\,|\,L(i) \ge L_{[s]}\}$ is finite-sample optimal in terms of Bayes risk. That is,
\begin{equation}
    \widehat{S}_{\text{opt}} \in \argmin_{\widehat{S}} \E_\pi \P[\widehat{S} \neq S].
\end{equation}
for all $s$ and $p$, where the infimum on $\widehat{S}_p$ is taken over all procedures.
\end{proposition}

The proof of Proposition \ref{prop:likelihood-ratio-thresholding} is found  in Section \ref{suppsec:proofs}.

% \begin{remark}
% While the assumption that the alternatives have a common density $f_a$ is slightly more restrictive than in Proposition \ref{prop:optimal-oracle-procedures}, it is not excessively so if one considers a fully Bayesian alternative, where $f_a = p_1f_1 + p_2f_2 + \ldots + p_sf_s$ is a random mixture of alternatives $f_1,\ldots,f_s$ with probability weights $p_1,\ldots,p_s$.
% \end{remark}

The characterization of optimal likelihood ratio thresholding procedures in Proposition \ref{prop:likelihood-ratio-thresholding} may not always yield practical estimators, as the density of alternatives, and number of signals are typically unknown.
Still, some insights can be gained by virtue of Proposition \ref{prop:likelihood-ratio-thresholding}.
In particular, when MLR fails (or equivalently, when the errors in model \eqref{eq:model-additive} do not have log-concave densities), data thresholding is sub-optimal.

\begin{example}[Sub-optimality of data thresholding] \label{exmp:suboptimal-data-thresholding}
Let the errors have iid generalized Gaussian density with $\nu=1/2$, i.e., $\log{f_0(x)}\propto -x^{1/2}$. 
Let dimension $p=2$, sparsity $s=1$ with uniform prior, and signal size $\delta=1$.
That is, $\mathbb P[\mu = (0,1)^\mathrm{T}] = \mathbb P[\mu = (1,0)^\mathrm{T}] = 1/2$.
If the observations take on values $x = (x_1, x_2)^\mathrm{T} = (1,2)^\mathrm{T}$, we see from a comparison of the likelihoods (and hence, the posteriors),
$$
\log \frac{f(x|\{1\})}{f(x|\{2\})} = 2x_1^{1/2} + 2(x_2 - 1)^{1/2} - 2x_2^{1/2} - 2(x_1 - 1)^{1/2} = 4 - 2\sqrt{2} > 0,
$$
that even though $x_1<x_2$, the set $\{1\}$ is a better estimate of support than $\{2\}$, i.e., $\mathbb P[S=\{1\}\,\big|\,x] > \mathbb P[S=\{2\}\,\big|\,x]$.
\end{example}

This simple example shows that, in the case when the errors have super-exponential tails, the optimal procedures are in general \emph{not} data thresholding.
A slightly more general conclusion can be found in Corollary \ref{cor:log-convex}.

\begin{remark} \label{rmk:tail-assumptions}
Consider the model \eqref{eq:model-additive} with independent errors, Proposition \ref{prop:likelihood-ratio-thresholding}, and indeed, Example \ref{exmp:suboptimal-data-thresholding} demonstrate that thresholding procedures are in fact \emph{sub-optimal} for $\text{AGG}(\nu)$ models with $\nu<1$.
Therefore, the optimality of thresholding procedures (specifically, Bonferroni's procedure) only applies to $\text{AGG}(\nu)$ models with $\nu\ge1$. 
% This suggests that the condition $\nu\ge1$ in Corollary \ref{cor:minimax-over-dependence} is tight.

If we restrict the space of methods to only thresholding procedures, then results in Section \ref{subsec:point-wise-minimax} state that the phase transition phenomenon --- the 0-1 law in the sense of Corollary \ref{cor:point-wise-minimax} --- is universal in all error models with rapidly varying tails.
This includes $\text{AGG}(\nu)$ models {\it for all} $\nu>0$.
In contrast, models with heavy (regularly varying) tailed errors do not exhibit this phenomenon (see Theorem \ref{thm:heavy-tails}).
We summarize the properties of thresholding procedures in Table \ref{table:role-of-thresholding}. 
\end{remark}

\begin{table}[ht]
    \centering
    \caption{Properties of thresholding procedures under different error distributions when errors are independent. Properties of the error distributions are listed in brackets.}
    \medskip
    \begin{tabular}{p{45mm}p{40mm}p{40mm}} \toprule
        Thresholding procedure & Bayes optimality &  Phase transition \\ 
        (Error distributions) &  (Log-concave density) & (Rapidly-varying tails) \\ \midrule
        AGG($\nu$), $\nu\ge1$ & Yes (Yes) & Yes (Yes) \\ \cmidrule{1-3}
        AGG($\nu$), $0<\nu<1$ & No (No) & Yes (Yes) \\ \cmidrule{1-3}
        Power laws & No (No) & No (No) \\ \bottomrule
    \end{tabular}
    \label{table:role-of-thresholding}
\end{table}

% It should be remarked that Corollary \ref{cor:log-convex} assumes the existence and knowledge of a maximum signal size $\delta_s$. 
% When maximum signal sizes are unknown a priori, a large observation may be attributed to either a truly large signal, or to the error.
% Common practice has been to attribute large observations to signals, and not errors.

% As an example, consider the linear regression
% \begin{equation} \label{eq:regression}
%  Y = X\mu + \xi,
% \end{equation}
% where $\mu$ is a vector of regression coefficients of interest to be inferred from observations of $X$ and $Y$.
% If the design matrix $X$ is of full column rank, then the OLS estimator of $\mu$ can be formed 
% \begin{equation*}
%     \widehat{\mu} = \left(X'X\right)^{-1}X'Y = \mu + \epsilon,
% \end{equation*}
% where $\epsilon := (X'X)^{-1}X'\xi$.
% Hence we recover the generic problem \eqref{eq:model}. 
% The support recovery problem is therefore equivalent to the fundamental model selection problem.
% Often an investigator calculates the t-scores of each coefficient as 
% \begin{equation} \label{eq:linear-model-selection}
%     \widehat{\mu}(i) \Big/ \widehat{\mathrm{s.e.}}(\widehat{\mu}(i)),
% \end{equation}
% where $\widehat{\mathrm{s.e.}}(\widehat{\mu}(i))$ is the estimated standard error of $\widehat{\mu}(i)$.
% The investigator then chooses indices with large t-scores to enter the model.
% If the errors in model \eqref{eq:regression} are iid Gaussian, the expression \eqref{eq:linear-model-selection} is t-distributed and have power-law tails; the discussion above suggests that this commonplace procedure may be sub-optimal for bounded signals.

### 2020-08-17 4.exact_support_recovery/4.numerical.tex
add draft converted from thesis

We examine numerically the boundaries \eqref{eq:strong-classification-boundary} under several error tail assumptions for independence errors in this section.
Numerical experiments for dependent errors will be deferred until we characterize the \ac{URS} conditions in Chapter \ref{chap:URS}.

To demonstrate the phase transition phenomenon under different error tail densities, we simulate from the additive error model \eqref{eq:model-additive} with
\begin{itemize}
    \item Gaussian errors, where the density is given by
    $f(x) = \frac{1}{\sqrt{2\pi}}\exp{\left\{-x^2/2\right\}}$.
    \item Laplace errors, where the density is given by $f(x) = \frac{1}{2}\exp{\left\{-\left|x\right|\right\}}$.
    \item Generalized Gaussian $\nu=1/2$, with density
    $f(x) = \frac{1}{2}\exp{\big\{-2\left|x\right|^{1/2}\big\}}$.
\end{itemize}
The sparsity and signal size of the sparse mean vector are parametrized as in equations \eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized}, respectively.
The support set $S$ is estimated with 
$\widetilde{S} = \left\{i:x(i)>\sqrt{2\log{p}}\right\}$ 
under the Gaussian errors, 
$\widetilde{S} = \left\{i:x(i)>\log{p} + (\log{\log{p}})/2\right\}$ 
under the Laplace errors, and with
$\widetilde{S} = \{i:x(i)> \frac{1}{4}\left(W\left(-c/(ep\log{p})\right) + 1\right)^2\}$
under the generalized Gaussian ($\nu = 1/2$) errors. Here $W$ is the Lambert W function, i.e., $W=f^{-1}$ where $f(x)=x\exp{(x)}$.
The choices of thresholds correspond to Bonferroni's procedures with FWER decreasing at a rate of $1/\sqrt{\log{p}}$, therefore satisfying the assumptions in Theorem \ref{thm:sufficient}.
Experiments were repeated 1000 times under each sparsity-and-signal-size combination.

The results of the numerical experiments are shown in Figure \ref{fig:phase-simulated}.
The numerical results illustrate that the predicted boundaries are not only accurate in high-dimensions ($p=10000$, right panels of Figure \ref{fig:phase-simulated}), but also practically meaningful even at moderate dimensions ($p=100$, left panels of Figure \ref{fig:phase-simulated}).

\begin{figure}
      \centering
      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_p100.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_p10000.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_Laplace_p100_4.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_Laplace_p10000_4.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_NLC_p100.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_NLC_p10000.eps}
      \caption{The empirical probability of exact support recovery from numerical experiments, as a function of sparsity level $\beta$ and signal sizes $r$, from Gaussian error models (upper panels), Laplace error models (middle panels), and generalized Gaussian with $\nu=1/2$ (lower panels); darker color indicates higher probability of exact support recovery. 
      The experiments were repeated 1000 times for each sparsity-signal size combination, and for dimensions $p=100$ (left panels) and $p=10000$ (right panels). Numerical results agree with the boundaries described in Theorem \ref{thm:sufficient}; convergence is noticeably slower for under generalized Gaussian ($\nu=1/2$) errors.
      For reference, the dashed and dash-dotted lines represent the weak classification and detection boundaries (see Chapter \ref{chap:phase-transitions}).}
      \label{fig:phase-simulated}
\end{figure}

### 2020-08-17 4.exact_support_recovery/4.other-boundaries.tex
add draft converted from thesis

The strong classification boundaries extend beyond the AGG models.
As our analysis in Section \ref{sec:boundary} suggests, all additive error models where the errors have URS maxima demonstrate this phase transition phenomenon under appropriate parametrization of the sparsity and signal sizes.
We derive explicit boundaries for two additional classes of models under the general form of the additive noise models \eqref{eq:model-additive}, with heavier and lighter tails than the AGG models, respectively.

We would like to point out that the sparsity and signal sizes can be re-parametrized for the boundaries to have different shapes.
For example in the case of Gaussian errors, if we re-parametrize sparsity $s$ with 
$\widetilde{\beta} = 2 - \left(1 + \sqrt{1-\beta}\right)^2$ where $\widetilde{\beta}\in(0,1)$, then the signal sparsity would have a slightly more complicated form:
$$
\left|S_p\right| = \left\lfloor p^{1-\beta} \right\rfloor = \left\lfloor p^{\left(\sqrt{2 - \widetilde{\beta}} - 1\right)^2}\right\rfloor,
$$
while the strong classification boundary would take on the simpler form:
\begin{equation}\label{eq:altenative-parametrization}
g(\beta) = \widetilde{g}(\widetilde{\beta}) = 2 - \widetilde{\beta}.
\end{equation}
In the next two classes of models we will adopt parametrizations such that the boundaries are of the form $\widetilde{g}$ in \eqref{eq:altenative-parametrization}.

\subsection{Additive error models with heavier-than-AGG tails}

Distributions such as the log-normal have heavier tails than the AGG model, yet the tails are nevertheless rapidly-varying. 
Therefore, Proposition \ref{prop:rapid-varying-tails} applies, and we expect to see phase-transition-type results when the additive errors have these heavier-than-AGG tails.

\begin{example}[Heavier than AGG] \label{exmp:heavier-than-AGG}
Let $\gamma>1$, $c>0$, and suppose that
\begin{equation} \label{eq:heavier-than-AGG}
    \log{\overline{F}(x)} = - \left(\log x\right)^\gamma \left(c+M(x)\right),
\end{equation}
where $\lim_{x\to\infty} M(x)\log^\gamma{x}= 0$. Then, Relation \eqref{eq:rapid-varying-tails} holds under 
model \eqref{eq:heavier-than-AGG}. Further, if the entries in the array are independent, the 
maxima are relatively stable.

The behavior of the quantiles $u_p$ in this model is as follows. As $p\to\infty,$
\begin{equation*}
    u_p \sim \exp{\left\{\left(c^{-1}\log{p}\right)^{1/\gamma}\right\}}
    \iff c\left(\log{u_p}\right)^{\gamma} + o(1) = \log(p) = - \log \overline{F}(u_p).
\end{equation*}
since $u_p$ diverges, and $M(u_p)$ is $o((\log^\gamma u_p)^{-1})$.
\end{example}

Following Example \ref{exmp:heavier-than-AGG}, assume that the errors in Model \eqref{eq:model-additive} have rapidly varying right tails
\begin{equation} \label{eq:heavier-than-AGG-boundary-1}
    \log{\overline{F}(x)} = - \left(\log x\right)^\gamma \left(c+M(x)\right),
\end{equation}
as $x\to \infty$, and left tails
\begin{equation} \label{eq:heavier-than-AGG-boundary-2}
    \log{{F}(x)} = - \left(\log{(-x)}\right)^\gamma \left(c+M(-x)\right),
\end{equation}
as $x\to -\infty$.

\begin{theorem} \label{thm:heavier-than-AGG}
Suppose the marginals $F$ follows \eqref{eq:heavier-than-AGG-boundary-1} and \eqref{eq:heavier-than-AGG-boundary-2}.
Let
$$
k(\beta) = \log{p} - \left((\log{p})^{1/\gamma} + \log{(1-\beta)}\right)^\gamma,
$$
and let the signal $\mu$ have 
$$|S_p| = \left\lfloor pe^{-k(\beta)} \right\rfloor$$
non-zero entries. Assume the magnitudes of non-zero signal entries are in the range between
$$\underline{\Delta} = \exp{\left\{(\log{p})^{1/\gamma}\right\}}\underline{r}
\quad\text{and}\quad
\overline{\Delta} = \exp{\left\{(\log{p})^{1/\gamma}\right\}}\overline{r}.$$
If $\underline{r} > \widetilde{g}(\beta) = 2 - \beta$, then Bonferroni's procedure $\widehat{S}_p$ (defined in \eqref{eq:Bonferroni-procedure}) with appropriately calibrated FWER $\alpha\to 0$ achieves asymptotic perfect support recovery, under arbitrary dependence of the errors.

On the other hand, when the errors are uniformly relatively stable, if $\overline{r} < \widetilde{g}(\beta) = 2 - \beta$, then no thresholding procedure can achieve asymptotic perfect support recovery with positive probability.
\end{theorem}

\subsection{Additive error models with lighter-than-AGG tails}

Similar to how Proposition \ref{prop:rapid-varying-tails} applies to models with heavier-than-AGG tails, it also to error models with lighter tails than the AGG class.

\begin{example}[Lighter than AGG] \label{exmp:lighter-than-AGG}
With $\nu>0$, and $L(x)$ a slowly varying function, the class of distributions
\begin{equation} \label{eq:lighter-than-AGG}
    \log{\overline{F}(x)} = - \exp{\left\{x^\nu L(x)\right\}},
\end{equation}
is rapidly varying.
The quantiles can be derived explicitly in a subclass of \eqref{eq:lighter-than-AGG} where $L(x)\to 1$, or equivalently, when $\log{|\log{\overline{F}(x)}|}\sim x^\nu$,
\begin{equation*}
    u_p \sim \left(\log \log{p}\right)^{1/\nu}
    \iff \exp{\left\{u_p^\nu\left(1+o(1)\right)\right\}} = \log(p) = - \log \overline{F}(u_p).
\end{equation*}
\end{example}
%The proofs of the rapid variation of the distributions in Examples \ref{exmp:heavier-than-AGG} and \ref{exmp:lighter-than-AGG} are entirely analogous to that of Example \ref{exmp:AGG}, and omitted.

Following Example \ref{exmp:lighter-than-AGG}, assume that errors in Model \eqref{eq:model-additive} has rapidly varying right tails
\begin{equation} \label{eq:lighter-than-AGG-boundary-1}
        \log{\overline{F}(x)} = - \exp{\left\{x^\nu L(x)\right\}},
\end{equation}
where $L(x)$ is a slowly varying function, as $x\to\infty$, and left tails
\begin{equation} \label{eq:lighter-than-AGG-boundary-2}
        \log{\overline{F}(x)} = - \exp{\left\{-x^\nu L(-x)\right\}},
\end{equation}
as $x\to -\infty$.

The phase transition results in multiple testing problems under such tail assumptions is characterizes as follows.

\begin{theorem} \label{thm:lighter-than-AGG}
Suppose marginals $F$ follow \eqref{eq:lighter-than-AGG-boundary-1} and \eqref{eq:lighter-than-AGG-boundary-2}.
Let
$$
k(\beta) = \log{p} - \left(\log(p)\right)^{(1-\beta)^\nu},
$$
and let the signal $\mu$ have 
$$|S_p| = \left\lfloor pe^{-k(\beta)} \right\rfloor$$
non-zero entries. Assume the magnitudes of non-zero signal entries are in the range between
$$\underline{\Delta} = \log{\log{p}}^{1/\nu}\underline{r}
\quad\text{and}\quad
\overline{\Delta} = \log{\log{p}}^{1/\nu}\overline{r}.$$
If $\underline{r} > \widetilde{g}(\beta) = 2 - \beta$, then Bonferroni's procedure $\widehat{S}_p$ (defined in \eqref{eq:Bonferroni-procedure}) with appropriately calibrated FWER $\alpha\to 0$ achieves asymptotic perfect support recovery, under arbitrary dependence of the errors.

On the other hand, when the errors are uniformly relatively stable, if $\overline{r} < \widetilde{g}(\beta) = 2 - \beta$, then no thresholding procedure can achieve asymptotic perfect support recovery with positive probability.
\end{theorem}

### 2020-08-17 4.exact_support_recovery/4.phase_transition_results.tex
add draft converted from thesis

% We present the sufficient conditions for asymptotic exact support recovery in Section \ref{subsec:sufficient}.
% The study of maxima plays a central part in the study of support recovery problems.
% We present the key concepts regarding the behavior of the maxima, and in particular, the concentration of maxima phenomena, in Sections \ref{subsec:RS} and \ref{subsec:URS}. 
% These concepts enable to state a partial converse in Section \ref{subsec:necessary}.

We present the sufficient condition under which exact support recovery \eqref{eq:exact-recovery} can be achieved in Section \ref{subsec:sufficient}.
A very general class of dependence structures characterized by the uniform relative stability concept will be introduced in Section \ref{subsec:URS}, to prepare us for the necessary condition in Section \ref{subsec:necessary}.

Section \ref{subsec:dense-signals} discusses the case in which signals are denser than parametrized in \eqref{eq:sparsity-parametrized}, and Section \ref{suppsec:numerical} illustrates the phase transition phenomena with numerical examples.

\subsection{Sufficient conditions for exact support recovery}
\label{subsec:sufficient}

Following \citet*{butucea2018variable}, we define the parameter space for the signals $\mu$ as
\begin{align} \label{eq:minimax-signal-config-over}
    \Theta_p^+(\beta, \underline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|\le\lfloor p^{1-\beta}\rfloor, \nonumber \\
    &\quad\quad\mu(i)\ge (\nu\underline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\}.
\end{align}
Our first result states that, when $F\in \text{AGG}(\nu)$ with $\nu>0$, regardless of the error dependence structure, (asymptotic) perfect support recovery is achieved by applying Bonferroni's procedure with appropriately calibrated FWER, as long as the minimum signal size $\underline{r}$ is above the strong classification boundary \eqref{eq:strong-classification-boundary}.

\begin{theorem} \label{thm:sufficient}
Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.
Let $\widehat{S}_p$ be the Bonferroni's procedure \eqref{eq:Bonferroni-procedure} with vanishing FWER $\alpha = \alpha(p) \to 0$, such that %\fbox{slower than any polynomial}
$\alpha p^\delta\to \infty$ for every $\delta>0$.
If
\begin{equation} \label{eq:signal-above-boundary}
    \underline{r} > g(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu,
\end{equation}
then we have
\begin{equation} \label{eq:exact-supporot-recovery}
    \lim_{p\to\infty}\sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \neq S_p] = 0.
\end{equation}
\end{theorem}

\begin{corollary}[Classes of procedures attaining the boundary]
\label{cor:FWER-controlling_procedures}  
Relation \eqref{eq:exact-supporot-recovery} holds for any FWER-controlling procedure that is strictly more powerful than Bonferroni's procedure. 
This includes Holm's procedure \citep*{holm1979simple}, and in the case of independent errors, Hochberg's procedure \citep*{hochberg1988sharper}, and the {\v{S}}id{\'a}k procedure \citep*{vsidak1967rectangular}.
\end{corollary}

\begin{example} \label{exmp:FWER-controlling_procedures}
Under Gaussian errors, the particular choice of the thresholding at $t_p = \sqrt{2\log{p}}$ in \eqref{eq:Bonferroni-procedure} corresponds to a Bonferroni's procedure with FWER decreasing at a rate of $(\log{p})^{-1/2}$, and hence Theorem \ref{thm:sufficient} applies. 
By Corollary \ref{cor:FWER-controlling_procedures}, Holm's procedure --- and when the errors are independent, the {\v{S}}id{\'a}k, and Hochberg procedures --- with FWER controlled at $(\log{p})^{-1/2}$ all achieve perfect support recovery provided that $\underline{r}>g(\beta)$.
\end{example}

%Proof of Theorem \ref{thm:sufficient} is found in Section \ref{sec:proofs}, 
The claims in Example \ref{exmp:FWER-controlling_procedures} are verified in Section \ref{suppsec:proofs}.

We now turn to the proof of Theorem \ref{thm:sufficient}.

\begin{proof}[Proof of Theorem \ref{thm:sufficient}]
Throughout the proof, dependence on $p$ will be suppressed to simplify notations when such omissions do not lead to ambiguity.

Under the $\text{AGG}(\nu)$ model, it is easy to see from equation \eqref{eq:AGG-quantiles} that the thresholds in Bonferroni's procedure are 
\begin{equation}\label{e:AGG-threshold}
t_p = F^{\leftarrow}(1 - \alpha/p) = (\nu\log{(p/\alpha)})^{1/\nu}(1+o(1)).
\end{equation}
It is known that Bonferroni's procedure $\widehat{S}_p = \left\{i:x(i)>t_p\right\}$ controls the FWER.  Indeed,
\begin{align} \label{eq:Bonferroni-FWER-control}
    \P\left[\widehat{S} \subseteq S\right] 
        &= 1 - \P\left[\max_{i\in S^c}x(i) > t_p\right] = 1 - \P\left[\max_{i\in S^c}\epsilon(i) > t_p\right]\nonumber \\
      % \ge 1 - \P\left[\max_{i\in\{1,\ldots,p\}}\epsilon(i) > t_p\right] \nonumber \\
        &\ge 1 - \sum_{i=1}^{p}\P\left[\epsilon(i)>t_p\right] \ge 1 - \alpha(p) \to 1,
\end{align}
where we used the union bound in the first inequality. 
Notice that the lower bound \eqref{eq:Bonferroni-FWER-control} is independent of the parameter $\mu$ (as well as the dependence structures), and hence holds uniformly over the parameter space, i.e.,
\begin{equation} \label{eq:exact-supporot-recovery-FWER}
    \lim_{p\to\infty}\inf_{\mu\in\Theta_p^+(\beta, \underline{r})} P[\widehat{S}_p \subseteq S_p] = 1.
\end{equation}

On the other hand, for the probability of no missed detection, we have:
\begin{equation*}
    \P\left[\widehat{S} \supseteq S\right] 
        = \P\left[\min_{i\in S}x(i) > t_p\right]
        = \P\left[\min_{i\in S}x(i) - (\nu\underline{r}\log p)^{1/\nu} > t_p - (\nu\underline{r}\log p)^{1/\nu} \right].
\end{equation*}
Since the signal sizes are no smaller than $(\nu\underline{r}\log p)^{1/\nu}$, we have
\begin{equation*}
    x(i) - \left(\nu\underline{r}\log{p}\right)^{1/\nu} \ge \epsilon(i), \quad \text{for all }i\in S,
\end{equation*}
and hence we obtain
\begin{equation} \label{eq:sufficient-proof-eq1}
    \P\left[\widehat{S} \supseteq S\right] \ge 
    \P\left[\min_{i\in S}\epsilon(i) > (\nu\log{(p/\alpha)})^{1/\nu}(1+o(1)) - (\nu\underline{r}\log p)^{1/\nu} \right],
\end{equation}
where we plugged in the expression for $t_p$ in \eqref{e:AGG-threshold}.
Now, since the minimum signal size is bounded below by $\underline{r} > \left(1 + (1-\beta)^{1/\nu}\right)^\nu$, we have $\underline{r}^{1/\nu}-(1-\beta)^{1/\nu}>1$, and so we can pick a $\delta > 0$ such that 
\begin{equation} \label{eq:choice-of-delta}
    \delta < \left(\underline{r}^{1/\nu} - (1-\beta)^{1/\nu}\right)^\nu - 1.
\end{equation}
Since by assumption, for all $\delta>0$, we have $p^{-\delta} = o\left(\alpha(p)\right)$, there is an
$M=M(\delta)$ such that $p/\alpha(p) < p^{1+\delta}$ for all $p\ge M$. Thus, from \eqref{eq:sufficient-proof-eq1}, we further conclude that for $p\ge M$ we have
\begin{align}
    \P\Big[\widehat{S} \supseteq S\Big]
      &\ge \P\Big[\min_{i\in S}\epsilon(i) > \left((1+\delta)\nu\log{p}\right)^{1/\nu}(1+o(1)) - (\nu\underline{r}\log p)^{1/\nu} \Big] \nonumber \\
      &= \P\Big[\max_{i\in S}\left(-\epsilon(i)\right) < \underbrace{\left(\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}\right)(\nu\log{p})^{1/\nu}(1+o(1))}_{=:\text{A}} \Big] \nonumber \\
      &\ge 1 - \lfloor p^{1-\beta} \rfloor \times \overline{F}_-(\text{A}), \label{eq:sufficient-proof-eq2}
      % &\ge 1 - |S|\times\P\Big[(-\epsilon(1)) \ge \left(\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}\right)(\nu\log{p})^{1/\nu}(1+o(1)) \Big] 
\end{align}
where $\overline{F}_-(x) = \P[-\epsilon(i)>x]$ is the survival function of the $(-\epsilon(i))$'s.
Notice that \eqref{eq:sufficient-proof-eq2} follows from the union bound and the assumption that ${|S_p|}\le{\lfloor p^{1-\beta}\rfloor}$. 
Therefore, the lower bound does not depend on $\mu$ (nor on the error dependence structure), and holds uniformly in the parameter space. In turn, we obtain 
\begin{equation} \label{eq:exact-supporot-recovery-FWNR}
    \inf_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \supseteq S_p] \ge 1 - \lfloor p^{1-\beta} \rfloor \times \overline{F}_-(\text{A}).
\end{equation}

If $\beta=1$, we conclude that the right-hand-side of \eqref{eq:exact-supporot-recovery-FWNR} 
converges to $1$, since $\text{A}\to+\infty$.

Let now $\beta\in (0,1)$ and $u_p^- :=  F_-^{\leftarrow}(1-1/p)$. 
The fact that $p\overline{F}_-(u_p^-) \le 1$, implies
\begin{equation}
    \lfloor p^{1-\beta} \rfloor \times \overline{F}_-(\text{A}) \le 
    \frac{\overline{F}_-\left(\text{B}\times{u_{\lfloor p^{1-\beta}\rfloor}^-}\right)} {\overline{F}_-\left({u_{\lfloor p^{1-\beta}\rfloor}^-}\right)} \label{eq:sufficient-proof-eq3}
    % \P\Big[\frac{\max_{i\in S}(-\epsilon(i))}{u_{|S|}}\frac{u_{|S|}}{u_{\lfloor p^{1-\beta}\rfloor}} < \underbrace{\frac{\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}}{(1-\beta)^{1/\nu}}\left(1+o(1)\right)}_{=:\text{B}}\Big], \label{eq:exact-supporot-recovery-FWNR}
\end{equation}
where $\text{B} := {\text{A}}/{u_{\lfloor p^{1-\beta}\rfloor}^-}$.

Notice that by assumption, the $-\epsilon(i)$'s are also 
AGG$(\nu)$ distributed and by Proposition \ref{prop:quantile}, 
$u_p^{-}:= F_-^{\leftarrow}(1-1/p) \sim (\nu \log(p))^{1/\nu}$,
as $p\to\infty$. Therefore, we have
\begin{equation} \label{eq:sufficient-proof-eq4}
    u_{\lfloor p^{1-\beta}\rfloor}^- \sim \left(\nu(1-\beta)\log{p}\right)^{1/\nu}
\end{equation}
and 
\begin{equation*}
\text{B} = \frac{\text{A}}{u_{\lfloor p^{1-\beta}\rfloor}^-}
= \frac{\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}}{(1-\beta)^{1/\nu}}\left(1+o(1)\right) \to c>1
\end{equation*}
as $p\to\infty$, by our choice of $\delta$ in \eqref{eq:choice-of-delta}.

Finally, since the distribution $F_-$ has \emph{rapidly varying} tails (by Definition \ref{def:rapid-variation} and Example \ref{exmp:AGG}), applying Proposition \ref{prop:rapid-varying-tails}, we conclude that \eqref{eq:sufficient-proof-eq3} vanishes. Consequently, the lower bound on the right-hand-side of \eqref{eq:exact-supporot-recovery-FWNR} converges to 1.
This, combined with \eqref{eq:exact-supporot-recovery-FWER}, entails {$\lim_{p\to\infty} \inf_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p = S_p]= 1$, and hence the desired conclusion \eqref{eq:exact-supporot-recovery}, which completes the proof}.
\end{proof}

The statements in Theorem \ref{thm:sufficient} can be strengthened, to prepare us for a minimax result given in Section \ref{sec:optimality} below.

\begin{remark} \label{rmk:sufficient-strengthened}
In the proof of Theorem \ref{thm:sufficient}, both \eqref{eq:Bonferroni-FWER-control} and \eqref{eq:sufficient-proof-eq2} hold uniformly over all error dependence structures.
Therefore, \eqref{eq:exact-supporot-recovery-FWER} and \eqref{eq:exact-supporot-recovery-FWNR} may be strengthened to yield
\begin{equation} \label{eq:exact-supporot-recovery-strengthened}
    \lim_{p\to\infty}\sup_{\substack{\mu\in\Theta_p^+(\beta, \underline{r})\\ {\cal E}\in D(F)}} P[\widehat{S}_p \neq S_p] = 0,
\end{equation}
for $\underline{r} > g(\beta)$, where $D(F)$ is the collection of all arrays with common marginal $F$, i.e., 
\begin{equation} \label{eq:common-marginal-distribution}
    D(F)=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\sim F\;\text{for all }i=1,\ldots,p, \text{and}\; p=1,2,\ldots\}.
\end{equation}
\end{remark}

\begin{remark}
We emphasize that Theorem \ref{thm:sufficient} holds for errors with \emph{arbitrary} dependence structures. 
Intuitively, this is because the maxima of the errors grow at their fastest in the case of independence. 
Formally, the light-tailed nature of the error distribution allowed us to obtain sharp tail estimates via simple union bounds, valid under arbitrary dependence.
% Formally, this result stems from the fact that maxima of distributions with \emph{rapidly varying tails} (Definition \ref{def:rapid-variation}) can be bounded from above using quantiles of their marginal distribution, under arbitrary dependence.
\end{remark}
% We turn next to the study of maxima and present the tools used in the proof of Theorem \ref{thm:sufficient}.
% Thus, the support recovery problem is hardest under independent errors.
% The relationship between dependence and the behavior of maxima is discussed next in Section \ref{sec:URS}, where we will see that the phase-transition phenomenon is not limited to just the AGG models and independent errors; such phenomenon exists for all error models with rapidly varying tails, and under a surprisingly large class of dependent structures.
% On the other hand, the converse of Theorem \ref{thm:sufficient} will need an (extremely mild) assumption on error dependence structures.

\subsection{Dependence and uniform relative stability}
\label{subsec:URS}

An important ingredient needed for a converse of Theorem \ref{thm:sufficient} is an appropriate characterization of the error dependence structure under which the strong classification boundary \eqref{eq:strong-classification-boundary} is tight.
The notion of \emph{uniform relative stability} turns out to be the key.
% in characterizing such dependence structures when studying the behavior of maxima of dependent light-tailed sequences.

\begin{definition}[Uniform Relative Stability] \label{def:URS}
Under the notations established in Definition \ref{def:RS}, the triangular array ${\cal E}$ is said to have uniform relatively stable (URS) maxima if for \emph{every} sequence of subsets $S_p\subseteq\{1,\ldots,p\}$ such that $|S_p| \to \infty$, we have
\begin{equation} \label{eq:URS-condition}
    \frac{1}{u_{|S_p|}} M_{S_p} := \frac{1}{u_{|S_p|}} \max_{i\in S_p} \epsilon_p(i) \xrightarrow{\P} 1,
\end{equation}
as $p\to\infty$, where $u_q,\ q\in \{1,\ldots,p\}$ is the generalized quantile in \eqref{eq:quantiles}.
The collection of arrays ${\cal E} = \{ \epsilon_p(i) \}$ with URS maxima is 
denoted $U(F)$.
\end{definition}

Uniform relative stability is, as its name suggests, a stronger requirement on dependence than relative stability (recall Definition \ref{def:RS}). 
Proposition \ref{prop:rapid-varying-tails} states that an array with iid components sharing a marginal distribution $F$ with rapidly varying tails (Definition  \ref{def:rapid-variation}) has relatively stable maxima; it is easy to see that URS also follows, by independence of the entries.

\begin{corollary} \label{cor:AGG-is-URS}
An independent array ${\cal E}$ with common marginals $F\in\text{AGG}(\nu)$, $\nu>0$, is URS; in this case, URS holds with $u_{|S_p|} \sim \left(\nu\log{|S_p|}\right)^{1/\nu}$.
\end{corollary}

On the other hand, RS and URS hold under much broader dependence structures than just 
independent errors. 
These conditions are extremely mild and can be shown to hold for many classes of error models.  
In Chapter \ref{chap:URS}, we will focus extensively on the Gaussian case, which is of great interest in applications and is rather challenging. 
We will provide simple necessary and sufficient condition for uniform relative stability in terms of the covariance structures.

The relative stability concepts are important because they characterize the dependence structures under which the maxima of error sequences {\em concentrate} around the quantiles \eqref{eq:quantiles} in the sense of \eqref{eq:RS-condition}.
This concentration of maxima phenomena, in turn, is the key to establishing the necessary conditions of the phase transition results in support recovery problems.

% The importance of the URS dependence class in statistics is seen in the study of support recovery problems, discussed next.

\subsection{Necessary conditions for exact support recovery}
\label{subsec:necessary}

With the preparations from Section \ref{subsec:URS}, we are ready to state the necessary conditions for exact support recovery \eqref{eq:exact-recovery} by thresholding procedures. 
It turns out that the strong classification boundary \eqref{eq:strong-classification-boundary} is tight, under the general dependence structure characterized by URS (Definition \ref{def:URS}).

Formally, we define the parameter space for the signals $\mu$ to be
\begin{align} \label{eq:minimax-signal-config-under}
    \Theta_p^-(\beta, \overline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|=\lfloor p^{1-\beta}\rfloor, \nonumber \\
    &\quad\quad0<\mu(i)\le(\nu\overline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\}.
\end{align}

\begin{theorem} \label{thm:necessary}
    Let ${\cal E}$ be a triangular array with common $\text{AGG}(\nu)$ marginal $F$, $\nu > 0$.
    % Let the signal $\mu$ have $|S_p| = \lfloor p^{(1-\beta)} \rfloor$ non-zero entries where $\beta\in(0,1]$, where the signal sizes $\mu(i)$, $i\in S_p$ are at most $\overline{\Delta} = \left(\nu\overline{r}\log p\right)^{1/\nu}$.
    % and the signals $\mu$ have $s=|S|=\lfloor p^{1-\beta}\rfloor$ be as described in Theorem \ref{thm:sufficient}. 
    Assume further that the errors ${\cal E}$ have uniform relatively stable maxima and minima, i.e., ${\cal E}\in U(F)$, and $(-{\cal E}) = \{-\epsilon_{p}(i)\} \in U(F)$.
    If 
    \begin{equation} \label{eq:signal-below-boundary}
        \overline{r} < g(\beta) = \left(1+(1-\beta)^{1/\nu}\right)^\nu,
    \end{equation}
    then
    \begin{equation} \label{eq:classification-impossible-dependent}
        \lim_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \inf_{\mu\in{\Theta_p^-(\beta, \overline{r})}} \P[\widehat{S}_p \neq S_p] = 1,
    \end{equation}
    where ${\cal T}$ is the class of all thresholding procedures \eqref{eq:thresholding-procedure}.
\end{theorem}

% We comment on some consequences of the theorem, before presenting its proof.
Our first comment is on the signal sizes, and in particular, the gap between the sufficient conditions (Theorem \ref{thm:sufficient}) and the necessary conditions (Theorem \ref{thm:necessary}).

\begin{remark} \label{rmk:gap-between-sufficient-necessary}
The sufficient condition in Theorem \ref{thm:sufficient} requires that \emph{all} signals be larger than the strong classification boundary $g(\beta)$ in order to achieve exact support recovery \eqref{eq:exact-recovery}, while Theorem \ref{thm:necessary} states that exact support recovery fails (in the sense of \eqref{eq:exact-recovery-failure}) when \emph{all} signal sizes are below the boundary --- the two conditions are \emph{not} complements of each other.
This gap between the sufficient and necessary conditions on signal sizes, however, may be difficult to bridge.
Indeed, in general, when signal sizes straddle the boundary $g(\beta)$, either outcome is possible, as we demonstrate in Example \ref{exmp:signals-straddling-the-boundary} below.
\end{remark}

\begin{example}[Signals straddling the boundary]
\label{exmp:signals-straddling-the-boundary}
Let the signal $\mu$ have $|S_p| = \lfloor p^{(1-\beta)} \rfloor$ non-zero entries, composed of two disjoint sets $S_p = S_p^{(1)}\cup S_p^{(2)}$.
Let also the magnitude of the signals be equal within the two sets, i.e., $\mu(i)=\sqrt{2r^{(k)}\log{p}}$ if $i\in S_p^{(k)}$ for some constants $r^{(k)} > 0$ for $k=1,2$.
For simplicity, assume that the errors are iid standard Gaussians.

Consider two scenarios
\begin{enumerate}
    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1+\delta)$ with $|S_p^{(1)}|=|S_p|-1$, $|S_p^{(2)}|=1$, 
    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1-\delta)g(\beta)$ with $|S_p^{(1)}|=\lfloor|S_p|/2\rfloor$, $|S_p^{(2)}|=|S_p| - |S_p^{(1)}|$.
\end{enumerate}
for some constants $0<\delta<1-\beta<1$. 
In both cases, signals in $S_p^{(1)}$ (respectively, $S_p^{(2)}$) are above (respectively, below) the strong classification boundary \eqref{eq:strong-classification-boundary}.
However, in the first scenario, we have $\mathbb{P}[\widehat{S}^{\text{Bonf}}_p=S_p]\to 1$ where $\widehat{S}^{\text{Bonf}}_p$ is the Bonferroni's procedure described in Theorem \ref{thm:sufficient}, 
while in the second scenario, we have $\mathbb{P}[\widehat{S}_p=S_p]\to 0$ for \emph{all} thresholding procedures $\widehat{S}_p$.
\end{example}
The claims in Example \ref{exmp:signals-straddling-the-boundary} are verified in Section \ref{suppsec:proofs}.

Our second comment is on the interplay between thresholding procedures and the dependence class characterized by URS.
\begin{remark} \label{rmk:dependence-assumptions}
Paraphrasing Theorems \ref{thm:sufficient} and \ref{thm:necessary}: 
if we consider only thresholding procedures, then for a very large class of dependence structures, we cannot improve upon the Bonferroni procedure $\widehat{S}_p^{\text{Bonf}}$. 
Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we have
\begin{equation}
    \lim_{p\to\infty} \P[\widehat{S}_p^{\text{Bonf}}\neq S_p]
    = \begin{cases}
    \limsup_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 0, & \text{if}\quad \underline{r} > g(\beta),\\
    \liminf_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 1, & \text{if}\quad \overline{r} < g(\beta)\\
    \end{cases}
\end{equation}
where $\cal T$ is the set of all thresholding procedures \eqref{eq:thresholding-procedure}.

Theorem \ref{thm:necessary} also yields an answer the question raised in \citet{butucea2018variable}.
In particular, the authors of \citep{butucea2018variable} commented that independent error is the  `least favorable model' in the problem of support recovery, and 
conjectured that the support recovery problem may be easier to solve under dependence, similar to how the problem of signal detection is easier under dependent 
errors (see \cite{hall2010innovated}). 
Surprisingly, our results here state that asymptotically, \emph{all} error dependence structures in the large URS class are equally difficult for \emph{thresholding procedures}. Therefore, the phase transition behavior is universal in the class of dependence structures characterized by URS.

To facilitate comparison with results in existing literature, we will formulate explicit minimax statements in Section \ref{sec:optimality}.
\end{remark}

We must emphasize that the restriction to the URS dependence class is \emph{not} an assumption of convenience. 
The condition on dependence characterized by uniform relative stability is, in fact, the weakest of its kind in the literature.
We will characterize the class URS dependence class in Chapter \ref{chap:URS} below.

% \begin{remark}   {\color{blue} Here is an idea -- one could estimate the threshold robustly.  For example,
% suppose that we know that the support set is of size $\le p^{1-\beta_0}$, for some fixed $\beta_0\in(0,1)$.  Assume also (for simplicity) that the
% signals can only be positive.  Then, let
% $$
% T_p := x_{([p^{1-\beta_0}])},
% $$
% be the top $[p^{1-\beta_0}]$-th order statistic of the data.  Then, I believe, but I have not proved it that in the absence of signal
% $T_p/u_p \to 1$ in probability.  This should be easy to verify in the iid case and it is an {\bf open problem} in the general URS case. 
% Therefore, one can take the threshold to be:
% $$ t_p(\delta)  := T_p\times (1+\delta),$$ 
% where $\delta>0$ is something tiny (which can also be made to vanish slowly as $p\to\infty$.

% We know, from our theory that if a threshold estimator is to be able to recover the support, then all the signal entries should be 
% above $T_p$ (since we assume that the sparsity $\beta<\beta_0$).  Thus, it is plausible that in this case, the value of
% $T_p$ is unaffected by the signal and $T_p\sim u_p$ in probability.  Now, the factor $1+\delta$ makes the threshold $t_p$ just large enough for it to
% miss any false positives, and if $\delta>0$ is small, to capture all the signal, as $p\to\infty$.

% This idea can be easily checked with simulations to see how well it does in practice.  It is almost completely non-parametric!!! 
% What do you think?   If it ``works", should we include it? 
% }
% \end{remark}

We conclude with the proof of Theorem \ref{thm:necessary}.

\begin{proof} [Proof of Theorem \ref{thm:necessary}]
To avoid cumbersome double subscript notations, we will sometimes suppress dependence on $p$ of the set sequences $\widehat{S}_p$ and $S_p$ in the proof.

Since the estimator $\widehat{S}_p = \{x(i) \ge t_p(x)\}$ is thresholding, exact support recovery takes place if and only if the threshold separates the signals and null part, i.e.,
\begin{equation*}
    \P[\widehat{S}_p = S_p] 
    = \P\left[\max_{i\in S^c}x(i) < t_p(x) \le \min_{i\in S}x(i)\right]
    \le \P\left[\max_{i\in S^c}x(i) < \min_{i\in S}x(i)\right].
\end{equation*}
Since the right-hand-side does not depend on the procedure $\widehat{S}_p$, we also have
\begin{equation} \label{eq:classification-possible-dependent-proof-1}
    \sup_{\widehat{S}_p\in{\cal T}} \P[\widehat{S}_p = S_p] 
    \le \P\left[\max_{i\in S^c}x(i) < \min_{i\in S}x(i)\right]
    \le \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
\end{equation}
where we used the assumption that the signal sizes are no greater than $\overline{\Delta}$.
Let $S^* = S_p^*$ be a sequence of support sets that maximize the right-hand-side of \eqref{eq:classification-possible-dependent-proof-1}, i.e., let
$$
S_p^* = \argmax_{S\subseteq\{1,\ldots,p\}:|S| = \lfloor p^{1-\beta}\rfloor} \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
$$
where ties can be broken lexicographically if multiple maximizers exist.
Then,
% Since there is only a finite number support set $S$ in $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we can bound \eqref{eq:classification-possible-dependent-proof-1} from above uniformly over $\mathcal{S}$ as well.
% In particular, let 
% $$
% S^* = S^*_p \in \argmax_{S\in{\mathcal{S}}}\P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
% $$
we obtain the following bound which only depends on $\overline{r}$ and the distribution of ${\cal E}$,
\begin{align}
    \sup_{\widehat{S}_p\in{\cal T}} \sup_{\mu\in\Theta^-_p(\beta,\overline{r})} \P[\widehat{S}_p = S_p] 
    % \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right]
    &\le \P\left[{\max_{i\in S^{*c}}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S^*}\epsilon(i)}\right] \nonumber \\
% \end{align}
% \begin{align}
% \P\left[\max_{i\in S^c}x(i) < \min_{i\in S}x(i)\right]  
%   &= \P\left[\frac{\max_{i\in S^c}x(i)}{u_p} < \frac{\min_{i\in S}x(i)}{u_p}\right] \nonumber \\
%   &\le  \P\left[\frac{\max_{i\in S^c}\epsilon(i)}{u_p} < \frac{\min_{i\in S}\overline{\Delta} + \epsilon(i)}{u_p}\right] \nonumber \\
  &= \P\left[ \frac{M_{S^{*c}}}{u_p} < \frac{\overline{\Delta} - m_{S^*}}{u_p} \right], \label{eq:classification-possible-dependent-proof-2}
\end{align}
where $M_{S^{*c}} = \max_{i\in S^{*c}}\epsilon(i)$ and $m_{S^*} = \max_{i\in S^*}\left(-\epsilon(i)\right)$.
Since the error arrays ${\cal E}$ and $(-{\cal E})$ are URS by assumption, using the expression for the AGG quantiles \eqref{eq:AGG-quantiles}, we have
\begin{equation} \label{eq:classification-possible-dependent-proof-3}
    \frac{M_{S^{*c}}}{u_p} = \frac{M_{S^{*c}}}{u_{|S^{*c}|}} \frac{u_{|S^{*c}|}}{u_p} \xrightarrow{\P} 1,
\quad \text{and} \quad
\frac{m_{S^*}}{u_p} = \frac{m_{S^*}}{u_{|S^*|}} \frac{u_{|S^*|}}{u_p} \xrightarrow{\P} (1-\beta)^{1/\nu},
\end{equation}
so that the two random terms in probability \eqref{eq:classification-possible-dependent-proof-2} converge to constants.
Notice that the second relation in \eqref{eq:classification-possible-dependent-proof-3} holds by URS for any $\beta\in(0,1)$; when $\beta=1$, the relation holds since ${u_{|S^*|}}/{u_p}$ vanishes while $\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight.

Since signal sizes are bounded above by $\overline{r} < \left(1 + (1-\beta)^{1/\nu}\right)^{\nu}$, we can write $\overline{r}^{1/\nu} = 1 + (1-\beta)^{1/\nu} - d$ for some $d > 0$. By our parametrization of $\overline{\Delta}$, we have
\begin{equation} \label{eq:classification-possible-dependent-proof-4}
    \frac{\overline{\Delta}}{u_p} = \left(1+(1-\beta)^{1/\nu}-d\right)(1+o(1)).
\end{equation}
Combining \eqref{eq:classification-possible-dependent-proof-3} and \eqref{eq:classification-possible-dependent-proof-4}, we conclude that the right-hand-side of the probability \eqref{eq:classification-possible-dependent-proof-2} converges in probability to a constant strictly less than 1, that is, 
\begin{equation}
    \frac{\overline{\Delta} - m_S}{u_p} \xrightarrow{\P} 1 - d,
\end{equation}
while ${M_{S^{*c}}}/{u_p} \xrightarrow{\P} 1$.
Therefore, the probability in \eqref{eq:classification-possible-dependent-proof-2} must go to 0.
\end{proof}

\subsection{Dense signals}
\label{subsec:dense-signals}

We treat briefly the case of dense signals,
% In the revision of the initial manuscript, the associate editor pointed out the important issue of dense signals, 
where the size of the support set is proportional to the problem dimension, i.e. $s\sim cp$ for some constant $c\in(0,1)$.
We show that in this case, a phase-transition-type result still holds, independently of the value of $c$. 
Analogous to the set-up of Theorems \ref{thm:sufficient} and \ref{thm:necessary}, let
\begin{align} \label{eq:minimax-signal-config-over-dense}
    \Theta_p^{\mathrm{d}+}(c, \underline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|\le\lfloor cp\rfloor, \nonumber \\
    &\quad\quad\mu(i)\ge (\nu\underline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\},
\end{align}
where ``$\mathrm{d}$'' in the notation $\Theta_p^{\mathrm{d}+}$ stands for ``dense''. 
Similarly, define
\begin{align} \label{eq:minimax-signal-config-under-dense}
    \Theta_p^{\mathrm{d}-}(c, \overline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|=\lfloor cp\rfloor, \nonumber \\
    &\quad\quad0<\mu(i)\le (\nu\overline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\}.
\end{align}

\begin{theorem} \label{thm:dense-signals}
Let $c\in(0,1)$ be a fixed constant, and let $\widehat{S} = \widehat{S}^{\text{Bonf}}_p$ denote the Bonferroni's procedure as described in Theorem \ref{thm:sufficient}.
In the context of Theorem \ref{thm:sufficient}, if $\underline{r} > 1$, then we have
\begin{equation} \label{eq:exact-supporot-recovery-dense}
    \lim_{p\to\infty}\sup_{\mu\in\Theta_p^{d+}(c, \underline{r})} \P[\widehat{S}_p \neq S_p] = 0.
\end{equation}
While in the context of Theorem \ref{thm:necessary}, if $\overline{r} < 1$, then
\begin{equation} \label{eq:classification-impossible-dependent-dense}
    \lim_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \inf_{\mu\in{\Theta_p^{d-}(c, \overline{r})}} \P[\widehat{S}_p \neq S_p] = 1,
\end{equation}
where ${\cal T}$ is the class of all thresholding procedures \eqref{eq:thresholding-procedure}.
\end{theorem}

\begin{remark}
Notice that the boundary for the signal size parameter is identically $1$ in this dense regime.
Therefore, if we interpret $\beta = 0$ of the parametrization \eqref{eq:sparsity-parametrized} as $s\sim cp$, where $c\in(0,1)$, then the strong classification boundary \eqref{eq:strong-classification-boundary} may be continuously extended to the left-end point where $g(0)=1$.
\end{remark}

\begin{proof}[Proof of Theorem \ref{thm:dense-signals}]
The proof is entirely analogous to that of Theorems \ref{thm:sufficient} and \ref{thm:necessary}.
Specifically, \eqref{eq:exact-supporot-recovery-dense} follows by replacing $\lfloor p^{1-\beta} \rfloor$ with $\lfloor cp \rfloor$ in Relation \eqref{eq:sufficient-proof-eq2} onward, and replacing \eqref{eq:sufficient-proof-eq4} with
$$
u_s^- \sim (\nu\log{cp})^{1/\nu} \sim (\nu\log{p})^{1/\nu}.
$$
in the proof of Theorem \ref{thm:sufficient}.
Similarly, \eqref{eq:classification-impossible-dependent-dense} follows the proof of Theorem \ref{thm:necessary}. 
Indeed, by using the fact that
$$
\frac{u_{|S^{*c}|}}{u_p} \sim \frac{(\nu\log{(1-c)p})^{1/\nu}}{(\nu\log{p})^{1/\nu}} \to 1
$$
and ${u_{|S^*|}}/{u_p}\to 1$ for all $c\in(0,1)$, we see that Relation \eqref{eq:classification-possible-dependent-proof-3} holds with $\beta=0$, and the rest of Theorem \ref{thm:necessary} applies.
\end{proof}

\subsection{Numerical illustrations for independent errors}
\label{suppsec:numerical}
\input{4.exact_support_recovery/4.numerical.tex}

### 2020-08-17 4.exact_support_recovery/4.proofs-convexity.tex
add draft converted from thesis

\subsection{Proofs of Propositions \ref{prop:optimal-oracle-procedures} and \ref{prop:likelihood-ratio-thresholding}}

\begin{proof}[Proof of Proposition \ref{prop:optimal-oracle-procedures}]
The problem of support recovery can be equivalently stated as a classification problem, where the discrete parameter space is $\mathcal{S} = \{S\subseteq\{1,\ldots,p\}:|S|=s\}$, and the observation $x \in\R^p$ has likelihood $f(x|S)$ indexed by the support set $S$.

By the optimality of the Bayes classifier (see, e.g., \citep{domingos1997optimality}), a set estimator that maximizes the probability of support recovery is such that
$$
\widehat{S} \in \argmax_{S\in \mathcal{S}} f(x|S) \pi(S).
$$
Since we know from \eqref{eq:uniform} that $\pi(S)$ is uniform, the problem in our context reduces to showing that $f(x|\widehat{S}^*) = f(x|\widehat{S})$, where $f(x|S)$ is the conditional distribution of data given the unordered support $S$,
$$
f(x|S) 
= \sum_{P\in\sigma(S)} f(x|P) \pi^{\text{ord}}(P|S) 
= \frac{1}{s!} \left(\sum_{P\in\sigma{(S)}} \prod_{i=1}^s {f_{i}(x(P(i)))}\right) \prod_{k\not\in S}{f_0(x(k))},
$$
where $\sigma(S)$ is the set of all permutations of the indices in the support set $S$.

Suppose $\widehat{S} \neq \widehat{S}^*$, then there must be indices $j \in \widehat{S}$ and $j' \in \widehat{S}^c$ such that $x(j) \le x(j')$.
We exchange the labels of $x(j)$ and $x(j')$, and form a new estimate $\widehat{S}\,' = \big(\widehat{S}\setminus\{j\}\big)\cup\{j'\}$.
Comparing the likelihoods under $\widehat{S}$ and $\widehat{S}\,'$, we have
\begin{align}
    f(x|\widehat{S}) - f(x|\widehat{S}\,') 
    &= \frac{1}{s!} \sum_{P\in\sigma{(\widehat{S})}} \prod_{i=1}^s {f_{i}(x(P(i)))} f_0(x(j'))\prod_{k\not\in \widehat{S}\cup\{j'\}}{f_0(x(k))} - \nonumber \\
    &\quad\quad\quad - \frac{1}{s!} \sum_{P'\in\sigma{(\widehat{S}')}} \prod_{i=1}^s {f_{i}(x(P'(i)))} f_0(x(j)) \prod_{k\not\in \widehat{S}'\cup\{j\}}{f_0(x(k))} \nonumber \\
    &= \frac{1}{s!} \left(\sum_{i=1}^s a_i  \Big(f_i(x(j)) f_0(x(j')) - f_i(x(j')) f_0(x(j))\Big) \right) \prod_{k\not\in \widehat{S}\cup\{j'\}}{f_0(x(k))}, \label{eq:MLR-optimality-proof}
    % = \log{f_\delta(x(j))} + \log{f_0(x(j'))} - \log{f_\delta(x(j'))} - \log{f_0(x(j))} 
\end{align}
where the last equality follows by first summing over all permutations fixing $P(i) = j$ and $P'(i) = j'$, and setting $a_i = \sum_{P\in\sigma{(\widehat{S}\setminus\{j\})}} \prod_{i'\neq i} {f_{i'} (x(P(i')))}$. Notice that the $a_i$'s are non-negative.

Since $x(j) \le x(j')$, and that each of $\{f_0, f_{i}\}$ is an MLR family, we have
$$
\frac{f_i(x(j))}{f_0(x(j))} - \frac{f_i(x(j'))}{f_0(x(j'))} \le 0 \implies f_i(x(j)) f_0(x(j')) - f_i(x(j')) f_0(x(j)) \le 0.
$$
Using Relation \eqref{eq:MLR-optimality-proof}, we conclude that $f(x|\widehat{S}) \le f(x|\widehat{S}\,')$.
This implies that any estimator that is not $\widehat{S}^*$ may be improved, and the optimality follows.
\end{proof}

\begin{lemma} \label{lemma:four-point-concavity}
Let $\phi$ be any concave function on $\R$. For any $x<y\in\R$, and $\delta>0$ we have
$$
\phi(x) + \phi(y+\delta) \le \phi(y) + \phi(x+\delta).
$$
\end{lemma}

\begin{proof}[Proof of Lemma \ref{lemma:four-point-concavity}]
Pick $\lambda = \delta/(y-x+\delta)$, by concavity of $f$ we have
\begin{equation} \label{eq:four-point-concavity-1}
    \lambda \phi(x) + (1-\lambda) \phi(y+\delta) 
    \le \phi(\lambda x + (1-\lambda)(y+\delta)) 
    = \phi(y),
\end{equation}
and
\begin{equation} \label{eq:four-point-concavity-2}
    (1-\lambda) \phi(x) + \lambda \phi(y+\delta)
    \le \phi((1-\lambda) x + \lambda(y+\delta)) 
    = \phi(x+\delta).
\end{equation}
Summing up \eqref{eq:four-point-concavity-1} and \eqref{eq:four-point-concavity-2} and we arrive at the conclusion as desired.
\end{proof}

\begin{proof}[Proof of Proposition \ref{prop:likelihood-ratio-thresholding}]
The proof is entirely analogous to that of Proposition \ref{prop:optimal-oracle-procedures}.
Since we know from \eqref{eq:uniform} that $\pi(S)$ is uniform, the problem reduces to showing that $f(x|\widehat{S}_{\text{opt}}) = f(x|\widehat{S})$, where 
$$
\widehat{S} \in \argmax_{S \in \mathcal{S}} f(x|S) \pi(S).
$$
and
$f(x|S)$ is the conditional distribution of data given the unordered support $S$,
\begin{equation} \label{eq:likelihood-ratio-thresholding-proof}
    f(x|S) = \sum_P f(x|P) \pi^{\text{ord}}(P|S) = \prod_{j\in S} f_a(x(j)) \prod_{j\not\in S}{f_0(x(j))}.
\end{equation}
Suppose $\widehat{S} \neq \widehat{S}_{\text{opt}}$, then there must be indices $j \in \widehat{S}$ and $j' \in \widehat{S}^c$ such that $L(j) \le L(j')$.
If we exchange the labels of $L(j)$ and $L(j')$, that is, we form a new estimate $\widehat{S}\,' = \big(\widehat{S}\setminus\{j\}\big)\cup\{j'\}$,
comparing the log-likelihoods under $\widehat{S}$ and $\widehat{S}\,'$, we have
\begin{equation*}
    \log{f(x|\widehat{S})} - \log{f(x|\widehat{S}\,')} 
    = \log{f_a(x(j))} + \log{f_0(x(j'))} - \log{f_a(x(j'))} - \log{f_0(x(j))}.
\end{equation*}
By the definition of $L(j)$'s, and the order relations, we obtain
\begin{equation*}
    \log{f(x|\widehat{S})} - \log{f(x|\widehat{S}\,')} 
    = \log{L(j)} - \log{L(j')} \le 0
\end{equation*}
This implies that any estimator that is not $\widehat{S}_{\text{opt}}$ may be improved, and the optimality follows.
\end{proof}

\begin{remark}
In the non-log-concave setting, where we know that thresholding procedures are suboptimal, likelihood thresholding procedures are promising, thanks to Proposition \ref{prop:likelihood-ratio-thresholding}. 
However, in the case where signals have difference sizes, likelihood thresholding procedures are undefined;
in such settings, existence of an optimal procedure is an open problem.

Indeed, in the proof of Proposition \ref{prop:likelihood-ratio-thresholding}, identical the signal densities are needed so that the relation \eqref{eq:likelihood-ratio-thresholding-proof} holds.
\end{remark}

\subsection{Sub-optimality of data thresholding procedures}

We provide a slightly more general result on the sub-optimality of data thresholding procedures.

\begin{corollary} \label{cor:log-convex}
Consider the additive error model \eqref{eq:model-additive}.
Let the errors $\epsilon$ be independent with common distribution $F$.
Let each of the $s$ signals be located on $\{1,\ldots,p\}$ uniformly at random with equal magnitude $0<\delta<\infty$.
% , independently with probability $p_1,\ldots,p_s$.
% , {\color{red} so that we have $f_a = p_1f_1 + p_2f_2 + \ldots + p_sf_s$.}
If errors $\epsilon$ are iid with density $f$ log-convex on $[K, +\infty)$, then whenever $j\in\widehat{S}_{\text{opt}}$ for some $x(j) > K+\delta$, we must have $j'\in\widehat{S}_{\text{opt}}$ for all $j'$ such that $K+\delta \le x(j') < x(j)$.
\end{corollary}

Specifically, if there are $m$ observations exceeding $K+\delta_s$, with $m>s$, then the top $m-s$ observations will \emph{not} be included in the optimal estimator $\widehat{S}_{\text{opt}}$.
This shows that, in the case when the errors have super-exponential tails, the optimal procedures are in general \emph{not} data thresholding.

\begin{proof}[Proof of Corollary \ref{cor:log-convex}]
Since the alternative $f_{a}(t) = {f(t-\delta)}$ are log-convex on $[K+\delta, \infty)$, by Relation \eqref{eq:concavity-implies-MLR} in the proof of Lemma \ref{lemma:MLR-log-concavity} and appealing to log-convexity (rather than log-concavity), the likelihood ratio
$$
L(j) := \frac{f_a(x(j))}{f_0(x(j))} %= \sum_{i=1}^s \frac{p_if_{i}(x(j))}{f_0(x(j))},
$$
is decreasing in $x(j)$ on $[K+\delta, \infty)$.
The proof is complete by applying Proposition \ref{prop:likelihood-ratio-thresholding}.
\end{proof}

### 2020-08-17 4.exact_support_recovery/4.proofs-examples.tex
add draft converted from thesis

\subsection{Proof of the claims in Examples \ref{exmp:FWER-controlling_procedures} and \ref{exmp:signals-straddling-the-boundary}}
\label{subsec:proofs-examples}

\begin{proof}[Proof of claims in Example \ref{exmp:FWER-controlling_procedures}]
By the Mill's ratio for the standard Gaussian distribution,
$$
\frac{t_p \P\left[Z>t_p\right]}{\phi(t_p)} \to 1,\quad \text{as}\quad t_p\to\infty,
$$
where $Z\sim \text{N}(0,1)$. 
Using the expression for $t_p = \sqrt{2\log{p}}$, we have
$$
p \;\P\left[Z>t_p\right] \sim \sqrt{2\pi}^{-1}\left(2\log{p}\right)^{-1/2} \to 0,
$$
as desired. The rest of the claims follow from Corollary \ref{cor:FWER-controlling_procedures}.
\end{proof}

\begin{proof}[Proof of claims in Example \ref{exmp:signals-straddling-the-boundary}]
In the first scenario, signal sizes in $S^{(1)}_p$ are by definition above the strong classification boundary \eqref{eq:strong-classification-boundary}.
The signal in $S^{(2)}_p$ has size parameter $1+\delta<2-\beta<(1+\sqrt{1-\beta})^2$, and therefore falls below the boundary.

It remains to show that $\mathbb{P}[\widehat{S}^{\text{Bonf}}_p=S_p]\to 1$.
To do so, we define two new arrays 
$$
{\cal Y}^{(k)} = \{y^{(k)}_p(j),\;j=1,2,\ldots,p\},\quad k\in\{1,2\}_p,
$$
where $y^{(k)}_p(j)=x_p(j)$ if $j\not\in S^{(k)}_p$, and $y^{(k)}_p(j)=\widetilde{\epsilon}_p(j)$ if $j\in S^{(k)}_p$, using an independent error array $\{\widetilde{\epsilon}_p(j),\;j=1,\ldots,p\}$ with iid standard Gaussian elements.
That is, we replace the elements in $S^{(1)}_p$ and $S^{(2)}_p$ with iid standard Gaussian noise.
Notice both arrays ${\cal Y}^{(1)}$ and ${\cal Y}^{(2)}$ satisfy the conditions in Theorem \ref{thm:sufficient} (with sparsity parameter equal to $\beta$ and $1$, respectively). 
Hence, we have
$$
\P[\widehat{S}^{\text{Bonf}}_p\subseteq S_p] 
= \P\left[\max_{j\in S^c}x(j) \le t_p\right]
\le \P\left[\max_{j\in S^c}y^{(1)}(j) \le t_p\right] \to 0,
$$
and 
\begin{align*}
    \P[\widehat{S}^{\text{Bonf}}_p\supseteq S_p]
    = \P\left[\min_{j\in S}x(j) > t_p\right] 
    &\ge 1 - \P\left[\min_{j\in S^{(1)}}x(j) \le t_p\right] - \P\left[\min_{j\in S^{(2)}}x(j) \le t_p\right] \\
    &\ge 1 - \P\left[\min_{j\in S^{(1)}}y^{(2)}_p(j) \le t_p\right] - \P\left[\min_{j\in S^{(2)}}y^{(1)}_p(j) \le t_p\right] 
    \to 1,
\end{align*}
where $t_p$ is the threshold in Bonferroni's procedure. The conclusion follows.
% only need to show $\mathbb{P}[S^{(2)}_p\subseteq\widehat{S}^{\text{Bonf}}_p]\to 1$.

In the second scenario, the signal sizes in $S^{(2)}$ by definition falls below the strong classification boundary \eqref{eq:strong-classification-boundary}.
To see that no thresholding procedure succeeds, we adapt the proof of Theorem \ref{thm:necessary}.
In particular, we obtain
$$
    \P[\widehat{S}_p = S_p] 
    \le \P\left[\max_{j\in S^c}x(j) \le t_p < \min_{j\in S}x(j)\right]
    \le \P\left[\max_{j\in S^c}x(j) < \min_{j\in S^{(2)}}x(j)\right].
$$
By the assumption that signals in $S^{(2)}$ have size parameter $(1-\delta)g(\beta)$, we have
\begin{equation}
\P\left[\max_{j\in S^c}x(j) < \min_{j\in S^{(2)}}x(j)\right]
= \P\left[ \frac{M_{S^{c}}}{u_p} < \frac{\sqrt{2(1-\delta)g(\beta)\log{p}} - m_{S^{(2)}}}{u_p}\right], 
\end{equation}
where $M_{S^{c}} = \max_{j\in S^{c}}\epsilon(j)$ and $m_{S^{(2)}} = \max_{j\in S^{(2)}}\left(-\epsilon(j)\right)$.
The ratio on the left-hand-side of the inequality converges to 1 as in \eqref{eq:classification-possible-dependent-proof-3} in the main text, whereas the term on the right-hand-side
\begin{align*}
    \frac{\sqrt{2(1-\delta)g(\beta)\log{p}} - m_{S^{(2)}}}{u_p} 
    &= \sqrt{(1-\delta)g(\beta)} - \frac{m_{S^{(2)}}}{u_{|S^{(2)}|}} \frac{u_{|S^{(2)}|}}{u_p} \\
    &\xrightarrow{\P} \sqrt{(1-\delta)} + \sqrt{1-\beta}(\sqrt{(1-\delta)} - 1) < 1.
\end{align*}
where we used the URS of the error arrays, and that 
$$
u_{|S^{(2)}|} \sim \sqrt{2\log{(p^{1-\beta}/2)}} 
= \sqrt{2(({1-\beta})\log{p}-\log2)} \sim \sqrt{2({1-\beta})\log{p}}.
$$
to conclude the convergence in probability.
\end{proof}

### 2020-08-17 4.exact_support_recovery/exact_support_recovery.tex
add draft converted from thesis

We focus on exact support recovery problems in this chapter, and generalize the results we obtained in Chapter \ref{chap:phase-transitions} to additive error models with much relaxed distributional and dependence assumptions.

Consider the additive error model \eqref{eq:model-additive} with the triangular array of errors,
\begin{equation} \label{eq:error-array}
    {\cal E} = \left\{ (\epsilon_p(i))_{i=1}^p,\ p=1,2,\dots\right\},
\end{equation}
where the $\epsilon_p(i)$'s have common cumulative distribution function $F(x)=\P[\epsilon_p(i)\le x]$.
In contrast to the assumptions in Chapter \ref{chap:phase-transitions}, we only require the errors to have common marginal distributions, and allow them to have potentially arbitrary dependence.
% We will study the role of dependence in support recovery problems in Section \ref{sec:URS}.

Although our method of analysis applies to all light-tailed error distributions with rapidly varying tails (see Definition \ref{def:rapid-variation}), to be concrete and better convey the main ideas, we will focus on the class of $\mathrm{AGG}(\nu)$ laws (see Definition \ref{def:AGG}).
Extensions of the results to other error models are presented in Section \ref{suppsec:other-boundaries}.

As in Chapter \ref{chap:phase-transitions}, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector $\mu = \left(\mu(i)\right)_{i=1}^p$ where the sparsity, with a few exceptions which will be explicitly stated, is parametrized as
\begin{equation} \label{eq:sparsity-parametrized}
    s = |S_p| = \lfloor p^{1 -\beta} \rfloor, % \quad \text{with } 0 < \beta \le 1 \; \text{(fixed)},
\end{equation}
with $0 < \beta \le 1$ fixed.

We assume that the non-zero entries of $\mu$ are positive and take values in the interval $\left[\underline{\Delta},\overline{\Delta}\right)\subset (0,\infty)$.
That is, $0<\underline{\Delta}\le\mu(i)<\overline{\Delta}\le+\infty$, for all $i\in S_p$.
The lower and upper bound on the signal sizes $\underline{\Delta}$ and $\overline{\Delta}$ are parametrized as
\begin{equation} \label{eq:signal-size-parametrized}
    \underline{\Delta} = \underline{\Delta}(p) = (\nu \underline{r} \log{p})^{1/\nu} \quad \text{and} \quad
    \overline{\Delta} = \overline{\Delta}(p)  = (\nu \overline{r} \log{p})^{1/\nu},
\end{equation}
with parameters $0 < \underline{r} \le \overline{r} \le +\infty$.
Notice that the parametrization now depends on the shape of the assumed error distributions $\mathrm{AGG}(\nu)$ through the parameter $\nu$.

According to Lemma \ref{lemma:risk-exact-recovery-probability}, in order to study the asymptotic behaviors of $\mathrm{risk}^{\mathrm{E}}$, it is sufficient to establish minimal conditions under which the support sets can be consistently estimated, i.e.,
\begin{equation} \label{eq:exact-recovery} 
    \P[\widehat{S}_p = S_p] \longrightarrow 1 \quad \text{as } \; p\to\infty, 
\end{equation}
where $\widehat{S}_p$ is an estimate of the true signal support set $S_p$.

\medskip

Several authors have studied the support recovery problem in terms of the Hamming loss and obtained minimax optimality results (see, e.g., \cite{ji2012ups, genovese2012comparison, jin2014optimality, butucea2018variable}).
% We briefly review the recent work by \cite{butucea2018variable}, whose .
In the special case of Gaussian marginals, \cite{butucea2018variable} showed that the boundary \eqref{eq:strong-classification-boundary-Gaussian} exists in a minimax sense.
That is, when errors are \emph{independent} Gaussians, the Hamming loss cannot be made to vanish if signal sizes fall below the boundary \eqref{eq:strong-classification-boundary-Gaussian} by any procedure. 
Conversely, if signal size falls below, the Hamming loss can be made to vanish with a specific thresholding procedure.

Unfortunately, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and the sharp result does not carry over directly to the study of the probability of support recovery or exact support recovery risk.
More importantly, despite their elegance, these Hamming loss-minimax studies naturally amounts to the analysis of the elementary case of iid data, and is by design blind to non-trivial error-dependence structures.
This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
% This is arguably a consequence of the inherent limitation of the Hamming-loss approach. 
% For practitioners, a minimax statement in the Gaussian case seems to offer little guidance.
% Indeed, in applications, independence is an exception rather than the rule; Gaussianity of the errors may also be unnecessarily restrictive.

So far in the literature, the role of dependence, and that of the distributional assumptions in model \eqref{eq:model-additive} remain largely unexplored.  
This chapter offers advances in both directions, and provides a close-to-complete solution of the exact support recovery problem. (See also, Chapter \ref{chap:URS}.)
We briefly summarize our contributions next.

\medskip

In Section \ref{sec:boundary}, we study exact support recovery in the sense of \eqref{eq:exact-recovery} directly, under general distributional and dependence assumptions. 
In particular, we describe the phase transition phenomena in the dependent AGG model, under the scaling described in \eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized}.
Consider the function
\begin{equation} \label{eq:strong-classification-boundary}
    g(\beta) = g_\nu(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu, \quad \nu>0,
\end{equation}
which we refer to as the {\em strong classification boundary}.
In Theorem \ref{thm:sufficient} we show that, 
% under the general distributional assumptions in Section \ref{subsec:set-up}, 
if the signal sizes are above the boundary (i.e., $\underline{r}> g(\beta)$), the \ac{FWER}-controlling procedures described in Section \ref{sec:statistical-procedures} with appropriately calibrated levels achieve \emph{exact support recovery} as in \eqref{eq:exact-recovery}.

Conversely, we show in Theorem \ref{thm:necessary}, that for a surprisingly large class of dependence structures characterized by the concept of \emph{uniform relative stability} (URS, see Definition \ref{def:URS} below), when the signal size is below the boundary  (i.e., $r<g(\beta)$), no thresholding procedure can achieve the asymptotically perfect support recovery \eqref{eq:exact-recovery}. In fact,
\begin{equation} \label{eq:exact-recovery-failure}
    \mathbb{P}\left[\widehat{S}_p=S_p\right]\longrightarrow 0,\quad \mbox{ as }p\to \infty,
\end{equation}
for all $\widehat{S}_p$ in the form of \eqref{eq:thresholding-procedure}.

These two results show that the thresholding procedures obey a phase transition phenomenon in a strong, \emph{point-wise} sense over the class of URS dependence structures, and over the class of AGG$(\nu),\ \nu>0$ error distributions. 
The conclusions are fundamentally stronger and more informative than the minimax statements in the literature (see, e.g., \cite{butucea2018variable}).
The techniques developed in this here are also entirely different from those in \citet{ji2012ups} or \citet{butucea2018variable}, and transparent characterizations of the dependence conditions under which the phase transition type result holds will be established in the Chapter \ref{chap:URS} later.

% The strong classification boundary $g$ characterizes a phase-transition phenomenon similar to that of the signal detection and approximate support recovery. 
% A preview of this result is presented in Figure \ref{fig:phase}.

% \begin{figure}
%       \centering
%       \includegraphics[width=0.45\textwidth]{./figures/phase_diagram_Gaussian_no_dashed_area.eps}
%       \includegraphics[width=0.45\textwidth]{./figures/phase_diagram_double_exponential.eps}
%       \caption{The phase diagrams of the detection, weak classification, and strong classification boundaries against sparse alternatives under Gaussian (left) and Laplace distributed (right) errors. Here $\beta$ and ${r}$ parametrize the signal sparsity and the lower and upper bounds of the signal sizes, respectively. 
%       The signal detection problem can be answered perfectly (asymptotically) inside the \emph{Detectable} region; false discovery proportion and non-discovery proportion can be made to vanish in the \emph{Weakly classifiable} region. We study in this paper the strong classification boundary, above which the support recovery can be achieved \emph{exactly} in the \emph{Classifiable} region $\{(\beta, {r}):{r}>g(\beta)\}$. 
%       In a large class of dependence structures characterized by URS, when signal sizes fall below the strong classification boundary \eqref{eq:strong-classification-boundary}, i.e. $\{(\beta, {r}):{r}<g(\beta)\}$, no thresholding procedure succeeds in the exact support recovery problem. }
%       \label{fig:phase}
% \end{figure}

\medskip

We show in Section \ref{sec:optimality} that data thresholding procedures are not only asymptotically, but in fact, finite sample optimal when the errors are independent and identically distributed (iid) with log-concave densities. 
In this case, no estimator can achieve perfect support recovery when the signal is below the strong classification boundary \eqref{eq:strong-classification-boundary}.  
Consequently, in the case of $\text{AGG}(\nu)$ errors with $\nu\ge 1$, the strong 
classification boundary is shown to hold in the minimax 
sense for \emph{all} procedures. This is formalized in Theorem \ref{thm:necessary-strengthened} and Corollary \ref{cor:minimax-over-dependence}.

\medskip

The phase transition phenomena for two additional classes of error distributions with either heavier or lighter tails than the AGG distributions will be described in Section \ref{suppsec:other-boundaries}.

\medskip

A final surprising result that had only recently been noticed by the statistical community is that thresholding procedures, including data-dependent ones, are not optimal in general in the support recovery problem when the errors have heavy (regularly-varying) tails. 
\citet{arias2019detection} discussed the phenomena in approximate support recovery problems.
In this case, we also demonstrate the absence of a phase transition phenomenon in exact support recovery by thresholding, in Section \ref{suppsec:heavy-tailed}.

% In this sense, for $\nu\ge 1$ our results are rather complete.  We note here that our focus is not on minimax analysis of the support recovery problem, where a large class of distributional and dependence structures are considered.  
% In some sense, the worst case scenario (see also \cite{butucea2018variable}) is when the errors are independent.  
% In contrast, we establish the phase-transition phenomenon, for fixed but very general dependence conditions characterized by the URS property.

%We show that when the error-distribution $F$ is log-concave, then the thresholding procedures are optimal (for independent errors).  Therefore, in this regime the {\em strong classification boundary} $g$ is universal.  
%That is, if $r<g(\beta)$, no estimator can achieve perfect support recovery as $p\to\infty$. 
% \fbox{maybe skip the next sentence} 
% In fact, going beyond the class of rapidly varying distributions, (e.g., for heavy Pareto-type tails) the support recovery problem is fundamentally different and there may no longer be a phase-transition phenomenon.

\section{Exact support recovery under AGG errors}
\label{sec:boundary}
\input{4.exact_support_recovery/4.phase_transition_results.tex}

\section{Bayes minimax optimality and (sub)optimality of thresholding procedures}
\label{sec:optimality}
\input{4.exact_support_recovery/4.minimax.tex}

\section{Strong classification boundaries in other light-tailed error models}
\label{suppsec:other-boundaries}
\input{4.exact_support_recovery/4.other-boundaries.tex}

\section{Thresholding procedures under heavy-tailed errors}
\label{suppsec:heavy-tailed}
\input{4.exact_support_recovery/4.heavy-tailed.tex}

\section{Additional proofs}
\label{suppsec:proofs}
\input{4.exact_support_recovery/4.proofs-examples.tex}
\input{4.exact_support_recovery/4.proofs-convexity.tex}

### 2020-08-17 5.URS/5.numerical.tex
add draft converted from thesis

The characterization of \ac{URS} with the UDD condition allows us to simulate Gaussian errors and illustrate the effect of dependence on the phase transition behavior in finite dimensions.
We shall compare the performance of the Bonferroni's procedure, which is agnostic to both sparsity and signal size, with the oracle procedure which picks the top-s observations.

The first set of experiments explores short-range dependent errors from an auto-regressive (AR) models.
\begin{itemize}
	\item AR(1) Gaussian errors with parameter $\rho = -0.5$, $\rho = 0.5$, and $\rho = 0.9$,
	where the autocovariance functions decay exponentially, 
	$\rho_{k} = \rho^{k}$.
\end{itemize}
We again apply both the sparsity- and signal-size agnostic Bonferroni's procedure, i.e., $\widehat{S} = \{i:x(i)>\sqrt{2\log{p}}\}$, as well as the oracle procedure $\widehat{S}^* = \{i:x(i)\ge x_{[s]}\}$, $s=|S|$, to all settings.
Results of the numerical experiments for the AR models are shown in Figure \ref{fig:phase-simulated-dependent}.

As was commented in the main text, for dependent errors the oracle procedures is able to recover support of signals with higher probability than the Bonferroni procedures in finite dimensions; compare left and right columns of Figure \ref{fig:phase-simulated-dependent}.
Short range dependent observations, however, there is not a pronounced difference.
The results of the experiments are very similar to that of the independent Gaussian case.

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR-05_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR-05_p10000_oracle.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR05_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR05_p10000_oracle.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR09_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR09_p10000_oracle.eps}
    \caption{The empirical probability of exact support recovery from numerical experiments, as a function of sparsity level $\beta$ and signal sizes $r$. Darker colors indicate higher probability of exact support recovery. 
    Three AR(1) models with autocorrelation functions $(-0.5)^k$ (upper), 
    $0.5^k$ (middle), and $0.9^k$ (lower) are simulated.
    The experiments were repeated 1000 times for each sparsity-signal size combination.
    In finite dimensions ($p=10000$), the Bonferroni procedures (left) suffers small loss of power compared to the oracle procedures (right).
    A phase transition in agreement with the predicted boundary \eqref{eq:strong-classification-boundary} can be seen in the AR models.
    The boundaries (solid, dashed, and dash-dotted lines) are as in Fig \ref{fig:phase-simulated}.}
    \label{fig:phase-simulated-dependent}
\end{figure}

\medskip

The second set of experiments explores exact support recovery in additive error models in the cases of long-range dependent but UDD, as well as non-UDD errors.
In particular we simulate
\begin{itemize}
    \item Fractional Gaussian noise (fGn) with Hurst parameter $H = 0.75$ and $H = 0.9$. 
    The autocovariance functions are 
    % $$\rho_{k} \sim 2H(2H-1)k^{2H-2},$$
    $$\rho_{k} \sim 0.75k^{-0.6} \quad \text{and} \quad \rho_{k} \sim 1.44k^{-0.2},$$
    as $k\to\infty$.
    Both fGn models represent the regime of long-range dependence, where covariances decay very slowly to zero, so that $\sum|\rho_k| = \infty$; see, e.g., \citep{taqqu2003livre}.
    Observe that every stationary Gaussian process with vanishing autocovariance gives rise to an UDD array as concluded in Corollary \ref{cor:stationary-Gaussian-errors}.
    \item The non-UDD Gaussian errors described in Example \ref{exmp:counter-example}.
\end{itemize}
We will apply both the sparsity-and-signal-size-agnostic Bonferroni's procedure, i.e., $\widetilde{S} = \{i:x(i)>\sqrt{2\log{p}}\}$, as well as the oracle procedure $\widehat{S}^* = \{i:x(i)\ge x_{[s]}\}$, $s=|S|$, to all settings.
Results of the numerical experiments for the fGn and non-UDD models are shown in Figure \ref{fig:phase-simulated-very-dependent}.

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_fGn075_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_fGn075_p10000_oracle.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_fGn09_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_fGn09_p10000_oracle.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_block_structure_p10000_agnostic7.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_block_structure_p10000_oracle6.eps}
    \caption{The empirical probability of exact support recovery from numerical experiments, as a function of sparsity level $\beta$ and signal sizes $r$. Darker colors indicate higher probability of exact support recovery. 
    Two fGn models with Hurst parameter $H = 0.75$ (upper), 
    $H = 0.9$ (middle), and the non-UDD errors in Example \ref{exmp:counter-example} (lower) are simulated.
    The experiments were repeated 1000 times for each sparsity-signal size combination.
    In finite dimensions ($p=10000$), the oracle procedures (right) is able to recover support for weaker signals than the Bonferroni procedures (left) when errors are heavily dependent, although they have the same phase transition limit.
    The non-UDD errors demonstrate qualitatively different behavior, enabling support recovery for strictly weaker signals.
    The boundaries (solid, dashed, and dash-dotted lines) are as in Fig \ref{fig:phase-simulated}.
    In the non-UDD example, dashed lines represent the limit attained by Bonferroni's procedures.
    See text for additional comments.}
    \label{fig:phase-simulated-very-dependent}
\end{figure}

Notice that the oracle procedure sets its thresholds more aggressively (at roughly $\sqrt{2\log s}$) than the Bonferroni procedure (at $\sqrt{2\log p}$).
Although this difference vanishes as $p\to\infty$, in finite dimensions ($p=10\,000$) the advantage can be felt. 
Indeed, in all our experiments the oracle procedure is able to recover support of signals with higher probability than the Bonferroni procedures; compare left and right columns of Figure  \ref{fig:phase-simulated-very-dependent}.
Notice also that there is an increase in probability of recovery near $\beta=0$ for oracle procedures.
This is an artifact in finite dimensions due to the fact that $s = \lfloor p^{1-\beta}\rfloor < p/2$, and there are more signals than nulls. The oracle procedures is able to adjust to this reversal by lowering its threshold accordingly.

For UDD errors, Theorem \ref{thm:necessary} predicts that exact recovery of the support is impossible when signal sizes are below the boundary \eqref{eq:strong-classification-boundary}, even with oracle procedures. 
% Both the AR and the fGn models generate UDD Gaussian errors, and should demonstrate the same phase-transition boundary.
However, the rate of this convergence (i.e., $\P[\widehat{S}^*=S]\to0\;\text{or}\;1$) can be very slow when the errors are heavily dependent,
even though all AR and fGn models demonstrate qualitatively the same behavior in line with the predicted boundary \eqref{eq:strong-classification-boundary}. 
In finite dimensions ($p=10\,000$), as dependence in the errors increases (fGN(H=0.75) to fGN(H=0.9)), the oracle procedure becomes more powerful at recovering signal support with high probability for weaker signals.

On the other hand, as demonstrated in Example \ref{exmp:counter-example}, non-UDD errors yield qualitatively different behavior; exact support recovery is possible for signal sizes strictly weaker than that in the UDD case. 
Lower-right panel of Figure \ref{fig:phase-simulated-very-dependent} demonstrates in this example that the signal support can be recovered as long as the signal sizes are larger than $4(1-\beta)$.

\medskip

For completeness, we verify the claims in Example \ref{exmp:counter-example}.

\begin{proof}[Proof of claims in Example \ref{exmp:counter-example}]
Recall that $\widehat{S}^* = \{j:x(j)>t_p^*\}$, where $t_p^* = \sqrt{2(1-\beta)\log{p}}$. 
Analogous to \eqref{eq:Bonferroni-FWER-control} in the proof of Theorem \ref{thm:sufficient}, we have
\begin{align*}
    \P\left[\widehat{S} \subseteq S\right] 
        &= 1 - \P\left[\max_{j\in S^c}x(j) > t_p^*\right] 
        = 1 - \P\left[\max_{j\in S^c}\epsilon(j) > t_p^*\right] \nonumber \\
      % \ge 1 - \P\left[\max_{j\in\{1,\ldots,p\}}\epsilon(j) > t_p\right] \nonumber \\
        &\ge 1 - \P\left[\max_{j\in\{1,\ldots,p\}}\epsilon(j) > t_p^*\right] 
        \ge 1 - \P\left[\max_{j\in\{1,\ldots,\lfloor p^{1-\beta}\rfloor\}}\widetilde{\epsilon}(j) > t_p^*\right]
\end{align*}
where $\left(\widetilde{\epsilon}\right)_{j=1}^{\lfloor p^{1-\beta}\rfloor}$'s are independent Gaussian errors; in the last inequality we used the assumption that there are at most $\lfloor p^{1-\beta}\rfloor$ independently distributed Gaussian errors in $\left(\epsilon_p(j)\right)_{j=1}^p$.
By Example \ref{exmp:FWER-controlling_procedures} (with $\lfloor p^{1-\beta}\rfloor$ taking the role of $p$), we know that the FWER goes to 0 at a rate of 
$\left(2\log{\lfloor p^{1-\beta}\rfloor}\right)^{-1/2}$.
Therefore, the probability of no false inclusion converges to 1.

On the other hand, since the signal sizes are no smaller than $(\nu\underline{r}\log p)^{1/\nu}$, similar to \eqref{eq:sufficient-proof-eq1}, we obtain
\begin{align}
    \P\left[\widehat{S} \supseteq S\right] 
    &\ge \P\left[\min_{j\in S}\epsilon(j) > \sqrt{2(1-\beta)\log{p})} - \sqrt{2\underline{r}\log{p}} \right] \nonumber \\
    &= \P\left[\max_{j\in S}\left(-\epsilon(j)\right) < \sqrt{2\log{p})}\left(\sqrt{\underline{r}}-\sqrt{1-\beta}\right) \right] \nonumber \\
    &= \P\left[\frac{\max_{j\in S}(-\epsilon(j))}{u_{|S|}} < \frac{\sqrt{\underline{r}}-\sqrt{1-\beta}}{\sqrt{1-\beta}}\left(1+o(1)\right) \right], \label{eq:sufficient-proof-counter-example}
\end{align}
where in the last line we used the quantiles \eqref{eq:AGG-quantiles}.
Since the minimum signal size is bounded below by $\underline{r} > 4(1-\beta)$, the right-hand-side of the inequality in \eqref{eq:sufficient-proof-counter-example} converges to a constant strictly larger than 1. While the left-hand-side, by Slepian's Lemma \cite{slepian1962one}, is stochastically smaller than a r.v. going to 1, i.e.,
\begin{equation}
  \frac{1}{u_{|S|}} \max_{j\in S}(-\epsilon(j)) \stackrel{d}{\le} \frac{1}{u_{|S|}} \max_{j\in S} \epsilon^*(j) \stackrel{\P}{\longrightarrow} 1,
\end{equation}
where $\left({\epsilon^*}\right)_{j=1}^{\lfloor p^{1-\beta}\rfloor}$'s are independent Gaussian errors.
Therefore the probability in \eqref{eq:sufficient-proof-counter-example} must also converge to 1.
\end{proof}

### 2020-08-17 5.URS/5.proofs-Ramsey.tex
add draft converted from thesis

% We start by providing a general result on the structure of arbitrary correlation matrices in this section, which helps us establish the `only if' part of Theorem \ref{thm:Gaussian-weak-dependence}. 
% Its proof uses the Ramsey Theorem from graph theory, which we briefly review next.

Given any integer $k\ge 1$, there is always an integer $R(k,k)$ called the {\em Ramsey number}:
\begin{equation}\label{eq:Ramsey-number}
k\le R(k,k)\le \binom{2k-2}{k-1}
\end{equation}
such that the following property holds:
every undirected graph with at least $R(k,k)$ vertices will contain {\em either} a clique of size $k$, or an {\em independent set} of $k$ nodes. 
Recall that a clique is a complete sub-graph where all pairs of nodes are connected, and an independent set is a set of nodes where no two nodes are connected.

This result is a consequence of the celebrated work of \citet{ramsey2009problem}, which 
gave birth to Ramsey Theory (see e.g., \citet{conlon2015recent}).  
The Ramsey Theorem and the upper bound \eqref{eq:Ramsey-number} (established first in \cite{erdos1935combinatorial}) are at the heart of the proof of the following result.
%An excellent introduction to Ramsey theory is given in \url{http://math.mit.edu/~fox/MAT307-lecture05.pdf}.

\begin{proposition} \label{prop:lower-bound-correlation-Ramsey}
  Fix $\gamma\in(0,1)$ and let $P = \left(\rho(i,j)\right)_{n\times n}$ be an arbitrary correlation
  matrix. If 
  \begin{equation}\label{eq:Ramsey-the-k-def}
   k:= \lfloor \log_2({n})/2 \rfloor  \ge \lceil 1/\gamma \rceil + 1,
  \end{equation}
  then there is a set of $k$ indices $K = \{l_1, \ldots, l_k\}\subseteq \{1,\ldots,n\}$ 
  such that 
  \begin{equation} \label{eq:lower-bound-correlation-Ramsey}
      \rho(i,j) \ge -\gamma, \mbox{ for all } i,j\in K.
  \end{equation}
\end{proposition}

\begin{proof}[Proof of Proposition \ref{prop:lower-bound-correlation-Ramsey}]
By using \eqref{eq:Ramsey-number} and a refinement of the Stirling's formula, 
we will show at the end of the proof that for $k \le \log_2({n})/2$, we have 
\begin{equation}\label{eq:Ramsey-bounds}
 R(k,k) \le n,
\end{equation}
where $R(k,k)$ is the Ramsey number.

Now, construct a graph with vertices $\{1,\dots,n\}$ such that there is an edge between nodes $i$ and $j$ if and only if $\rho(i,j) > -\gamma$. 
In view of \eqref{eq:Ramsey-bounds} and Ramsey's theorem (see e.g., Theorem 1 in \cite{fox2009lecture} or \cite{conlon2015recent} for a recent survey on Ramsey theory), there is a subset of $k$ nodes $K =\{l_1,\dots,l_k\}$, which is either a {\em complete graph} or an {\em independent set}.

If $K$ is a complete graph, then by our construction of the graph, Relation \eqref{eq:lower-bound-correlation-Ramsey} holds.

Now, suppose that $K$ is a set of independent nodes.  This means, again by the construction of our graph, that
$$
\rho(i,j) < -\gamma,\quad\mbox{for all }i\not= j\in K.
$$
Let $Z_i,\ i \in K$ be zero-mean random variables such that 
$\rho(i,j) = \E [Z_iZ_j]$. Observe that
\begin{equation} \label{eq:Ramsey-proof-contradiction}
    \var\left( \sum_{i\in K} Z_i\right) 
    = \sum_{i\in K} \var(Z_i) + \sum_{\substack{i\not=j\\i,j \in K}} \cov(Z_i, Z_j) 
    <  k - k(k-1)\gamma,
\end{equation}
since $\var(Z_i)=1$ and $\rho(i,j)<-\gamma$ for $i\neq j$.
By our assumption, $k\ge \left(\lceil 1/\gamma \rceil + 1\right)$, or equivalently, $(k-1) \ge 1/\gamma$, the variance in \eqref{eq:Ramsey-proof-contradiction} is negative. 
This is a contradiction showing that there are no independent sets $K$ with cardinality $k$.

To complete the proof, it remains to show that Relation \eqref{eq:Ramsey-bounds} holds.
In view of the upper bound on the Ramsey numbers \eqref{eq:Ramsey-number}, it 
is enough to show that $k \le \log_2(\sqrt{n})$ implies
$$
\binom{2k-2}{k-1} \le n.
$$
This follows from a refinement of the Stirling formula, due to \citet{robbins1955remark}:
$$
 \sqrt{2\pi} m^{m+1/2} e^{-m} e^{\frac{1}{(12 m +1)}} \le  m! \le \sqrt{2\pi} m^{m+1/2} e^{-m} 
 e^{\frac{1}{12 m}}.
$$
Indeed, letting $\widetilde k:= k-1$, and applying the above upper and lower bounds 
to the  terms $(2\widetilde k)!$ and $\widetilde k!$, respectively, we obtain:
\begin{align*}
\binom{2k-2}{k-1} \equiv \frac{(2\widetilde k)!}{ (\widetilde k!)^2 }
\le \frac{2^{2\widetilde k}}{\sqrt{\pi \widetilde k}}\exp\left \{ \frac{1}{24 \widetilde k} -
\frac{2}{ 12 \widetilde k +1}\right\} < 2^{2 k}
\end{align*}
where the last two inequalities follow by simply dropping positive factors less than $1$.
Since $2k \le \log_2(n)$, the above bound implies Relation \eqref{eq:Ramsey-bounds} 
and the proof is complete.
\end{proof}

Using Proposition \ref{prop:lower-bound-correlation-Ramsey}, we establish the key lemma used in the proof of Theorem \ref{thm:Gaussian-weak-dependence}.

\begin{lemma} \label{lemma:positive-correlation}
  Let $c\in(0,1)$, and $P = \left(\rho(i,j)\right)_{(n+1)\times(n+1)}$ be a correlation matrix such that \begin{equation} \label{eq:positive-correlation-lemma-condition}
      \rho(1,j) > c \quad \mbox{for all } j = 1,\ldots,n+1.
  \end{equation}
  If $n \ge 2^{2\lceil2/c^2\rceil+4}$, then there is a set of indices $K = \{l_1, \ldots, l_k\}\subseteq \{2,\ldots,n+1\}$ of cardinality $k = |K| = \lfloor\log_2{\sqrt{n}}\rfloor$, such that 
  \begin{equation} \label{eq:positive-correltation-lemma-conclusion}
      \rho(i,j) > \frac{c^2}{2} \quad\mbox{for all } i,j\in K.
  \end{equation}
  That is, all entries of the $k\times k$ sub-correlation matrix $P_K:=\left(\rho(i,j)\right)_{i,j\in K}$ are larger than $c^2/2$.
\end{lemma}

\begin{proof}[Proof of Lemma \ref{lemma:positive-correlation}]
    Let $Z_1, \ldots, Z_{n+1}$ be random variables with covariance matrix $P$.
    Denote $\rho_j = \rho(1,j)$ and define 
    \begin{equation}
      R(j) = 
      \begin{cases}
        \frac{1}{\sqrt{1-\rho_j^2}}\left(Z(j) - \rho_j Z(1)\right), &\mbox{if } \rho_j<1,\\
        R^* &\mbox{if } \rho_j=1,
      \end{cases}
    \end{equation}
    where $R^*$ is an arbitrary zero-mean, unit-variance random variable.
    It is easy to see that $\var(R(j)) = 1$, and
    \begin{align*}
    \cov\left(Z(i), Z(j)\right) &= \cov\left(\rho_i Z(1) + \sqrt{1-\rho_i^2} R(i), \; \rho_j Z(1) + \sqrt{1-\rho_j^2} R(j)\right) \\
        &= \rho_i\rho_j + \sqrt{1-\rho_i^2}\sqrt{1-\rho_j^2} \;\cov\left(R(i), R(j)\right) \\
        &\ge c^2 + \min\left\{\cov\left(R(i), R(j)\right), 0\right\}.
    \end{align*}

    Therefore, Relation \eqref{eq:positive-correltation-lemma-conclusion} would hold if we can find a set of indices $K = \{l_1,\ldots,l_k\}$ such that $\cov\left(R(i),R(j)\right)>-c^2/2$ for all $i,j\in K$, where $k=|K|=\lfloor\log_2\sqrt{n}\rfloor$.
    This, however, follows from Proposition \ref{prop:lower-bound-correlation-Ramsey} applied to $\left(R(j)\right)_{j=2}^{n+1}$ with $\gamma = c^2/2$, provided that 
    $$
    k = \lfloor\log_2\sqrt{n}\rfloor \ge \lceil 2/c^2 \rceil + 1.
    $$
    The last inequality indeed follows form the assumption that $n \ge 2^{2\lceil2/c^2\rceil+4}$.
\end{proof}

### 2020-08-17 5.URS/5.proofs-UDD-URS.tex
add draft converted from thesis

Recall that our objective is to show \eqref{eq:URS-condition}. 
We will do so in two stages; namely, we will prove that for all $\delta>0$, we have 
\begin{equation} \label{eq:URS-condition-upper-side}
    \P\left[\frac{M_{S_p}}{u_{|S_p|}} > 1+\delta\right] \to 0,
\end{equation}
and
\begin{equation} \label{eq:URS-condition-lower-side}
    \P\left[\frac{M_{S_p}}{u_{|S_p|}} < 1-\delta\right] \to 0,
\end{equation}
for any sequence of subsets $S_p$ such that $|S_p|\to\infty$.
Although the first step \eqref{eq:URS-condition-upper-side} was already shown in Proposition \ref{prop:rapid-varying-tails}, regardless of the dependence structure, we provide in this section a more refined result. 
Specifically, the following result states that for the AGG model, the constant $\delta$ in Proposition \ref{prop:rapid-varying-tails} can be replaced by a vanishing sequence $c_p\to 0$.

\begin{lemma}[Upper tails of AGG maxima] \label{lemma:AGG-maxima-upper-tails}
Let ${\cal E}$ be an array with marginal distribution $F\in\text{AGG}(\nu)$, $\nu>0$. If we pick
\begin{equation} \label{eq:choice-of-c_p}
    c_p = \frac{u_{p\log{p}}}{u_p} - 1,    
\end{equation} 
where $u_p = F^{\leftarrow}(1-1/p)$, then we have $c_p>0$, $c_p\to 0$, and
\begin{equation} \label{eq:AGG-max-upper-bound}
    \P\left[\frac{M_p}{u_p}-(1+c_p) > 0\right] \to 0.
\end{equation}
\end{lemma}
The proof can be found in Section \ref{subsec:bounding-upper-tails-of-maxima} below.

Since Lemma \ref{lemma:AGG-maxima-upper-tails} holds regardless of the dependence structure, the same conclusions hold if one replaces $M_p$ by $M_{S_p} = \max_{j\in S_p}\epsilon(j)$ and $p$ by $q = q(p)=|S_p|$, where $S_p$ is any sequence of sets such that $q \equiv |S_p| \to \infty$.
This entails \eqref{eq:URS-condition-upper-side}.

On the other hand, the proof of \eqref{eq:URS-condition-lower-side} uses a more elaborate argument based on the Sudakov-Fernique bound.
We proceed by first bounding the probability by an expectation. 
For all $\delta>0$, we have
\begin{align}
    \P\left[\frac{M_{S_p}}{u_q}<1-\delta\right] 
        &= \P\left[-\left(\frac{M_{S_p}}{u_q} - (1+c_q)\right) > \delta + c_q\right] \nonumber \\
        %&\le \P\left[\max{\left\{-\left(\frac{M_{S_p}}{u_q} - (1+c_q)\right),0\right\}} > \delta + c_q\right] \nonumber \\
        &\le \P\left[\left(\frac{M_{S_p}}{u_q} - (1+c_q)\right)_->\delta+c_q\right] \nonumber \\
        &\le \frac{1}{\delta + c_q}\E\left[\left(\frac{M_{S_p}}{u_q} - (1+c_q)\right)_-\right], \label{eq:Gaussian-maxima-lower-expectation-bound}
\end{align}
where $(x)_-:=\max\{-x,0\}$ and the last line follows from the Markov inequality.
The next result shows that the upper bound in \eqref{eq:Gaussian-maxima-lower-expectation-bound} vanishes.
\begin{lemma} \label{lemma:Gaussian-maxima-lower-expectation}
  Let ${\cal E}$ be a Gaussian UDD  array  and 
  $S_p\subseteq\{1,\ldots,p\}$ be an arbitrary sequence of sets 
  such that $q = q(p) = |S_p|\to\infty$.  Then, for $M_{S_p}:= \max_{j\in S_p} \epsilon_p(j)$ and $c_q$ as in \eqref{eq:choice-of-c_p}, we have
  \begin{equation} \label{eq:Gaussian-maxima-lower-expectation}
    \E\left[\left(\frac{M_{S_p}}{u_q} - (1+c_q)\right)_-\right] \to 0,\ \ \quad \mbox{ as }p\to \infty.
  \end{equation}
\end{lemma}
The proof of the lemma is given in Section \ref{subsec:bounding-lower-tails-of-maxima} below.

Going back to the proof of Theorem \ref{thm:Gaussian-weak-dependence}, we observe that Relations \eqref{eq:Gaussian-maxima-lower-expectation-bound} and \eqref{eq:Gaussian-maxima-lower-expectation} imply \eqref{eq:URS-condition-lower-side}, which completes the proof of the `if' part. \qed

\begin{remark} Only the Sudakov-Fernique minorization argument used in the proof of Lemma \ref{lemma:Gaussian-maxima-lower-expectation}, relies on the Gaussian assumption. We expect the techniques and results here to be useful in extending Theorem \ref{thm:Gaussian-weak-dependence} to more general class of distributions, say, the AGG model.
\end{remark}

\subsection{Bounding the upper tails of AGG maxima}
\label{subsec:bounding-upper-tails-of-maxima}

\begin{proof}[Proof of Lemma \ref{lemma:AGG-maxima-upper-tails}]
Recall by \eqref{eq:AGG-quantiles} that 
\begin{equation*}
    u_q\sim\left(\nu\log{q}\right)^{1/\nu}, \quad q\to\infty,
\end{equation*}
so that
\begin{equation} %\label{eq:choice-of-c_p}
c_p  = \frac{u_{p\log{p}}}{u_p} -1 = \left(\frac{\log{p}+\log{\log{p}}}{\log{p}}\right)^{1/\nu}(1+o(1)) - 1 \rightarrow 0 \quad \mbox{as } p\to\infty.
\end{equation} 
By the union bound, we have
\begin{align}
    \P\left[\frac{M_p}{u_p} > 1+c_p\right] 
        &\le \sum_{j=1}^p \P\left[\frac{\epsilon_p(j)}{u_p} > 1+c_p\right] 
        = p \overline{F}\left(u_{p\log{p}}\right) \label{eq:AGG-maxima-upper-tails-proof-1} \\
        &= p \overline{F}\left(F^{\leftarrow}\left(1-\frac{1}{p\log{p}}\right)\right) \le \frac{1}{\log{p}} \rightarrow 0. \nonumber
\end{align}
where the last inequality follows from the fact that $F\left(F^{\leftarrow}(u)\right)\ge u$ for all $u\in[0,1]$.
\end{proof}

In addition to Lemma \ref{lemma:AGG-maxima-upper-tails}, which says the upper tail vanishes in probability, we will also prepare a result which states that the upper tail also vanishes in expectation.

\begin{lemma} \label{lemma:AGG-max-uniform-integrability}
Let $M_p$ and $c_p$ be as in Lemma \ref{lemma:AGG-maxima-upper-tails}, and denote 
$$
\xi_p := \frac{M_p}{(1+c_p)u_p}.
$$
Then there exists $p_0,t_0 > 0$, and absolute constant $C>0$ such that
\begin{equation} \label{eq:lemma-AGG-uniform-integrability}
    \P\left[\xi_p > t \right]\le \exp{\{-Ct^\nu\}}, \quad \text{for all} \quad p>p_0, t>t_0.
\end{equation}
In particular, the set of random variables $\{\left(\xi_p\right)_+,p\in\N\}$ is uniformly integrable.
\end{lemma}
\begin{proof}[Proof of Lemma \ref{lemma:AGG-max-uniform-integrability}]
Recalling that $(1+c_p)u_p = u_{p\log{p}}$, and by applying the union bound as in \eqref{eq:AGG-maxima-upper-tails-proof-1}, we have
\begin{align}
    \log \P\left[\xi_p > t\right] 
        &\le \log p + \log{\overline{F}\left(u_{p\log{p}}t\right)} \nonumber \\
        &\le \log p - \frac{1}{\nu}\left(u_{p\log{p}}t\right)^\nu(1-\delta). \label{eq:lemma-AGG-uniform-integrability-proof-1}
\end{align}
for $t > t_0(\delta)>0$, where $\delta\in(0,1)$ is an arbitrarily small number fixed in advance. 
This follows from the assumption that $F\in\text{AGG}(\nu)$ and the Definition \ref{def:AGG} of AGG tails.
Using in \eqref{eq:lemma-AGG-uniform-integrability-proof-1} the explicit expressions for quantiles in \eqref{eq:AGG-quantiles}, we obtain
\begin{equation} \label{eq:lemma-AGG-uniform-integrability-proof-2}
    \log \P\left[\xi_p > t\right] \le \log p - \underbrace{\left(1+o(1)\right)(1-\delta)t^\nu}_{\text{greater than }1\text{ for large }t}\log{p} - t^\nu\underbrace{\log{\log{p}}\left(1+o(1)\right)(1-\delta)}_{\text{greater than }C\text{ for large }p}.
\end{equation}
For large $t$, we have $\left(1+o(1)\right)(1-\delta)t^\nu > 1$, so that sum of the first two terms on the right-hand side of \eqref{eq:lemma-AGG-uniform-integrability-proof-2} is negative.
Also, for $p$ larger than some constant $p_0(\delta)$, we have $\log{\log{p}}\left(1+o(1)\right)(1-\delta) > C$ for some constant $C$ that does not depend on $p$.
Therefore \eqref{eq:lemma-AGG-uniform-integrability} holds for $t>t_0(\delta)$ and $p>p_0(\delta)$, and the proof is complete.
\end{proof}

\begin{corollary} \label{cor:AGG-max-upper-bound-expectation}
The upper tails of AGG maxima vanish in expectation, i.e.,
    \begin{equation} \label{eq:AGG-max-bound-upper-expectation}
    \E\left[\left(\frac{M_p}{u_p} - (1+c_p)\right)_+\right]
    \to 0 \quad\text{as }\; p\to\infty,
\end{equation}
where $(a)_+ := \max\{a,0\}$.
\end{corollary}

\begin{proof}[Proof of Corollary \ref{cor:AGG-max-upper-bound-expectation}]
Since $c_p\ge0$ is a sequence converging to 0, we have $c_p < 1$ for $p \ge p_0$. Hence for any $t>0$, we have
\begin{align}
    \P\left[\left(\frac{M_p}{u_p} - (1+c_p)\right)_+ > t\right] 
    &= \P\left[(1+c_p)\left(\xi_p-1\right)_+ > t\right] \nonumber \\
    &\le \P\left[\left(\xi_p-1\right)_+ > t/2\right] 
    \le \P\left[\xi_p > t/2 \right]. \label{eq:AGG-max-bound-upper-expectation-proof}
\end{align}
By Lemma \ref{lemma:AGG-max-uniform-integrability}, $\{\left(\xi_p\right)_+\}$ is u.i., therefore by Relation \eqref{eq:AGG-max-bound-upper-expectation-proof}, $\{\left(M_p/u_p - (1+c_p)\right)_+,\;p\in\N\}$ is u.i. as well.
Since by Lemma \ref{lemma:AGG-maxima-upper-tails}, $\left(M_p/u_p - (1+c_p)\right)_+\to 0$ in probability, Relation \eqref{eq:AGG-max-bound-upper-expectation} follows from the established uniform integrability.
\end{proof}

\subsection{Bounding the lower tails of Gaussian maxima}
\label{subsec:bounding-lower-tails-of-maxima}

The main goal of this section is to establish the following result.

\begin{proposition} \label{prop:Gaussian-maxima-expectation-lower-bound}
For every UDD Gaussian array $\cal E$, and any sequence of subsets
$S_p\subseteq\{1,\ldots,p\}$ such that $q = q(p) = |S_p|\to \infty$, we have
\begin{equation} \label{eq:AGG-max-bound-expectation}
    \liminf_{p\to\infty} \E\left[\frac{M_{S_p}}{u_q}\right] \ge 1,
\end{equation}
where $M_S = \max_{j\in S}\epsilon(j)$.
\end{proposition}
% We suppressed dependence on $p$ for both $S = S_p$ and $s = s(p) = |S_p|$ for convenience of notation.

Lemma \ref{lemma:Gaussian-maxima-lower-expectation}, which is the key to the proof of the `if' part of Theorem \ref{thm:Gaussian-weak-dependence}, follows immediately from this proposition.

\begin{proof}[Proof of Lemma \ref{lemma:Gaussian-maxima-lower-expectation}]
We start with the identity
$$
\E\left[\frac{M_{S_p}}{u_q}-(1+c_q)\right] = \E\left[\left(\frac{M_{S_p}}{u_q}-(1+c_q)\right)_+\right] - \E\left[\left(\frac{M_{S_p}}{u_q}-(1+c_q)\right)_-\right].
$$
By re-arranging terms and taking limsup/liminf, we obtain
\begin{align} \label{e:lim-sup-vanishes}
    0 \le &\limsup_{p\to\infty}\E\left[\left(\frac{M_{S_p}}{u_q}-(1+c_q)\right)_-\right]\nonumber \\
        \le & \limsup_{p\to\infty}\E\left[\left(\frac{M_{S_p}}{u_q}-(1+c_q)\right)_+\right] - \liminf_{p\to\infty}\E\left[\frac{M_{S_p}}{u_q}-(1+c_q)\right]\\
        = & - \liminf_{p\to\infty}\E\left[\frac{M_{S_p}}{u_q}-(1+c_q)\right],
        \label{e:lim-inf-bound}
\end{align}
where the last equality follows from the fact that the lim-sup in \eqref{e:lim-sup-vanishes} vanishes by Corollary \ref{cor:AGG-max-upper-bound-expectation}.
On the other hand, since $c_q\to 0$, we have
$$
\liminf_{p\to\infty}\E\left[\frac{M_{S_p}}{u_q}-(1+c_q)\right] 
= \liminf_{p\to\infty}\E\left[\frac{M_{S_p}}{u_q}-1\right] \ge 0,
$$
where the last inequality follows from Proposition \ref{prop:Gaussian-maxima-expectation-lower-bound}.  This shows that 
the right-hand side of \eqref{e:lim-inf-bound} is non-positive and hence
\eqref{eq:Gaussian-maxima-lower-expectation} holds. 
\end{proof}

A interesting fact on the relationship between the upper quantiles and the expectation of iid maxima will be needed for the proof of  Proposition \ref{prop:Gaussian-maxima-expectation-lower-bound}.
The following lemma may be of independent interest.
% The following result applies to AGG models as well as a wider range of models, provided that tail densities are monotone discreasing.

\begin{lemma} \label{lemma:expectation-lower}
Let $(X_i)_{i=1}^p$ be $p$ iid random variables with distribution $F$ such that $\E[(X_i)_-]$ exists, i.e.,
$$
\E[\max\{-X_i, 0\}] < \infty.
$$
Let $M_p = \max_{i=1,\ldots,p}X_i$. Assume that $F$ has a density $f$, which is eventually decreasing. 
More precisely, we suppose there exists a 
$C_0$ such that $0<F(C_0)<1$, and $f(x_1) \ge f(x_2)$ whenever $C_0 < x_1 \le x_2$. 
Under these assumptions, we have,
$$
\liminf_{p\to\infty}\frac{\E M_p}{u_{p+1}} \ge 1,
$$
where $u_{p+1} = F^{\leftarrow}(1 - 1/(p+1))$.
\end{lemma}

\begin{proof}[Proof of Lemma \ref{lemma:expectation-lower}]
% For ease of exposition we let $C_0 = 0$; the case where $C_0 > 0$ can be handled using exactly the same arguments.
Write 
$$
X_i = F^{\leftarrow}(U_i)
$$
where $U_i$ are iid uniform random variables on $(0,1)$.
Denote $M^{U}_p$ as the maximum of the $U_i$'s, we have $\E M_p = \E\left[F^{\leftarrow}(M^{U}_p)\right]$, and by conditioning, we obtain
\begin{align} \label{eq:lemma:expectation-lower-proof-1}
    \E M_p &= \E\left[F^{\leftarrow}(M^{U}_p)\;\big|\;M^{U}_p \ge F(C_0)\right] \P\left[M^{U}_p \ge F(C_0)\right] + \nonumber \\ 
           &\quad\quad +\E\left[F^{\leftarrow}(M^{U}_p)\;\big|\;M^{U}_p < F(C_0)\right] \P\left[M^{U}_p < F(C_0)\right]. 
\end{align} 
We first handle the first term in the summation. Since $f$ is decreasing beyond $C_0$, $F$ is concave on $(C_0, \infty)$, and $F^{\leftarrow}$ is convex on $(F(C_0), 1)$. By Jensen's inequality, we have
\begin{equation*}
    \E\left[F^{\leftarrow}(M^{U}_p)\;\big|\;M^{U}_p \ge F(C_0)\right] 
        \ge F^{\leftarrow}\left(\E[M^{U}_p\;|\;M^{U}_p\ge F(C_0)]\right).
\end{equation*}
With a direct calculation, one can show that 
\begin{equation*}
    F^{\leftarrow}\left(\E[M^{U}_p\;|\;M^{U}_p\ge F(C_0)]\right)
    = F^{\leftarrow}\left(\left(1-\frac{1}{p+1}\right)\left(\frac{1-F(C_0)^{p+1}}{1-F(C_0)^{p}}\right)\right),
\end{equation*}
and hence
\begin{align*}
    \E\left[F^{\leftarrow}(M^{U}_p)\;\big|\;M^{U}_p \ge F(C_0)\right] 
        &\ge F^{\leftarrow}\left(\left(1-\frac{1}{p+1}\right)\left(\frac{1-F(C_0)^{p+1}}{1-F(C_0)^{p}}\right)\right) \\
        &\ge F^{\leftarrow}\left(1-\frac{1}{p+1}\right) = u_{p+1}.
\end{align*}
Since $\P[M^{U}_p\le m\big|\;M^{U}_p < F(C_0)] = \left(m/F(C_0)\right)^p \le m/F(C_0)$ for $m\le F(C_0))$, we have
$$\left(M^{U}_p\;\big|\;M^{U}_p < F(C_0)\right)\stackrel{\text{d}}{\ge} \left(U_1\;\big|\;U_1 < F(C_0)\right),$$
where and the latter is the uniform distribution on $(0,F(C_0))$.
Therefore, for the second term of the sum in \eqref{eq:lemma:expectation-lower-proof-1}, by monotonicity of $F^{\leftarrow}$, we obtain
\begin{align*}
    \E\left[F^{\leftarrow}(M^{U}_p)\;\big|\;M^{U}_p < F(C_0)\right] 
        &\ge \E\left[F^{\leftarrow}(U_1)\;\big|\;U_1 < F(C_0)\right] \\
        &= \E\left[X_1\;\big|\;X_1 < C_0\right].
\end{align*}
Finally, since $\P\left[M^{U}_p < F(C_0)\right] = F(C_0)^p = 1 - \P\left[M^{U}_p \ge F(C_0)\right]$, by \eqref{eq:AGG-quantiles}, we have
\begin{align*}
    \frac{\E M_p}{u_{p+1}} 
        &\ge \left(1 - F(C_0)^p\right) + \frac{\E\left[X_1\;\big|\;X_1 < C_0\right]}{u_{p+1}} F(C_0)^p.
\end{align*}
The conclusion follows since the right-hand-side of the last inequality converges to 1.
\end{proof}

We now ready to prove Proposition \ref{prop:Gaussian-maxima-expectation-lower-bound}. 
This is where the UDD dependence assumption is used.

\begin{proof}[Proof of Proposition \ref{prop:Gaussian-maxima-expectation-lower-bound}]
% Assume without loss of generality that the $\epsilon(j)$'s have unit variances.
Define the canonical (pseudo) metric on $S_p$,
$$
d(i,j) = \sqrt{\E\left[\left(\epsilon(i)-\epsilon(j)\right)^2\right]}.
$$
It can be easily checked that the canonical metric takes values between 0 and 2.
For arbitrary $\delta\in(0,1)$, take $\gamma = \sqrt{2(1-\delta)}$, and
let $\mathcal{N}$ be a $\gamma$-packing of $S_p$. That is, let $\mathcal{N}$ be a subset of $S_p$, such that for any $i,j\in\mathcal{N}$, $i\neq j$, we have $d(i,j)\ge\gamma$, i.e.,
\begin{equation}\label{e:gamma-packing-def}
d(i,j) = \sqrt{2\left(1-\Sigma_p(i,j)\right)} \ge \gamma = \sqrt{2(1-\delta)},
\end{equation}
or equivalently, $\Sigma_p(i,j) \le \delta$.
We claim that we can find a $\gamma$-packing $\mathcal{N}$ whose number of elements is at least 
\begin{equation} \label{eq:packing-number-lower-bound}
    |\mathcal{N}| \ge q/N(\delta).
\end{equation}
Indeed, $\mathcal{N}$ can be constructed iteratively as follows:
\begin{itemize}[
    align=left,
    leftmargin=4em,
    itemindent=0pt,
    labelsep=0pt,
    labelwidth=4em
    ]
    \raggedright
    \item[{\bf Step 1:}] Set $S_p^{(1)}:=S_p$ and $\mathcal{N}:=\{j_1\}$, where $j_1\in S_p^{(1)}$ is an arbitrary element. Set $k:=1$.\\
    \item[{\bf Step 2:}] Set $S_p^{(k+1)}:=S_p^{(k)}\setminus B_\gamma(j_k)$, where
    $$
    B_\gamma(j_k) := \{i\in S_p: \;d(i,j_k) < \gamma \equiv \sqrt{2(1-\delta)}\}.
    $$
    \item[{\bf Step 3:}] If $S_p^{(k)} \neq \emptyset$, pick an arbitrary $j_{k+1}\in S_p^{(k)}$, set $\mathcal{N}:=\mathcal{N}\cup\{j_{k+1}\}$, and $k:=k+1$, go to step 2; otherwise, stop.
\end{itemize}
By the definition of UDD (see Definition \ref{def:UDD}), there are at most $N(\delta)$ coordinates whose covariance with $\epsilon(j)$ exceed $\delta$. 
Therefore at each iteration, $\left|B_\gamma(j_k)\right|\le N(\delta)$, and hence
$$
\left|S_p^{(k+1)}\right| \ge \left|S_p^{(k)}\right| - \left| B_\gamma(j_k)\right| \ge q - kN(\delta).
$$
The construction can continue for at least $q/N(\delta)$ iterations, and we have $|\mathcal{N}| \ge \lfloor q/N(\delta) \rfloor$ as desired.

Now we define on this $\gamma$-packing $\mathcal{N}$ an independent Gaussian process $\left(\eta(j)\right)_{j\in\mathcal{N}}$, 
$$\eta(j) = \frac{\gamma}{\sqrt{2}}Z(j) \quad j\in \mathcal{N},$$
where $Z(j)$'s are iid standard normal random variables.
Observe that by the definition of $\gamma$-packing in \eqref{e:gamma-packing-def}, the increments of the new process are smaller than those of the original process in the following sense, 
$$
\E\left[\left(\eta(i)-\eta(j)\right)^2\right] = \gamma^2 \le d^2(i,j) = \E\left[\left(\epsilon(i)-\epsilon(j)\right)^2\right]
$$
for all $i\neq j$, $i,j\in\mathcal{N}$. Applying the Sudakov-Fernique inequality (see, e.g., Theorem 2.2.3 in \citep{adler2009random}) to  $\left(\eta(j)\right)_{j\in\mathcal{N}}$ and  $\left(\epsilon(j)\right)_{j\in\mathcal{N}}$, we have
\begin{equation}\label{eq:Sudakov-1}
\E\left[\max_{j\in\mathcal{N}}\eta(j)\right] \le \E\left[\max_{j\in\mathcal{N}}\epsilon(j)\right] \le \E\left[\max_{j\in{S_p}}\epsilon(j)\right].
\end{equation}
Since the $\left(\eta(j)\right)_{j\in\mathcal{N}}$ are independent Gaussians, Lemma \ref{lemma:expectation-lower} yields the lower bound,
\begin{equation}\label{eq:Sudakov-2}
\liminf_{p\to\infty} \E\left[\frac{\max_{j\in\mathcal{N}}\eta(j)}{u_{|\mathcal{N}|}}\right] \ge \frac{\gamma}{\sqrt{2}} = \sqrt{1-\delta}.
\end{equation}
Using the expressions \eqref{eq:AGG-quantiles} for the quantiles 
of AGG models (with $\nu=2$ here), we have
\begin{equation}\label{eq:Sudakov-3}
\frac{u_{|\mathcal{N}|}}{u_q} 
\ge \left(\frac{\log q-\log{N(\delta)}}{\log{q}}\right)^{1/2}\left(1+o(1)\right)\to 1,
\end{equation}
since $N(\delta)$ does not depend on $q= q(p)\to \infty$, and that $|\mathcal{N}|\ge q/N(\delta)$.

By combining \eqref{eq:Sudakov-1}, \eqref{eq:Sudakov-2} and \eqref{eq:Sudakov-3}, we conclude that
\begin{align*}
    \liminf_{p\to\infty} \E\left[\frac{\max_{j\in{S_p}}\epsilon(j)}{u_q}\right] 
    &\ge \liminf_{p\to\infty} \E\left[\frac{\max_{j\in\mathcal{N}}\eta(j)}{u_q}\right] &\text{by } \eqref{eq:Sudakov-1}\\
    &\ge \liminf_{p\to\infty} \E\left[\frac{\max_{j\in\mathcal{N}}\eta(j)}{u_{|\mathcal{N}|}}\right]  &\text{by } \eqref{eq:Sudakov-3} \\
    &\ge \sqrt{1-\delta}.  &\text{by } \eqref{eq:Sudakov-2}
\end{align*} 
Since $\delta>0$ is arbitrary, \eqref{eq:AGG-max-bound-expectation} follows as desired.
\end{proof}

% The current proof of Theorem \ref{thm:Gaussian-weak-dependence} relies on Slepian's lemma \cite{slepian1962one}. 
% \begin{lemma}[Slepian's Lemma] \label{lemma:Slepian}
% For two zero-mean Gaussian sequences $\left(\eta(j)\right)_{j=1}^p$ and $\left(z(j)\right)_{j=1}^p$, if
% $$
% \E[\eta(j)^2] \le \E[z(j)^2] \quad \text{and} \quad \E[\eta(i)\eta(j)] \le \E[z(i)z(j)]
% $$
% for all $i,j\in \{1,\ldots,p\}$, then 
% $$
% \P\left[\max_{j\in\{1,\ldots,p\}}\eta(j) \le u\right] \ge \P\left[\max_{j\in\{1,\ldots,p\}}z(j) \le u\right]
% $$
% for all $u\in\mathbb R$.
% \end{lemma}

### 2020-08-17 5.URS/5.proofs-URS-UDD.tex
add draft converted from thesis

In view of Remark \ref{rmk:choice-of-N(delta)}, UDD is equivalent to the requirement that
$N(\delta) := 1+\sup_{p} N_p(\delta) < \infty$ for all $\delta\in(0,1)$,
where 
\begin{equation} \label{eq:N_p(c)}
    N_p(\delta) := \max_{j\in\{1,\ldots,p\}} \Big|\{i:i\neq j,\;\Sigma_p(j,i) > \delta\}\Big|.
\end{equation}
Therefore, if ${\cal E}$ is not UDD, then there must exist a constant $c\in (0,1)$ for which $N(c)$ is infinite, i.e., there is a subsequence $\widetilde p\to\infty$ such that $N_{\widetilde p}(c) \to \infty$.
Without loss of generality,  we may assume that $\widetilde{p}=p$.

Let $j_p(c)$ be the maximizers of \eqref{eq:N_p(c)}, and let
\begin{equation} \label{eq:sub-sequence_of_sets}
S_p(c):= \{ i\in\{1,\dots,p\}\, :\, \Sigma_p(j_p(c), i) > c \}.% \quad\quad \text{for all }k\in S_p(c).
\end{equation}
Observe that $|S_p(c)| = N_p(c)+1 \to \infty$, as $p\to\infty$ 
(note $j_p(c) \in S_{p}(c)$).

Applying Lemma \ref{lemma:positive-correlation} to the set of random variables indexed by $S_p(c)$, we conclude, for $N_p(c) \ge 2^{2\lceil2/c^2\rceil+4}$, there must be a further subset 
\begin{equation} \label{eq:further_sub-sequence_of_sets}
  K_p(c) \subseteq S_p(c),
\end{equation}
of cardinality 
\begin{equation} \label{eq:further_sub-sequence_of_sets_size}
k_p(c) := \left|K_p(c)\right| \ge \log_2{\sqrt{N_p(c)}},
\end{equation}
such that all pairwise correlations of the random variables indexed by $K_p(c)$ are greater than $c^2/2$.
Since the sequence $N_p(c)\to\infty$, by \eqref{eq:further_sub-sequence_of_sets_size}, we have $k_p(c)\to\infty$ as $p\to\infty$.

Therefore, we have identified a sequence of subsets $K_p(c)\subseteq\{1,\ldots,p\}$ with the following two properties:
\begin{enumerate}
  \item $k_p(c) := \left|K_p(c)\right| \to \infty$, as $p\to\infty$, and
  \item For all $i,j\in K_p(c)$, we have
  \begin{equation} \label{eq:further_sub-sequence_of_sets_cor}
    \Sigma_p(i,j) > c^2/2.
  \end{equation}
\end{enumerate}
Without loss of generality, we may assume $K_p(c) = \{1,\ldots,k_p(c)\} \subseteq \{1,\ldots,p\}$, upon re-labeling of the coordinates.

Now consider a Gaussian sequence $\epsilon^* = \{\epsilon^*(j),\;j = 1,2,\ldots\}$, independent of ${\cal E}$, defined as follows:
$$
\epsilon^*(j):= Z \left(c/\sqrt{2}\right) + Z(j) \sqrt{1-{c^2}/{2}}, \quad j = 1, 2, \ldots,
$$ 
where $Z$ and $Z(j), j = 1, 2, \ldots$ are independent standard normal random variables. 
Hence,
\begin{equation} \label{eq:Slepian-conclusion-condition-1}
    {\rm Var}(\epsilon^*(j)) = 1 = {\rm Var}(\epsilon_p(j)),
\end{equation}
and
\begin{equation} \label{eq:Slepian-conclusion-condition-2}
    \cov(\epsilon^*(i),\epsilon^*(j)) = \frac{c^2}{2} \le \cov(\epsilon_p(i),\epsilon_p(j)),
\end{equation}
for all $p$, and all $i\neq j$, $i,j\in K_p(c)$.
Thus we have, as $p\to\infty$, 
\begin{equation} \label{eq:!UDD=>subsequence-fail}
    \frac{1}{u_{k_p(c)}} \max_{j\in K_p(c)} \epsilon^*(j) = \frac{c/\sqrt{2}}{u_{k_p(c)}}Z + \frac{\sqrt{1-c^2/2}}{u_{k_p(c)}} \max_{j\in K_p(c)} Z(j) \stackrel{\mathbb P}{\to} \sqrt{1-\frac{c^2}{2}},
\end{equation}
where the convergence in probability follows from Proposition \ref{prop:rapid-varying-tails} part \ref{prop:rapid-varying-tails_part-ii}.
%The fact that the last limit is strictly less than $1$, together with Relation \eqref{eq:Slepian-conclusion}, shows that \eqref{eq:URS-condition} is impossible, for $S_p:=K_p(c)$.

Relations \eqref{eq:Slepian-conclusion-condition-1} and \eqref{eq:Slepian-conclusion-condition-2}, by Slepian's Lemma \cite{slepian1962one}, also imply,
\begin{equation}\label{eq:Slepian-conclusion}
  \frac{1}{u_{k_p(c)}} \max_{j\in K_p(c)} \epsilon^*(j) \stackrel{d}{\ge} \frac{1}{u_{k_p(c)}} \max_{j\in K_p(c)} \epsilon_p(j).
\end{equation}
Therefore, by \eqref{eq:Slepian-conclusion} and \eqref{eq:!UDD=>subsequence-fail}, for all $\sqrt{1-c^2/2} \le \delta < 1$, we have,
$$
\P\left[\frac{1}{u_{k_p(c)}} \max_{j\in K_p(c)} \epsilon_p(j) < \delta \right] \to 1 \quad\mbox{as  }p\to\infty.
$$
This contradicts the definition of URS (with the particular choice of $S_p:=K_p(c)$), and the proof of the `only if' part is complete.

### 2020-08-17 5.URS/URS.tex
add draft converted from thesis

In this chapter, we establish a complete characterization of URS for Gaussian arrays in terms of a simple condition on the covariance structures.
The condition is as follows.

% The proof of the main result is deferred until Section \ref{sec:proofs}.

% We define the class of dependence structures, referred to as uniformly decreasing dependence (UDD), for Gaussian arrays via their covariance matrices.

\begin{definition}[Uniformly decreasing dependence (UDD)] \label{def:UDD}
Consider a triangular array of jointly Gaussian distributed errors 
${\cal E} = \left\{\left(\epsilon_p(i)\right)_{i=1}^p, p = 1,2,\ldots\right\}$ 
with unit variances,
$$
\epsilon_p \sim \text{N}(0, \Sigma_p), \quad p=1,2,\ldots.
$$
The array ${\cal E}$ is said to be uniform decreasingly dependent (UDD) if 
for every $\delta>0$ there exists a finite $N(\delta)<\infty$, such that for every $i\in\{1,\ldots,p\}$, and $p\in\N$, we have
\begin{equation} \label{eq:UDD-definition}
    \Big|\left\{k\in\{1,\ldots,p\}:\Sigma_p(i,k)>\delta\right\}\Big| \le N(\delta)\quad \text{for all  } \delta>0.
\end{equation}
\end{definition}
That is, for every coordinate $i$, the number of elements which are more than $\delta$-correlated with $\epsilon_p(i)$ does not exceed $N(\delta)$.

Note that the bound in \eqref{eq:UDD-definition} holds uniformly in $i$ and $p$, and only depends on $\delta$.
Also observe that on the left-hand side of \eqref{eq:UDD-definition}, we merely count in each row of $\Sigma_p$ the number of exceedances of covariances (not their absolute values!) over level $\delta$.

\begin{remark} \label{rmk:choice-of-N(delta)}
Without loss of generality, we may require that $N(\delta)$ be a monotone non-increasing function of $\delta$, for we can take
$$
N(\delta) = \sup_{p,i} \Big|\{k:\Sigma_p(i,k)>\delta\}\Big|,
$$
which is non-increasing in $\delta$.
Definition \ref{def:UDD} therefore states that the array is UDD when $N(\delta)<\infty$ for all $\delta>0$.
\end{remark}

Observe that the UDD condition does not depend on the order of the coordinates in the error 
vector $\epsilon_p = (\epsilon_p(i))_{i=1}^p$.  Often times, however, the errors are thought of 
coming from a stochastic process indexed by time or space.  To illustrate the generality of the 
UDD condition, we formulate next a simple sufficient condition (UDD$^\prime$) that is easier to 
check in a time-series context.

\begin{definition}[UDD\,$^\prime$]\label{d:UDD-prime}
For $\epsilon_p \sim \mathrm{N}(0,\Sigma_p)$ with unit variances, an array ${\cal E} = \left(\epsilon_p(i)\right)_{i=1}^p$ is said to satisfy the UDD\,$^\prime$ condition if there 
exist:
\begin{enumerate}
    \item[(i)] permutations $l = l_p$ of $\{1,\ldots,p\}$, for all $p\in\N$, and
    \item[(ii)] a non-negative sequence $(r_n)_{n=1}^\infty$ converging to zero $r_n\to 0$, as $n\to\infty$,
\end{enumerate}
such that 
\begin{equation} \label{eq:weak-correlation}
    \sup_{p\in\N} |\Sigma_p\left(i',j'\right)| \le r_{|i-j|}.
\end{equation}
where $i' = l(i)$, $j' = l(j)$, for all $i,j\in\{1,\ldots,p\}$.
\end{definition}

\begin{remark}
Without loss of generality, we may also require that $r_n$ be non-increasing in $n$, for we can replace $r_n$ with the non-increasing sequence $r'_n = \sup_{m\ge n} r_m$.
\end{remark}

\begin{proposition} \label{prop:UDD-equivalent}
UDD\,$^\prime$ implies UDD.
\end{proposition}

\begin{proof}%[Proof of Proposition \ref{prop:UDD-equivalent}]
%The functions $N(\delta)$ and $r(n)=r_n$ are inverses of each other.
% {\bf $\text{UDD} \implies \text{UDD'}$:}
% If $N(0)<\infty$, then we can take 
% $$
% r_n = \underbrace{1, \ldots, 1}_{\lfloor N(0)/2\rfloor + 1}, 0, 0, \ldots.
% $$
% and recursively construct the permutations as follows.
% Start with any element

% We proof the contrapositive. 
% Suppose for all permutations and any sequence $r_n\to0$, there exists $i,j$ such that $\Sigma(i',j')>r_{|i'-j'|}$,
% then for any $\delta>0$ and any finite $M<\infty$, we can take $r_n$ to be a sequence of $M$ 1's followed by a $\delta$, i.e., 
% $$
% r_n = \underbrace{1, \ldots, 1}_{M+1}, \delta, \ldots.
% $$
% \fbox{Not true:}
% However, since there exists $i',j'$ such that $\Sigma(i',j')>r_{|i'-j'|}$, the set 
% $$
% S = l^{-1}\left(\left\{j',i'-N,\ldots,i'-1,i',i'+1,\ldots,i'+N\right\}\right)
% $$

% {\bf $\text{UDD'} \implies \text{UDD}$:} 
Since $r_n\to 0$, for any $\delta > 0$, there exists an integer 
$M = M(\delta)<\infty$ such that $r_n\le\delta$, for all $n\ge M$. 
Thus, by \eqref{eq:weak-correlation}, for every fixed 
$j' \in\{1,\ldots,p\}$, we can have $|\cov(\epsilon_p(k'),\epsilon_p(j'))| > \delta$,
only if $k'$ belongs to the set:
$$ 
 \left\{ k' \in \{1,\dots,p\} \, :\, j-M \le  k := l_p^{-1}(k') \le j+M \right\},
$$
where $j:= l_p^{-1}(j')$. That is, there are at most $2M+1<\infty$ indices  $k'\in\{1,\dots,p\}$, whose covariances with $\epsilon(j')$ may exceed $\delta$. 
Since this holds uniformly in $j'\in\{1,\ldots,p\}$, Condition UDD follows with 
$N(\delta) = 2M+1$.
\end{proof}

% \begin{definition}[Uniformly decreasing dependence (UDD)] \label{def:weak-dependence}
% Consider a triangular array of jointly Gaussian distributed errors $\left(\epsilon_p(j)\right)_{j=1}^p$ with unit variances, $\epsilon_p \sim \mathcal N(0,\Sigma_p)$. The array ${\cal E}$ is said to be uniform decreasingly dependent (UDD) with rate $(r_n)_{n=1}^\infty$ if 
% \begin{equation} \label{eq:weak-correlation}
%     \sup_p |\Sigma_p(i,j)| \le r_{|i-j|}
% \end{equation}
% such that $r_n\to 0$, as $n\to\infty$.
% \end{definition}
% 
% \begin{remark} \label{rmk:UDD-equivalent}
% In situations where there is no natural ordering of the components, it is sufficient that a permutation of the vector $\epsilon$ in its coordinates satisfy the requirements above. 
% In fact, the UDD condition can be equivalently stated as follows: for any $\delta>0$, and any coordinate $j\in\{1,\ldots,p\}$, there are at most $N(\delta)<\infty$ coordinates whose covariances with $\epsilon(j)$ exceed $\delta$; here $N(\delta)$ is a deterministic function independent of $p$.
% $N(\delta) \to 1$ as $\delta \to 0$.
% \end{remark}

We now state the main result of this section: a Gaussian sequence is URS if and only if it is UDD.
The URS condition essentially requires that the dependencies decay in a uniform fashion, the rate at which dependence decay does \emph{not} matter.

\begin{theorem} \label{thm:Gaussian-weak-dependence}
Let ${\cal E}$ be a Gaussian triangular array with standard normal marginals.  
The array ${\cal E}$ has uniformly relatively stable (URS) maxima if and only if it is uniformly decreasing dependent (UDD).
\end{theorem}

% The proof of Theorem \ref{thm:Gaussian-weak-dependence} is given in Section \ref{sec:proofs}.

Specifically, for stationary Gaussian arrays, we have the following corollary.

\begin{corollary} \label{cor:stationary-Gaussian-errors}
Let ${\cal E} = \{\epsilon_p(i) = Z(i)\}$ for a stationary Gaussian time series ${\cal Z} = \{Z(i)\}$.
Then $\cal E$ is {URS} if and only if the autocovariance function $\cov(Z(k), Z(0))\to 0$, as $k\to\infty$.
\end{corollary}

Corollary \ref{cor:stationary-Gaussian-errors} follows by Theorem \ref{thm:Gaussian-weak-dependence} and the observation that UDD is equivalent to vanishing autocovariance of $\cal Z$.
A slightly weaker form of the ``if'' part was established in Theorem 3 of \cite{berman1964limit}.

Returning again to the study of support recovery problems, Theorem \ref{thm:Gaussian-weak-dependence} and the necessary condition for exact support recovery in Theorem \ref{thm:necessary} yields the following result.

\begin{corollary} \label{cor:weakly-dependent-errors}
For UDD Gaussian errors, the result in Theorem \ref{thm:necessary} holds.
\end{corollary}

As a counterpart to Remark \ref{rmk:dependence-assumptions}, we demonstrate the tightness of the dependence conditions in Theorem \ref{thm:necessary}.
Specifically, we demonstrate that if the URS dependence condition is violated, then it may be possible to recover the support of weaker signals below the boundary.

\begin{example} \label{exmp:counter-example}
Suppose ${\cal E} = \left(\epsilon_p(i)\right)_{i=1}^p$ is Gaussian, and is comprised of $\lfloor p^{1-\beta}\rfloor$ blocks, each of size at least $\lfloor p^\beta \rfloor$; 
let the elements of each block have correlation 1, and let elements from different blocks be independent. 
If $\underline{r} \ge 4(1-\beta)$, then the procedure $\widehat{S} = \big\{i:x(i)>\sqrt{2(1-\beta)\log{p}}\big\}$ yields $\mathbb P[\widehat{S} = S] \to 1$. 
This requirement on signal size is strictly weaker than that of the strong classification boundary, since $4(1-\beta) < (1 + \sqrt{1-\beta})^2$ on $\beta\in(0,1)$.
\end{example}

The above example shows that if the correlations of the Gaussian errors do not decay in a uniform fashion (UDD fails), then we can do substantially better in terms of support recovery.
The claims in the example are verified in Section \ref{suppsec:proofs}, while numerical simulations of this example can be found in Section \ref{suppsec:numerical}.

\medskip

We conclude with a brief discussion on the relationships between UDD and other dependence conditions in the context of extreme value theory, before proceeding to the proof of Theorem \ref{thm:Gaussian-weak-dependence}.

Suppose that the array of errors  ${\cal E}$ comes from a stationary Gaussian time series $\epsilon(i),\ i\in \mathbb{N}$, with auto-covariance $r_p=\cov(\epsilon(i+p),\epsilon(i))$. 
One is interested in the asymptotic behavior of the maxima $M_p:=\max_{i=1,\dots,p} \epsilon(i)$.

In this setting, the Berman's condition, introduced in \cite{berman1964limit}, requires that
\begin{equation} \label{eq:Berman}
    r_p \log p \to 0,\ \ \mbox{ as }p\to\infty.
\end{equation}
This condition entails that 
\begin{equation}
    \label{eq:Gauss-max-in-distribution}
  a_p (M_p - b_p) \stackrel{d}{\longrightarrow } Z,\  \ \mbox{ as }p\to\infty,
\end{equation}
with the Gumbel limit distribution $\mathbb P [Z\le x] = \exp\{-e^{-x}\},\ x\in \mathbb R$, 
where 
$$
a_p = \sqrt{2\log p},\quad b_p  = \sqrt{2\log p} - \frac{1}{2}\left(\sqrt{2\log p}\right)^{-1}\left(\log \log (p) + \log(4\pi)\right),
$$ 
are {\em the same} centering and normalization sequences
as in the case of iid $\epsilon(i)$'s.  
Berman's condition is one of the weakest dependence conditions  in the literature for which this result holds. See, e.g., Theorem 4.4.8 in \cite{embrechts2013modelling}, where \eqref{eq:Berman} is described as ``very weak''.

For dependence conditions weaker than \eqref{eq:Berman}, the sequences of normalizing and centering constants in \eqref{eq:Gauss-max-in-distribution} are {\em different} from the iid case, and the corresponding limit is no longer Gumbel; see, for example, Theorems 6.5.1 and  6.6.4 in \cite{leadbetter2012extremes}, and \cite{mccormick1976weak}. 
% In particular, \cite{mccormick1976weak} derived the normalizing constants when both $r_p\to 0$ monotonically and  $r_p \log p \to \infty$ monotonically, as $p\to\infty$. 
% In this case, convergence in distribution still takes place, with the maxima concentrating along a sequence asymptotic to \eqref{eq:quantiles}.

On the other hand, in our high dimensional support estimation context, the notion of relative stability is sufficient and more natural than the finer notions of distributional convergence.
If one is merely interested in the asymptotic relative stability of the Gaussian maxima, then Berman's condition can be relaxed significantly (see also, Theorem 4.1 of \cite{berman1964limit}). 
Observe that by Proposition \ref{prop:UDD-equivalent},  the Berman condition \eqref{eq:Berman} implies UDD and hence relative stability (Theorem \ref{thm:Gaussian-weak-dependence}), i.e., 
\begin{equation} \label{eq:Gaussian-URS}
  \frac{1}{b_p} M_p \stackrel{\mathbb P}{\to} 1,\quad\mbox{as}\quad p\to\infty.
\end{equation}
This {\em concentration of maxima} property can be readily deduced from \eqref{eq:Gauss-max-in-distribution}, since $a_p b_p \sim 2\log(p) \to \infty$ as $p\to\infty$.
Theorem \ref{thm:Gaussian-weak-dependence} shows that \eqref{eq:Gaussian-URS} holds if the much weaker uniform dependence condition UDD holds. 
Note that our condition is coordinate free --- neither monotonicity of the sequence $r_p$ nor stationarity of the underlying array is required.

% The method of proof is also very different from the results on distributional convergence in the references mentioned above.

\medskip

The rest of this chapter is devoted to the proof of the main result, i.e., Theorem \ref{thm:Gaussian-weak-dependence}. 
We first introduce a key lemma regarding the structure of correlation matrix of high-dimensional random variables.
The proof uses a surprising, yet elegant application of Ramsey's Theorem from the study of combinatorics.
%; this application, and its consequences in high-dimensional probability, are presented in Section \ref{subsec:Ramsey}.
The `only if' part of Theorem \ref{thm:Gaussian-weak-dependence} follows from this lemma, in Section \ref{sec:URS=>UDD}.

The proof of the `if' part is detailed in Section \ref{sec:UDD=>URS}.
The arguments there was recently extended to establish bounds on the rate of concentration of maxima in \cite{kartsioukas2019rate}; see also, \cite{tanguy2015some} and references therein for related work on this topic.

\section{Ramsey's Coloring theorem and structure of correlation matrices} 
\label{sec:Ramsey}
\input{5.URS/5.proofs-Ramsey.tex}

\section{URS implies UDD (`only if' part of Theorem \ref{thm:Gaussian-weak-dependence})} 
\label{sec:URS=>UDD}
\input{5.URS/5.proofs-URS-UDD.tex}

\section{UDD implies URS (`if' part of Theorem \ref{thm:Gaussian-weak-dependence})} 
\label{sec:UDD=>URS}
\input{5.URS/5.proofs-UDD-URS.tex}

\section{Numerical illustrations of exact support recovery under dependence}
\label{sec:URS-numerical}
\input{5.URS/5.numerical.tex}

### 2020-08-17 6.GWAS/6.GWAS-phase-transitions.tex
add draft converted from thesis

% Specifically, we develop recipes to find suitable designs of association studies such that combination of the dimensionality $p$, sparsity $\beta$, and signal sizes $r$ of the problem lands in the desired region of risk control, as predicted by the results in Section \ref{sec:chisq-boundaries}.

% Of course, in applications, not all three of the parameters $(p, \beta, r)$ can be altered as we wish.
% In particular, the problem dimensions and sparsity levels are usually determined by the underlying physical processes.
% In the GWAS example, the number of genomic marker locations is determined by the chip used for gene sequencing, while the number of relevant genomic locations is a consequence of the biological process.
% Therefore, in order to achieve a desired level of error control, we can often only hope to influence the statistical signal sizes.

Returning to the problem of \emph{high-dimensional} marginal screenings for categorical covariates, we explore the manifestation of the phase transition in the exact-approximate support recovery problem in the genetic context.

Recall Theorem \ref{thm:chi-squared-exact-approx-boundary} predicts that FWER and FNR can be simultaneously controlled in large dimensions if and only if 
\begin{equation}
    r = \frac{\lambda}{2\log{p}} = \frac{w^2n}{2\log{p}} > 1.
\end{equation}
Therefore, if we were to apply FWER-controlling procedures at low nominal levels (say, $5\%$), then the FNR would experience a phase transition in the sense that, if
\begin{equation} \label{eq:power-1-region}
    r>1 \iff w^2 > \frac{2\log{p}}{n},
\end{equation}
then the FNR can be close to 0; otherwise, FNR must be close to 1.

% Translating this result into the language of association tests, 
Using the parametric relationship described in Corollary \ref{cor:signal-size-odds-ratio-conditional-frequency} (and Proposition \ref{prop:signal-size-odds-ratio}), 
the inequalities in \eqref{eq:power-1-region} implicitly define regions of $(f, R)$ where associations are discoverable with high power, for a given $\phi_1$.
Further, the boundary of such discoverable regions sharpens as dimensionality diverges. 
We illustrate this phase transition through a numerical example next.

\begin{figure}
      \centering
      \includegraphics[width=0.49\textwidth]{OR-RAF_plots/OR-RAF_p4.png} \includegraphics[width=0.49\textwidth]{OR-RAF_plots/OR-RAF_p1e2.png} \includegraphics[width=0.49\textwidth]{OR-RAF_plots/OR-RAF_p1e6.png} \includegraphics[width=0.49\textwidth]{OR-RAF_plots/OR-RAF_BC_study.png}
      \caption{The OR-RAF diagram visualizing the marginal power of discovery in genetic association studies, after applying Bonferroni's procedure with nominal FWER at $5\%$ level. Sample sizes are marked in each panel, and the problem dimensions are, respectively, $p=4$ (upper-left), $p=10^2$ (upper-right), and $p=10^6$ (lower-left), so that $n/\log{p}$ are roughly constant. Red curves mark the boundaries ($r=1$) of the phase transition for the exact-approximate support recovery problem; dashed curves are the equi-signal (equi-power) curves. The phase transition in signal sizes $\lambda$ translates into the phase transition in terms of $(f,R)$, and sharpens as $p\to\infty$; see Example \ref{exmp:OR-RAF_phase_transition}. In the lower-right panel, we visualize discovered associations (blue circles) in a recent GWA study (Michailidou et al. (2017)); the estimated odds ratios and risk allele frequencies are subject to survival bias and should not be taken at their face values; see Remark \ref{rmk:OR-RAF_false_evidence}.
      } 
      \label{fig:OR-RAF_GWAS}
\end{figure}

\begin{example}
\label{exmp:OR-RAF_phase_transition}
Consider association tests on $2\times2$ contingency tables at $p$ locations as introduced in Section \ref{sec:motivation-chisq}, where the counts follow 
a multinomial distribution
% independent binomial distributions 
% $$
% O_{11} \sim \mathrm{Binom}(n\phi_1, fR/(fR+1-f)),\quad 
% O_{21} \sim \mathrm{Binom}(n(1-\phi_1), fR/(fR+1-f)),
% $$
parametrized by $(f, R, \phi_1)$ as in Section \ref{sec:optimal-design}.
Assume that the phenotype marginals are fixed at $\phi_1 = \phi_2 = 1/2$.
% --- as is the case in genetic association studies --- 
Applying Bonferroni's procedure with nominal FWER at $\alpha=5\%$ level, we can approximate the marginal power of association tests by
\begin{equation} \label{eq:power-approximation}
    \P[\chi^2_{1}(\lambda)>\chi^2_{1,\alpha/p}],
\end{equation}
where $\chi^2_{1,\alpha/p}$ is the upper $(\alpha/p)$-quantile of a central chi-squared distribution with 1 degree of freedom.
We calculate this marginal power as a function of the parameters $(f,R)$ in three scenarios:
\begin{itemize}
    \item $p=4$, $n=3\times10^4$ 
    \item $p=10^2$, $n=1\times10^5$
    \item $p=10^6$, $n=3\times10^6$
\end{itemize}
and visualize the results as heatmaps\footnote{Since genetic variants can always be relabelled such that Variant 1 is positively associated with Cases, we only produce part of the diagram where $R>1$.
Sample sizes marked in the figure are adjusted by a factor of $1/2$, to reflect the genetic context where a pair of alleles are measured for every individual at every genomic location.} (referred to as OR-RAF diagrams) in Figure \ref{fig:OR-RAF_GWAS}.
These parameter values are chosen so that $\log{p}/n$ are roughly constant (around $4.6\times10^{-5}$).

We also overlay ``equi-signal'' curves, i.e., functions implicitly defined by the equations $r=c$ for a range of $c$ (dashed curves), and highlight the predicted boundary of phase transition for the exact-approximate support recovery problem $r=1$ (red curves).
The change in marginal power clearly sharpens around the predicted boundary $r=1$ as dimensionality diverges.
\end{example}

% --- or equivalently, the marginal power ---

\begin{remark}
\label{rmk:OR-RAF_false_evidence}
In an attempt to find empirical evidence of our theoretical predictions, we chart the genetic variants associated with breast cancer, discovered in a 2017 study by \citet{michailidou2017association} in an OR-RAF diagram. 
The estimated risk allele frequencies ($f$) and odds ratios ($R$) are taken from the NHGRI-EBI GWAS catalog \cite{macarthur2016new}, and plotted against a power heatmap calculated according to the reported sample sizes. 
See lower-right panel of Figure \ref{fig:OR-RAF_GWAS}.

It is tempting to believe, on careless inspection, that roughly \emph{all} discovered associations fall inside the high power region of the diagram, therefore demonstrating the phase transition in statistical power.
Unfortunately, the estimates here are subject to survival {bias} --- the study in fact uses the {same} dataset for \emph{both} support estimation and parameter estimation, without adjusting the latter for the selection process.
The seemingly striking agreement between the power calculations and the estimated effects of reported associations \emph{should not} be taken as evidence for the validity of our theory.
We conjecture, as the theory predicts, that accurate and unbiased parameter estimates from an independent replication will still place the associations in the high power region of the diagram. 
\end{remark}

Finally, we demonstrate with an example how results in Sections \ref{sec:chisq-boundaries} and \ref{sec:odds-and-power} may be used for planning prospective association studies.

\begin{example}
In a GWAS with $p = 10^6$ genomic marker locations, researchers wish to locate genetic associations with the trait of interest.
Specifically, they wish to maximize power in the region where genetic variants have risk allele frequencies of $0.01$ and odds ratios of $1.2$.
By Corollary \ref{cor:optimal-design}, the optimal design has a fraction of cases $\phi^* = 0.478$, yielding the statistical signal size per sample $w^2\approx9.00\times10^{-5}$ according to Corollary \ref{cor:signal-size-odds-ratio-conditional-frequency}.

If we wish to achieve exact-approximate support recovery in the sense of \eqref{eq:support-recovery-success}, Theorem \ref{thm:chi-squared-exact-approx-boundary} predicts that the signal size parameter $r$ has to be at least $\widetilde{g}(\beta)= 1$.
This signal size calls for a sample size of $n = \lambda / w^2 = 2r\log(p)/w^2 \approx 307,011$.
In a typically GWAS, a pair of alleles are sequenced for every marker location, bringing the required number of subjects in the study to $n/2 \approx 153,509$.
\end{example}

In comparison, a more accurate power calculation directly using \eqref{eq:power-approximation} predicts that $n / 2 = 165,035$ subjects are needed, under the set of parameters ($p=10^6$, $f=0.01$, $R=1.2$) and $\mathrm{FWER}=0.05$, $\mathrm{FNR}=0.5$; this is $7\%$ higher than our crude asymptotic approximation.
% The accuracy of the asymptotic approximations, by nature of the statements in Theorem \ref{thm:chi-squared-exact-boundary} and \ref{thm:chi-squared-approx-boundary}, depends on how close the error metrics are to zero.
% For example, the number of subjects needed for $\mathrm{FWER}=\mathrm{FWNR}=0.01$ is $499,598$, an $8\%$ increase over the asymptotic prediction; at $\mathrm{FWER}=\mathrm{FWNR}=0.1$, this number becomes $398,996$, some $14\%$ lower than the asymptotic result.
In general, we recommend using the more precise calculations over the back-of-the-envelope asymptotics for planning prospective studies and performing systematic reviews;
a user-friendly web application implementing the more precise approximations is provided in \cite{gao2019upass}.
Nevertheless, the theoretical results on phase transitions generate simple, accurate, and powerful insights that cannot be easily derived from numerical calculations.

### 2020-08-17 6.GWAS/6.chi-square-distributions.tex
add draft converted from thesis

We shall recall, and establish, some auxiliary facts about chi-square distributions. 
These facts will be used in the proofs of Theorem \ref{thm:chi-squared-exact-boundary} and Theorem \ref{thm:chi-squared-approx-boundary}.

\begin{lemma}[Rapid variation of chi-square distribution tails] \label{lemma:rapid-variation-chisq}
The central chi-square distribution with $\nu$ degrees of freedom has rapidly varying tails.
That is, 
\begin{equation} \label{eq:rapid-variation-chisq}
    \lim_{x\to\infty}\frac{\P[\chi_\nu^2(0)>tx]}{\P[\chi_\nu^2(0)>x]} = 
    \begin{cases}
    0, & t > 1 \\
    1, & t = 1 \\
    \infty, & 0 < t < 1
\end{cases},
\end{equation}
where we overloaded the notation $\chi_\nu^2(0)$ to represent a random variable with the chi-square distribution.
\end{lemma}

\begin{proof}[Proof of Lemma \ref{lemma:rapid-variation-chisq}]
When $\nu=1$, the chi-square distribution reduces to a squared Normal, and \eqref{eq:rapid-variation-chisq} follows from the rapid variation of the standard Normal distribution.
For $\nu\ge2$, we recall the following bound on tail probabilities (see, e.g., \citep{inglot2010inequalities}),
$$
\frac{1}{2}\mathcal{E}_\nu(x) \le \P[\chi_\nu^2(0)>x] \le \frac{x}{(x-\nu+2)\sqrt{\pi}} \mathcal{E}_\nu(x), \quad \nu\ge2,\;x>\nu-2,
$$
where $\mathcal{E}_\nu(x) = \exp\left\{-\frac{1}{2}[(x-\nu-(\nu-2)\log(x/\nu) + \log\nu]\right\}$.
Therefore, we have 
$$
\frac{(x-\nu+2)\sqrt{\pi}}{2x}\frac{\mathcal{E}_\nu(tx)}{\mathcal{E}_\nu(x)} 
\le \frac{\P[\chi_\nu^2(0)>tx]}{\P[\chi_\nu^2(0)>x]}
\le \frac{2tx}{(tx-\nu+2)\sqrt{\pi}}\frac{\mathcal{E}_\nu(tx)}{\mathcal{E}_\nu(x)},
$$
where ${\mathcal{E}_\nu(tx)}/{\mathcal{E}_\nu(x)} = \exp\{-\frac{1}{2}[(t-1)x-(\nu-2)\log{t}]\}$ converges to $0$ or $\infty$ depending on whether $t>1$ or $0<t<1$.
The case where $t=1$ is trivial.
\end{proof}

Lemma \ref{lemma:rapid-variation-chisq} and Proposition \ref{prop:rapid-varying-tails} yield the following Corollary.

\begin{corollary} \label{cor:relative-stability}
Maxima of independent observations from central chi-square distributions with $\nu$ degrees of freedom are relatively stable. 
Specifically, let $\epsilon_p = \left(\epsilon_p(i)\right)_{i=1}^p$ be independently and identically distributed (iid) $\chi_\nu^2(0)$ random variables. 
Then the triangular array ${\cal E} = \{\epsilon_p, p\in\N\}$ has relatively stable (RS) maxima in the sense of \eqref{eq:RS-condition}.
\end{corollary}

\begin{lemma}[Stochastic monotonicity] \label{lemma:stochastic-monotonicity}
The non-central chi-square distribution is stochastically monotone in its non-centrality parameter.
Specifically, for two non-central chi-square distributions both with $\nu$ degrees of freedom, and non-centrality parameters $\lambda_1 \le \lambda_2$, we have $\chi^2_\nu(\lambda_1) \stackrel{\mathrm{d}}{\le} \chi^2_\nu(\lambda_2)$. 
That is,
\begin{equation} \label{eq:stochastic-monotonicity}
    \P[\chi^2_\nu(\lambda_1) \le t] \ge \P[\chi^2_\nu(\lambda_2) \le t], \quad \text{for any}\quad t\ge0.
\end{equation}
where we overloaded the notation $\chi_\nu^2(\lambda)$ to represent a random variable with the chi-square distribution with non-centrality parameter $\lambda$ and degree-of-freedom parameter $\nu$.
\end{lemma}

\begin{proof}[Proof of Lemma \ref{lemma:stochastic-monotonicity}]
Recall that non-central chi-square distributions can be written as sums of $\nu-1$ standard normal random variables and a non-central normal random variable with mean $\sqrt{\lambda}$ and variance 1,
\begin{equation*}
    \chi_\nu^2(\lambda) 
    \stackrel{\mathrm{d}}{=} Z_1^2 + \ldots + Z_{\nu-1}^2 + (Z_\nu + \sqrt{\lambda})^2.
\end{equation*}
Therefore, it suffices to show that $\P[(Z+\sqrt{\lambda})^2 \le t]$ is non-increasing in $\lambda$ for any $t\ge0$, where $Z$ is a standard normal random variable.
We rewrite this expression in terms of standard normal probability function $\Phi$,
\begin{align}
    \P[(Z+\sqrt{\lambda})^2 \le t] 
    &= \P[-\sqrt{\lambda} - \sqrt{t} \le Z \le -\sqrt{\lambda} + \sqrt{t}] \nonumber \\
    &= \Phi(-\sqrt{\lambda} + \sqrt{t}) - \Phi(-\sqrt{\lambda} - \sqrt{t}). \label{eq:stochastic-monotonicity-proof-1}
\end{align}
The derivative of the last expression (with respect to $\lambda$) is 
\begin{equation} \label{eq:stochastic-monotonicity-proof-2}
    \frac{1}{2\sqrt{\lambda}} \left(\phi(\sqrt{\lambda} + \sqrt{t}) - \phi(\sqrt{\lambda} - \sqrt{t})\right) 
    = \frac{1}{2\sqrt{\lambda}} \left(\phi(\sqrt{\lambda} + \sqrt{t}) - \phi(\sqrt{t} - \sqrt{\lambda})\right),
\end{equation}
where $\phi$ is the density of the standard normal distribution.
Notice that we have used the symmetry of $\phi$ around 0 in the last expression.

Since $0 \le \max\{\sqrt{\lambda} - \sqrt{t}, \sqrt{t} - \sqrt{\lambda}\} < \sqrt{t} + \sqrt{\lambda}$ when $t>0$, by monotonicity of the normal density on $(0,\infty)$, we conclude that the derivative \eqref{eq:stochastic-monotonicity-proof-2} is indeed negative.
Therefore, \eqref{eq:stochastic-monotonicity-proof-1} is decreasing in $\lambda$, and \eqref{eq:stochastic-monotonicity} follows for $t>0$.
For $t = 0$, equality holds in \eqref{eq:stochastic-monotonicity} with both probabilities being 0.
\end{proof}

Finally, we derive asymptotic expressions for  chi-square quantiles.

\begin{lemma}[Chi-square quantiles] \label{lemma:chisq-quantiles}
Let $F$ be the central chi-square distributions with $\nu$ degrees of freedom, and let $u(y)$ be the $(1-y)$-th generalized quantile of $F$, i.e.,
\begin{equation} \label{eq:quantiles-generic}
    u(y) = F^\leftarrow(1 - y).
\end{equation}
Then 
\begin{equation}
    u(y) \sim 2\log(1/y), \quad \text{as }y\to0. 
\end{equation}
\end{lemma}

\begin{proof}[Proof of Lemma \ref{lemma:chisq-quantiles}]
The case where $\nu=1$ follows from the well-known formula for Normal quantiles (see, e.g., Proposition 1.1 in \cite{gao2018fundamental})
$$
F^\leftarrow(1 - y) = \Phi^\leftarrow(1-y/2)\sim\sqrt{2\log{(2/y)}}\sim\sqrt{2\log{(1/y)}}.
$$
The case where $\nu\ge2$ follows from the following estimates of high quantiles of chi-square distributions (see, e.g., \citep{inglot2010inequalities}),
$$
    \nu +  2\log(1/y) -5/2 \le u(y) \le \nu +  2\log(1/y) + 2\sqrt{\nu\log(1/y)}, \quad \text{for all }y\le0.17,
$$
where both the lower and upper bound are asymptotic to $2\log(1/y)$.
\end{proof}

### 2020-08-17 6.GWAS/6.chi-square.tex
add draft converted from thesis

Similar to the analysis of additive error models in Chapter \ref{chap:phase-transitions}, we will work with triangular arrays of chi-square models \eqref{eq:model-chisq} indexed by $p$.
We adopt the same parametrization for the sparsity of the non-centrality parameter vectors $\lambda = \lambda_p$,
\begin{equation} \label{eq:signal-sparsity}
    |S_p| = \left\lfloor p^{1-\beta} \right\rfloor, \quad \beta\in(0,1]
\end{equation}
where $\beta$ parametrizes the problem sparsity.
The closer $\beta$ is to 1, the sparser the support $S_p$; conversely, when $\beta$ is close to 0, the support is dense with many non-null signals.

We parametrize the range of the non-zero and perhaps unequal signals in the chi-square model with
\begin{equation} \label{eq:signal-size}
    \underline{\Delta} = 2\underline{r}\log{p}
    \le \lambda(i) \le
    \overline{\Delta} = 2\overline{r}\log{p}, \quad \text{for all}\;\;i\in S_p,
\end{equation}
for some constants $0<\underline{r}\le\overline{r}\le+\infty$.

\subsection{The exact support recovery problem}
\label{subsec:exact-support-recovery-chisq}

The first main result characterizes the phase transition phenomenon in the exact support recovery problem under the chi-square model.

\begin{theorem} \label{thm:chi-squared-exact-boundary}
Consider the high-dimensional chi-squared model \eqref{eq:model-chisq} with signal sparsity and size as described in \eqref{eq:signal-sparsity} and \eqref{eq:signal-size}.
The function 
\begin{equation} \label{eq:exact-boundary-chisquared}
    g(\beta) = \left(1 + \sqrt{1-\beta}\right)^2
\end{equation}
characterizes the phase transition of exact support recovery problem.
Specifically, if $\underline{r} > {{g}}(\beta)$, then Bonferroni's, Sid\'ak's, Holm's, and Hochberg's procedures with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FWER levels all achieve asymptotically exact support recovery in the sense of \eqref{eq:support-recovery-success}.

Conversely, if $\overline{r} < {{g}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, we have $\P[\widehat{S}_p=S_p]\to0$.
Therefore, in view of Lemma \ref{lemma:risk-exact-recovery-probability}, exact support recovery asymptotically fails for all thresholding procedures in the sense of \eqref{eq:support-recovery-failure}.
\end{theorem}

% \begin{figure}
%   \begin{center}
%     \includegraphics[width=0.7\textwidth]{./pics/phase_diagram_chisquared_ALL_boundaries.eps}
%   \end{center}
%    \caption{The phase diagram for the high-dimensional chi-square model \eqref{eq:model-chisq}, illustrating the boundaries of the exact support recovery (FWER + FWNR; top curve; Theorem \ref{thm:chi-squared-exact-boundary}), the approximate-exact support recovery (FDR + FWNR; second curve from top; Theorem \ref{thm:chi-squared-approx-exact-boundary}), the exact-approximate support recovery (FWER + FNR; horizontal line $r=1$; Theorem \ref{thm:chi-squared-exact-approx-boundary}), and the approximate support recovery problems (FDR + FNR; tilted line $r=\beta$; Theorem \ref{thm:chi-squared-approx-boundary}). The signal detection problem (type I + type II errors of the global test; lower curve) was studied in Donoho and Jin (2004). In each region of the diagram and above, the annotated statistical risk can be made to vanish, as dimension $p$ diverges. Conversely, the risks has liminf at least one. All boundaries are unaffected by the degree-of-freedom. All boundaries are identical to those in the Gaussian additive error model \eqref{eq:model-additive} under one-side alternatives; c.f., results in Section \ref{sec:additive-error-model-boundaries}.}
%    \label{fig:phase-chi-squared}
% \end{figure}

The procedures listed in Theorem \ref{thm:chi-squared-exact-boundary} were reviewed in Section \ref{sec:statistical-procedures}. 
Proof of the theorem can be found in Section \ref{subsec:proof-chi-squared-exact-boundary}. 
% The boundary \eqref{eq:exact-boundary-chisquared} is plotted in Figure \ref{fig:phase-chi-squared}.

It is evident that the exact support recovery boundary \eqref{eq:exact-boundary-chisquared} coincides with that in parallel results for the Gaussian additive error models \eqref{eq:model-additive} in Chapter \ref{chap:phase-transitions}.
Implications of these results will be discussed in Section \ref{subsec:one-vs-two-sided} below.

\begin{remark} \label{rmk:strong-classification-boundary-2}
Theorem \ref{thm:chi-squared-exact-boundary} predicts that the asymptotic boundaries are the same for all values of the parameter $\nu$.
In simulations (Section \ref{sec:numerical}), we find this asymptotic prediction to be quite accurate for $\nu\le3$ even in moderate dimensions ($p=100$). 
For $\nu>3$, the phase transitions take place somewhat above the boundary ${g}$.
The behavior is qualitatively similar for the other three phase transitions (see Theorems \ref{thm:chi-squared-exact-approx-boundary}, \ref{thm:chi-squared-approx-boundary}, and \ref{thm:chi-squared-approx-exact-boundary} below).
\end{remark}

\subsection{The exact-approximate support recovery problem}
\label{subsec:exact-approx-support-recovery-chisq}

The next theorem describes the phase transition in the exact-approximate support recovery problem.

\begin{theorem} \label{thm:chi-squared-exact-approx-boundary}
In the context of Theorem \ref{thm:chi-squared-exact-boundary}, 
the function 
\begin{equation} \label{eq:exact-approx-boundary-chisquared}
    \widetilde{g}(\beta) = 1
\end{equation}
characterizes the phase transition of exact-approximate support recovery problem.
Specifically, if $\underline{r} > \widetilde{g}(\beta)$, then the procedures listed in Theorem \ref{thm:chi-squared-exact-boundary} with slowly vanishing nominal FWER levels achieve asymptotically exact-approximate support recovery in the sense of \eqref{eq:support-recovery-success}.

Conversely, if $\overline{r} < \widetilde{g}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, the exact-approximate support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
\end{theorem}

Theorem \ref{thm:chi-squared-exact-approx-boundary} is proved in Section \ref{subsec:proof-chi-squared-mix-boundaries}.

\subsection{The approximate support recovery problem}
\label{subsec:approx-support-recovery-chisq}

Our third main result characterizes the phase transition phenomenon in the approximate support recovery problem in the chi-square model.

\begin{theorem} \label{thm:chi-squared-approx-boundary}
Consider the high-dimensional chi-squared model \eqref{eq:model-chisq} with signal sparsity and size as described in \eqref{eq:signal-sparsity} and \eqref{eq:signal-size}.
The function 
\begin{equation} \label{eq:approx-boundary-chisquared}
    h(\beta) = \beta
\end{equation}
characterizes the phase transition of approximate support recovery problem.
Specifically, if $\underline{r} > {h}(\beta)$, then the \ac{BH}procedure $\widehat{S}_p$ (defined in Section \ref{sec:statistical-procedures}) with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FDR levels achieves asymptotically approximate support recovery in the sense of \eqref{eq:support-recovery-success}.

Conversely, if $\overline{r} < {h}(\beta)$, then approximate support recovery asymptotically fails in the sense of \eqref{eq:support-recovery-failure} for all thresholding procedures.
\end{theorem}

Theorem \ref{thm:chi-squared-approx-boundary} is proved in Section \ref{subsec:proof-chi-squared-mix-boundaries} below.

\subsection{The approximate-exact support recovery problem}
\label{subsec:aprox-exact-support-recovery-chisq}

A counterpart of Theorem \ref{thm:Gaussian-error-approx-exact-boundary} also holds in the chi-square models.

\begin{theorem} \label{thm:chi-squared-approx-exact-boundary}
In the context of Theorem \ref{thm:chi-squared-approx-boundary}, the function 
\begin{equation} \label{eq:approx-exact-boundary-chisquared}
    \widetilde{h}(\beta) = \left(\sqrt{\beta} + \sqrt{1-\beta}\right)^2
\end{equation}
characterizes the phase transition of approximate-exact support recovery problem.
Specifically, if $\underline{r} > \widetilde{h}(\beta)$, then the Benjamini-Hochberg procedure with slowly vanishing nominal FDR levels achieves asymptotically approximate-exact support recovery in the sense of \eqref{eq:support-recovery-success}.

Conversely, if $\overline{r} < \widetilde{h}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, the approximate-exact support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
\end{theorem}

Theorem \ref{thm:chi-squared-approx-exact-boundary} is proved in Section \ref{subsec:proof-chi-squared-exact-boundary}.

Notice that all phase transitions boundaries are identical to those in the Gaussian additive error model \eqref{eq:model-additive} under one-side alternative.
We refer readers to Figure \ref{fig:phase-Gaussian-errors} in Section \ref{sec:additive-error-model-boundaries} for a visualization of the results in Theorems \ref{thm:chi-squared-exact-boundary} through \ref{thm:chi-squared-approx-exact-boundary}.

\medskip

The all four Theorems so far focus only on the idealized models \eqref{eq:model-chisq} where statistics are \emph{independent}.
Support recovery problems under dependent observations remain to be explored.
Recall in Chapter \ref{chap:phase-transitions} we showed that the boundary for the exact support recovery problem in the additive error model \eqref{eq:model-additive} continues to hold even under severe dependence and general distributional assumptions.
We conjecture that similar results would also hold, under classes of dependence structures that are ``not too different from independence'', in the chi-square models.
As an example, in the GWAS application, dependence among the genetic markers at different locations (known as linkage disequilibrium) decay as a function of their physical distances on the genome \citep{bush2012genome}, resulting in locally dependent test statistics.
It would be of great interest to extend the current theory to cover important dependence structures that arise in such applications.

\subsection{Comparison of one- versus two-sided alternatives in additive error models}
\label{subsec:one-vs-two-sided}

% $\mathrm{risk}^{\mathrm{EA}}$ and $\mathrm{risk}^{\mathrm{AE}}$.
As alluded to in Section \ref{sec:motivation-chisq} in the introduction, we draw explicit comparisons between the one-sided and two-sided alternatives in Gaussian additive error models \eqref{eq:model-additive}.
% The exact, and the approximate support recovery problems in the additive error model \eqref{eq:model-additive} under standard Gaussian errors have been studied in \cite{gao2018fundamental} and \cite{arias2017distribution}, respectively.

The exact support recovery problem in the dependent Gaussian additive error model \eqref{eq:model-additive} was studied in Chapter \ref{chap:phase-transitions}, with parametrization of sparsity identical to that in \eqref{eq:signal-sparsity}, whereas the range of the non-zero (and perhaps unequal) mean shifts $\mu(i)$ was parametrized as 
\begin{equation*}
    \underline{\Delta} = \sqrt{2\underline{r}\log{p}}
    \le \mu(i) \le
    \overline{\Delta} = \sqrt{2\overline{r}\log{p}}, \quad \text{for all}\;\;i\in S_p,
\end{equation*}
for some constants $0<\underline{r}\le\overline{r}\le+\infty$.
Under this one-sided alternative, a phase transition in the $r$-$\beta$ plane was described, where the boundary was found to be identical to \eqref{eq:exact-boundary-chisquared} in Theorem \ref{thm:chi-squared-exact-boundary} for the chi-square models \eqref{eq:model-chisq-Chapter6}.

As discussed in Section \ref{sec:motivation-chisq}, support recovery problems in the chi-square model with $\nu=1$, , corresponds to the support recovery problems in the additive model under two-sided alternatives.
This implies that the asymptotic signal size requirements are identical between the two-sided alternative and its one-sided counterpart, in order to achieve exact support recovery.
As we shall see in numerical experiments (in Section \ref{sec:numerical} below), the difference is not very pronounced even in moderate dimensions, and vanishes as $p\to\infty$, in accordance with Theorem \ref{thm:chi-squared-exact-boundary}.

\medskip

Comparisons can also be drawn in the approximate, approximate-exact, and exact approximate support recovery problems between the two types of alternatives.

Specifically, the approximate support recovery problem in the Gaussian additive error model \eqref{eq:model-additive} under one-sided alternatives exhibits a phase transition phenomenon characterized by a boundary that coincides with \eqref{eq:approx-boundary-chisquared} in Theorem \ref{thm:chi-squared-approx-boundary}.
Similar to the exact support recovery problem, this indicates vanishing difference in the difficulties of the two types alternatives in approximate support recovery problems.

Comparing Theorems \ref{thm:chi-squared-exact-approx-boundary} to \ref{thm:Gaussian-error-exact-approx-boundary} and Theorems \ref{thm:chi-squared-approx-exact-boundary} to \ref{thm:Gaussian-error-approx-exact-boundary}, we see that the phase transition boundaries under the two types of alternatives are also identical in the exact-approximate and approximate-exact support recovery problems.
The additional uncertainty in the two-sided alternatives do not call for larger signal sizes asymptotically in these problems.

\medskip

To complete the comparisons, we point out that the phase transition boundaries for the sparse signal {detection} problem in the two types of alternatives are both identical to \eqref{eq:detection-boundary-large-signals}. This was analyzed in \cite{donoho2004higher}.

### 2020-08-17 6.GWAS/6.numerical.tex
add draft converted from thesis

We illustrate with simulations the phase transition phenomena in the chi-square model, and compare numerically the required signal sizes in support recovery problems between the two types of alternatives in the additive error model.
% We also demonstrate the fundamental trade-off between odds ratios and relative frequencies in association studies, as outlined in Proposition \ref{prop:signal-size-odds-ratio} and Corollary \ref{cor:signal-size-odds-ratio-conditional-frequency}, using evidence from large-scale genetic studies.

\subsection{Exact support recovery}

The sparsity of the signal vectors in the experiments are parametrized as in \eqref{eq:signal-sparsity}. 
Signal sizes are assumed equal with magnitude $\lambda(i)=2r\log{p}$ for $i\in S$.
We estimate the support set $S$ using Bonferroni's procedure with nominal FWER level set at $1/(5{\log{p}})$.
The nominal FWER levels vanishes slowly, in line with the assumptions in Theorem \ref{thm:chi-squared-exact-boundary}.
Experiments were repeated 1000 times at each of the 400 sparsity-signal-size combinations, for dimensions $p=10^2, 10^3$, and $10^4$.

The empirical probabilities of exact support recovery under Bonferroni's procedure are shown in Figure \ref{fig:phase-simulated-chi-squared}.
The numerical results suggest not only good accuracy of the predicted boundaries in high-dimensions ($p=10^4$, right panels of Figure \ref{fig:phase-simulated-chi-squared}), but also practical relevance of the theoretical predictions in moderate dimensions ($p=100$, left panels of Figure \ref{fig:phase-simulated-chi-squared}).

\begin{figure}
      \centering
      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu1_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu1_p1000.eps}
      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu1_p10000.eps}
      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu2_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu2_p1000.eps}
      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu2_p10000.eps}
      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu3_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu3_p1000.eps}
      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu3_p10000.eps}
      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu6_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu6_p1000.eps}
      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu6_p10000.eps}
      \caption{The empirical probability of exact support recovery of Bonferroni's procedure in the chi-squared model \eqref{eq:model-chisq}. 
      We simulate $\nu=1, 2, 3, 6$ (first to last row), at dimensions $p=10^2, 10^3, 10^4$ (left to right column), for a grid of sparsity levels $\beta$ and signal sizes $r$.
      The experiments were repeated 1000 times for each sparsity-signal size combination; darker color indicates higher probability of exact support recovery.  
      Numerical results are in general agreement with the boundaries described in Theorem \ref{thm:chi-squared-exact-boundary}; for large $\nu$'s, the phase transitions take place somewhat above the predicted boundaries.
      The boundary for the approximate support recovery (Theorem \ref{thm:chi-squared-approx-boundary}) and the detection boundary (see Donoho and Jin (2004)) are plotted for comparison.} 
      \label{fig:phase-simulated-chi-squared}
\end{figure}

We conduct further experiments to examine the optimality claims in Theorem \ref{thm:chi-squared-exact-boundary} by comparing with the oracle procedure with thresholds $t_p=\min_{i\in S}x(i)$.
We also examine the claims in Section \ref{subsec:one-vs-two-sided}, and compare the one-sided alternatives in Gaussian additive models with the two-sided alternatives (or equivalently, the chi-square model with $\nu=1$).
We apply Bonferroni's procedure and the oracle thresholding procedure in both settings.

Experiments were repeated 1000 times for a grid of signal size values ranging from $r=0$ to $6$, and for dimensions $10^2, 10^3$, and $10^5$.
Results of the experiments, shown in Figure \ref{fig:one-vs-two-sided-exact_support_recovery}, suggest vanishing difference between difficulties of two-sided vs one-sided alternatives in the additive error models, as well as vanishing difference between the powers of Bonferroni's procedures and the oracle procedures as $p\to\infty$.

\begin{figure}
      \centering
      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p1000.eps}
      % \includegraphics[width=0.33\textwidth]{sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p10000.eps}
      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p100000.eps}
      \caption{The empirical probability of exact support recovery of Bonferroni's procedure (solid curves) and the oracle procedure (dashed curves) in the chi-squared model with one degree of freedom (marked `2') in the additive Gaussian error model and under one-sided alternatives (marked `1'). 
      We simulate at dimensions $p=10^2, 10^3, 10^5$ (left to right) for a grid of signal sizes $r$ and sparsity level $\beta=0.6$.
      The experiments were repeated 1000 times for each method-model-signal-size combination. 
      Numerical results show evidence of convergence to the 0-1 law as predicted by Theorem \ref{thm:chi-squared-exact-boundary}; regions where asymptotically exact support recovery can be achieved are shaded in grey.
      The difference in power between Bonferroni's procedure and the oracle procedure, as well as in the two types of alternatives both decrease as dimensionality increases.} 
      \label{fig:one-vs-two-sided-exact_support_recovery}
\end{figure}

\subsection{Approximate, and approximate-exact support recovery}

Similar experiments are conducted to examine the optimality claims in Theorem \ref{thm:chi-squared-approx-boundary}, and in Section \ref{subsec:one-vs-two-sided}.
We define an oracle thresholding procedure for approximate support recovery, where the threshold is chosen to minimize the empirical risk.
That is,
$$
t_p(x, S) \in \argmin_{t\in\R} \frac{|\widehat{S}(t)\setminus S|}{\max\{|\widehat{S}(t)|,1\}} + \frac{|S\setminus \widehat{S}(t)|}{\max\{|{S}|,1\}},
%\mathcal{R^\mathrm{oracle}} \in \argmin_{\widehat{S}(\mathcal{R})\in\mathcal{S}} \mathrm{risk}^{\mathrm{A}}(\mathcal{R}),
$$
where $\widehat{S}(t) = \{i\;|\;x(i)\ge t\}$;
in implementation, we only need to scan the values of observations $t\in\{x(1), \ldots, x(p)\}$. 
The nominal FDR level for the BH procedure is set at $1/(5{\log{p}})$, therefore slowly vanishing, in line with the assumptions in Theorem \ref{thm:chi-squared-approx-boundary}; all other parameters are identical to that in the experiments for exact support recovery.
Results of the experiments are shown in Figure \ref{fig:one-vs-two-sided-approx_support_recovery} and Figure \ref{fig:phase-simulated-chi-squared-approx-boundary}.

We also examine the boundary described in Theorem \ref{thm:chi-squared-exact-approx-boundary}.
Experimental settings are identical to that in the experiments for approximate support recovery.
% Results for the BH procedure are in general close to that of the oracle procedure,
We compare the performance of the BH procedure with an oracle procedure with threshold
$$
t_p(x, S) \in \min_{i\in S} x(i),
$$
and visualize results of the experiments in Figure \ref{fig:phase-simulated-chi-squared-approx-exact-boundary}.
Notice that the BH procedure sets its threshold somewhat higher than the oracle, especially for small $\beta$'s. 
The empirical risk of the oracle procedure (not shown here in the interest of space) follows much more closely the predicted boundary \eqref{eq:approx-exact-boundary-chisquared}.

\begin{figure}
      \centering
      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p1000.eps}
      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p100000.eps}
      \caption{The empirical risk of approximate support recovery of Benjamini-Hochberg's procedure (solid curves) and the oracle procedure (dashed curves) in the chi-squared model with one degree of freedom (marked `2') and in the additive Gaussian error model under one-sided alternatives (marked `1'). 
      We simulate at dimensions $p=10^2, 10^3, 10^5$ (left to right) for a grid of signal sizes $r$ and sparsity level $\beta=0.6$.
      The experiments were repeated 1000 times for each method-model-signal-size combination. 
      Numerical results show evidence of convergence to the 0-1 law as predicted by Theorem \ref{thm:chi-squared-approx-boundary}; regions where asymptotically approximate support recovery can be achieved are shaded in grey.
      The difference in risks between Benjamini-Hochberg's procedure and the oracle procedure, as well as in the two types of alternatives, both decrease as dimensionality increases.} 
      \label{fig:one-vs-two-sided-approx_support_recovery}
\end{figure}

\begin{figure}
      \centering
      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu1_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu1_p1000.eps}
      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu1_p10000.eps}
      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu2_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu2_p1000.eps}
      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu2_p10000.eps}
      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu3_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu3_p1000.eps}
      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu3_p10000.eps}
      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu6_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu6_p1000.eps}
      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu6_p10000.eps}
      \caption{The estimated risk of approximate support recovery $\mathrm{risk}^{\mathrm{A}}$ (see \eqref{eq:risk-approximate}) of the Benjamini-Hochberg procedure in the chi-squared model \eqref{eq:model-chisq}. 
      We simulate $\nu=1, 2, 3, 6$ (first to last row), at dimensions $p=10^2, 10^3, 10^4$ (left to right column), for a grid of sparsity levels $\beta$ and signal sizes $r$.
      The experiments were repeated 1000 times for each sparsity-signal size combination; darker color indicates higher larger $\mathrm{risk}^{\mathrm{A}}$. 
      Numerical results are generally in agreement with the boundaries described in Theorem \ref{thm:chi-squared-approx-boundary}; for large $\nu$'s, the phase transitions take place somewhat above the predicted boundaries.
      The boundary for the exact support recovery problem (Theorem \ref{thm:chi-squared-exact-boundary}) and the detection boundary (see Donoho and Jin (2004)) are plotted for comparison.} 
      \label{fig:phase-simulated-chi-squared-approx-boundary}
\end{figure}

\begin{figure}
      \centering
      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu1_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu1_p1000.eps}
      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu1_p10000.eps}
      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu2_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu2_p1000.eps}
      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu2_p10000.eps}
      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu3_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu3_p1000.eps}
      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu3_p10000.eps}
      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu6_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu6_p1000.eps}
      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu6_p10000.eps}
      \caption{The estimated risk of approximate-exact support recovery $\mathrm{risk}^{\mathrm{EA}}$ (see \eqref{eq:risk-approx-exact}) of the Benjamini-Hochberg procedure in the chi-squared model \eqref{eq:model-chisq}. 
      We simulate $\nu=1, 2, 3, 6$ (first to last row), at dimensions $p=10^2, 10^3, 10^4$ (left to right column), for a grid of sparsity levels $\beta$ and signal sizes $r$.
      The experiments were repeated 1000 times for each sparsity-signal size combination; darker color indicates higher larger $\mathrm{risk}^{\mathrm{EA}}$. 
      Numerical results are generally in agreement with the boundaries described in Theorem \ref{thm:chi-squared-approx-exact-boundary}; for small $\beta$'s and large $\nu$'s, the phase transitions take place somewhat above the predicted boundaries.
      Other boundaries in the support recovery and the detection problems are plotted for comparison.} 
      \label{fig:phase-simulated-chi-squared-approx-exact-boundary}
\end{figure}

### 2020-08-17 6.GWAS/6.odds-and-power.tex
add draft converted from thesis

We return to the application of association screenings for categorical variables, and put the results in the previous section to use.
In particular, we focus on the exact-approximate support recovery problem, and demonstrate the consequences of its phase transition (Theorem \ref{thm:chi-squared-exact-approx-boundary}) in genetic association studies.

In order to do so, we must first connect the concept of ``statistical signal size'' $\lambda$ with some key quantities in association tests.
While ``signal size'' likely sounds foreign to most practitioners, it is intimately linked with the concept of ``effect sizes'' --- or odds ratios --- in association studies, which are frequently estimated and reported in GWAS catalogs.
We characterize the relationship between the two quantities in the special, but fairly common case of association tests on 2-by-2 contingency tables in Section \ref{sec:odds-and-power}.

% Unlike in additive models where the parameter $\mu$ has the interpretation of signal-to-noise ratios, the meaning of the signal sizes $\lambda$ in chi-square model is perhaps not as transparent.

Consider a 2-by-2 multinomial distribution with marginal probabilities of phenotypes $(\phi_1, \phi_2)$ and genotypes $(\theta_1, \theta_2)$.
The \emph{probability} table (as opposed to the table of multinomial \emph{counts} in the introduction) is as follows.
\begin{center}
    \begin{tabular}{cccc}
    \hline
    & \multicolumn{2}{c}{Genotype} \\
    \cline{2-3}
    Probabilities & Variant 1 & Variant 2 & Total by phenotype \\
    \hline
    Cases & $\mu_{11}$ & $\mu_{12}$ & $\phi_1$ \\
    Controls & $\mu_{21}$ & $\mu_{22}$ & $\phi_2$ \\
    Total by genotype & $\theta_1$ & $\theta_2$ & 1 \\
    \hline
    \end{tabular}
\end{center}
The odds ratio (i.e., ``effect size'') is defined as the ratio of the phenotype frequencies between the two genotype variants,
\begin{equation} \label{eq:odds-ratio}
    \text{R} := \frac{\mu_{11}}{\mu_{21}}\Big/\frac{\mu_{12}}{\mu_{22}}
    = \frac{\mu_{11}\mu_{22}}{\mu_{12}\mu_{21}}.
\end{equation}
The multinomial distribution is fully parametrized by the trio $(\theta_1, \phi_1, R)$.
Odds ratios further away from 1 indicate greater contrasts between the probability of outcomes.
Independence between the genotypes and phenotypes would imply an odds ratio of one, and hence $\mu_{jk} = \phi_j\theta_k$, for all $j,k \in\{1,2\}$.

% When data are sampled from the multinomial distribution, the chi-square test defined in \eqref{eq:chisq-statistic} is asymptotically equivalent to tests including, e.g., the likelihood ratio test and Welch's t-test, both in terms of level and power \cite{ferguson2017course,gao2019upass}.
For a sequence of local alternatives $\mu^{(1)}, \mu^{(2)}, \ldots$, such that $\sqrt{n}(\mu^{(n)}_{jk} - \phi_j\theta_k)$ converges to a constant table $\delta = (\delta_{jk})$, the chi-square test statistics converge in distribution to the non-central chi-squared distribution with non-centrality parameter 
\begin{equation*}
    \lambda = \sum_{j=1}^2 \sum_{k=1}^2 {\delta_{jk}^2}/{(\phi_j\theta_k)}.
\end{equation*}
See, e.g., \cite{ferguson2017course}.
Hence, for large samples from a fixed distribution $(\mu_{ij})$, the statistic is well approximated by a $\chi^2_1(\lambda)$ distribution, where
\begin{equation} 
\lambda = n\sum_{j=1}^2 \sum_{k=1}^2 \frac{(\mu_{jk} - \phi_j\theta_k)^2}{\phi_j\theta_k}.
\end{equation}
%Since $\lambda$ is linear in the number of samples $n$, 
% Power of association tests at $\alpha$ level is approximately $\P[\chi^2_{\nu}(\lambda)>\chi^2_{\nu,\alpha}]$, where $\chi^2_{\nu,\alpha}$ is the upper $\alpha$-quantile of a central Chi-squared distribution.
Power calculations therefore only depend on the $\mu_{jk}$'s through $\lambda=nw^2$, where we define 
\begin{equation} \label{eq:signal-size-chisq}
    w^2:=\lambda/n
\end{equation} 
to be the \emph{signal size per sample}. 
Statistical power would be increasing in $w^2$ for fixed sample sizes.

The next proposition states that the statistical signal size per sample can be parametrized by the odds ratio and the marginals in the probability table.

\begin{proposition} \label{prop:signal-size-odds-ratio}
Consider a 2-by-2 multinomial distribution with marginal distributions $(\phi_1, \phi_2 = 1-\phi_2)$ and $(\theta_1, \theta_2=1-\theta_1)$.
Let signal size $w^2$ be defined as in \eqref{eq:signal-size-chisq}, and odds ratio $\text{R}$ be defined as in \eqref{eq:odds-ratio}. 
If $R=1$, we have $w^2 = 0$; if $R\in(0,1)\cup(1,+\infty)$, then we have
\begin{equation} \label{eq:signal-size-odds-ratio}
    w^2(\text{R}) =
    \frac{1}{4A(\text{R}-1)^2}\left(B+CR-\sqrt{(B+CR)^2-4A(R-1)^2}\right)^2,
\end{equation}
where $A = \phi_1\theta_1\phi_2\theta_2$, $B = \phi_1\theta_1+\phi_2\theta_2$, and $C = \phi_1\theta_2+\phi_2\theta_1$.
\end{proposition}

Proposition \ref{prop:signal-size-odds-ratio} is derived in Section \ref{subsec:proof-signal-size-odds-ratio}.

To understand Proposition \ref{prop:signal-size-odds-ratio}, we illustrate Relation \eqref{eq:signal-size-odds-ratio} for selected values of marginals $\theta_1$ and $\phi_1$ in Figure \ref{fig:signal-vs-odds}.
Observe in the figure that an odds ratio further away from one corresponds to stronger statistical signal per sample, ceteris paribus.
However, this ``valley'' pattern is in general not symmetric around 1, except for balanced marginal distributions ($\phi_1=1/2$ or $\theta_1=1/2$).
While the odds ratio $R$ can be arbitrarily close to 0 or diverge to $+\infty$ for any marginal distribution, the signal sizes $w^2$ are bounded from above by constants that depend only on the marginals.
% This is quantified in the next corollary.

\begin{figure}
      \centering
      \includegraphics[width=0.49\textwidth]{pics/singal-vs-odds-p05}
      \includegraphics[width=0.49\textwidth]{pics/singal-vs-odds-p0333}            
      \caption{Signal sizes per sample $w^2$ as functions of odds ratios in 2-by-2 multinomial distributions for selected genotype marginals in balanced (left) and unbalanced (right) designs; see Relation \eqref{eq:signal-size-odds-ratio} in Proposition \ref{prop:signal-size-odds-ratio}. For given marginal distributions, extreme odds ratios imply stronger statistical signals at a given sample size. However, the signal sizes are bounded above by constants that depend on the marginal distributions; see Relations \eqref{eq:signal-size-upper-bound-1} and \eqref{eq:signal-size-upper-bound-2}. % Unbalanced marginal distributions -- or rare variants -- lead to smaller signal sizes at a given odds ratio.
      } 
      \label{fig:signal-vs-odds}
\end{figure}

\begin{corollary} \label{cor:signal-limits-OR}
The signal size as a function of the odds ratio $w^2(R)$ is decreasing on $(0,1)$ and increasing on $(1,\infty)$, with limits
\begin{equation} \label{eq:signal-size-upper-bound-1}
    \lim_{\text{R}\to0_+} w^2(\text{R}) = \min\left\{\frac{\phi_1\theta_1}{\phi_2\theta_2}, \frac{\phi_2\theta_2}{\phi_1\theta_1}\right\},
\end{equation}
and
\begin{equation} \label{eq:signal-size-upper-bound-2}
    \lim_{\text{R}\to+\infty} w^2(\text{R}) = \min\left\{\frac{\phi_1\theta_2}{\phi_2\theta_1}, \frac{\phi_2\theta_1}{\phi_1\theta_2}\right\}.
\end{equation}
\end{corollary}
% Proof of Corollary \ref{cor:signal-limits-OR} is found in Appendix \ref{sec:proof-signal-size-odds-ratio}.

Corollary \ref{cor:signal-limits-OR} immediately implies that balanced designs with roughly equal number of cases and controls are not necessarily the most informative.

For example, in a study where a third of the recruited subjects carry the genetic variant positively correlated with the trait (i.e., $\theta_1=1/3$), an unbalanced design with $\phi_1=1/3$ would maximize $w^2$ at large odds ratios.
This unbalanced design is much more efficient compared to, say, a balanced design with $\phi_1=1/2$.
In the first case, we have $w^2\to1$ as $R\to\infty$; whereas in the second design, $w^2<1/2$ no matter how large $R$ is.
This difference can also be read by comparing the dashed curve ($\theta_1=1/3$, $\phi_1=1/2$) in the left panel of Figure \ref{fig:signal-vs-odds}, with the solid curve ($\theta_1=1/3$, $\phi_1=1/3$) in the right panel of Figure \ref{fig:signal-vs-odds}.

### 2020-08-17 6.GWAS/6.optimal-design.tex
add draft converted from thesis

For a study with a fixed budget, i.e., a fixed total number of subjects $n$, the researcher is free to choose the fraction of cases $\phi_1$ to be included in the study.
A natural question is how this budget should be allocated to maximize the statistical power of discovery, or equivalently, the signal sizes $\lambda=nw^2$.

In principal, Relation \eqref{eq:signal-size-odds-ratio} can be optimized with respect to the fraction of cases $\phi_1$ in order to find optimal designs, if $\theta_1$ is known and held constant.
In practice, this is not the case.
While the fraction of cases can be controlled, the distributions of genotypes \emph{in the study} are often unknown prior to data collection, and can change with the case-to-control ratio.

Fortunately, the conditional distributions of genotypes in the healthy control groups are often estimated by existing studies, and are made available by consortia such as the NHGRI-EBI GWAS catalog \cite{macarthur2016new}.
% Assume (after appropriate relabelling, hence without loss of generality) that the first variant is associated with an increased risk of disease, and is henceforth referred to as the risk variant.
We denote the conditional frequency of the first genetic variant in the control group as $(f, 1-f)$, where
\begin{equation} \label{eq:RAF}
    f := \mu_{21} / \phi_2.
\end{equation}
The multinomial probability is fully parametrized by the new trio: $(f, \phi_1, R)$.
\begin{center}
    \begin{tabular}{cccc}
    \hline
    & \multicolumn{2}{c}{Genotype} \\
    \cline{2-3}
    Probabilities & Variant 1 & Variant 2 & Total by phenotype \\
    \hline
    Cases & $\frac{\phi_1fR}{fR+1-f}$ & $\frac{\phi_1(1-f)}{fR+1-f}$ & $\phi_1$ \\
    Controls & $f(1-\phi_1)$ & $(1-f)(1-\phi_1)$ & $1-\phi_1$ \\
    \hline
    \end{tabular}
\end{center}
Proposition \ref{prop:signal-size-odds-ratio} may also be re-stated in terms of the new parametrization.

% Note that all these quantities refer to what is in the study, and differ from their counterparts in the general population.

\begin{corollary} \label{cor:signal-size-odds-ratio-conditional-frequency}
In the 2-by-2 multinomial distribution with marginals $(\phi_1, \phi_2 = 1-\phi_1)$, and conditional distribution of the variants in the control group $(f, 1-f)$,
Relation \eqref{eq:signal-size-odds-ratio} holds with $\theta_1 = {\phi_1fR}/{(fR+1-f)} + f(1-\phi_1)$ and $\theta_2 = 1-\theta_1$.
\end{corollary}

The choice of $\phi_1$ now has a practical solution.

\begin{corollary} \label{cor:optimal-design}
In the context of Corollary \ref{cor:signal-size-odds-ratio-conditional-frequency},
the optimal design $(\phi^*_1, \phi^*_2)$ that maximizes the signal size per sample $w^2$ is prescribed by
\begin{equation} \label{eq:optimal-design}
    \phi_1^* = \frac{fR+1-f}{fR+1-f+\sqrt{R}}, \quad\text{and}\quad 
    \phi_2^* = 1-\phi_1^*.
\end{equation}
% when the denominator in \eqref{eq:optimal-design} is non-zero; otherwise, $\phi_1^*=\phi_2^*=1/2$.
\end{corollary}

Corollary \ref{cor:optimal-design} is proved in Section \ref{subsec:proof-signal-size-odds-ratio}.

Of particular interest in the genetics literature are genetic variants with very low allele frequencies in the control group (i.e., $f\approx 0$), known as rare variants.
In such cases, Equation \eqref{eq:optimal-design} can be approximated using the Taylor expansion,
\begin{equation} \label{eq:optimal-design-approx}
    \phi_1^* = \frac{1}{1 + \sqrt{R}} + \frac{(R-\sqrt{R})f}{1+\sqrt{R}} + O(f^2).
\end{equation}
To illustrate, for rare and adversarial factors ($f\approx0$ and $R>1$), the optimal $\phi_1^*$ is less than $1/2$.
Therefore, for studies under a fixed budget, controls should constitute the majority of the subjects, in order to maximize power.
On the other hand, for rare and protective factors ($f\approx0$ and $R<1$), the optimal $\phi_1^*$ is greater than $1/2$, and cases should be the majority.

### 2020-08-17 6.GWAS/6.proofs-GWAS.tex
add draft converted from thesis

We review some properties of the chi-square distributions in Section \ref{sec:chi-square-distributions}, before presenting the proofs of the main theorems on phase transitions in Sections \ref{subsec:proof-chi-squared-exact-boundary}, \ref{subsec:proof-chi-squared-approx-boundary}, and \ref{subsec:proof-chi-squared-mix-boundaries}.
Results relating signal sizes and effect sizes in association tests will be justified in Section \ref{subsec:proof-signal-size-odds-ratio}.

\subsection{Auxiliary facts of chi-square distributions}
\label{sec:chi-square-distributions}
\input{6.GWAS/6.chi-square-distributions.tex}

\subsection{Proof of Theorem \ref{thm:chi-squared-exact-boundary}}
\label{subsec:proof-chi-squared-exact-boundary}

\begin{proof}[Proof of Theorem \ref{thm:chi-squared-exact-boundary}]
We first prove the sufficient condition.
The Bonferroni procedure sets the threshold at $t_p = F^\leftarrow(1-\alpha/p)$, which, by Lemma \ref{lemma:chisq-quantiles}, is asymptotic to $2\log{p} - 2\log{\alpha}$.
By the assumption on $\alpha$ in \eqref{eq:slowly-vanishing-error}, for any $\delta>0$, we have $p^{-\delta}=o(\alpha)$.
Therefore, we have $-\log\alpha\le\delta\log{p}$ for large $p$, and
\begin{equation*} 
    1 \le \limsup_{p\to\infty}\frac{2\log{p} - 2\log{\alpha}}{2\log{p}} \le 1+\delta,
\end{equation*}
for any $\delta>0$.
Hence, $t_p\sim 2\log{p}$.

The condition $\underline{r} > {{g}}(\beta)$ implies, after some algebraic manipulation,
$\sqrt{\underline{r}} -\sqrt{1-\beta} > 1$.
Therefore, we can pick $q>1$ such that 
\begin{equation} \label{eq:choice-of-q}
    \sqrt{\underline{r}} -\sqrt{1-\beta} > \sqrt{q} > 1.
\end{equation}
Setting the $t^* = t^*_p = 2q\log{p}$, we have $t_p < t^*_p$ for large $p$.

On the one hand, $\text{FWER} = 1 - \P[\widehat{S}_p \subseteq S_p]$ vanishes under the Bonferroni procedure with $\alpha\to0$.
On the other hand, for large $p$, the probability of no missed detection is bounded from below by
\begin{equation} \label{eq:chi-square-sufficient-1}
    \P[\widehat{S}_p \supseteq S_p] 
    = \P[\min_{i\in S} x(i) \ge t_p] 
    \ge \P[\min_{i\in S} x(i) \ge t^*] 
    \ge 1 - p^{1-\beta}\P[\chi_\nu^2(\underline{\Delta}) < t^*],
\end{equation}
where we have used the fact that signal sizes are bounded below by $\underline{\Delta}$, and the stochastic monotonicity of chi-square distributions (Lemma \ref{lemma:stochastic-monotonicity}) in the last inequality.
Writing
$$
\chi_\nu^2(\underline{\Delta}) \stackrel{\mathrm{d}}{=} Z_1^2 + \ldots + Z_{\nu-1}^2 + (Z_\nu + \sqrt{\underline{\Delta}})^2
$$
where $Z_i$'s are iid standard normal variables, we have
\begin{align}
    \P[\chi_\nu^2({\underline{\Delta}}) < t^*]
    &\le \P[(Z_\nu+\sqrt{\underline{\Delta}})^2 < t^*] 
    = \P[|Z_\nu+\sqrt{\underline{\Delta}}| < \sqrt{t^*}]  \nonumber \\
    &\le \P\left[Z_\nu < - \sqrt{\underline{\Delta}} +  \sqrt{t^*}\right] \nonumber \\
    &= \P\left[Z_\nu < \sqrt{2\log{p}}\left(\sqrt{q} - \sqrt{\underline{r}}\right)\right]. \label{eq:chi-square-sufficient-2}
\end{align}
By our choice of $q$ in \eqref{eq:choice-of-q}, the last probability in \eqref{eq:chi-square-sufficient-2} can be bounded from above by 
\begin{align*}
    \P\Big[Z_\nu < -\sqrt{2(1-\beta)\log{p}}\Big]
    &\sim \frac{\phi\left(-\sqrt{2(1-\beta)\log{p}}\right)}{\sqrt{2(1-\beta)\log{p}}} \\
    &= \frac{1}{\sqrt{2(1-\beta)\log{p}}}p^{-(1-\beta)},
\end{align*}
where the first line uses Mill's ratio for Gaussian distributions (see Section \ref{sec:Gaussian-distributions} and Relation \eqref{eq:Mills-ratio}).
This, combined with \eqref{eq:chi-square-sufficient-1}, completes the proof of the sufficient condition for the Bonferroni's procedure.

Under the assumption of independence, Sid\'ak's, Holm's, and Hochberg's procedures are strictly more powerful than Bonferroni's procedure, while controlling FWER at the nominal levels.
Therefore, the risks of exact support recovery for these procedures also vanishes.
This completes the proof for the first part of Theorem \ref{thm:chi-squared-exact-boundary}.

We now show the necessary condition. 
We first normalize the maxima by the chi-square quantiles $u_p = F^{\leftarrow}(1-1/p)$, where $F$ is the distribution of a (central) chi-square random variable,
\begin{equation} \label{eq:chi-square-necessary-0}
 \P[\widehat{S}_p = S_p] \le \P\left[M_{S^c} <  t_p \le m_{S} \right]
  % &= \P\left[\frac{\max_{i\in S^c}x(i)}{u_p} < \frac{\min_{i\in S}x(i)}{u_p}\right] \nonumber \\
  % &\le  \P\left[\frac{\max_{i\in S^c}\chi_\nu^2(\lambda(i))}{u_p} < \frac{\min_{i\in S}\chi_\nu^2(\lambda(i))}{u_p}\right] \nonumber \\
  \le \P\left[ \frac{M_{S^c}}{u_p} < \frac{m_S}{u_p} \right],
\end{equation}
where $M_{S^c} = \max_{i\in S^c}x(i)$ and $m_{S} = \min_{i\in S}x(i)$.
By the relative stability of chi-square random variables (Corollary \ref{cor:relative-stability}), we know that ${M_{S^c}}/{u_{|S^c|}}\to1$ in probability. 
Further, using the expression for $u_p$ (Lemma \ref{lemma:chisq-quantiles}), we obtain
$$
\frac{u_{p-p^{1-\beta}}}{u_{p}} \sim \frac{2\log{(p-p^{1-\beta})}}{2\log{p}} = \frac{\log{p}+\log{(1-p^{-\beta})}}{\log{p}} \sim 1.
$$
Therefore, the left-hand-side of the last probability in \eqref{eq:chi-square-necessary-0} converges to 1,
\begin{equation} \label{eq:chi-square-necessary-1}
    \frac{M_{S^c}}{u_{p}} = \frac{M_{S^c}}{u_{p-p^{1-\beta}}} \frac{u_{p-p^{1-\beta}}}{u_{p}} \stackrel{\P}{\longrightarrow} 1.
\end{equation}

Meanwhile, for any $i\in S$, by Lemma \ref{lemma:stochastic-monotonicity} and the fact that signal sizes are bounded above by $\overline{\Delta}$, we have,
\begin{equation*}
    {\chi_\nu^2(\lambda(i))} \stackrel{\mathrm{d}}{\le}
    {\chi_\nu^2(\overline{\Delta})} \stackrel{\mathrm{d}}{=} 
    {Z_1^2 + \ldots + Z_{\nu-1}^2 + \left(Z_\nu + \sqrt{\overline{\Delta}}\right)^2}.
\end{equation*}
Dividing through by $u_p$, and taking minimum over $S$, we obtain
\begin{equation} \label{eq:chi-square-necessary-3}
    \frac{m_S}{u_p} 
    = \min_{i\in S} \frac{\chi_\nu^2(\lambda(i))}{u_p} 
    % \stackrel{\mathrm{d}}{\le} \min \left\{\frac{\chi_\nu^2(\overline{\Delta})}{u_p}, s \text{ iid copies} \right\} \\
    \stackrel{\mathrm{d}}{\le} 
    \min_{i\in S}\left\{\frac{Z_1^2(i) + \ldots + Z_{\nu-1}^2(i)}{u_p} + \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{u_p}\right\}.
\end{equation}
Let $i^\dagger = i^\dagger_p$ be the index minimizing the second term in \eqref{eq:chi-square-necessary-3}, i.e.,
\begin{equation}
    i^\dagger := \argmin_{i\in S} \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{u_p}
    = \argmin_{i\in S} f_p\left(Z_\nu(i)\right),
    % \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{2\log{p}},
\end{equation}
where $f_p(x):=(x+\sqrt{\overline{\Delta}})^2/(2\log{p})$. 
We shall first show that 
\begin{equation} \label{eq:chi-square-necessary-4}
    %\min_{i\in S} \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{2\log{p}} 
    \P[ f_p(Z_\nu(i^\dagger)) < 1 -\delta ] \to 1,
\end{equation}
for some small $\delta>0$.
On the one hand, we know (by solving a quadratic inequality) that
\begin{equation} \label{eq:chi-square-necessary-5}
    f_p(x)<1-\delta \iff \frac{x}{\sqrt{2\log{p}}} \in (-(\sqrt{\overline{r}}+\sqrt{1-\delta}), -(\sqrt{\overline{r}}-\sqrt{1-\delta})).
\end{equation}
On the other hand, we know (by relative stability of iid Gaussians \cite{gao2018fundamental}) that 
\begin{equation} \label{eq:chi-square-necessary-6}
    % f_p(\min_{i\in S}z_\nu(i)) =
    \frac{\min_{i\in S} Z_\nu(i)}{\sqrt{2\log{p}}}
    \to -\sqrt{1-\beta} \quad\text{in probability}.
\end{equation}
Further, by the assumption on the signal sizes $\overline{r} < (1+\sqrt{1-\beta})^2$, we have,
\begin{equation*}
    -(\sqrt{\overline{r}}+1) < -1 <- \sqrt{1-\beta} < - (\sqrt{\overline{r}}-1).
\end{equation*}
Therefore we can picking a small $\delta>0$ such that 
\begin{equation} \label{eq:chi-square-necessary-7}
    -(\sqrt{\overline{r}}+1) < -(\sqrt{\overline{r}}+\sqrt{1-\delta})
    < - \sqrt{1-\beta}
    < - (\sqrt{\overline{r}}-\sqrt{1-\delta})
    < - (\sqrt{\overline{r}}-1).
\end{equation}
Combining \eqref{eq:chi-square-necessary-5}, \eqref{eq:chi-square-necessary-6}, and \eqref{eq:chi-square-necessary-7}, we obtain
\begin{align*}
    \P\left[\min_{i\in S} f_p(Z_\nu(i)) < 1-\delta\right]
    &= \P\left[ f_p(Z_\nu(i^\dagger)) < 1-\delta \right] \\
    &\ge \P\left[ f_p\left(\min_{i\in S}Z_\nu(i)\right) < 1-\delta \right] \to 1,
\end{align*}
and we arrive at \eqref{eq:chi-square-necessary-4}.
As a corollary, since $u_p\sim2\log{p}$, it follows that
\begin{equation} \label{eq:chi-square-necessary-8}
    \P\left[\min_{i\in S}\frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{u_p} < 1-\delta\right]\to1.
\end{equation}

Finally, by independence between $Z_1^2(i)+\ldots+Z_{\nu-1}^2(i)$ and $(Z_\nu^2(i)+\sqrt{\overline{\Delta}})^2$, and the fact that $i^\dagger$ is a function of only the latter, we have
$$
Z_1^2(i^\dagger)+\ldots+Z_{\nu-1}^2(i^\dagger) 
\stackrel{\mathrm{d}}{=} Z_1^2(i)+\ldots+Z_{\nu-1}^2(i) 
\quad \text{for all} \;\; i\in S.
$$
Therefore, $Z_1^2(i^\dagger)+\ldots+Z_{\nu-1}^2(i^\dagger) = O_\P(1)$, and 
\begin{equation} \label{eq:chi-square-necessary-9}
    \frac{Z_1^2(i^\dagger)+\ldots+Z_{\nu-1}^2(i^\dagger)}{u_p} \to 0 \quad \text{in probability}. 
\end{equation}
Together, \eqref{eq:chi-square-necessary-8} and \eqref{eq:chi-square-necessary-9} imply that
\begin{align}
    \P\left[\frac{m_S}{u_p}<1-\delta\right]
    &\ge \P\left[\min_{i\in S}\left\{\frac{Z_1^2(i) + \ldots + Z_{\nu-1}^2(i)}{u_p} + \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{u_p}\right\} < 1-\delta\right] \nonumber \\
    &\ge \P\left[\frac{Z_1^2(i^\dagger) + \ldots + Z_{\nu-1}^2(i^\dagger)}{u_p} + \frac{(Z_\nu(i^\dagger) + \sqrt{\overline{\Delta}})^2}{u_p} < 1-\delta\right] \to 1. \label{eq:chi-square-necessary-10}
\end{align}
In view of \eqref{eq:chi-square-necessary-0}, \eqref{eq:chi-square-necessary-1}, and \eqref{eq:chi-square-necessary-10}, we conclude that exact recovery cannot succeed with any positive probability.
The proof of the necessary condition is complete.
\end{proof}

\subsection{Proof of Theorem \ref{thm:chi-squared-approx-boundary}}
\label{subsec:proof-chi-squared-approx-boundary}

We first show the necessary condition. 
That is, when $\overline{r} < \beta$, no thresholding procedure is able to achieve approximate support recovery.

The proof follows the ideas in \cite{arias2017distribution}, and is very similar to the proof of Theorem \ref{thm:Gaussian-error-approx-boundary}. 
One could in principle obtain the proofs in this section by referencing arguments that have appeared in Section \ref{sec:proofs}.
We choose to present the the proof here in full to make this section self-contained.

\begin{proof}[Proof of necessary condition in Theorem \ref{thm:chi-squared-approx-boundary}]
Denote the distributions of $\chi^2_\nu(0)$, $\chi^2_\nu(\underline{\Delta})$ and $\chi^2_\nu(\overline{\Delta})$ as $F_0$, $F_{\underline{a}}$, and $F_{\overline{a}}$ respectively.

% We first show the necessary condition, i.e., when $\overline{r}<\beta$, approximate support recovery cannot be achieved with any thresholding procedure.
% In particular, we show that the liminf of the sum of FDP and NDP is at least 1.

Recall that thresholding procedures are of the form
$$
\widehat{S}_p = \left\{i\,|\,x(i) > t_p(x)\right\}.
$$
Denote $\widehat{S} := \left\{i\,|\,x(i) > t_p(x)\right\}$, and $\widehat{S}(u) := \left\{i\,|\,x(i) > u\right\}$.
For any threshold $u\ge t_p$ we must have $\widehat{S}(u)\subseteq\widehat{S}$, and hence
\begin{equation} \label{eq:approx-boundary-proof-FDP}
    \text{FDP} := \frac{|\widehat{S}\setminus{S}|}{|\widehat{S}|} \ge \frac{|\widehat{S}\setminus{S}|}{|\widehat{S}\cup{S}|} = \frac{|\widehat{S}\setminus{S}|}{|\widehat{S}\setminus{S}| + |S|} \ge
    \frac{|\widehat{S}(u)\setminus{S}|}{|\widehat{S}(u)\setminus{S}| + |S|}.
\end{equation}
On the other hand, for any threshold $u\le t_p$ we must have $\widehat{S}(u)\supseteq\widehat{S}$, and hence
\begin{equation} \label{eq:approx-boundary-proof-NDP}
    \text{NDP} := \frac{|{S}\setminus\widehat{S}|}{|{S}|} \ge 
    \frac{|{S}\setminus\widehat{S}(u)|}{|{S}|}.
\end{equation}
Since either $u\ge t_p$ or  $u\le t_p$ must take place, putting \eqref{eq:approx-boundary-proof-FDP} and \eqref{eq:approx-boundary-proof-NDP} together, we have
\begin{equation} \label{eq:approx-boundary-proof-converse-1}
    \text{FDP} + \text{NDP} 
    \ge \frac{|\widehat{S}(u)\setminus{S}|}{|\widehat{S}(u)\setminus{S}|+|{S}|} \wedge \frac{|{S}\setminus\widehat{S}(u)|}{|{S}|},
\end{equation}
for any $u$.
Therefore it suffices to show that for a suitable choice of $u$, the RHS of \eqref{eq:approx-boundary-proof-converse-1} converges to 1 in probability; the desired conclusion on FDR and FNR follows by the dominated convergence theorem.

Let $t^* = 2q\log{p}$ for some fixed $q$, we obtain an estimate of the tail probability
\begin{align}
    \overline{F_0}(t^*) 
    &= \P[\chi_\nu^2(0) > t^*] 
    = \frac{2^{-\nu/2}}{\Gamma(\nu/2)} \int_{2q\log{p}}^\infty x^{\nu/2-1}e^{-x/2} \mathrm{d}x \nonumber \\
    &\sim \frac{2^{-\nu/2}}{\Gamma(\nu/2)} 2\left(2q\log{p}\right)^{\nu/2-1}p^{-q}. \label{eq:approx-boundary-proof-null-tail-prob}
\end{align}
where $a_p\sim b_p$ is taken to mean $a_p/b_p\to 1$; this tail estimate was also obtained in \cite{donoho2004higher}.
Observe that $|\widehat{S}(t^*)\setminus{S}|$ has distribution $\text{Binom}(p-s, \overline{F_0}(t^*))$ where $s=|S|$, denote $X = X_p := {|\widehat{S}(t^*)\setminus{S}|}/{|S|}$, and we have 
$$
\mu := \E\left[X\right] = \frac{(p-s)\overline{F_0}(t^*)}{s},
\quad \text{and} \quad
\var\left(X\right) = \frac{(p-s)\overline{F_0}(t^*){F_0}(t^*)}{s^2} \le \mu/s.
$$
Therefore for any $M>0$, we have, by Chebyshev's inequality,
\begin{equation}
    \P\left[X < M\right] 
    \le \P\left[\left|X-\mu\right| > \mu - M\right]
    \le \frac{\mu/s}{(\mu-M)^2}
    = \frac{1/(\mu s)}{(1-M/\mu)^2}. \label{eq:approx-boundary-proof-converse-2}
\end{equation}
Now, from the expression of $\overline{F_0}(t^*)$ in \eqref{eq:approx-boundary-proof-null-tail-prob}, we obtain
$$
\mu = (p^\beta - 1)\overline{F_0}(t^*) \sim \frac{2^{1-\nu/2}}{\Gamma(\nu/2)} \left(2q\log{p}\right)^{\nu/2-1}p^{\beta-q}.
$$
Since $\overline{r}<\beta$, we can pick $q$ such that $\overline{r}<q<\beta$. 
In turn, we have $\mu \to\infty$, as $p\to\infty$.
Therefore the last expression in \eqref{eq:approx-boundary-proof-converse-2} converges to 0, and we conclude that $X\to\infty$ in probability, and hence
\begin{equation} \label{eq:approx-boundary-proof-converse-3}
\frac{|\widehat{S}(t^*)\setminus{S}|}{|\widehat{S}(t^*)\setminus{S}|+|{S}|} 
= \frac{X}{X+1} \to 1 \quad \text{in probability}.
\end{equation}

On the other hand, we show that with the same choice of $u = t^*$,
\begin{equation} \label{eq:approx-boundary-proof-converse-4}
    \frac{|{S}\setminus\widehat{S}(t^*)|}{|{S}|}\to 1 \quad \text{in probability}.
\end{equation}
By the stochastic monotonicity of chi-square distributions (Lemma \ref{lemma:stochastic-monotonicity}), the probability of missed detection for each signal is lower bounded by $\P[\chi^2_\nu(\lambda_i) \le t^*] \ge F_{\overline{a}}(t^*)$.
Therefore, $|{S}\setminus\widehat{S}(t^*)| \stackrel{\mathrm{d}}{\ge} \text{Binom}(s, {F_{\overline{a}}}(t^*))$, and it suffices to show that ${F_{\overline{a}}}(t^*)$ converges to 1.
This is indeed the case, since
\begin{align*}
    {F_{\overline{a}}}(t^*) 
    &= \P[Z_1^2 + \ldots + Z_\nu^2 + 2\sqrt{2\overline{r}\log{p}} Z_\nu + 2\overline{r}\log{p} \le 2q\log{p}] \\
    &\ge \P[Z_1^2 + \ldots + Z_\nu^2 \le (q-\overline{r})\log{p}, \; 2\sqrt{2\overline{r}\log{p}} Z_\nu \le (q-\overline{r})\log{p}],
\end{align*}
and both events in the last line have probability going to 1 as $p\to\infty$.
The necessary condition is shown.
\end{proof}

We now turn to the sufficient condition. 
That is, when $\underline{r} > \beta$, the Benjamini-Hochberg procedure with slowly vanishing FDR levels achieves asymptotic approximate support recovery.
The structure for the proof of sufficient condition follows that of Theorem 2 in \cite{arias2017distribution}.

\begin{proof}[Proof of sufficient condition in Theorem \ref{thm:chi-squared-approx-boundary}]
The FDR vanishes by our choice of $\alpha$ and the FDR-controlling property of the BH procedure.
It only remains to show that FNR also vanishes.

To do so we compare the FNR under the alternative specified in Theorem \ref{thm:chi-squared-approx-boundary} to one with all of the signal sizes equal to $\underline{\Delta}$.
Let $x(i)$ be vectors of independent observations with $p-s$ nulls having $\chi^2_\nu(0)$ distributions, and $s$ signals having $\chi^2_\nu(\underline{\Delta})$ distributions.
By Lemma \ref{lemma:monotonicity-BH-procedure}, it suffices to show that the FNR under the BH procedure in this setting vanishes.

Let $\widehat{G}$ denote the empirical survival function as in \eqref{eq:empirical-tail-distribution}.
Define the empirical survival functions for the null part and signal part
\begin{equation} \label{eq:empirical-survival-null-signal}
    \widehat{W}_\text{null}(t) = \frac{1}{p-s}\sum_{i\not\in S}\mathbbm{1}\{x(i) \ge t\},
    \quad
    \widehat{W}_\text{signal}(t) = \frac{1}{s}\sum_{i\in S}\mathbbm{1}\{x(i) \ge t\},
\end{equation}
where $s=|S|$, so that
$$
\widehat{G}(t) = \frac{p-s}{p}\widehat{W}_\text{null}(t) + \frac{s}{p}\widehat{W}_\text{signal}(t).
$$

Apply Lemma \ref{lemma:empirical-process} to the two summands in $\widehat{G}$, we obtain
$\widehat{G}(t) = G(t) + \widehat{R}(t)$.
where 
\begin{equation} \label{eq:empirical-process-mean}
    G(t) = \frac{p-s}{p}\overline{F_0}(t) + \frac{s}{p}\overline{F_a}(t),
\end{equation}
where $\overline{F_0}$ and $\overline{F_{a}}$ are the survival functions of $\chi_\nu^2(0)$ and $\chi_\nu^2(\underline{\Delta})$ respectively, and 
\begin{equation} \label{eq:empirical-process-residual}
    \widehat{R}(t) = O_\P\left(\xi_p\sqrt{\overline{F_0}(t)F_0(t)} + \frac{s}{p}\xi_s\sqrt{\overline{F_a}(t)F_a(t)}\right),
\end{equation}
uniformly in $t$.

Recall (see proof of Lemma \ref{lemma:monotonicity-BH-procedure}) that the BH procedure is the thresholding procedure with threshold set at $\tau$ (defined in \eqref{eq:approx-boundary-proof-tau}).
% \begin{equation} \label{eq:approx-boundary-proof-tau-recall}
%     \tau = \inf\{t\,|\,\overline{F_0}(t)\le\alpha\widehat{G}(t)\}. 
%     %= \min\{t\,|\,\overline{F_0}(t)=\alpha\widehat{G}(t)\}.
% \end{equation}
The NDP may also be re-written as 
$$
\text{NDP} = \frac{|{S}\setminus\widehat{S}|}{|{S}|} = \frac{1}{s}\sum_{i\in S}\mathbbm{1}\{x(i) < \tau\} = 1 - \widehat{W}_\text{signal}(\tau),
$$
so that it suffices to show that 
\begin{equation} \label{eq:approx-boundary-proof-sufficient-1}
    \widehat{W}_\text{signal}(\tau)\to 1
\end{equation} in probability.
Applying Lemma \ref{lemma:empirical-process} to $\widehat{W}_\text{signal}$, we know that 
$$
\widehat{W}_\text{signal}(\tau) = \overline{F_a}(\tau) + O_\P\left(\xi_s\sqrt{\overline{F_a}(\tau)F_a(\tau)}\right) = \overline{F_a}(\tau) + o_\P(1).
$$
So it suffices to show that $F_a(\tau)\to 0$ in probability.
Now let $t^* = 2q\log(p)$ for some $q$ such that $\beta<q<\underline{r}$.
We have 
\begin{align}
    F_a(t^*) 
    &= \P[\chi^2_\nu(\underline{\Delta}) \le t^*]
    \le \P\left[2\sqrt{\underline{\Delta}}Z_\nu \le t^* - \underline{\Delta}\right] \nonumber \\
    &= \P\left[Z_\nu \le \frac{t^*}{2\sqrt{\underline{\Delta}}} - \frac{\sqrt{\underline{\Delta}}}{2}\right] 
    = \P\left[Z_\nu \le \frac{q-\underline{r}}{2\sqrt{\underline{r}}}\sqrt{2\log{p}}\right] \to 0. \label{eq:approx-boundary-proof-sufficient-2}
\end{align} 
Hence in order to show \eqref{eq:approx-boundary-proof-sufficient-1}, it suffices to show 
\begin{equation} \label{eq:approx-boundary-proof-sufficient-3}
    \P\left[\tau \le t^*\right] \to 1.
\end{equation}
By \eqref{eq:empirical-process-mean}, the mean of the empirical process $\widehat{G}$ evaluated at $t^*$ is
\begin{equation} \label{eq:approx-boundary-proof-sufficient-4}
    G(t^*) = \frac{p-s}{p}\overline{F_0}(t^*) + \frac{s}{p}\overline{F_a}(t^*).
\end{equation}
The first term, using Relation \eqref{eq:approx-boundary-proof-null-tail-prob}, is asymptotic to $p^{-q}L(p)$, where $L(p)$ is the logarithmic term in $p$.
The second term, since $\overline{F_a}(t^*)\to 1$ by Relation \eqref{eq:approx-boundary-proof-sufficient-2}, is asymptotic to $p^{-\beta}$.
Therefore, $G(t^*) \sim p^{-q}L(p) + p^{-\beta} \sim p^{-\beta}$, since 
$p^{\beta-q}L(p)\to0$ where $q>\beta$.

The fluctuation of the empirical process at $t^*$, by Relation \eqref{eq:empirical-process-residual}, is 
\begin{align*}
    \widehat{R}(t^*) 
    &= O_\P\left(\xi_p\sqrt{\overline{F_0}(t^*)F_0(t^*)} + \frac{s}{p}\xi_s\sqrt{\overline{F_a}(t^*)F_a(t^*)}\right)\\
    &= O_\P\left(\xi_p\sqrt{\overline{F_0}(t^*)}\right) + o_\P\left(p^{-\beta}\right).
\end{align*}
By \eqref{eq:approx-boundary-proof-null-tail-prob} and the expression for $\xi_p$, the first term is $O_\P\left(p^{-(q+1)/2}L(p)\right)$ where $L(p)$ is a poly-logarithmic term in $p$.
Since $\beta<\min\{q,1\}$, we have $\beta<(q+1)/2$, and hence $\widehat{R}(t^*) = o_\P(p^{-\beta})$.

Putting the mean and the fluctuation of $\widehat{G}(t^*)$ together, we obtain
$$
\widehat{G}(t^*) = G(t^*) + \widehat{R}(t^*) \sim_\P G(t^*) \sim p^{-\beta},
$$
and therefore, together with \eqref{eq:approx-boundary-proof-null-tail-prob}, we have
$$
\overline{F_0}(t^*)/\widehat{G}(t^*) = p^{\beta-q}L(p)(1+o_{\P}(1)),
$$
which is eventually smaller than the FDR level $\alpha$ by the assumption \eqref{eq:slowly-vanishing-error} and the fact that $\beta<q$.
That is, 
$$
\P\left[\overline{F}_0(t^*) / \widehat{G}(t^*) < \alpha\right] \to 1.
$$
By definition of $\tau$ (recall \eqref{eq:approx-boundary-proof-tau}), this implies that $\tau \le t^*$ with probability tending to 1, and \eqref{eq:approx-boundary-proof-sufficient-3} is shown.
The proof for the sufficient condition is complete.
\end{proof}

\subsection{Proof of Theorems \ref{thm:chi-squared-exact-approx-boundary} and \ref{thm:chi-squared-approx-exact-boundary}}
\label{subsec:proof-chi-squared-mix-boundaries}

As with the proof of Theorem \ref{thm:chi-squared-approx-boundary}, one could shorten the presentations in this section by referencing arguments Section \ref{sec:proofs}.
Again, we choose to present the the proof in full to make this section self-contained.

\begin{proof}[Proof of Theorem \ref{thm:chi-squared-exact-approx-boundary}]
% The reduction to equal signal sizes can be achieved 
We first show the sufficient condition.
Similar to the proof of Theorem \ref{thm:chi-squared-approx-boundary}, it suffices to show that
\begin{equation} \label{eq:exact-approx-boundary-proof-sufficient-1}
    \text{NDP} = 1 - \widehat{W}_\text{signal}(t_p) \to 0,
\end{equation}
where $t_p$ is the threshold of Bonferroni's procedure.

Since $\underline{r}>\widetilde{g}(\beta)=1$, we can pick $q$ such that $1<q<\underline{r}$.
Let $t^* = 2q\log{p}$, we have $t_p<t_p^*$ for large $p$ as in the proof of Theorem \ref{thm:chi-squared-exact-boundary}.
Therefore for large $p$, we have
$$
\widehat{W}_\text{signal}(t_p) \ge \widehat{W}_\text{signal}(t^*) \ge \overline{F_a}(t^*) + o_\P(1),
$$
where the last inequality follows from the stochastic monotonicity of the chi-square family (Lemma \ref{lemma:stochastic-monotonicity}), and Lemma \ref{lemma:empirical-process}.
Indeed, $F_a(t^*)\to0$ by \eqref{eq:approx-boundary-proof-sufficient-2} and our choice of $q<\underline{r}$. 
The proof of the sufficient condition is complete.

Proof of the necessary condition follows a similar structure to that of Theorem \ref{thm:chi-squared-approx-boundary}.
That is, we show that $\mathrm{FWER} + \mathrm{FNR}$ has liminf at least 1 by working with the lower bound
\begin{equation} \label{eq:exact-approx-boundary-proof-necessary-1}
    \mathrm{FWER}(\mathcal{R}) + \mathrm{FNR}(\mathcal{R}) \ge \P\left[\max_{i\in S^c}x(i)>u\right] \wedge \E\left[\frac{|S\setminus \widehat{S}(u)|}{|S|}\right],
\end{equation}
which holds for any thresholding procedure $\mathcal{R}$ and for arbitrary $u\in\R$.
By the assumption that $\overline{r}<\widetilde{g}(\beta)=1$, we can pick $q$ such that $\overline{r}<q<1$ and let $u = t^*=2q\log{p}$.
By relative stability of chi-squared random variables (Lemma \ref{lemma:rapid-variation-chisq}), we have
\begin{equation} \label{eq:exact-approx-boundary-proof-necessary-2}
    \P\left[\frac{\max_{i\in S^c} x(i)}{2\log{p}} > \frac{t^*}{2\log{p}}\right] \to 1.
\end{equation}
where the first fraction in \eqref{eq:exact-approx-boundary-proof-necessary-2} converges to 1, while the second converges to $q<1$.
On the other hand, by our choice of $q>\overline{r}$, the second term in \eqref{eq:exact-approx-boundary-proof-necessary-1} also converges to 1 as in \eqref{eq:approx-boundary-proof-converse-4}.
This completes the proof of the necessary condition.
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm:chi-squared-approx-exact-boundary}]
We first show the sufficient condition.
Since FDR control is guaranteed by the BH procedure, we only need to show that the FWNR also vanishes, that is,
\begin{equation} \label{eq:approx-exact-boundary-proof-sufficient-1}
    \P\left[\min_{i\in S}x(i) \ge \tau\right] \to 1,
\end{equation}
where $\tau$ is the threshold for the BH procedure.

By the assumption that $\underline{r}>\widetilde{h}(\beta)=(\sqrt{\beta}+\sqrt{1-\beta})^2$, we have $\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{\beta}$, so we can pick $q>0$, such that 
\begin{equation} \label{eq:approx-exact-boundary-proof-sufficient-2}
\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{q}>\sqrt{\beta}.
\end{equation}
Let $t^*=2q\log{p}$, we claim that 
\begin{equation} \label{eq:approx-exact-boundary-proof-sufficient-3}
\P\left[\tau\le t^*\right]\to 1.
\end{equation}
Indeed, by our choice of $q>\beta$, \eqref{eq:approx-exact-boundary-proof-sufficient-3} follows in the same way that \eqref{eq:approx-boundary-proof-sufficient-3} did.

With this $t^*$, we have
\begin{equation} \label{eq:approx-exact-boundary-proof-sufficient-4}
    \P\left[\min_{i\in S}x(i) \ge \tau\right] \ge 
    % \P\left[\min_{i\in S}x(i) \ge t^* \ge \tau\right] \ge
    \P\left[\min_{i\in S}x(i) \ge t^*,\; t^* \ge \tau\right].
\end{equation}
However, by our choice of $\sqrt{q} < \sqrt{\underline{r}}-\sqrt{1-\beta}$, the probability of the first event on the right-hand side of \eqref{eq:approx-exact-boundary-proof-sufficient-4} also goes to 1 according to \eqref{eq:chi-square-sufficient-1} and \eqref{eq:chi-square-sufficient-2}.
Together with \eqref{eq:approx-exact-boundary-proof-sufficient-3}, this proves \eqref{eq:approx-exact-boundary-proof-sufficient-1}, and completes proof of the sufficient condition.

The necessary condition follows from the lower bound
\begin{equation} \label{eq:approx-exact-boundary-proof-necessary-1}
    \mathrm{FDR}(\mathcal{R}) + \mathrm{FWNR}(\mathcal{R}) \ge \E\left[\frac{|\widehat{S}(u)\setminus S|}{|\widehat{S}(u)\setminus S| + |S|}\right] \wedge 
    \P\left[\min_{i\in S}x(i)<u\right],
\end{equation}
which holds for any thresholding procedure $\mathcal{R}$ and for arbitrary $u\in\R$.

By the assumption that $\overline{r}<\widetilde{h}(\beta)=(\sqrt{\beta}+\sqrt{1-\beta})^2$, we can pick a constant $q>0$, such that 
\begin{equation} \label{eq:approx-exact-boundary-proof-necessary-2}
    \sqrt{\overline{r}} - \sqrt{1-\beta} < \sqrt{q} < \sqrt{\beta}.
\end{equation}
Let also $u = t^*=2q\log{p}$.
By our choice of $q < \beta$, we know from \eqref{eq:approx-boundary-proof-converse-3} that the first term on the right-hand-side of \eqref{eq:approx-exact-boundary-proof-necessary-1} converges to 1.
It remains to show that the second term in \eqref{eq:approx-exact-boundary-proof-necessary-1} also converges to 1.

For the second term in \eqref{eq:approx-exact-boundary-proof-necessary-1}, dividing through by $2\log{p}$, we obtain
\begin{equation} \label{eq:approx-exact-boundary-proof-necessary-3}
    \P\left[\min_{i\in S}x(i)<t^*\right] = \P\left[ \frac{m_{S}}{2\log{p}} < q \right].
\end{equation}
Similar to \eqref{eq:chi-square-necessary-3}, we have
\begin{equation} \label{eq:approx-exact-boundary-proof-necessary-4}
    \frac{m_{S}}{2\log{p}} 
    \stackrel{\mathrm{d}}{\le} \min_{i\in S}\frac{Z_1^2(i) + \ldots + Z_{\nu-1}^2(i)}{2\log{p}} + \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{2\log{p}}.
\end{equation}
Define $i^\dagger = i^\dagger_p$ to be the index minimizing the second term in \eqref{eq:approx-exact-boundary-proof-necessary-4}, i.e.,
\begin{equation}
    i^\dagger := \argmin_{i\in S} f_p\left(Z_\nu(i)\right),
    % \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{2\log{p}},
\end{equation}
where $f_p(x):=(x+\sqrt{\overline{\Delta}})^2/(2\log{p})$.

Since $\sqrt{q}>\sqrt{\overline{r}}-\sqrt{1-\beta}$ and $q>0$, we have
$\frac{\sqrt{\overline{r}}-\sqrt{q}}{\sqrt{1-\beta}}<1$.
Also, since
$$
    \frac{\sqrt{\overline{r}}+\sqrt{q}}{\sqrt{1-\beta}}>0,
    \quad\text{and}\quad
    \frac{\sqrt{\overline{r}}-\sqrt{q}}{\sqrt{1-\beta}} < \frac{\sqrt{\overline{r}}+\sqrt{q}}{\sqrt{1-\beta}},
$$
we can further pick a constant $\beta_0\in(0,1]$ such that
\begin{equation} \label{eq:approx-exact-boundary-proof-necessary-5}
    \frac{\sqrt{\overline{r}}-\sqrt{q}}{\sqrt{1-\beta}} 
    < \sqrt{\beta_0} < 
    \frac{\sqrt{\overline{r}}+\sqrt{q}}{\sqrt{1-\beta}}.
\end{equation}
Let $Z_{[1]}\le Z_{[2]}\le\ldots\le Z_{[s]}$ be the order statistics of 
$\{Z_\nu(i)\}_{i\in S}$ and define $k=\lfloor s^{1-\beta_0}\rfloor$.
Applying Lemma \ref{lemma:relative-stability-order-statistics} (stated below), we obtain
% \begin{equation*} 
% Z_{[k]} \sim -\sqrt{2\beta_0\log{s}} \sim -\sqrt{2\beta_0(1-\beta)\log{p}}.
% % , \quad\text{as}\;\;p\to\infty.
% \end{equation*}
% Therefore, we have,
\begin{equation} \label{eq:approx-exact-boundary-proof-necessary-6}
    % f_p(\min_{i\in S}z_\nu(i)) =
    \frac{Z_{[k]}}{\sqrt{2\log{p}}}
    = \frac{Z_{[k]}}{\sqrt{2\log{s}}} \frac{\sqrt{2\log{s}}}{\sqrt{2\log{p}}} 
    \to -\sqrt{\beta_0(1-\beta)}
    % \left(-(\sqrt{\overline{r}}+\sqrt{q}), -(\sqrt{\overline{r}}-\sqrt{q})\right) 
    \quad\text{in probability}.
\end{equation}
Since we know (by solving a quadratic inequality) that
\begin{equation} \label{eq:approx-exact-boundary-proof-necessary-7}
    f_p(x)<q \iff \frac{x}{\sqrt{2\log{p}}} \in \left(-(\sqrt{\overline{r}}+\sqrt{q}), -(\sqrt{\overline{r}}-\sqrt{q})\right),
\end{equation}
combining \eqref{eq:approx-exact-boundary-proof-necessary-5}, \eqref{eq:approx-exact-boundary-proof-necessary-6}, and 
\eqref{eq:approx-exact-boundary-proof-necessary-7}, it follows that
\begin{equation*}
    %\min_{i\in S} \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{2\log{p}} 
    \P\left[ f_p\left(Z_\nu(i^\dagger)\right) < q \right] \ge \P\left[ f_p\left(Z_{[k]}\right) < q \right] \to 1.
\end{equation*}
Finally, using \eqref{eq:chi-square-necessary-9}, we conclude that 
$$
\P\left[\min_{i\in S}x(i)<t^*\right] = 
\P\left[\frac{m_{S}}{2\log{p}} < q\right] \ge
\P\left[o_\P(1) + f_p\left(Z_\nu(i^\dagger)\right) < q \right] \to 1.
$$
Therefore, the two terms on the right-hand-side of \eqref{eq:approx-exact-boundary-proof-necessary-1} both converge 1. 
This completes the proof of the necessary condition.
\end{proof}

It only remains to justify \eqref{eq:approx-exact-boundary-proof-necessary-6}.

\begin{lemma}[Relative stability of order statistics]
\label{lemma:relative-stability-order-statistics}
Let $Z_{[1]} \le \ldots \le Z_{[s]}$ be the order statistics of $s$ iid standard Gaussian random variables.
Let $\beta_0\in(0,1]$ and define $k=\lfloor s^{1-\beta_0}\rfloor$, then we have
\begin{equation}
    \frac{Z_{[k]}}{\sqrt{2\log{s}}} \to -\sqrt{\beta_0} \quad\text{in probability}.
\end{equation}
\end{lemma}

\begin{proof}[Proof of Lemma \ref{lemma:relative-stability-order-statistics}]
Using the Renyi representation for order statistics, we write
\begin{equation} \label{eq:relative-stability-order-statistics-proof-1}
    Z_{[i]} = \Phi^{\leftarrow}(U_{[i]}),
\end{equation}
where $U_{[i]}$ is the $i^\mathrm{th}$ (smallest) order statistic of $s$ independent uniform random variables over $(0,1)$.
Since $U_{[i]}$ has a $\mathrm{Beta}(i, s+1-i)$ distribution, with mean and standard deviation,
$$
\E[U_{[k]}] = k/(s+1) \sim s^{-\beta_0}, 
\quad \text{and} \quad
{\mathrm{sd}(U_{[k]})} = \frac{1}{s+1}\sqrt{\frac{k(s+1-k)}{s+2}} \sim s^{-\frac{1+\beta_0}{2}},
$$
we obtain by Chebyshev's inequality 
% (since $\E[U_{[k]}]/\mathrm{sd}(U_{[k]})\sim p^{(1-\beta_0)/2}$) 
$$
\P\left[s^{-\beta_0}(1-\epsilon) < U_{[k]} < s^{-\beta_0}(1+\epsilon)\right] \to 1,
$$
where $\epsilon$ is an arbitrary positive constant.
This implies, by representation \eqref{eq:relative-stability-order-statistics-proof-1},
\begin{equation} \label{eq:relative-stability-order-statistics-proof-2}
    \P\left[\Phi^{\leftarrow}\left(s^{-\beta_0}(1-\epsilon)\right) < Z_{[k]} < \Phi^{\leftarrow}\left(s^{-\beta_0}(1+\epsilon)\right)\right] \to 1.
\end{equation}
Using the expression for standard Gaussian quantiles (see, e.g., Proposition 1.1. in \cite{gao2018fundamental}), we know that
\begin{align*}
    \Phi^{\leftarrow}\left(s^{-\beta_0}(1-\epsilon)\right) 
    &\sim -\sqrt{2\log{\left(s^{\beta_0}/(1-\epsilon)\right)}} \\
    &= -\sqrt{2(\beta_0\log{s} - \log{(1-\epsilon)})} \sim -\sqrt{2\beta_0\log{s}},
\end{align*}
and similarly $\Phi^{\leftarrow}\left(s^{-\beta_0}(1+\epsilon)\right)\sim -\sqrt{2\beta_0\log{s}}$.
Since both ends of the interval in \eqref{eq:relative-stability-order-statistics-proof-2} are asymptotic to $-\sqrt{2\beta_0\log{s}}$, 
% dividing through by $\sqrt{2\log{s}}$, and 
the desired conclusion follows.
\end{proof}

\subsection{Proof of Proposition \ref{prop:signal-size-odds-ratio} and Corollary \ref{cor:signal-limits-OR}}
\label{subsec:proof-signal-size-odds-ratio}

\begin{proof}[Proof of Proposition \ref{prop:signal-size-odds-ratio} and Corollary \ref{cor:signal-limits-OR}]
We parametrize the 2-by-2 multinomial distribution with the parameter $\delta$, 
\begin{equation} \label{eq:reparametrize-2-by-2-table-1}
    \mu_{11} = \phi_1\theta_1+\delta,\quad 
    \mu_{12} = \phi_1\theta_2-\delta,\quad 
    \mu_{21} = \phi_2\theta_1-\delta,\quad 
    \mu_{22} = \phi_2\theta_2+\delta.
\end{equation}
By relabelling of categories, we may assume $0<\theta_1,\phi_1\le1/2$ without loss of generality.
Note that $\delta$ must lie within the range $[\delta_\mathrm{min}, \delta_\mathrm{max}]$, where
$$
\delta_\mathrm{min} := \max\{-\phi_1\theta_1, -\phi_2\theta_2, \phi_1\theta_2-1, \phi_2\theta_1-1\} 
= -\phi_1\theta_1,
$$
and
$$
\delta_\mathrm{max} := \min\{1-\phi_1\theta_1, 1-\phi_2\theta_2, \phi_1\theta_2, \phi_2\theta_1\}
= \min\{\phi_1\theta_2, \phi_2\theta_1\},
$$
in order for $\mu_{ij}\ge0$ for all $i,j\in \{1,2\}$.
Under this parametrization, Relation \eqref{eq:odds-ratio} then becomes
\begin{equation} \label{eq:odds-ratio-delta}
    \text{R} = \frac{\mu_{11}\mu_{22}}{\mu_{12}\mu_{21}}
    = \frac{\phi_1\theta_1\phi_2\theta_2 + \delta(\phi_1\theta_1+\phi_2\theta_2)+\delta^2}{\phi_1\theta_1\phi_2\theta_2 - \delta(\phi_1\theta_2+\phi_2\theta_1)+\delta^2},
\end{equation}
which is one-to-one and increasing in $\delta$ on $(\delta_\mathrm{min}, \delta_\mathrm{max})$.
Equation \eqref{eq:signal-size-chisq} becomes
\begin{equation} \label{eq:signal-size-chisq-delta}
w^2 = \sum_{i=1}^2 \sum_{j=1}^2 \frac{(\mu_{ij} - \phi_i\theta_j)^2}{\phi_i\theta_j}
= \delta^2\sum_i\sum_j \frac{1}{\phi_i\theta_j}
= \frac{\delta^2}{\phi_1\theta_1\phi_2\theta_2},
\end{equation}
Solving for $\delta$ in \eqref{eq:odds-ratio-delta}, and plugging into the expression for signal size \eqref{eq:signal-size-chisq-delta} yields Relation \eqref{eq:signal-size-odds-ratio}.
Corollary \ref{cor:signal-limits-OR} follows from the fact that $w^2(\delta)$ is decreasing on $[\delta_\mathrm{min},0)$, increasing on $(0,\delta_\mathrm{max}]$, with limits
$$
\lim_{d\to \delta_\mathrm{min}} w^2(\delta) = \frac{\phi_1\theta_1}{\phi_2\theta_2},
\quad
\text{and}
\quad
\lim_{d\to \delta_\mathrm{max}} w^2(\delta) = \min\left\{\frac{\phi_1\theta_2}{\phi_2\theta_1}, \frac{\phi_2\theta_1}{\phi_1\theta_2}\right\}.
$$
The other three cases ($1/2\le\theta_1,\phi_1\le1$; $0<\theta_1\le1/2\le\phi_1\le1$; and $0\le\phi_1\le1/2\le\theta_1\le1$) may be obtained similarly, or by appealing to the symmetry of the problem.
\end{proof}

\begin{proof}[Proof of Corollary \ref{cor:optimal-design}]
Using the parametrization in \eqref{eq:reparametrize-2-by-2-table-1} and in Corollary \ref{cor:signal-size-odds-ratio-conditional-frequency}, we solve for $\delta$ in \eqref{eq:odds-ratio-delta} to obtain
\begin{align}
    \delta &= \frac{\phi_1 fR}{fR+1-f} - \left(\frac{\phi_1 fR}{fR+1-f} + f(1-\phi_1)\right)\phi_1 \nonumber \\
    &= \frac{f(1-f)\phi_1(1-\phi_1)(R-1)}{fR+1-f}. \label{eq:reparametrize-2-by-2-table-2}
\end{align}
Substituting \eqref{eq:reparametrize-2-by-2-table-2} into the expression \eqref{eq:signal-size-chisq-delta}, after some simplification, yields
\begin{equation} \label{eq:reparametrize-2-by-2-table-3}
    w^2 = \frac{f(1-f)\phi_1(1-\phi_1)(R-1)^2}{\left[\phi_1 R + (1-\phi_1)D\right]\left[\phi_1 + (1-\phi_1)D\right]},
\end{equation}
where $D = fR+1-f > 0$.
Therefore, he derivative of \eqref{eq:reparametrize-2-by-2-table-3} with respect to $\phi_1$ is
\begin{equation} \label{eq:signal-size-first-derivative}
    \frac{\mathrm{d}w^2}{\mathrm{d}\phi_1} = 
    \frac{f(1-f)(R-1)^2}{\left[\phi_1 R+(1-\phi_1)D\right]^2 \left[\phi_1+(1-\phi_1)D\right]^2} \left[(D^2-R)\phi_1^2 - 2D^2\phi_1 + D^2\right].
\end{equation}
Further, we obtain the second derivative with respect to $\phi_1$,
\begin{equation} \label{eq:signal-size-second-derivative}
    \frac{\mathrm{d}^2w^2}{\mathrm{d}\phi_1^2} = 
    h(R,f) \left[(\phi_1-1)D^2 - \phi_1R\right],
\end{equation}
where $h$ is some function of $(R,f)$ taking on strictly positive values.

Since $\left[(\phi_1-1)D^2 - \phi_1R\right]<0$, the second derivative \eqref{eq:signal-size-second-derivative} must be strictly negative on $[0,1]$.
This implies that the first derivative \eqref{eq:signal-size-first-derivative} is strictly decreasing on $[0,1]$. 
Since the first derivative \eqref{eq:signal-size-first-derivative} is strictly positive at $\phi_1=0$, and strictly negative at $\phi_1=1$, it must have a unique zero between 0 and 1, and hence, the solution to $(D^2-R)\phi_1^2 - 2D^2\phi_1 + D^2 = 0$ in the interval of $[0,1]$ must be the maximizer of \eqref{eq:reparametrize-2-by-2-table-3} --- when $D^2-R>0$, the smaller of the two roots maximizes \eqref{eq:reparametrize-2-by-2-table-3}, and when $D^2-R<0$, it is the larger of the two.
They share the same expression ${D}/{(D+\sqrt{R})}$, which coincides with \eqref{eq:optimal-design}.
Finally, when $D^2=R$, the only root $\phi_1^*=1/2$, which also coincides with \eqref{eq:optimal-design}, is the maximizer of \eqref{eq:reparametrize-2-by-2-table-3}.
\end{proof}

### 2020-08-17 SB_draft.tex
add draft converted from thesis

% Use the University of Michigan thesis class.
\documentclass[thesis]{./tex/thesis-umich}

% Use natbib for citation styling
\usepackage{natbib}
%\bibliographystyle{abbrvnat}
\bibliographystyle{apa}
\setcitestyle{authoryear,open={(},close={)}}

%
% My definitions:
%
\def\bbN{{\mathbb N}}
\def\bbZ{{\mathbb Z}}
\def\bbR{{\mathbb R}}
\def\bbC{{\mathbb C}}

\def\P{{\mathbb P}}
\def\E{{\mathbb E}}

\newcommand{\var}{{\rm {Var}}}
\newcommand{\cov}{{\rm {Cov}}}

\def\N{\mathbb N}
\def\R{\mathbb R}
\def\Z{\mathbb Z}
\usepackage{bm}
\renewcommand\vec[1]{{\bm #1}}

\def\alert#1{\fbox{#1}}
\def\what{\widehat}
\def\noi{\noindent}
\def\MSE{{\rm m.s.e.}}
% \newcommand\comment[1]{{}}
\def\refeq#1{(\ref{e:#1})}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
\newcommand\version[2]{{#1}} % The short version of the paper
%\newcommand\version[2]{{#2}} % The long version of the paper

%\startlocaldefs
\numberwithin{equation}{chapter}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[chapter]
% my defs
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}{Assumption}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
%\endlocaldefs

% Title of the thesis
\title{Concentration of Maxima and Fundamental Limits in High-Dimensional  Testing and Inference}
% \title{Phase Transitions in High-dimensional Testing Problems and Concentration of Maxima}

% Author name
\author{Zheng Gao\\Stilian Stoev}

% Email
\email{gaozheng@umich.edu\\sstoev@umich.edu}

% ORCID
\ORCID{xxxx-xxxx-xxxx-xxxx}

% Department
\department{Statistics}

% Year of completion
\year=2020

% Frontispiece
\frontispiece{
\includegraphics[width=5.5in]{./pics/frontispiece.jpg}\\
\vspace{1in}
\begin{flushleft}
{%\fontfamily{pbk}\selectfont 
For what is a man, what has he got? %\\
%If not himself, then he has naught.
}
\end{flushleft}
}

% Default style for front pages
\frontpagestyle{1}

% Dedication
\dedication{ %
\centering
}

% Acknowledgments
\acknowledgments{ %
}

% This command sets the width of the acknowledgments area as a fraction
% of the total width of the text area.
\acknowledgmentswidth{0.8}

% Preface
% \preface[2]{ %
% This is a preface.}

% Commands to hide or show lists of figures, tables, etc.
\hidelistoftables
% \showlistofprograms
% \showlistofappendices

% Definition of any abbreviations used.
\abbreviations{
 \acro{AGG}{asymptotically generalized Gaussian}
 \acro{BH}{Benjamini-Hochberg}
 \acro{CDF}{cumulative distribution function}
 \acro{FDR}{false discovery rate}
 \acro{FNR}{false non-discovery rate}
 \acro{FWER}{family-wise error rate}
 \acro{FWNR}{family-wise non-discovery rate}
 \acro{GWAS}{genome-wide association studies}
 \acro{HC}{higher-criticism}
 \acro{iid}{independent and identically distributed}
 \acro{LR}{likelihood-ratio}
 \acro{RS}{relatively stable/relative stability}
 \acro{SNP}{single-nucleotide polymorphisms}
 \acro{URS}{uniform relatively stable/uniform relative stability}
}

% Some abstract text
\abstract{
This text presents a collection of new results and recent developments on the phase transition phenomena in sparse signal problems, and makes the connection to the forces behind these statistcal results --- a probablistic phenomena known as concentration of maxima.
We begin with idealized models where high-dimensional signals are observed with independent additive Gaussian noise.
Under suitable parametrization of the signal sparsity and signal sizes, 
we characterize several new phase transition phenomena in high-dimensional additive error models, and derive the signal sizes necessary and sufficient for statistical procedures to simultaneously control false discovery (in terms of Type I error, {FDR}, or {FWER}) and missed detection (in terms of Type II error, {FNR}, or {FWNR}) in large dimensions.
% Several new phase transition phenomena are characterized.
Specifically, we show that, depending on the signal sparsity and signal sizes, the sum of the statistical risks for false discovery  and missed detection either can be controlled at very low levels in high dimensions, or must be at least one in the limit, for all thresholding procedures.

The phase transition in the case of family-wise type I and type II error control is further generalized to cover non-Gaussian and dependent observations.
We show that the sharp zero-one law continues to hold under a very broad class of error dependence structures, and for a very broad class of error distributions with light, rapidly varying, tails.
The key to this important generalization is a certain {concentration of maxima} phenomenon known as relative stability. 
We demystify the dependence conditions of the phase transition by providing a complete characterization of the relative stability concept for Gaussian triangular arrays in terms of their correlation structures.
% The proof uses classic Sudakov-Fernique and Slepian lemma arguments along with a curious application of Ramsey's coloring theorem.

Finally, motivated by marginal screenings of categorical variables, we study high-dimensional multiple testing problems where test statistics have approximate chi-square distributions.
Phase transitions are established for support recovery problems in high-dimensional chi-square models.
Remarkably, the degree-of-freedom parameters in the chi-square distributions do not affect the boundaries in all phase transitions.
% Several well-known procedures are shown to attain these boundaries.
We also elucidate on the notion of signal sizes in association tests by characterizing its relationship with marginal frequencies, odds ratio, and sample sizes in $2\times2$ contingency tables. 
This allows us to illustrate an interesting manifestation of the phase transition phenomena in % \ac{GWAS},
genome-wide association studies (GWAS), 
and explain some long-standing empirical observations on the discoverability of signals in GWAS.
As an auxiliary result, we show that, perhaps surprisingly, given total sample sizes, balanced designs in such association studies rarely deliver optimal power. % for detecting rare genetic variants with high odds ratios.
% We provide explicit formulas for power calculations, as well as software tools for finding the optimal study designs.
% The phase transition phenomena is demonstrated with numerical simulations, and with empirical evidence from GWAS.
% data from the NHGRI-EBI GWAS catalog.
}
%\hideabstractpagenumber

%% DOCUMENT AREA
\begin{document}

\chapter{Introduction}
\label{chap:intro}
\input{./1.intro/introduction.tex}

\chapter{Techincal Preparations and Background}
\label{chap:background}
\input{./2.background/background.tex}

\chapter{The Phase Transition Phenomena in Independent Gaussian Error Models} 
\label{chap:phase-transitions}
\input{./3.phase_transitions/phase_transitions.tex}

\chapter{Exact Support Recovery and Minimax Optimality} 
\label{chap:exact-support-recovery}
\input{./4.exact_support_recovery/exact_support_recovery.tex}

\chapter{Characterization of Uniform Relative Stability for Gaussian Arrays}
\label{chap:URS}
\input{./5.URS/URS.tex}

\chapter{The Phase Transition Phenomena in Genome-wide Association Studies} 
\label{chap:GWAS}
\input{./6.GWAS/GWAS.tex}

% \appendix
% \chapter{U-PASS: A Software for Unified Power Analysis and Forensics for Qualitative Traits in Genetic Association Studies} \label{app:UPASS}
% \addcontentsline{toc}{chapter}{Appendix~\ref{app:UPASS}: U-PASS: A Software for Unified Power Analysis and Forensics for Qualitative Traits in Genetic Association Studies}
% \input{./appendix/UPASS.tex}

% \chapter{Using Appendices} \label{app:appendix2}

% Give this command the relative path to the .bib file.
\bibliography{./tex/thesis}

\end{document}

### 2020-08-17 appendix/A.alternative_specification.tex
add draft converted from thesis

% \subsection{Two ways to specify alternative hypothesis}

In the power calculations outlined in Section \ref{sec:power-analysis-overview}, the disease models are used to describe the distribution of the data under the alternative hypothesis.
Specifically, they are used to specify the conditional distributions of the allele variants, given the phenotypes.
The probability of observing a risk allele in the control group, known as risk allele frequency (RAF), is defined as follows,
\begin{equation}
    f := \mathbb{P}[\,\text{risk allele}\,|\,\text{control group}\,] 
    = \frac{\mu_{21}}{1-\phi} 
    = \frac{\pi_{22} + \pi_{21}/2}{\pi_{22} + \pi_{21} + \pi_{20}}.
\end{equation}
The risk allele frquency is fully determined by the disease model through the probability table $\mu$. This parametrization was also introduced in \eqref{eq:RAF}.

Similarly, the odds ratio between the two allele variants, 
\begin{equation}
    R:=\frac{\mu_{11}\mu_{22}}{\mu_{12}\mu_{21}} 
    = \frac{(\pi_{12} + \pi_{11}/2)(\pi_{20} + \pi_{21}/2)}{(\pi_{10} + \pi_{11}/2)(\pi_{22} + \pi_{21}/2)},
\end{equation}
is also determined by the disease model and its parameters. See definition in \eqref{eq:odds-ratio}.

In turn, the parameters $(f, R)$, together with the sample sizes $(\phi, n)$, fully describe the distribution of our data under the alternative hypothesis (by determining the probability vector $\mu$ and the sample size $n$).
Power of association tests, therefore, depends on (and only on) the set of ``canonical parameters'':

\begin{itemize}
    \item Risk allele frequency among the controls (f).
    \item Odds ratio (R) of having the defined trait between the two allele variants.
    \item One of the two equivalent ways of parametrizing the sample sizes.
\end{itemize}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/flowchart.eps}
    \caption{The process of a typical power analysis for genetic association tests.
    The quantities depend on, and can be calculated from the values of their parents in the directed graph. 
    Power can be calculated as long as one set of parameters in each branch is known.
    While there is a one-to-one correspondence between the sample size specifications $(n_1, n_2)$ and $(\phi, n)$, the mapping from disease model specifications to $(f, R)$ is many-to-one. 
    %That is, one cannot recover the disease model specifications from the allelic tables, or equivalently, reported risk allele frequencies and odds ratios.
    }
    \label{fig:flowchart}
\end{figure}

We visualize the process of power analysis in Figure \ref{fig:flowchart}.
Notice that in power calculations, we can either describe the alternative hypothesis with a disease model, or through the canonical parameters ($f, R$). 
Both approaches are sufficient for the purpose of power analysis.
Unfortunately, these two parametrizations are commonly confused.
We emphasize that the risk allele frequency in the control group ($f$) is not equivalent to the risk allele frequency in the general population ($p$); odds ratio ($R$) is not equivalent to genotype relative risk (GRR).

\bigskip

As illustrated in  Figure \ref{fig:flowchart}, power calculations are mediated through the canonical parameters, which are invariant to different model specifications.
That is, different disease model specifications may lead to the {\it same} set of canonical parameters ($f, R$), and consequently the) {\it same} distributions of the allele variant counts.
From a statistical perspective, the disease models that map to the same set of canonical parameters are equivalent in terms of power.

For example, the following set of disease models and parameters imply the same set of canonical parameters $(f = 0.290, R = 1.575)$, and therefore enjoy the same power at the same sample sizes ($n_1 = n_2 = 1000$).
\begin{center}
    \begin{tabular}{cc|cc}
    \hline
    Disease Model & $(\text{Prev}, p, \text{GRR})$ & $(f, R)$ & Power \\
    \hline 
    Multiplicative & $(0.1, 0.3, 1.500)$ & $(0.290, 1.575)$ & 0.990 \\
    Additive & $(0.1, 0.3, 1.588)$ & $(0.290, 1.575)$ & 0.990 \\
    Dominant & $(0.1, 0.3, 1.909)$ & $(0.290, 1.575)$ & 0.990 \\
    Recessive & $(0.1, 0.3, 2.666)$ & $(0.290, 1.575)$ & 0.990 \\
    \hline
    \end{tabular}
\end{center}

Conversely, different disease models with the same parameters, map to drastically different canonical parameters.
For example, the default disease model parameters in the GAS calculator,
\begin{align}
    \text{Disease prevalence in the population}: & \quad \text{Prev} = 0.1 \\
    \text{Risk allele frequency in the population}: & \quad p = 0.5\\
    \text{Genotype relative risk}: & \quad \text{GRR} = 1.5.
\end{align}
map to very different canonical parameters under different disease model assumptions (assuming the same sample sizes of $n_1 = n_2 = 1000$), which leads to drastically different statistical power.
\begin{center}
    \begin{tabular}{cc|cc}
    \hline
    Disease Model & $(\text{Prev}, p, \text{GRR})$ & $(f, R)$ & Power \\
    \hline 
    Multiplicative & $(0.1, 0.5, 1.5)$ & $(0.489, 1.568)$ & 0.995 \\
    Additive & $(0.1, 0.5, 1.5)$ & $(0.491, 1.453)$ & 0.920 \\
    Dominant & $(0.1, 0.5, 1.5)$ & $(0.495, 1.224)$ & 0.282 \\
    Recessive & $(0.1, 0.5, 1.5)$ & $(0.494, 1.281)$ & 0.098 \\
    \hline
    \end{tabular}
\end{center}

In the application, we provide users with a ``Disease model converter'' that implements this many-to-one conversion from the disease model specifications to the canonical parameters.

% \subsection{Comparisons of the two approaches}
% \label{subsec:comparing-two-approaches}
\bigskip

While the disease models may carry additional insights into the biological process, the canonical parameters also have their unique advantages.
We offer an incomplete list of comparisons of the two approaches, and discuss their usage in practice.

\medskip\noindent
{\bf Interpretability and communicability.}
In general, geneticists and biostatisticians seem to agree that disease models are more interpretable.
The concept of genotype relative risks, in particular, seems easier to reason about than odds ratios in the canonical parameters definition.
Disease models also seem to be the de facto mode of model specification when performing power analysis for study planning and grant applications.

The ``nonparametric'' approach to model specification through the canonical parameters is somewhat lesser known to the statistical genetics community.
The canonical parameters are typically estimated and reported as outcomes of the research, but not used as inputs to the power analysis for planning purposes.

\medskip\noindent
{\bf Availability of parameter estimates.}
The canonical parameters $f$ and $R$ can be estimated from data collected in the study.
They are also reported and curated in GWAS catalogs such as the NHGRI-EBI Catalog \citep{macarthur2016new}.

On the other hand, accurate information regarding the disease model parameters can be more difficult to obtain, partly because some parameters in the disease models cannot be estimated from the association studies alone.

In particular, disease prevalence in population (Prev), as well as risk allele frequency in population ($p$), must be obtained from other studies or surveys targeting the general population; the association studies, unless matching the proportion of cases in the population vs in the study ($\phi=\text{Prev}$), cannot produce estimates without using external information.
Genetic association studies rarely explicitly estimate the disease model and its parameters.
In fact, we are not aware of a GWAS catalog that reports and curates the disease models and their estimated parameters.

This paucity of information on disease model parameters is not an issue if we are planning to study a trait for which we have little prior knowledge.
In this case, the purpose of power analysis is to determine the range of models and parameters that lead to discovery of associations, given the study designs.

In contrast, in confirmatory / follow-up studies and systematic reviews, our main interest is in the statistical validity of the reported findings.
Power analysis then serves to find efficient designs, and to validate the claims made.
Knowledge obtained in prior studies (in the form of parameter estimates) are indeed necessary.

\medskip\noindent
{\bf Robustness against model misspecification.}
Disease models are useful in as much as they help us understand the biology behind the data we observe.
Unfortunately, like all models, they can be misspecified. 
For example, the following genotype relative risks,
\begin{equation*}
    \frac{\pi_{10}}{\pi_{10} + \pi_{20}} : \frac{\pi_{11}}{\pi_{11} + \pi_{21}} : \frac{\pi_{12}}{\pi_{12} + \pi_{22}}
    = 1 : 3 : 4,
\end{equation*}
does not follow any of the common disease models.
In this case, different studies may come up with different disease models (say, Dominant and Additive), and of course, different parameter estimates.

Suppose a researcher wishes to perform a meta analysis or confirmatory experiment of the existing results, where the literature reports inconsistent estimates of disease models and parameters,
he would a have a difficult time pooling the information from these different sources. 
And even when they are pooled, the resulting model usually does not fall in one of the familiar categories --- there is no existing tool with which to perform power analysis.
The researcher will likely have to forgo the information from one model, and use estimates from only the other.

On the other hand, the canonical parameters are invariant to the disease model choices, and accommodate models falling outside the usual categories. 
They can also be easily combined to produce pooled estimates.
This universality allows us to perform power analysis in a unified fashion, regardless of the disease models assumed.
This also paves the way for the ``OR-RAF diagram'', as well as systematic reviews of statistical validity of existing studies; see Section \ref{sec:review-GWAS-studies} below.

\medskip\noindent
{\bf Robustness against human errors.}
The disparity in availability of parameter estimates we mentioned earlier can lead to unintended consequences, one of which is potentially incorrect usage of power calculators.
This issue, although minor, is critical to the correctness of the results of our power analysis.

Recall that the specification of a disease model requires as input the risk allele frequency (RAF) in the general population ($p$).
The RAF reported in the NHGRI-EBI Catalog \citep{macarthur2016new}, in contrast, refers to RAF in the control group ($f$).
With RAF in population often unavailable, it is tempting to substitute the RAF in control group into the calculations.
While the two quantities may be close when diseases prevalence and penetrance are low, their difference becomes non-negligible if either of the two conditions are violated, leading to grossly distorted results.

Performing power analysis with the canonical parameters is not guaranteed to prevent this human error, as mistake in the other direction could also happen.
But perhaps it is more robust to such mistakes, since what is readily available matches with what is required as input.

\medskip\noindent
{\bf Compatibility of parameters.}
We make another minor comment regarding correct usage of disease models.

We caution users that not all values of the disease model parameter combinations are valid.
For example, in a multiplicative model, the parameters 
\begin{equation*}
    p = 0.1, \quad \text{Prev} = 0.5, \quad \text{GRR} = 1.5,
\end{equation*}
would result in the conditional probability of having two risk allele copies greater than 1.
(In this case, the GAS calculator \citep{johnson2017gas} would produce the error message: ``I don't like the genetic model you requested!'', without explicitly pointing to the compatibility issue.)

Although an experienced geneticist would immediately notice the impossibility of the disease model parameter combinations, these contradictions may not be obvious to the untrained eye.
The end user of the software -- experienced or not -- is ultimately responsible for inputting valid values when specifying a disease model.

On the other hand, any combination of 
\begin{equation*}
    f\in(0,1), \quad \text{and} \quad R\in(0,+\infty)
\end{equation*}
is valid. 
Parameter compatibility is not an problem for the set of canonical parameters.

\medskip\noindent
{\bf Recommendations on model specification in power analysis.}
Since both the disease models and the canonical parameters are sufficient for the purpose of power analysis, it is natural to ask why (and when) should one take the canonical parameters approach, given that the more familiar disease models would also suffice.

We believe that either approach may be preferred, depending on the use cases.
Recall that power analysis is useful in at least three scenarios:
\begin{enumerate}
    \item {\it Planning for an exploratory study, where little is known about the associations.}

    In this case, the top branch in Figure \ref{fig:flowchart} is unknown to the researcher.
    The goal is to find out the range of disease models and parameters that are discoverable given the study designs.
    Power analysis is also to some extent exploratory in nature.

    \item {\it Planning for a confirmatory study, where something is known about the associations and one wishes to validate the findings with an efficient design.}

    In this case, the top branch in Figure \ref{fig:flowchart} is known, and the variables in the bottom branch is what we are solving for.
    The goal of power analysis is to provide a set of efficient study designs with sufficient power.

    \item {\it Reviewing the reported findings and verify the statistical validity.}

    In the third case, one looks to find out whether the claims of statistical significance are congruent with the evidence from data.
    A claim supported by very weak or contradictory evidence should invite further investigations.
    In this case, both branches in Figure \ref{fig:flowchart} have to be available.
\end{enumerate}

In view of the discussions above, we propose the following general guidelines for power analysis in genetic association studies.

\begin{itemize}
    \item When designing an association study where little to no prior information is available, either approach is valid. However, disease models may be easier to interpret and communicate.
    \item When designing a follow-up or confirmatory study, or conducting a systematic review, researchers may wish to choose the approach for which the parameter estimates are available, or of better quality. Typically the canonical parameters are better estimated, reported, and curated.
\end{itemize}
% The simple answer is the following: the canonical parameter approach is better suited to planning confirmatory studies and performing systematic reviews, which to the best of our knowledge, could not be readily done prior to our tool. 
% We expect many exceptions to these suggested choices.
The comments we made about the two approaches should not be taken as criticisms, but rather as reminders of the potential pitfalls in power analysis.
In either approach, care needs to be exercised in order to produce valid results.

### 2020-08-17 appendix/A.power_analysis.tex
add draft converted from thesis

We briefly review the main steps of a typical power analysis for genetic association studies.

\medskip
{\bf 1. Disease model specifications.}
A typical power analysis for genetic association studies begin by specifying an alternative hypothesis through a disease model (dominant, recessive, multiplicative, additive, etc.), which assumes:

\begin{itemize}
    \item The genotype relative risks (GRR).
    \item Risk allele frequency in the general population ($p$).
    \item Disease prevalence in the general population (Prev).
\end{itemize}

The disease model and parameters determine the joint distribution of the genotypes and phenotyes {\it in the population}, shown in the following table.

\begin{center}
    \begin{tabular}{cccc}
    \hline
    & \multicolumn{3}{c}{Risk allele copies} \\
    \cline{2-4}
    Population Prob. & 0 copies & 1 copy & 2 copies \\
    \hline
    Cases & $\pi_{10}$ & $\pi_{11}$ & $\pi_{12}$ \\
    Controls & $\pi_{20}$ & $\pi_{21}$ & $\pi_{22}$ \\
    \hline
    \end{tabular}
\end{center}

In the disease models, the conditional probabilities of having the disease, given the risk allele copy numbers, satisfy the following relations,

\begin{equation} \label{eq:GRR}
    \frac{\pi_{10}}{\pi_{10} + \pi_{20}} : \frac{\pi_{11}}{\pi_{11} + \pi_{21}} : \frac{\pi_{12}}{\pi_{12} + \pi_{22}}
    = \begin{cases}
    1 : \text{GRR} : \text{GRR}^2, &\text{Multiplicative} \\
    1 : \text{GRR} : 2\times\text{GRR}-1, & \text{Additive} \\
    1 : \text{GRR} : \text{GRR}, & \text{Dominant} \\
    1 : 1 : \text{GRR}, & \text{Recessive}
\end{cases}
\end{equation}
where GRR is strictly greater than 1 under the alternative, and equal to 1 under the null hypothesis.

The disease prevalence determines the sum of the probabilities of cases in the population,
\begin{equation} \label{eq:prev}
    \pi_{10} + \pi_{11} + \pi_{12} = \text{Prev}.
\end{equation}

The risk allele frequency in the general population, $p$, assuming Hardy-Weinberg equilibrium, satisfies 
\begin{equation} \label{eq:RAF-pop}
    \pi_{10} + \pi_{20} = (1-p)^2, \quad \pi_{11} + \pi_{21} = 2p(1-p), \quad \pi_{12} + \pi_{22} = p^2.
\end{equation}

The population probabilities are determined by the disease model and its parameters (GRR, Prev, and $p$).
The six unknowns  $(\pi_{10},\ldots,\pi_{22})$ and are solved for using the six equations above: two from Relation \eqref{eq:GRR}, one from \eqref{eq:prev}, and three from \eqref{eq:RAF-pop}.

\bigskip
{\bf 2. Sampling adjustments.}
Next, the probabilities of observing each genotype-phenotype combination are adjusted according the number of cases and controls recruited \emph{in the studies}, where the sample sizes are specified with the number of cases ($n_1$) and controls ($n_2$), or equivalently, the fraction of cases ($\phi$) and total number of subjects ($n$).

\begin{center}
    \begin{tabular}{cccc}
    \hline
    & \multicolumn{3}{c}{Risk allele copies} \\
    \cline{2-4}
    Prob. in study & 0 copies & 1 copy & 2 copies \\
    \hline
    Cases & $\pi_{10}\frac{\phi}{\text{Prev}}$ & $\pi_{11}\frac{\phi}{\text{Prev}}$ & $\pi_{12}\frac{\phi}{\text{Prev}}$ \\
    Controls & $\pi_{20}\frac{1-\phi}{1-\text{Prev}}$ & $\pi_{21}\frac{1-\phi}{1-\text{Prev}}$ & $\pi_{22}\frac{1-\phi}{1-\text{Prev}}$ \\
    \hline
    \end{tabular}
\end{center}

As an example, if $\phi > \text{Prev}$, the probabilities are adjusted to account for over-sampling of cases.
Conversely, adjustments are needed to account for under-sampling of cases.

The relative frequencies of allele type-phenotype combinations {\it in the study} are then calculated as follows.

\begin{center}
    \begin{tabular}{ccc}
    \hline
    & \multicolumn{2}{c}{Allele variant} \\
    \cline{2-3}
    Prob. in study & Risk allele & Non-risk allele \\
    \hline
    Cases & $\phi\left(\frac{\pi_{12}}{\text{Prev}}+\frac{\pi_{11}}{2\times\text{Prev}}\right)$ & $\phi\left(\frac{\pi_{11}}{2\times\text{Prev}}+\frac{\pi_{10}}{\text{Prev}}\right)$ \\
    Controls & $(1-\phi)\left(\frac{\pi_{22}}{1-\text{Prev}}+\frac{\pi_{21}}{2(1-\text{Prev})}\right)$ & $(1-\phi)\left(\frac{\pi_{21}}{2(1-\text{Prev})}+\frac{\pi_{20}}{1-\text{Prev}}\right)$ \\
    \hline
    \end{tabular}
\end{center}

This final table corresponds to the probabilities underlying the $2\times2$ multinomial counts that we introduced in Chapter \ref{chap:intro}.
We denote the relative frequencies of allele type-phenotype combinations with $\mu = (\mu_{11}, \mu_{12}, \mu_{21}, \mu_{22})$, as we did in Chapter \ref{chap:GWAS}.

\begin{center}
    \begin{tabular}{cccc}
    \hline
    & \multicolumn{2}{c}{Allele variant} & \\
    \cline{2-3}
    Prob. in study & Risk allele & Non-risk allele & Total by phenotype \\
    \hline
    Cases & $\mu_{11}$ & $\mu_{12}$ & $\phi = \mu_{11} + \mu_{12}$ \\
    Controls & $\mu_{21}$ & $\mu_{22}$ & $1-\phi = \mu_{21} + \mu_{22}$ \\
    \hline
    \end{tabular}
\end{center}

\bigskip
{\bf 3. Power calculations.}
Finally, the power of an statistical test is calculated as the probability of (a correct) rejection, assuming that the data (i.e., tabulated counts of the allele type-phenotype combinations) follow a multinomial or binomial distribution with sample size $2n$, since each individual has a pair of alleles.

These steps form the basis of the calculations implemented in the most existing tools, including the GAS calculator \citep{johnson2017gas}.

Some common association tests include the likelihood ratio test, Pearson's chi-square test, tests of zero slope coefficient in logistic regressions, as well as t-tests for equal proportions.
Although not explicitly stated, the GAS calculator assumes the test of association to be Welch's t-test.
In principal, power analysis has to be tailored to the association test used.
Fortunately, many of these tests are asymptotically equivalent in terms of power \citep{ferguson2017course, gao2019upass}, and results of the power approximation applies to all asymptotically equivalent tests.

% \footnote{Caveat: The final step in the power calculations does not apply to association tests performed directly on the 2-by-3 contingency tables of phenotype-genotype combinations (e.g., the Cochran-Armitage test).Therefore, the GAS calculator should not be used if these tests are to be applied.}.

### 2020-08-17 appendix/A.setup.tex
add draft converted from thesis

{\bf Software availability.}
U-PASS runs as an R Shiny application. It is a free, open source software under the MIT license.
A live instance of the application is hosted at 
\url{https://power.stat.lsa.umich.edu/u-pass/}.
The source code can be obtained from the repository hosting service Github, by running in the computer's terminal:
\begin{verbatim}
  clone https://github.com/Pill-GZ/U-PASS.git
\end{verbatim}
or by downloading directly from the GitHub page: 
\url{https://github.com/Pill-GZ/U-PASS}.

Should the user choose to run the application from their local machine, we recommend downloading the source code, and follow the next two steps of this user guide.

\bigskip
\noindent
{\bf Installation and dependencies.}
We have collected the required R packages inside the R script
\texttt{install\_required\_packages.R}.
These packages can be installed by navigating to the project folder, and running in the computer's terminal:
\begin{verbatim}
  Rscript install_required_packages.R 
\end{verbatim}
or by running the following command from inside R (RStudio):
\begin{verbatim}
  source("install_required_packages.R")    
\end{verbatim}
The U-PASS software itself requries no installation.

\bigskip
\noindent
{\bf Start/terminate the application.}
The application can be started by running in the computer's terminal:
\begin{verbatim}
  Rscript -e 'library(methods);
              shiny::runApp("./", launch.browser=TRUE)'
\end{verbatim}
or by running the following command from inside R (RStudio):
\begin{verbatim}
  shiny::runApp()
\end{verbatim}
The application can be terminated by simply closing the browser (or browser tab).
Alternatively, the application can be terminated by pressing \texttt{Ctrl} + \texttt{C} in the terminal, or by clicking on the red stop button in Rstudio.

### 2020-08-17 appendix/A.use_case_illustrations.tex
add draft converted from thesis

The software has three main functionalities, namely, reviewing the GWAS literature, designing prospective association studies, and converting between disease models and canonical parametrizations.
We detail each of the three functionalities of the application, and illustrate with examples.

\subsection{Reviewing reported findings in the GWAS catalog}
\label{sec:review-GWAS-studies}

The ``OR-RAF power diagram'' tab of the application provides a tool for reviewing reported associations from existing studies.
The application calculates statistical power based the core parameters common to models of qualitative traits:

\begin{itemize}
    \item Sample sizes, i.e., the number of cases and controls i.e., $(n_1, n_2)$ or $(\phi, n)$.
    \item The canonical parameters $(f, R)$.
\end{itemize}

Users need only prescribe the sample sizes, by one of two ways provided in the first box, i.e., total sample size + fraction of cases, or number of cases + number of controls.

Statistical power of common association tests, including the likelihood ratio test, chi-square test, Welch's t-test, and the LR test, have the same asymptotic power curves.
This shared power limit is calculated as a function of $f$ and $R$, and visualized as a heatmap referred to as the OR-RAF diagram.

\bigskip

We provide users the options to load and overlay findings reported in the NHGRI-EBI GWAS Catalog \citep{macarthur2016new}, or upload data from other sources compliant with the Catalog's data format.

The visualization is adaptive and fully interactive.
The initial sample sizes are dynamically adjusted, and automatically determined from texts of the article reporting the user selected loci.
Since the sampling structures are many and varied across different studies, and no uniform reporting format is enforced in the catalog, the initial sample sizes are best estimates from the extracted texts.
Information of the selected loci and the study is also dynamically displayed below the diagram.

\bigskip

The unified power analysis allows us to examine results from different studies employing different models and applicable tests, in the same diagram, with the same power limits.
This allows for a systematic review of reported findings for their statistical validity.
In particular, a reported association predicted to have low power given the study's sample size -- lying in the dark regions of the OR-RAF diagram -- while not impossible, invites further scrutiny.
%\footnote{It should be noted that a reported association predicted to have high power is not automatically accurate, as survival bias induced by multiple testing may inflate the reported $f$ and $R$ estimates.}. 
Studies where reported associations show misalignment with the predicted powered curves should also be further investigated for potential problems in the data curation process.

\begin{figure}
    \centering
    \includegraphics[width=0.49\textwidth]{figures/forensics1.png}
    \includegraphics[width=0.49\textwidth]{figures/forensics2.png}
    \caption{The OR-RAF diagram of two studies where gross misalignments were identified. 
    Left: Dominguez-Cruz et al. (2018), right: Haryono et al. (2015). 
    The reported odds ratios and risk allele frequencies of the discovered associations in these two papers are charted with orange (and red) circles. 
    Dark regions represent $f$-$R$ parameter combinations that are predicted to have low power of dicovery under the current sample sizes.
    See text for more comments.}
    \label{fig:forensics}
\end{figure}

We illustrate this forensics feature of the the software with two GWAS studies by \cite{dominguez2018pilot} and \cite{haryono2015pilot}, shown in Figure \ref{fig:forensics}. 
Gross misalignments with our power analysis were identified in both cases.
    Uppon contact, \cite{dominguez2018pilot} confirmed that this misalignment is the result of a problem in the data curation process of the GWAS Catalog (Dominguez-Cruz, personal communication). 
    In particular, the risk allele frequencies reported in the Catalog were based on all subjects in the study, as opposed to only the control group, while the Catalog requires that risk allele frequencies be reported in the control group only. 
    As a consequence, the risk allele frequencies are systematically overestimated, shifting the reported findings to the right in the diagram.
    The study by \cite{haryono2015pilot}, though may very well hold valid results, calls for further scrutiny of its statistical methodologies given the apparent incongruity of its conclusions at the reported the sample sizes.

In general, however, we expect the forensics aspect of our software to be useful for discovering problems with data entry and catalog curation process, as well as for assessing the reproducibility and robustness of reported findings.

\subsection{Designing association studies}
\label{sec:design-my-study}

The ``Design my studies'' tab of the application provides a tool for finding optimal designs of association studies.
The tool requires inputs in a four-step process.
\begin{enumerate}
    \item Model specification.
    \item Sample size constraints specification.
    \item False discovery Criteria specification.
    \item Power specification.
\end{enumerate}
Each of the steps can be specified in a number of alternative ways.

\bigskip
\noindent
{\bf Step 1: Model specification.}
We provide two three ways to describe the model for biological process of the disease or trait of interest.

The distribution of observations can be specified through the canonical parameters, risk allele frequency in the control group ($f$) and odds ratio ($R$).
Estimates for these quantities in previous studies of the same trait can be found in GWAS catalogs such as the NHGRI-EBI Catalog.
See Section \ref{sec:optimal-design} for their definitions.

Alternatively, users may opt to specify through the disease models, of which we implement the four most popular ones: additive, multiplicative, dominant, and recessive.
See Section \ref{sec:power-analysis-overview} below for the definitions of the quantities involved in the disease models.
We remind users the difference between the risk allele frequency in the control group ($f$) versus risk allele frequency in the general population ($p$); only the latter is used in the disease model specifications.

Advanced users may choose to use a more succinct ``signal size per sample'' option, which directly parametrizes the signal sizes ($\lambda/n$).
Definition of signal size $\lambda$ can be found in Section \ref{sec:odds-and-power}.

\bigskip
\noindent
{\bf Step 2: Sample size specifications.}
The second step requires users input the sample size constraints of the study.
The three available options are ``Budget / total number of subjects'', ``Number of cases'', and ``Fraction of cases''.
In the subsequent calculations, the selected and specified quantities are treated as fixed.
With only one unknown parameter left in the flow of power calculations (recall the flowchart in Fig. \ref{fig:flowchart}), we calculate power as a function of the  remaining specified parameter.
In particular,

\begin{itemize}
    \item If the constraint is total budget, power is shown as a function of the fraction of cases.
    \item If the constraint is number of cases, power is shown as a function of the number of controls.
    \item If the constraint is fraction of cases, power is shown as a function of the total number of subjects.
\end{itemize}

\bigskip
\noindent
{\bf Steps 3 and 4: False discovery and power specifications.}
The final two steps require as input the desired level of false discovery and false non-discovery control.
Both specification can be done through the marginal levels, i.e., Type I error and Type II error, or alternatively, through the multiple testing-adjusted levels, i.e., family-wise error rate (FWER) and family-wise non-discovery rate (FWNR).

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/UPASS_power_analysis.png}
    \caption{A screenshot of the user interface for the ``Design my study'' tab of the software. The inputs are as described in the numerical example in Section \ref{sec:design-my-study}. Results of the power calculation are visualized in an interactive plot in the application.}
    \label{fig:UPASS-power-analysis}
\end{figure}

\bigskip
\noindent
{\bf An example: designing prospective studies.}
A researcher wishes to find out how many controls are needed in order to detect an association between a risk variant described by a multiplicative model with parameters:
$$
\text{GRR} = 1.2, \quad p = 0.3, \quad \text{Prev} = 0.1.
$$
The study has recruited 1000 subjects in the case group, and is aiming for power of 80\% with FWER controlled at 5\% level adjusted for the multiplicity of $10^6$ tests.

In the application, we input the disease model parameters in the first step.
In the second step, we select the sample size constraint as ``number of cases'' and set to 1000.
The third step, we selected FWER as the criteria, and set the appropriate levels and multiplicity; a p-value cut off ($0.05/10^6=5\times10^{-8}$) is automatically calculated and displayed.
The final step, we choose ``Type II error / (1-power)'' as the target and select $1-80\%=20\%$.

The result of the calculation shows that the targeted power cannot be achieved at the current number of cases, no matter how many controls are recruited.
Therefore, the researcher should consider recruiting more subjects in the case group in order to in crease power.
For example, if there are instead 4000 subjects in the case group, then we would need only roughly 4929 controls in order to achieve the desired level of power.

\subsection{Converting disease models into canonical parametrization}

The ``Disease model converter'' tab of the application provides a tool for converting disease models into their implied canonical parameters.
See Figure \ref{fig:UPASS-model-converter} for a screenshot.

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/UPASS_model_converter.png}
    \caption{A screenshot of the user interface for the ``Disease model converter'' tab of the software. See Section \ref{sec:disease-models} for details of the conversion between disease models and canonical parameters in genome-wide association studies.}
    \label{fig:UPASS-model-converter}
\end{figure}

The converter implements the mapping from disease models to the canonical parameters as detailed in Section \ref{sec:disease-models} and  illustrated in Figure \ref{fig:flowchart}.
The tool also allows users to copy the model parameters into the ``Design my study'' tab for power calculations.
Several numerical examples, discussed in Section  \ref{sec:disease-models}, are provided in the tool.

### 2020-08-17 appendix/UPASS.tex
add draft converted from thesis

We introduce the software we developed for the power analysis of genetic association studies of qualitative traits in this appendix.
Section \ref{sec:power-analysis-overview} reviews the typical process of study planning employed by geneticists.
Disease models are often used to specify the distribution of observations under the alternative hypothesis in power analysis. 
In Section \ref{sec:disease-models}, we revisit the use of these disease models and argue for an alternative way of model parametrization that is better suited to conducting systematic reviews and confirmatory studies.
Section \ref{sec:user-guide} provides three example usages of the software.
Instructions for downloading, installing, launching, and terminating the software can be found in Section \ref{sec:UPASS-misc}.

\section{Power analysis in genetic association studies}
\label{sec:power-analysis-overview}
\input{./appendix/A.power_analysis.tex}

\section{Specification of alternatives in power analysis}
\label{sec:disease-models}
\input{./appendix/A.alternative_specification.tex}

\section{Use case illustrations}
\label{sec:user-guide}
\input{./appendix/A.use_case_illustrations.tex}

\section{Download, installation, and usage}
\label{sec:UPASS-misc}
\input{./appendix/A.setup.tex}

### 2020-08-17 figures/phase_diagram_Gaussian_ALL_boundaries.R

@@ -1,0 +1,53 @@
+#### Theoretical phase diagram - all known boundaries ####
+
+setEPS()
+postscript("phase_diagram_Gaussian_ALL_boundaries.eps", height = 5, width = 5)
+# png("phase_diagram_chisquared_ALL_boundaries.png", height = 400, width = 400, units = "px")
+plot.ylim <- 4
+beta.seq <- seq(0,1,0.001)
+strong.classification.boundary <- (sqrt(1-beta.seq) + 1)^2
+classification.boundary.FDR_FNDR <- (sqrt(1-beta.seq) + sqrt(beta.seq))^2
+classification.boundary.FWER_FNR <- rep(1, length(beta.seq))
+weak.classification.boundary <- beta.seq
+detection.boundary.bonf <- (1-sqrt(1-beta.seq))^2
+detection.boundary <- detection.boundary.bonf
+detection.boundary[1:(length(beta.seq)/2)] <- 0
+detection.boundary[(length(beta.seq)/2):(length(beta.seq)*3/4)] <- 
+  beta.seq[(length(beta.seq)/2):(length(beta.seq)*3/4)] - 0.5
+par(mar = c(3,3,2,2))
+plot(beta.seq, strong.classification.boundary, type = 'l',
+     xaxs="i", yaxs="i", ylim = c(0,plot.ylim),
+     xlab = expression(beta), ylab = expression(r),
+     las = 1)
+lines(beta.seq, detection.boundary, type = 'l')
+polygon(x = c(beta.seq,rev(beta.seq)),
+        y = c(detection.boundary,rep(0,length(beta.seq))),
+        col = grey(0.0), border = T)
+polygon(x = c(beta.seq,rev(beta.seq)),
+        y = c(detection.boundary,rev(weak.classification.boundary)),
+        col = grey(0.2), border = T)
+polygon(x = c(beta.seq,rev(beta.seq)),
+        y = c(weak.classification.boundary,rev(classification.boundary.FWER_FNR)),
+        col = grey(0.4), border = T)
+polygon(x = c(beta.seq,rev(beta.seq)),
+        y = c(classification.boundary.FWER_FNR,rev(classification.boundary.FDR_FNDR)),
+        col = grey(0.6), border = T)
+polygon(x = c(beta.seq,rev(beta.seq)),
+        y = c(classification.boundary.FDR_FNDR,rev(strong.classification.boundary)),
+        col = grey(0.8), border = T)
[…]

### 2020-08-18 abstract.tex
reformatting
Introduced the sptinger book format
(see folder "svmono")

* Made cosmetic changes to make it compile

* Rewriting the "Preface" by using the original "abstract"

* Note: The preface and the intro need strengtheneing in order to make our "selling points" more clear/compelling.

--- 2020-08-17 SB_draft.tex
@@
-% Use the University of Michigan thesis class.
-\documentclass[thesis]{./tex/thesis-umich}
+\preface
 
-% Use natbib for citation styling
-\usepackage{natbib}
-%\bibliographystyle{abbrvnat}
-\bibliographystyle{apa}
-\setcitestyle{authoryear,open={(},close={)}}
+%\fbox{From Springer}
+%{\color{blue}
+%% Please write your preface here
+%Use the template \emph{preface.tex} together with the Springer document class SVMono (monograph-type books) or SVMult (edited books) to %style your preface in the Springer layout.
 
+%A preface\index{preface} is a book's preliminary statement, usually written by the \textit{author or editor} of a work, which states its origin, scope,
+ %purpose, plan, and intended audience, and which sometimes includes afterthoughts and acknowledgments of assistance. 
+%When written by a person other than the author, it is called a foreword. The preface or foreword is distinct from the introduction, which deals with 
+%the subject of the work.
 %
-% My definitions:
-%
-\def\bbN{{\mathbb N}}
-\def\bbZ{{\mathbb Z}}
-\def\bbR{{\mathbb R}}
-\def\bbC{{\mathbb C}}
+%Customarily \textit{acknowledgments} are included as last part of the preface.}
 
-\def\P{{\mathbb P}}
-\def\E{{\mathbb E}}
+This text presents a collection of new results and recent developments on the phase transition phenomena in sparse signal problems.
+The main theme is the study of the fundamental limits in testing and signal support recovery in high-dimensions.  This subject has 
+received a lot of attention since the seminal works of \cite{ingster1998minimax,donoho2004higher} \fbox{Add references}. These works
+have established the presence of fundamental limits in the so-called {\em needle in haystack} problems, where sparse 
+signal is observed in high-dimensional additive noise.  In this setting, two archetypal problems arise -- the {\em signal detection} and 
+{\em support support recovery}.  Signal detection is a hypothesis testing problem, which aims to determine the presence of non-zero
+signal in some of the dimensions. On the other hand, support recovery is an inference problem, where one aims to estimates the set of
+coordinates with non-trivial signal.
 
-\newcommand{\var}{{\rm {Var}}}
-\newcommand{\cov}{{\rm {Cov}}}
+  to , pamounts to testing for the presence of a signal, while the support recovery is an inference problem
 
-\def\N{\mathbb N}
-\def\R{\mathbb R}
-\def\Z{\mathbb Z}
-\usepackage{bm}
-\renewcommand\vec[1]{{\bm #1}}
+aims to do inference 
+on the components of the signal  deals with
 
-\def\alert#1{\fbox{#1}}
-\def\what{\widehat}
-\def\noi{\noindent}
-\def\MSE{{\rm m.s.e.}}
-% \newcommand\comment[1]{{}}
-\def\refeq#1{(\ref{e:#1})}
+ , where one wants to {\em detect}
+the presence of a sparse signal observed with high-dimensional additive noise.
 
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
+testing and inference problems, which manifest themselves 
+as sharp phase-transitions between regimes where the statistical problems are possible or impossible to solve.
 
-\newcommand*\diff{\mathop{}\!\mathrm{d}}
-\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
-\newcommand\version[2]{{#1}} % The short version of the paper
-%\newcommand\version[2]{{#2}} % The long version of the paper
+Such phase transitions are formally described in the high-dimensional asymptotics regime where both the signal size and its dimension 
+grow to infinity, while the sample size is {\em fixed}.   In such a regime, sparse signals can be detected and their non-zero entries can be 
+recovered
 
-%\startlocaldefs
-\numberwithin{equation}{chapter}
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[chapter]
-% my defs
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{assumption}{Assumption}
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\theoremstyle{remark}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{example}[theorem]{Example}
-%\endlocaldefs
+  with the help of asympt
 
-% Title of the thesis
-\title{Concentration of Maxima and Fundamental Limits in High-Dimensional  Testing and Inference}
-% \title{Phase Transitions in High-dimensional Testing Problems and Concentration of Maxima}
+ a  may be formulated as
+{\em phase transitions} between the on a certain sparsity
 
-% Author name
-\author{Zheng Gao\\Stilian Stoev}
-
-% Email
-\email{gaozheng@umich.edu\\sstoev@umich.edu}
-
-% ORCID
-\ORCID{xxxx-xxxx-xxxx-xxxx}
-
-% Department
-\department{Statistics}
-
-% Year of completion
-\year=2020
-
-% Frontispiece
-\frontispiece{
-\includegraphics[width=5.5in]{./pics/frontispiece.jpg}\\
-\vspace{1in}
-\begin{flushleft}
-{%\fontfamily{pbk}\selectfont 
-For what is a man, what has he got? %\\
-%If not himself, then he has naught.
-}
-\end{flushleft}
-}
-
-% Default style for front pages
-\frontpagestyle{1}
-
-% Dedication
-\dedication{ %
-\centering
-}
-
-% Acknowledgments
-\acknowledgments{ %
-}
-
-% This command sets the width of the acknowledgments area as a fraction
-% of the total width of the text area.
-\acknowledgmentswidth{0.8}
-
-% Preface
-% \preface[2]{ %
-% This is a preface.}
-
-% Commands to hide or show lists of figures, tables, etc.
-\hidelistoftables
-% \showlistofprograms
-% \showlistofappendices
-
-% Definition of any abbreviations used.
-\abbreviations{
- \acro{AGG}{asymptotically generalized Gaussian}
- \acro{BH}{Benjamini-Hochberg}
- \acro{CDF}{cumulative distribution function}
- \acro{FDR}{false discovery rate}
- \acro{FNR}{false non-discovery rate}
- \acro{FWER}{family-wise error rate}
- \acro{FWNR}{family-wise non-discovery rate}
- \acro{GWAS}{genome-wide association studies}
- \acro{HC}{higher-criticism}
- \acro{iid}{independent and identically distributed}
- \acro{LR}{likelihood-ratio}
- \acro{RS}{relatively stable/relative stability}
- \acro{SNP}{single-nucleotide polymorphisms}
- \acro{URS}{uniform relatively stable/uniform relative stability}
-}
-
-% Some abstract text
-\abstract{
-This text presents a collection of new results and recent developments on the phase transition phenomena in sparse signal problems, and makes the connection to the forces behind these statistcal results --- a probablistic phenomena known as concentration of maxima.
+  and makes the connection to the forces behind these statistcal results --- a probablistic phenomena known as concentration of maxima.
 We begin with idealized models where high-dimensional signals are observed with independent additive Gaussian noise.
@@
 As an auxiliary result, we show that, perhaps surprisingly, given total sample sizes, balanced designs in such association studies rarely deliver optimal power.
-% for detecting rare genetic variants with high odds ratios.
-% We provide explicit formulas for power calculations, as well as software tools for finding the optimal study designs.
-% The phase transition phenomena is demonstrated with numerical simulations, and with empirical evidence from GWAS.
-% data from the NHGRI-EBI GWAS catalog.
-}
-%\hideabstractpagenumber
 
-%% DOCUMENT AREA
-\begin{document}
-
-\chapter{Introduction}
-\label{chap:intro}
-\input{./1.intro/introduction.tex}
-
-\chapter{Techincal Preparations and Background}
-\label{chap:background}
-\input{./2.background/background.tex}
-
-\chapter{The Phase Transition Phenomena in Independent Gaussian Error Models} 
-\label{chap:phase-transitions}
-\input{./3.phase_transitions/phase_transitions.tex}
-
-\chapter{Exact Support Recovery and Minimax Optimality} 
-\label{chap:exact-support-recovery}
-\input{./4.exact_support_recovery/exact_support_recovery.tex}
-
-\chapter{Characterization of Uniform Relative Stability for Gaussian Arrays}
-\label{chap:URS}
-\input{./5.URS/URS.tex}
-
-\chapter{The Phase Transition Phenomena in Genome-wide Association Studies} 
-\label{chap:GWAS}
-\input{./6.GWAS/GWAS.tex}
-
-% \appendix
-% \chapter{U-PASS: A Software for Unified Power Analysis and Forensics for Qualitative Traits in Genetic Association Studies} \label{app:UPASS}
-% \addcontentsline{toc}{chapter}{Appendix~\ref{app:UPASS}: U-PASS: A Software for Unified Power Analysis and Forensics for Qualitative Traits in Genetic Association Studies}
-% \input{./appendix/UPASS.tex}
-
-% \chapter{Using Appendices} \label{app:appendix2}
-
-% Give this command the relative path to the .bib file.
-\bibliography{./tex/thesis}
-
-\end{document}
+\vspace{\baselineskip}
+\begin{flushright}\noindent
+Chicago \hfill {\it Zheng Gao }\\
+Ann Arbor, August 2020\hfill {\it Stilian Stoev}\\
+\end{flushright}

### 2020-08-18 acronyms.tex
reformatting
Introduced the sptinger book format
(see folder "svmono")

* Made cosmetic changes to make it compile

* Rewriting the "Preface" by using the original "abstract"

* Note: The preface and the intro need strengtheneing in order to make our "selling points" more clear/compelling.

\extrachap{Acronyms}

 \begin{description}[CABR]
  \item[AGG]{asymptotically generalized Gaussian}
  \item[BH]{Benjamini-Hochberg}
 \item[CDF]{cumulative distribution function}
 \item[FDR]{false discovery rate}
 \item[FNR]{false non-discovery rate}
 \item[FWER]{family-wise error rate}
 \item[FWNR]{family-wise non-discovery rate}
 \item[GWAS]{genome-wide association studies}
 \item[HC]{higher-criticism}
 \item[iid]{independent and identically distributed}
 \item[LR]{likelihood-ratio}
 \item[RS]{relatively stable/relative stability}
 \item[SNP]{single-nucleotide polymorphisms}
 \item[URS]{uniform relatively stable/uniform relative stability}
 \end{description}

### 2020-08-18 abstract.tex
wrote a preface
Replaced the technical abstract with my version of a "Preface".  It needs editing.  Zheng's original Abstract is "commented" in the file "abstract.tex"

@@
 This text presents a collection of new results and recent developments on the phase transition phenomena in sparse signal problems.
-The main theme is the study of the fundamental limits in testing and signal support recovery in high-dimensions.  This subject has 
-received a lot of attention since the seminal works of \cite{ingster1998minimax,donoho2004higher} \fbox{Add references}. These works
-have established the presence of fundamental limits in the so-called {\em needle in haystack} problems, where sparse 
-signal is observed in high-dimensional additive noise.  In this setting, two archetypal problems arise -- the {\em signal detection} and 
-{\em support support recovery}.  Signal detection is a hypothesis testing problem, which aims to determine the presence of non-zero
-signal in some of the dimensions. On the other hand, support recovery is an inference problem, where one aims to estimates the set of
-coordinates with non-trivial signal.
+The main theme is the study of the fundamental limits in high-dimensional testing and inference. Since the seminal works
+of \cite{ingster1998minimax} and \cite{donoho2004higher}, the subject has received a lot of attention in the literature with important contributions
+from \fbox{Add references}.  These works (among others) have discovered the presence of fundamental limits in the so-called 
+{\em needle in haystack} problems, where a sparse signal is observed in high-dimensional additive noise.  In this setting, two archetypal 
+problems arise -- the {\em signal detection} and {\em support support recovery}.  Signal detection is a hypothesis testing problem, which amounts
+to testing for the presence of non-zero signal in some (any) of the dimensions.
+Support recovery, on the other hand, is an inference problem, which aims to estimate the signal support -- the locations of the non-zero signal components.
+The fundamental limits of these problems are studied in the so-called high-dimensional asymptotics regime where the sample size $n$ is fixed and the dimension $p$ of the underlying signal
+grows to infinity.
 
-  to , pamounts to testing for the presence of a signal, while the support recovery is an inference problem
+From a probabilistic perspective, the above phase transition phenomena are asymptotic zero-one type laws, as $p\to\infty$.  
+Namely, consider a sparse signal with  {\em support size} on the order of $p^{1-\beta}$ for some parameter $\beta\in (0,1)$.  
+Parameterize the non-zero {\em signal amplitude} by $\Delta(p^r)$, 
+for some $r>0$ and a suitable monotone non-decreasing function $\Delta(\cdot)$.  Then, for a broad range of error distributions and
+statistical problems, one encounters a sharp transition between the regimes where the problem is solvable and unsolvable depending on 
+the signal magnitude $r$ and signal sparsity $\beta$.  More precisely, there exists a boundary function $f(\beta)$ such that if 
+the signal magnitudes are {\em above} the boundary, $r> f(\beta)$, then the problem can be solved with vanishing loss as $p\to\infty$, with a suitable statistical procedure.
+On the other hand, if the signal is below that same boundary, i.e., $r<f(\beta)$, all statistical procedures fail to  provide a solution with a vanishing loss, as $p\to\infty$.
+Of course, depending on whether one considers the  detection (testing) or support recovery
+(inference) problems, different loss functions quantify success and failure. The choice of the loss functions is often guided by the 
+applications, resulting in a wide variety of phase-transitions (see e.g.\ Figure \ref{FIGURE} \fbox{FIGURE?}).
 
-aims to do inference 
-on the components of the signal  deals with
+{\bf The contributions of this work.} The fundamental limits of the classic detection problem hinge 
+of the analysis of the discrepancy between the {\em null} and {\em alternative} hypotheses e.g., via Hellinger distance.  Thus, perhaps 
+for  technical reasons, much of the analysis was done under the assumption that the additive errors are independent and/or Gaussian.  
+In this work, we demonstrate that the support recovery problems, especially {\em exact support recovery}, are best understood from 
+the novel perspective of the {\em concentration of maxima} phenomenon in extreme value theory.  It turns out that under a very broad 
+range of light-tailed error distributions and under a {\em very} broad range of error dependence structures, the maxima of the errors, 
+when rescaled (but not centered!) converge in probability to a positive constant. This concentration property leads to a complete solution 
+of the exact  support recovery problem for the broad family of thresholding procedures.  Most if not all existing support estimation procedures 
+are types thresholding procedures.   That is, the signal support estimate comprises of all components exceeding a suitable (potentially 
+data-dependent)  threshold.  We show, by exploiting concentration of maxima, that thresholding procedures obey a phase-transition, where if the signal is above a 
+certain boundary, asymptotically exact recovery is possible while below the boundary all thresholding procedures fail, as $p\to\infty$.  
+Remarkably, light-tailed maxima concentrate under very broad and strong dependence.  This is exemplified by our characterization of
+the concentration of maxima phenomenon for Gaussian triangular arrays.  For example, in the special case of stationary Gaussian time
+series, vanishing auto-covariance is necessary and sufficient for the maxima to concentrate in the same way as independent standard 
+normal random variables.   These probabilistic contributions are of independent interest and extend classic work of \cite{berman1964limit}. 
+Concentration of maxima is a type of super-concentration phenomenon studied also in \cite{chatterjee:2014} and \cite{tanguy:2015}.
+The robustness of the concentration of maxima phenomenon to dependence can perhaps explain the universality 
+of phase transitions in support recovery problems.
 
- , where one wants to {\em detect}
-the presence of a sparse signal observed with high-dimensional additive noise.
+The use of concentration of maxima phenomenon highlights one core idea in our work, which allows for a first of its kind comprehensive 
+treatment of thresholding procedures under very broad error-dependence conditions.  The text involves also a full spectrum of related results 
+such as minimax-optimality and finite-sample Bayes-optimality in support estimation.  Using different type of loss functions and typeI error 
+controls, we obtain a rich picture of the exact and approximate support recovery problems in high dimensions.  
+Many of these phase transitions have not appeared in previously published literature.
 
-testing and inference problems, which manifest themselves 
-as sharp phase-transitions between regimes where the statistical problems are possible or impossible to solve.
+High-dimensional support recovery problems arise in many modern applications ranging from cybersecurity to  statistical genetics.  
+Genome-wide association studies (GWAS) in genetics is a particularly natural application, where the theoretical phase-transition results help 
+explain and quantify a previously observed empirical phenomenon of the so-called steep part of the power curve.  
+In the last chapter of this work, we detail this application and highlight future theoretical and practical consequences of our work.
 
-Such phase transitions are formally described in the high-dimensional asymptotics regime where both the signal size and its dimension 
-grow to infinity, while the sample size is {\em fixed}.   In such a regime, sparse signals can be detected and their non-zero entries can be 
-recovered
+{\bf Target audience.} The original research presented in this text originates from the doctoral dissertation of the first author in the 
+Statistics department at the University of Michigan, Ann Arbor.  The main goal of this text is to provide a comprehensive treatment of the
+exact and approximate support recovery problems by utilizing existing and newly developed probabilistic tools on concentration of maxima.
+The text also provides a self-contained introduction to the state-of-the-art in the dynamic area of phase-transitions in high-dimensional 
+testing and inference.  It is accessible to doctoral students in Statistics with background in measure-theoretic probability and  
+statistics as well as to researchers in applied fields working with high-dimensional data sets.  The text can be used as a reference and a
+supplement to a special topics course on high-dimensional inference.
 
-  with the help of asympt
+{\bf Acknowledgements.} The authors gratefully acknowledge the support of all colleagues from the Statistics Department at the 
+University of Michigan, Ann Arbor.   Special thanks (in alphabetical order) go to Xuming He, Tailen Hsing, Michalis Kallitsis, Liza Levina, 
+Rodderick Little, Ya'acov Ritov, Kerby Shedden, Jinqi Shen, Jonathan Terhorst, Gongjun Xu, \fbox{add more}
+The authors were partially supported by the NSF program {\em Algorithms for Threat Detection}.
 
- a  may be formulated as
-{\em phase transitions} between the on a certain sparsity
+\comment{
+
+  \fbox{ ADD ATD}
+
+application of t
+complete pi phase transitions in support estimation under several important loss functions arising
+in applications.  This leads to a rich picture of phase transitions,
+
+ Our contributions involve a The support
+
+  for the support to be recovered (as $p\to\infty$) the
+
+ effectively implies that for the support to be possible to estimate, the set of 
+positive signal entries must separate as $p\to\infty$
+from the rest of the signal, when the signal magnitude is above a certa is  with with
+
+one has that
 
@@
 and explain some long-standing empirical observations on the discoverability of signals in GWAS.
-As an auxiliary result, we show that, perhaps surprisingly, given total sample sizes, balanced designs in such association studies rarely deliver optimal power.
+As an auxiliary result, we show that, perhaps surprisingly, given total sample sizes, balanced designs in such association studies rarely deliver optimal power. }
 

### 2020-08-20 2.background/2.RV_and_RS.tex
addded some exercises
to Chapter 2.

@@
 %For brevity, we focus here on the $\text{AGG}(\nu)$ models.
+
+\section{Exercises}
+
+\fbox{ TO DO: Verify and add}
+
+\begin{enumerate}
+
+ \item (Inspired by \cite{resnick1973almost}) Let $\epsilon(i)\sim F,\ i=1,2,\cdots$ have arbitrary dependence 
+ and $u_p = F^{\leftarrow}(1-1/p)$.
+
+ {\bf (a)}   If for some $\delta_p\to 0$,
+ we have $\sum_{p} \overline{F}((1+\delta_p)u_p) <\infty$, then show that
+ $$
+ \limsup_{p\to\infty} \frac{M_p}{u_p} \le 1,\ \ \mbox{ almost surely,} 
+ $$
+ where $M_p:= \max_{i=1,\cdots,p} \epsilon(i)$.\\
+
+ {\bf (b)} Show that the condition of part {\bf (a)} holds for the Generalized AGG$(\nu),\ \nu>0$ distributions.\\
+
+ {\em Hint:} In part {\bf (a)}, argue that the events $\{ M_p > (1+\delta_p) u_p,\ \mbox{ infinitely often}\}$ and
+  $\{\epsilon(p) > )(1+\delta_p)u_p, \ \mbox{infinitely often}\}$ are equal. Appeal to the Borel Zero-One Law.\\
+
+ \item  Show that independent realizations from a Generalized AGG$(\nu),\ \nu>0$ distribution
+  are {\em almost surely stable}. That is, let $\epsilon(i)$'s be independent with distribution function $F$ as in Example \ref{exmp:AGG}.\\
+
+{\bf (a)} Show that there exists a sequence $\delta_p\to 0$, such that 
+$$
+\sum_p \overline F((1+\delta_p)u_p) <\infty\ \ \mbox{ and }\ \  \sum_p F^p((1-\delta_p)u_p) <\infty.
+$$
+ {\bf (b)} By appealing to the Borel Zero-One law, conclude that in this case
+ $$
+ \frac{1}{u_p} M_p {\longrightarrow} 1,\ \ \mbox{ almost surely}.
+ $$
+
+{\em Comment:} 
+\cite{resnick1973almost} provide a general necessary and sufficient condition for almost sure stability of independent maxima.\\
+
+ \item Prove Gnedenko's result in part (2) of Proposition \ref{prop:rapid-varying-tails}.\\
+
+\item Suppose that $F$ is heavy-tailed, i.e., $\overline F(x) \sim x^{-\alpha} L(x),$ as $x\to\infty$, for some $\alpha>0$ and a
+slowly varying function $L$.  That is, $L(tx)/L(t)\to 1$, as $t\to\infty$, for all $x>0$.\\
+
+{\bf (a)} Show that if $u_p$ is such that $p\overline F(u_p)\to 1$ as $p\to\infty$, then $p \overline F(x u_p)\to x^{-\alpha}$.\\
+
+{\bf (b)} Let $\epsilon(i)$'s be independent realizations from $F$. With $u_n$ as in part {\bf (a)}, show that
+$$ 
+\frac{M_p}{u_p} \stackrel{d}{\longrightarrow} Z,\ \ \mbox{ as }p\to\infty,
+$$ 
+where $M_p = \max_{i=1,\cdots,p} \epsilon(i)$ and $\P(Z\le x) = e^{-1/x^\alpha},\ x>0$.\\
+
+{\em Comment:} In the heavy-tailed case, rather than concentration of maxima (relative stability),
+we encounter {\em dispersion of maxima} where under rescaling $M_p$ converges in distribution to a proper random variable.\\
+
+\item Let  $M_p,\ p=1,2,\cdots$  be an infinite sequence of random variables such that
+$$
+\frac{M_p}{u_p} \stackrel{\P}{\longrightarrow} 1\ \ \mbox{ and }\ \ \frac{M_p}{v_p} \stackrel{d}{\longrightarrow} \xi,
+$$
+for some deterministic positive sequences  $u_p$ and $v_p$ and some non-zero random variable $\xi$.
+
+Show that $\lim_{p\to\infty} u_p/v_p = c$ and $\xi = c$, almost surely.\\
+
+{\em Hint:} Using Skorokhod's theorem there exist $\widetilde M_p$ and $\widetilde \xi$ on another probability space
+such that $M_p/v_p\stackrel{d}{=}\widetilde M_p/v_p \stackrel{a.s.}{\to} \widetilde \xi \stackrel{d}{=}\xi$.
+Then, recall the following criterion.
+
+\begin{lemma} We have $\eta_p\stackrel{\P}{\to} \eta,\ p\to\infty$ if and only if, for every sequence $p_n\to \infty$, there is a further
+subsequence $\{\widetilde p_n\}\subset\{p_n\}$, such that $\eta_{\widetilde p_n} \stackrel{a.s.}{\to} \eta$ almost surely, as $\widetilde p_n\to
+\infty$.
+\end{lemma}
+
+\item Prove that the Benjamini-Hochberg procedure in Definition \ref{def:BH} controls FDR for independent data.\\
+
+{\em Hint:} \fbox{ Give a good hint. }
+
+\item  
+\end{enumerate}

### 2020-08-20 abstract.tex
minor updates
going back to the original title
addded some exercises
to Chapter 2.

@@
 of \cite{ingster1998minimax} and \cite{donoho2004higher}, the subject has received a lot of attention in the literature with important contributions
-from \fbox{Add references}.  These works (among others) have discovered the presence of fundamental limits in the so-called 
-{\em needle in haystack} problems, where a sparse signal is observed in high-dimensional additive noise.  In this setting, two archetypal 
-problems arise -- the {\em signal detection} and {\em support support recovery}.  Signal detection is a hypothesis testing problem, which amounts
+from \cite{ji2012ups,genovese2012comparison,jin2014optimality,arias2017distribution,butucea2018variable}.  These works (among others) 
+ have discovered the presence of fundamental limits in the so-called  {\em needle in haystack} problems, where a sparse signal is observed in 
+ high-dimensional additive noise.  In this setting, two archetypal  problems arise -- the {\em signal detection} and {\em support support recovery}.  
+ Signal detection is a hypothesis testing problem, which amounts
 to testing for the presence of non-zero signal in some (any) of the dimensions.
@@
 On the other hand, if the signal is below that same boundary, i.e., $r<f(\beta)$, all statistical procedures fail to  provide a solution with a vanishing loss, as $p\to\infty$.
-Of course, depending on whether one considers the  detection (testing) or support recovery
-(inference) problems, different loss functions quantify success and failure. The choice of the loss functions is often guided by the 
-applications, resulting in a wide variety of phase-transitions (see e.g.\ Figure \ref{FIGURE} \fbox{FIGURE?}).
+Of course, depending on whether one considers the  detection (testing) or
+support recovery (inference) problems, different loss functions quantify success and failure. The choice of the loss functions is often guided by the 
+applications, resulting in a rich picture of phase-transitions (see e.g.\ Figure \ref{fig:phase-Gaussian-errors}).
 
@@
 of the analysis of the discrepancy between the {\em null} and {\em alternative} hypotheses e.g., via Hellinger distance.  Thus, perhaps 
-for  technical reasons, much of the analysis was done under the assumption that the additive errors are independent and/or Gaussian.  
+for  technical reasons, much of the analysis in the existing literature has been done under the assumption that the additive errors are 
+independent and/or Gaussian, or using loss functions unaffected by the dependence such as the Hamming loss.  
 In this work, we demonstrate that the support recovery problems, especially {\em exact support recovery}, are best understood from 
@@
 when rescaled (but not centered!) converge in probability to a positive constant. This concentration property leads to a complete solution 
-of the exact  support recovery problem for the broad family of thresholding procedures.  Most if not all existing support estimation procedures 
-are types thresholding procedures.   That is, the signal support estimate comprises of all components exceeding a suitable (potentially 
-data-dependent)  threshold.  We show, by exploiting concentration of maxima, that thresholding procedures obey a phase-transition, where if the signal is above a 
+of the exact  support recovery problem for the broad family of thresholding procedures.  Most if not all existing support estimation 
+procedures are types thresholding procedures (see Section \ref{sec:statistical-procedures}).   
+That is, the signal support estimate comprises of all components exceeding a suitable (potentially data-dependent)  threshold.
+We show, by exploiting concentration of maxima, that thresholding procedures obey a phase-transition, where if the signal is above a
 certain boundary, asymptotically exact recovery is possible while below the boundary all thresholding procedures fail, as $p\to\infty$.  
@@
 normal random variables.   These probabilistic contributions are of independent interest and extend classic work of \cite{berman1964limit}. 
-Concentration of maxima is a type of super-concentration phenomenon studied also in \cite{chatterjee:2014} and \cite{tanguy:2015}.
-The robustness of the concentration of maxima phenomenon to dependence can perhaps explain the universality 
+Concentration of maxima is a type of super-concentration phenomenon studied also in \cite{chatterjee2014superconcentration} 
+and \cite{tanguy:2015}. The robustness of the concentration of maxima phenomenon to dependence can perhaps explain the universality 
 of phase transitions in support recovery problems.
@@
 treatment of thresholding procedures under very broad error-dependence conditions.  The text involves also a full spectrum of related results 
-such as minimax-optimality and finite-sample Bayes-optimality in support estimation.  Using different type of loss functions and typeI error 
+such as minimax-optimality and finite-sample Bayes optimality in support estimation.  Using different type of loss functions and type I error 
 controls, we obtain a rich picture of the exact and approximate support recovery problems in high dimensions.  
-Many of these phase transitions have not appeared in previously published literature.
+Many of these phase transition results have not appeared in previously published literature.
 
-High-dimensional support recovery problems arise in many modern applications ranging from cybersecurity to  statistical genetics.  
-Genome-wide association studies (GWAS) in genetics is a particularly natural application, where the theoretical phase-transition results help 
-explain and quantify a previously observed empirical phenomenon of the so-called steep part of the power curve.  
-In the last chapter of this work, we detail this application and highlight future theoretical and practical consequences of our work.
+High-dimensional support recovery problems arise in many modern applications ranging from cybersecurity, theoretical computer science,
+to statistical genetics.  Genome-wide association studies (GWAS) in genetics is a particularly natural application, where the asymptotic 
+phase-transition results help explain and quantify a previously observed empirical phenomenon of the so-called steep part of the power 
+curve.  In the last chapter of this work, we detail this application and highlight future theoretical and practical consequences of our work.
 
@@
 
-{\bf Acknowledgements.} The authors gratefully acknowledge the support of all colleagues from the Statistics Department at the 
-University of Michigan, Ann Arbor.   Special thanks (in alphabetical order) go to Xuming He, Tailen Hsing, Michalis Kallitsis, Liza Levina, 
+{\bf Acknowledgements.} The authors gratefully acknowledge the support of their families and all colleagues from the Statistics Department 
+at the University of Michigan, Ann Arbor.   Special thanks (in alphabetical order) go to Xuming He, Tailen Hsing, Michalis Kallitsis, Liza Levina, 
 Rodderick Little, Ya'acov Ritov, Kerby Shedden, Jinqi Shen, Jonathan Terhorst, Gongjun Xu, \fbox{add more}

### 2020-08-20 2.background/2.Exercises.tex
minor edits
added

1) ?.Example.tex files for each chapter conforming to the current style.

2) Began the "index".  If you want to include a term do \index{term}{term}

3) Fixed the level of the table-of-contents.

--- 2020-08-20 2.background/2.RV_and_RS.tex
@@
-The behavior of the maxima of identically distributed random variables has been studied extensively in the literature (see, e.g., \cite{leadbetter2012extremes,resnick2013extreme,embrechts2013modelling,de2007extreme}
-and the references therein). 
-% We show in this subsection that the maxima of errors with rapidly varying tails can be bounded above using quantiles of their marginal distribution, regardless of their dependence structure; this was a key step in the proof of Theorem \ref{thm:sufficient}.
-The concept of rapid variation plays an important role in the light-tailed case.
-
-\begin{definition}[Rapid variation] \label{def:rapid-variation}
-The survival function of a distribution, $\overline{F}(x) = 1 - F(x)$, is said to be rapidly varying if
-\begin{equation}\label{e:def:rapid-variation}
-\lim_{x\to\infty} \frac{\overline{F}(tx)}{\overline{F}(x)} 
-    = \begin{cases}
-    0, & t > 1\\
-    1, & t = 1\\
-    \infty, & 0 < t < 1
-\end{cases}.
-\end{equation}
-\end{definition}
-
-When $F(x)<1$ for all finite $x$, \citet{gnedenko1943distribution} showed that the distribution $F$ has rapidly varying tails if and only if the maxima of independent observations from $F$ are \emph{relatively stable} in the following sense.
-\begin{definition}[Relative stability] \label{def:RS}
-Let $\epsilon_p = \left(\epsilon_p(i)\right)_{i=1}^p$ be a sequence of random variables with identical marginal distributions $F$. 
-Define the sequence $(u_p)_{p=1}^\infty$ to be the $(1-1/p)$-th generalized quantile of $F$, i.e., 
-\begin{equation} \label{eq:quantiles}
-    u_p = F^\leftarrow(1 - 1/p).
-\end{equation}
-The triangular array ${\cal E} = \{\epsilon_p, p\in\N\}$ is said to have relatively stable (RS) maxima if
-\begin{equation} \label{eq:RS-condition}
-    \frac{1}{u_{p}} M_p := \frac{1}{u_{p}} \max_{i=1,\ldots,p} \epsilon_p(i) \xrightarrow{\P} 1,\quad \text{as }\;p\to\infty.
-\end{equation}
-\end{definition}
-
-In the case of independent and identically distributed $\epsilon_p(i)$'s, \citet{barndorff1963limit} and \citet{resnick1973almost} obtained necessary and sufficient conditions for the \emph{almost sure stability} of maxima, where the convergence in \eqref{eq:RS-condition} holds almost surely.
-
-While relative stability (and almost sure stability) is well-understood in the independent case, the role of dependence has not been fully explored.
-We start this investigation with a small refinement of Theorem 2 in \citet{gnedenko1943distribution} valid under arbitrary dependence.
-
-\begin{proposition}[Rapid variation and relative stability] \label{prop:rapid-varying-tails}
-Assume that the array ${\cal E}$ consists of identically distributed random 
-variables with cumulative distribution function $F$, where $F(x)<1$ for all finite $x>0$. 
-\begin{enumerate}
-    \item If $F$ has rapidly varying right tail, then for all $\delta>0$,
-        \begin{equation} \label{eq:rapid-varying-tails}
-            \P\left[\frac{1}{u_p} M_p\le1+\delta\right] \ge 1 - \frac{\overline F((1+\delta)u_p)}{\overline F(u_p)} \to 1.
-        \end{equation}
-    \item If, in addition, the array ${\cal E}$ has independent entries, then it is relatively stable if and only if $F$ has rapidly varying tail.
-    \label{prop:rapid-varying-tails_part-ii}
-\end{enumerate}
-\end{proposition}
-
-\begin{proof}[Proof of Proposition \ref{prop:rapid-varying-tails}] 
-By the union bound and the fact that 
-$p\overline F(u_p) \le 1$, we have
-\begin{align}\label{e:prop:rapid-varying-tails_part-i-1}
-\P [ M_p > (1+\delta)u_p] \le p \overline F((1+\delta)u_p)
- \le \frac{\overline F((1+\delta)u_p)}{\overline F(u_p)}.
-\end{align}
-In view of \eqref{e:def:rapid-variation} (rapid variation) and the fact that $u_p\to\infty$, as $p\to\infty$, the right-hand side of \eqref{e:prop:rapid-varying-tails_part-i-1} vanishes 
-as $p\to\infty$, for all $\delta>0$.  This completes the proof of \eqref{eq:rapid-varying-tails}. Part 2 is a re-statement of the classic result due to Gnedenko in \cite{gnedenko1943distribution}.
-\end{proof}
-
-We next demonstrate that Gaussian, Exponential, Laplace, and Gamma distributions all have rapidly varying tails.
-
-% \begin{corollary} \label{cor:AGG-is-RS}
-% If $F\in\text{AGG}(\nu)$, $\nu>0$, an independent array ${\cal E}$ is relatively stable. Further, $\text{AGG}(\nu)$ is the only class of model with $u_{p} \sim \left(\nu\log{p}\right)^{1/\nu}$.
-% \end{corollary}
-% 
-% \begin{proof}[Proof of Corollary \ref{cor:AGG-is-URS}]
-% By Proposition \ref{prop:rapid-varying-tails}, it is enough to show that in the AGG model,  $\overline{F}$ has rapidly varying tail. 
-% By definition of the AGG tails \eqref{def:AGG}, we have
-% $$
-% \lim_{t\to\infty} \frac{\log{\left(\overline{F}(tx)\Big/\overline{F}(t)\right)}}{-\frac{1}{\nu}t^\nu(x^\n% u-1)} = 1,
-% $$
-% where the denominator tends to $+\infty$ or $-\infty$ depending on whether $0<x<1$ or $x>1$.
-% Therefore, we must have $\overline{F}(tx) / \overline{F}(t)$ converging to $\infty$ or 0 in the correct range of $x$'s; the case where $x=1$ is trivial.
-% The last claim follows from the expression for AGG quantiles; see Proposition \ref{prop:quantile}.
-% \end{proof}
-
-\begin{example}[Generalized AGG] \label{exmp:AGG}
-A distribution is said to have \emph{Generalized AGG} right tail, if $\log{\overline{F}}$ is regularly varying,
-\begin{equation} \label{eq:GAGG}
-    \log{\overline{F}(x)} = - x^\nu L(x),
-\end{equation}
-where $\nu>0$ and $L: (0,+\infty)\to(0,+\infty)$ is a slowly varying function.
-(A function is said to be slowly varying if $\lim_{x\to\infty}L(tx)/L(x) = 1$ for all $t>0$.) Note that the $\text{AGG}(\nu)$ model corresponds to the special case where $L(x)\to 1/\nu$, as $x\to\infty$.
-
-Relation \eqref{eq:rapid-varying-tails} holds for all arrays $\cal E$ with \emph{generalized} AGG marginals; if the entries are independent, the maxima are relatively stable. 
-This follows directly from Proposition \ref{prop:rapid-varying-tails}, once we show that $F$ has rapidly varying tail. 
-Indeed, by \eqref{eq:GAGG}, we have
-$$
-\log{\left(\overline{F}(tx)\Big/ \overline{F}(x)\right)} = - L(x)x^\nu\left(t^\nu\frac{L(tx)}{L(x)} - 1\right),
-$$
-which converges to $-\infty$, 0, and $+\infty$, as $x\to\infty$, when $t>1$, $t=1$, and $t<1$, respectively, since $x^\nu L(x)\to\infty$ as $x\to\infty$ by definition of $L$.
-\end{example}
-
-The \ac{AGG} class encompasses a wide variety of rapidly varying tail models such as Gaussian and double exponential distributions.
-The larger class \eqref{eq:GAGG} is needed, however, for the Gamma distribution.
-
-More generally, distributions with heavier tails (e.g., log-normal) and lighter tails (e.g., Gompertz) outside the generalized AGG class \eqref{eq:GAGG} may also possess rapidly varying tails;
-heavy-tailed distributions like the Pareto and t-distributions, on the other hand, do not.
-These alternative classes of models are will be introduced when we study the phase transitions in Chapter \ref{chap:exact-support-recovery}. 
-%For brevity, we focus here on the $\text{AGG}(\nu)$ models.
-
-\section{Exercises}
-
 \fbox{ TO DO: Verify and add}

### 2020-08-20 preamble.tex
minor edits
added

1) ?.Example.tex files for each chapter conforming to the current style.

2) Began the "index".  If you want to include a term do \index{term}{term}

3) Fixed the level of the table-of-contents.

--- 2020-08-20 abstract.tex
@@
 exact and approximate support recovery problems by utilizing existing and newly developed probabilistic tools on concentration of maxima.
-The text also provides a self-contained introduction to the state-of-the-art in the dynamic area of phase-transitions in high-dimensional 
+The text also provides a quick introduction to the state-of-the-art in the dynamic area of phase-transitions in high-dimensional 
 testing and inference.  It is accessible to doctoral students in Statistics with background in measure-theoretic probability and  

### 2020-08-21 1.intro/introduction.tex

@@
 % Further, one would like to characterize the statistical procedures that achieve efficient detection and support recovery, whenever such goals become possible to achieve.
-We explore both the \emph{detection} and the \emph{support recovery} problems in this thesis. 
-More precisely, we are interested in the theoretical feasibility of both problems, and seek minimal conditions under which these problems can be consistently solved in large dimensions.
+In this text, we explore both the \emph{detection} and the \emph{support recovery} problems.  More precisely, we are interested in the 
+theoretical feasibility of both problems, and seek minimal conditions under which these problems can be consistently solved in large 
+dimensions.
 
@@
 Established are the necessary and sufficient conditions for exact support recovery in the high-dimensional asymptotic regime.
-This is a major theoretical contribution of the thesis, solving, and expanding on, open problems in the literature (see \cite{butucea2018variable, gao2018fundamental}).
+This is a major theoretical contribution of our approach, which solves and expands on open problems in the recent literature 
+(see \cite{butucea2018variable, gao2018fundamental}).
 The analysis of support recovery problem is intimately related to a \emph{concentration of maxima} phenomena in the analysis of extremes.

### 2020-08-21 2.background/2.AGG.tex

@@
-We introduce a fairly general class of distributions known as \ac{AGG} in this section, and state some properties about the tails of the AGG distributions.
+We introduce a fairly general class of distributions known as \ac{AGG} in this section, and state some properties about the tails of the 
+\index{AGG}{AGG} distributions.
 
 \begin{definition} \label{def:AGG}
-A distribution $F$ is called asymptotic generalized Gaussian with parameter $\nu>0$ (denoted $\text{AGG}(\nu)$) if
+A distribution $F$ is called \index{asymptotic generalized Gaussian}{asymptotic generalized Gaussian} 
+with parameter $\nu>0$ (denoted $\text{AGG}(\nu)$) if
 \begin{enumerate}

### 2020-08-21 2.background/2.Exercises.tex

@@
  {\em Hint:} In part {\bf (a)}, argue that the events $\{ M_p > (1+\delta_p) u_p,\ \mbox{ infinitely often}\}$ and
-  $\{\epsilon(p) > )(1+\delta_p)u_p, \ \mbox{infinitely often}\}$ are equal. Appeal to the Borel Zero-One Law.\\
+  $\{\epsilon(p) > (1+\delta_p)u_p, \ \mbox{infinitely often}\}$ are equal. Appeal to the Borel Zero-One Law.\\
 

### 2020-08-21 6.GWAS/GWAS.tex

We investigate the fundamental limits of multiple testing problems in high-dimensional chi-square models, and in genome-wide association studies as introduced in Section \ref{sec:motivation-chisq}.

In Section \ref{sec:chisq-boundaries}, we shall establish the phase transitions of the sparse chi-square model \eqref{eq:model-chisq}.
Recall that in large-scale screening studies where a large number of association tests are conducted, resulting statistics may be approximated by
\begin{equation} \label{eq:model-chisq-Chapter6}
    %x(i) \distras{\mathrm{ind.}} \chi_\nu^2\left(\lambda(i)\right), \quad i=1,\ldots,p.
    x(i) \sim \chi_\nu^2\left(\lambda(i)\right), \quad i=1,\ldots,p,
\end{equation}
where $\chi_\nu^2\left(\lambda(i)\right)$ is a chi-square distributed random variable with $\nu$ degrees of freedom and non-centrality parameter $\lambda(i)$.
In parallel to results in Chapter \ref{chap:phase-transitions}, we show that several commonly used family-wise error rate-control procedures --- including Bonferroni's procedure --- are asymptotically optimal for the {exact}, and {exact-approximate} support recovery problems (as defined in Definition \ref{def:exact-recovery-success-failure}) in idealized chi-square models \eqref{eq:model-chisq-Chapter6} with independent components.
We further show that the \ac{BH} procedure is asymptotically optimal for the {approximate}, and {approximate-exact} support recovery problems.
% \ref{thm:chi-squared-exact-boundary}, \ref{thm:chi-squared-exact-approx-boundary}, \ref{thm:chi-squared-approx-boundary}, and \ref{thm:chi-squared-approx-exact-boundary}.
Under appropriate parametrizations of the signal sizes and sparsity, they establish the phase transitions of support recovery problems in the chi-square model.
Remarkably, the degree-of-freedom parameter does not affect the asymptotic boundaries in any of the four support recovery problems.

All phase transition boundaries coincide with those in the additive error models obtained in Chapter \ref{chap:phase-transitions} under suitable parametrizations.
% and Figure \ref{fig:phase-chi-squared} continues to apply.
indicating vanishing differences between the difficulties of the one-sided and two-sided alternatives in the Gaussian additive error model \eqref{eq:model-additive}.

\medskip

We then return to association screenings of categorical variables in
Section \ref{sec:odds-and-power}, and present the consequences of the phase transition in the exact-approximate problem in large-scale genetic association studies.
% present empirical evidence for the phase transition in the exact-approximate problem using real data from large-scale association studies on breast cancer obtained from the NHGRI-EBI GWAS Catalog \citep{macarthur2016new}.
% demystify the notion of signal size $\lambda$ in this context.
% which is perhaps less transparent than in additive error models.
We do so by characterizing the relationship between the signal size $\lambda$ and the marginal frequencies, odds ratio, and sample sizes for association tests on 2-by-2 contingency tables.
% Specifically, the amount of signal, when rare variants are present, is weaker compared to the signal when the marginal distributions are balanced.
% In other words, reliable detection of the effects by rare variants would require more samples compared to common variants, even at the same odds ratio.
This result, establishing the relationship between sample sizes and signal sizes, is made precise in Section \ref{sec:odds-and-power}.

We elaborate on the implications of this relationship on optimal study designs for association studies in Section \ref{sec:optimal-design}.
Perhaps surprisingly, our analysis reveals that balanced designs with equal number of cases and controls are often statistically inefficient.
Practical consequences of these results in power analysis will be illustrated with data examples in Section \ref{sec:phase-transitions-in-GWAS}.

The phase transitions in the chi-square models are demonstrated with numerical simulations in Section \ref{sec:numerical}.
Proofs of results in this Chapter are collected in Section \ref{sec:proof-signal-size-odds-ratio}.

% Practical issues are also addressed to make for simple and effective power analysis.

\section{Support recovery problems in chi-squared models}
\label{sec:chisq-boundaries}
\input{6.GWAS/6.chi-square.tex}

\section{Odds ratios and statistical power}
\label{sec:odds-and-power}
\input{6.GWAS/6.odds-and-power.tex}

\section{Optimal study designs and rare variants}
\label{sec:optimal-design} 
\input{6.GWAS/6.optimal-design.tex}

\section{Phase transitions in large-scale association screening studies}
\label{sec:phase-transitions-in-GWAS}
\input{6.GWAS/6.GWAS-phase-transitions.tex}

\section{Numerical illustrations of the phase transitions in chi-square models}
\label{sec:numerical}
\input{6.GWAS/6.numerical.tex}

\section{Proofs}
\label{sec:proof-signal-size-odds-ratio}
\input{6.GWAS/6.proofs-GWAS.tex}

\section{Exercises}
\label{sec:Exercises-GWAS}
\input{6.GWAS/6.Exercises.tex}

### 2020-08-21 acronyms.tex

@@
  \begin{description}[CABR]
-  \item[AGG]{asymptotically generalized Gaussian}
-  \item[BH]{Benjamini-Hochberg}
- \item[CDF]{cumulative distribution function}
- \item[FDR]{false discovery rate}
- \item[FNR]{false non-discovery rate}
- \item[FWER]{family-wise error rate}
- \item[FWNR]{family-wise non-discovery rate}
- \item[GWAS]{genome-wide association studies}
- \item[HC]{higher-criticism}
- \item[iid]{independent and identically distributed}
- \item[LR]{likelihood-ratio}
- \item[RS]{relatively stable/relative stability}
- \item[SNP]{single-nucleotide polymorphisms}
- \item[URS]{uniform relatively stable/uniform relative stability}
+  \item[\index{AGG}{AGG}]{asymptotically generalized Gaussian}
+  \item[\index{BH}{BH}]{Benjamini-Hochberg}
+ \item[\index{CDF}{CDF}]{cumulative distribution function}
+ \item[\index{FDR}{FDR}]{false discovery rate}
+ \item[\index{FNR}{FNR}]{false non-discovery rate}
+ \item[\index{FWER}{FWER}]{family-wise error rate}
+ \item[\index{FWNR}{FWNR}]{family-wise non-discovery rate}
+ \item[\index{GWAS}{GWAS}]{genome-wide association studies}
+ \item[\index{HC}{HC}]{higher-criticism}
+ \item[\index{iid}{iid}]{independent and identically distributed}
+ \item[\index{LR}{LR}]{likelihood-ratio}
+ \item[\index{RS}{RS}]{relatively stable/relative stability}
+ \item[\index{SNP}{SNP}]{single-nucleotide polymorphisms}
+ \item[\index{URS}{URS}]{uniform relatively stable/uniform relative stability}
  \end{description}

### 2020-12-22 1.intro/introduction.tex
Addressed the minor typos of R2
I defined the command "\stilian" in the preamble and used it to make changes in response to the minor typos.

Please see reviews/GS_Annotated.pdf.

@@
 where $\epsilon := (X'X)^{-1}X'\xi$.
+\stilian{R2, Typo 2}{I see no problems here except that we are not in the high-dimensional regime $p\gg n$.
+If we were to address that, we need to expand the discussion.
+1) Talk about sparsity of $\mu$ 2) Introduce the assumption that if ${\rm supp}(\mu) = r <n$, then every $r$ of the $p$ columns of
+$X$ must be linearly independent -- is there a name for such a condition in the literature?
+We know it happens with probability one if $X$ has independent, say Gaussian, entries.
+3) Then, it seems clear that the support of $\mu$ will be identifiable if we replace the inverse with a Moore-Penrose inverse.
+BTW, an intriguing question: Given a design matrix $X$, consider the quantity:
+$$
+c_r(X) :=\min_{w\subset \{1,\cdots,p\},\ |w| = r} {\| (X_w' X_w)^{-1}\| \over \| X_w'X_w\| },
+$$
+where the minimum is taken over all subsets of indices $w$ with cardinality $r<n$ and $X_w:= (x_{i,j})_{j\in w}$ is the sub-matrix of $X$ obtained
+by selecting the columns indexed by the elements in $w\subset\{1,\cdots,p\}$.  Intuitively, $c_r(X)$ gives us the overall difficulty of identifying a 
+sparse signal $\mu$ with support of size $r$. \fbox{Going off on a tangent here...}}
 Hence we recover the generic problem \eqref{eq:model-additive}. 

### 2020-12-22 2.background/2.Exercises.tex
Update 2.Exercises.tex
Addressed the minor typos of R2
I defined the command "\stilian" in the preamble and used it to make changes in response to the minor typos.

Please see reviews/GS_Annotated.pdf.

@@
-\fbox{ TO DO: Verify and add}
+\stilian{R2, Typo 4}{I suggest we move all exercises to the online Supplement.  The supplement can have several chapters, the first of which could be 
+"A crash course on extremes" or ``Selected background from EVT".  It could address some comments on the reviewers that the practitioners could need 
+a lot of ``hand holding".  Similarly, in the Supplement we can put other ``basic" things we would like to have like ``Standard" derivations on the Sidak, BH procedure
+the definition of Tukey's Higher Criticism statistics and the results from Empirical processes that are used to study it...} \fbox{ TO DO: Verify and add}
 
@@
  \item (Inspired by \cite{resnick1973almost}) Let $\epsilon(i)\sim F,\ i=1,2,\cdots$ have arbitrary dependence 
- and $u_p = F^{\leftarrow}(1-1/p)$.
+ and $u_p = F^{\leftarrow}(1-1/p) \to \infty$.
 
@@
 
-{\em Hint:} \fbox{ Give a good hint. }
+\stilian{R2, Typo 5}{ \fbox{TO DO} {\em Hint:} \fbox{ Give a good hint. } }
 
-\item  
 \end{enumerate}

### 2020-12-22 2.background/2.statistical_procedures.tex
Addressed the minor typos of R2
I defined the command "\stilian" in the preamble and used it to make changes in response to the minor typos.

Please see reviews/GS_Annotated.pdf.

@@
 
-Examples of thresholding procedures include ones that aim to control FWER \eqref{eq:FWER-FWNR} --- Bonferroni's \cite{dunn1961multiple}, Sid\'ak's \citep{vsidak1967rectangular}, Holm's \citep{holm1979simple}, and Hochberg's procedure \citep{hochberg1988sharper} --- as well as procedures that target FDR \eqref{eq:FDR-FNR}, such as the Benjamini-Hochberg \cite{benjamini1995controlling} and the Cand\'es-Barber procedure \cite{barber2015controlling}.
+Examples of thresholding procedures include ones that aim to control FWER \eqref{eq:FWER-FWNR} --- Bonferroni's \cite{dunn1961multiple}, Sid\'ak's \citep{vsidak1967rectangular}, Holm's \citep{holm1979simple}, and Hochberg's procedure \citep{hochberg1988sharper} --- as well as procedures that target FDR \eqref{eq:FDR-FNR}, such as the Benjamini-Hochberg \cite{benjamini1995controlling} and the \stilian{R2,Typo 3}{fixed} Cand\`es-Barber procedure \cite{barber2015controlling}.
 Indeed, the class of thresholding procedures \eqref{eq:thresholding-procedure} is so general that it contains most (but not all) of the statistical procedures in the multiple testing literature.
@@
 Recall the order statistics of our observations $x_{[1]} \ge x_{[2]}  \ge \ldots \ge x_{[p]}$.
-\begin{definition}[Benjamini-Hochberg's procedure]
+\begin{definition}[Benjamini-Hochberg's procedure] \label{def:BH}
 Let $i^*$ be the largest index such that

### 2020-12-22 3.phase_transitions/3.global-tests.tex
Addressed the minor typos of R2
I defined the command "\stilian" in the preamble and used it to make changes in response to the minor typos.

Please see reviews/GS_Annotated.pdf.

@@
 
-To the best of our knowledge, performance of simple statistics such as $L_1$, $L_2$ norms, and $S$ in this weak signal setting have not been reported in the literature perhaps due to a perceived lack of novelty.
-Our first Theorem investigates the performance of these routine statistics for detecting sparse signals in high-dimensions, and summarizes the known results.
+To the best of our knowledge, performance of simple statistics such as $L_1$, $L_2$ norms, and \stilian{R2, Typo 7.  I suggest writing the following in red, but note that
+``S" can be confused with the support.  Can we use $\Sigma$ or ${\rm Sum}$? }{the sum statistic $S$ in \eqref{eq:sum-statistic}}
+in this weak signal setting have not been reported in the literature perhaps due to a perceived lack of novelty.
+Our first \stilian{Suggest replacing ``Theorem" with ``theorem" and using a capital letter only when we quote a specific Theorem X.Y.
+-- same for Lemma, Proposition, etc.}{Theorem} investigates the performance of these routine statistics for detecting sparse signals in high-dimensions, and summarizes the known results.
 

### 2020-12-22 4.exact_support_recovery/exact_support_recovery.tex
minor edits
added

1) ?.Example.tex files for each chapter conforming to the current style.

2) Began the "index".  If you want to include a term do \index{term}{term}

3) Fixed the level of the table-of-contents.
Addressed the minor typos of R2
I defined the command "\stilian" in the preamble and used it to make changes in response to the minor typos.

Please see reviews/GS_Annotated.pdf.

@@
 Unfortunately, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and the sharp result does not carry over directly to the study of the probability of support recovery or exact support recovery risk.
-More importantly, despite their elegance, these Hamming loss-minimax studies naturally amounts to the analysis of the elementary case of iid data, and is by design blind to non-trivial error-dependence structures.
+More importantly, despite their elegance, these Hamming loss-minimax studies naturally \stilian{replace ``amounts" by ``reduce"}{amounts} to the analysis of the elementary case of iid data, and is by design blind to non-trivial error-dependence structures.
 This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
@@
 \input{4.exact_support_recovery/4.proofs-convexity.tex}
+
+\input{4.exact_support_recovery/4.Exercises.tex}

### 2020-12-22 5.URS/5.proofs-UDD-URS.tex
Addressed the minor typos of R2
I defined the command "\stilian" in the preamble and used it to make changes in response to the minor typos.

Please see reviews/GS_Annotated.pdf.

@@
 Indeed, $\mathcal{N}$ can be constructed iteratively as follows:
-\begin{itemize}[
-    align=left,
-    leftmargin=4em,
-    itemindent=0pt,
-    labelsep=0pt,
-    labelwidth=4em
-    ]
-    \raggedright
-    \item[{\bf Step 1:}] Set $S_p^{(1)}:=S_p$ and $\mathcal{N}:=\{j_1\}$, where $j_1\in S_p^{(1)}$ is an arbitrary element. Set $k:=1$.\\
-    \item[{\bf Step 2:}] Set $S_p^{(k+1)}:=S_p^{(k)}\setminus B_\gamma(j_k)$, where
+\begin{itemize}    \raggedright
+    \item[{\bf 1:}] Set $S_p^{(1)}:=S_p$ and $\mathcal{N}:=\{j_1\}$, where $j_1\in S_p^{(1)}$ is an arbitrary element. Set $k:=1$.\\
+    \item[{\bf 2:}] Set $S_p^{(k+1)}:=S_p^{(k)}\setminus B_\gamma(j_k)$, where
     $$
@@
     $$
-    \item[{\bf Step 3:}] If $S_p^{(k)} \neq \emptyset$, pick an arbitrary $j_{k+1}\in S_p^{(k)}$, set $\mathcal{N}:=\mathcal{N}\cup\{j_{k+1}\}$, and $k:=k+1$, go to step 2; otherwise, stop.
+    \item[{\bf 3:}] If $S_p^{(k)} \neq \emptyset$, pick an arbitrary $j_{k+1}\in S_p^{(k)}$, set $\mathcal{N}:=\mathcal{N}\cup\{j_{k+1}\}$, and $k:=k+1$, go to step 2; otherwise, stop.
 \end{itemize}

### 2020-12-22 6.GWAS/6.chi-square.tex
Addressed the minor typos of R2
I defined the command "\stilian" in the preamble and used it to make changes in response to the minor typos.

Please see reviews/GS_Annotated.pdf.

@@
 characterizes the phase transition of approximate support recovery problem.
-Specifically, if $\underline{r} > {h}(\beta)$, then the \ac{BH}procedure $\widehat{S}_p$ (defined in Section \ref{sec:statistical-procedures}) with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FDR levels achieves asymptotically approximate support recovery in the sense of \eqref{eq:support-recovery-success}.
+Specifically, if $\underline{r} > {h}(\beta)$, then the \ac{BH} procedure $\widehat{S}_p$ (defined in Section \ref{sec:statistical-procedures}) with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FDR levels achieves asymptotically approximate support recovery in the sense of \eqref{eq:support-recovery-success}.
 
@@
 
-As discussed in Section \ref{sec:motivation-chisq}, support recovery problems in the chi-square model with $\nu=1$, , corresponds to the support recovery problems in the additive model under two-sided alternatives.
-This implies that the asymptotic signal size requirements are identical between the two-sided alternative and its one-sided counterpart, in order to achieve exact support recovery.
-As we shall see in numerical experiments (in Section \ref{sec:numerical} below), the difference is not very pronounced even in moderate dimensions, and vanishes as $p\to\infty$, in accordance with Theorem \ref{thm:chi-squared-exact-boundary}.
+As discussed in Section \ref{sec:motivation-chisq}, support recovery problems in the chi-square model with $\nu=1$ correspond to the support recovery problems in 
+the additive model under two-sided alternatives. This implies that the asymptotic signal size requirements are identical between the two-sided alternative and its 
+one-sided counterpart, in order to achieve exact support recovery. As we shall see in numerical experiments (in Section \ref{sec:numerical} below), the difference 
+is not very pronounced even in moderate dimensions, and vanishes as $p\to\infty$, in accordance with Theorem \ref{thm:chi-squared-exact-boundary}.
 

### 2020-12-22 6.GWAS/6.optimal-design.tex
Addressed the minor typos of R2
I defined the command "\stilian" in the preamble and used it to make changes in response to the minor typos.

Please see reviews/GS_Annotated.pdf.

@@
 
-Fortunately, the conditional distributions of genotypes in the healthy control groups are often estimated by existing studies, and are made available by consortia such as the NHGRI-EBI GWAS catalog \cite{macarthur2016new}.
+Fortunately, the conditional distributions of genotypes in the healthy control groups are often estimated by existing studies, and are made available by consortia such as the NHGRI-EBI GWAS catalog \citep{macarthur2016new}.
 % Assume (after appropriate relabelling, hence without loss of generality) that the first variant is associated with an increased risk of disease, and is henceforth referred to as the risk variant.

### 2020-12-22 preamble.tex
Addressed the minor typos of R2
I defined the command "\stilian" in the preamble and used it to make changes in response to the minor typos.

Please see reviews/GS_Annotated.pdf.

@@
 at the University of Michigan, Ann Arbor.   Special thanks (in alphabetical order) go to Xuming He, Tailen Hsing, Michalis Kallitsis, Liza Levina, 
-Rodderick Little, Ya'acov Ritov, Kerby Shedden, Jinqi Shen, Jonathan Terhorst, Gongjun Xu, \fbox{add more}
+Rodderick Little, Ya'acov Ritov, Kerby Shedden, Jinqi Shen, Jonathan Terhorst, Gongjun Xu, \stilian{R2, Typo 1}{\fbox{add more}}
 The authors were partially supported by the NSF program {\em Algorithms for Threat Detection}.

### 2020-12-31 2.background/2.RV_and_RS.tex
minor edits
added

1) ?.Example.tex files for each chapter conforming to the current style.

2) Began the "index".  If you want to include a term do \index{term}{term}

3) Fixed the level of the table-of-contents.
Added Remark 2.2
This addresses the fact that ependent maxima of rapidly varying variables cannot grow at a fasster rate than maxima of iid such variables.

--- 2020-08-17 2.background/2.RV_and_RS.tex
@@
 
+\stilian{ 
+\begin{remark} \label{rem:iid-max} Part (1) of Proposition \ref{prop:rapid-varying-tails} is equivalent to 
+\begin{equation}\label{e:rem:iid-max}
+  \P\left[\frac{1}{u_p} M_p >  1+\delta_p \right] \longrightarrow 0,\ \ \mbox{ as }p\to\infty,
+\end{equation}
+for some positive sequence $\delta_p\to 0$.  Notice on the other hand that if $M_p^*$ is the maximum of $p$ iid variables with distribution $F$,
+the relative stability property entails $M_p^*/u_p \to 1$, in probability, as $p\to\infty$.  Since the sequence $1+\delta_p\to 1$, 
+Relation \eqref{e:rem:iid-max} means that the rate of growth of the maxima $M_n$ in ${\cal E}$ cannot be faster than that of the independent
+maxima $M_p^*$.  This somewhat surprising fact is true regardless of the dependence structure of ${\cal E}$ and is solely a 
+consequence of the rapid variation of $F$.
+\end{remark}
+}{}
+
 We next demonstrate that Gaussian, Exponential, Laplace, and Gamma distributions all have rapidly varying tails.

### 2021-01-08 1.intro/introduction.tex
shortened version
* Implemented my corrections up to Ch.3.1

* Moved the proofs of Ch 3 and the sections on non-AGG models from Ch 4 to the Appendix -- which will become the online supplement.

* We need to cut just 5 pages now...  This can happen by re-distributing some proofs in the text (instead of having them in separate sections) and moving some more proofs from Ch.6 to the Appendix.

* Overall, I don't like the idea to eliminate the proofs from Ch. 3.   I also like having the non-AGG models in the main text, too.  I will think if we can shorten the manuscript in alternative ways....

  O

@@
 This fast and cheap access to data gave rise to fundamentally new ways of pursuing scientific questions.
-In contrast with the traditional hypothesis--experiment--analysis cycle where data are collected from the experiments, abundant information are often available before specific questions are even formulated.
-Such information can be used for not just evaluating hypotheses, but also for \emph{generating}, and \emph{selecting} the hypotheses to pursue. 
+In contrast with the traditional hypothesis--experiment--analysis cycle where data are collected from the experiments, \stilian{nowadays abundant data}{abundant information} are often available before specific questions are even formulated.
+Such \stilian{data}{information} can be used for not just evaluating hypotheses, but also for \emph{generating}, and \emph{selecting} the hypotheses to pursue. 
 As a result, {multiple testing} --- where a large number of hypotheses are formulated and screened for their plausibility simultaneously --- has become a staple of modern data-driven studies.
@@
 Another example of multiple testing problems arise in cybersecurity, where millions of IP addresses are monitored in real time.
-In this engineering application, statistics are collected and tests are performed for each IP address, in an attempt to locate the IP addresses with anomalous network activities, so that and malicious traffic and volumetric attacks can be filtered to protect end users of network services \citep{kallitsis2016amon}.
+In this engineering application, statistics are collected and tests are performed for each IP address, in an attempt to locate the IP addresses with anomalous network activities.
+Thus, malicious traffic and volumetric attacks can be filtered to protect end users of network services \citep{kallitsis2016amon}.
 
@@
 The signal, $\mu = (\mu(i))_{i=1}^p$, is a vector with $s$ non-zero components supported on the set $S=\{i:\mu(i)\neq 0\}$; the second term $\epsilon$ is a random error vector. 
-The goal of high-dimensional statistics is usually two-fold: 
+The goal of high-dimensional statistics is usually two-fold: \\
+
 \begin{enumerate}
-    \item To detect the presence of non-zero components in $\mu$. That is, to test the global hypothesis $\mu = 0$, which we call the \emph{detection} problem, and
-    \item To estimate the support set $S$, which we call the \emph{support recovery} problem.
+\item [{\rm I.}] (signal detection or {\em testing}) To detect the presence of non-zero components in $\mu$.
+That is, to test the global hypothesis $\mu = 0$, which we call the \emph{detection} problem, and\\
+
+\item[{\rm II.}] (support estimation or {\em inference})
+ To estimate the support set $S$, which we call the \emph{support recovery} problem.
 \end{enumerate}
-To illustrate, in the engineering application of cybersecurity, Internet service providers (ISP) routinely collect statistics of network traffic to determine if there are abnormal surges or blackouts.
-The data vector $x$ could represent, for example, incoming traffic volumes to each server node that the ISP maintains.
-In this case, the vector $\mu$ would be the average traffic volumes when under normal operating conditions, and $\epsilon$'s the fluctuations around these normal levels of traffic.
+\medskip
+To illustrate, in the engineering application of cybersecurity, Internet service providers (ISP) routinely monitor a large number of network traffic streams to determine 
+if there are abnormal surges, blackouts, or other types of anomalies.  The data vector $x$ could represent, for example, incoming traffic volumes to each server 
+node, internet protocol (IP) address, or port that the ISP monitors.  In this case, the vector $\mu$ represents the average traffic volumes in each of the streams 
+under normal operating conditions, and $\epsilon$'s -- the fluctuations around these normal levels of traffic.  
 % The ISPs collect, for example, incoming traffic volumes to each server to determine if there are abnormal surges or blackouts.
-The signal detection problem in this context is then equivalent to determining if there are \emph{any} anomalies among all servers, and the support recovery problem is equivalent to \emph{identifying} the servers with anomalies.
-Similar questions of signal detection and support recovery are pursued in large-scale microarray experiments, %\citep{dudoit2003multiple}, 
-brain imaging and fMRI analysis, %\citep{nichols2003controlling}, 
-and numerous other applications.
+The signal detection problem in this context is then equivalent to determining if there are \emph{any} anomalies among all data streams, and the support recovery problem is equivalent to \emph{identifying} the streams experiencing anomalies.
+%The dimension of $x$ (number of streams) is typically very large, while the non-trivial 
+%signal is sparse (relatively few data streams experience anomalies).
+Similar questions of signal detection and support recovery are pursued in large-scale microarray experiments \citep{dudoit2003multiple},
+brain imaging and fMRI analysis \citep{nichols2003controlling}, and numerous other anomaly detection applications.
 
-A common theme in such applications is that the errors are correlated, and that the signal vectors are believed to be sparse: the number of non-zero components in $\mu$ is small compared to the number of test performed --- in the cybersecurity example, while monitoring is performed over a large number of servers, it is often believed that only very few servers will be experiencing problems at any time.
+A common theme in such applications is that the errors are {\em correlated}, and that the signal vectors are believed to be {\em sparse}: the number of non-zero
+ (or large) components in $\mu$ is small compared to the number of tests performed.  In the cybersecurity context, while a very large number of data streams are 
+ monitored, typically only just a few of them will be experiencing problems at any time, barring large-scale outages or distributed denial of service attacks.
 Under such sparsity assumptions, it is natural to ask if and when one can reliably {(1)} detect the signals, and {(2)} recover the support set $S$.
@@
 where $\epsilon := (X'X)^{-1}X'\xi$.
-\stilian{R2, Typo 2}{I see no problems here except that we are not in the high-dimensional regime $p\gg n$.
+\stilian{R2, Typo 2 -- \fbox{DISCUSS} }{I see no problems here except that we are not in the high-dimensional regime $p\gg n$.
 If we were to address that, we need to expand the discussion.
@@
 
-Note that the components in the observation $x$ (and equivalently, the noise $\epsilon$) in \eqref{eq:model-additive} need not be independent. 
-In the linear regression example, even when the components of the noise term $\xi$ are independent, those of the OLS estimator \eqref{eq:OLS} need not be, unless we have an orthogonal design.
-Indeed, in practice, independence is the exception rather than the rule.
-Therefore a general theory of feasibility must address the role of the error dependence structures in such testing problems, and identify practical procedures that attain the performance limits in independent as well as dependent cases, as soon as the problems become theoretically feasible.
+Note that the components of the observation vector $x$ (and equivalently, the noise $\epsilon$) in \eqref{eq:model-additive} need not be independent. 
+In the linear regression example, even when the components of the noise term $\xi$ are independent, those of the OLS estimator \eqref{eq:OLS} need not be, 
+unless we have an orthogonal design. Indeed, in practice, independence is the exception rather than the rule.
+Therefore, a general theory of feasibility must address the role of the {\em error dependence} structure in such testing and support estimation 
+problems.  It is also important to identify practical and/or optimal procedures that attain the performance limits in independent as well as dependent cases, as soon 
+as the problems become theoretically feasible.  We address both themes in this text.
 

### 2021-01-08 2.background/2.AGG.tex
shortened version
* Implemented my corrections up to Ch.3.1

* Moved the proofs of Ch 3 and the sections on non-AGG models from Ch 4 to the Appendix -- which will become the online supplement.

* We need to cut just 5 pages now...  This can happen by re-distributing some proofs in the text (instead of having them in separate sections) and moving some more proofs from Ch.6 to the Appendix.

* Overall, I don't like the idea to eliminate the proofs from Ch. 3.   I also like having the non-AGG models in the main text, too.  I will think if we can shorten the manuscript in alternative ways....

  O

@@
-We introduce a fairly general class of distributions known as \ac{AGG} in this section, and state some properties about the tails of the 
-\index{AGG}{AGG} distributions.
+We introduce a fairly general class of \ac{AGG} distributions and \stilian{review their tail behavior,
+which will play an important role in the sequel.}{\fbox{check the edit}}
 
@@
 
-The AGG models include, for example, the Gaussian distribution ($\nu = 2$), and the Laplace distribution ($\nu = 1$) as special cases. 
-Since the requirement is only placed on the tail behavior, this class encompasses a large variety of light-tailed models, and is commonly used in the literature on high-dimensional testing \citep{cai2007estimation, arias2017distribution}.
+The AGG models include, for example, the standard Gaussian distribution ($\nu = 2$) and the Laplace distribution ($\nu = 1$) as special cases. 
+Since the requirement is only placed on the tail behavior, this class encompasses a large variety of light-tailed models. 
+This class is commonly used in the literature on high-dimensional testing
+ \citep{cai2007estimation, arias2017distribution}.
 
@@
 $$
-and so $x_l\le u_p \le x_u$, and the expression for the quantiles follow.
+and so $x_l\le u_p \le x_u$, and the expression for the quantiles follows.
 \end{proof}

### 2021-01-08 2.background/2.RV_and_RS.tex
shortened version
* Implemented my corrections up to Ch.3.1

* Moved the proofs of Ch 3 and the sections on non-AGG models from Ch 4 to the Appendix -- which will become the online supplement.

* We need to cut just 5 pages now...  This can happen by re-distributing some proofs in the text (instead of having them in separate sections) and moving some more proofs from Ch.6 to the Appendix.

* Overall, I don't like the idea to eliminate the proofs from Ch. 3.   I also like having the non-AGG models in the main text, too.  I will think if we can shorten the manuscript in alternative ways....

  O

@@
-The behavior of the maxima of identically distributed random variables has been studied extensively in the literature (see, e.g., \cite{leadbetter2012extremes,resnick2013extreme,embrechts2013modelling,de2007extreme}
-and the references therein). 
+The behavior of the maxima of identically distributed random variables has been studied extensively in the extreme 
+value theory literature \citep[see, e.g.,][and the references therein]{leadbetter2012extremes,resnick2013extreme,embrechts2013modelling,de2007extreme}. 
 % We show in this subsection that the maxima of errors with rapidly varying tails can be bounded above using quantiles of their marginal distribution, regardless of their dependence structure; this was a key step in the proof of Theorem \ref{thm:sufficient}.
@@
 \begin{definition}[Relative stability] \label{def:RS}
-Let $\epsilon_p = \left(\epsilon_p(i)\right)_{i=1}^p$ be a sequence of random variables with identical marginal distributions $F$. 
-Define the sequence $(u_p)_{p=1}^\infty$ to be the $(1-1/p)$-th generalized quantile of $F$, i.e., 
+Let $\epsilon_p = \left(\epsilon_p(i)\right)_{i=1}^p$ be a sequence of random variables with common marginal 
+distribution $F$. Define the sequence $(u_p)_{p=1}^\infty$ to be the $(1-1/p)$-th generalized quantile of $F$, i.e., 
 \begin{equation} \label{eq:quantiles}
@@
 In the case of independent and identically distributed $\epsilon_p(i)$'s, \citet{barndorff1963limit} and \citet{resnick1973almost} obtained necessary and sufficient conditions for the \emph{almost sure stability} of maxima, where the convergence in \eqref{eq:RS-condition} holds almost surely.
+\stilian{See also \cite{klass:1984} for further
+sharp results on almost sure stability.  Here, we will only need the weaker notion in \eqref{eq:RS-condition} 
+but extend our inquiry to the case of dependent $\epsilon_p(i)$'s.}{\fbox{The ref suggested by a reviewer -- Resnick?}}
 
 While relative stability (and almost sure stability) is well-understood in the independent case, the role of dependence has not been fully explored.
-We start this investigation with a small refinement of Theorem 2 in \citet{gnedenko1943distribution} valid under arbitrary dependence.
+We start this investigation with a small refinement of Theorem 2 in \citet{gnedenko1943distribution} valid under {\em
+arbitrary dependence.}
 
 \begin{proposition}[Rapid variation and relative stability] \label{prop:rapid-varying-tails}
-Assume that the array ${\cal E}$ consists of identically distributed random 
+Assume that the array ${\cal E}$ consists of identically distributed and possibly dependent random 
 variables with cumulative distribution function $F$, where $F(x)<1$ for all finite $x>0$. 
 \begin{enumerate}
-    \item If $F$ has rapidly varying right tail, then for all $\delta>0$,
+    \item If $F$ has rapidly varying right tail in the sense of \eqref{e:def:rapid-variation}, then for all $\delta>0$,
         \begin{equation} \label{eq:rapid-varying-tails}
@@
         \end{equation}
-    \item If, in addition, the array ${\cal E}$ has independent entries, then it is relatively stable if and only if $F$ has rapidly varying tail.
+    \item If the array ${\cal E}$ has independent entries, then it is relatively stable if and only if $F$ has rapidly varying tail, i.e., \eqref{def:rapid-variation} holds.
     \label{prop:rapid-varying-tails_part-ii}
@@
 In view of \eqref{e:def:rapid-variation} (rapid variation) and the fact that $u_p\to\infty$, as $p\to\infty$, the right-hand side of \eqref{e:prop:rapid-varying-tails_part-i-1} vanishes 
-as $p\to\infty$, for all $\delta>0$.  This completes the proof of \eqref{eq:rapid-varying-tails}. Part 2 is a re-statement of the classic result due to Gnedenko in \cite{gnedenko1943distribution}.
+as $p\to\infty$, for all $\delta>0$.  This completes the proof of \eqref{eq:rapid-varying-tails}. Part 2 is a re-statement of a classic result dating back to \cite{gnedenko1943distribution}.
 \end{proof}
@@
 \end{remark}
-}{}
+}{\fbox{The above remark addresses a question of a reviewer}}
 
-We next demonstrate that Gaussian, Exponential, Laplace, and Gamma distributions all have rapidly varying tails.
+We demonstrate next that the Gaussian, Exponential, Laplace, and Gamma distributions all have rapidly varying tails.
 
@@
 heavy-tailed distributions like the Pareto and t-distributions, on the other hand, do not.
-These alternative classes of models are will be introduced when we study the phase transitions in Chapter \ref{chap:exact-support-recovery}. 
+\stilian{More details on these alternative classes of models can be found in the Supplement.}
+{\fbox{Move these to the online Supplement?} 
+These alternative classes of models will be introduced when we study the phase transitions in 
+Chapter \ref{chap:exact-support-recovery}.}
 %For brevity, we focus here on the $\text{AGG}(\nu)$ models.

### 2021-01-08 2.background/2.asymptotics.tex
shortened version
* Implemented my corrections up to Ch.3.1

* Moved the proofs of Ch 3 and the sections on non-AGG models from Ch 4 to the Appendix -- which will become the online supplement.

* We need to cut just 5 pages now...  This can happen by re-distributing some proofs in the text (instead of having them in separate sections) and moving some more proofs from Ch.6 to the Appendix.

* Overall, I don't like the idea to eliminate the proofs from Ch. 3.   I also like having the non-AGG models in the main text, too.  I will think if we can shorten the manuscript in alternative ways....

  O

@@
-We look to derive useful asymptotic approximations for high dimensional problems, and analyze the afore-mentioned procedures in the regime where the dimensionality of the observations diverge.
-Throughout this text, we consider triangular arrays of observations as described in Models \eqref{eq:model-additive} and \eqref{eq:model-chisq}, and study the performance of procedures in the signal detection and support recovery tasks when
+We look to derive useful asymptotic approximations for high-dimensional problems, and analyze the afore-mentioned procedures in the regime where the dimensionality of the observations diverge.
+Throughout this text, we consider triangular arrays of observations as described in Models \eqref{eq:model-additive} and \eqref{eq:model-chisq}, and study the performance of various procedures in the signal detection and support recovery tasks when
 \begin{equation*}
@@
 
+\medskip
 {\bf Signal detection.}
-The asymptotic behavior of the statistical risk of signal detection problems \eqref{eq:risk-detection} in high dimensions was first studied in \cite{ingster1998minimax}, where a so-called phase transition phenomena was discovered for sparse additive models \eqref{eq:model-additive} with independent and Gaussian components.
-That is, depending on the signal size and sparsity of the signal $\mu$, the detection risk either vanishes, or has a liminf of 1 when we apply the theoretically optimal \ac{LR} test, as dimensionality of the problem diverges.
-The \ac{LR} test, unfortunately, relies on the knowledge of signal sparsity and signal sizes which are often unknown.
-The sparsity-and-signal-size-agnostic statistic \ac{HC} was identified to attain such optimal performance limits in sparse Gaussian models in \cite{donoho2004higher}. 
+\stilian{The asymptotic behavior of the statistical risk in signal detection problems \eqref{eq:risk-detection} in high dimensions was first studied by Yurii Ismailovich Ingster in the context of sparse additive models \eqref{eq:model-additive} with
+independent and Gaussian components. Specifically, \cite{ingster1998minimax} considered the behavior of the 
+theoretically optimal likelihood ratio (\ac{LR}) test in the high-dimensional asymptotic regime, where the dimension $p$ grows to infinity.
+Then, under certain parameterization of the size and sparsity of the signal $\mu$, there are only two possibilities: Either ${\rm risk}^D(LR)$ vanishes, as $p\to\infty$, or $\liminf_{p\to\infty} {\rm risk}^D(LR) =1$.
+The precise signal size and sparsity parameterizations as well as the so-called {\em detection boundary} discovered 
+by Ingster are described in Chapter \ref{chap:phase-transitions}.}{\fbox{replacing?}
+ where a phase transition phenomenon was discovered for 
+That is, as $p\to\infty$, depending on the size and sparsity of the signal $\mu$, the detection risk either vanishes, 
+or has a liminf of 1 when we apply the theoretically optimal likelihood ratio (\ac{LR}) test. }
+
+The \ac{LR} test, unfortunately, depends  relies on the knowledge of the signal sparsity and signal sizes which are 
+not available in practice. The sparsity-and-signal-size-agnostic statistic \ac{HC} in \eqref{eq:HC-statistic} was identified 
+to attain such optimal performance limits in sparse Gaussian models in \cite{donoho2004higher}. 
 A modified goodness-of-fit test statistic in \citet{zhang2002powerful}, and two statistics based on thresholded-$L_1$ and $L_2$ norms in \cite{zhong2013tests} were also shown to be asymptotically optimal in the detection problem.
-Recent studies have also focused on the behavior of detection risk \eqref{eq:risk-detection} in dense and scale mixture models \cite{cai2011optimal}, under general distributional assumptions \citep{cai2014optimal, arias2017distribution1}, as well as when errors are dependent \citep{hall2010innovated}.
+Recent studies have also focused on the behavior of detection risk \eqref{eq:risk-detection} in dense and scale mixture models \cite{cai2011optimal}, under general distributional assumptions \citep{cai2014optimal, arias2017distribution1}, as well as when the errors are dependent \citep{hall2010innovated}.
 A comprehensive review focusing on the role of \ac{HC} in detection problems can be found in \cite{donoho2015special}.
-Notwithstanding the extensive literature on the detection problem, performances of simple statistics such as $L_q$ norms \eqref{eq:Lq-norm} and sums \eqref{eq:sum-statistic}, to the best of our knowledge, have only been sparingly documented.
-We gather relevant results in Chapter \ref{chap:phase-transitions}, and make several new reports on the performance of statistics commonly used in practice.
+Notwithstanding the extensive literature on the detection problem, the performances of simple statistics such as 
+$L_q$ norms \eqref{eq:Lq-norm} and sums \eqref{eq:sum-statistic}, to the best of our knowledge, have only been 
+sparingly documented.  We gather relevant results in Chapter \ref{chap:phase-transitions}, and make several new 
+contributions on the performance of several statistics commonly used in practice.
 
@@
 Notable exceptions include \cite{wainwright2009information, wainwright2009sharp} and \cite{comminges2012tight} in regression problems.
-We refer readers to the recent book by \cite{wainwright2019high} (and in particular, the bibliographical sections of Chapters 7 and 15) for a comprehensive review.
+We refer the reader to the recent book by \cite{wainwright2019high} (and in particular, the bibliographical sections of Chapters 7 and 15, therein) for a comprehensive review.
 
@@
 Nevertheless, two important questions remained unanswered.
-Namely, precise phase-transition-type results for the exact support recovery risk \eqref{eq:risk-exact} and for the support recovery probability \eqref{eq:risk-prob} 
+Namely, precise phase-transition-type results for the exact support recovery risk 
+\eqref{eq:risk-exact} and for the support recovery probability \eqref{eq:risk-prob} 
 % --- akin to that obtained in \cite{arias2017distribution} for the approximate support recovery risk \eqref{eq:risk-approximate} --- 
@@
 in terms of these risk metrics have not been studied.
-Resolving these two issues, we show in this text that several well-known FWER-controlling procedures --- including Bonferroni's procedure --- are optimal in the additive error model under both one-sided and two-sided alternatives.
+\stilian{Some of our main contributions in this text are the solutions to these problems, presented in Chapters \ref{chap:phase-transitions} and \ref{chap:exact-support-recovery}, below.
+Specifically, it turns out that the simple Bonferoni thresholding procedure (among others) is asymptotically optimal for the exact support recovery problem in
+\eqref{eq:model-additive} under broad classes of error distributions. Furthermore, a phase-transition in the exact support recovery 
+problem for thresholding procedures is established under broad dependence conditions on the 
+errors using the concentration of maxima phenomenon (Chapter \ref{chap:exact-support-recovery}). While the 
+optimality of thresholding procedures under dependence remains an open question, in Chapter \ref{sec:optimality}, 
+we establish finite-sample Bayes optimality and sub-optimality results for these procedures under independence.  
+The landscape of the fundamental statistical limits in support estimation is yet to be fully charted. We conjecture, 
+however, that the general concentration of maxima phenomenon will lead to its complete solution under very broad error 
+dependence scenarios.  }{
+Resolving these two issues, we show in this text that several well-known FWER-controlling procedures --- including Bonferroni's procedure --- are optimal in the additive error model under both one-sided and two-sided alternatives.}
 % these results have appeared in \cite{gao2018fundamental} and \cite{gao2019five}
@@
 {\bf Approximate support recovery.}
-Performance limits of FDR-controlling procedures in the support recovery problem have been actively studied in recent years.
+The performance limits of FDR-controlling procedures in the support recovery problem have been actively studied in recent years.
 The asymptotic optimality of the Benjamini-Hochberg procedure
@@
 \cite{arias2017distribution} showed that a phase transition exists for  the approximate support recovery risk \eqref{eq:risk-approximate}.
-The \ac{BH} procedure \cite{benjamini1995controlling}, and the Cand\'es-Barber procedure \cite{barber2015controlling} was identified to be asymptotically optimal.
+The \ac{BH} procedure \cite{benjamini1995controlling}, and the \stilian{DISCUSS}{Is it Candes-Barber or Barber-Candes?}
+Cand\`es-Barber procedure \citep{barber2015controlling} was identified to be asymptotically optimal.
 % \citet{rabinovich2017optimal} further established the rate-optimality of both procedures under the same regime.
 However, \cite{arias2017distribution}, as all related work so far, assumed the non-nulls to follow a common alternative distribution.
-We derive a new phase transitions result that relaxes this assumption on the alternatives in Chapter \ref{chap:phase-transitions}.
+We derive a new phase transition result that relaxes this assumption on the alternatives in Chapter \ref{chap:phase-transitions}.
 
@@
 {\bf Asymmetric statistical risks.}
-Although weighted sums of false discovery and non-discovery have been studied in the literature mentioned above, none has considered simultaneous family-wise error control and marginal, location-wise power requirements.
-As a result, asymmetric statistical risks such as \eqref{eq:risk-exact-approx} and \eqref{eq:risk-approx-exact} have not been investigated.
-As argued in Section \ref{sec:risks}, properties of these asymmetric risks are of important practical concern in applications such as GWAS.
+Although weighted sums of false discovery and non-discovery have been studied in the literature mentioned above, \stilian{the case of simultaneous family-wise error control and marginal, location-wise power requirements, has not been previously considered.
+}{\fbox{Altered, check the wording.}} As a result, asymmetric statistical risks such as \eqref{eq:risk-exact-approx} and \eqref{eq:risk-approx-exact} have not
+been investigated.
+As argued in Section \ref{sec:risks}, the properties of these asymmetric risks are of important practical concern in applications such as GWAS.
 We study the asymptotic behavior of these risks in Chapters \ref{chap:phase-transitions} and \ref{chap:GWAS} of this text.
@@
 The chi-squared model and the motivating GWAS application are analyzed in Chapter \ref{chap:GWAS}.
-The results obtained therein help us understand the sharp power decay in GWAS that have been long observed \citep{bush2012genome} and recently reviewed and visualized \citep{gao2019upass}.
+\stilian{The results obtained therein help us explain the sharp power decay in GWAS known as the 
+{\em steep part of the power curve}.
+This empirical fact has long been observed by statistical geneticists \citep{bush2012genome} but so far it had not been mathematically quantified.
+\cite{gao2019upass} provide
+further details on the power and design in GWAS as well as an accompanying interactive 
+statistical software \citep{gaoUPASS_ShinyApp}.}{\fbox{altered the text, pls check/edit.}}
 

### 2021-01-08 2.background/2.risks_relations.tex
shortened version
* Implemented my corrections up to Ch.3.1

* Moved the proofs of Ch 3 and the sections on non-AGG models from Ch 4 to the Appendix -- which will become the online supplement.

* We need to cut just 5 pages now...  This can happen by re-distributing some proofs in the text (instead of having them in separate sections) and moving some more proofs from Ch.6 to the Appendix.

* Overall, I don't like the idea to eliminate the proofs from Ch. 3.   I also like having the non-AGG models in the main text, too.  I will think if we can shorten the manuscript in alternative ways....

  O

@@
 \begin{lemma} \label{lemma:risk-exact-recovery-probability}
-For any sequence of procedures for support recovery $\mathcal{R} = \mathcal{R}_p$, we have, 
+For any sequence of procedures for support recovery $\mathcal{R} = \mathcal{R}_p$, we have
 %The probability of exact recovery $\P[\widehat{S} = S]$, and risk of exact support recovery $\mathrm{risk}^{\mathrm{E}}$, defined in \eqref{eq:risk-exact}, are related as follows,
@@
 \end{equation}
-as $p\to\infty$. Dependence on $p$ was suppressed for notational convenience.
+as $p\to\infty$. Dependence on $p$ and ${\cal R}$ was suppressed for notational convenience.
 \end{lemma}
@@
 Keen readers must have noticed the asymmetry in Relation \eqref{eq:failure-recovery-implies-risk-1} when we discussed the relationship between the exact support recovery risk \eqref{eq:risk-exact} and the probability of exact support recovery \eqref{eq:risk-prob}.
-
+%
 %The converse of \eqref{eq:failure-recovery-implies-risk-1} is not true.
 While a trivial procedure that never rejects and a procedure that always rejects both have $\mathrm{risk}^{\mathrm{E}}$ equal to 1, the converse is not true.
-For example, it is possible that a procedure selects the true index set $S$ with probability $1/2$, but makes one false inclusion \emph{and} one false omission simultaneously the other half of the time.
+For example, it is possible that a procedure selects the true index set $S$ with probability $1/2$, but otherwise makes one false inclusion \emph{and} one false omission simultaneously.
 In this case the procedure will have 
@@
 The same argument applies to $\mathrm{risk}^{\mathrm{A}}$:
-a procedure may select the true index set $S$ with probability $1/2$, but makes enough false inclusions and omissions other half of the time, so that $\mathrm{risk}^{\mathrm{A}}$ is equal to one.
-Therefore, although the class of methods with risks equal to or exceeding 1 certainly contains the trivial procedures that we mentioned, they are not necessarily ``useless'' as some researchers have claimed (c.f., \citet{arias2017distribution}, Remark 2).
+a procedure may select the true index set $S$ with probability $1/2$, but makes enough false inclusions and omissions 
+the rest of the time, so that $\mathrm{risk}^{\mathrm{A}}$ is equal to one. Therefore, although the class of methods with 
+risks equal to or exceeding 1 certainly contains the trivial procedures that we mentioned, they are not necessarily 
+``useless'' as some researchers have claimed \citep[cf.\ Remark 2 in][]{arias2017distribution}.
 
@@
 \end{equation}
-A key observation in Relation \eqref{eq:Hamming-loss-lower-bound} is that the expected Hamming loss decouples into $p$ terms, and dependence of the estimates $\mathbbm{1}_{\widehat{S}}(i)$ among the $p$ locations no longer plays a role in the sum.
+A key observation in Relation \eqref{eq:Hamming-loss-lower-bound} is that the expected Hamming loss decouples into $p$ terms, and the dependence of the estimates $\mathbbm{1}_{\widehat{S}}(i)$ among the $p$ locations no longer plays any role in the sum.
 Therefore, studying support recovery problems via the expected Hamming loss is not very informative especially under severe dependence, as the bound \eqref{eq:Hamming-loss-lower-bound} may become {very} loose.

### 2021-01-08 2.background/2.statistical_procedures.tex
shortened version
* Implemented my corrections up to Ch.3.1

* Moved the proofs of Ch 3 and the sections on non-AGG models from Ch 4 to the Appendix -- which will become the online supplement.

* We need to cut just 5 pages now...  This can happen by re-distributing some proofs in the text (instead of having them in separate sections) and moving some more proofs from Ch.6 to the Appendix.

* Overall, I don't like the idea to eliminate the proofs from Ch. 3.   I also like having the non-AGG models in the main text, too.  I will think if we can shorten the manuscript in alternative ways....

  O

@@
 Typical choices of $q$ include $q=1, 2$ and $\infty$, where $L_\infty(x)$ is interpreted as the limit of $L_q(x)$ norms as $q\to\infty$, and is equivalent to $\max_{i}|x(i)|$.
-Test procedures based on \eqref{eq:Lq-norm} may then be written as $T(\mathcal{R}(x)) = \mathbbm{1}_{(t,+\infty)}(L_q(x))$, where the cutoff $t$ can be chosen to control the Type I error at desired levels.
+Test procedures based on \eqref{eq:Lq-norm} may then be written as $\mathcal{R}(x) = \mathbbm{1}_{(t,+\infty)}(L_q(x))$, where the cutoff $t$ can be chosen to control the Type I error at desired levels.
 
 While \eqref{eq:Lq-norm} measures the deviation of the data from the origin in an omnidirectional manner, statistics that are tailored to the alternatives can be used in the hopes of power improvement if the directions of the alternatives are known.
-For example, if we were to test positive mean shifts in the additive error model \eqref{eq:model-additive} in the one-sided alternative,
+For example, in the additive error model \eqref{eq:model-additive}, suppose we want to test for positive mean shifts, i.e., 
+we have a one-sided alternative
 \begin{equation} \label{eq:global-test-one-sided}
@@
     %\quad\text{v.s.}\quad 
-    \mathcal{H}_1: \mu(i)> 0, \; \text{for some }i\in\{1,\ldots,p\},
+    \mathcal{H}_1: \mu(i)> 0, \; \text{for some }i\in\{1,\ldots,p\}.
 \end{equation}
-one might consider monitoring the sum (or equivalently, the arithmetic average) of the observations, 
+Then, one might consider monitoring the sum (or equivalently, the arithmetic average) of the observations, 
+\stilian{Replacing $S$ with $T$}{\fbox{Pls check}}
 \begin{equation} \label{eq:sum-statistic}
-    S(x) := \sum_{i=1}^p{x(i)},
+    T(x) := \sum_{i=1}^p{x(i)},
 \end{equation}
@@
 Other tests based on the empirical \ac{CDF} are also available.
-Assuming the same one-sided alternative, let 
+Assuming the same one-sided alternative, let \stilian{Replacing $p(i)$ with $v(i)$ to avoid confusing with $p$}{\fbox{pls check}}
 \begin{equation}
-    p(i) = 1 - \sup\{F_i(y)\,:\,y<x(i)\}, \quad i = 1,\ldots,p,
+    v(i) = 1 - \sup\{F_i(y)\,:\,y<x(i)\}, \quad i = 1,\ldots,p,
 \end{equation}
@@
     \widehat{F}_p(t) = 
-    \frac{1}{p} \sum_{i=1}^p \mathbbm{1}_{(-\infty, t]}(p(i)).
+    \frac{1}{p} \sum_{i=1}^p \mathbbm{1}_{[0, t]}(v(i)).
 \end{equation}
@@
     \implies
-    \left\{\mathbb{B}(t)\right\}_{t\in[0,1]},
+    \left\{\mathbb{B}(t)\right\}_{t\in[0,1]},\ \ \ \mbox{ as } p\to\infty,
 \end{equation*}
@@
 Therefore, goodness-of-fit statistics such as Kolmogorov-Smirnov distance \citep{smirnov1948table}, Cramer-von Mises-type statistics \citep{cramer1928composition, anderson1952asymptotic} that measure the departure from this limiting behavior can be used for testing $\mathcal{H}_0$ against $\mathcal{H}_1$.
-Of particular interest is the \ac{HC} statistic, first proposed by \cite{tukey1976lecture},
-\begin{equation*} %\label{eq:HC-statistic}
+Of particular interest is the higher criticism (\ac{HC}) statistic, first proposed by \cite{tukey1976lecture},
+\begin{equation} \label{eq:HC-statistic}
     HC(x) = 
     \max_{0\le t\le\alpha_0}\frac{\widehat{F}_p(t) - t}{\sqrt{t(1 - t)/p}}.
-\end{equation*}
+\end{equation}
 
-Performance of these statistics in high-dimensional sparse signal detection problems will be reviewed in Section \ref{sec:asymptotics}, and analyzed in Chapter \ref{chap:phase-transitions}.
+\stilian{Each of the above statistics $L_q, T, M,$ or $HC$, gives rise to a decision rule, whereby the null hypothesis is rejected if 
+the statistic exceeds a suitably calibrated threshold. The choice of the threshold is typically determined based on large-sample limit 
+theorems. For example, as shown in Theorem 1.1 of \cite{donoho2004higher}, under the null hypothesis
+$$
+ \frac{HC(x)}{\sqrt{2\log\log(p)}} \longrightarrow  1,\ \ \mbox{ in probability,}
+$$ 
+as $p\to\infty$.  Thus, one decision rule is to reject ${\cal H}_0$, if $HC(x)> t(p,\alpha_p)$, where 
+$t(p,\alpha_p) = \sqrt{2\log\log(p)}(1+o(1))$.  As we will see, this yields an optimal signal detection procedure 
+\citep[see also Theorem 1.2 in ][]{donoho2004higher}.}{\fbox{added} Agree?} The performance of these statistics in high-dimensional 
+sparse signal detection problems will be reviewed in Section \ref{sec:asymptotics}, and analyzed in Chapter \ref{chap:phase-transitions}.
 
@@
 
-Examples of thresholding procedures include ones that aim to control FWER \eqref{eq:FWER-FWNR} --- Bonferroni's \cite{dunn1961multiple}, Sid\'ak's \citep{vsidak1967rectangular}, Holm's \citep{holm1979simple}, and Hochberg's procedure \citep{hochberg1988sharper} --- as well as procedures that target FDR \eqref{eq:FDR-FNR}, such as the Benjamini-Hochberg \cite{benjamini1995controlling} and the \stilian{R2,Typo 3}{fixed} Cand\`es-Barber procedure \cite{barber2015controlling}.
+Examples of thresholding procedures include ones that aim to control FWER \eqref{eq:FWER-FWNR} --- Bonferroni's \citep{dunn1961multiple}, Sid\'ak's \citep{vsidak1967rectangular}, Holm's \citep{holm1979simple}, and Hochberg's procedure \citep{hochberg1988sharper} --- as well as procedures that target FDR \eqref{eq:FDR-FNR}, such as the Benjamini-Hochberg \cite{benjamini1995controlling} and the \stilian{R2,Typo 3}{fixed} Cand\`es-Barber procedure \citep{barber2015controlling}.
 Indeed, the class of thresholding procedures \eqref{eq:thresholding-procedure} is so general that it contains most (but not all) of the statistical procedures in the multiple testing literature.
@@
 % It can be shown that Holm's procedure also controls FWER at $\alpha$ level, regardless of dependence in the data.
-A closely related, more aggressive (data-dependent) thresholding procedure is Hochberg's procedure \citep{hochberg1988sharper}
+A closely related, more aggressive (and also data-dependent) thresholding procedure is Hochberg's procedure \citep{hochberg1988sharper}.
 %\begin{definition}[Hochberg's procedure]
 %Hochberg's procedure 
-which replaces the index $i^*$ in Holm's procedure with the largest index such that
+It replaces the index $i^*$ in Holm's procedure with the largest index such that
 $$
@@
 $$
-Notice that both Holm's procedure and Hochberg's procedure compare p-values to the same thresholds $\alpha / (p-i+1)$.
+Notice that both Holm's and Hochberg's procedures compare p-values to the same thresholds $\alpha / (p-i+1)$.
 However, Holm's procedure only rejects the set of hypotheses whose p-values are all smaller than their respective thresholds.
@@
 
-It can be shown that Bonferroni's procedure and Holm's procedure both control FWER at their nominal levels, regardless of dependence in the data \citep{holm1979simple}.
-In contrast, Sid\'ak's procedure and Hochberg's procedure control FWER at nominal levels when data are independent \citep{vsidak1967rectangular, hochberg1988sharper}.
+It can be shown that Bonferroni's and Holm's procedures both control FWER at their nominal levels, regardless of dependence in the 
+data \citep{holm1979simple}.
+In contrast, Sid\'ak's and Hochberg's procedures control FWER at nominal levels when data are independent \citep{vsidak1967rectangular, hochberg1988sharper}.
+\stilian{DISCUSS}{Explain in the Supplement?}
 
-Last but not least, we review the \ac{BH} procedure, which aims at controlling \ac{FDR} in \eqref{eq:FDR-FNR}, proposed by  \cite{benjamini1995controlling}.
+Last but not least, we review the \ac{BH} procedure, which aims at controlling \ac{FDR} in 
+\eqref{eq:FDR-FNR}, proposed by  \cite{benjamini1995controlling}.
 
@@
 $$
-The Benjamini-Hochberg procedure with level $\alpha$ is the thresholding procedure with threshold
+The Benjamini-Hochberg (BH) procedure with level $\alpha$ is the thresholding procedure with threshold
 \begin{equation} \label{eq:BH-procedure}
@@
 The \ac{BH} procedure is shown to control the FDR at level $\alpha$ when the $x(i)$'s are independent \citep{benjamini1995controlling}. 
-Variations of the \ac{BH} procedure have been proposed to control the \ac{FDR} under dependent observations \citep{benjamini2001control}.
+\stilian{DISCUSS}{Again, explain in the Supplement?} Variations of this procedure have been proposed to control the \ac{FDR} under \stilian{certain models of}{\fbox{added} correct?} dependent observations \citep{benjamini2001control}.
 
@@
 
-Performance of these procedures in high-dimensional sparse signal support recovery problems will be reviewed in Section \ref{sec:asymptotics}, and analyzed in Chapters \ref{chap:phase-transitions}, \ref{chap:exact-support-recovery}, and \ref{chap:GWAS}.
+The performance of these procedures in high-dimensional sparse signal support recovery problems will be reviewed in Section \ref{sec:asymptotics}, and analyzed in Chapters \ref{chap:phase-transitions}, \ref{chap:exact-support-recovery}, and \ref{chap:GWAS}.

### 2021-01-08 2.background/2.statistical_risks.tex
shortened version
* Implemented my corrections up to Ch.3.1

* Moved the proofs of Ch 3 and the sections on non-AGG models from Ch 4 to the Appendix -- which will become the online supplement.

* We need to cut just 5 pages now...  This can happen by re-distributing some proofs in the text (instead of having them in separate sections) and moving some more proofs from Ch.6 to the Appendix.

* Overall, I don't like the idea to eliminate the proofs from Ch. 3.   I also like having the non-AGG models in the main text, too.  I will think if we can shorten the manuscript in alternative ways....

  O

@@
-We define the statistical risk metrics for signal detection and signal support recovery problems in this section.
+  
+\stilian{To understand the fundamental limits of the signal detection and support recovery problems, one needs to first
+define the respective notions of statistical risk.  In this section, we review many existing as well as some new notions 
+of statistical risk, motivated by applications. Formally, in both problems, we have a statistical procedure 
+${\cal R}={\cal R}(x)$, which is a measurable function of the data.
+In the testing context, ${\cal R}$ takes binary values encoding the presence or absence of a signal, while in the support
+recovery problem the values of ${\cal R}$ are sets of indices in $\{1,\cdots,p\}$.  The risk will then be a suitable 
+functional of ${\cal R}$ accounting for the Type I, Type II, and various mis-classification errors.}{We define the statistical risk metrics for signal detection and signal support recovery problems in this section.}
 
@@
 Recall that in sparse signal detection problems, our goal is to come up with a procedure, $\mathcal{R}(x)$, such that the null hypothesis is rejected if the data $x$ is deemed incompatible with the null.
-In the example of additive error models \eqref{eq:model-additive}, we wish to tell apart two hypotheses
+In the additive error models context \eqref{eq:model-additive}, we wish to tell apart two hypotheses
 \begin{equation} \label{eq:global-test-additive}
@@
 \end{equation} 
-Since the decision is binary, we may write the outcome of the procedure in the form of an indicator function, $T(\mathcal{R}(x))\in\{0,1\}$, where the function $T$ takes on value 1 if the null is to be rejected in favor of the alternative, and 0 if we fail to reject the null.
+Since the decision is binary, we may write the outcome of the procedure in the form of an indicator function, 
+$\mathcal{R}(x)\in\{0,1\}$, where ${\cal R}$ takes on value 1 if the null is to be rejected in favor of the alternative, 
+and 0 if we fail to reject the null. 
 The Type I and Type II errors of the procedure, i.e., the probability of wrong decisions under the null hypothesis $\mathcal{H}_0$ and alternative hypothesis $\mathcal{H}_1$, respectively, are defined as
 \begin{equation} \label{eq:type-II-error}
-    \alpha(\mathcal{R}) := \P_{\mathcal{H}_0}\left(T(\mathcal{R}(x))=1\right)
+    \alpha(\mathcal{R}) := \P_{\mathcal{H}_0}\left(\mathcal{R}(x)=1\right)
     \quad \text{and} \quad
-    \beta(\mathcal{R}) := \P_{\mathcal{H}_1}\left(T(\mathcal{R}(x))=0\right).
+    \beta(\mathcal{R}) := \P_{\mathcal{H}_1}\left(\mathcal{R}(x)=0\right).
 \end{equation}
@@
 {\bf Signal support recovery.}
-Turning to support recovery problems, our goal is to design a procedure $\mathcal R$ that produces a set estimate $\widehat{S}$ of the true index set of relevant variables $S$.
+Turning to support recovery problems, our goal is to design a procedure $\mathcal R$ that produces a set estimate $\widehat{S}= {\cal R}(x)$ of the true index set of relevant variables $S$.
 % The true index set, of course, depends on the modeling assumptions. 
 For example, in the sparse additive error model \eqref{eq:model-additive} we aim to estimate $S=\{i:\mu(i)\neq 0\}$, while in the sparse chi-square model \eqref{eq:model-chisq} the goal is to estimate $S=\{i:\lambda(i)\neq 0\}$.
-Formally, one should write $\widehat{S}(\mathcal{R}(x))$ to reflect the dependence of the set estimate on the procedure $\mathcal{R}$ and on the test statistics $x$; 
-for notational convenience, we suppress this dependence and simply write $\widehat{S}$.
-% in place of $\widehat{S}(\mathcal{R}(x))$
+\stilian{For simplicity of notation, we shall write $\widehat{S}$ for the support estimation procedure ${\cal R}(x)$.}{\xout{Formally, one should write $\widehat{S}_{{\cal R}}(x)$ to reflect the dependence of the set estimate on the
+procedure $\mathcal{R}$ and on the test statistics $x$; for notational convenience, we suppress this dependence and simply write $\widehat{S}$.
+}}% in place of $\widehat{S}(\mathcal{R}(x))$
 
-For a given procedure $\mathcal{R}$, the {false discovery rate} (FDR) 
-and the {false non-discovery rate} (FNR) of a procedure are defined as
+For a given procedure $\mathcal{R}$, its {false discovery rate} (FDR) 
+and  {false non-discovery rate} (FNR) are defined, respectively, as
 % of the procedure is defined to be the expected fraction of false findings not in the true index set, among the reported discoveries \cite{benjamini1995controlling}. 
@@
 
-A more stringent criterion for false discovery is the \ac{FWER},
-%family-wise error rate (FWER),
-% defined to be the probability of reporting at least one finding not contained in the true index set.
-and correspondingly, a more stringent criteria for false non-discovery is the \ac{FWNR},
-%family-wise non-discovery rate (FWNR), 
-i.e.,
-% the probability of missing at least one signal in the true index set. That is,
+A more stringent criterion for false discovery is the family-wise error rate (\ac{FWER}), defined to be the probability of 
+reporting at least one finding not contained 
+in the true index set.
+Correspondingly, a more stringent criterion for false non-discovery is the family-wise non-discovery rate (\ac{FWNR}), i.e., the probability of missing at least one signal in the true index set.
+That is,
 \begin{equation} \label{eq:FWER-FWNR}
@@
 We introduce five different statistical risk metrics, 
-each having different asymptotic limits in the support recovery problems as we will see later in this text. 
+each having different asymptotic limits in the support recovery problems as we will see in 
+Chapter \ref{chap:phase-transitions}.
 Following \cite{arias2017distribution}, we define the risk for \emph{approximate} support recovery as
@@
 In applications, however, attitudes towards Type I and Type II errors are often different.
-In the example of GWAS, where the number of candidate locations $p$ could be in the millions, researchers are typically interested in the marginal (location-wise) power of discovery, while exercising stringent (family-wise) false discovery control --- a situation not reflected in the above-mentioned risk metrics.
-This asymmetric consideration, and in particular the GWAS application, prompts us to consider risks that weigh both the family-wise error rate and the marginal power of discovery.
+In the example of GWAS, where the number of candidate locations $p$ could be in the millions, the researchers are typically interested in the marginal (location-wise) power of discovery, while exercising stringent (family-wise) false discovery control.
+ \stilian{Such types of asymmetric risks, while important in applications, have not been studied theoretically.  The}{ 
+ \xout{--- a situation not reflected in the above-mentioned risk metrics.
+This asymmetric consideration, and in particular the}} GWAS application, prompts us to consider risks that weigh both the family-wise error rate and the marginal power of discovery.
 One such risk metric is what shall be referred to as the \emph{exact-approximate} support recovery risk

### 2021-01-08 4.exact_support_recovery/exact_support_recovery.tex
shortened version
* Implemented my corrections up to Ch.3.1

* Moved the proofs of Ch 3 and the sections on non-AGG models from Ch 4 to the Appendix -- which will become the online supplement.

* We need to cut just 5 pages now...  This can happen by re-distributing some proofs in the text (instead of having them in separate sections) and moving some more proofs from Ch.6 to the Appendix.

* Overall, I don't like the idea to eliminate the proofs from Ch. 3.   I also like having the non-AGG models in the main text, too.  I will think if we can shorten the manuscript in alternative ways....

  O

--- 2020-08-17 4.exact_support_recovery/exact_support_recovery.tex
@@
 Unfortunately, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and the sharp result does not carry over directly to the study of the probability of support recovery or exact support recovery risk.
-More importantly, despite their elegance, these Hamming loss-minimax studies naturally amounts to the analysis of the elementary case of iid data, and is by design blind to non-trivial error-dependence structures.
+More importantly, despite their elegance, these Hamming loss-minimax studies naturally \stilian{reduce}{\xout{amounts}} to the analysis of the elementary case of iid data, and is by design blind to non-trivial error-dependence structures.
 This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
@@
 
-\section{Strong classification boundaries in other light-tailed error models}
-\label{suppsec:other-boundaries}
-\input{4.exact_support_recovery/4.other-boundaries.tex}
+%\section{Strong classification boundaries in other light-tailed error models}
+%\label{suppsec:other-boundaries}
+%\input{4.exact_support_recovery/4.other-boundaries.tex}
 
-\section{Thresholding procedures under heavy-tailed errors}
-\label{suppsec:heavy-tailed}
-\input{4.exact_support_recovery/4.heavy-tailed.tex}
+%\section{Thresholding procedures under heavy-tailed errors}
+%\label{suppsec:heavy-tailed}
+%\input{4.exact_support_recovery/4.heavy-tailed.tex}
 

### 2021-01-08 7.Supplement/supplement.tex
shortened version
* Implemented my corrections up to Ch.3.1

* Moved the proofs of Ch 3 and the sections on non-AGG models from Ch 4 to the Appendix -- which will become the online supplement.

* We need to cut just 5 pages now...  This can happen by re-distributing some proofs in the text (instead of having them in separate sections) and moving some more proofs from Ch.6 to the Appendix.

* Overall, I don't like the idea to eliminate the proofs from Ch. 3.   I also like having the non-AGG models in the main text, too.  I will think if we can shorten the manuscript in alternative ways....

  O

\chapter{Proofs for Chapter \ref{chap:phase-transitions}}
\label{sec:supplement:proofs}
\input{3.phase_transitions/3.proofs-phase-transitions.tex}

\chapter{Exact support recovery in non AGG models}

\section{Strong classification boundaries in other light-tailed error models}
\label{suppsec:other-boundaries}
\input{4.exact_support_recovery/4.other-boundaries.tex}

\section{Thresholding procedures under heavy-tailed errors}
\label{suppsec:heavy-tailed}
\input{4.exact_support_recovery/4.heavy-tailed.tex}

### 2021-01-08 preamble.tex
shortened version
* Implemented my corrections up to Ch.3.1

* Moved the proofs of Ch 3 and the sections on non-AGG models from Ch 4 to the Appendix -- which will become the online supplement.

* We need to cut just 5 pages now...  This can happen by re-distributing some proofs in the text (instead of having them in separate sections) and moving some more proofs from Ch.6 to the Appendix.

* Overall, I don't like the idea to eliminate the proofs from Ch. 3.   I also like having the non-AGG models in the main text, too.  I will think if we can shorten the manuscript in alternative ways....

  O

@@
  have discovered the presence of fundamental limits in the so-called  {\em needle in haystack} problems, where a sparse signal is observed in 
- high-dimensional additive noise.  In this setting, two archetypal  problems arise -- the {\em signal detection} and {\em support support recovery}.  
+ high-dimensional additive noise.  In this setting, two archetypal  problems arise -- the {\em signal detection} and {\em signal support recovery}.  
  Signal detection is a hypothesis testing problem, which amounts
@@
 series, vanishing auto-covariance is necessary and sufficient for the maxima to concentrate in the same way as independent standard 
-normal random variables.   These probabilistic contributions are of independent interest and extend classic work of \cite{berman1964limit}. 
+normal random variables.
+\stilian{This is in stark contrast with the behavior of sums, commonly studied under short- and long-range dependence conditions \citep[see e.g.][]{dedecker:doukhan:etal:2007,pipiras:taqqu:2017}.
+Simply put, the notion of weak dependence that entails that the maxima of dependent variables concentrate at the
+same rate as in the case of independence is fundamentally weaker than the conventional mixing conditions widely used in the study of sums.}{\fbox{added}}
+
+\stilian{Our}{\xout{These}} probabilistic contributions may be of independent interest and extend classic work of \cite{berman1964limit}. 
 Concentration of maxima is a type of super-concentration phenomenon studied also in \cite{chatterjee2014superconcentration} 
@@
 High-dimensional support recovery problems arise in many modern applications ranging from cybersecurity, theoretical computer science,
-to statistical genetics.  Genome-wide association studies (GWAS) in genetics is a particularly natural application, where the asymptotic 
-phase-transition results help explain and quantify a previously observed empirical phenomenon of the so-called steep part of the power 
-curve.  In the last chapter of this work, we detail this application and highlight future theoretical and practical consequences of our work.
+to statistical genetics.  Genome-wide association studies (GWAS) in genetics are particularly natural applications, where the asymptotic 
+phase-transition results help explain and quantify a previously observed empirical phenomenon of the so-called {\em steep part of the power 
+curve}  In the last chapter of this work, we detail this application and highlight future theoretical and practical consequences of our work.
 
@@
 
-\comment{
-
-  \fbox{ ADD ATD}
-
-application of t
-complete pi phase transitions in support estimation under several important loss functions arising
-in applications.  This leads to a rich picture of phase transitions,
-
- Our contributions involve a The support
-
-  for the support to be recovered (as $p\to\infty$) the
-
- effectively implies that for the support to be possible to estimate, the set of 
-positive signal entries must separate as $p\to\infty$
-from the rest of the signal, when the signal magnitude is above a certa is  with with
-
-one has that
-
-  and makes the connection to the forces behind these statistcal results --- a probablistic phenomena known as concentration of maxima.
-We begin with idealized models where high-dimensional signals are observed with independent additive Gaussian noise.
-Under suitable parametrization of the signal sparsity and signal sizes, 
-we characterize several new phase transition phenomena in high-dimensional additive error models, and derive the signal sizes necessary and sufficient for statistical procedures to simultaneously control false discovery (in terms of Type I error, {FDR}, or {FWER}) and missed detection (in terms of Type II error, {FNR}, or {FWNR}) in large dimensions.
-% Several new phase transition phenomena are characterized.
-Specifically, we show that, depending on the signal sparsity and signal sizes, the sum of the statistical risks for false discovery  and missed detection either can be controlled at very low levels in high dimensions, or must be at least one in the limit, for all thresholding procedures.
-
-The phase transition in the case of family-wise type I and type II error control is further generalized to cover non-Gaussian and dependent observations.
-We show that the sharp zero-one law continues to hold under a very broad class of error dependence structures, and for a very broad class of error distributions with light, rapidly varying, tails.
-The key to this important generalization is a certain {concentration of maxima} phenomenon known as relative stability. 
-We demystify the dependence conditions of the phase transition by providing a complete characterization of the relative stability concept for Gaussian triangular arrays in terms of their correlation structures.
-% The proof uses classic Sudakov-Fernique and Slepian lemma arguments along with a curious application of Ramsey's coloring theorem.
-
-Finally, motivated by marginal screenings of categorical variables, we study high-dimensional multiple testing problems where test statistics have approximate chi-square distributions.
-Phase transitions are established for support recovery problems in high-dimensional chi-square models.
-Remarkably, the degree-of-freedom parameters in the chi-square distributions do not affect the boundaries in all phase transitions.
-% Several well-known procedures are shown to attain these boundaries.
-We also elucidate on the notion of signal sizes in association tests by characterizing its relationship with marginal frequencies, odds ratio, and sample sizes in $2\times2$ contingency tables. 
-This allows us to illustrate an interesting manifestation of the phase transition phenomena in % \ac{GWAS},
-genome-wide association studies (GWAS), 
-and explain some long-standing empirical observations on the discoverability of signals in GWAS.
-As an auxiliary result, we show that, perhaps surprisingly, given total sample sizes, balanced designs in such association studies rarely deliver optimal power. }
-
 \vspace{\baselineskip}
@@
 Chicago \hfill {\it Zheng Gao }\\
-Ann Arbor, August 2020\hfill {\it Stilian Stoev}\\
+Ann Arbor, \DateEdited \hfill {\it Stilian Stoev}\\
 \end{flushright}

### 2021-01-13 1.intro/introduction.tex
edit up to Chapter 2; leaving some for discussion.

@@
 The proliferation of information technology has enabled us to collect and consume huge volumes of data at unprecedented speeds and at very low costs.
-This fast and cheap access to data gave rise to fundamentally new ways of pursuing scientific questions.
-In contrast with the traditional hypothesis--experiment--analysis cycle where data are collected from the experiments, \stilian{nowadays abundant data}{abundant information} are often available before specific questions are even formulated.
-Such \stilian{data}{information} can be used for not just evaluating hypotheses, but also for \emph{generating}, and \emph{selecting} the hypotheses to pursue. 
+This convenient access to data gave rise to a fundamentally different way of pursuing scientific questions.
+In contrast with the traditional hypothesis--experiment--analysis cycle where data are collected from the experiments, nowadays abundant data are often available before specific questions are even formulated.
+Such data can be used for not just evaluating hypotheses, but also for \emph{generating}, and \emph{selecting} the hypotheses to pursue. 
 As a result, {multiple testing} --- where a large number of hypotheses are formulated and screened for their plausibility simultaneously --- has become a staple of modern data-driven studies.
@@
 An archetypal example of multiple testing problems is genetic association studies \citep{bush2012genome}.
-In genetic association studies, scientists test hypotheses relating each of the hundreds of thousands of genetic marker locations to phenotypic traits of interest;
-the goal here is to select the set of most promising genetic markers for subsequent investigation.
+In these studies, scientists test hypotheses relating each of the hundreds of thousands of genetic marker locations to phenotypic traits of interest.
+For a phenotypic trait on which we have little prior knowledge, we cannot simply test for association on one or a few specific genetic locations, as there are often not enough empirical evidence or biological theory to pin point these genetic locations in the first place.
+Rather, the goal here is to select the set of most promising genetic markers from a large number of candidate locations for subsequent investigation.
+
 Another example of multiple testing problems arise in cybersecurity, where millions of IP addresses are monitored in real time.
-In this engineering application, statistics are collected and tests are performed for each IP address, in an attempt to locate the IP addresses with anomalous network activities.
-Thus, malicious traffic and volumetric attacks can be filtered to protect end users of network services \citep{kallitsis2016amon}.
+In this engineering application, statistics are collected and tests are performed for each IP address, in an attempt to locate the IP addresses with anomalous network activities, so that and malicious traffic and volumetric attacks can be filtered to protect end users of network services \citep{kallitsis2016amon}.
+Similar to the genetic application above, we use data to search over candidate IP addresses and identify locations of interest.
 
-We are motivated by the above examples in particular to study {high-dimensional} multiple testing problems where a large number of hypotheses are tested simultaneously.
-
+We are motivated very much by these examples to study {high-dimensional} multiple testing problems where a large number of hypotheses are tested simultaneously.
 % This high multiplicity of tests brings along a multitude of challenges, and has been a subject of extensive study in recent years.
-
-In the rest of the introduction, we shall review the main objectives of high-dimensional multiple testing, elaborate on these objectives in two classes of data models and in the context of the genetic applications, and briefly summarize the contents of this text.
-
-% While many such multiplicities are explicit, where screenings and selections of hypotheses, models, or variables are performed \emph{and} annouced, they may be completely ``silent'', where such selections are performed but not explicitly reported \citep{berry2012multiplicities}.
-
-% This paper seeks to establish some new asymptotic optimality results for common multiple testing procedures, including the Bonferroni procedure and the Benjamini-Hochberg procedure, in high-dimensional chi-square models.
-
-% This dissertation studies in detail the theoretical limits of multiple problems in high-dimensional sparse models
+In the rest of the introduction, we shall more review the main objectives of high-dimensional multiple testing, and elaborate on these objectives with two classes of data models in the context of various applications.
 
@@
 \begin{enumerate}
-\item [{\rm I.}] (signal detection or {\em testing}) To detect the presence of non-zero components in $\mu$.
-That is, to test the global hypothesis $\mu = 0$, which we call the \emph{detection} problem, and\\
+\item [{\rm I.}] \emph{Signal detection}: to detect the presence of non-zero components in $\mu$. That is, to test the global hypothesis $\mu = 0$. \\
 
-\item[{\rm II.}] (support estimation or {\em inference})
- To estimate the support set $S$, which we call the \emph{support recovery} problem.
+\item[{\rm II.}] \emph{Support recovery}: to estimate the support set $S$. This is also sometimes referred to as the \emph{support estimation} or \emph{signal identification} problem.
 \end{enumerate}
@@
 where $\mu$ is a $p$-dimensional vector of regression coefficients of interest to be inferred from observations of $X$ and $Y$.
-If the design matrix $X$ is of full column rank, then the ordinary least squares (OLS) estimator of $\mu$ can be formed 
+If the design matrix $X$ is of full column rank\footnote{This, of course, requires that we have more samples than dimensions, i.e., $n>p$.
+Nevertheless, multiplicity of tests is still present when $p$ itself is large -- the multiple testing problem is by no means exclusive to situations where $p\gg n$.}, then the ordinary least squares (OLS) estimator of $\mu$ can be formed
 \begin{equation} \label{eq:OLS}
@@
 where $\epsilon := (X'X)^{-1}X'\xi$. 
-\stilian{R2, Typo 2 -- \fbox{DISCUSS} }{I see no problems here except that we are not in the high-dimensional regime $p\gg n$.
+% \stilian{R2, Typo 2 -- \fbox{DISCUSS} }{I see no problems here except that we are not in the high-dimensional regime $p\gg n$.
 If we were to address that, we need to expand the discussion.
-1) Talk about sparsity of $\mu$ 2) Introduce the assumption that if ${\rm supp}(\mu) = r <n$, then every $r$ of the $p$ columns of
-$X$ must be linearly independent -- is there a name for such a condition in the literature?
+1) Talk about sparsity of $\mu$ 2) Introduce the assumption that if ${\rm supp}(\mu) = r <n$, then every $r$ of the $p$ columns of $X$ must be linearly independent -- is there a name for such a condition in the literature?
 We know it happens with probability one if $X$ has independent, say Gaussian, entries.
@@
 BTW, an intriguing question: Given a design matrix $X$, consider the quantity:
-$$
-c_r(X) :=\min_{w\subset \{1,\cdots,p\},\ |w| = r} {\| (X_w' X_w)^{-1}\| \over \| X_w'X_w\| },
-$$
-where the minimum is taken over all subsets of indices $w$ with cardinality $r<n$ and $X_w:= (x_{i,j})_{j\in w}$ is the sub-matrix of $X$ obtained
-by selecting the columns indexed by the elements in $w\subset\{1,\cdots,p\}$.  Intuitively, $c_r(X)$ gives us the overall difficulty of identifying a 
-sparse signal $\mu$ with support of size $r$. \fbox{Going off on a tangent here...}}
+% $$
+% c_r(X) :=\min_{w\subset \{1,\cdots,p\},\ |w| = r} {\| (X_w' X_w)^{-1}\| \over \| X_w'X_w\| },
+% $$
+% where the minimum is taken over all subsets of indices $w$ with cardinality $r<n$ and $X_w:= (x_{i,j})_{j\in w}$ is the sub-matrix of $X$ obtained by selecting the columns indexed by the elements in $w\subset\{1,\cdots,p\}$.
+Intuitively, $c_r(X)$ gives us the overall difficulty of identifying a sparse signal $\mu$ with support of size $r$.
+\fbox{Going off on a tangent here...}}
 Hence we recover the generic problem \eqref{eq:model-additive}. 
@@
 Note that the components of the observation vector $x$ (and equivalently, the noise $\epsilon$) in \eqref{eq:model-additive} need not be independent. 
-In the linear regression example, even when the components of the noise term $\xi$ are independent, those of the OLS estimator \eqref{eq:OLS} need not be, 
-unless we have an orthogonal design. Indeed, in practice, independence is the exception rather than the rule.
+In the linear regression example, even when the components of the noise term $\xi$ are independent, those of the OLS estimator \eqref{eq:OLS} need not be, except in the case of orthogonal designs.
+Indeed, in practice, independence is the exception rather than the rule.
 Therefore, a general theory of feasibility must address the role of the {\em error dependence} structure in such testing and support estimation 
-problems.  It is also important to identify practical and/or optimal procedures that attain the performance limits in independent as well as dependent cases, as soon 
-as the problems become theoretically feasible.  We address both themes in this text.
+problems.
+It is also important to identify practical and/or optimal procedures that attain the performance limits in independent as well as dependent cases, as soon as the problems become theoretically feasible.
+We address both themes in this text.
 

### 2021-01-13 2.background/2.statistical_procedures.tex
edit up to Chapter 2; leaving some for discussion.

@@
 Typical choices of $q$ include $q=1, 2$ and $\infty$, where $L_\infty(x)$ is interpreted as the limit of $L_q(x)$ norms as $q\to\infty$, and is equivalent to $\max_{i}|x(i)|$.
-Test procedures based on \eqref{eq:Lq-norm} may then be written as $\mathcal{R}(x) = \mathbbm{1}_{(t,+\infty)}(L_q(x))$, where the cutoff $t$ can be chosen to control the Type I error at desired levels.
+Test procedures based on \eqref{eq:Lq-norm} may then be written as $T(\mathcal{R}(x)) = \mathbbm{1}_{(t,+\infty)}(L_q(x))$, where the cutoff $t$ can be chosen to control the Type I error at desired levels.
 
 While \eqref{eq:Lq-norm} measures the deviation of the data from the origin in an omnidirectional manner, statistics that are tailored to the alternatives can be used in the hopes of power improvement if the directions of the alternatives are known.
-For example, in the additive error model \eqref{eq:model-additive}, suppose we want to test for positive mean shifts, i.e., 
-we have a one-sided alternative
+For example, in the additive error model \eqref{eq:model-additive}, suppose we want to test for positive mean shifts, i.e., one-sided alternative
 \begin{equation} \label{eq:global-test-one-sided}
@@
 Then, one might consider monitoring the sum (or equivalently, the arithmetic average) of the observations, 
-\stilian{Replacing $S$ with $T$}{\fbox{Pls check}}
 \begin{equation} \label{eq:sum-statistic}
-    T(x) := \sum_{i=1}^p{x(i)},
+    S(x) := \sum_{i=1}^p{x(i)},
 \end{equation}
@@
 Other tests based on the empirical \ac{CDF} are also available.
-Assuming the same one-sided alternative, let \stilian{Replacing $p(i)$ with $v(i)$ to avoid confusing with $p$}{\fbox{pls check}}
+Assuming the same one-sided alternative, let 
 \begin{equation}
-    v(i) = 1 - \sup\{F_i(y)\,:\,y<x(i)\}, \quad i = 1,\ldots,p,
+    q(i) = 1 - \sup\{F_i(y)\,:\,y<x(i)\}, \quad i = 1,\ldots,p,
 \end{equation}
@@
     \widehat{F}_p(t) = 
-    \frac{1}{p} \sum_{i=1}^p \mathbbm{1}_{[0, t]}(v(i)).
+    \frac{1}{p} \sum_{i=1}^p \mathbbm{1}_{[0, t]}(q(i)).
 \end{equation}
@@
 
-\stilian{Each of the above statistics $L_q, T, M,$ or $HC$, gives rise to a decision rule, whereby the null hypothesis is rejected if 
+Each of the above statistics $L_q$, $S$, $M$, or $HC$, gives rise to a decision rule, whereby the null hypothesis is rejected if 
 the statistic exceeds a suitably calibrated threshold. The choice of the threshold is typically determined based on large-sample limit 
@@
 $t(p,\alpha_p) = \sqrt{2\log\log(p)}(1+o(1))$.  As we will see, this yields an optimal signal detection procedure 
-\citep[see also Theorem 1.2 in ][]{donoho2004higher}.}{\fbox{added} Agree?} The performance of these statistics in high-dimensional 
+\citep[see also Theorem 1.2 in ][]{donoho2004higher}. The performance of these statistics in high-dimensional 
 sparse signal detection problems will be reviewed in Section \ref{sec:asymptotics}, and analyzed in Chapter \ref{chap:phase-transitions}.
@@
 
-Examples of thresholding procedures include ones that aim to control FWER \eqref{eq:FWER-FWNR} --- Bonferroni's \citep{dunn1961multiple}, Sid\'ak's \citep{vsidak1967rectangular}, Holm's \citep{holm1979simple}, and Hochberg's procedure \citep{hochberg1988sharper} --- as well as procedures that target FDR \eqref{eq:FDR-FNR}, such as the Benjamini-Hochberg \cite{benjamini1995controlling} and the \stilian{R2,Typo 3}{fixed} Cand\`es-Barber procedure \citep{barber2015controlling}.
+Examples of thresholding procedures include ones that aim to control FWER \eqref{eq:FWER-FWNR} --- Bonferroni's \citep{dunn1961multiple}, Sid\'ak's \citep{vsidak1967rectangular}, Holm's \citep{holm1979simple}, and Hochberg's procedure \citep{hochberg1988sharper} --- as well as procedures that target FDR \eqref{eq:FDR-FNR}, such as the Benjamini-Hochberg \cite{benjamini1995controlling} and the Barber-Cand\`es procedure \citep{barber2015controlling}.
 Indeed, the class of thresholding procedures \eqref{eq:thresholding-procedure} is so general that it contains most (but not all) of the statistical procedures in the multiple testing literature.
@@
 
-We review five thresholding procedures, starting with the well-known Bonferroni's procedure which aims at controlling family-wise error rates.
+Under the assumption that the data $x(i)$'s under the null have a common marginal distribution $F$, we review five thresholding procedures for support recovery, starting with the well-known Bonferroni's procedure which aims at controlling family-wise error rates.
 \begin{definition}[Bonferroni's procedure]
-Suppose the errors $\epsilon(i)$'s have a common marginal distribution $F$, Bonferroni's procedure with level $\alpha$ is the thresholding procedure that uses the threshold
+Bonferroni's procedure with level $\alpha$ is the thresholding procedure that uses the threshold
 \begin{equation} \label{eq:Bonferroni-procedure}
@@
 % It is easy to see that the family-wise error rate (FWER) is controlled at level $\alpha$ by applying the union bound, regardless of the error-dependence structure (see e.g.\ Relation \eqref{eq:Bonferroni-FWER-control}, below).
-The Bonferroni procedure is deterministic (i.e., non data-dependent), and only depends on the dimension of the problem and the null distribution.
+The Bonferroni procedure is deterministic, i.e. non data-dependent, and only depends on the dimension of the problem and the null distribution.
 A closely related procedure is Sid\'ak's procedure \citep{vsidak1967rectangular},
@@
 where $(i_1, \ldots, i_p)$ is a permutation of $\{1, \ldots, p\}$. 
-Denote the order statistics as $x_{[1]}, x_{[2]}, \ldots, x_{[p]}$.
+Denote these order statistics as $x_{[1]}, x_{[2]}, \ldots, x_{[p]}$.
 \begin{definition}[Holm's procedure]
@@
 
-It can be shown that Bonferroni's and Holm's procedures both control FWER at their nominal levels, regardless of dependence in the 
+It can be shown that both Bonferroni's and Holm's procedures control FWER at their nominal levels, regardless of dependence in the 
 data \citep{holm1979simple}.
@@
 The \ac{BH} procedure is shown to control the FDR at level $\alpha$ when the $x(i)$'s are independent \citep{benjamini1995controlling}. 
-\stilian{DISCUSS}{Again, explain in the Supplement?} Variations of this procedure have been proposed to control the \ac{FDR} under \stilian{certain models of}{\fbox{added} correct?} dependent observations \citep{benjamini2001control}.
+\stilian{DISCUSS}{Again, explain in the Supplement?} Variations of this procedure have been proposed to control the \ac{FDR} under certain models of dependent observations \citep{benjamini2001control}.
 

### 2021-01-13 2.background/2.statistical_risks.tex
edit up to Chapter 2; leaving some for discussion.

--- 2020-08-17 2.background/2.statistical_risks.tex
@@
+  
 We define the statistical risk metrics for signal detection and signal support recovery problems in this section.
+Formally, we denote a statistical procedure, i.e., measurable function of the data, as ${\cal R}={\cal R}(x)$.
+In the testing context, a procedure ${\cal R}$ produces a binary decision $T$ that represents our judgment on the presence or absence of a signal. 
+In the support recovery problem, a procedure ${\cal R}$ produces an index set $\widehat{S}$ that represents our estimate of the signal support.  
+The statistical risks are then suitable functionals of ${T}$ and $\widehat{S}$ in respective contexts. 
+%As we will see, these risk metrics will range from the familiar Type I, Type II errors in detection problems, to various mis-classification errors.
 
@@
 based on the $p$-dimensional observation $x$.
-Similarly in the chi-square model \eqref{eq:model-chisq}, we look to test
+Similarly, in the chi-square model \eqref{eq:model-chisq}, we look to test
 \begin{equation} \label{eq:global-test-chisq}
@@
 \end{equation} 
-Since the decision is binary, we may write the outcome of the procedure in the form of an indicator function, $T(\mathcal{R}(x))\in\{0,1\}$, where the function $T$ takes on value 1 if the null is to be rejected in favor of the alternative, and 0 if we fail to reject the null.
+Since the decision is binary, we may write the outcome of the procedure in the form of an indicator function, 
+$T(\mathcal{R}(x))\in\{0,1\}$, where $T=1$ if the null is to be rejected in favor of the alternative, and 0 if we fail to reject the null. 
 The Type I and Type II errors of the procedure, i.e., the probability of wrong decisions under the null hypothesis $\mathcal{H}_0$ and alternative hypothesis $\mathcal{H}_1$, respectively, are defined as
 \begin{equation} \label{eq:type-II-error}
-    \alpha(\mathcal{R}) := \P_{\mathcal{H}_0}\left(T(\mathcal{R}(x))=1\right)
+    \alpha(\mathcal{R}) := \P_{\mathcal{H}_0}\left(T()\mathcal{R}(x))=1\right)
     \quad \text{and} \quad
@@
 {\bf Signal support recovery.}
-Turning to support recovery problems, our goal is to design a procedure $\mathcal R$ that produces a set estimate $\widehat{S}$ of the true index set of relevant variables $S$.
+Turning to support recovery problems, our goal is to design a procedure that produces a set estimate $\widehat{S}({\cal R}(x))$ of the true index set of relevant variables $S$.
 % The true index set, of course, depends on the modeling assumptions. 
 For example, in the sparse additive error model \eqref{eq:model-additive} we aim to estimate $S=\{i:\mu(i)\neq 0\}$, while in the sparse chi-square model \eqref{eq:model-chisq} the goal is to estimate $S=\{i:\lambda(i)\neq 0\}$.
-Formally, one should write $\widehat{S}(\mathcal{R}(x))$ to reflect the dependence of the set estimate on the procedure $\mathcal{R}$ and on the test statistics $x$; 
-for notational convenience, we suppress this dependence and simply write $\widehat{S}$.
-% in place of $\widehat{S}(\mathcal{R}(x))$
+For simplicity of notation, we shall write $\widehat{S}$ for the support estimator $\widehat{S}({\cal R}(x))$.
 
-For a given procedure $\mathcal{R}$, the {false discovery rate} (FDR) 
-and the {false non-discovery rate} (FNR) of a procedure are defined as
+For a given procedure $\mathcal{R}$, its {false discovery rate} (FDR) 
+and  {false non-discovery rate} (FNR) are defined, respectively, as
 % of the procedure is defined to be the expected fraction of false findings not in the true index set, among the reported discoveries \cite{benjamini1995controlling}. 
@@
 In applications, however, attitudes towards Type I and Type II errors are often different.
-In the example of GWAS, where the number of candidate locations $p$ could be in the millions, researchers are typically interested in the marginal (location-wise) power of discovery, while exercising stringent (family-wise) false discovery control --- a situation not reflected in the above-mentioned risk metrics.
+In the example of GWAS, where the number of candidate locations $p$ could be in the millions, researchers are typically interested in the marginal (location-wise) power of discovery, while exercising stringent (family-wise) false discovery control.
+Such types of asymmetric risks, while important in applications, have not been studied theoretically.  
 This asymmetric consideration, and in particular the GWAS application, prompts us to consider risks that weigh both the family-wise error rate and the marginal power of discovery.

### 2021-01-13 6.GWAS/6.proofs-GWAS.tex
edit up to Chapter 2; leaving some for discussion.

@@
 One could in principle obtain the proofs in this section by referencing arguments that have appeared in Section \ref{sec:proofs}.
-We choose to present the the proof here in full to make this section self-contained.
+We choose to present the proof here in full to make this section self-contained.
 
@@
 As with the proof of Theorem \ref{thm:chi-squared-approx-boundary}, one could shorten the presentations in this section by referencing arguments Section \ref{sec:proofs}.
-Again, we choose to present the the proof in full to make this section self-contained.
+Again, we choose to present the proof in full to make this section self-contained.
 

### 2021-01-13 2.background/2.RV_and_RS.tex

@@
 In the case of independent and identically distributed $\epsilon_p(i)$'s, \citet{barndorff1963limit} and \citet{resnick1973almost} obtained necessary and sufficient conditions for the \emph{almost sure stability} of maxima, where the convergence in \eqref{eq:RS-condition} holds almost surely.
-\stilian{See also \cite{klass:1984} for further
-sharp results on almost sure stability.  Here, we will only need the weaker notion in \eqref{eq:RS-condition} 
-but extend our inquiry to the case of dependent $\epsilon_p(i)$'s.}{\fbox{The ref suggested by a reviewer -- Resnick?}}
+See also \cite{klass:1984} for further sharp results on almost sure stability, and \cite{naveau2003almost} for almost sure stability in stationary sequences.
+Here, we will only need the weaker notion in \eqref{eq:RS-condition} but extend our inquiry to the case of dependent $\epsilon_p(i)$'s.
 
@@
         \end{equation}
-    \item If the array ${\cal E}$ has independent entries, then it is relatively stable if and only if $F$ has rapidly varying tail, i.e., \eqref{def:rapid-variation} holds.
+    \item If the array ${\cal E}$ has independent entries, then it is relatively stable if and only if $F$ has rapidly varying tail, i.e., \eqref{e:def:rapid-variation} holds.
     \label{prop:rapid-varying-tails_part-ii}
@@
 
-\stilian{ 
 \begin{remark} \label{rem:iid-max} Part (1) of Proposition \ref{prop:rapid-varying-tails} is equivalent to 
@@
 \end{equation}
-for some positive sequence $\delta_p\to 0$.  Notice on the other hand that if $M_p^*$ is the maximum of $p$ iid variables with distribution $F$,
+for some positive sequence $\delta_p\to 0$.  
+Notice on the other hand that, if $M_p^*$ is the maximum of $p$ iid variables with distribution $F$,
 the relative stability property entails $M_p^*/u_p \to 1$, in probability, as $p\to\infty$.  Since the sequence $1+\delta_p\to 1$, 
 Relation \eqref{e:rem:iid-max} means that the rate of growth of the maxima $M_n$ in ${\cal E}$ cannot be faster than that of the independent
-maxima $M_p^*$.  This somewhat surprising fact is true regardless of the dependence structure of ${\cal E}$ and is solely a 
-consequence of the rapid variation of $F$.
+maxima $M_p^*$. 
+This somewhat surprising fact holds regardless of the dependence structure of ${\cal E}$ and is solely a consequence of the rapid variation of $F$.
 \end{remark}
-}{\fbox{The above remark addresses a question of a reviewer}}
 

### 2021-01-13 2.background/2.asymptotics.tex

@@
 {\bf Signal detection.}
-\stilian{The asymptotic behavior of the statistical risk in signal detection problems \eqref{eq:risk-detection} in high dimensions was first studied by Yurii Ismailovich Ingster in the context of sparse additive models \eqref{eq:model-additive} with
+The asymptotic behavior of the statistical risk in signal detection problems \eqref{eq:risk-detection} in high dimensions was first studied by \stilian{Yurii Ismailovich Ingster}{where did you find the full name?} in the context of sparse additive models \eqref{eq:model-additive} with
 independent and Gaussian components. Specifically, \cite{ingster1998minimax} considered the behavior of the 
 theoretically optimal likelihood ratio (\ac{LR}) test in the high-dimensional asymptotic regime, where the dimension $p$ grows to infinity.
-Then, under certain parameterization of the size and sparsity of the signal $\mu$, there are only two possibilities: Either ${\rm risk}^D(LR)$ vanishes, as $p\to\infty$, or $\liminf_{p\to\infty} {\rm risk}^D(LR) =1$.
-The precise signal size and sparsity parameterizations as well as the so-called {\em detection boundary} discovered 
-by Ingster are described in Chapter \ref{chap:phase-transitions}.}{\fbox{replacing?}
- where a phase transition phenomenon was discovered for 
-That is, as $p\to\infty$, depending on the size and sparsity of the signal $\mu$, the detection risk either vanishes, 
-or has a liminf of 1 when we apply the theoretically optimal likelihood ratio (\ac{LR}) test. }
+Then, under certain parameterization of the size and sparsity of the signal $\mu$, a dichotomy exists:
+either ${\rm risk}^D(\mathcal{R})$ vanishes as $p\to\infty$ where $\mathcal{R}$ is the \ac{LR} test, or $\liminf_{p\to\infty} {\rm risk}^D(\mathcal{R}) = 1$ for any procedure.
+The precise signal size and sparsity parameterizations as well as the so-called {\em detection boundary} discovered by Ingster are described in Chapter \ref{chap:phase-transitions}.
 
-The \ac{LR} test, unfortunately, depends  relies on the knowledge of the signal sparsity and signal sizes which are 
+The \ac{LR} test, unfortunately, relies on the knowledge of the signal sparsity and signal sizes which are 
 not available in practice. The sparsity-and-signal-size-agnostic statistic \ac{HC} in \eqref{eq:HC-statistic} was identified 
@@
 Notable exceptions include \cite{wainwright2009information, wainwright2009sharp} and \cite{comminges2012tight} in regression problems.
-We refer the reader to the recent book by \cite{wainwright2019high} (and in particular, the bibliographical sections of Chapters 7 and 15, therein) for a comprehensive review.
+We refer the reader to the recent book by \cite{wainwright2019high} (and in particular, the bibliographical sections of Chapters 7 and 15 therein) for a comprehensive review.
 
@@
 in terms of these risk metrics have not been studied.
-\stilian{Some of our main contributions in this text are the solutions to these problems, presented in Chapters \ref{chap:phase-transitions} and \ref{chap:exact-support-recovery}, below.
-Specifically, it turns out that the simple Bonferoni thresholding procedure (among others) is asymptotically optimal for the exact support recovery problem in
-\eqref{eq:model-additive} under broad classes of error distributions. Furthermore, a phase-transition in the exact support recovery 
-problem for thresholding procedures is established under broad dependence conditions on the 
-errors using the concentration of maxima phenomenon (Chapter \ref{chap:exact-support-recovery}). While the 
-optimality of thresholding procedures under dependence remains an open question, in Chapter \ref{sec:optimality}, 
-we establish finite-sample Bayes optimality and sub-optimality results for these procedures under independence.  
-The landscape of the fundamental statistical limits in support estimation is yet to be fully charted. We conjecture, 
-however, that the general concentration of maxima phenomenon will lead to its complete solution under very broad error 
-dependence scenarios.  }{
-Resolving these two issues, we show in this text that several well-known FWER-controlling procedures --- including Bonferroni's procedure --- are optimal in the additive error model under both one-sided and two-sided alternatives.}
-% these results have appeared in \cite{gao2018fundamental} and \cite{gao2019five}
+Some of our main contributions in this text are the solutions to these problems, presented in Chapters \ref{chap:phase-transitions} and \ref{chap:exact-support-recovery} below. 
+Specifically, we show that the Bonferroni thresholding procedure (among others) is asymptotically optimal for the exact support recovery problem in \eqref{eq:model-additive} under broad classes of error distributions.
+Furthermore, a phase-transition in the exact support recovery problem for thresholding procedures is established under broad dependence conditions on the errors using the concentration of maxima phenomenon (Chapter \ref{chap:exact-support-recovery}).
+We also establish finite-sample Bayes optimality and sub-optimality results for these procedures under independence, and by extension, arrive at minimax optimality results for the exact support recovery problem.
 
+The landscape of the fundamental statistical limits in support estimation is yet to be fully charted. 
+We conjecture, however, that the general concentration of maxima phenomenon will lead to its complete solution under very broad error 
+dependence scenarios.
 \medskip
@@
 \cite{arias2017distribution} showed that a phase transition exists for  the approximate support recovery risk \eqref{eq:risk-approximate}.
-The \ac{BH} procedure \cite{benjamini1995controlling}, and the \stilian{DISCUSS}{Is it Candes-Barber or Barber-Candes?}
-Cand\`es-Barber procedure \citep{barber2015controlling} was identified to be asymptotically optimal.
+The \ac{BH} procedure \cite{benjamini1995controlling}, and the Barber-Cand\`es procedure \citep{barber2015controlling} was identified to be asymptotically optimal.
 % \citet{rabinovich2017optimal} further established the rate-optimality of both procedures under the same regime.
@@
 {\bf Asymmetric statistical risks.}
-Although weighted sums of false discovery and non-discovery have been studied in the literature mentioned above, \stilian{the case of simultaneous family-wise error control and marginal, location-wise power requirements, has not been previously considered.
-}{\fbox{Altered, check the wording.}} As a result, asymmetric statistical risks such as \eqref{eq:risk-exact-approx} and \eqref{eq:risk-approx-exact} have not
+Although weighted sums of false discovery and non-discovery have been studied in the literature mentioned above, the case of simultaneous family-wise error control and marginal, location-wise power requirements, has not been previously considered.
+As a result, asymmetric statistical risks such as \eqref{eq:risk-exact-approx} and \eqref{eq:risk-approx-exact} have not 
 been investigated.
@@
 The chi-squared model and the motivating GWAS application are analyzed in Chapter \ref{chap:GWAS}.
-\stilian{The results obtained therein help us explain the sharp power decay in GWAS known as the 
-{\em steep part of the power curve}.
-This empirical fact has long been observed by statistical geneticists \citep{bush2012genome} but so far it had not been mathematically quantified.
-\cite{gao2019upass} provide
-further details on the power and design in GWAS as well as an accompanying interactive 
-statistical software \citep{gaoUPASS_ShinyApp}.}{\fbox{altered the text, pls check/edit.}}
+The results obtained therein help us explain a phenomenon in GWAS where statistical power decays sharply as function of sample size when the latter is in a small region known as the {\em steep part of the power curve}.
+This empirical fact has long been observed by statistical geneticists but has not been mathematically quantified.
+\cite{gao2019upass} provide further details on the power and design in GWAS as well as an accompanying interactive statistical software \citep{gaoUPASS_ShinyApp}.
 

### 2021-01-13 3.phase_transitions/3.global-tests.tex

--- 2020-08-17 3.phase_transitions/3.global-tests.tex
@@
 The optimality of sparse signal detection was first studied by \citet{ingster1998minimax}, who showed that a phase transition in the $r$-$\beta$ plane exists for the signal detection problem. 
-Specifically, assuming equal signal sizes with magnitude $\sqrt{2{r}\log{p}}$, if the signal size $r$ is above a so-called detection boundary,
+Specifically, consider the so-called {\em detection boundary} function:
 \begin{equation} \label{eq:detection-boundary-large-signals}
@@
     \begin{cases}
-        \max\{0,\; \beta - 1/2\} & 0 < \beta \le 3/4, \\
-        \left(1 - \sqrt{1-\beta}\right)^2 & 3/4 < \beta \le 1,
+        \max\{0,\beta -1/2\} & 0<\beta\le 3/4\\
+        \left(1 - \sqrt{1-\beta}\right)^2 & 3/4 < \beta \le 1.
     \end{cases}
+    \quad\quad \beta\in (0,1].
 \end{equation} 
-then the global null hypothesis $\mu(i)=0$ for all $i=1,\ldots,p$ can be distinguished from the alternative as $p\to\infty$ in the sense of \eqref{eq:support-recovery-success} using the likelihood ratio test;
-otherwise, when signal sizes fall below the boundary, no test can do better than a random guess.
-Adaptive tests such as Tukey's \ac{HC} \citep{donoho2004higher} and a modified goodness-of-fit test statistic of \citet{zhang2002powerful} have been identified to attain this performance limit without knowledge of the sparsity and signal sizes.
-% We visualize this boundary $f$ in the upper panel of Figure \ref{fig:phase-diagram-signal-detection}.
+Assume that the non-zero signal sizes are all equal and parameterized as $\sqrt{2{r}\log{p}}$.
+If the signal size parameter $r$ is {\em above} the detection boundary, i.e., $r>f(\beta)$, then the global null 
+hypothesis $\mu(i)=0$ for all $i=1,\dots,p$ can be distinguished from the alternative as $p\to\infty$ in the sense of \eqref{eq:support-recovery-success} using the likelihood ratio test.
+Otherwise, when the signal sizes fall below the boundary, i.e., $r< f(\beta)$, no test can do better than a
+random guess.  We visualize the detection boundary in the upper panel of Figure
+\ref{fig:phase-diagram-signal-detection}.
+
+Adaptive tests such as Tukey's \ac{HC} in \eqref{eq:HC-statistic} \citep{donoho2004higher} and a modified 
+goodness-of-fit test statistic of \citet{zhang2002powerful} have been identified to attain this performance limit 
+without knowledge of the sparsity and signal sizes.
 It is also known that the max-statistic \eqref{eq:max-statistic} is only efficient when $r>(1+\sqrt{1-\beta})^2$, and is therefore sub-optimal for denser signals where $1/2\le\beta\le 3/4$; see \cite{cai2011optimal}.
@@
 
-Notice that the scaling for the signal magnitude $\Delta = \sqrt{2r\log{p}}$ is useful for studying very sparse signals ($\beta>1/2$), but fails to reveal the difficulties of the detection problems when signals are relatively dense ($\beta<1/2$).
-Indeed, a different scaling is needed for small but dense signals.
-With slight overloading of notation, we parametrize signal sizes as 
+Notice that the scaling for the signal magnitude $\Delta = \sqrt{2r\log{p}}$ is useful for studying very sparse signals ($\beta>1/2$), but fails to reveal the difficulties of the detection problems when the signals are relatively dense
+($\beta<1/2$).  This is because $f(\beta) = 0,\ \beta\in (0,1/2]$. Thus, a different scaling is needed to study the regime of
+small but dense signals.  In this case, with slight overloading of notation, we parametrize signal sizes as 
 \begin{equation} \label{eq:signal-size-small} 
@@
 \end{equation}
-where $\underline{r}$ and $\overline{r}$ are negative constants.
-In this scaling for the faint signals, \citet{cai2011optimal} showed that a similar phase transition characterized by the following boundary,
+where $\underline{r}$ and $\overline{r}$ are {\rm negative} constants and 
+the signal magnitude vanishes, as $p\to\infty$.
+In this scaling, for the so-called faint signal regime, \citet{cai2011optimal} established a phase 
+transition result characterized by the following boundary,
 \begin{equation} \label{eq:detection-boundary-small-signals}
-    f_s(\beta) = \beta - 1/2, \quad 0 < \beta \le 1/2,
+    f_s(\beta) = \beta - 1/2, \quad 0 < \beta \le 1/2.
 \end{equation} 
-exists.
 Specifically, if $\overline{r}<f_s(\beta)$, the signal detection fails in the sense of \eqref{eq:support-recovery-failure} regardless of the procedures, while the \ac{HC} statistic continues to attain asymptotically perfect detection when $\underline{r}>f_s(\beta)$.
@@
       % Signal sizes $\Delta$, parametrized by $r$, increases with dimension $p$ inside the upper panel, and decreases with $p$ inside the power panel.
-      The diagrams illustrate the regions where the signal detection problem can be solved asymptotically by some of the commonly used statistics: the maximum ($M$), the sum-of-squares ($L_2$), the sum-of-absolute values ($L_1$), and the sum ($S$).
+      The diagrams illustrate the regions where the signal detection problem can be solved asymptotically by some of the commonly used statistics: the maximum ($M$), the sum-of-squares ($L_2$), the sum-of-absolute values ($L_1$), and the sum ($T$).
       In each region of the diagram, the annotated statistics can make the detection risk \eqref{eq:risk-detection} vanish, as dimension $p$ diverges. Conversely, the risks has liminf at least one.
@@
 
-To the best of our knowledge, performance of simple statistics such as $L_1$, $L_2$ norms, and $S$ in this weak signal setting have not been reported in the literature perhaps due to a perceived lack of novelty.
-Our first Theorem investigates the performance of these routine statistics for detecting sparse signals in high-dimensions, and summarizes the known results.
+To the best of our knowledge, performance of simple statistics such as $L_1$, $L_2$ norms, and 
+\stilian{the sum statistic $T$ in \eqref{eq:sum-statistic}}{R2, Typo 7}
+in this weak signal setting have not been reported in the literature. %perhaps due to a perceived lack of novelty. 
+Our first theorem establishes the performance of these simple but popular statistics for detecting sparse signals 
+in high-dimensions, and summarizes the known results.
 
@@
 
-Theorem \ref{thm:detection-optimality} is proved in Section \ref{sec:proofs} below.
+Theorem \ref{thm:detection-optimality} is proved in Section \ref{sec:supplement}.
 We visualize the results in Theorem in Figure \ref{fig:phase-diagram-signal-detection}.

### 2021-01-13 3.phase_transitions/3.proofs-phase-transitions.tex

@@
 
-\subsection{Auxiliary facts of Gaussian distributions}
+\section{Auxiliary facts of Gaussian distributions}
 \label{sec:Gaussian-distributions}
@@
 
-\subsection{Monotonicity of the Benjamini-Hochberg procedure}
+\section{Monotonicity of the Benjamini-Hochberg procedure}
 \label{suppsec:BH-monotonicity}
@@
 
-\subsection{Proof of Theorem \ref{thm:detection-optimality}}
+\section{Proof of Theorem \ref{thm:detection-optimality}}
 \label{subsec:proof-additive-error-detection-boundaries}
@@
 
-\subsection{Proof of Theorem \ref{thm:Gaussian-error-approx-boundary}}
+\section{Proof of Theorem \ref{thm:Gaussian-error-approx-boundary}}
 \label{subsec:proof-additive-error-approx-boundaries}
@@
 
-\subsection{Proof of Theorems \ref{thm:Gaussian-error-exact-approx-boundary} and \ref{thm:Gaussian-error-approx-exact-boundary}}
+\section{Proof of Theorems \ref{thm:Gaussian-error-exact-approx-boundary} and \ref{thm:Gaussian-error-approx-exact-boundary}}
 \label{subsec:proof-additive-error-mix-boundaries}

### 2021-01-13 3.phase_transitions/phase_transitions.tex
minor edits
added

1) ?.Example.tex files for each chapter conforming to the current style.

2) Began the "index".  If you want to include a term do \index{term}{term}

3) Fixed the level of the table-of-contents.

@@
-We study the fundamental limits of the signal detection and support recovery problems in the location models with independent Gaussian errors in this chapter.
+\stilian{The purpose of this chapter is to provide a unified review of the fundamental statistical limits in the 
+sparse signal detection and support recovery problems.  Our goal is to convey the main ideas and thus we shall focus on 
+the simple but important setting of independent Gaussian errors.}{\xout{We study the fundamental limits of the signal detection and support recovery problems in the location models with independent Gaussian errors in this chapter.}}
 Specifically, we derive the conditions under which the detection and support recovery problems succeed and fail in the sense of \eqref{eq:support-recovery-success} and \eqref{eq:support-recovery-failure}, in the additive error model
@@
 where the errors $\epsilon(i)$'s are \ac{iid} standard Gaussians random variables.
-We restrict our analysis to models with independent and identically distributed Gaussian errors for the moment.
-Both the distributional assumption and the independence assumption will be relaxed in the following chapters.
+Once again, we restrict our analysis to models with independent and identically distributed Gaussian errors for the 
+moment. Both the distributional assumption and the independence assumption will be relaxed substantially in the following chapters.
 
-As laid out in Section \ref{sec:asymptotics}, we work under the asymptotic regime where the problem dimension $p$ diverges to infinity.
-Let the signal vectors $\mu = \mu_p$ have 
+As laid out in Section \ref{sec:asymptotics}, we work under the asymptotic regime where the problem dimension 
+$p$ diverges to infinity.  The set of non-zero entires of the signal vector $\mu = \mu_p$ will be referred
+to as its {\em support} and denoted by 
+$$
+ S_p:=\{i\, :\, \mu(i)\not = 0\}.
+$$
+We shall assume that the size of the support is
 \begin{equation} \label{eq:signal-sparsity-additive}
-    |S_p| = \left\lfloor p^{1-\beta} \right\rfloor, \quad \beta\in(0,1]
+    |S_p| = \left\lfloor p^{1-\beta} \right\rfloor, \quad \beta\in(0,1],
 \end{equation}
-non-zero entries, where $\beta$ parametrizes the problem sparsity.
-The closer $\beta$ is to 1, the sparser the support $S$; conversely, when $\beta$ is close to 0, the support is dense with many non-null signals.
+where $\beta$ parametrizes the problem sparsity.
+The closer $\beta$ is to 1, the sparser the support $S_p$.  
+Conversely, when $\beta$ is close to 0, the support is dense with many non-null signals.
 We consider one-sided alternatives \eqref{eq:global-test-one-sided}, and parametrize the range of the non-zero (and perhaps unequal) signals with
@@
 
-\section{Proofs}
-\label{sec:proofs}
-\input{3.phase_transitions/3.proofs-phase-transitions.tex}
+%\section{Proofs}
+%\label{sec:proofs}
+%\input{3.phase_transitions/3.proofs-phase-transitions.tex}

### 2021-01-13 6.GWAS/GWAS.tex
Addressed the minor typos of R2
I defined the command "\stilian" in the preamble and used it to make changes in response to the minor typos.

Please see reviews/GS_Annotated.pdf.

@@
 % and Figure \ref{fig:phase-chi-squared} continues to apply.
-indicating vanishing differences between the difficulties of the one-sided and two-sided alternatives in the Gaussian additive error model \eqref{eq:model-additive}.
+This indicates vanishing differences between the difficulties of the one-sided and two-sided alternatives in the Gaussian additive error model \eqref{eq:model-additive}.
 
@@
 \input{6.GWAS/6.proofs-GWAS.tex}
-
-\section{Exercises}
-\label{sec:Exercises-GWAS}
-\input{6.GWAS/6.Exercises.tex}

### 2021-01-13 preamble.tex

@@
 of \cite{ingster1998minimax} and \cite{donoho2004higher}, the subject has received a lot of attention in the literature with important contributions
-from \cite{ji2012ups,genovese2012comparison,jin2014optimality,arias2017distribution,butucea2018variable}.  These works (among others) 
- have discovered the presence of fundamental limits in the so-called  {\em needle in haystack} problems, where a sparse signal is observed in 
- high-dimensional additive noise.  In this setting, two archetypal  problems arise -- the {\em signal detection} and {\em signal support recovery}.  
- Signal detection is a hypothesis testing problem, which amounts
-to testing for the presence of non-zero signal in some (any) of the dimensions.
-Support recovery, on the other hand, is an inference problem, which aims to estimate the signal support -- the locations of the non-zero signal components.
-The fundamental limits of these problems are studied in the so-called high-dimensional asymptotics regime where the sample size $n$ is fixed and the dimension $p$ of the underlying signal
-grows to infinity.
+from \cite{ji2012ups,genovese2012comparison,jin2014optimality,arias2017distribution,butucea2018variable}.
+These works, among many others, have discovered some fundamental limits in the so-called  {\em needle in haystack} problems, where a sparse signal is observed with high-dimensional additive noise.
+In this setting, two archetypal  problems arise -- the {\em signal detection} and {\em signal support recovery}.
+The signal detection refers to a global hypothesis testing problem that amounts
+to determining the presence of non-zero signal in any of its dimensions. 
+The support recovery, on the other hand, can be seen either as a multiple testing problem where the presence of non-zero signal is tested for each signal location of interest, or alternatively,  as an inference problem that aims to estimate the signal support, i.e., the locations of the non-zero signal components.
+The fundamental limits of these problems are studied in the so-called high-dimensional asymptotic regime where the dimension $p$ of the underlying signal grows to infinity, and the sample size $n$ is either bounded or grows slowly relative to $p$.
 
-From a probabilistic perspective, the above phase transition phenomena are asymptotic zero-one type laws, as $p\to\infty$.  
+From a probabilistic perspective, these aforementioned fundamental limits are stated as asymptotic zero-one type laws, as dimensionality diverges.  
 Namely, consider a sparse signal with  {\em support size} on the order of $p^{1-\beta}$ for some parameter $\beta\in (0,1)$.  
@@
 {\bf Acknowledgements.} The authors gratefully acknowledge the support of their families and all colleagues from the Statistics Department 
-at the University of Michigan, Ann Arbor.   Special thanks (in alphabetical order) go to Xuming He, Tailen Hsing, Michalis Kallitsis, Liza Levina, 
-Rodderick Little, Ya'acov Ritov, Kerby Shedden, Jinqi Shen, Jonathan Terhorst, Gongjun Xu, \stilian{R2, Typo 1}{\fbox{add more}}
+at the University of Michigan, Ann Arbor.
+Special thanks (in alphabetical order) go to Xuming He, Tailen Hsing, Michalis Kallitsis, Liza Levina, Yuanzhi Li, Rodderick Little, Ya'acov Ritov, Kerby Shedden, Jinqi Shen, Jonathan Terhorst, Gongjun Xu.
 The authors were partially supported by the NSF program {\em Algorithms for Threat Detection}.

### 2021-01-13 4.exact_support_recovery/exact_support_recovery.tex
Chapter 4
Implementing the corrections...

@@
 Although our method of analysis applies to all light-tailed error distributions with rapidly varying tails (see Definition \ref{def:rapid-variation}), to be concrete and better convey the main ideas, we will focus on the class of $\mathrm{AGG}(\nu)$ laws (see Definition \ref{def:AGG}).
-Extensions of the results to other error models are presented in Section \ref{suppsec:other-boundaries}.
+\stilian{Extensions of the results to other error models are presented in Section \ref{suppsec:other-boundaries}.}{
+\fbox{But, we may bring them back if eliminating the proofs from Ch. 6 gives us enough space!}}
 
-As in Chapter \ref{chap:phase-transitions}, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector $\mu = \left(\mu(i)\right)_{i=1}^p$ where the sparsity, with a few exceptions which will be explicitly stated, is parametrized as
+As in Chapter \ref{chap:phase-transitions}, we assume the signal in model \eqref{eq:model-additive} to be a sparse vector $\mu_p = \left(\mu_p(i)\right)_{i=1}^p$, with support
+$
+S_p:= \{ i\, :\, \mu_p(i)\not = 0\}.
+$ 
+The signal sparsity, with a few exceptions which will be explicitly stated, is parametrized as
 \begin{equation} \label{eq:sparsity-parametrized}
@@
 with parameters $0 < \underline{r} \le \overline{r} \le +\infty$.
-Notice that the parametrization now depends on the shape of the assumed error distributions $\mathrm{AGG}(\nu)$ through the parameter $\nu$.
+Notice that the parametrization now depends on the shape of the assumed error distributions $\mathrm{AGG}(\nu)$ through the parameter $\nu>0$.
 
-According to Lemma \ref{lemma:risk-exact-recovery-probability}, in order to study the asymptotic behaviors of $\mathrm{risk}^{\mathrm{E}}$, it is sufficient to establish minimal conditions under which the support sets can be consistently estimated, i.e.,
+According to Lemma \ref{lemma:risk-exact-recovery-probability}, in order to study the asymptotic behaviors of 
+the {\em exact support recovery} $\mathrm{risk}^{\mathrm{E}}$, it is sufficient to establish conditions under which the support sets can be consistently estimated, i.e.,
 \begin{equation} \label{eq:exact-recovery} 
@@
 
-Several authors have studied the support recovery problem in terms of the Hamming loss and obtained minimax optimality results (see, e.g., \cite{ji2012ups, genovese2012comparison, jin2014optimality, butucea2018variable}).
+Several authors have studied the support recovery problem in terms of the Hamming loss and obtained minimax optimality results \citep[see, e.g.][]{ji2012ups, genovese2012comparison, jin2014optimality, butucea2018variable}.
 % We briefly review the recent work by \cite{butucea2018variable}, whose .
 In the special case of Gaussian marginals, \cite{butucea2018variable} showed that the boundary \eqref{eq:strong-classification-boundary-Gaussian} exists in a minimax sense.
-That is, when errors are \emph{independent} Gaussians, the Hamming loss cannot be made to vanish if signal sizes fall below the boundary \eqref{eq:strong-classification-boundary-Gaussian} by any procedure.
-Conversely, if signal size falls below, the Hamming loss can be made to vanish with a specific thresholding procedure.
+That is, when errors are \emph{independent} Gaussians and the signal sizes fall below the boundary 
+\eqref{eq:strong-classification-boundary-Gaussian}, then no procedure can have a vanishing Hamming
+loss, as $p\to\infty$.  Conversely, if signal sizes are above that same boundary, the Hamming loss can be made to 
+vanish with a specific thresholding procedure.
 
-Unfortunately, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and the sharp result does not carry over directly to the study of the probability of support recovery or exact support recovery risk.
-More importantly, despite their elegance, these Hamming loss-minimax studies naturally \stilian{reduce}{\xout{amounts}} to the analysis of the elementary case of iid data, and is by design blind to non-trivial error-dependence structures.
-This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
+Unfortunately, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, but
+not necessary for support recovery \eqref{eq:exact-recovery}, and the sharp results of \cite{butucea2018variable}, 
+do not carry over directly to the study of the probability of support recovery or the exact support recovery risk.
+More importantly, despite their elegance, these Hamming loss-minimax studies naturally reduce to the analysis of the special case of iid errors, which is by design blind to non-trivial error-dependence structures.
+%%This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
 % This is arguably a consequence of the inherent limitation of the Hamming-loss approach. 
@@
 
-So far in the literature, the role of dependence, and that of the distributional assumptions in model \eqref{eq:model-additive} remain largely unexplored.  
+So far in the literature, the role of dependence, and that of the distributional assumptions in model \eqref{eq:model-additive} remained largely unexplored.  
 This chapter offers advances in both directions, and provides a close-to-complete solution of the exact support recovery problem. (See also, Chapter \ref{chap:URS}.)
@@
 
-Conversely, we show in Theorem \ref{thm:necessary}, that for a surprisingly large class of dependence structures characterized by the concept of \emph{uniform relative stability} (URS, see Definition \ref{def:URS} below), when the signal size is below the boundary  (i.e., $r<g(\beta)$), no thresholding procedure can achieve the asymptotically perfect support recovery \eqref{eq:exact-recovery}.
-In fact,
+Conversely, under mild error-dependence conditions, we show in Theorem \ref{thm:necessary}, that
+no thresholding procedure can achieve the asymptotically perfect support recovery \eqref{eq:exact-recovery}
+when the signal size is below the boundary  (i.e., $r<g(\beta)$).   In fact, in this case, we have
 \begin{equation} \label{eq:exact-recovery-failure}
@@
 \end{equation}
-for all $\widehat{S}_p$ in the form of \eqref{eq:thresholding-procedure}.
+for all $\widehat{S}_p$ in the form of \eqref{eq:thresholding-procedure}.  This strong 
+impossibility of exact support recovery result holds for a surprisingly large class of dependence structures 
+characterized by the concept of \emph{uniform relative stability} (URS, see Definition \ref{def:URS} below).
 
-These two results show that the thresholding procedures obey a phase transition phenomenon in a strong, \emph{point-wise} sense over the class of URS dependence structures, and over the class of AGG$(\nu),\ \nu>0$ error distributions.
-The conclusions are fundamentally stronger and more informative than the minimax statements in the literature (see, e.g., \cite{butucea2018variable}).
-The techniques developed in this here are also entirely different from those in \citet{ji2012ups} or \citet{butucea2018variable}, and transparent characterizations of the dependence conditions under which the phase transition type result holds will be established in the Chapter \ref{chap:URS} later.
+These two results show that the thresholding procedures obey a phase transition phenomenon in a strong, 
+\emph{point-wise} sense over the class of errors with AGG$(\nu),\ \nu>0$ marginal distributions {\em and} URS 
+dependence. The conclusions are fundamentally stronger and more informative than the minimax statements in the literature \citep[see, e.g.,][]{butucea2018variable}.
+The techniques developed here are also entirely different from those in \citet{ji2012ups} or \citet{butucea2018variable}.
+\stilian{It should be noted that the URS condition is fundamentally weaker than the conventional ``mixing conditions'' employed in the analysis of sums and averages.
+This is because the key to exact support recovery is the study of extremes
+(viz maxima) which have fundamentally different behavior than sums, under dependence.
+More insights and transparent characterizations of the dependence conditions under which the phase transition type result holds will be established in the Chapter \ref{chap:URS}.}{\fbox{check}}
 
@@
 \medskip
-
 The phase transition phenomena for two additional classes of error distributions with either heavier or lighter tails than the AGG distributions will be described in Section \ref{suppsec:other-boundaries}.

### 2021-01-15 4.exact_support_recovery/4.minimax.tex
updated Ch 4
I updated up to and including Ch 4.2.2.

Hope to finish tomorrow.

@@
 
-Meanwhile, if we search over \emph{all procedures}, but expand the parameter space to include {all} dependence structures, then a different minimax optimality statement holds for Bonferroni's procedure.
+Meanwhile, if we search over \emph{all procedures}, but expand the space of models to include {\em all} dependence structures, then a different minimax optimality statement holds for Bonferroni's procedure.
 This result, formally stated in Section \ref{subsec:minimax-over-dependence}, is a consequence of our characterization of the finite-sample Bayes optimality of thresholding procedures in Sections \ref{subsec:Bayes-optimality} and \ref{subsec:optimal-procedure-sub-exponential}.
@@
 
-In studying support recovery problems (e.g., \citet{arias2017distribution}), restrictions to the thresholding procedures are sometimes justified by arguing that such procedures are the ``reasonable'' choice for estimating the support set.
+\stilian{\fbox{SUGGESTION}}{ What do you think about making the Bayesian stuff a Chapter?
+I think it stands well on its own...
+plus it is somewhat different from the ``non-Bayesian'' setup of the previous support recovery results...}
+
+\stilian{
+In studying support recovery problems \citep[e.g.,][]{arias2017distribution}, often the attention is restricted to the class of
+thresholding procedures.  This is justified by arguing that such procedures are the ``reasonable'' choice for estimating the support set.
 %  In Theorem \ref{thm:sufficient} we saw that a (FWER-controlling) thresholding procedure is indeed consistent for support recovery. 
 % It is natural to ask if it will be sufficient to restrict our attention to only such procedures.
-We show in this section that, perhaps surprisingly, for general error models, thresholding procedures are not always optimal, even when the observations are independent.
+We show in this section that, in many cases, the finite-sample Bayes optimal procedures do indeed belong to the class of thresholding procedures.  
+Perhaps surprisingly, however, we also show that for general error models, the thresholding procedures are sub-optimal, 
+even when the observations are independent.  Roughly speaking, in the additive error 
+models \eqref{eq:model-additive},  this distinction depends on whether or not the error density is log-concave 
+(Proposition \ref{prop:log-concave} and Corollary \ref{cor:log-convex}).}{\fbox{edited, agree?}}
 
-We shall identify the optimal procedure for support recovery problems under a Bayesian setting with general distributional assumptions (including but not limited to additive models \eqref{eq:model-additive}).
-Specifically, we assume that there is an ordered set $P = (i_1,\ldots,i_s)$, $i_i\in\{1,\ldots,p\}$, and $s$ (not necessarily equal) densities $f_{1}, \ldots, f_{s}$, such that the observations indexed by $P$ have corresponding densities.
-That is,
+We shall identify the optimal procedure for support recovery problems under a Bayesian setting with general distributional assumptions 
+(including but not limited to additive models \eqref{eq:model-additive}). 
+Specifically, consider an ordered set $P = (i_1,\ldots,i_s)$ of $s$ distinct indices in $\{1,\ldots,p\}$, which will be referred to 
+as the {\em ordered support} of the signal.  Consider also $s$ (not necessarily equal) signal densities 
+$f_{1}, \ldots, f_{s}$ as well as an error density $f_0$. We shall assume that the observations with indices $i_j$ 
+are drawn independently from $f_j$:
 \begin{equation} \label{eq:signal-distributions-ordered}
-x(i_j) \sim f_j, \quad j=1,\ldots,s.
+x(i_j) \sim f_j, \quad j=1,\ldots,s,
 \end{equation}
-Let also the rest $(p-s)$ observations have common density $f_0$, i.e., $x(i)\sim f_0$ for $i\not\in S$.
+while the remaining $(p-s)$ observations have common density $f_0$, i.e., $x(i)\sim f_0$ for $i\not\in S$. 
 We further assume that the observations $x$ are mutually independent.
 
-We adopt here a Bayesian framework to measure statistical risks. 
-Let the ordered support $P=(i_1,\ldots,i_s)$ have prior
+We adopt now a Bayesian framework to measure statistical risks and assume that the underlying (unknown) support is {\em random}. Namely,
+let the ordered support $P=(i_1,\ldots,i_s)$ have prior
 \begin{equation} \label{eq:uniform-ordered}
@@
 for all distinct $1\le i_1, \ldots, i_s\le p$.
-Consequently, the unordered support $S=\{i_1,\ldots,i_s\}$ is distributed uniformly in the collection of all set of size $s$, with the unordered uniform distribution $\pi^{\text{u}}$.
-That is, for all for all $S\in\mathcal{S}:=\left\{S\subseteq\{1,\ldots,p\};|S|=s\right\}$, we have
+Consequently, the unordered support $S=\{i_1,\ldots,i_s\}$ is distributed uniformly over the collection of all sets of size $s$, with 
+the unordered uniform distribution $\pi^{\text{u}}$. That is, for all $S\in\mathcal{S}:=\left\{S\subseteq\{1,\ldots,p\};|S|=s\right\}$, we have 
 \begin{equation} \label{eq:uniform}
@@
 where the probability is taken over the randomness in the observations only. 
+\stilian{(The $x(i)$'s are conditionally independent, given the ordered support $P$.)}{\fbox{added.  Agree?}}
 The Bayes optimal procedures should minimize 
@@
 
-Their relationship is summarized in the following lemma.
+The relationship between the above two notions is summarized next.
 

### 2021-01-15 4.exact_support_recovery/4.numerical.tex
updated Ch 4
I updated up to and including Ch 4.2.2.

Hope to finish tomorrow.

@@
-We examine numerically the boundaries \eqref{eq:strong-classification-boundary} under several error tail assumptions for independence errors in this section.
-Numerical experiments for dependent errors will be deferred until we characterize the \ac{URS} conditions in Chapter \ref{chap:URS}.
+\stilian{Here, we examine numerically the applicability of the asymptotic boundaries 
+\eqref{eq:strong-classification-boundary} for finite $p$.
+We consider independent errors for several popular models of the marginal distribution.
+Numerical experiments for dependent errors will be deferred to Chapter \ref{chap:URS}.}{\fbox{check}}
 
@@
 under the generalized Gaussian ($\nu = 1/2$) errors. Here $W$ is the Lambert W function, i.e., $W=f^{-1}$ where $f(x)=x\exp{(x)}$.
-The choices of thresholds correspond to Bonferroni's procedures with FWER decreasing at a rate of $1/\sqrt{\log{p}}$, therefore satisfying the assumptions in Theorem \ref{thm:sufficient}.
-Experiments were repeated 1000 times under each sparsity-and-signal-size combination.
+The choices of thresholds correspond to Bonferroni's procedures with FWER decreasing at a rate of 
+${\cal O}(1/\sqrt{\log{p}})$, therefore satisfying the assumptions in Theorem \ref{thm:sufficient}.
+The experiments were repeated independently 1000 times under each sparsity-and-signal-size combination.
 
+\stilian{Figure \ref{fig:phase-simulated} shows the resulting empirical probabilities of exact support recovery over 
+a grid of $r$ and $\beta$ values for the cases of small dimensions ($p=100$, left panels) and high dimensions ($p=10\ 000$, right panels).  
+Observe that the asymptotic boundary is rather accurate in the high-dimensional regime.  
+The phase-transition phenomenon is also evident and practically relevant in dimensions as small 
+as $p=100$.}{ \fbox{suggested replacement of the following}
  The results of the numerical experiments are shown in Figure \ref{fig:phase-simulated}.
-The numerical results illustrate that the predicted boundaries are not only accurate in high-dimensions ($p=10000$, right panels of Figure \ref{fig:phase-simulated}), but also practically meaningful even at moderate dimensions ($p=100$, left panels of Figure \ref{fig:phase-simulated}).
+The numerical results illustrate that the predicted boundaries are not only accurate in high-dimensions ($p=10^4$, right panels of Figure \ref{fig:phase-simulated}), but also practically meaningful even at moderate dimensions ($p=100$, left panels of Figure \ref{fig:phase-simulated}).}
+
+     \stilian{\fbox{Question:}} {In Figure \ref{fig:phase-simulated}
+      Do we know what the DETECTION boundary is for Non-Gaussian  AGG$(1/2)$?  You are plotting a line in the 
+      bottom panels for the DETECTION boundary, but is this exactly a line?  Has this been studied in the literature 
+      actually or are we CONJECTURING this boundary -- note that Chapter 3 focuses on the Gaussian case only and we don't prove the detection 
+      boundary, right?}
 
@@
       \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_NLC_p10000.eps}
-      \caption{The empirical probability of exact support recovery from numerical experiments, as a function of sparsity level $\beta$ and signal sizes $r$, from Gaussian error models (upper panels), Laplace error models (middle panels), and generalized Gaussian with $\nu=1/2$ (lower panels); darker color indicates higher probability of exact support recovery.
+      \caption{The empirical probability of exact support recovery from numerical experiments, as a function of sparsity level $\beta$ and signal sizes $r$, 
+      from Gaussian error models (upper panels), Laplace error models (middle panels), and generalized Gaussian with $\nu=1/2$ (lower panels); darker color indicates higher probability of exact support recovery.
       The experiments were repeated 1000 times for each sparsity-signal size combination, and for dimensions $p=100$ (left panels) and $p=10000$ (right panels). 
-Numerical results agree with the boundaries described in Theorem \ref{thm:sufficient}; convergence is noticeably slower for under generalized Gaussian ($\nu=1/2$) errors.
-      For reference, the dashed and dash-dotted lines represent the weak classification and detection boundaries (see Chapter \ref{chap:phase-transitions}).}
-      \label{fig:phase-simulated}
+      The numerical results agree with the boundaries described in Theorem \ref{thm:sufficient}. The convergence is noticeably slower for under the heavier 
+      generalized Gaussian ($\nu=1/2$) errors.  For reference, the dashed and dash-dotted lines represent the weak classification and detection boundaries
+       (see Chapter \ref{chap:phase-transitions}).
+      \label{fig:phase-simulated}}
 \end{figure}

### 2021-01-15 5.URS/URS.tex
minor edits
added

1) ?.Example.tex files for each chapter conforming to the current style.

2) Began the "index".  If you want to include a term do \index{term}{term}

3) Fixed the level of the table-of-contents.
updated Ch 4
I updated up to and including Ch 4.2.2.

Hope to finish tomorrow.

@@
 
+\medskip
+\noindent{\bf The Berman and UDD conditions.} 
+ \label{UDD_and_Berman}
  Suppose that the array of errors  ${\cal E}$ comes from a stationary Gaussian time series $\epsilon(i),\ i\in \mathbb{N}$, with auto-covariance $r_p=\cov(\epsilon(i+p),\epsilon(i))$. 

### 2021-01-15 4.exact_support_recovery/4.pointwise.minimax.tex
.

--- 2020-08-17 4.exact_support_recovery/4.minimax.tex
@@
 % This is an enhancement (in the asymptotic sense) of the minimax results in Section 4.1 of \cite{butucea2018variable}, where the supremum was taken over the dependence structures.
-
-\subsection{Bayes optimality in support recovery problems}
-\label{subsec:Bayes-optimality}
-
-In studying support recovery problems (e.g., \citet{arias2017distribution}), restrictions to the thresholding procedures are sometimes justified by arguing that such procedures are the ``reasonable'' choice for estimating the support set.
-%  In Theorem \ref{thm:sufficient} we saw that a (FWER-controlling) thresholding procedure is indeed consistent for support recovery. 
-% It is natural to ask if it will be sufficient to restrict our attention to only such procedures.
-We show in this section that, perhaps surprisingly, for general error models, thresholding procedures are not always optimal, even when the observations are independent.
-
-We shall identify the optimal procedure for support recovery problems under a Bayesian setting with general distributional assumptions (including but not limited to additive models \eqref{eq:model-additive}).
-Specifically, we assume that there is an ordered set $P = (i_1,\ldots,i_s)$, $i_i\in\{1,\ldots,p\}$, and $s$ (not necessarily equal) densities $f_{1}, \ldots, f_{s}$, such that the observations indexed by $P$ have corresponding densities.
-That is,
-\begin{equation} \label{eq:signal-distributions-ordered}
-x(i_j) \sim f_j, \quad j=1,\ldots,s.
-\end{equation}
-Let also the rest $(p-s)$ observations have common density $f_0$, i.e., $x(i)\sim f_0$ for $i\not\in S$.
-We further assume that the observations $x$ are mutually independent.
-
-We adopt here a Bayesian framework to measure statistical risks. 
-Let the ordered support $P=(i_1,\ldots,i_s)$ have prior
-\begin{equation} \label{eq:uniform-ordered}
-\pi((i_1,\ldots, i_s)) = {(p-s)!}/{p!},
-\end{equation}
-for all distinct $1\le i_1, \ldots, i_s\le p$.
-Consequently, the unordered support $S=\{i_1,\ldots,i_s\}$ is distributed uniformly in the collection of all set of size $s$, with the unordered uniform distribution $\pi^{\text{u}}$.
-That is, for all for all $S\in\mathcal{S}:=\left\{S\subseteq\{1,\ldots,p\};|S|=s\right\}$, we have
-\begin{equation} \label{eq:uniform}
-\pi^{\text{u}}
-(\{i_1,\ldots, i_s\}) = \sum_{\sigma}\pi((i_{\sigma(1)},\ldots, i_{\sigma(s)})) = {(p-s)!s!}/{p!},
-\end{equation}
-where the sum is taken over all permuations of $\{1,2,\ldots,s\}$.
-
-For any fixed configuration $P$, consider the loss function,
-$$
-\ell(\widehat{S},S) := \P[\widehat{S} \neq S] = \P_{P}[\widehat{S} \neq S],
-$$
-where the probability is taken over the randomness in the observations only.
-The Bayes optimal procedures should minimize 
-\begin{equation} \label{eq:Bayes-risk}
-    \E_\pi \P[\widehat{S} \neq S],
-\end{equation}
-where the expectation is taken over the random configurations $P$, with a uniform distribution $\pi$ as specified in \eqref{eq:uniform-ordered}.
-
-% For a sequence of estimators $\widehat{S} = \widehat{S}_p$, the asymptotically optimal procedures are defined to be the ones that minimize the asymptotic Bayes risk,
-% \begin{equation} \label{eq:Bayes-risk}
-%     R(\widehat{S}) := \limsup_{p\to\infty} \E_{P,{\cal E}} [\ell(\widehat{S},S)] = \limsup_{p\to\infty} \P_{P,{\cal E}}[\widehat{S} \neq S].
-% \end{equation}
-
-If, however, the sparsity $s = |S|$ of the problem is known, then a natural estimator for $S$ would be based on the set of top $s$ order statistics.
-\begin{definition}[Oracle data thresholding]
-We call $\widehat{S}^* = \{i\,|\, x(i)\ge x_{[s]}\}$ the oracle data thresholding procedure, where $x_{[1]} \ge \ldots \ge x_{[p]}$ are the order statistics of $x$.
-\end{definition}
-
-The finite-sample optimality of the oracle thresholding procedure $\widehat{S}^*$ is intimately linked with the \emph{monotone likelihood ratio} (MLR) property.
-\begin{definition}[Monotone Likelihood Ratio]
-A family of positive densities on $\R$, $\{f_\delta, \delta \in U\}$, is said to have the MLR property if, for all $\delta_0, \delta_1\in U\subseteq\R$ such that $\delta_0 < \delta_1$, the likelihood ratio $\left(f_{\delta_1}(x)/f_{\delta_0}(x)\right)$ is an increasing function of $x$.
-\end{definition}
-
-Their relationship is summarized in the following lemma.
-
-\begin{proposition} \label{prop:optimal-oracle-procedures}
-Let the observations $x(i)$, $i=1,\ldots,p$ be as prescribed as in \eqref{eq:signal-distributions-ordered} through \eqref{eq:uniform-ordered}.
-If each of $\{f_0, f_{1}\},\ldots,\{f_0,f_{s}\}$ form an MLR family, then the oracle data thresholding procedure $\widehat{S}^* = \{i\,|\, x(i)\ge x_{[s]}\}$ is finite-sample optimal in terms of Bayes risk $\E_\pi \P[\widehat{S} \neq S]$.
-That is,
-\begin{equation} \label{eq:finite-sample-Bayes-optimal}
-    \widehat{S}^* \in \argmin_{\widehat{S}} \E_\pi \P[\widehat{S} \neq S].
-\end{equation}
-for all $s$ and $p$.
-\end{proposition}
-
-The proof of Proposition \ref{prop:optimal-oracle-procedures} is found in Section \ref{suppsec:proofs}.
-
-We emphasize that the oracle thresholding procedures are in fact \emph{finite-sample optimal} in the above Bayesian context.
-Further, our setup allows for different alternative distributions, and relaxes the assumptions of \citet{butucea2018variable} when studying distributional generalizations, where the alternatives are assumed to be identically distributed.
-
-It remains to understand when the key MLR property holds. 
-We elaborate on this question next.
-
-\subsection{Bayes optimality under sub-exponential errors}
-\label{subsec:optimal-procedure-sub-exponential}
-
-Returning to the more concrete signal-plus-noise model \eqref{eq:model-additive}, it turns out that the error tail behavior is what determines the optimality of data thresholding procedures.
-In this setting, log-concavity of the error densities is \emph{equivalent} to the MLR property (Lemma \ref{lemma:MLR-log-concavity}).
-This, in turn, yields the finite-sample optimality of data thresholding procedures (Proposition \ref{prop:log-concave}).
-
-\begin{lemma} \label{lemma:MLR-log-concavity}
-Let $\delta$ be the magnitude of the non-zero signals in the signal-plus-noise model \eqref{eq:model-additive} with positive error density $f_0$, and let $f_\delta(x) = f_0(x-\delta)$.
-The family $\{f_\delta, \delta \in \R\}$ has the MLR property if and only if the error density $f_0$ is log-concave.
-\end{lemma}
-
-\begin{proof}[Proof of Lemma \ref{lemma:MLR-log-concavity}]
-Suppose MLR holds, we will show that $f_0(t) = \exp\{\phi(t)\}$ for some concave function $\phi$.
-By the assumption of MLR, for any $x_1 < x_2$, setting $\delta_0 = 0$, and $\delta_1 = (x_2 - x_1)/2 > 0$, we have
-\begin{equation*}
-    \log{\frac{f_{\delta_1}(x_2)}{f_{\delta_0}(x_2)}}
-    = \phi\left(\frac{(x_1+x_2)}{2}\right)- \phi(x_2) 
-    \ge \phi(x_1)- \phi\left(\frac{(x_1+x_2)}{2}\right) 
-    = \log{\frac{f_{\delta_1}(x_1)}{f_{\delta_0}(x_1)}}.
-\end{equation*}
-This implies that the log-density $\phi(t)$ is midpoint-concave, i.e., for all $x_1$ and $x_2$, we have,
-\begin{equation}
-    \phi\left(\frac{(x_1+x_2)}{2}\right) 
-    \ge \frac{1}{2} \phi(x_1) + \frac{1}{2} \phi(x_2).
-\end{equation}
-For Lebesgue measurable functions, midpoint concavity is equivalent to concavity by the Sierpinki Theorem (see, e.g., Sec I.3 of \cite{donoghue2014distributions}). This proves the `only-if' part.
-
-For the `if' part, when  $\phi(t) = \log{(f_0(t))}$ is log-concave, then for any $\delta_0 < \delta_1$, and any $x<y$, we have
-\begin{equation} \label{eq:concavity-implies-MLR}
-    \log{\frac{f_{\delta_1}(y)}{f_{\delta_0}(y)}} - \log{\frac{f_{\delta_1}(x)}{f_{\delta_0}(x)}}
-    = \phi(y-\delta_1) - \phi(y-\delta_0) - \phi(x-\delta_1) + \phi(x-\delta_0) \ge 0,
-\end{equation}
-where the last inequality is a simple consequence of concavity (see Lemma \ref{lemma:four-point-concavity}). This proves the `if' part.
-\end{proof}
-
-Proposition \ref{prop:optimal-oracle-procedures} and Lemma \ref{lemma:MLR-log-concavity} yield immediately the following.
-
-\begin{proposition} \label{prop:log-concave}
-Consider the additive error model \eqref{eq:model-additive}.
-Let the errors $\epsilon$ be independent with common distribution $F$.
-Let the signal $\mu$ have $s$ positive entries with magnitudes $0<\delta_1\le\ldots\le\delta_s$, located on $\{1,\ldots,p\}$ as prescribed in \eqref{eq:uniform-ordered}.
-If $F$ has a positive, log-concave density $f$, then the oracle thresholding procedure $\widehat{S}^* = \{i\,;\,x(i)\ge x_{[s]}\}$ is finite-sample optimal in terms of Bayes risk in the sense of \eqref{eq:finite-sample-Bayes-optimal}.
-\end{proposition} 
-Notice that under MLR (or equivalently, log-concavity of the errors in additive models), the oracle thresholding procedure is finite-sample optimal even in the case where the signals have different (positive) sizes.
-
-The assumption of log-concavity of the densities is compatible with the AGG model when $\nu\ge1$, as demonstrated in the next example.
-
-\begin{example} \label{exmp:AGG-logconcave}
-The generalized Gaussian density $f(x)\propto \exp\{-|x|^\nu/\nu\}$ is log-concave for all $\nu\ge1$.
-Therefore in the additive error model \eqref{eq:model-additive}, according to Proposition \ref{prop:log-concave}, the oracle thresholding procedure is Bayes optimal in the sense of \eqref{eq:finite-sample-Bayes-optimal}.
-\end{example}
-
-%(This also explains the $\gamma\ge 1$ condition in Theorem 1 of Arias-Castro and Chen)
-
-Consider the asymptotic Bayes risk as defined in \eqref{eq:Bayes-risk}, the statement for the necessary condition of support recovery, with the help of Proposition \ref{prop:log-concave}, can be strengthened to include all procedures (in the Bayesian context), regardless of whether they are thresholding.
-
-\begin{theorem} \label{thm:necessary-strengthened}
-Consider the additive model \eqref{eq:model-additive} where the $\epsilon_p(i)$'s are independent and identically distributed with log-concave densities in the AGG class. 
-Let the signals be as prescribed in Proposition \ref{prop:log-concave}.
-If the signal sizes fall below the strong classification boundary \eqref{eq:strong-classification-boundary}, i.e. $\overline{r}<g(\beta)$,
-then we have
-\begin{equation} \label{eq:classification-impossible-Bayes}
-    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi \P[\widehat{S}_p\neq S_p] = 1,
-\end{equation}
-where the infimum on $\widehat{S}_p$ is taken over all procedures.
-\end{theorem}
-
-\begin{proof}[Proof of Theorem \ref{thm:necessary-strengthened}]
-When errors are independent with log-concave density, the oracle thresholding procedure $\widehat{S}^*_p$, by Proposition \ref{prop:log-concave}, minimizes the Bayes risk \eqref{eq:Bayes-risk} among \emph{all} procedures.
-That is,
-$$
-\liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi\P[\widehat{S}_p\neq S_p]
-\ge \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p].
-$$
-Since $\widehat{S}^*_p$ belongs to the class of all thresholding procedures, we have
-\begin{align*}
-    \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p] 
-    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \E_\pi\P[\widehat{S}_p\neq S_p] \\
-    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \inf_{S_p} \P[\widehat{S}_p\neq S_p] = 1,
-\end{align*}
-when $\overline{r}<g(\beta)$, where the last line follows from Theorem \ref{thm:necessary}.
-\end{proof}
-
-% \begin{remark}
-% In view of Theorem \ref{thm:necessary-strengthened}, Bonferroni's thresholding procedure $\widehat{S}_p^{\text{Bonf}}$ described in Theorem \ref{thm:sufficient} is an asymptotically minimax procedure over the class of error models $U(F)$.
-% That is, in the class of errors with AGG($\nu$) marginals $F$ where $\nu\ge1$, we have
-% \begin{equation} \label{eq:minimax}
-%     \widehat{S}_p^{\text{Bonf}} \in \argmin_{\widehat{S}_p} \sup_{{\cal E}\in U(F)} R(\widehat{S}_p),
-% \end{equation}
-% where the minimum is taken over \emph{all} procedures $\widehat{S}$.
-% It can be shown that the supremum in the Bayes risk formulation \eqref{eq:minimax}, where $S$ is random and uniformly distributed, can be replaced by a supremum over all possible (deterministic) configurations of support sets.
-% This can be done by applying Theorem 1.1 in the supplement of \citep{butucea2018variable}.
-% We content ourselves with a Bayesian minimax result here.
-% \end{remark}
-
-\subsection{Minimax optimality over all procedures}
-\label{subsec:minimax-over-dependence}
-
-% In the previous section we demonstrated the minimax optimality of thresholding procedures, in a point-wise sense over a large class of dependence structure.
-Theorem \ref{thm:necessary-strengthened} allows us to state another minimax conclusion --- one in which we search over \emph{all procedures}, by allowing the supremum in the minimax statement to be taken over the dependence structures.
-
-\begin{corollary}
-\label{cor:minimax-over-dependence}
-Let $D(F)$ be the collection of error arrays with common marginal $F$ as defined in \eqref{eq:common-marginal-distribution} where $F$ is an $\text{AGG}(\nu)$ distribution.
-Let also $\widehat{S}^{\text{Bonf}}_p$ be Bonferroni's procedure as described in Theorem \ref{thm:sufficient}.
-If $\underline{r}>g(\beta)$, then we have
-\begin{equation} \label{eq:minimax-over-dependence-over}
-    \limsup_{p\to\infty} \sup_{\substack{\mu\in\Theta_p^+(\beta,\underline{r})\\ {\cal E}\in D(F)}} \P(\widehat{S}^{\text{Bonf}}_p \neq S_p) = 0.
-\end{equation}
-Further, when $\underline{r}<g(\beta)$, and $F$ has a positive log-concave density $f$, we have
-\begin{equation} \label{eq:minimax-over-dependence-under}
-    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \sup_{\substack{\mu\in\Theta_p^+(\beta,\underline{r})\\ {\cal E}\in D(F)}} \P(\widehat{S}_p \neq S_p) = 
-    1,
-\end{equation}
-where the infimum on $\widehat{S}_p$ is taken over all procedures.
-\end{corollary}
-
-\begin{remark}
-Since the class $\text{AGG}(\nu)$, $\nu\ge1$ contains distributions with log-concave densities (Example \ref{exmp:AGG-logconcave}), the minimax statement \eqref{eq:minimax-over-dependence-under} continues to hold if the supremum is taken over the entire class $F\in\text{AGG}(\nu)$, $\nu\ge1$.
-We opted for a more informative formulation which emphasizes the log-concavity condition on the density of $F$.
-\end{remark}
-
-\begin{remark}
-Corollary \ref{cor:minimax-over-dependence} is no stronger than Corollary \ref{cor:point-wise-minimax}. 
-In Corollary \ref{cor:point-wise-minimax} we search over only the class of thresholding procedures, but offer a tight, point-wise lower bound on the asymptotic risk over the class of URS dependence structures.
-On the other hand, Corollary \ref{cor:minimax-over-dependence} provides a uniform lower bound for the asymptotic risk over all dependence structures, which may not be tight except in the case of independent errors.
-% , and when the errors have nice, log-concave densities.
-\end{remark}
-
-\begin{proof}[Proof of Corollary \ref{cor:minimax-over-dependence}]
-Relation \eqref{eq:minimax-over-dependence-over} is a re-statement of Remark \ref{rmk:sufficient-strengthened}.
-
-For any distribution $\pi$ (with a slight abuse of notation) over the parameter space $\Theta_p^+\times D(F)$, we have
-\begin{equation} \label{eq:minimax-over-dependence-under-proof}
-    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \sup_{\substack{\mu\in\Theta_p^+(\beta, \underline{r})\\ {\cal E}\in D(F)}} \P(\widehat{S}_p \neq S_p) 
-\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_{\pi} \P(\widehat{S}_p \neq S_p),
-\end{equation}
-since the supremum is bounded from below by expectations.
-In particular, define $\pi$ to be the uniform distribution over the configurations $\Theta_p^*\times I(f)$, where
-\begin{align*}
-    \Theta_p^* &=
-    \{\mu\in\mathbb{R}^d:\;|S_p|=\lfloor p^{1-\beta}\rfloor,\;\mu(i)=0\;\text{for all }i\not\in S, \;\text{and}\\
-    &\quad\quad\mu(i) = (\nu{r}\log{p})^{1/\nu}\;\text{for all }i\in S,\;\text{where}\;\underline{r}<r<g(\beta)\},
-\end{align*}
-and 
-% \begin{align*}
-%     I(f)&=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\;\text{are independently and identically distributed}\\
-%     &\quad\quad\text{with density}\; f(x)\propto \exp\{-|x|^\nu/\nu\}\}.
-% \end{align*}
-\begin{equation*}
-    I(f)=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\;\text{\ac{iid} with density}\; f(x)\propto \exp\{-|x|^\nu/\nu\}\}.
-\end{equation*}
-
-Since the density $f$ of $F$ is log-concave, the distribution of the signal configurations satisfies the conditions in Theorem \ref{thm:necessary-strengthened}.
-Thus, the desired conclusion \eqref{eq:minimax-over-dependence-under} follows from Theorem \ref{thm:necessary-strengthened} and \eqref{eq:minimax-over-dependence-under-proof}.
-\end{proof}
-
-\subsection{Bayes optimality of likelihood ratio thresholding}
-\label{subsec:optimal-procedure-super-exponential}
-
-The following result provides the general form of finite-sample Bayes optimal procedures.
-It turns out that in general, \emph{likelihood ratio thresholding} is optimal.
-
-\begin{proposition} \label{prop:likelihood-ratio-thresholding}
-Let the observations $x(i)$, $i=1,\ldots,p$ have $s$ signals as prescribed in \eqref{eq:uniform-ordered} having common density $f_a$, and let the rest $(p-s)$ locations have common density $f_0$.
-Define the likelihood ratios 
-$$
-L(i) := {f_a(x(i))}\big/{f_0(x(i))},
-$$
-and let $L_{[1]} \ge L_{[2]} \ge \ldots \ge L_{[p]}$ be the order statistics of the $L(i)$'s.
-Then the procedure $\widehat{S}_{\text{opt}} = \{i\,|\,L(i) \ge L_{[s]}\}$ is finite-sample optimal in terms of Bayes risk. That is,
-\begin{equation}
-    \widehat{S}_{\text{opt}} \in \argmin_{\widehat{S}} \E_\pi \P[\widehat{S} \neq S].
-\end{equation}
-for all $s$ and $p$, where the infimum on $\widehat{S}_p$ is taken over all procedures.
-\end{proposition}
-
-The proof of Proposition \ref{prop:likelihood-ratio-thresholding} is found  in Section \ref{suppsec:proofs}.
-
-% \begin{remark}
-% While the assumption that the alternatives have a common density $f_a$ is slightly more restrictive than in Proposition \ref{prop:optimal-oracle-procedures}, it is not excessively so if one considers a fully Bayesian alternative, where $f_a = p_1f_1 + p_2f_2 + \ldots + p_sf_s$ is a random mixture of alternatives $f_1,\ldots,f_s$ with probability weights $p_1,\ldots,p_s$.
-% \end{remark}
-
-The characterization of optimal likelihood ratio thresholding procedures in Proposition \ref{prop:likelihood-ratio-thresholding} may not always yield practical estimators, as the density of alternatives, and number of signals are typically unknown.
-Still, some insights can be gained by virtue of Proposition \ref{prop:likelihood-ratio-thresholding}.
-In particular, when MLR fails (or equivalently, when the errors in model \eqref{eq:model-additive} do not have log-concave densities), data thresholding is sub-optimal.
-
-\begin{example}[Sub-optimality of data thresholding] \label{exmp:suboptimal-data-thresholding}
-Let the errors have iid generalized Gaussian density with $\nu=1/2$, i.e., $\log{f_0(x)}\propto -x^{1/2}$. 
-Let dimension $p=2$, sparsity $s=1$ with uniform prior, and signal size $\delta=1$.
-That is, $\mathbb P[\mu = (0,1)^\mathrm{T}] = \mathbb P[\mu = (1,0)^\mathrm{T}] = 1/2$.
-If the observations take on values $x = (x_1, x_2)^\mathrm{T} = (1,2)^\mathrm{T}$, we see from a comparison of the likelihoods (and hence, the posteriors),
-$$
-\log \frac{f(x|\{1\})}{f(x|\{2\})} = 2x_1^{1/2} + 2(x_2 - 1)^{1/2} - 2x_2^{1/2} - 2(x_1 - 1)^{1/2} = 4 - 2\sqrt{2} > 0,
-$$
-that even though $x_1<x_2$, the set $\{1\}$ is a better estimate of support than $\{2\}$, i.e., $\mathbb P[S=\{1\}\,\big|\,x] > \mathbb P[S=\{2\}\,\big|\,x]$.
-\end{example}
-
-This simple example shows that, in the case when the errors have super-exponential tails, the optimal procedures are in general \emph{not} data thresholding.
-A slightly more general conclusion can be found in Corollary \ref{cor:log-convex}.
-
-\begin{remark} \label{rmk:tail-assumptions}
-Consider the model \eqref{eq:model-additive} with independent errors, Proposition \ref{prop:likelihood-ratio-thresholding}, and indeed, Example \ref{exmp:suboptimal-data-thresholding} demonstrate that thresholding procedures are in fact \emph{sub-optimal} for $\text{AGG}(\nu)$ models with $\nu<1$.
-Therefore, the optimality of thresholding procedures (specifically, Bonferroni's procedure) only applies to $\text{AGG}(\nu)$ models with $\nu\ge1$. 
-% This suggests that the condition $\nu\ge1$ in Corollary \ref{cor:minimax-over-dependence} is tight.
-
-If we restrict the space of methods to only thresholding procedures, then results in Section \ref{subsec:point-wise-minimax} state that the phase transition phenomenon --- the 0-1 law in the sense of Corollary \ref{cor:point-wise-minimax} --- is universal in all error models with rapidly varying tails.
-This includes $\text{AGG}(\nu)$ models {\it for all} $\nu>0$.
-In contrast, models with heavy (regularly varying) tailed errors do not exhibit this phenomenon (see Theorem \ref{thm:heavy-tails}).
-We summarize the properties of thresholding procedures in Table \ref{table:role-of-thresholding}. 
-\end{remark}
-
-\begin{table}[ht]
-    \centering
-    \caption{Properties of thresholding procedures under different error distributions when errors are independent. Properties of the error distributions are listed in brackets.}
-    \medskip
-    \begin{tabular}{p{45mm}p{40mm}p{40mm}} \toprule
-        Thresholding procedure & Bayes optimality &  Phase transition \\ 
-        (Error distributions) &  (Log-concave density) & (Rapidly-varying tails) \\ \midrule
-        AGG($\nu$), $\nu\ge1$ & Yes (Yes) & Yes (Yes) \\ \cmidrule{1-3}
-        AGG($\nu$), $0<\nu<1$ & No (No) & Yes (Yes) \\ \cmidrule{1-3}
-        Power laws & No (No) & No (No) \\ \bottomrule
-    \end{tabular}
-    \label{table:role-of-thresholding}
-\end{table}
-
-% It should be remarked that Corollary \ref{cor:log-convex} assumes the existence and knowledge of a maximum signal size $\delta_s$. 
-% When maximum signal sizes are unknown a priori, a large observation may be attributed to either a truly large signal, or to the error.
-% Common practice has been to attribute large observations to signals, and not errors.
-
-% As an example, consider the linear regression
-% \begin{equation} \label{eq:regression}
-%  Y = X\mu + \xi,
-% \end{equation}
-% where $\mu$ is a vector of regression coefficients of interest to be inferred from observations of $X$ and $Y$.
-% If the design matrix $X$ is of full column rank, then the OLS estimator of $\mu$ can be formed 
-% \begin{equation*}
-%     \widehat{\mu} = \left(X'X\right)^{-1}X'Y = \mu + \epsilon,
-% \end{equation*}
-% where $\epsilon := (X'X)^{-1}X'\xi$.
-% Hence we recover the generic problem \eqref{eq:model}. 
-% The support recovery problem is therefore equivalent to the fundamental model selection problem.
-% Often an investigator calculates the t-scores of each coefficient as 
-% \begin{equation} \label{eq:linear-model-selection}
-%     \widehat{\mu}(i) \Big/ \widehat{\mathrm{s.e.}}(\widehat{\mu}(i)),
-% \end{equation}
-% where $\widehat{\mathrm{s.e.}}(\widehat{\mu}(i))$ is the estimated standard error of $\widehat{\mu}(i)$.
-% The investigator then chooses indices with large t-scores to enter the model.
-% If the errors in model \eqref{eq:regression} are iid Gaussian, the expression \eqref{eq:linear-model-selection} is t-distributed and have power-law tails; the discussion above suggests that this commonplace procedure may be sub-optimal for bounded signals.

### 2021-01-15 4.exact_support_recovery/4.phase_transition_results.tex
a mess
I tried separating Ch 4 into 2 chapters and I am almost done.  It is still a mess but it might work out nicely!

@@
 
-We present the sufficient condition under which exact support recovery \eqref{eq:exact-recovery} can be achieved in Section \ref{subsec:sufficient}.
-A very general class of dependence structures characterized by the uniform relative stability concept will be introduced in Section \ref{subsec:URS}, to prepare us for the necessary condition in Section \ref{subsec:necessary}.
-
-Section \ref{subsec:dense-signals} discusses the case in which signals are denser than parametrized in \eqref{eq:sparsity-parametrized}, and Section \ref{suppsec:numerical} illustrates the phase transition phenomena with numerical examples.
-
-\subsection{Sufficient conditions for exact support recovery}
+\section{Sufficient conditions for exact support recovery}
 \label{subsec:sufficient}
@@
 
-\subsection{Dependence and uniform relative stability}
+\section{Dependence and uniform relative stability}
 \label{subsec:URS}
@@
 
-\subsection{Necessary conditions for exact support recovery}
+\section{Necessary conditions for exact support recovery}
 \label{subsec:necessary}
@@
 
-\subsection{Dense signals}
+\section{Dense signals}
 \label{subsec:dense-signals}
@@
 
-\subsection{Numerical illustrations for independent errors}
+\section{Numerical illustrations for independent errors}
 \label{suppsec:numerical}

### 2021-01-15 4.exact_support_recovery/exact_support_recovery.tex
.
a mess
I tried separating Ch 4 into 2 chapters and I am almost done.  It is still a mess but it might work out nicely!

--- 2021-01-08 4.exact_support_recovery/exact_support_recovery.tex
@@
 We focus on exact support recovery problems in this chapter, and generalize the results we obtained in Chapter \ref{chap:phase-transitions} to additive error models with much relaxed distributional and dependence assumptions.
+Sufficient conditions for exact support recovery \eqref{eq:exact-recovery} are given in 
+Section \ref{subsec:sufficient}.  A very general class of dependence structures characterized by the uniform relative stability concept will 
+be introduced in Section \ref{subsec:URS}, to prepare us for the necessary condition in Section \ref{subsec:necessary}.
+Section \ref{subsec:dense-signals} discusses the dense signal regime, and Section \ref{suppsec:numerical} illustrates the phase transition 
+phenomena with numerical examples.  We begin with an overview of our results in the context of the existing literature.
 
-Consider the additive error model \eqref{eq:model-additive} with the triangular array of errors,
+\section{Contributions and related work} Consider the additive error model \eqref{eq:model-additive} with the triangular array of errors,
 \begin{equation} \label{eq:error-array}
@@
 In the special case of Gaussian marginals, \cite{butucea2018variable} showed that the boundary \eqref{eq:strong-classification-boundary-Gaussian} exists in a minimax sense.
-That is, when errors are \emph{independent} Gaussians, the Hamming loss cannot be made to vanish if signal sizes fall below the boundary \eqref{eq:strong-classification-boundary-Gaussian} by any procedure.
+That is, when the errors are \emph{independent} Gaussians, the Hamming loss cannot be made to vanish if the signal sizes fall below the boundary \eqref{eq:strong-classification-boundary-Gaussian} by any procedure.
 Conversely, if signal size falls below, the Hamming loss can be made to vanish with a specific thresholding procedure.
 
-Unfortunately, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and the sharp result does not carry over directly to the study of the probability of support recovery or exact support recovery risk.
-More importantly, despite their elegance, these Hamming loss-minimax studies naturally \stilian{reduce}{\xout{amounts}} to the analysis of the elementary case of iid data, and is by design blind to non-trivial error-dependence structures.
+Unfortunately, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and the latter sharp results do not carry over directly to the study of the probability of support recovery or exact support recovery risk.
+More importantly, despite their elegance, these Hamming loss-minimax studies naturally reduce to the analysis of the elementary case of iid data, and is by design blind to non-trivial error-dependence structures.
 This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
@@
 
-So far in the literature, the role of dependence, and that of the distributional assumptions in model \eqref{eq:model-additive} remain largely unexplored.  
-This chapter offers advances in both directions, and provides a close-to-complete solution of the exact support recovery problem. (See also, Chapter \ref{chap:URS}.)
+So far in the literature, the role of dependence, and that of the distributional assumptions in model 
+\eqref{eq:model-additive} have remained largely unexplored.
+This chapter offers advances in both directions, and provides a close-to-complete solution of the exact support recovery problem.
+(See also, Chapter \ref{chap:URS}.)
 We briefly summarize our contributions next.
@@
 \medskip
-
-In Section \ref{sec:boundary}, we study exact support recovery in the sense of \eqref{eq:exact-recovery} directly, under general distributional and dependence assumptions. 
+In Section \ref{subsec:sufficient}, we study exact support recovery in the sense of \eqref{eq:exact-recovery} directly, under general 
+distributional and dependence assumptions.
 In particular, we describe the phase transition phenomena in the dependent AGG model, under the scaling described in \eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized}.
@@
 
+%In Chapter \ref{sec:optimality} we study the finite-sample optimality of the threshold-based support estimation procedures in a Bayesian setting.
+
 % The strong classification boundary $g$ characterizes a phase-transition phenomenon similar to that of the signal detection and approximate support recovery. 
@@
 \medskip
-
-We show in Section \ref{sec:optimality} that data thresholding procedures are not only asymptotically, but in fact, finite sample optimal when the errors are independent and identically distributed (iid) with log-concave densities.
-In this case, no estimator can achieve perfect support recovery when the signal is below the strong classification boundary \eqref{eq:strong-classification-boundary}.  
-Consequently, in the case of $\text{AGG}(\nu)$ errors with $\nu\ge 1$, the strong 
-classification boundary is shown to hold in the minimax 
-sense for \emph{all} procedures. This is formalized in Theorem \ref{thm:necessary-strengthened} and Corollary \ref{cor:minimax-over-dependence}.
-
-\medskip
-
 The phase transition phenomena for two additional classes of error distributions with either heavier or lighter tails than the AGG distributions will be described in Section \ref{suppsec:other-boundaries}.
@@
 \medskip
-
-A final surprising result that had only recently been noticed by the statistical community is that thresholding procedures, including data-dependent ones, are not optimal in general in the support recovery problem when the errors have heavy (regularly-varying) tails.
-\citet{arias2019detection} discussed the phenomena in approximate support recovery problems.
-In this case, we also demonstrate the absence of a phase transition phenomenon in exact support recovery by thresholding, in Section \ref{suppsec:heavy-tailed}.
+To conclude this summary, we emphasize that the sharp phase transition results established in this chapter apply only to
+the general class of thresholding procedures.  In Chapter \ref{chap:optimality}, we characterize the finite-sample Bayes optimal support estimation procedures.
+It will turn out that in many cases the optimal procedures are in fact thresholding procedures.  This will lead to complete phase transition
+results valid for all types of support estimators, for certain classes of error models. In general, however, thresholding procedures
+can be sub-optimal.  This has only recently been noticed by the statistical community in the case when the errors have heavy (regularly-varying) tails. 
+\citet{arias2019detection} discussed the phenomenon in approximate support recovery problems.  In this case, we also demonstrate the absence 
+of a phase transition phenomenon in exact support recovery by thresholding, in Section \ref{suppsec:heavy-tailed}.
 
@@
 
-\section{Exact support recovery under AGG errors}
-\label{sec:boundary}
+%\section{Exact support recovery under AGG errors}
+%\label{sec:boundary}
 \input{4.exact_support_recovery/4.phase_transition_results.tex}
+\input{4.exact_support_recovery/4.pointwise.minimax.tex}
 
-\section{Bayes minimax optimality and (sub)optimality of thresholding procedures}
-\label{sec:optimality}
-\input{4.exact_support_recovery/4.minimax.tex}
+%\section{Bayes minimax optimality and (sub)optimality of thresholding procedures}
 

### 2021-01-15 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
a mess
I tried separating Ch 4 into 2 chapters and I am almost done.  It is still a mess but it might work out nicely!

--- 2020-08-17 4.exact_support_recovery/4.minimax.tex
@@
-We establish in this section minimax versions of our results from Section \ref{sec:boundary}.
-Specifically, if we restrict ourselves to \emph{the class of thresholding procedures} $\cal T$ (defined in \eqref{eq:thresholding-procedure}), then Bonferroni's procedure is minimax optimal, for \emph{any} fixed dependence structures in the URS class.
-This is formalized in Corollary \ref{cor:point-wise-minimax} in Section \ref{subsec:point-wise-minimax}.
-We refer to this result as \emph{point-wise} minimax, to emphasize the fact that this optimality holds for every \emph{fixed} URS array.
-
-Meanwhile, if we search over \emph{all procedures}, but expand the parameter space to include {all} dependence structures, then a different minimax optimality statement holds for Bonferroni's procedure.
-This result, formally stated in Section \ref{subsec:minimax-over-dependence}, is a consequence of our characterization of the finite-sample Bayes optimality of thresholding procedures in Sections \ref{subsec:Bayes-optimality} and \ref{subsec:optimal-procedure-sub-exponential}.
-% The result is of independent interest and it is the main contribution of this section.
-
 Finally, we offer some insights into the support recovery problem in the case when errors have heavier-than-exponential tails in Section \ref{subsec:optimal-procedure-super-exponential}.
 
-\subsection{Point-wise minimax optimality}
-\label{subsec:point-wise-minimax}
-
-Theorems \ref{thm:sufficient} and \ref{thm:necessary} can be cast in the form of an asymptotic minimax statement. 
-% (concealing the gap between sufficient and necessary conditions as pointed out in Remark \ref{rmk:gap-between-sufficient-necessary}).
-
-\begin{corollary}[Point-wise minimax]
-\label{cor:point-wise-minimax}
-Let $\widehat{S}^{\text{Bonf}}$ be the sequence of Bonferroni's procedure described in Theorem \ref{thm:sufficient}. 
-Let also the errors have common $\text{AGG}(\nu)$ distribution $F$ with parameter $\nu>0$, and $\Theta_p^+$ be as defined in \eqref{eq:minimax-signal-config-over}.
-If $\underline{r}>g(\beta)$, then we have
-\begin{equation} \label{eq:point-wise-minimax-above}
-    \limsup_{p\to\infty} \sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P(\widehat{S}^{\text{Bonf}}_p \neq S_p) = 0,
-\end{equation}
-for arbitrary dependence structure of the error array ${\cal E} = \{\epsilon_p(i)\}_p$.
-Let $\cal T$ be the class of thresholding procedures \eqref{eq:thresholding-procedure}. 
-If $\underline{r}<g(\beta)$, then we have
-\begin{equation} \label{eq:point-wise-minimax-below}
-    \liminf_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P(\widehat{S}_p \neq S_p) = 1,
-\end{equation}
-for any error dependence structure such that ${\cal E}\in U(F)$ and ${(-\cal E)}\in U(F)$.
-\end{corollary}
-
-\begin{proof}[Proof of Corollary \ref{cor:point-wise-minimax}]
-The first conclusion \eqref{eq:point-wise-minimax-above} is a restatement of Theorem \ref{thm:sufficient}.
-
-For the second statement \eqref{eq:point-wise-minimax-below}, since $\underline{r}<g(\beta)$, we can pick a sequence $\mu^*\in\Theta_p^+(\beta, \underline{r})$ such that $|S_p| = \lfloor p^{1-\beta}\rfloor$, with signals having the same signal size $\mu(i)=(2r\log{p})^{1/\nu}$ for all $i\in S_p$, where $\underline{r}<{r}<g(\beta)$.
-For this particular choice of $\mu^*$ we have $\mu^*\in\Theta_p^-(\beta, \overline{r})$ where $r<\overline{r}<g(\beta)$,
-and according to Theorem \ref{thm:necessary}, we obtain $\lim_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \mathbb P[\widehat{S}_p \neq S_p] = 1$, for all dependence structures in the URS class.
-\end{proof}
-
-\begin{remark}
-Theorem \ref{thm:necessary} is a stronger result than the traditional minimax claim in Relation \eqref{eq:point-wise-minimax-below}.
-Indeed,  \eqref{eq:classification-impossible-dependent} involves an infimum (over the class $\Theta^-_p$) while \eqref{eq:point-wise-minimax-below} has a supremum (over the class $\Theta^+_p$).
-
-On the other hand, Corollary \ref{cor:point-wise-minimax} is more informative than many minimax-type statements, since it applies ``point-wise'' to any fixed error dependence structure in the URS class.
-\end{remark}
-
-\begin{remark}
-Corollary \ref{cor:point-wise-minimax} echoes Remark \ref{rmk:dependence-assumptions}: for a very large class of dependence structures, we cannot improve upon Bonferroni's procedure in exact support recovery problems (asymptotically), unless we look beyond thresholding procedures.
-% There is a limited amount of literature on non-thresholding procedures that utilize the error dependence structures to improve power.
-% A notable effort was made by \citet{jin2014optimality}, where the performance (in terms of Hamming loss) of a so-called graphlet screening procedure was studied. 
-\end{remark}
-
-% This is an enhancement (in the asymptotic sense) of the minimax results in Section 4.1 of \cite{butucea2018variable}, where the supremum was taken over the dependence structures.
-
-\subsection{Bayes optimality in support recovery problems}
+\section{Bayes optimality in support recovery problems}
 \label{subsec:Bayes-optimality}
@@
 
-The finite-sample optimality of the oracle thresholding procedure $\widehat{S}^*$ is intimately linked with the \emph{monotone likelihood ratio} (MLR) property.
+\subsection{When is oracle thresholding Bayes optimal?} % under sub-exponential errors}
+\label{subsec:optimal-procedure-sub-exponential}
+
+An elegant answer of this question can be given in terms of the \emph{monotone likelihood ratio} (MLR) property.
+
 \begin{definition}[Monotone Likelihood Ratio]
@@
 
-Their relationship is summarized in the following lemma.
+The following result provides a general criterion for the finite-sample optimality of the oracle thresholding 
+procedure $\widehat{S}^*$.
 
@@
 \end{proposition} 
+\begin{proof}%[Proof of Proposition \ref{prop:optimal-oracle-procedures}]
+The problem of support recovery can be equivalently stated as a classification problem, where the discrete parameter space is $\mathcal{S} = \{S\subseteq\{1,\ldots,p\}:|S|=s\}$, and the observation $x \in\R^p$ has likelihood $f(x|S)$ indexed by the support set $S$.
 
-The proof of Proposition \ref{prop:optimal-oracle-procedures} is found in Section \ref{suppsec:proofs}.
+By the optimality of the Bayes classifier (see, e.g., \citep{domingos1997optimality}), a set estimator that maximizes the probability of support recovery is such that
+$$
+\widehat{S} \in \argmax_{S\in \mathcal{S}} f(x|S) \pi(S).
+$$
+Since we know from \eqref{eq:uniform} that $\pi(S)$ is uniform, the problem in our context reduces to showing that $f(x|\widehat{S}^*) = f(x|\widehat{S})$, where $f(x|S)$ is the conditional distribution of data given the unordered support $S$,
+$$
+f(x|S) 
+= \sum_{P\in\sigma(S)} f(x|P) \pi^{\text{ord}}(P|S) 
+= \frac{1}{s!} \left(\sum_{P\in\sigma{(S)}} \prod_{i=1}^s {f_{i}(x(P(i)))}\right) \prod_{k\not\in S}{f_0(x(k))},
+$$
+where $\sigma(S)$ is the set of all permutations of the indices in the support set $S$.
 
-We emphasize that the oracle thresholding procedures are in fact \emph{finite-sample optimal} in the above Bayesian context.
-Further, our setup allows for different alternative distributions, and relaxes the assumptions of \citet{butucea2018variable} when studying distributional generalizations, where the alternatives are assumed to be identically distributed.
+Suppose $\widehat{S} \neq \widehat{S}^*$, then there must be indices $j \in \widehat{S}$ and $j' \in \widehat{S}^c$ such that $x(j) \le x(j')$.
+We exchange the labels of $x(j)$ and $x(j')$, and form a new estimate $\widehat{S}\,' = \big(\widehat{S}\setminus\{j\}\big)\cup\{j'\}$.
+Comparing the likelihoods under $\widehat{S}$ and $\widehat{S}\,'$, we have
+\begin{align}
+    f(x|\widehat{S}) - f(x|\widehat{S}\,') 
+    &= \frac{1}{s!} \sum_{P\in\sigma{(\widehat{S})}} \prod_{i=1}^s {f_{i}(x(P(i)))} f_0(x(j'))\prod_{k\not\in \widehat{S}\cup\{j'\}}{f_0(x(k))} - \nonumber \\
+    &\quad\quad\quad - \frac{1}{s!} \sum_{P'\in\sigma{(\widehat{S}')}} \prod_{i=1}^s {f_{i}(x(P'(i)))} f_0(x(j)) \prod_{k\not\in \widehat{S}'\cup\{j\}}{f_0(x(k))} \nonumber \\
+    &= \frac{1}{s!} \left(\sum_{i=1}^s a_i  \Big(f_i(x(j)) f_0(x(j')) - f_i(x(j')) f_0(x(j))\Big) \right) \prod_{k\not\in \widehat{S}\cup\{j'\}}{f_0(x(k))}, \label{eq:MLR-optimality-proof}
+    % = \log{f_\delta(x(j))} + \log{f_0(x(j'))} - \log{f_\delta(x(j'))} - \log{f_0(x(j))} 
+\end{align}
+where the last equality follows by first summing over all permutations fixing $P(i) = j$ and $P'(i) = j'$, and setting $a_i = \sum_{P\in\sigma{(\widehat{S}\setminus\{j\})}} \prod_{i'\neq i} {f_{i'} (x(P(i')))}$.
+Notice that the $a_i$'s are non-negative.
 
-It remains to understand when the key MLR property holds. 
-We elaborate on this question next.
+Since $x(j) \le x(j')$, and that each of $\{f_0, f_{i}\}$ is an MLR family, we have
+$$
+\frac{f_i(x(j))}{f_0(x(j))} - \frac{f_i(x(j'))}{f_0(x(j'))} \le 0 \implies f_i(x(j)) f_0(x(j')) - f_i(x(j')) f_0(x(j)) \le 0.
+$$
+Using Relation \eqref{eq:MLR-optimality-proof}, we conclude that $f(x|\widehat{S}) \le f(x|\widehat{S}\,')$.
+This implies that any estimator that is not $\widehat{S}^*$ may be improved, and the optimality follows.
+\end{proof}
 
-\subsection{Bayes optimality under sub-exponential errors}
-\label{subsec:optimal-procedure-sub-exponential}
+We emphasize that under the MLR conditions in Proposition \ref{prop:optimal-oracle-procedures},
+ the oracle thresholding procedures are in fact \emph{finite-sample optimal} in the 
+above Bayesian context. Further, our setup allows for different alternative distributions, and relaxes the assumptions 
+of \citet{butucea2018variable} when studying distributional generalizations, where the alternatives are assumed to be identically distributed.
 
+It remains to understand when the key MLR property holds.  We elaborate on this question next.
 Returning to the more concrete signal-plus-noise model \eqref{eq:model-additive}, it turns out that the error tail behavior is what determines the optimality of data thresholding procedures.
@@
 
-\begin{proof}[Proof of Lemma \ref{lemma:MLR-log-concavity}]
+\begin{proof}%[Proof of Lemma \ref{lemma:MLR-log-concavity}]
 Suppose MLR holds, we will show that $f_0(t) = \exp\{\phi(t)\}$ for some concave function $\phi$.
@@
 \end{equation}
-where the last inequality is a simple consequence of concavity (see Lemma \ref{lemma:four-point-concavity}). This proves the `if' part.
+where the last inequality is a simple consequence of concavity (see Lemma \ref{lemma:four-point-concavity} below). This proves the `if' part.
+\end{proof}
+\begin{lemma} \label{lemma:four-point-concavity}
+Let $\phi$ be any concave function on $\R$. For any $x<y\in\R$, and $\delta>0$ we have
+$$
+\phi(x) + \phi(y+\delta) \le \phi(y) + \phi(x+\delta).
+$$
+\end{lemma}
+
+\begin{proof}%[Proof of Lemma \ref{lemma:four-point-concavity}]
+Pick $\lambda = \delta/(y-x+\delta)$, by concavity of $f$ we have
+\begin{equation} \label{eq:four-point-concavity-1}
+    \lambda \phi(x) + (1-\lambda) \phi(y+\delta) 
+    \le \phi(\lambda x + (1-\lambda)(y+\delta)) 
+    = \phi(y),
+\end{equation}
+and
+\begin{equation} \label{eq:four-point-concavity-2}
+    (1-\lambda) \phi(x) + \lambda \phi(y+\delta)
+    \le \phi((1-\lambda) x + \lambda(y+\delta)) 
+    = \phi(x+\delta).
+\end{equation}
+Summing up \eqref{eq:four-point-concavity-1} and \eqref{eq:four-point-concavity-2} and we arrive at the conclusion as desired.
 \end{proof}
@@
 
-\begin{proof}[Proof of Theorem \ref{thm:necessary-strengthened}]
+\begin{proof}%[Proof of Theorem \ref{thm:necessary-strengthened}]
 When errors are independent with log-concave density, the oracle thresholding procedure $\widehat{S}^*_p$, by Proposition \ref{prop:log-concave}, minimizes the Bayes risk \eqref{eq:Bayes-risk} among \emph{all} procedures.
@@
 
+\subsection{Bayes optimality of likelihood ratio thresholding}
+\label{subsec:optimal-procedure-super-exponential}
+
+When the MLR condition in Proposition \ref{prop:optimal-oracle-procedures} is violated, the oracle thresholding 
+procedures can in fact be sub-optimal (see Example \ref{exmp:suboptimal-data-thresholding}, below). 
+The following result provides the general form of the finite-sample Bayes optimal procedures.
+It turns out that in general, \emph{likelihood ratio thresholding} is optimal.
+
+\begin{proposition} \label{prop:likelihood-ratio-thresholding}
+Let the observations $x(i)$, $i=1,\ldots,p$ have $s$ signals as prescribed in \eqref{eq:uniform-ordered} having common density $f_a$, and let the rest $(p-s)$ locations have common density $f_0$.
+Define the likelihood ratios 
+$$
+L(i) := {f_a(x(i))}\big/{f_0(x(i))},
+$$
+and let $L_{[1]} \ge L_{[2]} \ge \ldots \ge L_{[p]}$ be the order statistics of the $L(i)$'s.
+Then the procedure $\widehat{S}_{\text{opt}} = \{i\,|\,L(i) \ge L_{[s]}\}$ is finite-sample optimal in terms of Bayes risk. That is,
+\begin{equation}
+    \widehat{S}_{\text{opt}} \in \argmin_{\widehat{S}} \E_\pi \P[\widehat{S} \neq S].
+\end{equation}
+for all $s$ and $p$, where the infimum on $\widehat{S}_p$ is taken over all procedures.
+\end{proposition} 
+\begin{proof}%[Proof of Proposition \ref{prop:likelihood-ratio-thresholding}]
+The proof is entirely analogous to that of Proposition \ref{prop:optimal-oracle-procedures}.
+Since we know from \eqref{eq:uniform} that $\pi(S)$ is uniform, the problem reduces to showing that $f(x|\widehat{S}_{\text{opt}}) = f(x|\widehat{S})$, where 
+$$
+\widehat{S} \in \argmax_{S \in \mathcal{S}} f(x|S) \pi(S).
+$$
+and
+$f(x|S)$ is the conditional distribution of data given the unordered support $S$,
+\begin{equation} \label{eq:likelihood-ratio-thresholding-proof}
+    f(x|S) = \sum_P f(x|P) \pi^{\text{ord}}(P|S) = \prod_{j\in S} f_a(x(j)) \prod_{j\not\in S}{f_0(x(j))}.
+\end{equation}
+Suppose $\widehat{S} \neq \widehat{S}_{\text{opt}}$, then there must be indices $j \in \widehat{S}$ and $j' \in \widehat{S}^c$ such that $L(j) \le L(j')$.
+If we exchange the labels of $L(j)$ and $L(j')$, that is, we form a new estimate $\widehat{S}\,' = \big(\widehat{S}\setminus\{j\}\big)\cup\{j'\}$,
+comparing the log-likelihoods under $\widehat{S}$ and $\widehat{S}\,'$, we have
+\begin{equation*}
+    \log{f(x|\widehat{S})} - \log{f(x|\widehat{S}\,')} 
+    = \log{f_a(x(j))} + \log{f_0(x(j'))} - \log{f_a(x(j'))} - \log{f_0(x(j))}.
+\end{equation*}
+By the definition of $L(j)$'s, and the order relations, we obtain
+\begin{equation*}
+    \log{f(x|\widehat{S})} - \log{f(x|\widehat{S}\,')} 
+    = \log{L(j)} - \log{L(j')} \le 0
+\end{equation*}
+This implies that any estimator that is not $\widehat{S}_{\text{opt}}$ may be improved, and the optimality follows.
+\end{proof}
+
+The characterization of optimal likelihood ratio thresholding procedures in Proposition \ref{prop:likelihood-ratio-thresholding} may not always yield practical estimators, as the density of alternatives, and number of signals are typically unknown.
+Still, some insights can be gained by virtue of Proposition \ref{prop:likelihood-ratio-thresholding}.
+In particular, when MLR fails (or equivalently, when the errors in model \eqref{eq:model-additive} do not have log-concave densities), data thresholding is sub-optimal.
+
+\begin{example}[Sub-optimality of data thresholding] \label{exmp:suboptimal-data-thresholding}
+Let the errors have iid generalized Gaussian density with $\nu=1/2$, i.e., $\log{f_0(x)}\propto -x^{1/2}$. 
+Let dimension $p=2$, sparsity $s=1$ with uniform prior, and signal size $\delta=1$.
+That is, $\mathbb P[\mu = (0,1)^\mathrm{T}] = \mathbb P[\mu = (1,0)^\mathrm{T}] = 1/2$.
+If the observations take on values $x = (x_1, x_2)^\mathrm{T} = (1,2)^\mathrm{T}$, we see from a comparison of the likelihoods (and hence, the posteriors),
+$$
+\log \frac{f(x|\{1\})}{f(x|\{2\})} = 2x_1^{1/2} + 2(x_2 - 1)^{1/2} - 2x_2^{1/2} - 2(x_1 - 1)^{1/2} = 4 - 2\sqrt{2} > 0,
+$$
+that even though $x_1<x_2$, the set $\{1\}$ is a better estimate of support than $\{2\}$, i.e., $\mathbb P[S=\{1\}\,\big|\,x] > \mathbb P[S=\{2\}\,\big|\,x]$.
+\end{example}
+
+This simple example shows that, in the case when the errors have super-exponential tails, the optimal procedures are in general \emph{not} data thresholding.
+A slightly more general conclusion can be found in Corollary \ref{cor:log-convex}.
+
+\subsection{Sub-optimality of data thresholding procedures}
+
+We provide a slightly more general result on the sub-optimality of data thresholding procedures.
+
+\begin{corollary} \label{cor:log-convex}
+Consider the additive error model \eqref{eq:model-additive}.
+Let the errors $\epsilon$ be independent with common distribution $F$.
+Let each of the $s$ signals be located on $\{1,\ldots,p\}$ uniformly at random with equal magnitude $0<\delta<\infty$.
+% , independently with probability $p_1,\ldots,p_s$.
+% , {\color{red} so that we have $f_a = p_1f_1 + p_2f_2 + \ldots + p_sf_s$.}
+If errors $\epsilon$ are iid with density $f$ log-convex on $[K, +\infty)$, then whenever $j\in\widehat{S}_{\text{opt}}$ for some $x(j) > K+\delta$, we must have $j'\in\widehat{S}_{\text{opt}}$ for all $j'$ such that $K+\delta \le x(j') < x(j)$.
+\end{corollary}
+
+Specifically, if there are $m$ observations exceeding $K+\delta_s$, with $m>s$, then the top $m-s$ observations will \emph{not} be included in the optimal estimator $\widehat{S}_{\text{opt}}$.
+This shows that, in the case when the errors have super-exponential tails, the optimal procedures are in general \emph{not} data thresholding.
+
+\begin{proof}[Proof of Corollary \ref{cor:log-convex}]
+Since the alternative $f_{a}(t) = {f(t-\delta)}$ are log-convex on $[K+\delta, \infty)$, by Relation \eqref{eq:concavity-implies-MLR} in the proof of Lemma \ref{lemma:MLR-log-concavity} and appealing to log-convexity (rather than log-concavity), the likelihood ratio
+$$
+L(j) := \frac{f_a(x(j))}{f_0(x(j))} %= \sum_{i=1}^s \frac{p_if_{i}(x(j))}{f_0(x(j))},
+$$
+is decreasing in $x(j)$ on $[K+\delta, \infty)$.
+The proof is complete by applying Proposition \ref{prop:likelihood-ratio-thresholding}.
+\end{proof}
+
+\begin{remark}[An open problem]
+In the non-log-concave setting, where we know that thresholding procedures are suboptimal, likelihood thresholding procedures are promising, thanks to Proposition \ref{prop:likelihood-ratio-thresholding}.
+
+In the case where the signals have difference sizes, however, likelihood thresholding procedures are undefined since 
+in the proof of Proposition \ref{prop:likelihood-ratio-thresholding}, the signal densities need to be identical for Relation \eqref{eq:likelihood-ratio-thresholding-proof} to hold.
+In such cases, the existence of an optimal procedure is an open problem.
+\end{remark}
+
 % \begin{remark}
@@
 % \end{remark}
+
+\section{Minimax optimality in exact support recovery}
+
+We establish in this section minimax versions of our results from Chapter \ref{chap:exact-support-recovery}.
+Specifically, if we restrict ourselves to \emph{the class of thresholding procedures} $\cal T$ (defined in \eqref{eq:thresholding-procedure}), then Bonferroni's procedure is minimax optimal, for \emph{any} fixed dependence structures in the URS class.
+This is formalized in Corollary \ref{cor:point-wise-minimax} below.% in Section \ref{subsec:point-wise-minimax}.
+We refer to this result as \emph{point-wise} minimax, to emphasize the fact that this optimality holds for every \emph{fixed} URS array.
+
+Meanwhile, if we search over \emph{all procedures}, but expand the model space to include {\em all} dependence 
+structures, then a different minimax optimality statement holds for Bonferroni's procedure.
+This result, formally stated in Section \ref{subsec:minimax-over-dependence}, is a consequence of our characterization 
+of the finite-sample Bayes optimality of thresholding procedures in Sections \ref{subsec:Bayes-optimality} and \ref{subsec:optimal-procedure-sub-exponential}.
+% The result is of independent interest and it is the main contribution of this section.
+
+\subsection{Point-wise minimax optimality for thresholding procedures}
+\label{subsec:point-wise-minimax}
+
+Theorems \ref{thm:sufficient} and \ref{thm:necessary} can be cast in the form of an asymptotic minimax statement. 
+% (concealing the gap between sufficient and necessary conditions as pointed out in Remark \ref{rmk:gap-between-sufficient-necessary}).
+
+\begin{corollary}[Point-wise minimax]
+\label{cor:point-wise-minimax}
+Let $\widehat{S}^{\text{Bonf}}$ be the sequence of Bonferroni's procedure described in Theorem \ref{thm:sufficient}. 
+Let also the errors have common $\text{AGG}(\nu)$ distribution $F$ with parameter $\nu>0$, and $\Theta_p^+$ be as defined in \eqref{eq:minimax-signal-config-over}.
+If $\underline{r}>g(\beta)$, then we have
+\begin{equation} \label{eq:point-wise-minimax-above}
+    \limsup_{p\to\infty} \sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P(\widehat{S}^{\text{Bonf}}_p \neq S_p) = 0,
+\end{equation}
+for arbitrary dependence structure of the error array ${\cal E} = \{\epsilon_p(i)\}_p$.
+Let $\cal T$ be the class of thresholding procedures \eqref{eq:thresholding-procedure}. 
+If $\underline{r}<g(\beta)$, then we have
+\begin{equation} \label{eq:point-wise-minimax-below}
+    \liminf_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P(\widehat{S}_p \neq S_p) = 1,
+\end{equation}
+for any error dependence structure such that ${\cal E}\in U(F)$ and ${(-\cal E)}\in U(F)$.
+\end{corollary}
+
+\begin{proof}%[Proof of Corollary \ref{cor:point-wise-minimax}]
+The first conclusion \eqref{eq:point-wise-minimax-above} is a restatement of Theorem \ref{thm:sufficient}.
+
+For the second statement \eqref{eq:point-wise-minimax-below}, since $\underline{r}<g(\beta)$, we can pick a sequence $\mu^*\in\Theta_p^+(\beta, \underline{r})$ such that $|S_p| = \lfloor p^{1-\beta}\rfloor$, with signals having the same signal size $\mu(i)=(2r\log{p})^{1/\nu}$ for all $i\in S_p$, where $\underline{r}<{r}<g(\beta)$.
+For this particular choice of $\mu^*$ we have $\mu^*\in\Theta_p^-(\beta, \overline{r})$ where $r<\overline{r}<g(\beta)$,
+and according to Theorem \ref{thm:necessary}, we obtain $\lim_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \mathbb P[\widehat{S}_p \neq S_p] = 1$, for all dependence structures in the URS class.
+\end{proof}
+
+\begin{remark}
+Theorem \ref{thm:necessary} is a stronger result than the traditional minimax claim in Relation \eqref{eq:point-wise-minimax-below}.
+Indeed,  \eqref{eq:classification-impossible-dependent} involves an infimum (over the class $\Theta^-_p$) while \eqref{eq:point-wise-minimax-below} has a supremum (over the class $\Theta^+_p$).
+
+On the other hand, Corollary \ref{cor:point-wise-minimax} is more informative than many minimax-type statements, since it applies ``point-wise'' to any fixed error dependence structure in the URS class.
+\end{remark}
+
+\begin{remark}
+Corollary \ref{cor:point-wise-minimax} echoes Remark \ref{rmk:dependence-assumptions}: for a very large class of dependence structures, we cannot improve upon Bonferroni's procedure in exact support recovery problems (asymptotically), unless we look beyond thresholding procedures.
+% There is a limited amount of literature on non-thresholding procedures that utilize the error dependence structures to improve power.
+% A notable effort was made by \citet{jin2014optimality}, where the performance (in terms of Hamming loss) of a so-called graphlet screening procedure was studied. 
+\end{remark}
+
+% This is an enhancement (in the asymptotic sense) of the minimax results in Section 4.1 of \cite{butucea2018variable}, where the supremum was taken over the dependence structures.
 
@@
 \end{corollary}
-
-\begin{remark}
-Since the class $\text{AGG}(\nu)$, $\nu\ge1$ contains distributions with log-concave densities (Example \ref{exmp:AGG-logconcave}), the minimax statement \eqref{eq:minimax-over-dependence-under} continues to hold if the supremum is taken over the entire class $F\in\text{AGG}(\nu)$, $\nu\ge1$.
-We opted for a more informative formulation which emphasizes the log-concavity condition on the density of $F$.
-\end{remark}
-
-\begin{remark}
-Corollary \ref{cor:minimax-over-dependence} is no stronger than Corollary \ref{cor:point-wise-minimax}. 
-In Corollary \ref{cor:point-wise-minimax} we search over only the class of thresholding procedures, but offer a tight, point-wise lower bound on the asymptotic risk over the class of URS dependence structures.
-On the other hand, Corollary \ref{cor:minimax-over-dependence} provides a uniform lower bound for the asymptotic risk over all dependence structures, which may not be tight except in the case of independent errors.
-% , and when the errors have nice, log-concave densities.
-\end{remark}
-
-\begin{proof}[Proof of Corollary \ref{cor:minimax-over-dependence}]
+\begin{proof}%[Proof of Corollary \ref{cor:minimax-over-dependence}]
 Relation \eqref{eq:minimax-over-dependence-over} is a re-statement of Remark \ref{rmk:sufficient-strengthened}.
@@
 
-\subsection{Bayes optimality of likelihood ratio thresholding}
-\label{subsec:optimal-procedure-super-exponential}
+\begin{remark}
+Since the class $\text{AGG}(\nu)$, $\nu\ge1$ contains distributions with log-concave densities (Example \ref{exmp:AGG-logconcave}), the minimax statement \eqref{eq:minimax-over-dependence-under} continues to hold if the supremum is taken over the entire class $F\in\text{AGG}(\nu)$, $\nu\ge1$.
+We opted for a more informative formulation which emphasizes the log-concavity condition on the density of $F$.
+\end{remark}
 
-The following result provides the general form of finite-sample Bayes optimal procedures.
-It turns out that in general, \emph{likelihood ratio thresholding} is optimal.
+\begin{remark}
+Corollary \ref{cor:minimax-over-dependence} is no stronger than Corollary \ref{cor:point-wise-minimax}. 
+In Corollary \ref{cor:point-wise-minimax} we search over only the class of thresholding procedures, but offer a tight, point-wise lower bound on the asymptotic risk over the class of URS dependence structures.
+On the other hand, Corollary \ref{cor:minimax-over-dependence} provides a uniform lower bound for the asymptotic risk over all dependence structures, which may not be tight except in the case of independent errors.
+% , and when the errors have nice, log-concave densities.
+\end{remark}
 
-\begin{proposition} \label{prop:likelihood-ratio-thresholding}
-Let the observations $x(i)$, $i=1,\ldots,p$ have $s$ signals as prescribed in \eqref{eq:uniform-ordered} having common density $f_a$, and let the rest $(p-s)$ locations have common density $f_0$.
-Define the likelihood ratios 
-$$
-L(i) := {f_a(x(i))}\big/{f_0(x(i))},
-$$
-and let $L_{[1]} \ge L_{[2]} \ge \ldots \ge L_{[p]}$ be the order statistics of the $L(i)$'s.
-Then the procedure $\widehat{S}_{\text{opt}} = \{i\,|\,L(i) \ge L_{[s]}\}$ is finite-sample optimal in terms of Bayes risk. That is,
-\begin{equation}
-    \widehat{S}_{\text{opt}} \in \argmin_{\widehat{S}} \E_\pi \P[\widehat{S} \neq S].
-\end{equation}
-for all $s$ and $p$, where the infimum on $\widehat{S}_p$ is taken over all procedures.
-\end{proposition}
+\section{A discussion on optimality}
 
-The proof of Proposition \ref{prop:likelihood-ratio-thresholding} is found  in Section \ref{suppsec:proofs}.
+  \stilian{Here we briefly discuss the optimality and sub-optimality of the 
+ thresholding procedures.}{Needs work}
 
-% \begin{remark}
-% While the assumption that the alternatives have a common density $f_a$ is slightly more restrictive than in Proposition \ref{prop:optimal-oracle-procedures}, it is not excessively so if one considers a fully Bayesian alternative, where $f_a = p_1f_1 + p_2f_2 + \ldots + p_sf_s$ is a random mixture of alternatives $f_1,\ldots,f_s$ with probability weights $p_1,\ldots,p_s$.
-% \end{remark}
+%\begin{remark} \label{rmk:tail-assumptions}
 
-The characterization of optimal likelihood ratio thresholding procedures in Proposition \ref{prop:likelihood-ratio-thresholding} may not always yield practical estimators, as the density of alternatives, and number of signals are typically unknown.
-Still, some insights can be gained by virtue of Proposition \ref{prop:likelihood-ratio-thresholding}.
-In particular, when MLR fails (or equivalently, when the errors in model \eqref{eq:model-additive} do not have log-concave densities), data thresholding is sub-optimal.
-
-\begin{example}[Sub-optimality of data thresholding] \label{exmp:suboptimal-data-thresholding}
-Let the errors have iid generalized Gaussian density with $\nu=1/2$, i.e., $\log{f_0(x)}\propto -x^{1/2}$. 
-Let dimension $p=2$, sparsity $s=1$ with uniform prior, and signal size $\delta=1$.
-That is, $\mathbb P[\mu = (0,1)^\mathrm{T}] = \mathbb P[\mu = (1,0)^\mathrm{T}] = 1/2$.
-If the observations take on values $x = (x_1, x_2)^\mathrm{T} = (1,2)^\mathrm{T}$, we see from a comparison of the likelihoods (and hence, the posteriors),
-$$
-\log \frac{f(x|\{1\})}{f(x|\{2\})} = 2x_1^{1/2} + 2(x_2 - 1)^{1/2} - 2x_2^{1/2} - 2(x_1 - 1)^{1/2} = 4 - 2\sqrt{2} > 0,
-$$
-that even though $x_1<x_2$, the set $\{1\}$ is a better estimate of support than $\{2\}$, i.e., $\mathbb P[S=\{1\}\,\big|\,x] > \mathbb P[S=\{2\}\,\big|\,x]$.
-\end{example}
-
-This simple example shows that, in the case when the errors have super-exponential tails, the optimal procedures are in general \emph{not} data thresholding.
-A slightly more general conclusion can be found in Corollary \ref{cor:log-convex}.
-
-\begin{remark} \label{rmk:tail-assumptions}
 Consider the model \eqref{eq:model-additive} with independent errors, Proposition \ref{prop:likelihood-ratio-thresholding}, and indeed, Example \ref{exmp:suboptimal-data-thresholding} demonstrate that thresholding procedures are in fact \emph{sub-optimal} for $\text{AGG}(\nu)$ models with $\nu<1$.
@@
 We summarize the properties of thresholding procedures in Table \ref{table:role-of-thresholding}.
-\end{remark}
+
+%\end{remark}
 

### 2021-01-16 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
update
Cleaned up the new Chapter 5.

@@
 If, however, the sparsity $s = |S|$ of the problem is known, then a natural estimator for $S$ would be based on the set of top $s$ order statistics.
+
+\stilian{\fbox{COMMENT} Just like for the likelihood thresholding procedure, we should be more careful about the ties and how to define
+the oracle thresholding procedure so that $\widehat{S}^*$ has exactly $s$ elements.  I propose the following change}{\, }
+
+\stilian{
+
+For any collection of numbers $\{a_i,\ i=1,\cdots,s\}$, let 
+$$
+\langle a_1,\cdots,a_s\rangle := (a_{[1]},\cdots,a_{[s]})
+$$
+denote the vector of $a_i$'s arranged in a non-increasing order.
+
+\begin{definition}[Oracle data thresholding] Let $x_{[1]} \ge \ldots \ge x_{[p]}$ be the order statistics of
+the data vector $x$.  Any estimator $\widehat{S}^* :=\{ i_1,\cdots,i_s\}$, where
+ $$
+  \langle x(i_1),\cdots,x(i_s)\rangle  = (x_{[1]},\cdots,x_{[s]})
+ $$ 
+ will be referred to as an {\em oracle thresholding estimator}.
+ \end{definition}
+
+ Simply put, the oracle thresholding estimators are comprised of the indices corresponding to the $s$ largest values in the
+ data.  Note that, in the absence of ties among the largest $s+1$ data values, the oracle thresholding estimator is unique.  
+ For concreteness,  one can break possible ties lexicographically.  In many cases, 
+ the oracle thresholding estimators will be almost surely unique.}
+{\fbox{IMPORTANT, replacing the following}
 \begin{definition}[Oracle data thresholding]
 We call $\widehat{S}^* = \{i\,|\, x(i)\ge x_{[s]}\}$ the oracle data thresholding procedure, where $x_{[1]} \ge \ldots \ge x_{[p]}$ are the order statistics of $x$.
-\end{definition}
+\end{definition}}
 
@@
 Let the observations $x(i)$, $i=1,\ldots,p$ be as prescribed as in \eqref{eq:signal-distributions-ordered} through \eqref{eq:uniform-ordered}.
-If each of $\{f_0, f_{1}\},\ldots,\{f_0,f_{s}\}$ form an MLR family, then the oracle data thresholding procedure $\widehat{S}^* = \{i\,|\, x(i)\ge x_{[s]}\}$ is finite-sample optimal in terms of Bayes risk $\E_\pi \P[\widehat{S} \neq S]$.
+If each of the pairs $\{f_0, f_{1}\},\ldots,\{f_0,f_{s}\}$ forms an MLR family, then every oracle data thresholding procedure $\widehat{S}^*$ is finite-sample optimal in terms of Bayes risk $\E_\pi \P[\widehat{S} \neq S]$.
 That is,
@@
 
-By the optimality of the Bayes classifier (see, e.g., \citep{domingos1997optimality}), a set estimator that maximizes the probability of support recovery is such that
+By the optimality of the Bayes classifier \citep[see, e.g.,][]{domingos1997optimality}, a set estimator that maximizes the probability of support recovery is such that
 $$
@@
 $$
-Since we know from \eqref{eq:uniform} that $\pi(S)$ is uniform, the problem in our context reduces to showing that $f(x|\widehat{S}^*) = f(x|\widehat{S})$, where $f(x|S)$ is the conditional distribution of data given the unordered support $S$,
+Since we know from \eqref{eq:uniform} that $\pi(\cdot)$ is uniform, the problem in our context reduces to showing that $f(x|\widehat{S}^*) = f(x|\widehat{S})$, where $f(x|S)$ is the conditional distribution of data given the unordered support $S$,
 $$
@@
 
-Suppose $\widehat{S} \neq \widehat{S}^*$, then there must be indices $j \in \widehat{S}$ and $j' \in \widehat{S}^c$ such that $x(j) \le x(j')$.
-We exchange the labels of $x(j)$ and $x(j')$, and form a new estimate $\widehat{S}\,' = \big(\widehat{S}\setminus\{j\}\big)\cup\{j'\}$.
+Suppose that $\widehat{S}$ is {\em not} an oracle thresholding estimator, then there must be indices 
+$j \in \widehat{S}$ and $j' \not \in \widehat{S}$ such that $x(j) < x(j')$.
+We exchange the labels of $x(j)$ and $x(j')$, and form a new estimate 
+$\widehat{S}\,' = \big(\widehat{S}\setminus\{j\}\big)\cup\{j'\}$.
 Comparing the likelihoods under $\widehat{S}$ and $\widehat{S}\,'$, we have
@@
 
-Since $x(j) \le x(j')$, and that each of $\{f_0, f_{i}\}$ is an MLR family, we have
+Since $x(j) < x(j')$, and since each of $\{f_0, f_{i}\}$ is an MLR family, we have
 $$
@@
 Using Relation \eqref{eq:MLR-optimality-proof}, we conclude that $f(x|\widehat{S}) \le f(x|\widehat{S}\,')$.
-This implies that any estimator that is not $\widehat{S}^*$ may be improved, and the optimality follows.
+\stilian{Continuing this way, we can successively improve the likelihood of every estimator until we arrive at an oracle thresholding estimator, proving the desired optimality.
+Note that with the same argument, any two oracle
+thresholding estimators have the same likelihood.}{
+\fbox{replacing} This implies that any estimator that is not $\widehat{S}^*$ may be improved, and the optimality follows.}
 \end{proof}
@@
 \end{equation}
-For Lebesgue measurable functions, midpoint concavity is equivalent to concavity by the Sierpinki Theorem (see, e.g., Sec I.3 of \cite{donoghue2014distributions}). This proves the `only-if' part.
+For Lebesgue measurable functions, midpoint concavity is equivalent to concavity by the Sierpinki Theorem \citep[see, e.g., Sec I.3 of][]{donoghue2014distributions}. This proves the `only-if' part.
 
@@
 \begin{proposition} \label{prop:log-concave}
-Consider the additive error model \eqref{eq:model-additive}.
-Let the errors $\epsilon$ be independent with common distribution $F$.
+Consider the additive error model \eqref{eq:model-additive}, where the $\epsilon(i)$'s are
+independent with common distribution $F$.
 Let the signal $\mu$ have $s$ positive entries with magnitudes $0<\delta_1\le\ldots\le\delta_s$, located on $\{1,\ldots,p\}$ as prescribed in \eqref{eq:uniform-ordered}.
-If $F$ has a positive, log-concave density $f$, then the oracle thresholding procedure $\widehat{S}^* = \{i\,;\,x(i)\ge x_{[s]}\}$ is finite-sample optimal in terms of Bayes risk in the sense of \eqref{eq:finite-sample-Bayes-optimal}.
+
+If $F$ has a positive, log-concave density $f$, then the support estimator % oracle thresholding procedure 
+$$
+ \widehat{S}^* := \{i\, :\, x(i)\ge x_{[s]}\}
+$$ 
+is  %a.s.\ unique and
+finite-sample optimal in terms of Bayes risk in the sense of \eqref{eq:finite-sample-Bayes-optimal}.
 \end{proposition} 
-Notice that under MLR (or equivalently, log-concavity of the errors in additive models), the oracle thresholding procedure is finite-sample optimal even in the case where the signals have different (positive) sizes.
+\begin{proof} The independence and the fact that the observations have densities implies the absence of 
+ties among the order statistics $\{x_{[i]}\}$, with probability one.  Thus, the oracle thresholding procedure is a.s.\ unique 
+and given by $\widehat{S}^* = \{i\, :\, x(i)\ge x_{[s]}\}$.  The result then follows from 
+Proposition \ref{prop:optimal-oracle-procedures} and Lemma \ref{lemma:MLR-log-concavity}.
+\end{proof}
 
-The assumption of log-concavity of the densities is compatible with the AGG model when $\nu\ge1$, as demonstrated in the next example.
+\begin{remark}
+Propositions \ref{prop:optimal-oracle-procedures} and \ref{prop:log-concave} show that under MLR (or equivalently, 
+log-concavity of the errors in additive models), the oracle thresholding procedures are finite-sample optimal even in the case where the signals have different (positive) sizes.
+This fascinating property perhaps
+explains the success of the thresholding estimators.
+\end{remark}
+
+The assumption of log-concavity of the densities is compatible with the AGG model when $\nu\ge1$, as 
+demonstrated in the next example.
 
@@
 
-Consider the asymptotic Bayes risk as defined in \eqref{eq:Bayes-risk}, the statement for the necessary condition of support recovery, with the help of Proposition \ref{prop:log-concave}, can be strengthened to include all procedures (in the Bayesian context), regardless of whether they are thresholding.
+\stilian{COMMENT}{Consider moving the following discussion \& theorem to the section on Minimax below...}
+
+Consider the asymptotic Bayes risk as defined in \eqref{eq:Bayes-risk}. The statement for the 
+necessary condition of support recovery, with the help of Proposition \ref{prop:log-concave}, can be 
+strengthened to include all procedures (in the Bayesian context), regardless of whether they are thresholding.
 
@@
 \begin{proof}%[Proof of Theorem \ref{thm:necessary-strengthened}]
-When errors are independent with log-concave density, the oracle thresholding procedure $\widehat{S}^*_p$, by Proposition \ref{prop:log-concave}, minimizes the Bayes risk \eqref{eq:Bayes-risk} among \emph{all} procedures.
+When the errors are independent with log-concave density, the oracle thresholding procedure $\widehat{S}^*_p$, by Proposition \ref{prop:log-concave}, minimizes the Bayes risk \eqref{eq:Bayes-risk} among \emph{all} procedures.
 That is,
@@
 When the MLR condition in Proposition \ref{prop:optimal-oracle-procedures} is violated, the oracle thresholding 
-procedures can in fact be sub-optimal (see Example \ref{exmp:suboptimal-data-thresholding}, below). 
-The following result provides the general form of the finite-sample Bayes optimal procedures.
-It turns out that in general, \emph{likelihood ratio thresholding} is optimal.
+procedures can in fact be sub-optimal (see Example \ref{exmp:suboptimal-data-thresholding} and 
+Section \ref{sec:sup-optimality-of-thresholding}, below).  
+%
+\stilian{In this section, we demonstrate that thresholding the \emph{likelihood ratio} rather than signal values
+yields the finite-sample Bayes optimal procedures.  We consider a special but sufficiently general case of signal 
+models with equal densities.
 
-\begin{proposition} \label{prop:likelihood-ratio-thresholding}
-Let the observations $x(i)$, $i=1,\ldots,p$ have $s$ signals as prescribed in \eqref{eq:uniform-ordered} having common density $f_a$, and let the rest $(p-s)$ locations have common density $f_0$.
+Namely, let the observations $x(i)$, $i=1,\ldots,p$ have $s$ signals as prescribed in \eqref{eq:uniform-ordered} with {\em common} ``signal'' density $f_a$, and let the remaining $(p-s)$ locations have common ``error'' density $f_0$.
 Define the likelihood ratios 
@@
 and let $L_{[1]} \ge L_{[2]} \ge \ldots \ge L_{[p]}$ be the order statistics of the $L(i)$'s.
-Then the procedure $\widehat{S}_{\text{opt}} = \{i\,|\,L(i) \ge L_{[s]}\}$ is finite-sample optimal in terms of Bayes risk. That is,
+
+\begin{definition}[Oracle likelihood ratio thresholding] Recall that $\langle a_1,\cdots,a_s\rangle$ denotes
+the vector of $a_i$'s arranged in a non-increasing order.  Any estimator $\hat S = \{i_1,\cdots,i_s\}$ such that
+$$
+\langle L(i_1),\cdots,L(i_s) \rangle = (L_{[1]},\cdots,L_{[s]}),
+$$
+will be referred to as an {\em oracle likelihood thresholding} estimator of the support $S$.
+\end{definition}
+\begin{proposition} \label{prop:likelihood-ratio-thresholding} Any oracle likelihood ratio thresholding 
+procedure $\widehat{S}_{\text{LRT}}$ is finite-sample optimal in terms of Bayes risk. That is,
 \begin{equation}
-    \widehat{S}_{\text{opt}} \in \argmin_{\widehat{S}} \E_\pi \P[\widehat{S} \neq S].
+    \widehat{S}_{\text{LRT}} \in \argmin_{\widehat{S} \in {\mathcal S}} \E_\pi \P[\widehat{S} \neq S].
 \end{equation}
-for all $s$ and $p$, where the infimum on $\widehat{S}_p$ is taken over all procedures.
+for all $s$ and $p$, where the infimum on $\widehat{S}$ is taken over all support estimators of size $s$.
 \end{proposition} 
+}{Introducing part of the proposition as a definition....}
+
+\stilian{NOTE}{This change \& definition
+ was motivated by the annoying fact that we could have ties among the likelihood ratios.  Also, to my understanding we
+ must LIMIT OURSELVES to estimators of size $s$, so we should limit $|\widehat{S}_{{\rm LRT}}|$ to $s$. \fbox{CORRECT?} I am SORRY if I made a MESS.}
+
 \begin{proof}%[Proof of Proposition \ref{prop:likelihood-ratio-thresholding}]
-The proof is entirely analogous to that of Proposition \ref{prop:optimal-oracle-procedures}.
-Since we know from \eqref{eq:uniform} that $\pi(S)$ is uniform, the problem reduces to showing that $f(x|\widehat{S}_{\text{opt}}) = f(x|\widehat{S})$, where 
+The proof is analogous to that of Proposition \ref{prop:optimal-oracle-procedures}.
+We need to show that
+$
+\widehat{S}_{\rm LRT} \in \argmax_{S \in \mathcal{S}} f(x|S) \pi(S).
+$
+Since the distribution $\pi$ of the support $S$ 
+is uniform (recall \eqref{eq:uniform}), it is equivalent to prove that 
 $$
-\widehat{S} \in \argmax_{S \in \mathcal{S}} f(x|S) \pi(S).
+f(x|\widehat{S}_{\text{LRT}}) = \max_{S \in \mathcal {S}} f(x|S),
 $$ 
-and
-$f(x|S)$ is the conditional distribution of data given the unordered support $S$,
+where  $f(x|S)$ is the conditional distribution of the data given the unordered support $S$,
 \begin{equation} \label{eq:likelihood-ratio-thresholding-proof}
@@
 \end{equation}
-Suppose $\widehat{S} \neq \widehat{S}_{\text{opt}}$, then there must be indices $j \in \widehat{S}$ and $j' \in \widehat{S}^c$ such that $L(j) \le L(j')$.
-If we exchange the labels of $L(j)$ and $L(j')$, that is, we form a new estimate $\widehat{S}\,' = \big(\widehat{S}\setminus\{j\}\big)\cup\{j'\}$,
+Suppose $\widehat S\in {\mathcal S}$ is {\em not} an oracle likelihood thresholding estimator. 
+Then from the definition of the likelihood ratio thresholding procedure, there 
+must be indices 
+$j \in \widehat S$ and $j' \not \in \widehat{S}$ such that $L(j) < L(j')$.
+If we exchange the labels of $L(j)$ and $L(j')$, that is, we form a new estimate 
+$\widehat{S}\,' = \big(\widehat{S}\setminus\{j\}\big)\cup\{j'\}$,
 comparing the log-likelihoods under $\widehat{S}$ and $\widehat{S}\,'$, we have
@@
     \log{f(x|\widehat{S})} - \log{f(x|\widehat{S}\,')} 
-    = \log{L(j)} - \log{L(j')} \le 0
+    = \log{L(j)} - \log{L(j')} > 0
 \end{equation*}
-This implies that any estimator that is not $\widehat{S}_{\text{opt}}$ may be improved, and the optimality follows.
+\stilian{This shows that $\widehat S$ cannot be Bayes optimal unless it is a likelihood thresholding estimator.
+Note that with the same argument for every two likelihood thresholding estimators $\widehat S'$
+and $\widehat S''$, we have $ f(x|\widehat{S}') = f(x|\widehat{S}'')$, proving the desired optimality.
+}{\fbox{Please check.} See also the change in the oracle thresholding argument.}
 \end{proof}
 
-The characterization of optimal likelihood ratio thresholding procedures in Proposition \ref{prop:likelihood-ratio-thresholding} may not always yield practical estimators, as the density of alternatives, and number of signals are typically unknown.
-Still, some insights can be gained by virtue of Proposition \ref{prop:likelihood-ratio-thresholding}.
+The characterization of optimal likelihood ratio thresholding procedures in Proposition \ref{prop:likelihood-ratio-thresholding} may not always yield practical estimators, as the density of the alternatives, and the number of signals $s$
+are typically unknown. Still, some insights can be gained by virtue of Proposition \ref{prop:likelihood-ratio-thresholding}.
 In particular, when MLR fails (or equivalently, when the errors in model \eqref{eq:model-additive} do not have log-concave densities), data thresholding is sub-optimal.
@@
 
-\subsection{Sub-optimality of data thresholding procedures}
+\subsection{Sub-optimality of data thresholding procedures}\label{sec:sup-optimality-of-thresholding}
 
@@
 % , {\color{red} so that we have $f_a = p_1f_1 + p_2f_2 + \ldots + p_sf_s$.}
-If errors $\epsilon$ are iid with density $f$ log-convex on $[K, +\infty)$, then whenever $j\in\widehat{S}_{\text{opt}}$ for some $x(j) > K+\delta$, we must have $j'\in\widehat{S}_{\text{opt}}$ for all $j'$ such that $K+\delta \le x(j') < x(j)$.
+Assume the errors $\epsilon(i)$'s are iid with density $f$ that is log-convex on $[K, +\infty)$, for some $K>0$.
+
+If $\widehat{S}_{\rm opt}$ is the Bayes optimal (i.e., the oracle likelihood thresholding estimator), then, whenever 
+$j\in\widehat{S}_{\text{opt}}$ for some $x(j) > K+\delta$, we must necessarily have $j'\in\widehat{S}_{\text{opt}}$ for 
+all $j'$ such that $K+\delta \le x(j') < x(j)$.
 \end{corollary}
 
-Specifically, if there are $m$ observations exceeding $K+\delta_s$, with $m>s$, then the top $m-s$ observations will \emph{not} be included in the optimal estimator $\widehat{S}_{\text{opt}}$.
-This shows that, in the case when the errors have super-exponential tails, the optimal procedures are in general \emph{not} data thresholding.
+Specifically, if there are $m$ observations exceeding $K+\delta$, with $m>s$, then the top $m-s$ observations will \emph{not} be included in the optimal estimator $\widehat{S}_{\text{opt}}$.
+This shows that, in the case when the
+errors have super-exponential tails, the optimal procedures are in general \emph{not} data thresholding.
 
 \begin{proof}[Proof of Corollary \ref{cor:log-convex}]
-Since the alternative $f_{a}(t) = {f(t-\delta)}$ are log-convex on $[K+\delta, \infty)$, by Relation \eqref{eq:concavity-implies-MLR} in the proof of Lemma \ref{lemma:MLR-log-concavity} and appealing to log-convexity (rather than log-concavity), the likelihood ratio
+Since the density of the alternatives $f_{a}(t) = {f(t-\delta)}$ is log-convex on $[K+\delta, \infty)$, by Relation \eqref{eq:concavity-implies-MLR} in the proof of Lemma \ref{lemma:MLR-log-concavity} and appealing to log-convexity (rather than log-concavity), the likelihood ratio
 $$
@@
 $$
-is decreasing in $x(j)$ on $[K+\delta, \infty)$.
-The proof is complete by applying Proposition \ref{prop:likelihood-ratio-thresholding}.
+is decreasing in $x(j)$ on $[K+\delta, \infty)$.  The claim follows from Proposition \ref{prop:likelihood-ratio-thresholding}.
 \end{proof}
 
-\begin{remark}[An open problem]
-In the non-log-concave setting, where we know that thresholding procedures are suboptimal, likelihood thresholding procedures are promising, thanks to Proposition \ref{prop:likelihood-ratio-thresholding}.
+\begin{remark}[An open problem] As we have seen, the thresholding estimators are no longer optimal 
+in the additive model with error-densities heavier than exponential.   Thanks to Proposition 
+\ref{prop:likelihood-ratio-thresholding}, the oracle likelihood thresholding procedures are promising alternatives
+that can lead us to practical support estimators.
 
-In the case where the signals have difference sizes, however, likelihood thresholding procedures are undefined since 
-in the proof of Proposition \ref{prop:likelihood-ratio-thresholding}, the signal densities need to be identical for Relation \eqref{eq:likelihood-ratio-thresholding-proof} to hold.
-In such cases, the existence of an optimal procedure is an open problem.
+In the case where the signals have difference sizes, however, the argument in the proof of Proposition \ref{prop:likelihood-ratio-thresholding} breaks downs since the signal densities need to be identical for Relation \eqref{eq:likelihood-ratio-thresholding-proof} to hold.
+In such cases, the characterization of the optimal procedure is an open problem.
 \end{remark}
@@
 This result, formally stated in Section \ref{subsec:minimax-over-dependence}, is a consequence of our characterization 
-of the finite-sample Bayes optimality of thresholding procedures in Sections \ref{subsec:Bayes-optimality} and \ref{subsec:optimal-procedure-sub-exponential}.
+of the finite-sample Bayes optimality of thresholding procedures in Section \ref{subsec:optimal-procedure-sub-exponential}.
 % The result is of independent interest and it is the main contribution of this section.

### 2021-01-16 4.exact_support_recovery/4.phase_transition_results.tex
update
cleaned up Ch 4.

Both (new) Ch 4 and 5 are ready to re-read.

@@
 \end{theorem}
-
-\begin{corollary}[Classes of procedures attaining the boundary]
-\label{cor:FWER-controlling_procedures}  
-Relation \eqref{eq:exact-supporot-recovery} holds for any FWER-controlling procedure that is strictly more powerful than Bonferroni's procedure. 
-This includes Holm's procedure \citep*{holm1979simple}, and in the case of independent errors, Hochberg's procedure \citep*{hochberg1988sharper}, and the {\v{S}}id{\'a}k procedure \citep*{vsidak1967rectangular}.
-\end{corollary}
-
-\begin{example} \label{exmp:FWER-controlling_procedures}
-Under Gaussian errors, the particular choice of the thresholding at $t_p = \sqrt{2\log{p}}$ in \eqref{eq:Bonferroni-procedure} corresponds to a Bonferroni's procedure with FWER decreasing at a rate of $(\log{p})^{-1/2}$, and hence Theorem \ref{thm:sufficient} applies.
-By Corollary \ref{cor:FWER-controlling_procedures}, Holm's procedure --- and when the errors are independent, the {\v{S}}id{\'a}k, and Hochberg procedures --- with FWER controlled at $(\log{p})^{-1/2}$ all achieve perfect support recovery provided that $\underline{r}>g(\beta)$.
-\end{example}
-
-%Proof of Theorem \ref{thm:sufficient} is found in Section \ref{sec:proofs}, 
-The claims in Example \ref{exmp:FWER-controlling_procedures} are verified in Section \ref{suppsec:proofs}.
-
-We now turn to the proof of Theorem \ref{thm:sufficient}.
-
-\begin{proof}[Proof of Theorem \ref{thm:sufficient}]
-Throughout the proof, dependence on $p$ will be suppressed to simplify notations when such omissions do not lead to ambiguity.
+\begin{proof}%[Proof of Theorem \ref{thm:sufficient}]
+Throughout the proof, the dependence on $p$ will be suppressed to simplify notations when such omissions do not lead to ambiguity.
 
@@
 
-The statements in Theorem \ref{thm:sufficient} can be strengthened, to prepare us for a minimax result given in Section \ref{sec:optimality} below.
+\medskip
+We end this section with several comments and applications of Theorem \ref{thm:sufficient}.
+\begin{corollary}[Classes of procedures attaining the boundary]
+\label{cor:FWER-controlling_procedures}  
+Relation \eqref{eq:exact-supporot-recovery} holds for any FWER-controlling procedure that is strictly more powerful than Bonferroni's procedure. 
+This includes Holm's procedure \citep*{holm1979simple}, and in the case of independent errors, Hochberg's procedure \citep*{hochberg1988sharper}, and the {\v{S}}id{\'a}k procedure \citep*{vsidak1967rectangular}.
+\end{corollary}
+
+\begin{example} \label{exmp:FWER-controlling_procedures}
+Under Gaussian errors, the particular choice of the thresholding at $t_p = \sqrt{2\log{p}}$ in \eqref{eq:Bonferroni-procedure} corresponds to a Bonferroni's procedure with FWER decreasing at a rate of ${\cal O}((\log{p})^{-1/2})$, and hence Theorem \ref{thm:sufficient} applies.
+By Corollary \ref{cor:FWER-controlling_procedures}, Holm's procedure --- and when the errors are independent, the {\v{S}}id{\'a}k, and Hochberg procedures --- with FWER controlled at $(\log{p})^{-1/2}$ all achieve perfect support recovery provided that $\underline{r}>g(\beta)$.
+
+\begin{proof}[Example \ref{exmp:FWER-controlling_procedures}]
+By the Mill's ratio for the standard Gaussian distribution,
+$$
+\frac{t_p \P\left[Z>t_p\right]}{\phi(t_p)} \to 1,\quad \text{as}\quad t_p\to\infty,
+$$
+where $Z\sim \text{N}(0,1)$. 
+Using the expression for $t_p = \sqrt{2\log{p}}$, we have
+$$
+p \;\P\left[Z>t_p\right] \sim \sqrt{2\pi}^{-1}\left(2\log{p}\right)^{-1/2} \to 0,
+$$
+as desired. The rest of the claims follow from Corollary \ref{cor:FWER-controlling_procedures}.
+\end{proof}
+\end{example}
+
+The statements in Theorem \ref{thm:sufficient} can be strengthened, to prepare us for a minimax result given in Section \ref{sec:minimax} below.
 
@@
 \end{theorem}
-
-% We comment on some consequences of the theorem, before presenting its proof.
-Our first comment is on the signal sizes, and in particular, the gap between the sufficient conditions (Theorem \ref{thm:sufficient}) and the necessary conditions (Theorem \ref{thm:necessary}).
-
-\begin{remark} \label{rmk:gap-between-sufficient-necessary}
-The sufficient condition in Theorem \ref{thm:sufficient} requires that \emph{all} signals be larger than the strong classification boundary $g(\beta)$ in order to achieve exact support recovery \eqref{eq:exact-recovery}, while Theorem \ref{thm:necessary} states that exact support recovery fails (in the sense of \eqref{eq:exact-recovery-failure}) when \emph{all} signal sizes are below the boundary --- the two conditions are \emph{not} complements of each other.
-This gap between the sufficient and necessary conditions on signal sizes, however, may be difficult to bridge.
-Indeed, in general, when signal sizes straddle the boundary $g(\beta)$, either outcome is possible, as we demonstrate in Example \ref{exmp:signals-straddling-the-boundary} below.
-\end{remark}
-
-\begin{example}[Signals straddling the boundary]
-\label{exmp:signals-straddling-the-boundary}
-Let the signal $\mu$ have $|S_p| = \lfloor p^{(1-\beta)} \rfloor$ non-zero entries, composed of two disjoint sets $S_p = S_p^{(1)}\cup S_p^{(2)}$.
-Let also the magnitude of the signals be equal within the two sets, i.e., $\mu(i)=\sqrt{2r^{(k)}\log{p}}$ if $i\in S_p^{(k)}$ for some constants $r^{(k)} > 0$ for $k=1,2$.
-For simplicity, assume that the errors are iid standard Gaussians.
-
-Consider two scenarios
-\begin{enumerate}
-    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1+\delta)$ with $|S_p^{(1)}|=|S_p|-1$, $|S_p^{(2)}|=1$, 
-    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1-\delta)g(\beta)$ with $|S_p^{(1)}|=\lfloor|S_p|/2\rfloor$, $|S_p^{(2)}|=|S_p| - |S_p^{(1)}|$.
-\end{enumerate}
-for some constants $0<\delta<1-\beta<1$. 
-In both cases, signals in $S_p^{(1)}$ (respectively, $S_p^{(2)}$) are above (respectively, below) the strong classification boundary \eqref{eq:strong-classification-boundary}.
-However, in the first scenario, we have $\mathbb{P}[\widehat{S}^{\text{Bonf}}_p=S_p]\to 1$ where $\widehat{S}^{\text{Bonf}}_p$ is the Bonferroni's procedure described in Theorem \ref{thm:sufficient}, 
-while in the second scenario, we have $\mathbb{P}[\widehat{S}_p=S_p]\to 0$ for \emph{all} thresholding procedures $\widehat{S}_p$.
-\end{example}
-The claims in Example \ref{exmp:signals-straddling-the-boundary} are verified in Section \ref{suppsec:proofs}.
-
-Our second comment is on the interplay between thresholding procedures and the dependence class characterized by URS.
-\begin{remark} \label{rmk:dependence-assumptions}
-Paraphrasing Theorems \ref{thm:sufficient} and \ref{thm:necessary}: 
-if we consider only thresholding procedures, then for a very large class of dependence structures, we cannot improve upon the Bonferroni procedure $\widehat{S}_p^{\text{Bonf}}$. 
-Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we have
-\begin{equation}
-    \lim_{p\to\infty} \P[\widehat{S}_p^{\text{Bonf}}\neq S_p]
-    = \begin{cases}
-    \limsup_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 0, & \text{if}\quad \underline{r} > g(\beta),\\
-    \liminf_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 1, & \text{if}\quad \overline{r} < g(\beta)\\
-    \end{cases}
-\end{equation}
-where $\cal T$ is the set of all thresholding procedures \eqref{eq:thresholding-procedure}.
-
-Theorem \ref{thm:necessary} also yields an answer the question raised in \citet{butucea2018variable}.
-In particular, the authors of \citep{butucea2018variable} commented that independent error is the  `least favorable model' in the problem of support recovery, and 
-conjectured that the support recovery problem may be easier to solve under dependence, similar to how the problem of signal detection is easier under dependent 
-errors (see \cite{hall2010innovated}). 
-Surprisingly, our results here state that asymptotically, \emph{all} error dependence structures in the large URS class are equally difficult for \emph{thresholding procedures}.
-Therefore, the phase transition behavior is universal in the class of dependence structures characterized by URS.
-
-To facilitate comparison with results in existing literature, we will formulate explicit minimax statements in Section \ref{sec:optimality}.
-\end{remark}
-
-We must emphasize that the restriction to the URS dependence class is \emph{not} an assumption of convenience. 
-The condition on dependence characterized by uniform relative stability is, in fact, the weakest of its kind in the literature.
-We will characterize the class URS dependence class in Chapter \ref{chap:URS} below.
-
-% \begin{remark}   {\color{blue} Here is an idea -- one could estimate the threshold robustly.  For example,
-% suppose that we know that the support set is of size $\le p^{1-\beta_0}$, for some fixed $\beta_0\in(0,1)$.  Assume also (for simplicity) that the
-% signals can only be positive.  Then, let
-% $$
-% T_p := x_{([p^{1-\beta_0}])},
-% $$
-% be the top $[p^{1-\beta_0}]$-th order statistic of the data.  Then, I believe, but I have not proved it that in the absence of signal
-% $T_p/u_p \to 1$ in probability.  This should be easy to verify in the iid case and it is an {\bf open problem} in the general URS case. 
-% Therefore, one can take the threshold to be:
-% $$ t_p(\delta)  := T_p\times (1+\delta),$$ 
-% where $\delta>0$ is something tiny (which can also be made to vanish slowly as $p\to\infty$.
-
-% We know, from our theory that if a threshold estimator is to be able to recover the support, then all the signal entries should be 
-% above $T_p$ (since we assume that the sparsity $\beta<\beta_0$).  Thus, it is plausible that in this case, the value of
-% $T_p$ is unaffected by the signal and $T_p\sim u_p$ in probability.  Now, the factor $1+\delta$ makes the threshold $t_p$ just large enough for it to
-% miss any false positives, and if $\delta>0$ is small, to capture all the signal, as $p\to\infty$.
-
-% This idea can be easily checked with simulations to see how well it does in practice.  It is almost completely non-parametric!!! 
-% What do you think?   If it ``works", should we include it? 
-% }
-% \end{remark}
-
-We conclude with the proof of Theorem \ref{thm:necessary}.
-
-\begin{proof} [Proof of Theorem \ref{thm:necessary}]
+\begin{proof} %[Proof of Theorem \ref{thm:necessary}]
 To avoid cumbersome double subscript notations, we will sometimes suppress dependence on $p$ of the set sequences $\widehat{S}_p$ and $S_p$ in the proof.
@@
 
+% We comment on some consequences of the theorem, before presenting its proof.
+We end this section with several remarks on the scope and consequences
+of our results. Our first comment is on the signal sizes, and in particular, the gap 
+between the sufficient conditions (Theorem \ref{thm:sufficient}) and the necessary 
+conditions (Theorem \ref{thm:necessary}).
+
+\begin{remark}[Minding the gap] \label{rmk:gap-between-sufficient-necessary}
+The sufficient condition in Theorem \ref{thm:sufficient} requires that \emph{all} signals be larger than the strong classification boundary $g(\beta)$ in order to achieve exact support recovery \eqref{eq:exact-recovery}, while Theorem \ref{thm:necessary} states that exact support recovery fails (in the sense of \eqref{eq:exact-recovery-failure}) when \emph{all} signal sizes are below the boundary --- the two conditions are \emph{not} complements of each other.
+This gap between the sufficient and necessary conditions on signal sizes, however, may be difficult to bridge.
+Indeed, in general, when signal sizes straddle the boundary $g(\beta)$, either outcome is possible, as we demonstrate in 
+Example \ref{exmp:signals-straddling-the-boundary} below.
+\end{remark}
+
+\begin{example}[Signals straddling the boundary]
+\label{exmp:signals-straddling-the-boundary}
+Let the signal $\mu$ have $|S_p| = \lfloor p^{(1-\beta)} \rfloor$ non-zero entries, composed of two disjoint sets $S_p = S_p^{(1)}\cup S_p^{(2)}$.
+Let also the magnitude of the signals be equal within the two sets, i.e., $\mu(i)=\sqrt{2r^{(k)}\log{p}}$ if $i\in S_p^{(k)}$ for some constants $r^{(k)} > 0$ for $k=1,2$.
+For simplicity, assume that the errors are iid standard Gaussians.
+
+Consider two scenarios
+\begin{enumerate}
+    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1+\delta)$ with $|S_p^{(1)}|=|S_p|-1$, $|S_p^{(2)}|=1$, 
+    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1-\delta)g(\beta)$ with $|S_p^{(1)}|=\lfloor|S_p|/2\rfloor$, $|S_p^{(2)}|=|S_p| - |S_p^{(1)}|$.
+\end{enumerate}
+for some constants $0<\delta<1-\beta<1$. 
+In both cases, signals in $S_p^{(1)}$ (respectively, $S_p^{(2)}$) are above (respectively, below) the strong classification boundary \eqref{eq:strong-classification-boundary}.
+However, in the first scenario, we have $\mathbb{P}[\widehat{S}^{\text{Bonf}}_p=S_p]\to 1$ where $\widehat{S}^{\text{Bonf}}_p$ is the Bonferroni's procedure described in Theorem \ref{thm:sufficient}, 
+while in the second scenario, we have $\mathbb{P}[\widehat{S}_p=S_p]\to 0$ for \emph{all} thresholding procedures $\widehat{S}_p$.
+
+\begin{proof}[Example \ref{exmp:signals-straddling-the-boundary}]
+In the first scenario, signal sizes in $S^{(1)}_p$ are by definition above the strong classification boundary \eqref{eq:strong-classification-boundary}.
+The signal in $S^{(2)}_p$ has size parameter $1+\delta<2-\beta<(1+\sqrt{1-\beta})^2$, and therefore falls below the boundary.
+
+It remains to show that $\mathbb{P}[\widehat{S}^{\text{Bonf}}_p=S_p]\to 1$.
+To do so, we define two new arrays 
+$$
+{\cal Y}^{(k)} = \{y^{(k)}_p(j),\;j=1,2,\ldots,p\},\quad k\in\{1,2\}_p,
+$$
+where $y^{(k)}_p(j)=x_p(j)$ if $j\not\in S^{(k)}_p$, and $y^{(k)}_p(j)=\widetilde{\epsilon}_p(j)$ if $j\in S^{(k)}_p$, using an independent error array $\{\widetilde{\epsilon}_p(j),\;j=1,\ldots,p\}$ with iid standard Gaussian elements.
+That is, we replace the elements in $S^{(1)}_p$ and $S^{(2)}_p$ with iid standard Gaussian noise.
+Notice both arrays ${\cal Y}^{(1)}$ and ${\cal Y}^{(2)}$ satisfy the conditions in Theorem \ref{thm:sufficient} (with sparsity parameter equal to $\beta$ and $1$, respectively). 
+Hence, we have
+$$
+\P[\widehat{S}^{\text{Bonf}}_p\subseteq S_p] 
+= \P\left[\max_{j\in S^c}x(j) \le t_p\right]
+\le \P\left[\max_{j\in S^c}y^{(1)}(j) \le t_p\right] \to 0,
+$$
+and 
+\begin{align*}
+    \P[\widehat{S}^{\text{Bonf}}_p\supseteq S_p]
+    &= \P\left[\min_{j\in S}x(j) > t_p\right] 
+    \ge 1 - \P\left[\min_{j\in S^{(1)}}x(j) \le t_p\right] - \P\left[\min_{j\in S^{(2)}}x(j) \le t_p\right] \\
+    &\ge 1 - \P\left[\min_{j\in S^{(1)}}y^{(2)}_p(j) \le t_p\right] - \P\left[\min_{j\in S^{(2)}}y^{(1)}_p(j) \le t_p\right] 
+    \to 1,
+\end{align*}
+where $t_p$ is the threshold in Bonferroni's procedure. The conclusion follows.
+% only need to show $\mathbb{P}[S^{(2)}_p\subseteq\widehat{S}^{\text{Bonf}}_p]\to 1$.
+
+In the second scenario, the signal sizes in $S^{(2)}$ by definition fall below the strong classification boundary \eqref{eq:strong-classification-boundary}.
+To see that no thresholding procedure succeeds, we adapt the proof of Theorem \ref{thm:necessary}.
+In particular, we obtain
+$$
+    \P[\widehat{S}_p = S_p] 
+    \le \P\left[\max_{j\in S^c}x(j) \le t_p < \min_{j\in S}x(j)\right]
+    \le \P\left[\max_{j\in S^c}x(j) < \min_{j\in S^{(2)}}x(j)\right].
+$$
+By the assumption that signals in $S^{(2)}$ have size parameter $(1-\delta)g(\beta)$, we have
+\begin{equation}
+\P\left[\max_{j\in S^c}x(j) < \min_{j\in S^{(2)}}x(j)\right]
+= \P\left[ \frac{M_{S^{c}}}{u_p} < \frac{\sqrt{2(1-\delta)g(\beta)\log{p}} - m_{S^{(2)}}}{u_p}\right], 
+\end{equation}
+where $M_{S^{c}} = \max_{j\in S^{c}}\epsilon(j)$ and $m_{S^{(2)}} = \max_{j\in S^{(2)}}\left(-\epsilon(j)\right)$.
+The ratio on the left-hand-side of the inequality converges to 1 as in \eqref{eq:classification-possible-dependent-proof-3} in the main text, whereas the term on the right-hand-side
+\begin{align*}
+    \frac{\sqrt{2(1-\delta)g(\beta)\log{p}} - m_{S^{(2)}}}{u_p} 
+    &= \sqrt{(1-\delta)g(\beta)} - \frac{m_{S^{(2)}}}{u_{|S^{(2)}|}} \frac{u_{|S^{(2)}|}}{u_p} \\
+    &\xrightarrow{\P} \sqrt{(1-\delta)} + \sqrt{1-\beta}(\sqrt{(1-\delta)} - 1) < 1.
+\end{align*}
+where we used the URS of the error arrays, and that 
+$$
+u_{|S^{(2)}|} \sim \sqrt{2\log{(p^{1-\beta}/2)}} 
+= \sqrt{2(({1-\beta})\log{p}-\log2)} \sim \sqrt{2({1-\beta})\log{p}}.
+$$
+to conclude the convergence in probability.
+\end{proof}
+\end{example}
+
+Our second comment is on the interplay between thresholding procedures and the dependence class characterized by URS.
+\begin{remark} \label{rmk:dependence-assumptions}
+Paraphrasing Theorems \ref{thm:sufficient} and \ref{thm:necessary}: 
+if we consider only thresholding procedures, then for a very large class of dependence structures, we cannot improve upon the Bonferroni procedure $\widehat{S}_p^{\text{Bonf}}$. 
+Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we have
+\begin{equation}
+    \lim_{p\to\infty} \P[\widehat{S}_p^{\text{Bonf}}\neq S_p]
+    = \begin{cases}
+    \limsup_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 0, & \text{if}\quad \underline{r} > g(\beta),\\
+    \liminf_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 1, & \text{if}\quad \overline{r} < g(\beta)\\
+    \end{cases}
+\end{equation}
+where $\cal T$ is the set of all thresholding procedures \eqref{eq:thresholding-procedure}.
+
+Theorem \ref{thm:necessary} answers a question raised in \citet{butucea2018variable}.
+In particular, the authors of \citep{butucea2018variable} commented that independent error is the  `least favorable model' in the problem of support recovery, and 
+conjectured that the support recovery problem may be easier to solve under dependence, similar to how the problem of signal detection is easier under dependent 
+errors \citep{hall2010innovated}. 
+Surprisingly, our results here state that asymptotically, \emph{all} error dependence structures in the large URS class are equally difficult for \emph{thresholding procedures}.
+Therefore, the phase transition behavior is universal in the class of dependence structures characterized by URS.
+For more details, see also Section \ref{sec:minimax}.
+\end{remark}
+
+\begin{remark} We emphasize that the restriction to the URS dependence class in Theorem \ref{thm:necessary} is 
+\emph{not} an assumption of convenience. 
+The dependence condition characterized by uniform relative stability is, in fact, the weakest of its kind in the literature.
+We will characterize the class URS dependence class in Chapter \ref{chap:URS} below.
+\end{remark}
+
+% \begin{remark}   {\color{blue} Here is an idea -- one could estimate the threshold robustly.  For example,
+% suppose that we know that the support set is of size $\le p^{1-\beta_0}$, for some fixed $\beta_0\in(0,1)$.  Assume also (for simplicity) that the
+% signals can only be positive.  Then, let
+% $$
+% T_p := x_{([p^{1-\beta_0}])},
+% $$
+% be the top $[p^{1-\beta_0}]$-th order statistic of the data.  Then, I believe, but I have not proved it that in the absence of signal
+% $T_p/u_p \to 1$ in probability.  This should be easy to verify in the iid case and it is an {\bf open problem} in the general URS case. 
+% Therefore, one can take the threshold to be:
+% $$ t_p(\delta)  := T_p\times (1+\delta),$$ 
+% where $\delta>0$ is something tiny (which can also be made to vanish slowly as $p\to\infty$.
+
+% We know, from our theory that if a threshold estimator is to be able to recover the support, then all the signal entries should be 
+% above $T_p$ (since we assume that the sparsity $\beta<\beta_0$).  Thus, it is plausible that in this case, the value of
+% $T_p$ is unaffected by the signal and $T_p\sim u_p$ in probability.  Now, the factor $1+\delta$ makes the threshold $t_p$ just large enough for it to
+% miss any false positives, and if $\delta>0$ is small, to capture all the signal, as $p\to\infty$.
+
+% This idea can be easily checked with simulations to see how well it does in practice.  It is almost completely non-parametric!!! 
+% What do you think?   If it ``works", should we include it? 
+% }
+% \end{remark}
+
 \section{Dense signals}

### 2021-01-16 4.exact_support_recovery/4.proofs-examples.tex
update
Cleaned up the new Chapter 5.
update
cleaned up Ch 4.

Both (new) Ch 4 and 5 are ready to re-read.

@@
 \label{subsec:proofs-examples}
-
-\begin{proof}[Proof of claims in Example \ref{exmp:FWER-controlling_procedures}]
-By the Mill's ratio for the standard Gaussian distribution,
-$$
-\frac{t_p \P\left[Z>t_p\right]}{\phi(t_p)} \to 1,\quad \text{as}\quad t_p\to\infty,
-$$
-where $Z\sim \text{N}(0,1)$. 
-Using the expression for $t_p = \sqrt{2\log{p}}$, we have
-$$
-p \;\P\left[Z>t_p\right] \sim \sqrt{2\pi}^{-1}\left(2\log{p}\right)^{-1/2} \to 0,
-$$
-as desired. The rest of the claims follow from Corollary \ref{cor:FWER-controlling_procedures}.
-\end{proof}
-
-\begin{proof}[Proof of claims in Example \ref{exmp:signals-straddling-the-boundary}]
-In the first scenario, signal sizes in $S^{(1)}_p$ are by definition above the strong classification boundary \eqref{eq:strong-classification-boundary}.
-The signal in $S^{(2)}_p$ has size parameter $1+\delta<2-\beta<(1+\sqrt{1-\beta})^2$, and therefore falls below the boundary.
-
-It remains to show that $\mathbb{P}[\widehat{S}^{\text{Bonf}}_p=S_p]\to 1$.
-To do so, we define two new arrays 
-$$
-{\cal Y}^{(k)} = \{y^{(k)}_p(j),\;j=1,2,\ldots,p\},\quad k\in\{1,2\}_p,
-$$
-where $y^{(k)}_p(j)=x_p(j)$ if $j\not\in S^{(k)}_p$, and $y^{(k)}_p(j)=\widetilde{\epsilon}_p(j)$ if $j\in S^{(k)}_p$, using an independent error array $\{\widetilde{\epsilon}_p(j),\;j=1,\ldots,p\}$ with iid standard Gaussian elements.
-That is, we replace the elements in $S^{(1)}_p$ and $S^{(2)}_p$ with iid standard Gaussian noise.
-Notice both arrays ${\cal Y}^{(1)}$ and ${\cal Y}^{(2)}$ satisfy the conditions in Theorem \ref{thm:sufficient} (with sparsity parameter equal to $\beta$ and $1$, respectively). 
-Hence, we have
-$$
-\P[\widehat{S}^{\text{Bonf}}_p\subseteq S_p] 
-= \P\left[\max_{j\in S^c}x(j) \le t_p\right]
-\le \P\left[\max_{j\in S^c}y^{(1)}(j) \le t_p\right] \to 0,
-$$
-and 
-\begin{align*}
-    \P[\widehat{S}^{\text{Bonf}}_p\supseteq S_p]
-    = \P\left[\min_{j\in S}x(j) > t_p\right] 
-    &\ge 1 - \P\left[\min_{j\in S^{(1)}}x(j) \le t_p\right] - \P\left[\min_{j\in S^{(2)}}x(j) \le t_p\right] \\
-    &\ge 1 - \P\left[\min_{j\in S^{(1)}}y^{(2)}_p(j) \le t_p\right] - \P\left[\min_{j\in S^{(2)}}y^{(1)}_p(j) \le t_p\right] 
-    \to 1,
-\end{align*}
-where $t_p$ is the threshold in Bonferroni's procedure. The conclusion follows.
-% only need to show $\mathbb{P}[S^{(2)}_p\subseteq\widehat{S}^{\text{Bonf}}_p]\to 1$.
-
-In the second scenario, the signal sizes in $S^{(2)}$ by definition falls below the strong classification boundary \eqref{eq:strong-classification-boundary}.
-To see that no thresholding procedure succeeds, we adapt the proof of Theorem \ref{thm:necessary}.
-In particular, we obtain
-$$
-    \P[\widehat{S}_p = S_p] 
-    \le \P\left[\max_{j\in S^c}x(j) \le t_p < \min_{j\in S}x(j)\right]
-    \le \P\left[\max_{j\in S^c}x(j) < \min_{j\in S^{(2)}}x(j)\right].
-$$
-By the assumption that signals in $S^{(2)}$ have size parameter $(1-\delta)g(\beta)$, we have
-\begin{equation}
-\P\left[\max_{j\in S^c}x(j) < \min_{j\in S^{(2)}}x(j)\right]
-= \P\left[ \frac{M_{S^{c}}}{u_p} < \frac{\sqrt{2(1-\delta)g(\beta)\log{p}} - m_{S^{(2)}}}{u_p}\right], 
-\end{equation}
-where $M_{S^{c}} = \max_{j\in S^{c}}\epsilon(j)$ and $m_{S^{(2)}} = \max_{j\in S^{(2)}}\left(-\epsilon(j)\right)$.
-The ratio on the left-hand-side of the inequality converges to 1 as in \eqref{eq:classification-possible-dependent-proof-3} in the main text, whereas the term on the right-hand-side
-\begin{align*}
-    \frac{\sqrt{2(1-\delta)g(\beta)\log{p}} - m_{S^{(2)}}}{u_p} 
-    &= \sqrt{(1-\delta)g(\beta)} - \frac{m_{S^{(2)}}}{u_{|S^{(2)}|}} \frac{u_{|S^{(2)}|}}{u_p} \\
-    &\xrightarrow{\P} \sqrt{(1-\delta)} + \sqrt{1-\beta}(\sqrt{(1-\delta)} - 1) < 1.
-\end{align*}
-where we used the URS of the error arrays, and that 
-$$
-u_{|S^{(2)}|} \sim \sqrt{2\log{(p^{1-\beta}/2)}} 
-= \sqrt{2(({1-\beta})\log{p}-\log2)} \sim \sqrt{2({1-\beta})\log{p}}.
-$$
-to conclude the convergence in probability.
-\end{proof}

### 2021-01-16 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
update
cleaned up Ch 4.

Both (new) Ch 4 and 5 are ready to re-read.

@@
-Finally, we offer some insights into the support recovery problem in the case when errors have heavier-than-exponential tails in Section \ref{subsec:optimal-procedure-super-exponential}.
+In this chapter, we investigate the universality of the phase-transition results on exact support recovery established in
+Chapter \ref{chap:exact-support-recovery}.  Specifically, we would like to know to what extent the signal classification 
+boundary valid for thresholding estimators applies to the best possible support estimators.  The answer to this question 
+will complete the characterization of the fundamental limits in exact support recovery.
+
+To this end, we begin by characterizing the finite-sample Bayes optimality of the thresholding procedures (Section
+\ref{subsec:optimal-procedure-sub-exponential}). As we will see, the so-called oracle thresholding estimators are in 
+fact finite-sample optimal for certain classes of models.  These optimality results allow us to establish 
+powerful minimax formulations of the exact support recovery phase-transition phenomenon showing its universality for all estimators (Theorem \ref{thm:necessary-strengthened}).
+
+Perhaps surprisingly, however, thresholding estimators can be sub-optimal.  This is so for example 
+in the additive noise model with heavier than exponential error densities (Example 
+\ref{exmp:suboptimal-data-thresholding}).   In this case, the likelihood ratio
+thresholding rather than data thresholding can lead to optimal support estimators
+(Section \ref{subsec:optimal-procedure-super-exponential}).  In such cases, the universality 
+of the exact support recovery boundary remains an open question.
 
@@
 
-In studying support recovery problems (e.g., \citet{arias2017distribution}), restrictions to the thresholding procedures are sometimes justified by arguing that such procedures are the ``reasonable'' choice for estimating the support set.
-%  In Theorem \ref{thm:sufficient} we saw that a (FWER-controlling) thresholding procedure is indeed consistent for support recovery. 
-% It is natural to ask if it will be sufficient to restrict our attention to only such procedures.
-We show in this section that, perhaps surprisingly, for general error models, thresholding procedures are not always optimal, even when the observations are independent.
+In studying support recovery problems \citep[e.g.,][]{arias2017distribution}, restrictions to the thresholding procedures 
+are sometimes justified by arguing that such procedures are the ``reasonable'' choice for estimating the support set.
+We show in this chapter that, perhaps surprisingly, for general error models, thresholding procedures are not always 
+optimal, even when the observations are independent.
 
@@
 If, however, the sparsity $s = |S|$ of the problem is known, then a natural estimator for $S$ would be based on the set of top $s$ order statistics.
-
-\stilian{\fbox{COMMENT} Just like for the likelihood thresholding procedure, we should be more careful about the ties and how to define
-the oracle thresholding procedure so that $\widehat{S}^*$ has exactly $s$ elements.  I propose the following change}{\, }
+Such estimators will be referred to as oracle thresholding estimators and formally defined next.
 
 \stilian{ 
-
 For any collection of numbers $\{a_i,\ i=1,\cdots,s\}$, let 
@@
 
-\subsection{When is oracle thresholding Bayes optimal?} % under sub-exponential errors}
+\section{Bayes optimality of oracle thresholding} % under sub-exponential errors}
 \label{subsec:optimal-procedure-sub-exponential}
 
-An elegant answer of this question can be given in terms of the \emph{monotone likelihood ratio} (MLR) property.
+In this section, we study the Bayes optimality of the oracle thresholding procedures.  
+The following \emph{monotone likelihood ratio} (MLR) property will play a key role.
 
@@
 
-The following result provides a general criterion for the finite-sample optimality of the oracle thresholding 
+The next result provides a general criterion for the finite-sample Bayes optimality of the oracle thresholding 
 procedure $\widehat{S}^*$.
@@
 
-%(This also explains the $\gamma\ge 1$ condition in Theorem 1 of Arias-Castro and Chen)
-
-\stilian{COMMENT}{Consider moving the following discussion \& theorem to the section on Minimax below...}
-
-Consider the asymptotic Bayes risk as defined in \eqref{eq:Bayes-risk}. The statement for the 
-necessary condition of support recovery, with the help of Proposition \ref{prop:log-concave}, can be 
-strengthened to include all procedures (in the Bayesian context), regardless of whether they are thresholding.
-
-\begin{theorem} \label{thm:necessary-strengthened}
-Consider the additive model \eqref{eq:model-additive} where the $\epsilon_p(i)$'s are independent and identically distributed with log-concave densities in the AGG class. 
-Let the signals be as prescribed in Proposition \ref{prop:log-concave}.
-If the signal sizes fall below the strong classification boundary \eqref{eq:strong-classification-boundary}, i.e. $\overline{r}<g(\beta)$,
-then we have
-\begin{equation} \label{eq:classification-impossible-Bayes}
-    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi \P[\widehat{S}_p\neq S_p] = 1,
-\end{equation}
-where the infimum on $\widehat{S}_p$ is taken over all procedures.
-\end{theorem}
-
-\begin{proof}%[Proof of Theorem \ref{thm:necessary-strengthened}]
-When the errors are independent with log-concave density, the oracle thresholding procedure $\widehat{S}^*_p$, by Proposition \ref{prop:log-concave}, minimizes the Bayes risk \eqref{eq:Bayes-risk} among \emph{all} procedures.
-That is,
-$$
-\liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi\P[\widehat{S}_p\neq S_p]
-\ge \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p].
-$$
-Since $\widehat{S}^*_p$ belongs to the class of all thresholding procedures, we have
-\begin{align*}
-    \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p] 
-    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \E_\pi\P[\widehat{S}_p\neq S_p] \\
-    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \inf_{S_p} \P[\widehat{S}_p\neq S_p] = 1,
-\end{align*}
-when $\overline{r}<g(\beta)$, where the last line follows from Theorem \ref{thm:necessary}.
-\end{proof}
-
-\subsection{Bayes optimality of likelihood ratio thresholding}
+\section{Bayes optimality of likelihood ratio thresholding}
 \label{subsec:optimal-procedure-super-exponential}
@@
 
-\subsection{Sub-optimality of data thresholding procedures}\label{sec:sup-optimality-of-thresholding}
+\section{Sub-optimality of data thresholding procedures}\label{sec:sup-optimality-of-thresholding}
 
@@
 
-\section{Minimax optimality in exact support recovery}
+\section{Minimax optimality in exact support recovery} \label{sec:minimax}
 
 We establish in this section minimax versions of our results from Chapter \ref{chap:exact-support-recovery}.
-Specifically, if we restrict ourselves to \emph{the class of thresholding procedures} $\cal T$ (defined in \eqref{eq:thresholding-procedure}), then Bonferroni's procedure is minimax optimal, for \emph{any} fixed dependence structures in the URS class.
+Specifically, if we restrict ourselves to \emph{the class of thresholding procedures} $\cal T$ (defined in \eqref{eq:thresholding-procedure}), then Bonferroni's procedure is minimax optimal, for \emph{any} fixed dependence structure in the URS class.
 This is formalized in Corollary \ref{cor:point-wise-minimax} below.% in Section \ref{subsec:point-wise-minimax}.
@@
 \label{subsec:minimax-over-dependence}
+
+%(This also explains the $\gamma\ge 1$ condition in Theorem 1 of Arias-Castro and Chen)
+
+Consider the asymptotic Bayes risk as defined in \eqref{eq:Bayes-risk}. The statement for the 
+necessary condition of support recovery in Theorem \ref{thm:necessary}, with the help of Proposition 
+\ref{prop:log-concave}, can be strengthened to include all procedures (in the Bayesian context), regardless 
+of whether they are thresholding or not.
+
+\begin{theorem} \label{thm:necessary-strengthened}
+Consider the additive model \eqref{eq:model-additive} where the $\epsilon_p(i)$'s are independent and identically distributed with log-concave densities in the AGG class. 
+Let the signals be as prescribed in Proposition \ref{prop:log-concave}.
+If the signal sizes fall below the strong classification boundary \eqref{eq:strong-classification-boundary}, 
+i.e. $\overline{r}<g(\beta)$, then we have
+\begin{equation} \label{eq:classification-impossible-Bayes}
+    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi \P[\widehat{S}_p\neq S_p] = 1,
+\end{equation}
+where the infimum on $\widehat{S}_p$ is taken over all procedures.
+\end{theorem}
+
+\begin{proof}%[Proof of Theorem \ref{thm:necessary-strengthened}]
+When the errors are independent with log-concave density, the oracle thresholding procedure $\widehat{S}^*_p$, by Proposition \ref{prop:log-concave}, minimizes the Bayes risk \eqref{eq:Bayes-risk} among \emph{all} procedures.
+That is,
+$$
+\liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi\P[\widehat{S}_p\neq S_p]
+\ge \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p].
+$$
+Since $\widehat{S}^*_p$ belongs to the class of all thresholding procedures, we have
+\begin{align*}
+    \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p] 
+    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \E_\pi\P[\widehat{S}_p\neq S_p] \\
+    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \inf_{S_p} \P[\widehat{S}_p\neq S_p] = 1,
+\end{align*}
+when $\overline{r}<g(\beta)$, where the last line follows from Theorem \ref{thm:necessary}.
+\end{proof}
 
@@
 
-  \stilian{Here we briefly discuss the optimality and sub-optimality of the 
- thresholding procedures.}{Needs work}
+\stilian{NEEDS}{WORK}
 
-%\begin{remark} \label{rmk:tail-assumptions}
+Consider the model \eqref{eq:model-additive} with independent errors. Theorem \ref{thm:necessary-strengthened} 
+and Corollary \ref{cor:minimax-over-dependence} provide a nearly complete picture of the difficulty in the exact support 
+recovery problem, in the regime when the thresholding estimators are optimal. Specifically, in such cases the signal classification boundary is universal.
 
-Consider the model \eqref{eq:model-additive} with independent errors, Proposition \ref{prop:likelihood-ratio-thresholding}, and indeed, Example \ref{exmp:suboptimal-data-thresholding} demonstrate that thresholding procedures are in fact \emph{sub-optimal} for $\text{AGG}(\nu)$ models with $\nu<1$.
+ Proposition \ref{prop:likelihood-ratio-thresholding}, and indeed, Example \ref{exmp:suboptimal-data-thresholding} demonstrate that thresholding procedures are in fact \emph{sub-optimal} for $\text{AGG}(\nu)$ models with $\nu<1$.
 Therefore, the optimality of thresholding procedures (specifically, Bonferroni's procedure) only applies to $\text{AGG}(\nu)$ models with $\nu\ge1$. 
@@
     \medskip
-    \begin{tabular}{p{45mm}p{40mm}p{40mm}} \toprule
+    \begin{tabular}{p{40mm}p{37mm}p{37mm}} \toprule
         Thresholding procedure & Bayes optimality &  Phase transition \\ 

### 2021-01-16 4.exact_support_recovery/exact_support_recovery.tex
update
cleaned up Ch 4.

Both (new) Ch 4 and 5 are ready to re-read.
small typo

@@
-We focus on exact support recovery problems in this chapter, and generalize the results we obtained in Chapter \ref{chap:phase-transitions} to additive error models with much relaxed distributional and dependence assumptions.
-Sufficient conditions for exact support recovery \eqref{eq:exact-recovery} are given in 
-Section \ref{subsec:sufficient}.  A very general class of dependence structures characterized by the uniform relative stability concept will 
-be introduced in Section \ref{subsec:URS}, to prepare us for the necessary condition in Section \ref{subsec:necessary}.
+We focus on exact support recovery problems in this chapter, and generalize the results we obtained in 
+Chapter \ref{chap:phase-transitions} to additive error models with much relaxed distributional and dependence assumptions.  
+Here, we limit ourselves to the general class of thresholding estimators but allow for nearly arbitrary error dependence structure.  Questions on
+optimality and extensions to other classes of estimators are pursued in Chapter \ref{chap:optimality}.
+
+Sufficient conditions for exact support recovery \eqref{eq:exact-recovery} are given in Section \ref{subsec:sufficient}.  A very general class of 
+dependence structures characterized by the uniform relative stability concept will be introduced in Section \ref{subsec:URS}, to prepare us 
+for the necessary condition in Section \ref{subsec:necessary}.
 Section \ref{subsec:dense-signals} discusses the dense signal regime, and Section \ref{suppsec:numerical} illustrates the phase transition 
@@
 \input{4.exact_support_recovery/4.phase_transition_results.tex}
-\input{4.exact_support_recovery/4.pointwise.minimax.tex}
 
@@
 %\input{4.exact_support_recovery/4.heavy-tailed.tex}
-
-\section{Additional proofs}
-\label{suppsec:proofs}
-\input{4.exact_support_recovery/4.proofs-examples.tex}
-\input{4.exact_support_recovery/4.proofs-convexity.tex}

### 2021-01-28 3.phase_transitions/3.global-tests.tex
updated Ch 4
I updated up to and including Ch 4.2.2.

Hope to finish tomorrow.
Chaoter 3
Fixed some mathematical typos and incorporated the proof of Theorem 3.1 in the text.

Also "clarified" the statement of Theorem 3.1.  Please check.

@@
 \begin{theorem} \label{thm:detection-optimality}
-Consider the signal detection problem in the triangular array of Gaussian error models \eqref{eq:model-additive-Chapter3} where the sparsity is parametrized as in \eqref{eq:signal-sparsity-additive}.
-\begin{itemize}
-    \item For signals whose sizes are parametrized as in \eqref{eq:signal-size-additive}, the detection problem can be asymptotically solved in the sense of \eqref{eq:support-recovery-success} with $L_2$, $L_1$, or $S$ statistic when $\beta\le 1/2$; on the other hand, these statistics are asymptotically powerless in the sense of \eqref{eq:support-recovery-failure} when $\beta>1/2$.
-    \item For small and dense signals whose signal sizes are parametrized as in \eqref{eq:signal-size-small}, the detection problem can be asymptotically solved in the sense of \eqref{eq:support-recovery-success} with $L_2$ or $L_1$ statistic when $\underline{r}>\beta/2-{1}/{4}$; on the other hand, these statistics are asymptotically powerless in the sense of \eqref{eq:support-recovery-failure} when $\overline{r}<\beta/2-{1}/{4}$.
-    Further, tests based on the $S$ statistic can succeed asymptotically in the sense of \eqref{eq:support-recovery-success} when $\underline{r}>\beta-1/2$, hence attaining the boundary of detectability in \eqref{eq:detection-boundary-small-signals}.
-\end{itemize}
+Consider the signal detection problem in the triangular array of Gaussian error models \eqref{eq:model-additive-Chapter3} where the sparsity is parametrized as in \eqref{eq:signal-sparsity-additive}.\\
+
+{\em (i)}  For $\beta \in (1/2,1)$ and growing signals sizes as in \eqref{eq:signal-size-additive}, the statistics
+    $L_1, L_2$ and $T$ are asymptotically powerless in the sense of \eqref{eq:support-recovery-failure}.\\
+
+{\em (ii)} For $\beta \in (0,1/2]$ and growing signals sizes as in \eqref{eq:signal-size-additive}, the statistics
+    $L_1, L_2$ and $T$ solve the detection problem in the sense of \eqref{eq:support-recovery-success}.\\
+
+{\em (iii)} For dense and faint signals, i.e., $\beta \in (0,1/2]$ under the parameterization \eqref{eq:signal-size-small}, the sum statistic $T$
+    attains the optimal detectability boundary in \eqref{eq:detection-boundary-small-signals}.  That is, tests based on the sum statistic $T$ can 
+    succeed asymptotically in the sense of \eqref{eq:support-recovery-success} when $\underline{r}>\beta-1/2$.\\
+
+ {\em (iv)} In the dense and faint signal setting of {\em (iii)}, the $L_1$ and $L_2$ statistics are both 
+ sub-optimal. More precisely, they succeed in the sense of  \eqref{eq:support-recovery-success},  for $\underline{r}>\beta/2-{1}/{4}$, but fail in the 
+ sense of \eqref{eq:support-recovery-failure} when $\overline{r}<\beta/2-{1}/{4}$.
 \end{theorem}
+%Theorem \ref{thm:detection-optimality} is proved in Section \ref{sec:supplement}.
 
-Theorem \ref{thm:detection-optimality} is proved in Section \ref{sec:supplement}.
-We visualize the results in Theorem in Figure \ref{fig:phase-diagram-signal-detection}.
-It is worth noting that the $\beta$-$r$ parameter regions where $L_1$ and $L_2$ statistics are asymptotically powerful coincide, and these statistics are theoretically suboptimal for both sparse regimes ($\beta>1/2$) and relatively dense regimes ($\beta\le 1/2$).
+\begin{proof} The claims in parts {\rm (i)} and {\rm (ii)} about the $L_1$, $L_2$, and the sum statistic $T$ in the cases of diverging signal sizes 
+\eqref{eq:signal-size-additive} can be found in \cite{fan1996test} and \cite{candes2018lecture}. We prove here the statements for the cases {\rm (iii)}
+and {\rm (iv)}, where the signals are dense and small, as parametrized in \eqref{eq:signal-size-small}.
 
-Ideas have been proposed to combine statistics that are powerful for different alternatives to create adaptive tests that maintain high power for at all sparsity levels.
-Such adaptive tests can be constructed, for example, by leveraging the asymptotic independence of the sum- and supremum-type statistics \citep{hsing1995note}. 
+\stilian{For simplicity of the exposition, we will suppose that  in \eqref{eq:signal-size-small} we have 
+$\underline{r} = r = \overline{r}$, so that  $\mu(i) = p^r$.  The general case where $\underline{r}<\overline{r}$ is left as 
+an exercise.}{\fbox{How about that?}}
+
+{\em Part {\rm (iii)}:} We first show that the sum statistic $T$, or equivalently, the simple arithmetic mean attains the sparse signal 
+detection boundary.  By the normality and independence of the summands, we have
+\begin{equation}
+    \frac{1}{\sqrt{p}}\sum_{i=1}^p x(i) \sim 
+    \begin{cases}
+    \mathrm{N}(0, 1), & \text{under } H_0\\
+    \mathrm{N}(p^{(r-\beta)+1/2}, 1), & \text{under }  H_1.
+    \end{cases}
+\end{equation}
+It immediately follows that the two distributions can be distinguished perfectly if $p^{r-(\beta-1/2)}$ diverges, i.e., $r>\beta-1/2$. 
+This can be seen by simply setting the rejection region at $(p^{(r-\beta)+1/2}/2,\,+\infty)$ for the scaled statistic $\sum_{i=1}^p x(i)/\sqrt{p} $.
+According to the lower bound on the performance limit in detection problems \citep[see Theorem 8 in][]{cai2011optimal}, we have shown that $T$ attains the optimal detection boundary \eqref{eq:detection-boundary-small-signals}.
+
+{\em Part {\rm (iv)}:}  We now turn to the $L_2$-norm statistic.
+Recall a non-central chi-square random variable $\chi^2_k(\lambda)$ has mean $(k+\lambda)$ and variance $2(k+2\lambda)$.
+Since the observations have distributions $\mathrm{N}(0,1)$ under the null and $\mathrm{N}(p^r,1)$ under the alternative, we have $x^2(i)\sim \chi^2_1(0)$ for $i\not\in S$ and $x^2(i)\sim \chi^2_1(p^{2r})$ for $i\in S$.
+Therefore, the mean and variance of the (centered and scaled) $L_2$ statistics are
+\begin{equation}
+    \E\left[\frac{1}{\sqrt{p}}\sum_{i=1}^p \left(x(i)^2-1\right)\right] = 
+    \begin{cases}
+    0 & \text{under } H_0\\
+    p^{1-\beta}p^{2r}p^{-1/2} = p^{1/2-\beta+2r} & \text{under } H_1,
+    \end{cases}
+\end{equation}
+and 
+\begin{equation}\label{e:detection-variance}
+    \mathrm{Var}\left(\frac{1}{\sqrt{p}}\sum_{i=1}^p \left(x(i)^2-1\right)\right) = 
+    \begin{cases}
+    \frac{1}{p}2p = 2 & \text{under } H_0\\
+    \frac{1}{p}\left(2p+4p^{1-\beta+2r}\right) = 2(1+ 2p^{2r-\beta}) & \text{under } H_1,
+    \end{cases}
+\end{equation}
+respectively.
+By the central limit theorem, we have
+\begin{equation}
+    \frac{1}{\sqrt{2p}}\sum_{i=1}^p \left(x(i)^2-1\right) \implies \mathrm{N}(0,1),  
+\end{equation}
+under the null.    On the other hand, under the alternative, since $p^{2r-\beta}\to0$ for all $r<0$ and $\beta>0$, 
+ the variance in \eqref{e:detection-variance} converges to $2$, as $p\to\infty$ and an application of the Lyapunov version of 
+ the CLT, entails
+ \begin{equation}
+    \frac{1}{\sqrt{2p}}\left(\sum_{i=1}^p \left(x(i)^2-1\right) - p^{1/2-\beta+2r}\right) \implies \mathrm{N}(0,1).
+\end{equation}
+Hence, perfect detection with the $L_2$-norm is possible if $p^{1/2-\beta+2r}$ diverges, i.e., $r>\beta/2-1/4$.
+On the other hand, if $r<\beta/2-1/4$, the distributions of the (scaled) statistics merge under the null and the alternative.
+% \fbox{Hellinger distance is scale-invariant (show), detection is impossible}.
+
+The case of the $L_1$-norm is treated similarly.
+Let $Y=|X|$ where $X\sim|\mathrm{N}(\mu,1)|$. 
+Using the expressions for the mean and variance of $Y$ \citep[see, e.g.,][]{tsagris2014folded},
+\begin{align}
+    \mu_Y &= \E[Y] = \sqrt{\frac{2}{\pi}}e^{-\mu^2/2} + \mu(1-\Phi(-\mu)), \\
+    \sigma_Y^2 &= \mathrm{Var}(Y) = \mu^2 + 1 - \mu^2_Y,
+\end{align}
+where $\Phi$ is the CDF of a standard normal random variable,
+we have, regardless of the value of $\mu$,
+\begin{equation} \label{eq:bounded-variance-abs-Gaussian}
+    \sigma_Y^2 = \mathrm{Var}(Y) = \E(Y-\E Y)^2 \le \E(X-\E X)^2 = 1,
+\end{equation}
+where the inequality holds because absolute value is a Lipschitz function with Lipschitz constant 1.
+
+By the central limit theorem, we have,
+\begin{equation}
+    \frac{1}{\sqrt{p}}\left(\sum_{i=1}^p |x(i)| - \sqrt{\frac{2}{\pi}}\right) \implies \mathrm{N}(0, 1-2/\pi)
+\end{equation}
+under the null.
+On the other hand, when the alternative hypothesis holds, we have
+\begin{align*}
+    \E \left[ \frac{1}{\sqrt{p}} \left(\sum_{i=1}^p |x(i)| - \sqrt{\frac{2}{\pi}}\right) \right] 
+    &= \frac{p^{1-\beta}}{\sqrt{p}}\left[\left(\sqrt{\frac{2}{\pi}}e^{-\mu^2/2} + \mu\left(1-2\Phi(-\mu)\right) \right) - \sqrt{\frac{2}{\pi}} \right] \\
+    &= p^{1/2-\beta} \left[\sqrt{\frac{2}{\pi}}\left(e^{-p^{2r}/2} - 1 \right) + p^r\left(1-2\Phi(-\mu)\right) \right] \\
+    &= p^{1/2-\beta} \left[\sqrt{\frac{2}{\pi}}\left(-p^{2r}/2 - O(p^{4r})\right) + p^r\left(\sqrt{\frac{2}{\pi}}p^r + O(p^{3r})\right) \right] \\
+    &= p^{1/2-\beta} \sqrt{\frac{2}{\pi}} \left(p^{2r}/2 + O(p^{4r}) \right) \\
+    &= p^{1/2-\beta+2r} \sqrt{{1}/{2\pi}} + O(p^{1/2-\beta+4r}),
+\end{align*}
+and 
+\begin{align*}
+    \mathrm{Var} \left(\frac{1}{\sqrt{p}} \left(\sum_{i=1}^p |x(i)| - \sqrt{\frac{2}{\pi}}\right) \right) 
+    & = {\color{red}\frac{1}{p}}  (p-p^{1-\beta})(1-2/\pi) + {\color{red}\frac{1}{p}}   p^{1-\beta}\sigma_{Y}^2 \\
+    & \to 1-2/\pi,
+\end{align*}
+by the boundedness of $\sigma_{Y}^2$ shown in \eqref{eq:bounded-variance-abs-Gaussian}.
+Again, by the Lyapunov version of the central limit theorem, we conclude asymptotic normality of the centered and scaled $L_1$-norms under the alternative.
+In an entirely analogous argument to the $L_2$-norm case, asymptotically perfect detection can be achieved if $p^{1/2-\beta+2r}$ diverges, i.e., $r>\beta/2-1/4$.
+On the other hand, when $r<\beta/2-1/4$, the two hypotheses cannot be told apart by the $L_1$-norms since the distributions of the (scaled) statistics merge under the two hypotheses.
+\end{proof}
+
+The portmanteau of results in Theorem \ref{thm:detection-optimality} are visualized in Figure \ref{fig:phase-diagram-signal-detection}.
+It is worth noting that the $\beta$-$r$ parameter regions where $L_1$ and $L_2$ statistics are asymptotically powerful coincide, and 
+these statistics are theoretically suboptimal for both sparse regimes ($\beta>1/2$) and relatively dense regimes ($\beta\le 1/2$).
+
+Ideas have been proposed to combine statistics that are powerful for different alternatives to create adaptive tests that maintain high power 
+for at all sparsity levels. Such adaptive tests can be constructed, for example, by leveraging the asymptotic independence of the sum- and supremum-type statistics \citep{hsing1995note}. 
 Recently, \citet{xu2016adaptive} showed that for dependent observations under mixing and moment conditions, the sum-of-power-type statistics
@@
 Optimality properties of such adaptive tests and the optimal choice of the $q$-combinations, however, remain open problems.
-\cite{xu2016adaptive} suggested combine $q=1, 2, 3, \ldots, 6$, and  $q=\infty$, based empirical evidence from numerical experiments. 
-Theorem \ref{thm:detection-optimality} here implies that, at least for detecting one-sided alternatives, the $\widetilde{L}_2$ statistic (i.e., $L_2$ norm) and the $L_1$ norm are asymptotically dominated by the $\widetilde{L}_1$ statistic (or equivalently, the sum $S$).
+\cite{xu2016adaptive} suggested combining $q=1, 2, 3, \ldots, 6$, and  $q=\infty$, based empirical evidence from numerical experiments. 
+Theorem \ref{thm:detection-optimality} here implies that, at least for detecting one-sided alternatives, the $\widetilde{L}_2$ statistic (i.e., $L_2$ norm) and the $L_1$ norm are asymptotically dominated by the $\widetilde{L}_1$ statistic (or equivalently, the sum $T$).
 Therefore it is sufficient to include only the latter in the construction of the adaptive test.

### 2021-01-28 3.phase_transitions/3.proofs-phase-transitions.tex
Chaoter 3
Fixed some mathematical typos and incorporated the proof of Theorem 3.1 in the text.

Also "clarified" the statement of Theorem 3.1.  Please check.

@@
 \label{subsec:proof-additive-error-detection-boundaries}
-
-\begin{proof}[Proof of Theorem \ref{thm:detection-optimality}]
-Statements about $L_1$, $L_2$, and sum statistics $S$ in the case of diverging signal sizes \eqref{eq:signal-size-additive} can be found in \cite{fan1996test} and \cite{candes2018lecture}.
-We prove here the statements for the case where signals are dense and small, as parametrized in \eqref{eq:signal-size-small}.
-
-We first show that the sum statistic $S$, or equivalently, the simple arithmetic mean attains the sparse signal detection boundary.
-
-Consider the case of vanishing signals as prescribed in \eqref{eq:signal-size-small}, by normality of the summands, we have, 
-\begin{equation}
-    \frac{1}{\sqrt{p}}\sum_{i=1}^p x(i) \sim 
-    \begin{cases}
-    \mathrm{N}(0, 1), & \text{under } H_0\\
-    \mathrm{N}(p^{(r-\beta)+1/2}, 1), & \text{under }  H_1.
-    \end{cases}
-\end{equation}
-It immediately follows that the two distributions can be distinguished perfectly if $p^{r-(\beta-1/2)}$ diverges, i.e., $r>\beta-1/2$. 
-This can be seen by simply setting the rejection region at $(p^{(r-\beta)+1/2}/2,\,+\infty)$ for the scaled statistic $\sum_{i=1}^p x(i)/\sqrt{p} $.
-According to the lower bound on the performance limit in detection problems (see Theorem 8 in \cite{cai2011optimal}), we have shown that $S$ attains the optimal detection boundary \eqref{eq:detection-boundary-small-signals}.
-
-We now turn to the $L_2$-norms.
-Recall a non-central chi-square random variable $\chi^2_k(\lambda)$ has mean $(k+\lambda)$ and variance $2(k+2\lambda)$.
-Since the observations have distributions $\mathrm{N}(0,1)$ under the null and $\mathrm{N}(p^r,1)$ under the alternative, we have $x^2(i)\sim \chi^2_1(0)$ for $i\not\in S$ and $x^2(i)\sim \chi^2_1(p^{2r})$ for $i\in S$.
-Therefore, mean and variance of the (centered and scaled) $L_2$ statistics are
-\begin{equation}
-    \E\left[\frac{1}{\sqrt{p}}\sum_{i=1}^p \left(x(i)^2-1\right)\right] = 
-    \begin{cases}
-    0, & \text{under } H_0\\
-    p^{1-\beta}p^{2r}p^{-1/2} = p^{1/2-\beta+2r} & \text{under } H_1,
-    \end{cases}
-\end{equation}
-and 
-\begin{equation}
-    \mathrm{Var}\left(\frac{1}{\sqrt{p}}\sum_{i=1}^p \left(x(i)^2-1\right)\right) = 
-    \begin{cases}
-    \frac{1}{p}2p = 2, & \text{under } H_0\\
-    \frac{1}{p}\left(2p+2p^{1-\beta+2r}\right) = 2(1+p^{2r-\beta}) & \text{under } H_1,
-    \end{cases}
-\end{equation}
-respectively.
-By the (Lyapunov) central limit theorem, we have
-\begin{equation}
-    \frac{1}{2p}\sum_{i=1}^p \left(x(i)^2-1\right) \implies \mathrm{N}(0,1),
-\end{equation}
-under the null, and
-\begin{equation}
-    \frac{1}{2p}\left(\sum_{i=1}^p \left(x(i)^2-1\right) - p^{1/2-\beta+2r}\right) \implies \mathrm{N}(0,1),
-\end{equation}
-under the alternative since $p^{2r-\beta}\to0$ for all $r<0$ and $\beta>0$.
-Hence, perfect detection with the $L_2$-norm is possible if $p^{1/2-\beta+2r}$ diverges, i.e., $r>\beta/2-1/4$.
-On the other hand, if $r<\beta/2-1/4$, the distributions of the (scaled) statistics merge under the null and the alternative.
-% \fbox{Hellinger distance is scale-invariant (show), detection is impossible}.
-
-The case of $L_1$-norm is treated similarly.
-Let $Y=|X|$ where $X\sim|\mathrm{N}(\mu,1)|$. 
-Using the expressions for the mean and variance of $Y$ (see, e.g., \cite{tsagris2014folded}),
-\begin{align}
-    \mu_Y &= \E[Y] = \sqrt{\frac{2}{\pi}}e^{-\mu^2/2} + \mu(1-\Phi(-\mu)), \\
-    \sigma_Y^2 &= \mathrm{Var}(Y) = \mu^2 + 1 - \mu^2_Y,
-\end{align}
-where $\Phi$ is the CDF of a standard normal random variable,
-we have, regardless of the value of $\mu$,
-\begin{equation} \label{eq:bounded-variance-abs-Gaussian}
-    \sigma_Y^2 = \mathrm{Var}(Y) = \E(Y-\E Y)^2 \le \E(X-\E X)^2 = 1,
-\end{equation}
-where the inequality holds because absolute value is a Lipschitz function with Lipschitz constant 1.
-
-By the central limit theorem, we have,
-\begin{equation}
-    \frac{1}{\sqrt{p}}\left(\sum_{i=1}^p |x(i)| - \sqrt{\frac{2}{\pi}}\right) \implies \mathrm{N}(0, 1-2/\pi)
-\end{equation}
-under the null.
-On the other hand, when the alternative hypothesis holds, we have
-\begin{align*}
-    \E \left[ \frac{1}{\sqrt{p}} \left(\sum_{i=1}^p |x(i)| - \sqrt{\frac{2}{\pi}}\right) \right] 
-    &= \frac{p^{1-\beta}}{\sqrt{p}}\left[\left(\sqrt{\frac{2}{\pi}}e^{-\mu^2/2} + \mu\left(1-2\Phi(-\mu)\right) \right) - \sqrt{\frac{2}{\pi}} \right] \\
-    &= p^{1/2-\beta} \left[\sqrt{\frac{2}{\pi}}\left(e^{-p^{2r}/2} - 1 \right) + p^r\left(1-2\Phi(-\mu)\right) \right] \\
-    &= p^{1/2-\beta} \left[\sqrt{\frac{2}{\pi}}\left(-p^{2r}/2 - O(p^{4r})\right) + p^r\left(\sqrt{\frac{2}{\pi}}p^r + O(p^{3r})\right) \right] \\
-    &= p^{1/2-\beta} \sqrt{\frac{2}{\pi}} \left(p^{2r}/2 + O(p^{4r}) \right) \\
-    &= p^{1/2-\beta+2r} \sqrt{{1}/{2\pi}} + O(p^{1/2-\beta+4r}),
-\end{align*}
-and 
-\begin{align*}
-    \mathrm{Var} \left(\frac{1}{\sqrt{p}} \left(\sum_{i=1}^p |x(i)| - \sqrt{\frac{2}{\pi}}\right) \right) 
-    & = (1-p^{1-\beta})(1-2/\pi) + p^{1-\beta}\sigma_{Y}^2 \\
-    & \to 1-2/\pi,
-\end{align*}
-by boundedness of $\sigma_{Y}^2$ shown in \eqref{eq:bounded-variance-abs-Gaussian}.
-Again, by the (Lyapunov) central limit theorem, we conclude asymptotic normality of the centered and scaled $L_1$-norms under the alternative.
-In an entirely analogous argument to the $L_2$-norm case, asymptotically perfect detection can be achieved if $p^{1/2-\beta+2r}$ diverges, i.e., $r>\beta/2-1/4$.
-On the other hand, when $r<\beta/2-1/4$, the two hypotheses cannot be told apart by the $L_1$-norms since the distributions of the (scaled) statistics merge under the two hypotheses.
-\end{proof}
 

### 2021-01-28 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
Chaoter 3
Fixed some mathematical typos and incorporated the proof of Theorem 3.1 in the text.

Also "clarified" the statement of Theorem 3.1.  Please check.

@@
 \ref{subsec:optimal-procedure-sub-exponential}). As we will see, the so-called oracle thresholding estimators are in 
-fact finite-sample optimal for certain classes of models.  These optimality results allow us to establish 
+fact finite-sample optimal for many classes of models.  These optimality results allow us to establish 
 powerful minimax formulations of the exact support recovery phase-transition phenomenon showing its universality for all estimators (Theorem \ref{thm:necessary-strengthened}).
@@
 in the additive noise model with heavier than exponential error densities (Example 
-\ref{exmp:suboptimal-data-thresholding}).   In this case, the likelihood ratio
-thresholding rather than data thresholding can lead to optimal support estimators
+\ref{exmp:suboptimal-data-thresholding}).   In this case, {\em likelihood ratio
+thresholding} rather than {\em data thresholding} can lead to optimal support estimators
 (Section \ref{subsec:optimal-procedure-super-exponential}).  In such cases, the universality 
@@
 \stilian{Continuing this way, we can successively improve the likelihood of every estimator until we arrive at an oracle thresholding estimator, proving the desired optimality.
-Note that with the same argument, any two oracle
+Note that with the same argument, we obtain that any two oracle
 thresholding estimators have the same likelihood.}{
@@
 
-\begin{remark}[An open problem] As we have seen, the thresholding estimators are no longer optimal 
+\begin{remark}[{\bf An open problem\!}\,] As we have seen, the thresholding estimators are no longer optimal 
 in the additive model with error-densities heavier than exponential.   Thanks to Proposition 
@@
 
-In the case where the signals have difference sizes, however, the argument in the proof of Proposition \ref{prop:likelihood-ratio-thresholding} breaks downs since the signal densities need to be identical for Relation \eqref{eq:likelihood-ratio-thresholding-proof} to hold.
+In the case where the signals have different sizes, however, the argument in the proof of Proposition \ref{prop:likelihood-ratio-thresholding} breaks downs since the signal densities need to be identical for Relation \eqref{eq:likelihood-ratio-thresholding-proof} to hold.
 In such cases, the characterization of the optimal procedure is an open problem.

### 2021-01-29 3.phase_transitions/3.proofs-phase-transitions.tex
ch 3
almost done editing ch 3 (for formatting).  I need to absorb the auxuliary results from the appendix and check the proofs carefully once again. I like the new format where the proofs are presented right after the statments and the various support recovery criteria are presented in separate sections rather than sub-sections.  Thus, they are visible in the table of contents.

@@
 
-\section{Monotonicity of the Benjamini-Hochberg procedure}
-\label{suppsec:BH-monotonicity}
-\input{3.phase_transitions/3.BH_monotonicity.tex}
-
 \section{Proof of Theorem \ref{thm:detection-optimality}}
@@
 
-We first show the necessary condition. 
-That is, when $\overline{r} < \beta$, no thresholding procedure is able to achieve approximate support recovery.
-The arguments are similar to that in Theorem 1 of \cite{arias2017distribution}, although we allow for unequal signal sizes.
-
-\begin{proof}[Proof of necessary condition in Theorem \ref{thm:Gaussian-error-approx-boundary}]
-Denote the distributions of $\mathrm{N}(0,1)$, $\mathrm{N}(\underline{\Delta}, 1)$, and $\mathrm{N}((\overline{\Delta}, 1)$ as $F_0$, $F_{\underline{a}}$, and $F_{\overline{a}}$ respectively.
-
-% We first show the necessary condition, i.e., when $\overline{r}<\beta$, approximate support recovery cannot be achieved with any thresholding procedure.
-% In particular, we show that the liminf of the sum of FDP and NDP is at least 1.
-
-Recall that thresholding procedures are of the form
-$$
-\widehat{S}_p = \left\{i\,|\,x(i) > t_p(x)\right\}.
-$$
-Denote $\widehat{S} := \left\{i\,|\,x(i) > t_p(x)\right\}$, and $\widehat{S}(u) := \left\{i\,|\,x(i) > u\right\}$.
-For any threshold $u\ge t_p$ we must have $\widehat{S}(u)\subseteq\widehat{S}$, and hence
-\begin{equation} \label{eq:approx-boundary-proof-FDP-Gaussian}
-    \text{FDP} := \frac{|\widehat{S}\setminus{S}|}{|\widehat{S}|} \ge \frac{|\widehat{S}\setminus{S}|}{|\widehat{S}\cup{S}|} = \frac{|\widehat{S}\setminus{S}|}{|\widehat{S}\setminus{S}| + |S|} \ge
-    \frac{|\widehat{S}(u)\setminus{S}|}{|\widehat{S}(u)\setminus{S}| + |S|}.
-\end{equation}
-On the other hand, for any threshold $u\le t_p$ we must have $\widehat{S}(u)\supseteq\widehat{S}$, and hence
-\begin{equation} \label{eq:approx-boundary-proof-NDP-Gaussian}
-    \text{NDP} := \frac{|{S}\setminus\widehat{S}|}{|{S}|} \ge 
-    \frac{|{S}\setminus\widehat{S}(u)|}{|{S}|}.
-\end{equation}
-Since either $u\ge t_p$ or  $u\le t_p$ must take place, putting \eqref{eq:approx-boundary-proof-FDP-Gaussian} and \eqref{eq:approx-boundary-proof-NDP-Gaussian} together, we have
-\begin{equation} \label{eq:approx-boundary-proof-converse-1-Gaussian}
-    \text{FDP} + \text{NDP} 
-    \ge \frac{|\widehat{S}(u)\setminus{S}|}{|\widehat{S}(u)\setminus{S}|+|{S}|} \wedge \frac{|{S}\setminus\widehat{S}(u)|}{|{S}|},
-\end{equation}
-for any $u$.
-Therefore it suffices to show that for a suitable choice of $u$, the RHS of \eqref{eq:approx-boundary-proof-converse-1-Gaussian} converges to 1 in probability; the desired conclusion on FDR and FNR follows by the dominated convergence theorem.
-
-Let $t^* = \sqrt{2q\log{p}}$ for some fixed $q$, we obtain an estimate of the tail probability by Mill's ratio \eqref{eq:Mills-ratio}, 
-\begin{equation}
-    \overline{F_0}(t^*) 
-    \sim \frac{1}{t^*}\phi(t^*)
-    = \frac{1}{2\sqrt{\pi q\log{p}}} p^{-q}, \label{eq:approx-boundary-proof-null-tail-prob-Gaussian}
-\end{equation}
-where $a_p\sim b_p$ is taken to mean $a_p/b_p\to 1$.
-Observe that $|\widehat{S}(t^*)\setminus{S}|$ has distribution $\text{Binom}(p-s, \overline{F_0}(t^*))$ where $s=|S|$, denote $X = X_p := {|\widehat{S}(t^*)\setminus{S}|}/{|S|}$, and we have 
-$$
-\mu := \E\left[X\right] = \frac{(p-s)\overline{F_0}(t^*)}{s},
-\quad \text{and} \quad
-\var\left(X\right) = \frac{(p-s)\overline{F_0}(t^*){F_0}(t^*)}{s^2} \le \mu/s.
-$$
-Therefore for any $M>0$, we have, by Chebyshev's inequality,
-\begin{equation}
-    \P\left[X < M\right] 
-    \le \P\left[\left|X-\mu\right| > \mu - M\right]
-    \le \frac{\mu/s}{(\mu-M)^2}
-    = \frac{1/(\mu s)}{(1-M/\mu)^2}. \label{eq:approx-boundary-proof-converse-2-Gaussian}
-\end{equation}
-Now, from the expression of $\overline{F_0}(t^*)$ in \eqref{eq:approx-boundary-proof-null-tail-prob-Gaussian}, we obtain
-$$
-\mu = (p^\beta - 1)\overline{F_0}(t^*) \sim \frac{1}{2\sqrt{\pi q\log{p}}} p^{\beta-q}.
-$$
-Since $\overline{r}<\beta$, we can pick $q$ such that $\overline{r}<q<\beta$. 
-In turn, we have $\mu \to\infty$, as $p\to\infty$.
-Therefore the last expression in \eqref{eq:approx-boundary-proof-converse-2-Gaussian} converges to 0, and we conclude that $X\to\infty$ in probability, and hence
-\begin{equation} \label{eq:approx-boundary-proof-converse-3-Gaussian}
-\frac{|\widehat{S}(t^*)\setminus{S}|}{|\widehat{S}(t^*)\setminus{S}|+|{S}|} 
-= \frac{X}{X+1} \to 1 \quad \text{in probability}.
-\end{equation}
-
-On the other hand, we show that with the same choice of $u = t^*$, we have,
-\begin{equation} \label{eq:approx-boundary-proof-converse-4-Gaussian}
-    \frac{|{S}\setminus\widehat{S}(t^*)|}{|{S}|}\to 1 \quad \text{in probability}.
-\end{equation}
-By the stochastic monotonicity of Gaussian location family \eqref{eq:stochastic-monotonicity-Gaussian}, we have the following lower bound for the probability of missed detection for each signal $\mu(i)$, $i\in S$,
-\begin{equation} \label{eq:approx-boundary-proof-converse-5-Gaussian}
-    \P[\mathrm{N}(\mu(i), 1) \le t^*] \ge F_{\overline{a}}(t^*).
-\end{equation}
-Since $|{S}\setminus\widehat{S}(t^*)|$ can be written as the sum of $s$ independent Bernoulli random variables,
-\begin{equation*}
-    |{S}\setminus\widehat{S}(t^*)| = \sum_{i\in S} \mathbbm{1}_{(-\infty, t^*]}(x(i)),
-\end{equation*}
-using with \eqref{eq:approx-boundary-proof-converse-5-Gaussian}, we conclude that $|{S}\setminus\widehat{S}(t^*)| \stackrel{\mathrm{d}}{\ge} \text{Binom}(s, {F_{\overline{a}}}(t^*))$.
-Finally, we know that ${F_{\overline{a}}}(t^*)$ converges to 1 by our choice of diverging $t^*$, and the necessary condition is shown.
-\end{proof}
-
-We now turn to the sufficient condition. 
-That is, when $\underline{r} > \beta$, the Benjamini-Hochberg procedure with slowly vanishing FDR levels achieves asymptotic approximate support recovery.
-
-\begin{proof}[Proof of the sufficient condition in Theorem \ref{thm:Gaussian-error-approx-boundary}]
-The FDR vanishes by our choice of $\alpha$ and the FDR-controlling property of the BH procedure \citep{benjamini1995controlling}.
-It only remains to show that FNR also vanishes.
-
-To do so we compare the FNR under the alternative specified in Theorem \ref{thm:Gaussian-error-approx-boundary} to one with all of the signal sizes equal to $\underline{\Delta}$.
-By Lemma \ref{lemma:monotonicity-BH-procedure}, it suffices to show that the FNR under the BH procedure in this setting vanishes.
-Let $x(i)$ be vectors of independent observations with $p-s$ nulls having standard Gaussian distributions, and $s$ signals having $\mathrm{N}(\underline{\Delta}, 1)$ distributions.
-
-Denote the null and the alternative distributions as $F_0$ and $F_{a}$ respectively.
-Let $\widehat{G}$ denote the empirical survival function as in \eqref{eq:empirical-tail-distribution}.
-Define the empirical survival functions for the null part and signal part
-\begin{equation} \label{eq:empirical-survival-null-signal-Gaussian}
-    \widehat{W}_\text{null}(t) = \frac{1}{p-s}\sum_{i\not\in S}\mathbbm{1}\{x(i) \ge t\},
-    \quad
-    \widehat{W}_\text{signal}(t) = \frac{1}{s}\sum_{i\in S}\mathbbm{1}\{x(i) \ge t\},
-\end{equation}
-where $s=|S|$, so that
-$$
-\widehat{G}(t) = \frac{p-s}{p}\widehat{W}_\text{null}(t) + \frac{s}{p}\widehat{W}_\text{signal}(t).
-$$
-
-We need the following result to describe the deviations of the empirical distributions.
-\begin{lemma}[Theorem 1 of \citet{eicker1979asymptotic}] \label{lemma:empirical-process}
-Let $Z_1,\ldots,Z_k$ be iid with continuous survival function $Q$.
-Let $\widehat{Q}_k$ denote their empirical survival function and define 
-$\xi_k = \sqrt{2\log{\log{(k)}}/k}$ for $k \ge 3$. 
-Then
-$$
-\frac{1}{\xi_k}\sup_z\frac{|\widehat{Q}_k(z) - Q(z)|}{\sqrt{Q(z)(1 - Q(z))}} \to 1,
-$$
-in probability as $k \to \infty$.
-In particular,
-$$
-\widehat{Q}_k(z) = Q(z) + O_\P\left(\xi_k\sqrt{Q(z)(1 - Q(z))}\right),
-$$
-uniformly in z.
-\end{lemma}
-
-Apply Lemma \ref{lemma:empirical-process} to the two summands in $\widehat{G}$, we obtain
-$\widehat{G}(t) = G(t) + \widehat{R}(t)$,
-where 
-\begin{equation} \label{eq:empirical-process-mean-Gaussian}
-    G(t) = \frac{p-s}{p}\overline{F_0}(t) + \frac{s}{p}\overline{F_a}(t),
-\end{equation}
-and 
-\begin{equation} \label{eq:empirical-process-residual-Gaussian}
-    \widehat{R}(t) = O_\P\left(\xi_p\sqrt{\overline{F_0}(t)F_0(t)} + \frac{s}{p}\xi_s\sqrt{\overline{F_a}(t)F_a(t)}\right),
-\end{equation}
-uniformly in $t$.
-
-Recall (see proof of Lemma \ref{lemma:monotonicity-BH-procedure}) that the BH procedure is the thresholding procedure with threshold set at 
-\begin{equation} \label{eq:approx-boundary-proof-tau-Gaussian}
-    \tau = \inf\{t\,|\,\overline{F_0}(t)\le\alpha\widehat{G}(t)\}. 
-    %= \min\{t\,|\,\overline{F_0}(t)=\alpha\widehat{G}(t)\}.
-\end{equation}
-The NDP may also be re-written as 
-$$
-\text{NDP} = \frac{|{S}\setminus\widehat{S}|}{|{S}|} = \frac{1}{s}\sum_{i\in S}\mathbbm{1}\{x(i) < \tau\} = 1 - \widehat{W}_\text{signal}(\tau),
-$$
-so that it suffices to show that 
-\begin{equation} \label{eq:approx-boundary-proof-sufficient-1-Gaussian}
-    \widehat{W}_\text{signal}(\tau)\to 1
-\end{equation} in probability.
-Applying Lemma \ref{lemma:empirical-process} to $\widehat{W}_\text{signal}$, we know that 
-$$
-\widehat{W}_\text{signal}(\tau) = \overline{F_a}(\tau) + O_\P\left(\xi_s\sqrt{\overline{F_a}(\tau)F_a(\tau)}\right) = \overline{F_a}(\tau) + o_\P(1).
-$$
-So it suffices to show that $F_a(\tau)\to 0$ in probability.
-Now let $t^* = \sqrt{2q\log(p)}$ for some $q$ such that $\beta<q<\underline{r}$.
-We have 
-\begin{equation} \label{eq:approx-boundary-proof-sufficient-2-Gaussian}
-    F_a(t^*) 
-    = \Phi(t^* - \underline{\Delta}) 
-    = \Phi(\sqrt{2(q - \underline{r})\log{p}}) \to 0. 
-\end{equation}
-Hence in order to show \eqref{eq:approx-boundary-proof-sufficient-1-Gaussian}, it suffices to show 
-\begin{equation} \label{eq:approx-boundary-proof-sufficient-3-Gaussian}
-    \P\left[\tau \le t^*\right] \to 1.
-\end{equation}
-By \eqref{eq:empirical-process-mean-Gaussian}, the mean of the empirical process $\widehat{G}$ evaluated at $t^*$ is
-\begin{equation} \label{eq:approx-boundary-proof-sufficient-4-Gaussian}
-    G(t^*) = \frac{p-s}{p}\overline{F_0}(t^*) + \frac{s}{p}\overline{F_a}(t^*).
-\end{equation}
-The first term, using Relation \eqref{eq:approx-boundary-proof-null-tail-prob-Gaussian}, is asymptotic to $p^{-q}L(p)$, where $L(p)$ is the logarithmic term in $p$.
-The second term, since $\overline{F_a}(t^*)\to 1$ by Relation \eqref{eq:approx-boundary-proof-sufficient-2-Gaussian}, is asymptotic to $p^{-\beta}$.
-Therefore, $G(t^*) \sim p^{-q}L(p) + p^{-\beta} \sim p^{-\beta}$, since 
-$p^{\beta-q}L(p)\to0$ where $q>\beta$.
-
-The fluctuation of the empirical process at $t^*$, by Relation \eqref{eq:empirical-process-residual-Gaussian}, is 
-\begin{align*}
-    \widehat{R}(t^*) 
-    &= O_\P\left(\xi_p\sqrt{\overline{F_0}(t^*)F_0(t^*)} + \frac{s}{p}\xi_s\sqrt{\overline{F_a}(t^*)F_a(t^*)}\right)\\
-    &= O_\P\left(\xi_p\sqrt{\overline{F_0}(t^*)}\right) + o_\P\left(p^{-\beta}\right).
-\end{align*}
-By \eqref{eq:approx-boundary-proof-null-tail-prob-Gaussian} and the expression for $\xi_p$, the first term is $O_\P\left(p^{-(q+1)/2}L(p)\right)$ where $L(p)$ is a poly-logarithmic term in $p$.
-Since $\beta<\min\{q,1\}$, we have $\beta<(q+1)/2$, and hence $\widehat{R}(t^*) = o_\P(p^{-\beta})$.
-
-Putting the mean and the fluctuation of $\widehat{G}(t^*)$ together, we obtain
-$$
-\widehat{G}(t^*) = G(t^*) + \widehat{R}(t^*) \sim_\P G(t^*) \sim p^{-\beta},
-$$
-and therefore, together with \eqref{eq:approx-boundary-proof-null-tail-prob-Gaussian}, we have
-$$
-\overline{F_0}(t^*)/\widehat{G}(t^*) = p^{\beta-q}L(p)(1+o_{\P}(1)),
-$$
-which is eventually smaller than the FDR level $\alpha$ by the assumption \eqref{eq:slowly-vanishing-error} and the fact that $\beta<q$.
-That is, 
-$$
-\P\left[\overline{F}_0(t^*) / \widehat{G}(t^*) < \alpha\right] \to 1.
-$$
-By definition of $\tau$ (recall \eqref{eq:approx-boundary-proof-tau-Gaussian}), this implies that $\tau \le t^*$ with probability tending to 1, and \eqref{eq:approx-boundary-proof-sufficient-3-Gaussian} is shown.
-The proof for the sufficient condition is complete.
-\end{proof}
-
 \section{Proof of Theorems \ref{thm:Gaussian-error-exact-approx-boundary} and \ref{thm:Gaussian-error-approx-exact-boundary}}
 \label{subsec:proof-additive-error-mix-boundaries}
-
-Proof of Theorem \ref{thm:Gaussian-error-exact-approx-boundary} uses ideas from the proof of Theorem \ref{thm:Gaussian-error-approx-boundary} and is substantially shorter.
-
-\begin{proof}[Proof of Theorem \ref{thm:Gaussian-error-exact-approx-boundary}]
-We first show the sufficient condition. 
-Vanishing FWER is guaranteed by the properties of the procedures, and we only need to show that FNR also goes to zero. 
-Similar to the proof of Theorem \ref{thm:Gaussian-error-approx-boundary}, it suffices to show that
-\begin{equation} \label{eq:additive-error-exact-approx-boundary-proof-sufficient-1}
-    \text{NDP} = 1 - \widehat{W}_\text{signal}(t_p) \to 0,
-\end{equation}
-where $t_p$ is the threshold of Bonferroni's procedure.
-
-Since $\alpha$ vanishes slowly (see Definition \ref{eq:slowly-vanishing-error}), for any $\delta>0$, we have $p^{-\delta}=o(\alpha)$.
-Therefore, we have $-\log\alpha\le\delta\log{p}$ for large $p$, and
-\begin{equation*} 
-    1 \le \limsup_{p\to\infty}\frac{2\log{p} - 2\log{\alpha}}{2\log{p}} \le 1+\delta,
-\end{equation*}
-for any $\delta>0$.
-Therefore, by the expression for normal quantiles, we know that 
-$$
-t_p=F^\leftarrow(1-\alpha/p)\sim(2\log{p}-2\log{\alpha})^{1/2} \sim(2\log{p})^{1/2}.
-$$
-
-Since $\underline{r}>\widetilde{g}(\beta)=1$, we can pick $q$ such that $1<q<\underline{r}$.
-Let $t^* = \sqrt{2q\log{p}}$, we know that $t_p<t_p^*$ for large $p$.
-Therefore for large $p$, we have
-$$
-\widehat{W}_\text{signal}(t_p) \ge \widehat{W}_\text{signal}(t^*) \ge \overline{F_a}(t^*) + o_\P(1),
-$$
-where $\overline{F_a}$ is the survival function of $\mathrm{N}(\sqrt{2\underline{r}\log{p}}, 1)$; the last inequality follows from the stochastic monotonicity of the Gaussian location family \eqref{eq:stochastic-monotonicity-Gaussian}, and Lemma \ref{lemma:empirical-process}.
-Indeed, by our choice of $q<\underline{r}$, we obtain
-$$
-F_a(t^*) = \Phi\left(\sqrt{2(q-\underline{r})\log{p}}\right)\to0,
-$$
-and \eqref{eq:additive-error-exact-approx-boundary-proof-sufficient-1} is shown. 
-This completes the proof of the sufficient condition.
-
-The proof of the necessary condition follows similar structure as in the proof of Theorem \ref{thm:Gaussian-error-approx-boundary}, and uses the lower bound
-\begin{equation} \label{eq:additive-error-exact-approx-boundary-proof-necessary-1}
-    \mathrm{FWER}(\mathcal{R}) + \mathrm{FNR}(\mathcal{R}) \ge \P\left[\max_{i\in S^c}x(i)>u\right] \wedge \E\left[\frac{|S\setminus \widehat{S}(u)|}{|S|}\right],
-\end{equation}
-which holds for any arbitrary thresholding procedure $\mathcal{R}$ and arbitrary real $u\in\R$.
-
-By the assumption that $\overline{r}<\widetilde{g}(\beta)=1$, we can pick $q$ such that $\overline{r}<q<1$ and let $u = t^*=\sqrt{2q\log{p}}$ in \eqref{eq:additive-error-exact-approx-boundary-proof-necessary-1}.
-By relative stability of iid Gaussian random variables \eqref{eq:relative-stability-Gaussian-maxima}, we have
-\begin{equation} \label{eq:additive-error-exact-approx-boundary-proof-necessary-2}
-    \P\left[\frac{\max_{i\in S^c} x(i)}{\sqrt{2\log{p}}} > \frac{t^*}{\sqrt{2\log{p}}}\right] \to 1.
-\end{equation}
-since the first fraction in \eqref{eq:additive-error-exact-approx-boundary-proof-necessary-2} converges to 1, while the second converges to $q<1$.
-Therefore, the first term on the right-hand side of \eqref{eq:additive-error-exact-approx-boundary-proof-necessary-1} converges to 1.
-
-On the other hand, by the stochastic monotonicity of Gaussian location family \eqref{eq:stochastic-monotonicity-Gaussian}, the probability of missed detection for each signal is lower bounded by $\P[Z+\mu(i) \le t^*] \ge F_{\overline{a}}(t^*)$, where $Z$ is a standard Gaussian r.v., and $F_{\overline{a}}$ is the cdf of $\mathrm{N}(\sqrt{2\overline{r}\log{p}}, 1)$.
-Therefore, $|{S}\setminus\widehat{S}(t^*)| \stackrel{\mathrm{d}}{\ge} \text{Binom}(s, {F_{\overline{a}}}(t^*))$, and it suffices to show that ${F_{\overline{a}}}(t^*)$ converges to 1.
-Indeed,
-\begin{equation*}
-    {F_{\overline{a}}}(t^*) = \Phi(\sqrt{2(q-\overline{r})\log{p}}) \to 1,
-\end{equation*}
-by our choice of $q>\overline{r}$.
-Hence both quantities in the minimum on the right-hand side of \eqref{eq:additive-error-exact-approx-boundary-proof-necessary-1} converge to 1 in the limit, and the necessary condition is shown.
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{thm:Gaussian-error-approx-exact-boundary}]
-We first show the sufficient condition.
-Since FDR control is guaranteed by the BH procedure, we only need to show that the FWNR also vanishes, that is,
-\begin{equation} \label{eq:approx-exact-boundary-proof-sufficient-1-Gaussian}
-    \P\left[\min_{i\in S}x(i) \ge \tau\right] \to 1,
-\end{equation}
-where $\tau$ is the threshold for the BH procedure.
-
-By the assumption that $\underline{r}>\widetilde{h}(\beta)=(\sqrt{\beta}+\sqrt{1-\beta})^2$, we have $\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{\beta}$, so we can pick $q>0$, such that 
-\begin{equation} \label{eq:approx-exact-boundary-proof-sufficient-2-Gaussian}
-\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{q}>\sqrt{\beta}.
-\end{equation}
-We only need to show that with a specific choice of $t^*=\sqrt{2q\log{p}}$ where
-\begin{equation} \label{eq:additive-error-approx-exact-boundary-proof-sufficient-1}
-\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{q}>\sqrt{\beta},
-\end{equation}
-we have both
-\begin{equation} \label{additive-error-eq:approx-exact-boundary-proof-sufficient-2}
-\P\left[\tau\le t^*\right]\to 1,
-\end{equation}
-and 
-\begin{equation} \label{eq:additive-error-approx-exact-boundary-proof-sufficient-3}
-    \P\left[\min_{i\in S}x(i) \ge t^* \right] \to 1,
-\end{equation}
-so that 
-\begin{equation*} 
-    \P\left[\min_{i\in S}x(i) \ge \tau\right] \ge 
-    % \P\left[\min_{i\in S}x(i) \ge t^* \ge \tau\right] \ge
-    \P\left[\min_{i\in S}x(i) \ge t^*,\; t^* \ge \tau\right] \to 1.
-\end{equation*}
-
-Relation \eqref{additive-error-eq:approx-exact-boundary-proof-sufficient-2} follows in exactly the same way \eqref{eq:approx-boundary-proof-sufficient-3-Gaussian} did on page  \pageref{eq:approx-boundary-proof-sufficient-3-Gaussian}.
-
-Dividing the left-hand-side in Relation \eqref{eq:additive-error-approx-exact-boundary-proof-sufficient-3} by $\sqrt{2\log{p}}$, we have,
-\begin{align*}
-    \frac{\min_{i\in S}x(i)}{\sqrt{2\log{p}}} 
-    &= \frac{\min_{i\in S}\mu(i)+\epsilon(i)}{\sqrt{2\log{p}}} 
-    \stackrel{\mathrm{d}}{\ge} \frac{\sqrt{2\underline{r}\log{p}} + \min_{i\in S}\epsilon(i)}{\sqrt{2\log{p}}} \\
-    &\to -\sqrt{1-\beta} + \sqrt{\underline{r}},
-\end{align*}
-where the last convergence follows from the relative stability of iid Gaussians minima \eqref{eq:relative-stability-Gaussian-minima}. 
-On the other hand, ${t^*}/{\sqrt{2\log{p}}}=\sqrt{q}<\sqrt{\underline{r}}-\sqrt{1-\beta}$ by our choice of ${q}$, and Relation \eqref{eq:additive-error-approx-exact-boundary-proof-sufficient-3} follows.
-
-The necessary condition follows from the lower bound
-\begin{equation} \label{eq:additive-error-approx-exact-boundary-proof-necessary-1}
-    \mathrm{FDR}(\mathcal{R}) + \mathrm{FWNR}(\mathcal{R}) \ge \E\left[\frac{|\widehat{S}(u)\setminus S|}{|\widehat{S}(u)\setminus S| + |S|}\right] \wedge 
-    \P\left[\min_{i\in S}x(i)<u\right],
-\end{equation}
-which holds for any thresholding procedure $\mathcal{R}$ and for arbitrary $u\in\R$.
-In particular, we show that both terms in the minimum in \eqref{eq:additive-error-approx-exact-boundary-proof-necessary-1} converge to 1 when we set $u=t^*=\sqrt{2q\log{p}}$ where 
-\begin{equation}
-\sqrt{\overline{r}}-\sqrt{1-\beta}<\sqrt{q}<\sqrt{\beta}.
-\end{equation}
-
-On the one hand, we have,
-$$
-\frac{\min_{i\in S}x(i)}{\sqrt{2\log{p}}} 
-\stackrel{\mathrm{d}}{\le} \frac{\min_{i\in S}\epsilon(i)+\sqrt{2\overline{r}\log{p}}}{\sqrt{2\log{p}}} 
-\to \sqrt{\overline{r}}-\sqrt{1-\beta},
-$$
-by relative stability of iid Gaussians \eqref{eq:relative-stability-Gaussian-minima}. On the other hand, ${t^*}/{\sqrt{2\log{p}}}=\sqrt{q}>\sqrt{\underline{r}}-\sqrt{1-\beta}$ by our choice of ${q}$;
-this shows that the second term on the right-hand side of \eqref{eq:additive-error-approx-exact-boundary-proof-necessary-1} converges to 1.
-
-Observe that $|\widehat{S}(t^*)\setminus{S}|$ has distribution $\text{Binom}(p-s, \overline{\Phi}(t^*))$, and define $X = X_p := {|\widehat{S}(t^*)\setminus{S}|}/{|S|}$, we obtain,
-% On the other hand, define $ = \E[|S\setminus\widehat{S}(t^*)|/|S|]$,
-\begin{align*}
-    \mu &:= \E[X] = (p^\beta-1)\overline{\Phi}(t^*) 
-    \sim (p^\beta-1)\frac{\phi(t^*)}{t^*} \\
-    &\sim \frac{1}{\sqrt{2\pi}}\left(2q\log{p}\right)^{-1/2}p^{\beta-q}\to\infty,
-\end{align*}
-where the divergence follows from our choice of $q<\beta$.
-Using again Relations \eqref{eq:approx-boundary-proof-converse-2-Gaussian} and \eqref{eq:approx-boundary-proof-converse-3-Gaussian}, we conclude that the first term on the right-hand side of \eqref{eq:additive-error-approx-exact-boundary-proof-necessary-1} also converges to 1.
-This completes the proof of the necessary condition.
-\end{proof}

### 2021-01-31 2.background/2.AGG.tex

@@
-We introduce a fairly general class of \ac{AGG} distributions and \stilian{review their tail behavior,
-which will play an important role in the sequel.}{\fbox{check the edit}}
+We introduce a fairly general class of distributions known as asymptotic generalized Gaussians \ac{AGG}. 
+We also state some of their tail properties which play important roles in the analysis of phase transitions of high-dimensional testing problems.
 
@@
 \begin{proof}[Proof of Proposition \ref{prop:quantile}]
-By definition of AGG, for any $\epsilon>0$, there is a constant $C(\epsilon)$ such that for all $x\ge C$, we have
+By the definition of AGG, for any $\epsilon>0$, there is a constant $C=C(\epsilon)$ such that for all $x\ge C$, we have
 $$

### 2021-01-31 4.exact_support_recovery/4.phase_transition_results.tex
Remark 4.2 updated

--- 2020-08-17 4.exact_support_recovery/4.phase_transition_results.tex
@@
 
-Section \ref{subsec:dense-signals} discusses the case in which signals are denser than parametrized in \eqref{eq:sparsity-parametrized}, and Section \ref{suppsec:numerical} illustrates the phase transition phenomena with numerical examples.
+Section \ref{subsec:dense-signals} discusses the case where the signals are denser than the ones parametrized in 
+\eqref{eq:sparsity-parametrized}, and Section \ref{suppsec:numerical} illustrates the phase transition phenomena with numerical examples.
 
@@
 Let $\widehat{S}_p$ be the Bonferroni's procedure \eqref{eq:Bonferroni-procedure} with vanishing FWER $\alpha = \alpha(p) \to 0$, such that %\fbox{slower than any polynomial}
-$\alpha p^\delta\to \infty$ for every $\delta>0$.
+$\alpha p^\delta\to \infty$ for every $\delta>0$ (recall Definition \ref{def:slowly-vanishing}).
 If
@@
 
+The proof of this theorem is given blow.  We begin with some comments and state some consequences of this result.
+
+\stilian{There is a one-to-one correspondence between {\em signal support estimation} 
+and {\em multiple hypothesis testing}.  Indeed, every one of the many classic multiple testing procedures, 
+that perform $p$ tests of the null hypotheses ${\cal H}_{0,i}\, :\, \mu_p(i) = 0$ versus the alternatives 
+ ${\cal H}_{a,i}\, :\, \mu_p(i)\not =0,\ i=1,\cdots,p$ gives rise to a natural signal {\em support estimator} defined as
+ $\widehat S_p:=\{ i\, :\, {\cal H}_{0,i} \mbox{ is rejected }\}$. Such a support estimation procedure is said to 
+ control the family-wise error rate (FWER) if
+$$
+ \P_{{\cal H}_0} ( \widehat S_p  \not = \emptyset ) \to 0,\ \ \mbox{ as } p\to\infty,
+$$
+where ${\cal H}_0 = \cap_{i=1}^p {\cal H}_{0,i}$ is the global null hypothesis that there is no signal.
+Conversely, every support estimator $\widehat S_p$ amounts to performing multiple testing, where ${\cal H}_{0,i}$
+is rejected if $i \in \widehat S_p$.
+}
+{\fbox{IS THIS TRUE???} SHOULD WE MOVE this to CHAPTER 2. We should remind the reader what ``FWER-controlling procedure" is... 
+Honestly, I am a little CONFUSED about the following general statement.  When we are not talking about the detection problem, I am not 
+quite sure how to understand the term ``FWER-controlling procedure".  This is what made me suggest the above paragraph in blue.  Do you agree?
+}
+
 \begin{corollary}[Classes of procedures attaining the boundary]
@@
 Under Gaussian errors, the particular choice of the thresholding at $t_p = \sqrt{2\log{p}}$ in \eqref{eq:Bonferroni-procedure} corresponds to a Bonferroni's procedure with FWER decreasing at a rate of $(\log{p})^{-1/2}$, and hence Theorem \ref{thm:sufficient} applies.
-By Corollary \ref{cor:FWER-controlling_procedures}, Holm's procedure --- and when the errors are independent, the {\v{S}}id{\'a}k, and Hochberg procedures --- with FWER controlled at $(\log{p})^{-1/2}$ all achieve perfect support recovery provided that $\underline{r}>g(\beta)$.
+By Corollary \ref{cor:FWER-controlling_procedures}, Holm's procedure --- and when the errors are independent, the {\v{S}}id{\'a}k, and Hochberg procedures --- with FWER controlled at $(\log{p})^{-1/2}$ all achieve an asymptotically
+perfect support recovery provided that $\underline{r}>g(\beta)$.
 \end{example}
@@
 The claims in Example \ref{exmp:FWER-controlling_procedures} are verified in Section \ref{suppsec:proofs}.
-
 We now turn to the proof of Theorem \ref{thm:sufficient}.
@@
 \begin{proof}[Proof of Theorem \ref{thm:sufficient}]
-Throughout the proof, dependence on $p$ will be suppressed to simplify notations when such omissions do not lead to ambiguity.
+Throughout the proof, the dependence on $p$ will be suppressed to simplify notations when such omissions do not lead to ambiguity.
 
@@
 where we used the union bound in the first inequality. 
-Notice that the lower bound \eqref{eq:Bonferroni-FWER-control} is independent of the parameter $\mu$ (as well as the dependence structures), and hence holds uniformly over the parameter space, i.e.,
+Notice that the lower bound \eqref{eq:Bonferroni-FWER-control} is independent of the parameter $\mu$ (as well as 
+the error dependence structure), and hence it holds uniformly over the parameter space, i.e.,
 \begin{equation} \label{eq:exact-supporot-recovery-FWER}
@@
 
-On the other hand, for the probability of no missed detection, we have:
+On the other hand, for the probability of no missed detection, we need to use the parameterization of the signal strength.
+In this case, we have:
 \begin{equation*}
@@
 
-The statements in Theorem \ref{thm:sufficient} can be strengthened, to prepare us for a minimax result given in Section \ref{sec:optimality} below.
+In the following remarks we show that the statements in Theorem \ref{thm:sufficient} can be strengthened. They 
+prepare us for the minimax result given in Section \ref{sec:optimality} below.
 
@@
 In the proof of Theorem \ref{thm:sufficient}, both \eqref{eq:Bonferroni-FWER-control} and \eqref{eq:sufficient-proof-eq2} hold uniformly over all error dependence structures.
-Therefore, \eqref{eq:exact-supporot-recovery-FWER} and \eqref{eq:exact-supporot-recovery-FWNR} may be strengthened to yield
+Therefore, \eqref{eq:exact-supporot-recovery-FWER} and \eqref{eq:exact-supporot-recovery-FWNR} can be written as
 \begin{equation} \label{eq:exact-supporot-recovery-strengthened}
-    \lim_{p\to\infty}\sup_{\substack{\mu\in\Theta_p^+(\beta, \underline{r})\\ {\cal E}\in D(F)}} P[\widehat{S}_p \neq S_p] = 0,
+    \lim_{p\to\infty}\sup_{\substack{\mu\in\Theta_p^+(\beta, \underline{r})\\ {\cal E}\in D(F)}} \P[\widehat{S}_p \neq S_p] = 0,
 \end{equation}
@@
 \begin{remark}
-We emphasize that Theorem \ref{thm:sufficient} holds for errors with \emph{arbitrary} dependence structures. 
-Intuitively, this is because the maxima of the errors grow at their fastest in the case of independence. 
-Formally, the light-tailed nature of the error distribution allowed us to obtain sharp tail estimates via simple union bounds, valid under arbitrary dependence.
+We emphasize that Theorem \ref{thm:sufficient} holds for errors with an \emph{arbitrary} dependence structure. 
+This is because the maxima of errors with {\em rapidly varying} distributions grow at their fastest in the case of 
+independence (recall Remark \ref{rem:iid-max}).  Formally, this follows from the light-tailed nature of the error 
+distribution, which allows us to obtain sharp tail estimates via simple union bounds, valid under arbitrary 
+dependence (cf \eqref{e:prop:rapid-varying-tails_part-i-1}).
 % Formally, this result stems from the fact that maxima of distributions with \emph{rapidly varying tails} (Definition \ref{def:rapid-variation}) can be bounded from above using quantiles of their marginal distribution, under arbitrary dependence.
@@
 \begin{definition}[Uniform Relative Stability] \label{def:URS}
-Under the notations established in Definition \ref{def:RS}, the triangular array ${\cal E}$ is said to have uniform relatively stable (URS) maxima if for \emph{every} sequence of subsets $S_p\subseteq\{1,\ldots,p\}$ such that $|S_p| \to \infty$, we have
+Under the notations established in Definition \ref{def:RS}, the triangular array ${\cal E}$ is said to have uniformly relatively stable (URS) maxima if for \emph{every} sequence of subsets $S_p\subseteq\{1,\ldots,p\}$ such that $|S_p| \to \infty$,
+we have
 \begin{equation} \label{eq:URS-condition}
-    \frac{1}{u_{|S_p|}} M_{S_p} := \frac{1}{u_{|S_p|}} \max_{i\in S_p} \epsilon_p(i) \xrightarrow{\P} 1,
+    \frac{1}{u_{|S_p|}} M_{S_p} := \frac{1}{u_{|S_p|}} \max_{i\in S_p} \epsilon_p(i) \xrightarrow{\P} 1,\ \ \mbox{ as }p\to\infty,
 \end{equation}
-as $p\to\infty$, where $u_q,\ q\in \{1,\ldots,p\}$ is the generalized quantile in \eqref{eq:quantiles}.
+where $u_q,\ q\in \{1,\ldots,p\}$ is the generalized quantile in \eqref{eq:quantiles}.
 The collection of arrays ${\cal E} = \{ \epsilon_p(i) \}$ with URS maxima is 
@@
 
-Uniform relative stability is, as its name suggests, a stronger requirement on dependence than relative stability (recall Definition \ref{def:RS}). 
-Proposition \ref{prop:rapid-varying-tails} states that an array with iid components sharing a marginal distribution $F$ with rapidly varying tails (Definition  \ref{def:rapid-variation}) has relatively stable maxima; it is easy to see that URS also follows, by independence of the entries.
+Uniform relative stability is, as its name suggests, is a stronger dependence condition than relative stability (recall 
+Definition \ref{def:RS}).  Proposition \ref{prop:rapid-varying-tails} states that an array with iid components sharing 
+a marginal distribution $F$ with rapidly varying tails (Definition  \ref{def:rapid-variation}) has relatively stable maxima. 
+In this case, it is easy to see that URS also holds, by the independence of the entries.
 
 \begin{corollary} \label{cor:AGG-is-URS}
-An independent array ${\cal E}$ with common marginals $F\in\text{AGG}(\nu)$, $\nu>0$, is URS; in this case, URS holds with $u_{|S_p|} \sim \left(\nu\log{|S_p|}\right)^{1/\nu}$.
+An independent array ${\cal E}$ with common marginals $F\in\text{AGG}(\nu)$, $\nu>0$, is URS.  
+In this case, URS holds with $u_{|S_p|} \sim \left(\nu\log{|S_p|}\right)^{1/\nu}$.
 \end{corollary}
@@
 On the other hand, RS and URS hold under much broader dependence structures than just 
-independent errors. 
-These conditions are extremely mild and can be shown to hold for many classes of error models.  
-In Chapter \ref{chap:URS}, we will focus extensively on the Gaussian case, which is of great interest in applications and is rather challenging. 
-We will provide simple necessary and sufficient condition for uniform relative stability in terms of the covariance structures.
+independence.  These conditions are extremely mild and can be shown to hold for many classes of error models.  
+In Chapter \ref{chap:URS}, we will focus extensively on the Gaussian case, which is of great interest in applications 
+and is rather challenging.  We will provide simple necessary and sufficient condition for uniform relative stability in 
+terms of the error covariance structure and as we will see URS is a much weaker dependence condition than the traditional
+``mixing conditions'' in the literature \citep[see][for more insights]{leadbetter2012extremes}.
 
 The relative stability concepts are important because they characterize the dependence structures under which the maxima of error sequences {\em concentrate} around the quantiles \eqref{eq:quantiles} in the sense of \eqref{eq:RS-condition}.
-This concentration of maxima phenomena, in turn, is the key to establishing the necessary conditions of the phase transition results in support recovery problems.
+This {\em concentration of maxima phenomenon}, in turn, is the key to establishing the necessary conditions of the phase transition results in support recovery problems.
 
@@
 \end{theorem}
-
-% We comment on some consequences of the theorem, before presenting its proof.
-Our first comment is on the signal sizes, and in particular, the gap between the sufficient conditions (Theorem \ref{thm:sufficient}) and the necessary conditions (Theorem \ref{thm:necessary}).
-
-\begin{remark} \label{rmk:gap-between-sufficient-necessary}
-The sufficient condition in Theorem \ref{thm:sufficient} requires that \emph{all} signals be larger than the strong classification boundary $g(\beta)$ in order to achieve exact support recovery \eqref{eq:exact-recovery}, while Theorem \ref{thm:necessary} states that exact support recovery fails (in the sense of \eqref{eq:exact-recovery-failure}) when \emph{all} signal sizes are below the boundary --- the two conditions are \emph{not} complements of each other.
-This gap between the sufficient and necessary conditions on signal sizes, however, may be difficult to bridge.
-Indeed, in general, when signal sizes straddle the boundary $g(\beta)$, either outcome is possible, as we demonstrate in Example \ref{exmp:signals-straddling-the-boundary} below.
-\end{remark}
-
-\begin{example}[Signals straddling the boundary]
-\label{exmp:signals-straddling-the-boundary}
-Let the signal $\mu$ have $|S_p| = \lfloor p^{(1-\beta)} \rfloor$ non-zero entries, composed of two disjoint sets $S_p = S_p^{(1)}\cup S_p^{(2)}$.
-Let also the magnitude of the signals be equal within the two sets, i.e., $\mu(i)=\sqrt{2r^{(k)}\log{p}}$ if $i\in S_p^{(k)}$ for some constants $r^{(k)} > 0$ for $k=1,2$.
-For simplicity, assume that the errors are iid standard Gaussians.
-
-Consider two scenarios
-\begin{enumerate}
-    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1+\delta)$ with $|S_p^{(1)}|=|S_p|-1$, $|S_p^{(2)}|=1$, 
-    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1-\delta)g(\beta)$ with $|S_p^{(1)}|=\lfloor|S_p|/2\rfloor$, $|S_p^{(2)}|=|S_p| - |S_p^{(1)}|$.
-\end{enumerate}
-for some constants $0<\delta<1-\beta<1$. 
-In both cases, signals in $S_p^{(1)}$ (respectively, $S_p^{(2)}$) are above (respectively, below) the strong classification boundary \eqref{eq:strong-classification-boundary}.
-However, in the first scenario, we have $\mathbb{P}[\widehat{S}^{\text{Bonf}}_p=S_p]\to 1$ where $\widehat{S}^{\text{Bonf}}_p$ is the Bonferroni's procedure described in Theorem \ref{thm:sufficient}, 
-while in the second scenario, we have $\mathbb{P}[\widehat{S}_p=S_p]\to 0$ for \emph{all} thresholding procedures $\widehat{S}_p$.
-\end{example}
-The claims in Example \ref{exmp:signals-straddling-the-boundary} are verified in Section \ref{suppsec:proofs}.
-
-Our second comment is on the interplay between thresholding procedures and the dependence class characterized by URS.
-\begin{remark} \label{rmk:dependence-assumptions}
-Paraphrasing Theorems \ref{thm:sufficient} and \ref{thm:necessary}: 
-if we consider only thresholding procedures, then for a very large class of dependence structures, we cannot improve upon the Bonferroni procedure $\widehat{S}_p^{\text{Bonf}}$. 
-Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we have
-\begin{equation}
-    \lim_{p\to\infty} \P[\widehat{S}_p^{\text{Bonf}}\neq S_p]
-    = \begin{cases}
-    \limsup_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 0, & \text{if}\quad \underline{r} > g(\beta),\\
-    \liminf_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 1, & \text{if}\quad \overline{r} < g(\beta)\\
-    \end{cases}
-\end{equation}
-where $\cal T$ is the set of all thresholding procedures \eqref{eq:thresholding-procedure}.
-
-Theorem \ref{thm:necessary} also yields an answer the question raised in \citet{butucea2018variable}.
-In particular, the authors of \citep{butucea2018variable} commented that independent error is the  `least favorable model' in the problem of support recovery, and 
-conjectured that the support recovery problem may be easier to solve under dependence, similar to how the problem of signal detection is easier under dependent 
-errors (see \cite{hall2010innovated}). 
-Surprisingly, our results here state that asymptotically, \emph{all} error dependence structures in the large URS class are equally difficult for \emph{thresholding procedures}.
-Therefore, the phase transition behavior is universal in the class of dependence structures characterized by URS.
-
-To facilitate comparison with results in existing literature, we will formulate explicit minimax statements in Section \ref{sec:optimality}.
-\end{remark}
-
-We must emphasize that the restriction to the URS dependence class is \emph{not} an assumption of convenience. 
-The condition on dependence characterized by uniform relative stability is, in fact, the weakest of its kind in the literature.
-We will characterize the class URS dependence class in Chapter \ref{chap:URS} below.
-
-% \begin{remark}   {\color{blue} Here is an idea -- one could estimate the threshold robustly.  For example,
-% suppose that we know that the support set is of size $\le p^{1-\beta_0}$, for some fixed $\beta_0\in(0,1)$.  Assume also (for simplicity) that the
-% signals can only be positive.  Then, let
-% $$
-% T_p := x_{([p^{1-\beta_0}])},
-% $$
-% be the top $[p^{1-\beta_0}]$-th order statistic of the data.  Then, I believe, but I have not proved it that in the absence of signal
-% $T_p/u_p \to 1$ in probability.  This should be easy to verify in the iid case and it is an {\bf open problem} in the general URS case. 
-% Therefore, one can take the threshold to be:
-% $$ t_p(\delta)  := T_p\times (1+\delta),$$ 
-% where $\delta>0$ is something tiny (which can also be made to vanish slowly as $p\to\infty$.
-
-% We know, from our theory that if a threshold estimator is to be able to recover the support, then all the signal entries should be 
-% above $T_p$ (since we assume that the sparsity $\beta<\beta_0$).  Thus, it is plausible that in this case, the value of
-% $T_p$ is unaffected by the signal and $T_p\sim u_p$ in probability.  Now, the factor $1+\delta$ makes the threshold $t_p$ just large enough for it to
-% miss any false positives, and if $\delta>0$ is small, to capture all the signal, as $p\to\infty$.
-
-% This idea can be easily checked with simulations to see how well it does in practice.  It is almost completely non-parametric!!! 
-% What do you think?   If it ``works", should we include it? 
-% }
-% \end{remark}
-
-We conclude with the proof of Theorem \ref{thm:necessary}.
-
-\begin{proof} [Proof of Theorem \ref{thm:necessary}]
-To avoid cumbersome double subscript notations, we will sometimes suppress dependence on $p$ of the set sequences $\widehat{S}_p$ and $S_p$ in the proof.
+\begin{proof}
+To avoid cumbersome double subscript notations, we will sometimes suppress dependence on $p$ of the set sequences $\widehat{S}_p$ and $S_p$.
 
@@
 $$
-where ties can be broken lexicographically if multiple maximizers exist.
+where the ties can be broken lexicographically if multiple maximizers exist.
 Then,
@@
 \end{equation}
-so that the two random terms in probability \eqref{eq:classification-possible-dependent-proof-2} converge to constants.
-Notice that the second relation in \eqref{eq:classification-possible-dependent-proof-3} holds by URS for any $\beta\in(0,1)$; when $\beta=1$, the relation holds since ${u_{|S^*|}}/{u_p}$ vanishes while $\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight.
+so that the two random terms in the argument of the probability \eqref{eq:classification-possible-dependent-proof-2} converge to constants.
+Notice that the second relation in \eqref{eq:classification-possible-dependent-proof-3} holds by URS for any 
+$\beta\in(0,1)$ and when $\beta=1$, the relation holds since ${u_{|S^*|}}/{u_p}$ vanishes while 
+$\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight.
 
-Since signal sizes are bounded above by $\overline{r} < \left(1 + (1-\beta)^{1/\nu}\right)^{\nu}$, we can write $\overline{r}^{1/\nu} = 1 + (1-\beta)^{1/\nu} - d$ for some $d > 0$.
+Since the signal sizes are bounded above by $\overline{r} < \left(1 + (1-\beta)^{1/\nu}\right)^{\nu}$, we can write $\overline{r}^{1/\nu} = 1 + (1-\beta)^{1/\nu} - d$ for some $d > 0$.
 By our parametrization of $\overline{\Delta}$, we have
@@
 \end{equation}
-Combining \eqref{eq:classification-possible-dependent-proof-3} and \eqref{eq:classification-possible-dependent-proof-4}, we conclude that the right-hand-side of the probability \eqref{eq:classification-possible-dependent-proof-2} converges in probability to a constant strictly less than 1, that is,
+Combining \eqref{eq:classification-possible-dependent-proof-3} and \eqref{eq:classification-possible-dependent-proof-4}, we conclude that the term in right-hand-side of the probability \eqref{eq:classification-possible-dependent-proof-2} converges in probability to a constant strictly less than 1, that is,
 \begin{equation}
@@
 
+We end this section with several remarks.
+% We comment on some consequences of the theorem, before presenting its proof.
+Our first comment is on the signal sizes, and in particular, the gap between the sufficient conditions (Theorem \ref{thm:sufficient}) and the necessary conditions (Theorem \ref{thm:necessary}).
+
+\begin{remark} \label{rmk:gap-between-sufficient-necessary}
+The sufficient condition in Theorem \ref{thm:sufficient} requires that \emph{all} signals be larger than the strong classification boundary $g(\beta)$ in order to achieve exact support recovery \eqref{eq:exact-recovery}, while Theorem \ref{thm:necessary} states that exact support recovery fails (in the sense of \eqref{eq:exact-recovery-failure}) when \emph{all} signal sizes are below the boundary --- the two conditions are \emph{not} complements of each other.
+This gap between the sufficient and necessary conditions on signal sizes, however, may be difficult to bridge.
+Indeed, in general, when signal sizes straddle the boundary $g(\beta)$, either outcome is possible, as we demonstrate 
+in the following Example \ref{exmp:signals-straddling-the-boundary}.
+\end{remark}
+
+\begin{example}[Signals straddling the boundary]
+\label{exmp:signals-straddling-the-boundary}
+Let the signal $\mu$ have $|S_p| = \lfloor p^{(1-\beta)} \rfloor$ non-zero entries, where the signal support $S_p$
+is partitioned into two disjoint sets $S_p = S_p^{(1)}\cup S_p^{(2)}$. Let also the magnitude of the signal entries
+be equal within each of the two sets, i.e., $\mu(i)=\sqrt{2r^{(k)}\log{p}}$ if $i\in S_p^{(k)}$ for some constants $r^{(k)} > 0$ for $k=1,2$.
+For simplicity, assume that the errors are iid standard Gaussians.
+
+Consider two scenarios
+\begin{enumerate}
+    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1+\delta)$ with $|S_p^{(1)}|=|S_p|-1$, $|S_p^{(2)}|=1$, 
+    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1-\delta)g(\beta)$ with $|S_p^{(1)}|=\lfloor|S_p|/2\rfloor$, $|S_p^{(2)}|=|S_p| - |S_p^{(1)}|$.
+\end{enumerate}
+for some constants $0<\delta<1-\beta<1$. 
+In both cases, the signals in $S_p^{(1)}$ (respectively, $S_p^{(2)}$) are above (respectively, below) the strong 
+classification boundary \eqref{eq:strong-classification-boundary}.
+However, in the first scenario, we have $\mathbb{P}[\widehat{S}^{\text{Bonf}}_p=S_p]\to 1$ where $\widehat{S}^{\text{Bonf}}_p$ is the Bonferroni's procedure described in Theorem \ref{thm:sufficient},
+while in the second scenario, we have $\mathbb{P}[\widehat{S}_p=S_p]\to 0$ for \emph{all} thresholding procedures $\widehat{S}_p$.
+\end{example}
+
+The claims in Example \ref{exmp:signals-straddling-the-boundary} are verified in Section \ref{suppsec:proofs}.
+
+Our second comment is on the interplay between thresholding procedures and the dependence class characterized by URS.
+\begin{remark} \label{rmk:dependence-assumptions}
+Paraphrasing Theorems \ref{thm:sufficient} and \ref{thm:necessary}: 
+if we consider only thresholding procedures, then for a very large class of dependence structures, we cannot improve upon the Bonferroni procedure $\widehat{S}_p^{\text{Bonf}}$ \stilian{with {\em slowly vanishing} bound on the FWER $\alpha = \alpha(p)\to 0$ (recall Definitions \ref{def:Bonf} and \ref{def:slowly-vanishing}).}{\fbox{Added.
+Is it correct?}}
+Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we have
+\begin{equation}
+    \lim_{p\to\infty} \P[\widehat{S}_p^{\text{Bonf}}\neq S_p]
+    = \begin{cases}
+    \limsup_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 0, & \text{if}\quad \underline{r} > g(\beta),\\
+    \liminf_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 1, & \text{if}\quad \overline{r} < g(\beta)\\
+    \end{cases}
+\end{equation}
+where $\cal T$ is the set of all thresholding procedures \eqref{eq:thresholding-procedure}.
+
+Theorem \ref{thm:necessary} also yields an answer the question raised in \citet{butucea2018variable}.
+In particular, the authors of \citep{butucea2018variable} commented that independent error is the  `least favorable model' in the problem of support recovery, and 
+conjectured that the support recovery problem may be easier to solve under dependence, similar to how the problem of signal detection is easier under dependent 
+errors (see \cite{hall2010innovated}). 
+Surprisingly, our results here state that asymptotically, \emph{all} error dependence structures in the large URS class are equally difficult for \emph{thresholding procedures}.
+Therefore, the phase transition behavior is universal in the class of dependence structures characterized by URS.
+
+To facilitate comparison with results in existing literature, we will formulate explicit minimax statements in Section \ref{sec:optimality}.
+\end{remark}
+
+We must emphasize that the restriction to the URS dependence class is \emph{not} an assumption of convenience. 
+The condition on the dependence structure imposed by the uniform relative stability property is, in fact, the 
+weakest of its kind in the literature. \stilian{This is demonstrated in Chapter \ref{chap:URS} below, where we characterize
+the  {\em Gaussian} URS error arrays (see also page \pageref{UDD_and_Berman}).  The URS property holds also 
+for a great variety of non-Gaussian error models.  The comprehensive study of this new concentration of maxima 
+phenomenon, however, is in its infancy.  Nevertheless, the authors are convinced that URS is typically the rule rather 
+than an exception.}{\fbox{Check}}
+
+% \begin{remark}   {\color{blue} Here is an idea -- one could estimate the threshold robustly.  For example,
+% suppose that we know that the support set is of size $\le p^{1-\beta_0}$, for some fixed $\beta_0\in(0,1)$.  Assume also (for simplicity) that the
+% signals can only be positive.  Then, let
+% $$
+% T_p := x_{([p^{1-\beta_0}])},
+% $$
+% be the top $[p^{1-\beta_0}]$-th order statistic of the data.  Then, I believe, but I have not proved it that in the absence of signal
+% $T_p/u_p \to 1$ in probability.  This should be easy to verify in the iid case and it is an {\bf open problem} in the general URS case. 
+% Therefore, one can take the threshold to be:
+% $$ t_p(\delta)  := T_p\times (1+\delta),$$ 
+% where $\delta>0$ is something tiny (which can also be made to vanish slowly as $p\to\infty$.
+
+% We know, from our theory that if a threshold estimator is to be able to recover the support, then all the signal entries should be 
+% above $T_p$ (since we assume that the sparsity $\beta<\beta_0$).  Thus, it is plausible that in this case, the value of
+% $T_p$ is unaffected by the signal and $T_p\sim u_p$ in probability.  Now, the factor $1+\delta$ makes the threshold $t_p$ just large enough for it to
+% miss any false positives, and if $\delta>0$ is small, to capture all the signal, as $p\to\infty$.
+
+% This idea can be easily checked with simulations to see how well it does in practice.  It is almost completely non-parametric!!! 
+% What do you think?   If it ``works", should we include it? 
+% }
+% \end{remark}
+
+\stilian{
+We conclude with a brief remark on the dense signal regime.
+\begin{remark}[Dense signals]  In the case where the size of the support set is proportional to the 
+problem dimension, i.e. $|S_p| \sim cp$ for some constant $c\in(0,1)$.  Then, it can be shown
+that a phase-transition-type result still holds, independently of the value of $c$.  For more details, see
+Section \ref{subsec:dense-signals}.
+\end{remark}
+ }{\fbox{Replace the following section with a remark and move the section to the online supplement?}
+ This SAVES 1 PAGE ONLY}
 \subsection{Dense signals} 

### 2021-02-01 6.GWAS/GWAS.tex
rewrite GWAS Section intro

@@
-We investigate the fundamental limits of multiple testing problems in high-dimensional chi-square models, and in genome-wide association studies as introduced in Section \ref{sec:motivation-chisq}.
+The process of scientific discovery, as famously explained by Richard Faynman, usually starts with guesses in one form or another.
+The consequences of such guesses are then computed, and compared with experimental results.
+If the predictions disagree with experiment, then our guesses are wrong. ``That is all there is to it''  \citep{feynman2017character}.
 
-In Section \ref{sec:chisq-boundaries}, we shall establish the phase transitions of the sparse chi-square model \eqref{eq:model-chisq}.
-Recall that in large-scale screening studies where a large number of association tests are conducted, resulting statistics may be approximated by
+In previous chapters, we delved deep in to the theoretical underpinnings of the phase transition phenomena in high-dimensional multiple testing problems.
+The results are interesting in their own right.
+However, in the spirit of Faynman, we have not discovered any scientific law, but merely worked out mathematical consequences of our postulated models.
+In this chapter, our goal is to relate these predictions to real experimental data from the field of genetics, where large-scale simultaneous hypotheses testing problems often arise.
+From such comparisons, we will demonstrate that the phase transition laws are indeed accurate predictions of some curious phenomena in the real world.
+The accuracy of our predictions will lend credibility to the application of these ``laws of large dimensions'' in actual statistical problems.
+
+\medskip
+
+In our case, the experimental data used as the measuring stick come from genome-wide association studies (\ac{GWAS}), introduced in Section \ref{sec:motivation-chisq}.
+Recall that in \ac{GWAS}, a large number of marginal association tests are conducted simultaneously, resulting in statistics that can be approximated by
 \begin{equation} \label{eq:model-chisq-Chapter6}
@@
 where $\chi_\nu^2\left(\lambda(i)\right)$ is a chi-square distributed random variable with $\nu$ degrees of freedom and non-centrality parameter $\lambda(i)$.
-In parallel to results in Chapter \ref{chap:phase-transitions}, we show that several commonly used family-wise error rate-control procedures --- including Bonferroni's procedure --- are asymptotically optimal for the {exact}, and {exact-approximate} support recovery problems (as defined in Definition \ref{def:exact-recovery-success-failure}) in idealized chi-square models \eqref{eq:model-chisq-Chapter6} with independent components.
-We further show that the \ac{BH} procedure is asymptotically optimal for the {approximate}, and {approximate-exact} support recovery problems.
+
+We establish our theoretical predictions in two steps.
+In Section \ref{sec:chisq-boundaries} below, we shall first establish the phase transitions of the model \eqref{eq:model-chisq-Chapter6}.
+In parallel to results in Chapter \ref{chap:phase-transitions}, we show that several commonly used family-wise error rate-control procedures --- including Bonferroni's procedure --- are asymptotically optimal for the {exact}, and {exact-approximate} support recovery problems (recall Definition \ref{def:exact-recovery-success-failure}) in idealized chi-square models with independent components.
+Analogously, the \ac{BH} procedure is asymptotically optimal for the {approximate}, and {approximate-exact} support recovery problems.
 % \ref{thm:chi-squared-exact-boundary}, \ref{thm:chi-squared-exact-approx-boundary}, \ref{thm:chi-squared-approx-boundary}, and \ref{thm:chi-squared-approx-exact-boundary}.
@@
 
-All phase transition boundaries coincide with those in the additive error models obtained in Chapter \ref{chap:phase-transitions} under suitable parametrizations.
-% and Figure \ref{fig:phase-chi-squared} continues to apply.
-This indicates vanishing differences between the difficulties of the one-sided and two-sided alternatives in the Gaussian additive error model \eqref{eq:model-additive}.
-
-\medskip
-
-We then return to association screenings of categorical variables in
-Section \ref{sec:odds-and-power}, and present the consequences of the phase transition in the exact-approximate problem in large-scale genetic association studies.
+We then translate the canonical signal size and sparsity parametrizations into the vernacular of statistical geneticists in Section \ref{sec:odds-and-power}.
 % present empirical evidence for the phase transition in the exact-approximate problem using real data from large-scale association studies on breast cancer obtained from the NHGRI-EBI GWAS Catalog \citep{macarthur2016new}.
@@
 We do so by characterizing the relationship between the signal size $\lambda$ and the marginal frequencies, odds ratio, and sample sizes for association tests on 2-by-2 contingency tables. 
+These parameters are more often estimated and reported in \ac{GWAS} than the elusive signal size parameter $\lambda$.
 % Specifically, the amount of signal, when rare variants are present, is weaker compared to the signal when the marginal distributions are balanced.
 % In other words, reliable detection of the effects by rare variants would require more samples compared to common variants, even at the same odds ratio.
-This result, establishing the relationship between sample sizes and signal sizes, is made precise in Section \ref{sec:odds-and-power}.
+% This result, establishing the relationship between sample sizes and signal sizes, is made precise in Section \ref{sec:odds-and-power}.
+As a bonus, we point out an implications of this relationship on optimal study designs for association studies in Section \ref{sec:optimal-design}.
+Perhaps surprisingly, our analysis reveals that balanced designs with equal number of cases and controls are often statistically inefficient.
+% Practical consequences of these results in power analysis will be illustrated with data examples in Section \ref{sec:phase-transitions-in-GWAS}.
 
-We elaborate on the implications of this relationship on optimal study designs for association studies in Section \ref{sec:optimal-design}.
-Perhaps surprisingly, our analysis reveals that balanced designs with equal number of cases and controls are often statistically inefficient.
-Practical consequences of these results in power analysis will be illustrated with data examples in Section \ref{sec:phase-transitions-in-GWAS}.
+Armed with the results on phase transitions in the chi-square model, and a translation from the language of high-dimenstional statistics to the patois of association screening studies, we finally present in Section \ref{sec:phase-transitions-in-GWAS} the consequences of the phase transitions in \ac{GWAS}, and compare against real experimental data to evaluate the success of our predictions.
 
 The phase transitions in the chi-square models are demonstrated with numerical simulations in Section \ref{sec:numerical}.
-Proofs of results in this Chapter are collected in Section \ref{sec:proof-signal-size-odds-ratio}.
+Proofs are collected in the online Supplement.
+%in Section \ref{sec:proof-signal-size-odds-ratio}.
 

### 2021-02-01 6.GWAS/6.optimal-design.tex
move proofs of GWAS results: 1. move proofs of phase transition results to appendix. 2. move proofs of results on signal sizes in text

@@
 
-Corollary \ref{cor:optimal-design} is proved in Section \ref{subsec:proof-signal-size-odds-ratio}.
+\begin{proof}
+	Using the parametrization in \eqref{eq:reparametrize-2-by-2-table-1}, we solve for $\delta$ in \eqref{eq:odds-ratio-delta} to obtain
+	\begin{align}
+		\delta &= \frac{\phi_1 fR}{fR+1-f} - \left(\frac{\phi_1 fR}{fR+1-f} + f(1-\phi_1)\right)\phi_1 \nonumber \\
+		&= \frac{f(1-f)\phi_1(1-\phi_1)(R-1)}{fR+1-f}. \label{eq:reparametrize-2-by-2-table-2}
+	\end{align}
+	Substituting \eqref{eq:reparametrize-2-by-2-table-2} into the expression \eqref{eq:signal-size-chisq-delta}, after some simplification, yields
+	\begin{equation} \label{eq:reparametrize-2-by-2-table-3}
+	w^2 = \frac{f(1-f)\phi_1(1-\phi_1)(R-1)^2}{\left[\phi_1 R + (1-\phi_1)D\right]\left[\phi_1 + (1-\phi_1)D\right]},
+	\end{equation}
+	where $D = fR+1-f > 0$.
+	Therefore, he derivative of \eqref{eq:reparametrize-2-by-2-table-3} with respect to $\phi_1$ is
+	\begin{equation} \label{eq:signal-size-first-derivative}
+	\frac{\mathrm{d}w^2}{\mathrm{d}\phi_1} = 
+	\frac{f(1-f)(R-1)^2}{\left[\phi_1 R+(1-\phi_1)D\right]^2 \left[\phi_1+(1-\phi_1)D\right]^2} \left[(D^2-R)\phi_1^2 - 2D^2\phi_1 + D^2\right].
+	\end{equation}
+	Further, we obtain the second derivative with respect to $\phi_1$,
+	\begin{equation} \label{eq:signal-size-second-derivative}
+	\frac{\mathrm{d}^2w^2}{\mathrm{d}\phi_1^2} = 
+	h(R,f) \left[(\phi_1-1)D^2 - \phi_1R\right],
+	\end{equation}
+	where $h$ is some function of $(R,f)$ taking on strictly positive values.
+
+	Since $\left[(\phi_1-1)D^2 - \phi_1R\right]<0$, the second derivative \eqref{eq:signal-size-second-derivative} must be strictly negative on $[0,1]$.
+	This implies that the first derivative \eqref{eq:signal-size-first-derivative} is strictly decreasing on $[0,1]$. 
+	Since the first derivative \eqref{eq:signal-size-first-derivative} is strictly positive at $\phi_1=0$, and strictly negative at $\phi_1=1$, it must have a unique zero between 0 and 1, and hence, the solution to $(D^2-R)\phi_1^2 - 2D^2\phi_1 + D^2 = 0$ in the interval of $[0,1]$ must be the maximizer of \eqref{eq:reparametrize-2-by-2-table-3} --- when $D^2-R>0$, the smaller of the two roots maximizes \eqref{eq:reparametrize-2-by-2-table-3}, and when $D^2-R<0$, it is the larger of the two.
+	They share the same expression ${D}/{(D+\sqrt{R})}$, which coincides with \eqref{eq:optimal-design}.
+	Finally, when $D^2=R$, the only root $\phi_1^*=1/2$, which also coincides with \eqref{eq:optimal-design}, is the maximizer of \eqref{eq:reparametrize-2-by-2-table-3}.
+\end{proof}
 

### 2021-02-01 6.GWAS/6.proofs-GWAS.tex
move proofs of GWAS results: 1. move proofs of phase transition results to appendix. 2. move proofs of results on signal sizes in text

@@
 
-\subsection{Auxiliary facts of chi-square distributions}
+\section{Auxiliary facts of chi-square distributions}
 \label{sec:chi-square-distributions}
@@
 
-\subsection{Proof of Theorem \ref{thm:chi-squared-exact-boundary}}
+\section{Proof of Theorem \ref{thm:chi-squared-exact-boundary}}
 \label{subsec:proof-chi-squared-exact-boundary}
@@
 
-\subsection{Proof of Theorem \ref{thm:chi-squared-approx-boundary}}
+\section{Proof of Theorem \ref{thm:chi-squared-approx-boundary}}
 \label{subsec:proof-chi-squared-approx-boundary}
@@
 
-\subsection{Proof of Theorems \ref{thm:chi-squared-exact-approx-boundary} and \ref{thm:chi-squared-approx-exact-boundary}}
+\section{Proof of Theorems \ref{thm:chi-squared-exact-approx-boundary} and \ref{thm:chi-squared-approx-exact-boundary}}
 \label{subsec:proof-chi-squared-mix-boundaries}
@@
 \end{proof}
-
-\subsection{Proof of Proposition \ref{prop:signal-size-odds-ratio} and Corollary \ref{cor:signal-limits-OR}}
-\label{subsec:proof-signal-size-odds-ratio}
-
-\begin{proof}[Proof of Proposition \ref{prop:signal-size-odds-ratio} and Corollary \ref{cor:signal-limits-OR}]
-We parametrize the 2-by-2 multinomial distribution with the parameter $\delta$, 
-\begin{equation} \label{eq:reparametrize-2-by-2-table-1}
-    \mu_{11} = \phi_1\theta_1+\delta,\quad 
-    \mu_{12} = \phi_1\theta_2-\delta,\quad 
-    \mu_{21} = \phi_2\theta_1-\delta,\quad 
-    \mu_{22} = \phi_2\theta_2+\delta.
-\end{equation}
-By relabelling of categories, we may assume $0<\theta_1,\phi_1\le1/2$ without loss of generality.
-Note that $\delta$ must lie within the range $[\delta_\mathrm{min}, \delta_\mathrm{max}]$, where
-$$
-\delta_\mathrm{min} := \max\{-\phi_1\theta_1, -\phi_2\theta_2, \phi_1\theta_2-1, \phi_2\theta_1-1\} 
-= -\phi_1\theta_1,
-$$
-and
-$$
-\delta_\mathrm{max} := \min\{1-\phi_1\theta_1, 1-\phi_2\theta_2, \phi_1\theta_2, \phi_2\theta_1\}
-= \min\{\phi_1\theta_2, \phi_2\theta_1\},
-$$
-in order for $\mu_{ij}\ge0$ for all $i,j\in \{1,2\}$.
-Under this parametrization, Relation \eqref{eq:odds-ratio} then becomes
-\begin{equation} \label{eq:odds-ratio-delta}
-    \text{R} = \frac{\mu_{11}\mu_{22}}{\mu_{12}\mu_{21}}
-    = \frac{\phi_1\theta_1\phi_2\theta_2 + \delta(\phi_1\theta_1+\phi_2\theta_2)+\delta^2}{\phi_1\theta_1\phi_2\theta_2 - \delta(\phi_1\theta_2+\phi_2\theta_1)+\delta^2},
-\end{equation}
-which is one-to-one and increasing in $\delta$ on $(\delta_\mathrm{min}, \delta_\mathrm{max})$.
-Equation \eqref{eq:signal-size-chisq} becomes
-\begin{equation} \label{eq:signal-size-chisq-delta}
-w^2 = \sum_{i=1}^2 \sum_{j=1}^2 \frac{(\mu_{ij} - \phi_i\theta_j)^2}{\phi_i\theta_j}
-= \delta^2\sum_i\sum_j \frac{1}{\phi_i\theta_j}
-= \frac{\delta^2}{\phi_1\theta_1\phi_2\theta_2},
-\end{equation}
-Solving for $\delta$ in \eqref{eq:odds-ratio-delta}, and plugging into the expression for signal size \eqref{eq:signal-size-chisq-delta} yields Relation \eqref{eq:signal-size-odds-ratio}.
-Corollary \ref{cor:signal-limits-OR} follows from the fact that $w^2(\delta)$ is decreasing on $[\delta_\mathrm{min},0)$, increasing on $(0,\delta_\mathrm{max}]$, with limits
-$$
-\lim_{d\to \delta_\mathrm{min}} w^2(\delta) = \frac{\phi_1\theta_1}{\phi_2\theta_2},
-\quad
-\text{and}
-\quad
-\lim_{d\to \delta_\mathrm{max}} w^2(\delta) = \min\left\{\frac{\phi_1\theta_2}{\phi_2\theta_1}, \frac{\phi_2\theta_1}{\phi_1\theta_2}\right\}.
-$$
-The other three cases ($1/2\le\theta_1,\phi_1\le1$; $0<\theta_1\le1/2\le\phi_1\le1$; and $0\le\phi_1\le1/2\le\theta_1\le1$) may be obtained similarly, or by appealing to the symmetry of the problem.
-\end{proof}
-
-\begin{proof}[Proof of Corollary \ref{cor:optimal-design}]
-Using the parametrization in \eqref{eq:reparametrize-2-by-2-table-1} and in Corollary \ref{cor:signal-size-odds-ratio-conditional-frequency}, we solve for $\delta$ in \eqref{eq:odds-ratio-delta} to obtain
-\begin{align}
-    \delta &= \frac{\phi_1 fR}{fR+1-f} - \left(\frac{\phi_1 fR}{fR+1-f} + f(1-\phi_1)\right)\phi_1 \nonumber \\
-    &= \frac{f(1-f)\phi_1(1-\phi_1)(R-1)}{fR+1-f}. \label{eq:reparametrize-2-by-2-table-2}
-\end{align}
-Substituting \eqref{eq:reparametrize-2-by-2-table-2} into the expression \eqref{eq:signal-size-chisq-delta}, after some simplification, yields
-\begin{equation} \label{eq:reparametrize-2-by-2-table-3}
-    w^2 = \frac{f(1-f)\phi_1(1-\phi_1)(R-1)^2}{\left[\phi_1 R + (1-\phi_1)D\right]\left[\phi_1 + (1-\phi_1)D\right]},
-\end{equation}
-where $D = fR+1-f > 0$.
-Therefore, he derivative of \eqref{eq:reparametrize-2-by-2-table-3} with respect to $\phi_1$ is
-\begin{equation} \label{eq:signal-size-first-derivative}
-    \frac{\mathrm{d}w^2}{\mathrm{d}\phi_1} = 
-    \frac{f(1-f)(R-1)^2}{\left[\phi_1 R+(1-\phi_1)D\right]^2 \left[\phi_1+(1-\phi_1)D\right]^2} \left[(D^2-R)\phi_1^2 - 2D^2\phi_1 + D^2\right].
-\end{equation}
-Further, we obtain the second derivative with respect to $\phi_1$,
-\begin{equation} \label{eq:signal-size-second-derivative}
-    \frac{\mathrm{d}^2w^2}{\mathrm{d}\phi_1^2} = 
-    h(R,f) \left[(\phi_1-1)D^2 - \phi_1R\right],
-\end{equation}
-where $h$ is some function of $(R,f)$ taking on strictly positive values.
-
-Since $\left[(\phi_1-1)D^2 - \phi_1R\right]<0$, the second derivative \eqref{eq:signal-size-second-derivative} must be strictly negative on $[0,1]$.
-This implies that the first derivative \eqref{eq:signal-size-first-derivative} is strictly decreasing on $[0,1]$. 
-Since the first derivative \eqref{eq:signal-size-first-derivative} is strictly positive at $\phi_1=0$, and strictly negative at $\phi_1=1$, it must have a unique zero between 0 and 1, and hence, the solution to $(D^2-R)\phi_1^2 - 2D^2\phi_1 + D^2 = 0$ in the interval of $[0,1]$ must be the maximizer of \eqref{eq:reparametrize-2-by-2-table-3} --- when $D^2-R>0$, the smaller of the two roots maximizes \eqref{eq:reparametrize-2-by-2-table-3}, and when $D^2-R<0$, it is the larger of the two.
-They share the same expression ${D}/{(D+\sqrt{R})}$, which coincides with \eqref{eq:optimal-design}.
-Finally, when $D^2=R$, the only root $\phi_1^*=1/2$, which also coincides with \eqref{eq:optimal-design}, is the maximizer of \eqref{eq:reparametrize-2-by-2-table-3}.
-\end{proof}

### 2021-02-01 3.phase_transitions/3.Gaussian-support-recovery.tex
merge of Ch. 3 and the new Ch. 4 & 5
I merged my work on Ch 3 and Ch. 4&5 with the "revision-GWAS" branch.

Need some more work -- putting the Mill's ratio in Ch 2 perhaps...

@@
-Turning to support recovery problems in the Gaussian error model \eqref{eq:model-additive-Chapter3},
-we will analyze the asymptotic performance limits in terms of the risk metrics for exact, exact-approximate, approximate-exact support recovery problems (i.e., \eqref{eq:risk-exact}, \eqref{eq:risk-exact-approx}, and \eqref{eq:risk-approx-exact}, respectively), as well as the probability of support recovery \eqref{eq:risk-prob}.
-We will also review the recent result for exact support recovery risk \eqref{eq:risk-approximate} by \cite{arias2017distribution}, to reveal a rather complete landscape of support recovery problems in high-dimensional Gaussian error models.
+Turning to support recovery problems in the Gaussian error model \eqref{eq:model-additive-Chapter3}, in the rest of this chapter
+we will analyze the asymptotic performance limits in terms of the risk metrics for exact, exact-approximate, approximate-exact support recovery problems (i.e., \eqref{eq:risk-exact}, \eqref{eq:risk-exact-approx}, and \eqref{eq:risk-approx-exact}, respectively), as well as the probability of support recovery
+\eqref{eq:risk-prob}.  We will also review the recent result for exact support recovery risk \eqref{eq:risk-approximate} by \cite{arias2017distribution}, to 
+reveal a rather complete landscape of support recovery problems in high-dimensional Gaussian error models.
 
-We restrict our attention to the class of thresholding procedures in this section.
-Specifically, the lower bounds that we develop in Theorems \ref{thm:Gaussian-error-exact-boundary} through \ref{thm:Gaussian-error-approx-exact-boundary} below are only meant to apply to thresholding procedures.
-Although it is intuitively appealing to consider only data-thresholding procedures in multiple testing problems, such procedures are not always optimal in more general settings. 
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.7\textwidth]{./figures/phase_diagram_Gaussian_ALL_boundaries.eps}
+  \end{center}
+   \caption{The phase diagram of support recovery problems for the high-dimensional model \eqref{eq:model-additive-Chapter3}, illustrating the boundaries of the exact support recovery (FWER + FWNR; top curve; Theorem \ref{thm:Gaussian-error-exact-boundary}), the approximate-exact support recovery (FDR + FWNR; second curve from top; Theorem \ref{thm:Gaussian-error-approx-exact-boundary}), the exact-approximate support recovery (FWER + FNR; horizontal line $r=1$; Theorem \ref{thm:Gaussian-error-exact-approx-boundary}), and the approximate support recovery problems (FDR + FNR; tilted line $r=\beta$; Theorem \ref{thm:Gaussian-error-approx-boundary}).
+The signal detection problem (Type I + Type II errors of the global test; lower curve) was studied in Donoho and Jin (2004).
+In each region of the diagram and above, the annotated statistical risk can be made to vanish, as dimension $p$ diverges.
+Conversely, the risks has liminf at least one.}
+   \label{fig:phase-Gaussian-errors}
+\end{figure}
+
+In the rest of this chapter, we restrict our attention to the class of thresholding procedures. Specifically, the lower bounds that we develop in 
+Theorems \ref{thm:Gaussian-error-exact-boundary} through \ref{thm:Gaussian-error-approx-exact-boundary} below are only meant to apply to thresholding
+ procedures.  Although it is intuitively appealing to consider only data-thresholding procedures in multiple testing problems, such procedures are not always optimal in more general settings. 
 % Recently, \cite{arias2019detection} showed that thresholding procedures are in fact sub-optimal in the additive models \eqref{eq:model-additive} when errors have heavy (regularly-varying) tails. 
@@
 % The optimality of data-thresholding procedures in terms of other statistical risks is an open problem that invites a dedicated investigation in a future study.
-The optimality of thresholding procedures and the consequences of this restriction will be treated in Chapter \ref{chap:exact-support-recovery}.
+The optimality of thresholding procedures and the consequences of this restriction will be treated in Chapter \ref{chap:optimality}.
 
-\medskip
-
-A technical ingredient is needed in order to state our main results.
+\stilian{
+Figure \ref{fig:phase-Gaussian-errors} illustrates the rich landscape of phase transitions in support recovery for the various choices
+of statistical risk for the family of thresholding estimators, established in the following sections.}{\fbox{ added these words and moved the figure here}}
+We end this brief overview with a technical notion needed in order to state our main results.
 We define a rate at which the nominal levels of FWER or FDR go to zero.
@@
 
-\subsection{The exact support recovery problem}
+\section{The exact support recovery problem}
 \label{subsec:exact-support-recovery-Gaussian}
@@
 The function \eqref{eq:strong-classification-boundary-Gaussian} characterizes the phase transition of the exact support recovery problem.
-Specifically, if $\underline{r} > {{g}}(\beta)$, then Bonferroni's, Sid\'ak's, Holm's, and Hochberg's procedures with slowly vanishing  nominal FWER levels (as defined in Definition \ref{def:slowly-vanishing}) all achieve asymptotically exact support recovery in the sense of \eqref{eq:support-recovery-success}.
+Namely, the following two results hold.\\
 
-Conversely, if $\overline{r} < {{g}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, we have $\P[\widehat{S}_p=S_p]\to0$.
+{\rm (i)} If $\underline{r} > {{g}}(\beta)$, then Bonferroni's, Sid\'ak's, Holm's, and Hochberg's procedures with slowly vanishing  nominal FWER levels 
+(as defined in Definition \ref{def:slowly-vanishing}) all achieve asymptotically exact support recovery in the sense of \eqref{eq:support-recovery-success}. \\
+
+{\rm (ii)} Conversely, if $\overline{r} < {{g}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, we have $\P[\widehat{S}_p=S_p]\to0$.
 Therefore, in view of Lemma \ref{lemma:risk-exact-recovery-probability}, exact support recovery asymptotically fails for all thresholding procedures in the sense of \eqref{eq:support-recovery-failure}.
@@
 
-We visualize the result in a $\beta$-$r$ phase diagram in Figure \ref{fig:phase-Gaussian-errors}.
+We illustrate this result with a $\beta$-$r$ phase diagram in Figure \ref{fig:phase-Gaussian-errors}.  Theorem \ref{thm:Gaussian-error-exact-boundary} is in 
+fact a special case of the more general Theorem \ref{thm:sufficient}, below, which covers dependent as well as Gaussain and non-Gaussian errors.
+We will study the {\em exact support recovery} problem in greater detail and generality in Chapter \ref{chap:exact-support-recovery}.
 
-Theorem \ref{thm:Gaussian-error-exact-boundary} is in fact a special case of the more general Theorem \ref{thm:sufficient} which covers dependent and non-Gaussian errors.
-We will study the exact support recovery problem in greater detail, and prove the more general version of the Theorem in Chapter \ref{chap:exact-support-recovery}.
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.7\textwidth]{./figures/phase_diagram_Gaussian_ALL_boundaries.eps}
-  \end{center}
-   \caption{The phase diagram of support recovery problems for the high-dimensional chi-square model \eqref{eq:model-additive-Chapter3}, illustrating the boundaries of the exact support recovery (FWER + FWNR; top curve; Theorem \ref{thm:Gaussian-error-exact-boundary}), the approximate-exact support recovery (FDR + FWNR; second curve from top; Theorem \ref{thm:Gaussian-error-approx-exact-boundary}), the exact-approximate support recovery (FWER + FNR; horizontal line $r=1$; Theorem \ref{thm:Gaussian-error-exact-approx-boundary}), and the approximate support recovery problems (FDR + FNR; tilted line $r=\beta$; Theorem \ref{thm:Gaussian-error-approx-boundary}).
-The signal detection problem (Type I + Type II errors of the global test; lower curve) was studied in Donoho and Jin (2004).
-In each region of the diagram and above, the annotated statistical risk can be made to vanish, as dimension $p$ diverges.
-Conversely, the risks has liminf at least one.}
-   \label{fig:phase-Gaussian-errors}
-\end{figure}
-
-\subsection{The approximate support recovery problem}
+\section{The approximate support recovery problem}
 \label{subsec:approx-support-recovery-Gaussian}
@@
 We generalize the main results of \citet{arias2017distribution} to allow for unequal signal sizes. 
+The key to establishing this generalization is a monotonicity property of the \ac{BH} procedure, presented in the following 
+Section \ref{sec:BH-monotonicity}. Namely, the power of the \ac{BH} procedure in terms of FNR monotonically increases for stochastically 
+larger alternatives. This fact will be formalized in Lemma \ref{lemma:monotonicity-BH-procedure}, and may be of independent interest.
 
@@
 \end{equation}
-characterizes the phase transition of approximate support recovery problem.
-Specifically, if $\underline{r} > {h}(\beta)$, then the Benjamini-Hochberg procedure (defined in Section \ref{sec:statistical-procedures}) with slowly vanishing nominal FDR levels (as defined in Definition \ref{def:slowly-vanishing}) achieves asymptotically approximate support recovery in the sense of \eqref{eq:support-recovery-success}.
+characterizes the phase transition of approximate support recovery problem.  Specifically the following two results hold.\\
 
+{\rm (i)} If $\underline{r} > {h}(\beta)$, then the Benjamini-Hochberg procedure (defined in Section \ref{sec:statistical-procedures}) with slowly 
+vanishing nominal FDR levels (as defined in Definition \ref{def:slowly-vanishing}) achieves asymptotically approximate support recovery in the sense of \eqref{eq:support-recovery-success}.\\
+
+{\rm (ii)}
 Conversely, if $\overline{r} < {h}(\beta)$, then approximate support recovery asymptotically fails in the sense of \eqref{eq:support-recovery-failure} for all thresholding procedures.
@@
 
-Proof of Theorem \ref{thm:Gaussian-error-approx-boundary} is presented in Section \ref{sec:proofs}. 
-The key to proving this generalization is a monotonicity property of the \ac{BH} procedure. 
-Namely, the power of the \ac{BH} procedure in terms of FNR monotonically increases for stochastically larger alternatives.
-This fact will be formalized in Lemma \ref{lemma:monotonicity-BH-procedure}, and may be of independent interest.
+\begin{proof}[Proof of the necessary condition in Theorem \ref{thm:Gaussian-error-approx-boundary}]
+We first show part {\rm (ii)}.  That is, when $\overline{r} < \beta$, no thresholding procedure is able to achieve approximate support recovery.
+The arguments are similar to that in Theorem 1 of \cite{arias2017distribution}, although we allow for unequal signal sizes.
 
-\subsection{The exact-approximate support recovery problem}
+Denote the distributions of $\mathrm{N}(0,1)$, $\mathrm{N}(\underline{\Delta}, 1)$, and $\mathrm{N}((\overline{\Delta}, 1)$ as $F_0$, $F_{\underline{a}}$, and $F_{\overline{a}}$ respectively.
+
+% We first show the necessary condition, i.e., when $\overline{r}<\beta$, approximate support recovery cannot be achieved with any thresholding procedure.
+% In particular, we show that the liminf of the sum of FDP and NDP is at least 1.
+
+Recall that thresholding procedures are of the form
+$$
+\widehat{S}_p = \left\{i\,|\,x(i) > t_p(x)\right\}.
+$$
+Denote $\widehat{S} := \left\{i\,|\,x(i) > t_p(x)\right\}$, and $\widehat{S}(u) := \left\{i\,|\,x(i) > u\right\}$.
+For any threshold $u\ge t_p$ we must have $\widehat{S}(u)\subseteq\widehat{S}$, and hence
+\begin{equation} \label{eq:approx-boundary-proof-FDP-Gaussian}
+    \text{FDP} := \frac{|\widehat{S}\setminus{S}|}{|\widehat{S}|} \ge \frac{|\widehat{S}\setminus{S}|}{|\widehat{S}\cup{S}|} = \frac{|\widehat{S}\setminus{S}|}{|\widehat{S}\setminus{S}| + |S|} \ge
+    \frac{|\widehat{S}(u)\setminus{S}|}{|\widehat{S}(u)\setminus{S}| + |S|}.
+\end{equation}
+On the other hand, for any threshold $u\le t_p$ we must have $\widehat{S}(u)\supseteq\widehat{S}$, and hence
+\begin{equation} \label{eq:approx-boundary-proof-NDP-Gaussian}
+    \text{NDP} := \frac{|{S}\setminus\widehat{S}|}{|{S}|} \ge 
+    \frac{|{S}\setminus\widehat{S}(u)|}{|{S}|}.
+\end{equation}
+Since either $u\ge t_p$ or  $u\le t_p$ must take place, putting \eqref{eq:approx-boundary-proof-FDP-Gaussian} and \eqref{eq:approx-boundary-proof-NDP-Gaussian} together, we have
+\begin{equation} \label{eq:approx-boundary-proof-converse-1-Gaussian}
+    \text{FDP} + \text{NDP} 
+    \ge \frac{|\widehat{S}(u)\setminus{S}|}{|\widehat{S}(u)\setminus{S}|+|{S}|} \wedge \frac{|{S}\setminus\widehat{S}(u)|}{|{S}|},
+\end{equation}
+for any $u$.
+Therefore it suffices to show that for a suitable choice of $u$, the RHS of \eqref{eq:approx-boundary-proof-converse-1-Gaussian} converges to 1 in probability; the desired conclusion on FDR and FNR follows by the dominated convergence theorem.
+
+Let $t^* = \sqrt{2q\log{p}}$ for some fixed $q$, we obtain an estimate of the tail probability by Mill's ratio \eqref{eq:Mills-ratio}, 
+\begin{equation}
+    \overline{F_0}(t^*) 
+    \sim \frac{1}{t^*}\phi(t^*)
+    = \frac{1}{2\sqrt{\pi q\log{p}}} p^{-q}, \label{eq:approx-boundary-proof-null-tail-prob-Gaussian}
+\end{equation}
+where $a_p\sim b_p$ is taken to mean $a_p/b_p\to 1$.
+Observe that $|\widehat{S}(t^*)\setminus{S}|$ has distribution $\text{Binom}(p-s, \overline{F_0}(t^*))$ where $s=|S|$, denote $X = X_p := {|\widehat{S}(t^*)\setminus{S}|}/{|S|}$, and we have 
+$$
+\mu := \E\left[X\right] = \frac{(p-s)\overline{F_0}(t^*)}{s},
+\quad \text{and} \quad
+\var\left(X\right) = \frac{(p-s)\overline{F_0}(t^*){F_0}(t^*)}{s^2} \le \mu/s.
+$$
+Therefore for any $M>0$, we have, by Chebyshev's inequality,
+\begin{equation}
+    \P\left[X < M\right] 
+    \le \P\left[\left|X-\mu\right| > \mu - M\right]
+    \le \frac{\mu/s}{(\mu-M)^2}
+    = \frac{1/(\mu s)}{(1-M/\mu)^2}. \label{eq:approx-boundary-proof-converse-2-Gaussian}
+\end{equation}
+Now, from the expression of $\overline{F_0}(t^*)$ in \eqref{eq:approx-boundary-proof-null-tail-prob-Gaussian}, we obtain
+$$
+\mu = (p^\beta - 1)\overline{F_0}(t^*) \sim \frac{1}{2\sqrt{\pi q\log{p}}} p^{\beta-q}.
+$$
+Since $\overline{r}<\beta$, we can pick $q$ such that $\overline{r}<q<\beta$. 
+In turn, we have $\mu \to\infty$, as $p\to\infty$.
+Therefore the last expression in \eqref{eq:approx-boundary-proof-converse-2-Gaussian} converges to 0, and we conclude that $X\to\infty$ in probability, and hence
+\begin{equation} \label{eq:approx-boundary-proof-converse-3-Gaussian}
+\frac{|\widehat{S}(t^*)\setminus{S}|}{|\widehat{S}(t^*)\setminus{S}|+|{S}|} 
+= \frac{X}{X+1} \to 1 \quad \text{in probability}.
+\end{equation}
+
+On the other hand, we show that with the same choice of $u = t^*$, we have,
+\begin{equation} \label{eq:approx-boundary-proof-converse-4-Gaussian}
+    \frac{|{S}\setminus\widehat{S}(t^*)|}{|{S}|}\to 1 \quad \text{in probability}.
+\end{equation}
+By the stochastic monotonicity of Gaussian location family \eqref{eq:stochastic-monotonicity-Gaussian}, we have the following lower bound for the probability of missed detection for each signal $\mu(i)$, $i\in S$,
+\begin{equation} \label{eq:approx-boundary-proof-converse-5-Gaussian}
+    \P[\mathrm{N}(\mu(i), 1) \le t^*] \ge F_{\overline{a}}(t^*).
+\end{equation}
+Since $|{S}\setminus\widehat{S}(t^*)|$ can be written as the sum of $s$ independent Bernoulli random variables,
+\begin{equation*}
+    |{S}\setminus\widehat{S}(t^*)| = \sum_{i\in S} \mathbbm{1}_{(-\infty, t^*]}(x(i)),
+\end{equation*}
+using with \eqref{eq:approx-boundary-proof-converse-5-Gaussian}, we conclude that $|{S}\setminus\widehat{S}(t^*)| \stackrel{\mathrm{d}}{\ge} \text{Binom}(s, {F_{\overline{a}}}(t^*))$.
+Finally, we know that ${F_{\overline{a}}}(t^*)$ converges to 1 by our choice of diverging $t^*$, and the necessary condition is shown.
+\end{proof}
+
+\begin{proof}[Proof of the sufficient condition in Theorem \ref{thm:Gaussian-error-approx-boundary}]
+We now turn to the sufficient condition, i.e., part {\rm (i)}. That is, when $\underline{r} > \beta$, the Benjamini-Hochberg procedure with 
+slowly vanishing FDR levels achieves asymptotic approximate support recovery.
+
+The FDR vanishes by our choice of $\alpha$ and the FDR-controlling property of the BH procedure \citep{benjamini1995controlling}.
+It only remains to show that FNR also vanishes.
+
+To do so we compare the FNR under the alternative specified in Theorem \ref{thm:Gaussian-error-approx-boundary} to one with all of the signal sizes equal to $\underline{\Delta}$.
+By Lemma \ref{lemma:monotonicity-BH-procedure}, it suffices to show that the FNR under the BH procedure in this setting vanishes.
+Let $x(i)$ be vectors of independent observations with $p-s$ nulls having standard Gaussian distributions, and $s$ signals having $\mathrm{N}(\underline{\Delta}, 1)$ distributions.
+
+Denote the null and the alternative distributions as $F_0$ and $F_{a}$ respectively.
+Let $\widehat{G}$ denote the empirical survival function as in \eqref{eq:empirical-tail-distribution}.
+Define the empirical survival functions for the null part and signal part
+\begin{equation} \label{eq:empirical-survival-null-signal-Gaussian}
+    \widehat{W}_\text{null}(t) = \frac{1}{p-s}\sum_{i\not\in S}\mathbbm{1}\{x(i) \ge t\},
+    \quad
+    \widehat{W}_\text{signal}(t) = \frac{1}{s}\sum_{i\in S}\mathbbm{1}\{x(i) \ge t\},
+\end{equation}
+where $s=|S|$, so that
+$$
+\widehat{G}(t) = \frac{p-s}{p}\widehat{W}_\text{null}(t) + \frac{s}{p}\widehat{W}_\text{signal}(t).
+$$
+
+We need the following result to describe the deviations of the empirical distributions.
+\begin{lemma}[Theorem 1 of \citet{eicker1979asymptotic}] \label{lemma:empirical-process}
+Let $Z_1,\ldots,Z_k$ be iid with continuous survival function $Q$.
+Let $\widehat{Q}_k$ denote their empirical survival function and define 
+$\xi_k = \sqrt{2\log{\log{(k)}}/k}$ for $k \ge 3$. 
+Then
+$$
+\frac{1}{\xi_k}\sup_z\frac{|\widehat{Q}_k(z) - Q(z)|}{\sqrt{Q(z)(1 - Q(z))}} \to 1,
+$$
+in probability as $k \to \infty$.
+In particular,
+$$
+\widehat{Q}_k(z) = Q(z) + O_\P\left(\xi_k\sqrt{Q(z)(1 - Q(z))}\right),
+$$
+uniformly in z.
+\end{lemma}
+
+Apply Lemma \ref{lemma:empirical-process} to the two summands in $\widehat{G}$, we obtain
+$\widehat{G}(t) = G(t) + \widehat{R}(t)$,
+where 
+\begin{equation} \label{eq:empirical-process-mean-Gaussian}
+    G(t) = \frac{p-s}{p}\overline{F_0}(t) + \frac{s}{p}\overline{F_a}(t),
+\end{equation}
+and 
+\begin{equation} \label{eq:empirical-process-residual-Gaussian}
+    \widehat{R}(t) = O_\P\left(\xi_p\sqrt{\overline{F_0}(t)F_0(t)} + \frac{s}{p}\xi_s\sqrt{\overline{F_a}(t)F_a(t)}\right),
+\end{equation}
+uniformly in $t$.
+
+Recall (see proof of Lemma \ref{lemma:monotonicity-BH-procedure}) that the BH procedure is the thresholding procedure with threshold set at 
+\begin{equation} \label{eq:approx-boundary-proof-tau-Gaussian}
+    \tau = \inf\{t\,|\,\overline{F_0}(t)\le\alpha\widehat{G}(t)\}. 
+    %= \min\{t\,|\,\overline{F_0}(t)=\alpha\widehat{G}(t)\}.
+\end{equation}
+The NDP may also be re-written as 
+$$
+\text{NDP} = \frac{|{S}\setminus\widehat{S}|}{|{S}|} = \frac{1}{s}\sum_{i\in S}\mathbbm{1}\{x(i) < \tau\} = 1 - \widehat{W}_\text{signal}(\tau),
+$$
+so that it suffices to show that 
+\begin{equation} \label{eq:approx-boundary-proof-sufficient-1-Gaussian}
+    \widehat{W}_\text{signal}(\tau)\to 1
+\end{equation} in probability.
+Applying Lemma \ref{lemma:empirical-process} to $\widehat{W}_\text{signal}$, we know that 
+$$
+\widehat{W}_\text{signal}(\tau) = \overline{F_a}(\tau) + O_\P\left(\xi_s\sqrt{\overline{F_a}(\tau)F_a(\tau)}\right) = \overline{F_a}(\tau) + o_\P(1).
+$$
+So it suffices to show that $F_a(\tau)\to 0$ in probability.
+Now let $t^* = \sqrt{2q\log(p)}$ for some $q$ such that $\beta<q<\underline{r}$.
+We have 
+\begin{equation} \label{eq:approx-boundary-proof-sufficient-2-Gaussian}
+    F_a(t^*) 
+    = \Phi(t^* - \underline{\Delta}) 
+    = \Phi(\sqrt{2(q - \underline{r})\log{p}}) \to 0. 
+\end{equation}
+Hence in order to show \eqref{eq:approx-boundary-proof-sufficient-1-Gaussian}, it suffices to show 
+\begin{equation} \label{eq:approx-boundary-proof-sufficient-3-Gaussian}
+    \P\left[\tau \le t^*\right] \to 1.
+\end{equation}
+By \eqref{eq:empirical-process-mean-Gaussian}, the mean of the empirical process $\widehat{G}$ evaluated at $t^*$ is
+\begin{equation} \label{eq:approx-boundary-proof-sufficient-4-Gaussian}
+    G(t^*) = \frac{p-s}{p}\overline{F_0}(t^*) + \frac{s}{p}\overline{F_a}(t^*).
+\end{equation}
+The first term, using Relation \eqref{eq:approx-boundary-proof-null-tail-prob-Gaussian}, is asymptotic to $p^{-q}L(p)$, where $L(p)$ is the logarithmic term in $p$.
+The second term, since $\overline{F_a}(t^*)\to 1$ by Relation \eqref{eq:approx-boundary-proof-sufficient-2-Gaussian}, is asymptotic to $p^{-\beta}$.
+Therefore, $G(t^*) \sim p^{-q}L(p) + p^{-\beta} \sim p^{-\beta}$, since 
+$p^{\beta-q}L(p)\to0$ where $q>\beta$.
+
+The fluctuation of the empirical process at $t^*$, by Relation \eqref{eq:empirical-process-residual-Gaussian}, is 
+\begin{align*}
+    \widehat{R}(t^*) 
+    &= O_\P\left(\xi_p\sqrt{\overline{F_0}(t^*)F_0(t^*)} + \frac{s}{p}\xi_s\sqrt{\overline{F_a}(t^*)F_a(t^*)}\right)\\
+    &= O_\P\left(\xi_p\sqrt{\overline{F_0}(t^*)}\right) + o_\P\left(p^{-\beta}\right).
+\end{align*}
+By \eqref{eq:approx-boundary-proof-null-tail-prob-Gaussian} and the expression for $\xi_p$, the first term is $O_\P\left(p^{-(q+1)/2}L(p)\right)$ where $L(p)$ is a poly-logarithmic term in $p$.
+Since $\beta<\min\{q,1\}$, we have $\beta<(q+1)/2$, and hence $\widehat{R}(t^*) = o_\P(p^{-\beta})$.
+
+Putting the mean and the fluctuation of $\widehat{G}(t^*)$ together, we obtain
+$$
+\widehat{G}(t^*) = G(t^*) + \widehat{R}(t^*) \sim_\P G(t^*) \sim p^{-\beta},
+$$
+and therefore, together with \eqref{eq:approx-boundary-proof-null-tail-prob-Gaussian}, we have
+$$
+\overline{F_0}(t^*)/\widehat{G}(t^*) = p^{\beta-q}L(p)(1+o_{\P}(1)),
+$$
+which is eventually smaller than the FDR level $\alpha$ by the assumption \eqref{eq:slowly-vanishing-error} and the fact that $\beta<q$.
+That is, 
+$$
+\P\left[\overline{F}_0(t^*) / \widehat{G}(t^*) < \alpha\right] \to 1.
+$$
+By definition of $\tau$ (recall \eqref{eq:approx-boundary-proof-tau-Gaussian}), this implies that $\tau \le t^*$ with probability tending to 1, and \eqref{eq:approx-boundary-proof-sufficient-3-Gaussian} is shown.
+The proof for the sufficient condition is complete.
+\end{proof}
+
+\section{Monotonicity of the Benjamini-Hochberg procedure}
+\label{sec:BH-monotonicity}
+\input{3.phase_transitions/3.BH_monotonicity.tex}
+
+\section{The exact-approximate support recovery problem}
 \label{subsec:exact-approx-support-recovery-Gaussian}
@@
 \end{equation}
-characterizes the phase transition of exact-approximate support recovery problem.
-Specifically, if $\underline{r} > \widetilde{g}(\beta)$, then the procedures listed in Theorem \ref{thm:Gaussian-error-exact-boundary} with slowly vanishing nominal FWER levels (as defined in Definition \ref{def:slowly-vanishing}) achieve asymptotically exact-approximate support recovery in the sense of \eqref{eq:support-recovery-success}.
+characterizes the phase transition of exact-approximate support recovery problem.  Namely, the following two results hold.\\
 
-Conversely, if $\overline{r} < \widetilde{g}(\beta)$, then for any thresholding procedure $\widehat{S}$, the exact-approximate support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
+{\rm (i)} If $\underline{r} > \widetilde{g}(\beta)$, then the procedures listed in Theorem \ref{thm:Gaussian-error-exact-boundary} with slowly vanishing nominal FWER levels (as defined in Definition \ref{def:slowly-vanishing}) achieve asymptotically exact-approximate support recovery in the sense of \eqref{eq:support-recovery-success}.
+\\
+
+{\rm (ii)} Conversely, if $\overline{r} < \widetilde{g}(\beta)$, then for any thresholding procedure $\widehat{S}$, the exact-approximate support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
 \end{theorem}
 
-Theorem \ref{thm:Gaussian-error-exact-approx-boundary} is proved in Section \ref{sec:proofs}. 
-The phase transition boundary \eqref{eq:exact-approx-boundary-Gaussian} is visualized in Figure \ref{fig:phase-Gaussian-errors}.
+The phase transition boundary \eqref{eq:exact-approx-boundary-Gaussian} is visualized in Figure \ref{fig:phase-Gaussian-errors}. The proof of this result
+uses ideas from the proof of Theorem \ref{thm:Gaussian-error-approx-boundary} and is substantially shorter.
+
+\begin{proof}[Theorem \ref{thm:Gaussian-error-exact-approx-boundary}]
+We first show the sufficient condition. 
+Vanishing FWER is guaranteed by the properties of the procedures, and we only need to show that FNR also goes to zero. 
+Similar to the proof of Theorem \ref{thm:Gaussian-error-approx-boundary}, it suffices to show that
+\begin{equation} \label{eq:additive-error-exact-approx-boundary-proof-sufficient-1}
+    \text{NDP} = 1 - \widehat{W}_\text{signal}(t_p) \to 0,
+\end{equation}
+where $t_p$ is the threshold of Bonferroni's procedure.
+
+Since $\alpha$ vanishes slowly (see Definition \ref{eq:slowly-vanishing-error}), for any $\delta>0$, we have $p^{-\delta}=o(\alpha)$.
+Therefore, we have $-\log\alpha\le\delta\log{p}$ for large $p$, and
+\begin{equation*} 
+    1 \le \limsup_{p\to\infty}\frac{2\log{p} - 2\log{\alpha}}{2\log{p}} \le 1+\delta,
+\end{equation*}
+for any $\delta>0$.
+Therefore, by the expression for normal quantiles, we know that 
+$$
+t_p=F^\leftarrow(1-\alpha/p)\sim(2\log{p}-2\log{\alpha})^{1/2} \sim(2\log{p})^{1/2}.
+$$
+
+Since $\underline{r}>\widetilde{g}(\beta)=1$, we can pick $q$ such that $1<q<\underline{r}$.
+Let $t^* = \sqrt{2q\log{p}}$, we know that $t_p<t_p^*$ for large $p$.
+Therefore for large $p$, we have
+$$
+\widehat{W}_\text{signal}(t_p) \ge \widehat{W}_\text{signal}(t^*) \ge \overline{F_a}(t^*) + o_\P(1),
+$$
+where $\overline{F_a}$ is the survival function of $\mathrm{N}(\sqrt{2\underline{r}\log{p}}, 1)$; the last inequality follows from the stochastic monotonicity of the Gaussian location family \eqref{eq:stochastic-monotonicity-Gaussian}, and Lemma \ref{lemma:empirical-process}.
+Indeed, by our choice of $q<\underline{r}$, we obtain
+$$
+F_a(t^*) = \Phi\left(\sqrt{2(q-\underline{r})\log{p}}\right)\to0,
+$$
+and \eqref{eq:additive-error-exact-approx-boundary-proof-sufficient-1} is shown. 
+This completes the proof of the sufficient condition.
+
+The proof of the necessary condition follows similar structure as in the proof of Theorem \ref{thm:Gaussian-error-approx-boundary}, and uses the lower bound
+\begin{equation} \label{eq:additive-error-exact-approx-boundary-proof-necessary-1}
+    \mathrm{FWER}(\mathcal{R}) + \mathrm{FNR}(\mathcal{R}) \ge \P\left[\max_{i\in S^c}x(i)>u\right] \wedge \E\left[\frac{|S\setminus \widehat{S}(u)|}{|S|}\right],
+\end{equation}
+which holds for any arbitrary thresholding procedure $\mathcal{R}$ and arbitrary real $u\in\R$.
+
+By the assumption that $\overline{r}<\widetilde{g}(\beta)=1$, we can pick $q$ such that $\overline{r}<q<1$ and let $u = t^*=\sqrt{2q\log{p}}$ in \eqref{eq:additive-error-exact-approx-boundary-proof-necessary-1}.
+By relative stability of iid Gaussian random variables \eqref{eq:relative-stability-Gaussian-maxima}, we have
+\begin{equation} \label{eq:additive-error-exact-approx-boundary-proof-necessary-2}
+    \P\left[\frac{\max_{i\in S^c} x(i)}{\sqrt{2\log{p}}} > \frac{t^*}{\sqrt{2\log{p}}}\right] \to 1.
+\end{equation}
+since the first fraction in \eqref{eq:additive-error-exact-approx-boundary-proof-necessary-2} converges to 1, while the second converges to $q<1$.
+Therefore, the first term on the right-hand side of \eqref{eq:additive-error-exact-approx-boundary-proof-necessary-1} converges to 1.
+
+On the other hand, by the stochastic monotonicity of Gaussian location family \eqref{eq:stochastic-monotonicity-Gaussian}, the probability of missed detection for each signal is lower bounded by $\P[Z+\mu(i) \le t^*] \ge F_{\overline{a}}(t^*)$, where $Z$ is a standard Gaussian r.v., and $F_{\overline{a}}$ is the cdf of $\mathrm{N}(\sqrt{2\overline{r}\log{p}}, 1)$.
+Therefore, $|{S}\setminus\widehat{S}(t^*)| \stackrel{\mathrm{d}}{\ge} \text{Binom}(s, {F_{\overline{a}}}(t^*))$, and it suffices to show that ${F_{\overline{a}}}(t^*)$ converges to 1.
+Indeed,
+\begin{equation*}
+    {F_{\overline{a}}}(t^*) = \Phi(\sqrt{2(q-\overline{r})\log{p}}) \to 1,
+\end{equation*}
+by our choice of $q>\overline{r}$.
+Hence both quantities in the minimum on the right-hand side of \eqref{eq:additive-error-exact-approx-boundary-proof-necessary-1} converge to 1 in the limit, and the necessary condition is shown.
+\end{proof}
 
 \begin{remark}
-Boundary \eqref{eq:exact-approx-boundary-Gaussian} was briefly suggested by \citet{arias2017distribution}.
+The boundary \eqref{eq:exact-approx-boundary-Gaussian} was briefly suggested by \citet{arias2017distribution}.
 Unfortunately, it was falsely claimed that the boundary characterized the phase transition of the \emph{exact} support recovery problem, and the alleged proof was left as an ``exercise to the reader''.
@@
 
-\subsection{The approximate-exact support recovery problem}
+\section{The approximate-exact support recovery problem}
 \label{subsec:aprox-exact-support-recovery-Gaussian}
@@
 \end{equation}
-characterizes the phase transition of approximate-exact support recovery problem.
-Specifically, if $\underline{r} > \widetilde{h}(\beta)$, then the Benjamini-Hochberg procedure with slowly vanishing nominal FDR levels (as defined in Definition \ref{def:slowly-vanishing}) achieves asymptotically approximate-exact support recovery in the sense of \eqref{eq:support-recovery-success}.
+characterizes the phase transition of approximate-exact support recovery problem.  Namely, the following two results 
+hold.\\
 
-Conversely, if $\overline{r} < \widetilde{h}(\beta)$, then for any thresholding procedure $\widehat{S}$, the approximate-exact support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
+{\rm (i)} If $\underline{r} > \widetilde{h}(\beta)$, then the Benjamini-Hochberg procedure with slowly vanishing nominal FDR levels (as defined in Definition \ref{def:slowly-vanishing}) achieves asymptotically approximate-exact support recovery in the sense of \eqref{eq:support-recovery-success}.
+\\
+
+{\rm (ii)} Conversely, if $\overline{r} < \widetilde{h}(\beta)$, then for any thresholding procedure $\widehat{S}$, the approximate-exact support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
 \end{theorem}
 
-Theorem \ref{thm:Gaussian-error-approx-exact-boundary} is proved in Section \ref{sec:proofs}.
+%Theorem \ref{thm:Gaussian-error-approx-exact-boundary} is proved in Section \ref{sec:proofs}.
 The phase transition boundary \eqref{eq:approx-exact-boundary-Gaussian} is visualized in Figure \ref{fig:phase-Gaussian-errors}.
 
-\subsection{Asymptotic power analysis}
+\begin{proof}[Theorem \ref{thm:Gaussian-error-approx-exact-boundary}]
+We first show the sufficient condition (part {\rm (i)}).
+Since FDR control is guaranteed by the BH procedure, we only need to show that the FWNR also vanishes, that is,
+\begin{equation} \label{eq:approx-exact-boundary-proof-sufficient-1-Gaussian}
+    \P\left[\min_{i\in S}x(i) \ge \tau\right] \to 1,
+\end{equation}
+where $\tau$ is the threshold for the BH procedure.
+
+By the assumption that $\underline{r}>\widetilde{h}(\beta)=(\sqrt{\beta}+\sqrt{1-\beta})^2$, we have $\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{\beta}$, so we can pick $q>0$, such that 
+\begin{equation} \label{eq:approx-exact-boundary-proof-sufficient-2-Gaussian}
+\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{q}>\sqrt{\beta}.
+\end{equation}
+We only need to show that with a specific choice of $t^*=\sqrt{2q\log{p}}$ where
+\begin{equation} \label{eq:additive-error-approx-exact-boundary-proof-sufficient-1}
+\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{q}>\sqrt{\beta},
+\end{equation}
+we have both
+\begin{equation} \label{additive-error-eq:approx-exact-boundary-proof-sufficient-2}
+\P\left[\tau\le t^*\right]\to 1,
+\end{equation}
+and 
+\begin{equation} \label{eq:additive-error-approx-exact-boundary-proof-sufficient-3}
+    \P\left[\min_{i\in S}x(i) \ge t^* \right] \to 1,
+\end{equation}
+so that 
+\begin{equation*} 
+    \P\left[\min_{i\in S}x(i) \ge \tau\right] \ge 
+    % \P\left[\min_{i\in S}x(i) \ge t^* \ge \tau\right] \ge
+    \P\left[\min_{i\in S}x(i) \ge t^*,\; t^* \ge \tau\right] \to 1.
+\end{equation*}
+
+Relation \eqref{additive-error-eq:approx-exact-boundary-proof-sufficient-2} follows in exactly the same way \eqref{eq:approx-boundary-proof-sufficient-3-Gaussian} did on page  \pageref{eq:approx-boundary-proof-sufficient-3-Gaussian}.
+
+Dividing the left-hand-side in Relation \eqref{eq:additive-error-approx-exact-boundary-proof-sufficient-3} by $\sqrt{2\log{p}}$, we have,
+\begin{align*}
+    \frac{\min_{i\in S}x(i)}{\sqrt{2\log{p}}} 
+    &= \frac{\min_{i\in S}\mu(i)+\epsilon(i)}{\sqrt{2\log{p}}} 
+    \stackrel{\mathrm{d}}{\ge} \frac{\sqrt{2\underline{r}\log{p}} + \min_{i\in S}\epsilon(i)}{\sqrt{2\log{p}}} \\
+    &\to -\sqrt{1-\beta} + \sqrt{\underline{r}},
+\end{align*}
+where the last convergence follows from the relative stability of iid Gaussians minima \eqref{eq:relative-stability-Gaussian-minima}. 
+On the other hand, ${t^*}/{\sqrt{2\log{p}}}=\sqrt{q}<\sqrt{\underline{r}}-\sqrt{1-\beta}$ by our choice of ${q}$, and Relation \eqref{eq:additive-error-approx-exact-boundary-proof-sufficient-3} follows.
+
+The necessary condition follows from the lower bound
+\begin{equation} \label{eq:additive-error-approx-exact-boundary-proof-necessary-1}
+    \mathrm{FDR}(\mathcal{R}) + \mathrm{FWNR}(\mathcal{R}) \ge \E\left[\frac{|\widehat{S}(u)\setminus S|}{|\widehat{S}(u)\setminus S| + |S|}\right] \wedge 
+    \P\left[\min_{i\in S}x(i)<u\right],
+\end{equation}
+which holds for any thresholding procedure $\mathcal{R}$ and for arbitrary $u\in\R$.
+In particular, we show that both terms in the minimum in \eqref{eq:additive-error-approx-exact-boundary-proof-necessary-1} converge to 1 when we set $u=t^*=\sqrt{2q\log{p}}$ where 
+\begin{equation}
+\sqrt{\overline{r}}-\sqrt{1-\beta}<\sqrt{q}<\sqrt{\beta}.
+\end{equation}
+
+On the one hand, we have,
+$$
+\frac{\min_{i\in S}x(i)}{\sqrt{2\log{p}}} 
+\stackrel{\mathrm{d}}{\le} \frac{\min_{i\in S}\epsilon(i)+\sqrt{2\overline{r}\log{p}}}{\sqrt{2\log{p}}} 
+\to \sqrt{\overline{r}}-\sqrt{1-\beta},
+$$
+by relative stability of iid Gaussians \eqref{eq:relative-stability-Gaussian-minima}. On the other hand, ${t^*}/{\sqrt{2\log{p}}}=\sqrt{q}>\sqrt{\underline{r}}-\sqrt{1-\beta}$ by our choice of ${q}$;
+this shows that the second term on the right-hand side of \eqref{eq:additive-error-approx-exact-boundary-proof-necessary-1} converges to 1.
+
+Observe that $|\widehat{S}(t^*)\setminus{S}|$ has distribution $\text{Binom}(p-s, \overline{\Phi}(t^*))$, and define $X = X_p := {|\widehat{S}(t^*)\setminus{S}|}/{|S|}$, we obtain,
+% On the other hand, define $ = \E[|S\setminus\widehat{S}(t^*)|/|S|]$,
+\begin{align*}
+    \mu &:= \E[X] = (p^\beta-1)\overline{\Phi}(t^*) 
+    \sim (p^\beta-1)\frac{\phi(t^*)}{t^*} \\
+    &\sim \frac{1}{\sqrt{2\pi}}\left(2q\log{p}\right)^{-1/2}p^{\beta-q}\to\infty,
+\end{align*}
+where the divergence follows from our choice of $q<\beta$.
+Using again Relations \eqref{eq:approx-boundary-proof-converse-2-Gaussian} and \eqref{eq:approx-boundary-proof-converse-3-Gaussian}, we conclude that the first term on the right-hand side of \eqref{eq:additive-error-approx-exact-boundary-proof-necessary-1} also converges to 1.
+This completes the proof of the necessary condition.
+\end{proof}
+
+\section{Asymptotic power analysis: A discussion}
 \label{subsec:power-analysis}
+
+\stilian{We end this chapter with a general discussion on the effect of the signal sparsity on the interplay between 
+signal size and sparsity in the context of the detection and
+ support recovery problems.  Specifically, different support recovery criteria are compared.}{\fbox{added, check}}
 

### 2021-02-01 3.phase_transitions/3.global-tests.tex
merge of Ch. 3 and the new Ch. 4 & 5
I merged my work on Ch 3 and Ch. 4&5 with the "revision-GWAS" branch.

Need some more work -- putting the Mill's ratio in Ch 2 perhaps...

@@
 To the best of our knowledge, performance of simple statistics such as $L_1$, $L_2$ norms, and 
-\stilian{the sum statistic $T$ in \eqref{eq:sum-statistic}}{R2, Typo 7}
-in this weak signal setting have not been reported in the literature. %perhaps due to a perceived lack of novelty. 
+the sum statistic $T$ in \eqref{eq:sum-statistic} in this weak signal setting have not been reported in the literature. %perhaps due to a perceived lack of novelty. 
 Our first theorem establishes the performance of these simple but popular statistics for detecting sparse signals 
@@
 \begin{equation}
-    \frac{1}{\sqrt{2p}}\sum_{i=1}^p \left(x(i)^2-1\right) \implies \mathrm{N}(0,1),  
+    {\color{red}\frac{1}{\sqrt{2p}}}\sum_{i=1}^p \left(x(i)^2-1\right) \implies \mathrm{N}(0,1),  
 \end{equation}
@@
  \begin{equation}
-    \frac{1}{\sqrt{2p}}\left(\sum_{i=1}^p \left(x(i)^2-1\right) - p^{1/2-\beta+2r}\right) \implies \mathrm{N}(0,1).
+    {\color{red} \frac{1}{\sqrt{2p}}}\left(\sum_{i=1}^p \left(x(i)^2-1\right) - p^{1/2-\beta+2r}\right) \implies \mathrm{N}(0,1).
 \end{equation}

### 2021-02-01 3.phase_transitions/phase_transitions.tex
ch 3
almost done editing ch 3 (for formatting).  I need to absorb the auxuliary results from the appendix and check the proofs carefully once again. I like the new format where the proofs are presented right after the statments and the various support recovery criteria are presented in separate sections rather than sub-sections.  Thus, they are visible in the table of contents.
merge of Ch. 3 and the new Ch. 4 & 5
I merged my work on Ch 3 and Ch. 4&5 with the "revision-GWAS" branch.

Need some more work -- putting the Mill's ratio in Ch 2 perhaps...

@@
-\stilian{The purpose of this chapter is to provide a unified review of the fundamental statistical limits in the 
+The purpose of this chapter is to provide a unified review of the fundamental statistical limits in the 
 sparse signal detection and support recovery problems.  Our goal is to convey the main ideas and thus we shall focus on 
-the simple but important setting of independent Gaussian errors.}{\xout{We study the fundamental limits of the signal detection and support recovery problems in the location models with independent Gaussian errors in this chapter.}}
+the simple but important setting of independent Gaussian errors.
 Specifically, we derive the conditions under which the detection and support recovery problems succeed and fail in the sense of \eqref{eq:support-recovery-success} and \eqref{eq:support-recovery-failure}, in the additive error model
@@
 
+%\newpage
 \section{Sparse signal support recovery problems}

### 2021-02-01 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
merge of Ch. 3 and the new Ch. 4 & 5
I merged my work on Ch 3 and Ch. 4&5 with the "revision-GWAS" branch.

Need some more work -- putting the Mill's ratio in Ch 2 perhaps...

@@
 
-\section{A discussion on optimality}
+\section{Optimality and sub-optimality: A discussion}
 
@@
 
-Consider the model \eqref{eq:model-additive} with independent errors. Theorem \ref{thm:necessary-strengthened} 
-and Corollary \ref{cor:minimax-over-dependence} provide a nearly complete picture of the difficulty in the exact support 
-recovery problem, in the regime when the thresholding estimators are optimal. Specifically, in such cases the signal classification boundary is universal.
+We conclude with a brief summary on the optimality and sub-optimality of the thresholding procedures in the problem of exact support estimation.
+For clarity, we focus on the model \eqref{eq:model-additive} with {\em independent} errors.
 
- Proposition \ref{prop:likelihood-ratio-thresholding}, and indeed, Example \ref{exmp:suboptimal-data-thresholding} demonstrate that thresholding procedures are in fact \emph{sub-optimal} for $\text{AGG}(\nu)$ models with $\nu<1$.
-Therefore, the optimality of thresholding procedures (specifically, Bonferroni's procedure) only applies to $\text{AGG}(\nu)$ models with $\nu\ge1$. 
+Theorem \ref{thm:necessary-strengthened} and Corollary \ref{cor:minimax-over-dependence} provide a nearly complete picture of the difficulty 
+in the exact support  recovery problem, in the regime when the thresholding estimators are optimal.
+Specifically, in such cases the signal classification boundary is universal.
+On the other hand, Proposition \ref{prop:likelihood-ratio-thresholding}, and indeed, Example \ref{exmp:suboptimal-data-thresholding} demonstrate that thresholding procedures are \emph{sub-optimal} for $\text{AGG}(\nu)$ models with $\nu<1$.
+Therefore, the optimality of thresholding
+procedures (specifically, Bonferroni's procedure) only applies to $\text{AGG}(\nu)$ models with $\nu\ge1$. 
 % This suggests that the condition $\nu\ge1$ in Corollary \ref{cor:minimax-over-dependence} is tight.
 
-If we restrict the space of methods to only thresholding procedures, then results in Section \ref{subsec:point-wise-minimax} state that the phase transition phenomenon --- the 0-1 law in the sense of Corollary \ref{cor:point-wise-minimax} --- is universal in all error models with rapidly varying tails.
-This includes $\text{AGG}(\nu)$ models {\it for all} $\nu>0$.
-In contrast, models with heavy (regularly varying) tailed errors do not exhibit this phenomenon (see Theorem \ref{thm:heavy-tails}).
-We summarize the properties of thresholding procedures in Table \ref{table:role-of-thresholding}.
+If we restrict the space of methods to only thresholding procedures, then the results in Section \ref{subsec:point-wise-minimax} state that the phase 
+transition phenomenon --- the 0-1 law in the sense of Corollary \ref{cor:point-wise-minimax} --- is universal in all error models with rapidly varying tails.
+This includes $\text{AGG}(\nu)$ models {\it for all} $\nu>0$.  In contrast, models with heavy (regularly varying) tailed errors do not exhibit this phenomenon 
+(form more details, see Theorem \ref{thm:heavy-tails}).  We summarize the properties of thresholding procedures in 
+Table \ref{table:role-of-thresholding}.
 
@@
     \centering
-    \caption{Properties of thresholding procedures under different error distributions when errors are independent. Properties of the error distributions are listed in brackets.}
+    \caption{Properties of thresholding procedures under different error distributions when the errors are independent. 
+    Properties of the error distributions are listed in brackets.}
     \medskip

### 2021-02-01 2.background/2.Gaussian-distributions.tex
all in
I completed the merge of my work on ch. 3, 4 and 5 with the branch "revision-GWAS".  Ready for a "pull" to "revision-GWAS"

We end this chapter with several facts about univariate and multivariate Gaussian distributions that will be used in the rest of the manuscript. \\

{\bf Relative stability.} We first state the relative stability of iid standard Gaussian random variables.  Since the standard Gaussian distribution falls in the 
class of asymptotically generalized Gaussians (AGG; see Definition \ref{def:AGG}), by Example \ref{exmp:AGG}, we know that the triangular array ${\cal E} = \{\left(\epsilon_p(i)\right)_{i=1}^p, p\in\N\}$ has relatively stable (RS) maxima in the sense of \eqref{eq:RS-condition}, i.e.,
\begin{equation} \label{eq:relative-stability-Gaussian-maxima}
    \frac{1}{u_{p}} \max_{i=1,\ldots,p} \epsilon_p(i) \xrightarrow{\P} 1,\quad \text{as }\;p\to\infty,
\end{equation}
where $u_p$ is the $(1/p)$-th upper quantile as defined in \eqref{eq:AGG-quantiles}.
Similarly, since the array ${\cal E}$ has distributions symmetric around 0, it also has relatively stable minima
\begin{equation} \label{eq:relative-stability-Gaussian-minima}
    \frac{1}{u_{p}} \min_{i=1,\ldots,p} \epsilon_p(i) \xrightarrow{\P} -1,\quad \text{as }\;p\to\infty.
\end{equation}
The convergence in \eqref{eq:relative-stability-Gaussian-maxima} also holds almost surely.\\

{\bf Mill's ratio.} We give next the well-known bounds for the Mill's ratio of Gaussian tails.
Let $\Phi$ denote the CDF of the standard Gaussian distribution and $\phi$ its density.
One can show that for all $x>0$ we have
\begin{equation} \label{eq:Mills-ratio}
    \frac{x}{1+x^2}\phi(x) \le \overline{\Phi}(x) = 1-\Phi(x) \le \frac{1}{x}\phi(x),
\end{equation}
using e.g., integration by parts.  Note that this fact may be used to verify the rapid variation of $\Phi$, which entails 
the relative stability property above.\\

{\bf Stochastic monotonicity.} The third fact is the stochastic monotonicity of the Gaussian location family. 
In fact, for all location families $\{F_\delta(x)\}_\delta$ where $F_\delta(x) = F(x-\delta)$, we have,
\begin{equation} \label{eq:stochastic-monotonicity-Gaussian}
    F_{\delta_1}(t) \ge F_{\delta_2}(t), \quad \text{for all}\quad t\in\mathbb{R}\quad\text{and all}\quad \delta_1 \le \delta_2.
\end{equation}
Relation \eqref{eq:stochastic-monotonicity-Gaussian} holds, of course, when $F$ is the standard Gaussian distribution. \\

{\bf Slepian's lemma and the Sudakov-Fernique inequality.} 
The following two result will play fundamental roles in our characterization of uniform relative stability for Gaussian triangular arrays in 
Chapter \ref{chap:URS}. 
% Many more details and deeper insights can be found for example in the monographs 
%\cite{leadbetter2012extremes} and \cite{adler2009random}, among others. 
The first is the celebrated result due to \citet{slepian1962one}.

\begin{theorem}[Slepian's Lemma]\label{thm:Slepian-lemma} Let $\epsilon = (\epsilon(i))_{i=1}^p$ and $\eta = (\eta(i))_{i=1}^p$ be 
two multivariate normally distributed random vectors with zero means $\E [\epsilon(i)] = \E[\eta(i)] = 0$.

 If for all $i,j=1,\cdots,p$, we have
$$
\E [\epsilon(i)^2] = \E[\eta(i)^2],\ \ \ \mbox{ and }\ \ \ {\rm Cov}(\epsilon(i),\epsilon(j)) \le {\rm Cov}(\eta(i),\ \eta(j)),
$$
 then $\epsilon \stackrel{{\rm st}}{\ge} \eta$, i.e.,
$$
\P [ \epsilon(i) \le x_i,\ i=1,\cdots,p] \le \P [ \eta(i) \le x_i,\ i=1,\cdots,p].
$$
\end{theorem}

This result implies in particular that $M_\epsilon:= \max_{i=1,\cdots,p}\epsilon(i)$ dominates stochastically $M_\eta:= \max_{i=1,\cdots,p} \eta(i)$.
Thus, for example, the maximum of iid Gaussians are stochastically larger the maxima any positively correlated Gaussian vector 
with the same marginal distributions.

Slepian's lemma can be obtained as a corollary from the general Normal Comparison Lemma 
\citep[see, e.g., Theorem 4.2.1 on page 81 in][]{leadbetter2012extremes}.  See also Ch.\ 2 in \cite{adler2009random}.

The following result, known as the Sudakov-Fernique inequality is similar in spirit to Slepian's lemma but does not assume that the Gaussian 
vectors are centered. For a proof and, in fact, a more general result, see e.g., Theorem 2.2.5 on page 61 in \cite{adler2009random}.

\begin{theorem} [Sudakov-Fernique Inequality] \label{th:Sudakov-Fernique} 
Let $\epsilon = (\epsilon(i))_{i=1}^p$ and $\eta = (\eta(i))_{i=1}^p$ be 
two multivariate normally distributed random vectors.

If for all $i,j=1,\cdots,p$, we have 
$$
\E [ \epsilon(i) ] = \E [\eta(i)] \ \ \mbox{ and }\ \ \E [ (\epsilon(i)-\epsilon(j))^2] \le \E [ (\eta(i)-\eta(j))^2],
$$
then for $M_\epsilon = \max_{i=1,\cdots,p}\epsilon(i)$ and $M_\eta = \max_{i=1,\cdots,p} \eta(i)$, we have 
$$
 \E [ M_\epsilon ] \le \E [M_\eta].
$$
\end{theorem}

### 2021-02-01 2.background/2.RV_and_RS.tex
all in
I completed the merge of my work on ch. 3, 4 and 5 with the branch "revision-GWAS".  Ready for a "pull" to "revision-GWAS"

@@
 More generally, distributions with heavier tails (e.g., log-normal) and lighter tails (e.g., Gompertz) outside the generalized AGG class \eqref{eq:GAGG} may also possess rapidly varying tails;
-heavy-tailed distributions like the Pareto and t-distributions, on the other hand, do not.
-\stilian{More details on these alternative classes of models can be found in the Supplement.}
-{\fbox{Move these to the online Supplement?} 
-These alternative classes of models will be introduced when we study the phase transitions in 
-Chapter \ref{chap:exact-support-recovery}.}
-%For brevity, we focus here on the $\text{AGG}(\nu)$ models.
+heavy-tailed distributions like the Pareto and t-distributions, on the other hand, do not.   More details on these alternative classes of models can be 
+found in Chapter \ref{chap:non-AGG}.

### 2021-02-02 2.background/2.Gaussian-distributions.tex
working on ch. 6
implementing my corrections.

@@
 {\bf Slepian's lemma and the Sudakov-Fernique inequality.} 
-The following two result will play fundamental roles in our characterization of uniform relative stability for Gaussian triangular arrays in 
-Chapter \ref{chap:URS}. 
+The following two results will be instrumental in our characterization of uniform relative stability for 
+Gaussian triangular arrays in Chapter \ref{chap:URS}.  
 % Many more details and deeper insights can be found for example in the monographs 
@@
 
-\begin{theorem}[Slepian's Lemma]\label{thm:Slepian-lemma} Let $\epsilon = (\epsilon(i))_{i=1}^p$ and $\eta = (\eta(i))_{i=1}^p$ be 
+\begin{theorem}[Slepian's lemma]\label{thm:Slepian-lemma} Let $\epsilon = (\epsilon(i))_{i=1}^p$ and $\eta = (\eta(i))_{i=1}^p$ be 
 two multivariate normally distributed random vectors with zero means $\E [\epsilon(i)] = \E[\eta(i)] = 0$.
@@
 
-This result implies in particular that $M_\epsilon:= \max_{i=1,\cdots,p}\epsilon(i)$ dominates stochastically $M_\eta:= \max_{i=1,\cdots,p} \eta(i)$.
-Thus, for example, the maximum of iid Gaussians are stochastically larger the maxima any positively correlated Gaussian vector 
-with the same marginal distributions.
+This result implies in particular that $M_\epsilon:= \max_{i=1,\cdots,p}\epsilon(i)$ dominates stochastically $M_\eta:= \max_{i=1,\cdots,p} \eta(i)$ in the
+sense that
+\begin{equation}\label{e:Slepian-lemma-maxima}
+ \P[ M_\eta > u] \le \P [M_\epsilon > u],\ \ \mbox{ for all }u\in\mathbb R.
+\end{equation}
+In this case, we shall write $M_\eta \stackrel{d}{\le} M_\epsilon$.  This result shows, for example, that the maximum of iid Gaussians is 
+stochastically larger the maximum of any positively correlated Gaussian vector with the same marginal distributions.
 
@@
 
-The following result, known as the Sudakov-Fernique inequality is similar in spirit to Slepian's lemma but does not assume that the Gaussian 
-vectors are centered. For a proof and, in fact, a more general result, see e.g., Theorem 2.2.5 on page 61 in \cite{adler2009random}.
+The following result, known as the Sudakov-Fernique inequality, is similar in spirit to Slepian's lemma but it does not assume that the Gaussian 
+vectors are centered and yields a weaker conclusion -- an inequality between expectations. For a proof, many insights, and, in fact, a more 
+general result, see e.g., Theorem 2.2.5 on page 61 in \cite{adler2009random}.
 
@@
 $$
-\E [ \epsilon(i) ] = \E [\eta(i)] \ \ \mbox{ and }\ \ \E [ (\epsilon(i)-\epsilon(j))^2] \le \E [ (\eta(i)-\eta(j))^2],
+\E [ \epsilon(i) ] = \E [\eta(i)] \ \ \mbox{ and }\ \ \E [ (\eta(i)-\eta(j))^2] \le \E [ (\epsilon(i)-\epsilon(j))^2],
 $$
@@
 $$
- \E [ M_\epsilon ] \le \E [M_\eta].
+ \E [ M_\eta ] \le \E [M_\epsilon].
 $$

### 2021-02-02 5.URS/URS.tex
working on ch. 6
implementing my corrections.

@@
-In this chapter, we establish a complete characterization of URS for Gaussian arrays in terms of a simple condition on the covariance structures.
+Recall that the notion of uniform relative stability (URS) in Definition \ref{def:URS} is the key to the necessary conditions for exact support recovery 
+established in Theorem \ref{thm:necessary}.
+In this chapter, we provide a complete characterization of the class of URS Gaussian arrays in terms of a simple condition on their covariance structure.
 The condition is as follows.
@@
 \begin{enumerate}
-    \item[(i)] permutations $l = l_p$ of $\{1,\ldots,p\}$, for all $p\in\N$, and
+    \item[(i)] permutations $l_p$ of $\{1,\ldots,p\}$, for all $p\in\N$, and
     \item[(ii)] a non-negative sequence $(r_n)_{n=1}^\infty$ converging to zero $r_n\to 0$, as $n\to\infty$,
@@
 \end{equation}
-where $i' = l(i)$, $j' = l(j)$, for all $i,j\in\{1,\ldots,p\}$.
+where $i' = l_p(i)$, $j' = l_p(j)$, for all $i,j\in\{1,\ldots,p\}$.
 \end{definition}
@@
 
-We now state the main result of this section: a Gaussian sequence is URS if and only if it is UDD.
-The URS condition essentially requires that the dependencies decay in a uniform fashion, the rate at which dependence decay does \emph{not} matter.
+We now state the main result of this chapter.  It states that a Gaussian array is URS if and only if it is UDD.
+The URS condition essentially requires that the dependencies decay in a uniform fashion, the rate at which dependence decay 
+does \emph{not} matter.
 
@@
 
-Returning again to the study of support recovery problems, Theorem \ref{thm:Gaussian-weak-dependence} and the necessary condition for exact support recovery in Theorem \ref{thm:necessary} yields the following result.
+Returning again to the study of support recovery problems, Theorem \ref{thm:Gaussian-weak-dependence} and the necessary condition for exact support recovery in Theorem \ref{thm:necessary} yield the following result.
 
@@
 
-As a counterpart to Remark \ref{rmk:dependence-assumptions}, we demonstrate the tightness of the dependence conditions in Theorem \ref{thm:necessary}.
-Specifically, we demonstrate that if the URS dependence condition is violated, then it may be possible to recover the support of weaker signals below the boundary.
+One may ask, whether the UDD (equivalently, URS) condition can be relaxed further for the phase-transition result in Theorem \ref{thm:necessary} to 
+hold.  As a counterpart to Remark \ref{rmk:dependence-assumptions}, we demonstrate next that the dependence conditions in Theorem \ref{thm:necessary} 
+are nearly optimal.  Specifically, we show that if the URS dependence condition is violated, then it may be possible to recover the support 
+of weaker signals, falling below the boundary.   The main idea is to use the equivalence of URS and UDD to construct a Gaussian error array,
+whose correlations do not decay in a uniform fashion (UDD fails). As we will see, in such a case one can do substantially better in terms of 
+support recovery.  This shows that the URS condition is nearly optimal in the Gaussian setting.  
+Numerical simulations illustrating this example can be found in Section \ref{suppsec:numerical}, below.
 
-\begin{example} \label{exmp:counter-example}
-Suppose ${\cal E} = \left(\epsilon_p(i)\right)_{i=1}^p$ is Gaussian, and is comprised of $\lfloor p^{1-\beta}\rfloor$ blocks, each of size at least $\lfloor p^\beta \rfloor$; 
-let the elements of each block have correlation 1, and let elements from different blocks be independent. 
-If $\underline{r} \ge 4(1-\beta)$, then the procedure $\widehat{S} = \big\{i:x(i)>\sqrt{2(1-\beta)\log{p}}\big\}$ yields $\mathbb P[\widehat{S} = S] \to 1$. 
-This requirement on signal size is strictly weaker than that of the strong classification boundary, since $4(1-\beta) < (1 + \sqrt{1-\beta})^2$ on $\beta\in(0,1)$.
+\begin{example}[On the tightness of the URS condition for exact support recovery] \label{exmp:counter-example}
+Suppose ${\cal E} = \left(\epsilon_p(i)\right)_{i=1}^p$ is Gaussian, and is comprised of $\lfloor p^{1-\beta}\rfloor$ blocks, each of size at least $\lfloor p^\beta \rfloor$.
+Let the elements within each block have correlation 1, and let the elements from different blocks be independent.
+If $\underline{r} \ge 4(1-\beta)$, then the procedure 
+$$
+ \widehat{S} = \big\{i:x(i)>\sqrt{2(1-\beta)\log{p}}\big\}
+ $$ 
+yields exact support recovery, i.e., $\mathbb P[\widehat{S} = S] \to 1$, as $p\to\infty$.  This requirement on the signal size is strictly 
+weaker than that of the strong classification boundary, since $4(1-\beta) < (1 + \sqrt{1-\beta})^2$ on $\beta\in(0,1)$.
 \end{example} 
+\begin{proof}[Example \ref{exmp:counter-example}]
+Let $t_p^* = \sqrt{2(1-\beta)\log{p}}$  and observe that $\widehat{S} = \{j:x(j)>t_p^*\}$.
+Analogous to \eqref{eq:Bonferroni-FWER-control} in the proof of Theorem \ref{thm:sufficient}, we have
+\begin{align*}
+    \P\left[\widehat{S} \subseteq S\right] 
+        &= 1 - \P\left[\max_{j\in S^c}x(j) > t_p^*\right] 
+        = 1 - \P\left[\max_{j\in S^c}\epsilon(j) > t_p^*\right] \nonumber \\
+      % \ge 1 - \P\left[\max_{j\in\{1,\ldots,p\}}\epsilon(j) > t_p\right] \nonumber \\
+        &\ge 1 - \P\left[\max_{j\in\{1,\ldots,p\}}\epsilon(j) > t_p^*\right] 
+        \ge 1 - \P\left[\max_{j\in\{1,\ldots,\lfloor p^{1-\beta}\rfloor\}}\widetilde{\epsilon}(j) > t_p^*\right]
+\end{align*}
+where $\left(\widetilde{\epsilon}\right)_{j=1}^{\lfloor p^{1-\beta}\rfloor}$'s are independent Gaussian errors; in the last inequality we used the assumption that there are at most $\lfloor p^{1-\beta}\rfloor$ independently distributed Gaussian errors in $\left(\epsilon_p(j)\right)_{j=1}^p$.
+By Example \ref{exmp:FWER-controlling_procedures} (with $\lfloor p^{1-\beta}\rfloor$ taking the role of $p$), we know that the FWER goes to 0 at a rate of 
+$\left(2\log{\lfloor p^{1-\beta}\rfloor}\right)^{-1/2}$.
+Therefore, the probability of no false inclusion converges to 1.
 
-The above example shows that if the correlations of the Gaussian errors do not decay in a uniform fashion (UDD fails), then we can do substantially better in terms of support recovery.
-The claims in the example are verified in Section \ref{suppsec:proofs}, while numerical simulations of this example can be found in Section \ref{suppsec:numerical}.
+On the other hand, since the signal sizes are no smaller than $(\nu\underline{r}\log p)^{1/\nu} = \sqrt{2\underline{r}\log p}$ (for $\nu = 2$), similar to 
+\eqref{eq:sufficient-proof-eq1}, we obtain
+\begin{align}
+    \P\left[\widehat{S} \supseteq S\right] 
+    &\ge \P\left[\min_{j\in S}\epsilon(j) > \sqrt{2(1-\beta)\log{p}} - \sqrt{2\underline{r}\log{p}} \right] \nonumber \\
+    &= \P\left[\max_{j\in S}\left(-\epsilon(j)\right) < \sqrt{2\log{p}}\left(\sqrt{\underline{r}}-\sqrt{1-\beta}\right) \right] \nonumber \\
+    &= \P\left[\frac{\max_{j\in S}(-\epsilon(j))}{u_{|S|}} < \frac{\sqrt{\underline{r}}-\sqrt{1-\beta}}{\sqrt{1-\beta}}\left(1+o(1)\right) \right], \label{eq:sufficient-proof-counter-example}
+\end{align}
+where in the last line we used the quantiles \eqref{eq:AGG-quantiles}.
+Since the minimum signal size is bounded below by $\underline{r} > 4(1-\beta)$, the right-hand-side of the inequality in \eqref{eq:sufficient-proof-counter-example} converges to a constant strictly larger than 1.
+While the left-hand-side, by Slepian's lemma (recall
+Theorem \ref{thm:Slepian-lemma} and Relation \ref{e:Slepian-lemma-maxima}), is stochastically smaller than a r.v.\ going to 1.  Namely, we have
+\begin{equation}
+  \frac{1}{u_{|S|}} \max_{j\in S}(-\epsilon(j)) \stackrel{d}{\le} \frac{1}{u_{|S|}} \max_{j\in S} \epsilon^*(j) \stackrel{\P}{\longrightarrow} 1,
+\end{equation}
+where $\left({\epsilon^*}\right)_{j=1}^{\lfloor p^{1-\beta}\rfloor}$'s are independent Gaussian errors.
+Therefore the probability in \eqref{eq:sufficient-proof-counter-example} must also converge to 1.
+\end{proof}
 
@@
 
-We conclude with a brief discussion on the relationships between UDD and other dependence conditions in the context of extreme value theory, before proceeding to the proof of Theorem \ref{thm:Gaussian-weak-dependence}.
+Before proceeding to the proof of Theorem \ref{thm:Gaussian-weak-dependence}, we will briefly discuss 
+the relationships between UDD and other dependence conditions in the context of extreme value theory. The main idea
+we would like to convey is that UDD (and equivalently URS) is an exceptionally mild condition on the dependence of the array.
 

### 2021-02-03 2.background/2.Gaussian-distributions.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

@@
 
-\begin{theorem} [Sudakov-Fernique Inequality] \label{th:Sudakov-Fernique} 
+\begin{theorem} [The Sudakov-Fernique inequality] \label{th:Sudakov-Fernique} 
 Let $\epsilon = (\epsilon(i))_{i=1}^p$ and $\eta = (\eta(i))_{i=1}^p$ be 

### 2021-02-03 2.background/2.asymptotics.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

@@
 {\bf Signal detection.}
-The asymptotic behavior of the statistical risk in signal detection problems \eqref{eq:risk-detection} in high dimensions was first studied by \stilian{Yurii Ismailovich Ingster}{where did you find the full name?} in the context of sparse additive models \eqref{eq:model-additive} with
+The asymptotic behavior of the statistical risk in signal detection problems \eqref{eq:risk-detection} in high dimensions was first studied by 
+Yuri Izmailovich Ingster in the context of sparse additive models \eqref{eq:model-additive} with 
 independent and Gaussian components. Specifically, \cite{ingster1998minimax} considered the behavior of the 

### 2021-02-03 2.background/2.statistical_procedures.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

@@
 \begin{equation} \label{eq:sum-statistic}
-    S(x) := \sum_{i=1}^p{x(i)},
+    T(x) := \sum_{i=1}^p{x(i)},
 \end{equation}
@@
 Under the assumption that the data $x(i)$'s under the null have a common marginal distribution $F$, we review five thresholding procedures for support recovery, starting with the well-known Bonferroni's procedure which aims at controlling family-wise error rates.
-\begin{definition}[Bonferroni's procedure]
+\begin{definition}[Bonferroni's procedure] \label{def:Bonf}
 Bonferroni's procedure with level $\alpha$ is the thresholding procedure that uses the threshold
@@
 It can be shown that both Bonferroni's and Holm's procedures control FWER at their nominal levels, regardless of dependence in the 
-data \citep{holm1979simple}.
-In contrast, Sid\'ak's and Hochberg's procedures control FWER at nominal levels when data are independent \citep{vsidak1967rectangular, hochberg1988sharper}.
-\stilian{DISCUSS}{Explain in the Supplement?}
+data \citep{holm1979simple}. In contrast, Sid\'ak's and Hochberg's procedures control FWER at nominal levels when data are independent \citep{vsidak1967rectangular, hochberg1988sharper}.
 
@@
 
-Recall the order statistics of our observations $x_{[1]} \ge x_{[2]}  \ge \ldots \ge x_{[p]}$.
+Recall the order statistics of our observations are: $x_{[1]} \ge x_{[2]}  \ge \ldots \ge x_{[p]}$.
 \begin{definition}[Benjamini-Hochberg's procedure] \label{def:BH}
@@
 The \ac{BH} procedure is shown to control the FDR at level $\alpha$ when the $x(i)$'s are independent \citep{benjamini1995controlling}. 
-\stilian{DISCUSS}{Again, explain in the Supplement?} Variations of this procedure have been proposed to control the \ac{FDR} under certain models of dependent observations \citep{benjamini2001control}.
+ Variations of this procedure have been proposed to control the \ac{FDR} under certain models of dependent observations \citep{benjamini2001control}.
 

### 2021-02-03 3.phase_transitions/3.Gaussian-support-recovery.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

@@
 
-\stilian{
 Figure \ref{fig:phase-Gaussian-errors} illustrates the rich landscape of phase transitions in support recovery for the various choices
-of statistical risk for the family of thresholding estimators, established in the following sections.}{\fbox{ added these words and moved the figure here}}
+of statistical risk for the family of thresholding estimators, established in the following sections.
 We end this brief overview with a technical notion needed in order to state our main results.
@@
 
-\stilian{We end this chapter with a general discussion on the effect of the signal sparsity on the interplay between 
-signal size and sparsity in the context of the detection and
- support recovery problems.  Specifically, different support recovery criteria are compared.}{\fbox{added, check}}
+%We end this chapter with a general discussion on the effect of the signal sparsity on the interplay between 
+%signal size and sparsity in the context of the detection and
+% support recovery problems.  Specifically, different support recovery criteria are compared.
 

### 2021-02-03 3.phase_transitions/3.global-tests.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

@@
 
-\stilian{For simplicity of the exposition, we will suppose that  in \eqref{eq:signal-size-small} we have 
+For simplicity of the exposition, we will suppose that  in \eqref{eq:signal-size-small} we have 
 $\underline{r} = r = \overline{r}$, so that  $\mu(i) = p^r$.  The general case where $\underline{r}<\overline{r}$ is left as 
-an exercise.}{\fbox{How about that?}}
+an exercise.
 

### 2021-02-03 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
working on ch. 6
implementing my corrections.
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

@@
 
-\stilian{ 
+%\stilian{ 
 For any collection of numbers $\{a_i,\ i=1,\cdots,s\}$, let 
@@
  For concreteness,  one can break possible ties lexicographically.  In many cases, 
- the oracle thresholding estimators will be almost surely unique.}
-{\fbox{IMPORTANT, replacing the following}
-\begin{definition}[Oracle data thresholding]
-We call $\widehat{S}^* = \{i\,|\, x(i)\ge x_{[s]}\}$ the oracle data thresholding procedure, where $x_{[1]} \ge \ldots \ge x_{[p]}$ are the order statistics of $x$.
-\end{definition}}
+ the oracle thresholding estimators will be almost surely unique.
+ %}
+%{\fbox{IMPORTANT, replacing the following}
+%\begin{definition}[Oracle data thresholding]
+%We call $\widehat{S}^* = \{i\,|\, x(i)\ge x_{[s]}\}$ the oracle data thresholding procedure, where $x_{[1]} \ge \ldots \ge x_{[p]}$ are the order statistics of $x$.
+%\end{definition}}
 
@@
 Using Relation \eqref{eq:MLR-optimality-proof}, we conclude that $f(x|\widehat{S}) \le f(x|\widehat{S}\,')$.
-\stilian{Continuing this way, we can successively improve the likelihood of every estimator until we arrive at an oracle thresholding estimator, proving the desired optimality.
+Continuing this way, we can successively improve the likelihood of every estimator until we arrive at an oracle thresholding estimator, proving the desired optimality.
 Note that with the same argument, we obtain that any two oracle
-thresholding estimators have the same likelihood.}{
-\fbox{replacing} This implies that any estimator that is not $\widehat{S}^*$ may be improved, and the optimality follows.}
+thresholding estimators have the same likelihood.
 \end{proof}
@@
 %
-\stilian{In this section, we demonstrate that thresholding the \emph{likelihood ratio} rather than signal values
+
+In this section, we demonstrate that thresholding the \emph{likelihood ratio} rather than signal values
 yields the finite-sample Bayes optimal procedures.  We consider a special but sufficiently general case of signal 
@@
 \end{proposition}
-}{Introducing part of the proposition as a definition....}
-
-\stilian{NOTE}{This change \& definition
- was motivated by the annoying fact that we could have ties among the likelihood ratios.  Also, to my understanding we
- must LIMIT OURSELVES to estimators of size $s$, so we should limit $|\widehat{S}_{{\rm LRT}}|$ to $s$. \fbox{CORRECT?} I am SORRY if I made a MESS.}
 
@@
 \end{equation*}
-\stilian{This shows that $\widehat S$ cannot be Bayes optimal unless it is a likelihood thresholding estimator.
+This shows that $\widehat S$ cannot be Bayes optimal unless it is a likelihood thresholding estimator.
 Note that with the same argument for every two likelihood thresholding estimators $\widehat S'$
 and $\widehat S''$, we have $ f(x|\widehat{S}') = f(x|\widehat{S}'')$, proving the desired optimality.
-}{\fbox{Please check.} See also the change in the oracle thresholding argument.}
 \end{proof}
@@
 
-\stilian{NEEDS}{WORK}
-
 We conclude with a brief summary on the optimality and sub-optimality of the thresholding procedures in the problem of exact support estimation.

### 2021-02-03 5.URS/5.proofs-Ramsey.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

@@
 This result is a consequence of the celebrated work of \citet{ramsey2009problem}, which 
-gave birth to Ramsey Theory (see e.g., \citet{conlon2015recent}).  
-The Ramsey Theorem and the upper bound \eqref{eq:Ramsey-number} (established first in \cite{erdos1935combinatorial}) are at the heart of the proof of the following result.
+gave birth to Ramsey Theory \citep[see e.g.,][]{conlon2015recent}.  
+The Ramsey Theorem and the upper bound \eqref{eq:Ramsey-number} \citep[established first in][]{erdos1935combinatorial} are at the heart of the proof of the following result.
+A recent improvement on the upper bound is given by \cite{sah:2020}.
 %An excellent introduction to Ramsey theory is given in \url{http://math.mit.edu/~fox/MAT307-lecture05.pdf}.
@@
 
-\begin{proof}[Proof of Proposition \ref{prop:lower-bound-correlation-Ramsey}]
+\begin{proof}%[Proof of Proposition \ref{prop:lower-bound-correlation-Ramsey}]
 By using \eqref{eq:Ramsey-number} and a refinement of the Stirling's formula, 
@@
 
-Now, construct a graph with vertices $\{1,\dots,n\}$ such that there is an edge between nodes $i$ and $j$ if and only if $\rho(i,j) > -\gamma$. 
+Now, construct a graph with vertices $\{1,\dots,n\}$ such that there is an edge between nodes $i$ and $j$ if and only if $\rho(i,j) \ge -\gamma$. 
 In view of \eqref{eq:Ramsey-bounds} and Ramsey's theorem (see e.g., Theorem 1 in \cite{fox2009lecture} or \cite{conlon2015recent} for a recent survey on Ramsey theory), there is a subset of $k$ nodes $K =\{l_1,\dots,l_k\}$, which is either a {\em complete graph} or an {\em independent set}.
+Recall that in a
+complete graph, every two nodes are connected with an edge; while in independent sets, no two nodes are connected.
 
@@
     \begin{equation}
-      R(j) = 
+      R_j = 
       \begin{cases}
-        \frac{1}{\sqrt{1-\rho_j^2}}\left(Z(j) - \rho_j Z(1)\right), &\mbox{if } \rho_j<1,\\
+        \frac{1}{\sqrt{1-\rho_j^2}}\left(Z_j - \rho_j Z_1\right), &\mbox{if } \rho_j<1,\\
         R^* &\mbox{if } \rho_j=1,
@@
     where $R^*$ is an arbitrary zero-mean, unit-variance random variable.
-    It is easy to see that $\var(R(j)) = 1$, and
+    It is easy to see that $\var(R_j) = 1$, and
     \begin{align*}
-    \cov\left(Z(i), Z(j)\right) &= \cov\left(\rho_i Z(1) + \sqrt{1-\rho_i^2} R(i), \; \rho_j Z(1) + \sqrt{1-\rho_j^2} R(j)\right) \\
-        &= \rho_i\rho_j + \sqrt{1-\rho_i^2}\sqrt{1-\rho_j^2} \;\cov\left(R(i), R(j)\right) \\
-        &\ge c^2 + \min\left\{\cov\left(R(i), R(j)\right), 0\right\}.
+    \cov\left(Z_i, Z_j\right) &= \cov\left(\rho_i Z_1 + \sqrt{1-\rho_i^2} R_i, \; \rho_j Z_1 + \sqrt{1-\rho_j^2} R_j\right) \\
+        &= \rho_i\rho_j + \sqrt{1-\rho_i^2}\sqrt{1-\rho_j^2} \;\cov\left(R_i, R_j\right) \\
+        &> c^2 + \min\left\{\cov\left(R_i, R_j\right), 0\right\}.
     \end{align*}
 
-    Therefore, Relation \eqref{eq:positive-correltation-lemma-conclusion} would hold if we can find a set of indices $K = \{l_1,\ldots,l_k\}$ such that $\cov\left(R(i),R(j)\right)>-c^2/2$ for all $i,j\in K$, where $k=|K|=\lfloor\log_2\sqrt{n}\rfloor$.
-    This, however, follows from Proposition \ref{prop:lower-bound-correlation-Ramsey} applied to $\left(R(j)\right)_{j=2}^{n+1}$ with $\gamma = c^2/2$, provided that 
+    Therefore, Relation \eqref{eq:positive-correltation-lemma-conclusion} would hold if we can find a set of indices $K = \{l_1,\ldots,l_k\}$ such that $\cov\left(R_i,R_j\right)\ge -c^2/2$ for all $i,j\in K$, where $k=|K|=\lfloor\log_2\sqrt{n}\rfloor$.
+    This, however, follows from Proposition \ref{prop:lower-bound-correlation-Ramsey} applied to $\left(R_j\right)_{j=2}^{n+1}$ with $\gamma = c^2/2$, provided that 
     $$

### 2021-02-03 5.URS/5.proofs-UDD-URS.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

@@
 
-Going back to the proof of Theorem \ref{thm:Gaussian-weak-dependence}, we observe that Relations \eqref{eq:Gaussian-maxima-lower-expectation-bound} and \eqref{eq:Gaussian-maxima-lower-expectation} imply \eqref{eq:URS-condition-lower-side}, which completes the proof of the `if' part.
-\qed
+Going back to the proof of Theorem \ref{thm:Gaussian-weak-dependence}, we observe that Relations \eqref{eq:Gaussian-maxima-lower-expectation-bound} and \eqref{eq:Gaussian-maxima-lower-expectation} imply \eqref{eq:URS-condition-lower-side}, which completes the proof of the `if' part of
+Theorem \ref{thm:Gaussian-weak-dependence}. \qed
 
@@
 $$
-Then there exists $p_0,t_0 > 0$, and absolute constant $C>0$ such that
+Then there exist $p_0, t_0 > 0$, and an absolute constant $C>0$ such that
 \begin{equation} \label{eq:lemma-AGG-uniform-integrability}
-    \P\left[\xi_p > t \right]\le \exp{\{-Ct^\nu\}}, \quad \text{for all} \quad p>p_0, t>t_0.
+    \P\left[\xi_p > t \right]\le \exp{\{-Ct^\nu\}}, \quad \text{for all} \quad p>p_0,\ t>t_0.
 \end{equation}
@@
 for $t > t_0(\delta)>0$, where $\delta\in(0,1)$ is an arbitrarily small number fixed in advance. 
-This follows from the assumption that $F\in\text{AGG}(\nu)$ and the Definition \ref{def:AGG} of AGG tails.
-Using in \eqref{eq:lemma-AGG-uniform-integrability-proof-1} the explicit expressions for quantiles in \eqref{eq:AGG-quantiles}, we obtain
+This follows from the assumption that $F\in\text{AGG}(\nu)$ and Definition \ref{def:AGG} of the AGG distribution.
+Using in \eqref{eq:lemma-AGG-uniform-integrability-proof-1} the explicit expressions for the quantiles in \eqref{eq:AGG-quantiles}, we obtain
 \begin{equation} \label{eq:lemma-AGG-uniform-integrability-proof-2}
@@
 \end{equation}
-For large $t$, we have $\left(1+o(1)\right)(1-\delta)t^\nu > 1$, so that sum of the first two terms on the right-hand side of \eqref{eq:lemma-AGG-uniform-integrability-proof-2} is negative.
+For large $t$, we have $\left(1+o(1)\right)(1-\delta)t^\nu > 1$, so that the sum of the first two terms on the right-hand side of \eqref{eq:lemma-AGG-uniform-integrability-proof-2} is negative.
 Also, for $p$ larger than some constant $p_0(\delta)$, we have $\log{\log{p}}\left(1+o(1)\right)(1-\delta) > C$ for some constant $C$ that does not depend on $p$.
@@
 as well.
-Since by Lemma \ref{lemma:AGG-maxima-upper-tails}, $\left(M_p/u_p - (1+c_p)\right)_+\to 0$ in probability, Relation \eqref{eq:AGG-max-bound-upper-expectation} follows from the established uniform integrability.
+Since by Lemma \ref{lemma:AGG-maxima-upper-tails}, $\left(M_p/u_p - (1+c_p)\right)_+\to 0$ in probability, Relation \eqref{eq:AGG-max-bound-upper-expectation} follows from the established uniform integrability \citep[see, e.g., Theorem 6.6.1 in][]{resnick:1999book}.
 \end{proof}
@@
 
-Lemma \ref{lemma:Gaussian-maxima-lower-expectation}, which is the key to the proof of the `if' part of Theorem \ref{thm:Gaussian-weak-dependence}, follows immediately from this proposition.
+We will first show that Lemma \ref{lemma:Gaussian-maxima-lower-expectation}, which is the key to the proof of the `if' part of 
+Theorem \ref{thm:Gaussian-weak-dependence}, follows immediately from this proposition.
 
@@
 
-A interesting fact on the relationship between the upper quantiles and the expectation of iid maxima will be needed for the proof of  Proposition \ref{prop:Gaussian-maxima-expectation-lower-bound}.
-The following lemma may be of independent interest.
+The following interesting fact about the relationship between the upper quantiles and the expectation of iid maxima will be needed for the 
+proof of  Proposition \ref{prop:Gaussian-maxima-expectation-lower-bound}.
+%The following lemma may be of independent interest.
 % The following result applies to AGG models as well as a wider range of models, provided that tail densities are monotone discreasing.
@@
 
-\begin{proof}[Proof of Lemma \ref{lemma:expectation-lower}]
+\begin{proof}%[Proof of Lemma \ref{lemma:expectation-lower}]
 % For ease of exposition we let $C_0 = 0$; the case where $C_0 > 0$ can be handled using exactly the same arguments.
-Write 
+The idea comes from an argument in the monograph of \cite{boucheron:lugosi:massart:2013}.  Write 
 $$
@@
 \end{align} 
-We first handle the first term in the summation.
-Since $f$ is decreasing beyond $C_0$, $F$ is concave on $(C_0, \infty)$, and $F^{\leftarrow}$ is convex on $(F(C_0), 1)$.
-By Jensen's inequality, we have
+Focus on the first term in the summation. Since $f$ is decreasing beyond $C_0$, $F$ is concave on $(C_0, \infty)$, and $F^{\leftarrow}$ is convex on $(F(C_0), 1)$. By Jensen's inequality, we have
 \begin{equation*}
@@
 \end{equation*}
-With a direct calculation, one can show that 
+Using the fact that $M_p^U$ is the maximum of iid Uniform$(0,1)$ random variables, with a direct calculation one can show that 
 \begin{equation*}
@@
 and hence
-\begin{align*}
+\begin{align} \label{e:lemma:expectation-lower-bound-1.5}
     \E\left[F^{\leftarrow}(M^{U}_p)\;\big|\;M^{U}_p \ge F(C_0)\right] 
-        &\ge F^{\leftarrow}\left(\left(1-\frac{1}{p+1}\right)\left(\frac{1-F(C_0)^{p+1}}{1-F(C_0)^{p}}\right)\right) \\
+        &\ge F^{\leftarrow}\left(\left(1-\frac{1}{p+1}\right)\left(\frac{1-F(C_0)^{p+1}}{1-F(C_0)^{p}}\right)\right) \nonumber\\
         &\ge F^{\leftarrow}\left(1-\frac{1}{p+1}\right) = u_{p+1}.
-\end{align*}
-Since $\P[M^{U}_p\le m\big|\;M^{U}_p < F(C_0)] = \left(m/F(C_0)\right)^p \le m/F(C_0)$ for $m\le F(C_0))$, we have
+\end{align}
+Now, focus on the second term in \eqref{eq:lemma:expectation-lower-proof-1}. Since 
+$\P[M^{U}_p\le m\big|\;M^{U}_p < F(C_0)] = \left(m/F(C_0)\right)^p \le m/F(C_0)$ for $m\le F(C_0)$, we have
 $$\left(M^{U}_p\;\big|\;M^{U}_p < F(C_0)\right)\stackrel{\text{d}}{\ge} \left(U_1\;\big|\;U_1 < F(C_0)\right),$$
 where and the latter is the uniform distribution on $(0,F(C_0))$.
-Therefore, for the second term of the sum in \eqref{eq:lemma:expectation-lower-proof-1}, by monotonicity of $F^{\leftarrow}$, we obtain
-\begin{align*}
+Therefore, for the second term of the sum in \eqref{eq:lemma:expectation-lower-proof-1}, by the 
+monotonicity of $F^{\leftarrow}$, we obtain
+\begin{align} \label{e:lemma:expectation-lower-bound-1.75}
     \E\left[F^{\leftarrow}(M^{U}_p)\;\big|\;M^{U}_p < F(C_0)\right] 
-        &\ge \E\left[F^{\leftarrow}(U_1)\;\big|\;U_1 < F(C_0)\right] \\
+        &\ge \E\left[F^{\leftarrow}(U_1)\;\big|\;U_1 < F(C_0)\right] \nonumber \\
         &= \E\left[X_1\;\big|\;X_1 < C_0\right].
-\end{align*}
-Finally, since $\P\left[M^{U}_p < F(C_0)\right] = F(C_0)^p = 1 - \P\left[M^{U}_p \ge F(C_0)\right]$, by \eqref{eq:AGG-quantiles}, we have
+\end{align}
+Finally, since $\P\left[M^{U}_p < F(C_0)\right] = F(C_0)^p = 1 - \P\left[M^{U}_p \ge F(C_0)\right]$, by \eqref{e:lemma:expectation-lower-bound-1.5} and \eqref{e:lemma:expectation-lower-bound-1.75}, we have % \eqref{eq:AGG-quantiles},
 \begin{align*}
@@
 
-We now ready to prove Proposition \ref{prop:Gaussian-maxima-expectation-lower-bound}. 
+We are now ready to prove Proposition \ref{prop:Gaussian-maxima-expectation-lower-bound}. 
 This is where the UDD dependence assumption is used.
 
-\begin{proof}[Proof of Proposition \ref{prop:Gaussian-maxima-expectation-lower-bound}]
+\begin{proof}[Proposition \ref{prop:Gaussian-maxima-expectation-lower-bound}]
 % Assume without loss of generality that the $\epsilon(j)$'s have unit variances.
-Define the canonical (pseudo) metric on $S_p$,
+Recall that ${\cal E} = \{\epsilon_p(i),\ i=1,\cdots,p,\ p\in\N\}$ is a Gaussian array with standardized marginals.
+Define the canonical (pseudo) metric on $S_p \subset\{1,\cdots,p\}$,
 $$
@@
 It can be easily checked that the canonical metric takes values between 0 and 2.
-For arbitrary $\delta\in(0,1)$, take $\gamma = \sqrt{2(1-\delta)}$, and
+For an arbitrary $\delta\in(0,1)$, take $\gamma = \sqrt{2(1-\delta)}$, and
 let $\mathcal{N}$ be a $\gamma$-packing of $S_p$. That is, let $\mathcal{N}$ be a subset of $S_p$, such that for any $i,j\in\mathcal{N}$, $i\neq j$, we have $d(i,j)\ge\gamma$, i.e.,
@@
 $$
-for all $i\neq j$, $i,j\in\mathcal{N}$.
-Applying the Sudakov-Fernique inequality (see, e.g., Theorem 2.2.3 in \citep{adler2009random}) to  $\left(\eta(j)\right)_{j\in\mathcal{N}}$ and  $\left(\epsilon(j)\right)_{j\in\mathcal{N}}$, we have
+for all $i\neq j$, $i,j\in\mathcal{N}$. Applying the Sudakov-Fernique inequality (see Theorem \ref{th:Sudakov-Fernique})
+to  $\left(\eta(j)\right)_{j\in\mathcal{N}}$ and  $\left(\epsilon(j)\right)_{j\in\mathcal{N}}$, we have
 \begin{equation}\label{eq:Sudakov-1}
@@
 \end{equation}
-Using the expressions \eqref{eq:AGG-quantiles} for the quantiles 
+Using \eqref{eq:packing-number-lower-bound} and the expressions \eqref{eq:AGG-quantiles} for the quantiles 
 of AGG models (with $\nu=2$ here), we have
@@
 \end{equation}
-since $N(\delta)$ does not depend on $q= q(p)\to \infty$, and that $|\mathcal{N}|\ge q/N(\delta)$.
+since $N(\delta)$ does not depend on $q= q(p)\to \infty$.
 

### 2021-02-03 5.URS/URS.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

@@
 as in the case of iid $\epsilon(i)$'s.  
-Berman's condition is one of the weakest dependence conditions  in the literature for which this result holds.
+Berman's condition is one of the weakest dependence conditions  in the literature for which the convergence in \eqref{eq:Gauss-max-in-distribution} holds. 
 See, e.g., Theorem 4.4.8 in \cite{embrechts2013modelling}, where \eqref{eq:Berman} is described as ``very weak''.
 
-For dependence conditions weaker than \eqref{eq:Berman}, the sequences of normalizing and centering constants in \eqref{eq:Gauss-max-in-distribution} are {\em different} from the iid case, and the corresponding limit is no longer Gumbel; see, for example, Theorems 6.5.1 and  6.6.4 in \cite{leadbetter2012extremes}, and \cite{mccormick1976weak}.
+Instances where the dependence in the time series is so strong that Berman's condition \eqref{eq:Berman} fails have also been studied.  In such 
+cases, one may continue to have \eqref{eq:Gauss-max-in-distribution} but typically the sequences of normalizing and centering constants will be
+{\em different} from the iid case, and the corresponding limit is usually no longer Gumbel; see, for example, Theorems 6.5.1 and  6.6.4 in \cite{leadbetter2012extremes}, and \cite{mccormick1976weak}. 
 % In particular, \cite{mccormick1976weak} derived the normalizing constants when both $r_p\to 0$ monotonically and  $r_p \log p \to \infty$ monotonically, as $p\to\infty$. 
@@
 
-On the other hand, in our high dimensional support estimation context, the notion of relative stability is sufficient and more natural than the finer notions of distributional convergence.
-If one is merely interested in the asymptotic relative stability of the Gaussian maxima, then Berman's condition can be relaxed significantly (see also, Theorem 4.1 of \cite{berman1964limit}). 
+In our high dimensional support estimation context, the notion of relative stability is sufficient and more natural than the finer notions of distributional convergence.
+If one is merely interested in the asymptotic relative stability of the Gaussian maxima, then Berman's condition can be relaxed significantly 
+\citep[see also, Theorem 4.1 of][]{berman1964limit}.
 Observe that by Proposition \ref{prop:UDD-equivalent},  the Berman condition \eqref{eq:Berman} implies UDD and hence relative stability (Theorem \ref{thm:Gaussian-weak-dependence}), i.e.,
@@
 Theorem \ref{thm:Gaussian-weak-dependence} shows that \eqref{eq:Gaussian-URS} holds if the much weaker uniform dependence condition UDD holds. 
-Note that our condition is coordinate free --- neither monotonicity of the sequence $r_p$ nor stationarity of the underlying array is required.
+Note that our condition is coordinate free --- neither monotonicity of the sequence $r_p$ nor stationarity of the underlying array is required. This
+makes it substantially broader than the time series setting in the seminal work \cite{berman1964limit}.
 
@@
 The rest of this chapter is devoted to the proof of the main result, i.e., Theorem \ref{thm:Gaussian-weak-dependence}. 
-We first introduce a key lemma regarding the structure of correlation matrix of high-dimensional random variables.
+We first introduce a key lemma regarding the structure of an {\em arbitrary} correlation matrix of high-dimensional random variables.
 The proof uses a surprising, yet elegant application of Ramsey's Theorem from the study of combinatorics.
@@
 The proof of the `if' part is detailed in Section \ref{sec:UDD=>URS}.
-The arguments there was recently extended to establish bounds on the rate of concentration of maxima in \cite{kartsioukas2019rate}; see also, \cite{tanguy2015some} and references therein for related work on this topic.
+The arguments there have been recently extended to establish bounds on the rate of concentration of maxima in \cite{kartsioukas2019rate}; see also, \cite{tanguy2015some} and the related notion of super-concentration of \cite{chatterjee2014superconcentration}.
 
-\section{Ramsey's Coloring theorem and structure of correlation matrices} 
+\section{Ramsey's  theory and the structure of correlation matrices} 
 \label{sec:Ramsey}
@@
 
-\section{URS implies UDD (`only if' part of Theorem \ref{thm:Gaussian-weak-dependence})} 
+\section{URS implies UDD (Proof of the `only if' part of Theorem \ref{thm:Gaussian-weak-dependence})} 
 \label{sec:URS=>UDD}
@@
 
-\section{UDD implies URS (`if' part of Theorem \ref{thm:Gaussian-weak-dependence})} 
+\section{UDD implies URS (Proof of the `if' part of Theorem \ref{thm:Gaussian-weak-dependence})} 
 \label{sec:UDD=>URS}

### 2021-02-03 6.GWAS/6.proofs-GWAS.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

@@
 \end{align*}
-where the first line uses Mill's ratio for Gaussian distributions (see Section \ref{sec:Gaussian-distributions} and Relation \eqref{eq:Mills-ratio}).
+where the first line uses Mill's ratio for Gaussian distributions (see Section \ref{sec:Gaussian} and Relation \eqref{eq:Mills-ratio}).
 This, combined with \eqref{eq:chi-square-sufficient-1}, completes the proof of the sufficient condition for the Bonferroni's procedure.
@@
 \end{equation}
-On the other hand, we know (by relative stability of iid Gaussians \cite{gao2018fundamental}) that 
+On the other hand, we know (by the relative stability of iid Gaussians, recall Section \ref{sec:Gaussian}) that 
 \begin{equation} \label{eq:chi-square-necessary-6}
@@
 The proof follows the ideas in \cite{arias2017distribution}, and is very similar to the proof of Theorem \ref{thm:Gaussian-error-approx-boundary}. 
-One could in principle obtain the proofs in this section by referencing arguments that have appeared in Section \ref{sec:proofs}.
+One could in principle obtain the proofs in this section by referencing arguments that have appeared in Chapter \ref{chap:phase-transitions}.
 We choose to present the proof here in full to make this section self-contained.
@@
 
-As with the proof of Theorem \ref{thm:chi-squared-approx-boundary}, one could shorten the presentations in this section by referencing arguments Section \ref{sec:proofs}.
-Again, we choose to present the proof in full to make this section self-contained.
+As with the proof of Theorem \ref{thm:chi-squared-approx-boundary}, one could shorten the presentations in this section by 
+referencing arguments in Chapter \ref{chap:phase-transitions}.  Again, we choose to present the proof in full to make this section 
+self-contained.
 

### 2021-02-04 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
remove "Proof (Proof of"

@@
 
-\begin{proof}[Proof of Corollary \ref{cor:log-convex}]
+\begin{proof}[Corollary \ref{cor:log-convex}]
 Since the density of the alternatives $f_{a}(t) = {f(t-\delta)}$ is log-convex on $[K+\delta, \infty)$, by Relation \eqref{eq:concavity-implies-MLR} in the proof of Lemma \ref{lemma:MLR-log-concavity} and appealing to log-convexity (rather than log-concavity), the likelihood ratio

### 2021-02-04 6.GWAS/6.proofs-GWAS.tex
remove "Proof (Proof of"

@@
 We review some properties of the chi-square distributions in Section \ref{sec:chi-square-distributions}, before presenting the proofs of the main theorems on phase transitions in Sections \ref{subsec:proof-chi-squared-exact-boundary}, \ref{subsec:proof-chi-squared-approx-boundary}, and \ref{subsec:proof-chi-squared-mix-boundaries}.
-Results relating signal sizes and effect sizes in association tests will be justified in Section \ref{subsec:proof-signal-size-odds-ratio}.
+%Results relating signal sizes and effect sizes in association tests will be justified in Section \ref{subsec:proof-signal-size-odds-ratio}.
 
@@
 
-\begin{proof}[Proof of Theorem \ref{thm:chi-squared-exact-boundary}]
+\begin{proof}[Theorem \ref{thm:chi-squared-exact-boundary}]
 We first prove the sufficient condition.
@@
 
-\begin{proof}[Proof of necessary condition in Theorem \ref{thm:chi-squared-approx-boundary}]
+\begin{proof}[Necessary condition in Theorem \ref{thm:chi-squared-approx-boundary}]
 Denote the distributions of $\chi^2_\nu(0)$, $\chi^2_\nu(\underline{\Delta})$ and $\chi^2_\nu(\overline{\Delta})$ as $F_0$, $F_{\underline{a}}$, and $F_{\overline{a}}$ respectively.
@@
 
-\begin{proof}[Proof of sufficient condition in Theorem \ref{thm:chi-squared-approx-boundary}]
+\begin{proof}[Sufficient condition in Theorem \ref{thm:chi-squared-approx-boundary}]
 The FDR vanishes by our choice of $\alpha$ and the FDR-controlling property of the BH procedure.
@@
 
-\begin{proof}[Proof of Theorem \ref{thm:chi-squared-exact-approx-boundary}]
+\begin{proof}[Theorem \ref{thm:chi-squared-exact-approx-boundary}]
 % The reduction to equal signal sizes can be achieved 
@@
 
-\begin{proof}[Proof of Theorem \ref{thm:chi-squared-approx-exact-boundary}]
+\begin{proof}[Theorem \ref{thm:chi-squared-approx-exact-boundary}]
 We first show the sufficient condition.
@@
 
-\begin{proof}[Proof of Lemma \ref{lemma:relative-stability-order-statistics}]
+\begin{proof}[Lemma \ref{lemma:relative-stability-order-statistics}]
 Using the Renyi representation for order statistics, we write

### 2021-02-04 3.phase_transitions/3.global-tests.tex
accept changes in proof of Thm 3.1, Prop 5.1 and 5.3, Def. 5.3; other minor updates

@@
  {\em (iv)} In the dense and faint signal setting of {\em (iii)}, the $L_1$ and $L_2$ statistics are both 
- sub-optimal. More precisely, they succeed in the sense of  \eqref{eq:support-recovery-success},  for $\underline{r}>\beta/2-{1}/{4}$, but fail in the 
+ sub-optimal. More precisely, they succeed in the sense of  \eqref{eq:support-recovery-success} when $\underline{r}>\beta/2-{1}/{4}$, but fail in the 
  sense of \eqref{eq:support-recovery-failure} when $\overline{r}<\beta/2-{1}/{4}$.
@@
 \begin{equation}
-    {\color{red}\frac{1}{\sqrt{2p}}}\sum_{i=1}^p \left(x(i)^2-1\right) \implies \mathrm{N}(0,1),  
+    \frac{1}{\sqrt{2p}}\sum_{i=1}^p \left(x(i)^2-1\right) \implies \mathrm{N}(0,1),  
 \end{equation}
@@
  \begin{equation}
-    {\color{red} \frac{1}{\sqrt{2p}}}\left(\sum_{i=1}^p \left(x(i)^2-1\right) - p^{1/2-\beta+2r}\right) \implies \mathrm{N}(0,1).
+    \frac{1}{\sqrt{2p}}\left(\sum_{i=1}^p \left(x(i)^2-1\right) - p^{1/2-\beta+2r}\right) \implies \mathrm{N}(0,1).
 \end{equation}
@@
     \mathrm{Var} \left(\frac{1}{\sqrt{p}} \left(\sum_{i=1}^p |x(i)| - \sqrt{\frac{2}{\pi}}\right) \right) 
-    & = {\color{red}\frac{1}{p}}  (p-p^{1-\beta})(1-2/\pi) + {\color{red}\frac{1}{p}}   p^{1-\beta}\sigma_{Y}^2 \\
+    & = \frac{1}{p} (p-p^{1-\beta})(1-2/\pi) + \frac{1}{p} p^{1-\beta}\sigma_{Y}^2 \\
     & \to 1-2/\pi,

### 2021-02-04 2.background/2.AGG.tex

@@
 % 
-\begin{proof}[Proof of Proposition \ref{prop:quantile}]
+\begin{proof}[Proposition \ref{prop:quantile}]
 By the definition of AGG, for any $\epsilon>0$, there is a constant $C=C(\epsilon)$ such that for all $x\ge C$, we have

### 2021-02-04 2.background/2.risks_relations.tex

@@
 
-\begin{proof}[Proof of Lemma \ref{lemma:risk-exact-recovery-probability}]
+\begin{proof}[Lemma \ref{lemma:risk-exact-recovery-probability}]
 Notice that $\{\widehat{S}=S\}$ implies $\{\widehat{S}\subseteq S\} \cap \{\widehat{S}\supseteq S\}$, therefore we have for every fixed $p$,

### 2021-02-04 3.phase_transitions/3.Gaussian-support-recovery.tex

@@
 
-\begin{proof}[Proof of the necessary condition in Theorem \ref{thm:Gaussian-error-approx-boundary}]
+\begin{proof}[Necessary condition in Theorem \ref{thm:Gaussian-error-approx-boundary}]
 We first show part {\rm (ii)}.  That is, when $\overline{r} < \beta$, no thresholding procedure is able to achieve approximate support recovery.
@@
 
-\begin{proof}[Proof of the sufficient condition in Theorem \ref{thm:Gaussian-error-approx-boundary}]
+\begin{proof}[Sufficient condition in Theorem \ref{thm:Gaussian-error-approx-boundary}]
 We now turn to the sufficient condition, i.e., part {\rm (i)}. That is, when $\underline{r} > \beta$, the Benjamini-Hochberg procedure with 

### 2021-02-04 4.exact_support_recovery/4.heavy-tailed.tex
Addressed the minor typos of R2
I defined the command "\stilian" in the preamble and used it to make changes in response to the minor typos.

Please see reviews/GS_Annotated.pdf.

@@
 
-\begin{proof}[Proof of Theorem \ref{thm:heavy-tails}]
+\begin{proof}[Theorem \ref{thm:heavy-tails}]
 Recall the oracle thresholding procedure $\widehat{S}^* = \left\{i:x(i) \ge x_{[s]}\right\}$, and the set of all thresholding procedures, denoted 
@@
 $$
-where $Z_1$ and $Z_2$ are independent standard $\alpha$-Frechet random variables, i.e., $\P[Z_i \le t] = \exp{\{-x^{-\alpha}\}}$, $x>0$.
+where $Z_1$ and $Z_2$ are independent standard $\alpha$-Frechet random variables, i.e., $\P[Z_i \le x] = \exp{\{-x^{-\alpha}\}}$, $x>0$.
 \end{corollary}

### 2021-02-04 4.exact_support_recovery/4.phase_transition_results.tex

--- 2021-01-16 4.exact_support_recovery/4.phase_transition_results.tex
@@
 We emphasize that Theorem \ref{thm:sufficient} holds for errors with \emph{arbitrary} dependence structures. 
-Intuitively, this is because the maxima of the errors grow at their fastest in the case of independence. 
-Formally, the light-tailed nature of the error distribution allowed us to obtain sharp tail estimates via simple union bounds, valid under arbitrary dependence.
+Intuitively, this is because the maxima of the errors grow at their fastest in the case of independence (recall Remark \ref{rem:iid-max}). 
+Formally, the light-tailed nature of the error distribution allowed us to obtain sharp tail estimates via simple union bounds, 
+valid under arbitrary dependence.
 % Formally, this result stems from the fact that maxima of distributions with \emph{rapidly varying tails} (Definition \ref{def:rapid-variation}) can be bounded from above using quantiles of their marginal distribution, under arbitrary dependence.
@@
 
-\begin{proof}[Proof of Theorem \ref{thm:dense-signals}]
+\begin{proof}[Theorem \ref{thm:dense-signals}]
 The proof is entirely analogous to that of Theorems \ref{thm:sufficient} and \ref{thm:necessary}.

### 2021-02-04 4.exact_support_recovery/4.pointwise.minimax.tex

@@
 Finally, we offer some insights into the support recovery problem in the case when errors have heavier-than-exponential tails in Section \ref{subsec:optimal-procedure-super-exponential}.
-
-\subsection{Point-wise minimax optimality}
-\label{subsec:point-wise-minimax}
-
-Theorems \ref{thm:sufficient} and \ref{thm:necessary} can be cast in the form of an asymptotic minimax statement. 
-% (concealing the gap between sufficient and necessary conditions as pointed out in Remark \ref{rmk:gap-between-sufficient-necessary}).
-
-\begin{corollary}[Point-wise minimax]
-\label{cor:point-wise-minimax}
-Let $\widehat{S}^{\text{Bonf}}$ be the sequence of Bonferroni's procedure described in Theorem \ref{thm:sufficient}. 
-Let also the errors have common $\text{AGG}(\nu)$ distribution $F$ with parameter $\nu>0$, and $\Theta_p^+$ be as defined in \eqref{eq:minimax-signal-config-over}.
-If $\underline{r}>g(\beta)$, then we have
-\begin{equation} \label{eq:point-wise-minimax-above}
-    \limsup_{p\to\infty} \sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P(\widehat{S}^{\text{Bonf}}_p \neq S_p) = 0,
-\end{equation}
-for arbitrary dependence structure of the error array ${\cal E} = \{\epsilon_p(i)\}_p$.
-Let $\cal T$ be the class of thresholding procedures \eqref{eq:thresholding-procedure}. 
-If $\underline{r}<g(\beta)$, then we have
-\begin{equation} \label{eq:point-wise-minimax-below}
-    \liminf_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P(\widehat{S}_p \neq S_p) = 1,
-\end{equation}
-for any error dependence structure such that ${\cal E}\in U(F)$ and ${(-\cal E)}\in U(F)$.
-\end{corollary}
-
-\begin{proof}[Proof of Corollary \ref{cor:point-wise-minimax}]
-The first conclusion \eqref{eq:point-wise-minimax-above} is a restatement of Theorem \ref{thm:sufficient}.
-
-For the second statement \eqref{eq:point-wise-minimax-below}, since $\underline{r}<g(\beta)$, we can pick a sequence $\mu^*\in\Theta_p^+(\beta, \underline{r})$ such that $|S_p| = \lfloor p^{1-\beta}\rfloor$, with signals having the same signal size $\mu(i)=(2r\log{p})^{1/\nu}$ for all $i\in S_p$, where $\underline{r}<{r}<g(\beta)$.
-For this particular choice of $\mu^*$ we have $\mu^*\in\Theta_p^-(\beta, \overline{r})$ where $r<\overline{r}<g(\beta)$,
-and according to Theorem \ref{thm:necessary}, we obtain $\lim_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \mathbb P[\widehat{S}_p \neq S_p] = 1$, for all dependence structures in the URS class.
-\end{proof}
-
-\begin{remark}
-Theorem \ref{thm:necessary} is a stronger result than the traditional minimax claim in Relation \eqref{eq:point-wise-minimax-below}.
-Indeed,  \eqref{eq:classification-impossible-dependent} involves an infimum (over the class $\Theta^-_p$) while \eqref{eq:point-wise-minimax-below} has a supremum (over the class $\Theta^+_p$).
-
-On the other hand, Corollary \ref{cor:point-wise-minimax} is more informative than many minimax-type statements, since it applies ``point-wise'' to any fixed error dependence structure in the URS class.
-\end{remark}
-
-\begin{remark}
-Corollary \ref{cor:point-wise-minimax} echoes Remark \ref{rmk:dependence-assumptions}: for a very large class of dependence structures, we cannot improve upon Bonferroni's procedure in exact support recovery problems (asymptotically), unless we look beyond thresholding procedures.
-% There is a limited amount of literature on non-thresholding procedures that utilize the error dependence structures to improve power.
-% A notable effort was made by \citet{jin2014optimality}, where the performance (in terms of Hamming loss) of a so-called graphlet screening procedure was studied. 
-\end{remark}
-
-% This is an enhancement (in the asymptotic sense) of the minimax results in Section 4.1 of \cite{butucea2018variable}, where the supremum was taken over the dependence structures.

### 2021-02-04 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex

@@
 
-In studying support recovery problems \citep[e.g.,][]{arias2017distribution}, restrictions to the thresholding procedures 
-are sometimes justified by arguing that such procedures are the ``reasonable'' choice for estimating the support set.
+In studying support recovery problems, restrictions to the thresholding procedures 
+are sometimes justified by arguing that such procedures are the ``reasonable'' choice for estimating the support set \citep[e.g.,][]{arias2017distribution}.
 We show in this chapter that, perhaps surprisingly, for general error models, thresholding procedures are not always 
@@
 We shall identify the optimal procedure for support recovery problems under a Bayesian setting with general distributional assumptions (including but not limited to additive models \eqref{eq:model-additive}).
-Specifically, we assume that there is an ordered set $P = (i_1,\ldots,i_s)$, $i_i\in\{1,\ldots,p\}$, and $s$ (not necessarily equal) densities $f_{1}, \ldots, f_{s}$, such that the observations indexed by $P$ have corresponding densities.
+Specifically, we assume that there is an ordered set $P = (i_1,\ldots,i_s)$, $i_i\in\{1,\ldots,p\}$, and $s$ not necessarily equal densities $f_{1}, \ldots, f_{s}$, such that the observations indexed by set $P$ have corresponding densities.
 That is,
@@
 \end{equation}
-for all distinct $1\le i_1, \ldots, i_s\le p$.
+for all distinct $1\le i_1 < \ldots < i_s\le p$.
 Consequently, the unordered support $S=\{i_1,\ldots,i_s\}$ is distributed uniformly in the collection of all set of size $s$, with the unordered uniform distribution $\pi^{\text{u}}$.
@@
 $$
-where the probability is taken over the randomness in the observations only.
-The Bayes optimal procedures should minimize 
+where the probability is taken over the randomness in the observations $x$ only.
+The Bayes optimal procedures, by definitions, should minimize 
 \begin{equation} \label{eq:Bayes-risk}
@@
 
-If, however, the sparsity $s = |S|$ of the problem is known, then a natural estimator for $S$ would be based on the set of top $s$ order statistics.
+If, however, the sparsity $s = |S|$ of the problem is known, then a ``natural'' estimator for $S$ would be based on the set of top $s$ order statistics.
 Such estimators will be referred to as oracle thresholding estimators and formally defined next.
@@
 
-By the optimality of the Bayes classifier \citep[see, e.g.,][]{domingos1997optimality}, a set estimator that maximizes the probability of support recovery is such that
+By the optimality of the Bayes classifier \citep[see, e.g.,][]{domingos1997optimality}, a set estimator that maximizes the probability of support recovery is one such that
 $$
@@
 $j \in \widehat{S}$ and $j' \not \in \widehat{S}$ such that $x(j) < x(j')$.
-We exchange the labels of $x(j)$ and $x(j')$, and form a new estimate 
+We exchange the classifications of $x(j)$ and $x(j')$, and form a new estimate 
 $\widehat{S}\,' = \big(\widehat{S}\setminus\{j\}\big)\cup\{j'\}$.
@@
 are typically unknown. Still, some insights can be gained by virtue of Proposition \ref{prop:likelihood-ratio-thresholding}.
-In particular, when MLR fails (or equivalently, when the errors in model \eqref{eq:model-additive} do not have log-concave densities), data thresholding is sub-optimal.
+In particular, when MLR fails (for example, when the errors in model \eqref{eq:model-additive} do not have log-concave densities), data thresholding is sub-optimal.
 

### 2021-02-04 5.URS/5.proofs-UDD-URS.tex

@@
 
-\begin{proof}[Proof of Lemma \ref{lemma:AGG-maxima-upper-tails}]
+\begin{proof}[Lemma \ref{lemma:AGG-maxima-upper-tails}]
 Recall by \eqref{eq:AGG-quantiles} that 
@@
 \end{lemma}
-\begin{proof}[Proof of Lemma \ref{lemma:AGG-max-uniform-integrability}]
+\begin{proof}[Lemma \ref{lemma:AGG-max-uniform-integrability}]
 Recalling that $(1+c_p)u_p = u_{p\log{p}}$, and by applying the union bound as in \eqref{eq:AGG-maxima-upper-tails-proof-1}, we have
@@
 
-\begin{proof}[Proof of Corollary \ref{cor:AGG-max-upper-bound-expectation}]
+\begin{proof}[Corollary \ref{cor:AGG-max-upper-bound-expectation}]
 Since $c_p\ge0$ is a sequence converging to 0, we have $c_p < 1$ for $p \ge p_0$. Hence for any $t>0$, we have
@@
 
-\begin{proof}[Proof of Lemma \ref{lemma:Gaussian-maxima-lower-expectation}]
+\begin{proof}[Lemma \ref{lemma:Gaussian-maxima-lower-expectation}]
 We start with the identity

### 2021-02-04 6.GWAS/6.chi-square-distributions.tex

@@
 
-\begin{proof}[Proof of Lemma \ref{lemma:rapid-variation-chisq}]
+\begin{proof}[Lemma \ref{lemma:rapid-variation-chisq}]
 When $\nu=1$, the chi-square distribution reduces to a squared Normal, and \eqref{eq:rapid-variation-chisq} follows from the rapid variation of the standard Normal distribution.
@@
 
-\begin{proof}[Proof of Lemma \ref{lemma:stochastic-monotonicity}]
+\begin{proof}[Lemma \ref{lemma:stochastic-monotonicity}]
 Recall that non-central chi-square distributions can be written as sums of $\nu-1$ standard normal random variables and a non-central normal random variable with mean $\sqrt{\lambda}$ and variance 1,
@@
 
-\begin{proof}[Proof of Lemma \ref{lemma:chisq-quantiles}]
+\begin{proof}[Lemma \ref{lemma:chisq-quantiles}]
 The case where $\nu=1$ follows from the well-known formula for Normal quantiles (see, e.g., Proposition 1.1 in \cite{gao2018fundamental})

### 2021-02-04 6.GWAS/6.odds-and-power.tex

@@
 
-Proposition \ref{prop:signal-size-odds-ratio} is derived in Section \ref{subsec:proof-signal-size-odds-ratio}.
+\begin{proof}
+	We parametrize the 2-by-2 multinomial distribution with the parameter $\delta$, 
+	\begin{equation} \label{eq:reparametrize-2-by-2-table-1}
+	\mu_{11} = \phi_1\theta_1+\delta,\quad 
+	\mu_{12} = \phi_1\theta_2-\delta,\quad 
+	\mu_{21} = \phi_2\theta_1-\delta,\quad 
+	\mu_{22} = \phi_2\theta_2+\delta.
+	\end{equation}
+	By relabelling of categories, we may assume $0<\theta_1,\phi_1\le1/2$ without loss of generality.
+	Note that $\delta$ must lie within the range $[\delta_\mathrm{min}, \delta_\mathrm{max}]$, where
+	$$
+	\delta_\mathrm{min} := \max\{-\phi_1\theta_1, -\phi_2\theta_2, \phi_1\theta_2-1, \phi_2\theta_1-1\} 
+	= -\phi_1\theta_1,
+	$$
+	and
+	$$
+	\delta_\mathrm{max} := \min\{1-\phi_1\theta_1, 1-\phi_2\theta_2, \phi_1\theta_2, \phi_2\theta_1\}
+	= \min\{\phi_1\theta_2, \phi_2\theta_1\},
+	$$
+	in order for $\mu_{ij}\ge0$ for all $i,j\in \{1,2\}$.
+	Under this parametrization, Relation \eqref{eq:odds-ratio} then becomes
+	\begin{equation} \label{eq:odds-ratio-delta}
+	\text{R} = \frac{\mu_{11}\mu_{22}}{\mu_{12}\mu_{21}}
+	= \frac{\phi_1\theta_1\phi_2\theta_2 + \delta(\phi_1\theta_1+\phi_2\theta_2)+\delta^2}{\phi_1\theta_1\phi_2\theta_2 - \delta(\phi_1\theta_2+\phi_2\theta_1)+\delta^2},
+	\end{equation}
+	which is one-to-one and increasing in $\delta$ on $(\delta_\mathrm{min}, \delta_\mathrm{max})$.
+	Equation \eqref{eq:signal-size-chisq} becomes
+	\begin{equation} \label{eq:signal-size-chisq-delta}
+	w^2 = \sum_{i=1}^2 \sum_{j=1}^2 \frac{(\mu_{ij} - \phi_i\theta_j)^2}{\phi_i\theta_j}
+	= \delta^2\sum_i\sum_j \frac{1}{\phi_i\theta_j}
+	= \frac{\delta^2}{\phi_1\theta_1\phi_2\theta_2},
+	\end{equation}
+	Solving for $\delta$ in \eqref{eq:odds-ratio-delta}, and plugging into the expression for signal size \eqref{eq:signal-size-chisq-delta} yields Relation \eqref{eq:signal-size-odds-ratio}.
+
+	The other three cases ($1/2\le\theta_1,\phi_1\le1$; $0<\theta_1\le1/2\le\phi_1\le1$; and $0\le\phi_1\le1/2\le\theta_1\le1$) may be obtained similarly, or by appealing to the symmetry of the problem.
+\end{proof}
 
@@
 
+\begin{proof}
+	As in the proof of Proposition \ref{prop:signal-size-odds-ratio}, we examine the case where $0<\theta_1,\phi_1\le1/2$, and leave the other three cases an exercise.
+	Take the first derivative of the expression for $w^2$ in equation \eqref{eq:signal-size-chisq-delta} with respect to $\delta$, it is evident that $w^2(\delta)$ is decreasing on $[\delta_\mathrm{min},0)$, increasing on $(0,\delta_\mathrm{max}]$, with limits
+	$$
+	\lim_{d\to \delta_\mathrm{min}} w^2(\delta) = \frac{\phi_1\theta_1}{\phi_2\theta_2},
+	\quad
+	\text{and}
+	\quad
+	\lim_{d\to \delta_\mathrm{max}} w^2(\delta) = \min\left\{\frac{\phi_1\theta_2}{\phi_2\theta_1}, \frac{\phi_2\theta_1}{\phi_1\theta_2}\right\}.
+	$$
+\end{proof}
+
 Corollary \ref{cor:signal-limits-OR} immediately implies that balanced designs with roughly equal number of cases and controls are not necessarily the most informative.

### 2021-02-04 preamble.tex

@@
 normal random variables.
-\stilian{This is in stark contrast with the behavior of sums, commonly studied under short- and long-range dependence conditions \citep[see e.g.][]{dedecker:doukhan:etal:2007,pipiras:taqqu:2017}.
+This is in stark contrast with the behavior of sums, commonly studied under short- and long-range dependence conditions \citep[see e.g.][]{dedecker:doukhan:etal:2007,pipiras:taqqu:2017}.
 Simply put, the notion of weak dependence that entails that the maxima of dependent variables concentrate at the
-same rate as in the case of independence is fundamentally weaker than the conventional mixing conditions widely used in the study of sums.}{\fbox{added}}
+same rate as in the case of independence is fundamentally weaker than the conventional mixing conditions widely used in the study of sums.
 
-\stilian{Our}{\xout{These}} probabilistic contributions may be of independent interest and extend classic work of \cite{berman1964limit}. 
+Our probabilistic contributions may be of independent interest and extend classic work of \cite{berman1964limit}. 
 Concentration of maxima is a type of super-concentration phenomenon studied also in \cite{chatterjee2014superconcentration} 

### 2021-02-04 6.URS/6.numerical.tex
rename files and folders according to the new structure

--- 2020-08-17 5.URS/5.numerical.tex
@@
 Lower-right panel of Figure \ref{fig:phase-simulated-very-dependent} demonstrates in this example that the signal support can be recovered as long as the signal sizes are larger than $4(1-\beta)$.
-
-\medskip
-
-For completeness, we verify the claims in Example \ref{exmp:counter-example}.
-
-\begin{proof}[Proof of claims in Example \ref{exmp:counter-example}]
-Recall that $\widehat{S}^* = \{j:x(j)>t_p^*\}$, where $t_p^* = \sqrt{2(1-\beta)\log{p}}$. 
-Analogous to \eqref{eq:Bonferroni-FWER-control} in the proof of Theorem \ref{thm:sufficient}, we have
-\begin{align*}
-    \P\left[\widehat{S} \subseteq S\right] 
-        &= 1 - \P\left[\max_{j\in S^c}x(j) > t_p^*\right] 
-        = 1 - \P\left[\max_{j\in S^c}\epsilon(j) > t_p^*\right] \nonumber \\
-      % \ge 1 - \P\left[\max_{j\in\{1,\ldots,p\}}\epsilon(j) > t_p\right] \nonumber \\
-        &\ge 1 - \P\left[\max_{j\in\{1,\ldots,p\}}\epsilon(j) > t_p^*\right] 
-        \ge 1 - \P\left[\max_{j\in\{1,\ldots,\lfloor p^{1-\beta}\rfloor\}}\widetilde{\epsilon}(j) > t_p^*\right]
-\end{align*}
-where $\left(\widetilde{\epsilon}\right)_{j=1}^{\lfloor p^{1-\beta}\rfloor}$'s are independent Gaussian errors; in the last inequality we used the assumption that there are at most $\lfloor p^{1-\beta}\rfloor$ independently distributed Gaussian errors in $\left(\epsilon_p(j)\right)_{j=1}^p$.
-By Example \ref{exmp:FWER-controlling_procedures} (with $\lfloor p^{1-\beta}\rfloor$ taking the role of $p$), we know that the FWER goes to 0 at a rate of 
-$\left(2\log{\lfloor p^{1-\beta}\rfloor}\right)^{-1/2}$.
-Therefore, the probability of no false inclusion converges to 1.
-
-On the other hand, since the signal sizes are no smaller than $(\nu\underline{r}\log p)^{1/\nu}$, similar to \eqref{eq:sufficient-proof-eq1}, we obtain
-\begin{align}
-    \P\left[\widehat{S} \supseteq S\right] 
-    &\ge \P\left[\min_{j\in S}\epsilon(j) > \sqrt{2(1-\beta)\log{p})} - \sqrt{2\underline{r}\log{p}} \right] \nonumber \\
-    &= \P\left[\max_{j\in S}\left(-\epsilon(j)\right) < \sqrt{2\log{p})}\left(\sqrt{\underline{r}}-\sqrt{1-\beta}\right) \right] \nonumber \\
-    &= \P\left[\frac{\max_{j\in S}(-\epsilon(j))}{u_{|S|}} < \frac{\sqrt{\underline{r}}-\sqrt{1-\beta}}{\sqrt{1-\beta}}\left(1+o(1)\right) \right], \label{eq:sufficient-proof-counter-example}
-\end{align}
-where in the last line we used the quantiles \eqref{eq:AGG-quantiles}.
-Since the minimum signal size is bounded below by $\underline{r} > 4(1-\beta)$, the right-hand-side of the inequality in \eqref{eq:sufficient-proof-counter-example} converges to a constant strictly larger than 1.
-While the left-hand-side, by Slepian's Lemma \cite{slepian1962one}, is stochastically smaller than a r.v.
-going to 1, i.e.,
-\begin{equation}
-  \frac{1}{u_{|S|}} \max_{j\in S}(-\epsilon(j)) \stackrel{d}{\le} \frac{1}{u_{|S|}} \max_{j\in S} \epsilon^*(j) \stackrel{\P}{\longrightarrow} 1,
-\end{equation}
-where $\left({\epsilon^*}\right)_{j=1}^{\lfloor p^{1-\beta}\rfloor}$'s are independent Gaussian errors.
-Therefore the probability in \eqref{eq:sufficient-proof-counter-example} must also converge to 1.
-\end{proof}

### 2021-02-04 6.URS/6.proofs-URS-UDD.tex
rename files and folders according to the new structure

--- 2020-08-17 5.URS/5.proofs-URS-UDD.tex
@@
 
-Relations \eqref{eq:Slepian-conclusion-condition-1} and \eqref{eq:Slepian-conclusion-condition-2}, by Slepian's Lemma \cite{slepian1962one}, also imply,
+Relations \eqref{eq:Slepian-conclusion-condition-1} and \eqref{eq:Slepian-conclusion-condition-2}, by Slepian's Lemma (recall
+Theorem \ref{thm:Slepian-lemma}), also imply,
 \begin{equation}\label{eq:Slepian-conclusion}
@@
 $$
-This contradicts the definition of URS (with the particular choice of $S_p:=K_p(c)$), and the proof of the `only if' part is complete.
+This contradicts the definition of URS (with the particular choice of $S_p:=K_p(c)$), and the proof of the `only if' part of 
+Theorem \ref{thm:Gaussian-weak-dependence} is complete.

### 2021-02-04 7.GWAS/7.chi-square.tex
rename files and folders according to the new structure

--- 2020-12-22 6.GWAS/6.chi-square.tex
@@
-Similar to the analysis of additive error models in Chapter \ref{chap:phase-transitions}, we will work with triangular arrays of chi-square models \eqref{eq:model-chisq} indexed by $p$.
+Similar to the analysis of additive error models in Chapter \ref{chap:phase-transitions}, we will work with triangular arrays of chi-square models \eqref{eq:model-chisq-Chapter6} indexed by $p$.
 We adopt the same parametrization for the sparsity of the non-centrality parameter vectors $\lambda = \lambda_p$,
@@
 \begin{theorem} \label{thm:chi-squared-exact-boundary}
-Consider the high-dimensional chi-squared model \eqref{eq:model-chisq} with signal sparsity and size as described in \eqref{eq:signal-sparsity} and \eqref{eq:signal-size}.
+Consider the high-dimensional chi-squared model \eqref{eq:model-chisq-Chapter6} with signal sparsity and size as described in \eqref{eq:signal-sparsity} and \eqref{eq:signal-size}.
 The function 
@@
 \begin{theorem} \label{thm:chi-squared-approx-boundary}
-Consider the high-dimensional chi-squared model \eqref{eq:model-chisq} with signal sparsity and size as described in \eqref{eq:signal-sparsity} and \eqref{eq:signal-size}.
+Consider the high-dimensional chi-squared model \eqref{eq:model-chisq-Chapter6} with signal sparsity and size as described in \eqref{eq:signal-sparsity} and \eqref{eq:signal-size}.
 The function 
@@
 
-The all four Theorems so far focus only on the idealized models \eqref{eq:model-chisq} where statistics are \emph{independent}.
+The all four Theorems so far focus only on the idealized models \eqref{eq:model-chisq-Chapter6} where statistics are \emph{independent}.
 Support recovery problems under dependent observations remain to be explored.
@@
 Comparing Theorems \ref{thm:chi-squared-exact-approx-boundary} to \ref{thm:Gaussian-error-exact-approx-boundary} and Theorems \ref{thm:chi-squared-approx-exact-boundary} to \ref{thm:Gaussian-error-approx-exact-boundary}, we see that the phase transition boundaries under the two types of alternatives are also identical in the exact-approximate and approximate-exact support recovery problems.
-The additional uncertainty in the two-sided alternatives do not call for larger signal sizes asymptotically in these problems.
-
-\medskip
 
@@
 This was analyzed in \cite{donoho2004higher}.
+
+Therefore, all phase transition boundaries coincide with those in the additive error models obtained in Chapter \ref{chap:phase-transitions} under their respective parametrizations.
+% and Figure \ref{fig:phase-chi-squared} continues to apply.
+This indicates vanishing differences between the difficulties of the one-sided and two-sided alternatives in the Gaussian additive error model \eqref{eq:model-additive}.
+The additional uncertainty in the two-sided alternatives do not call for larger signal sizes in these problems, asymptotically.

### 2021-02-04 7.GWAS/7.numerical.tex
rename files and folders according to the new structure

--- 2020-08-17 6.GWAS/6.numerical.tex
@@
 The nominal FWER levels vanishes slowly, in line with the assumptions in Theorem \ref{thm:chi-squared-exact-boundary}.
-Experiments were repeated 1000 times at each of the 400 sparsity-signal-size combinations, for dimensions $p=10^2, 10^3$, and $10^4$.
+Experiments were repeated 1000 times at each of the 400 sparsity-signal-size combinations, 
+%for dimensions $p=10^2, 10^3$, and $10^4$.
+for dimension $p=10^4$.
 
 The empirical probabilities of exact support recovery under Bonferroni's procedure are shown in Figure \ref{fig:phase-simulated-chi-squared}.
-The numerical results suggest not only good accuracy of the predicted boundaries in high-dimensions ($p=10^4$, right panels of Figure \ref{fig:phase-simulated-chi-squared}), but also practical relevance of the theoretical predictions in moderate dimensions ($p=100$, left panels of Figure \ref{fig:phase-simulated-chi-squared}).
+The numerical results suggest good accuracy of the predicted boundaries in high-dimensions 
+(left panels of Figure \ref{fig:phase-simulated-chi-squared}).
+%but also practical relevance of the theoretical predictions in moderate dimensions 
+%($p=100$, left panels of Figure \ref{fig:phase-simulated-chi-squared}).
 
@@
 	\centering
-      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu1_p100.eps}
-      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu1_p1000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu1_p10000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu2_p100.eps}
-      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu2_p1000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu2_p10000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu3_p100.eps}
-      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu3_p1000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu3_p10000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu6_p100.eps}
-      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu6_p1000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu6_p10000.eps}
-      \caption{The empirical probability of exact support recovery of Bonferroni's procedure in the chi-squared model \eqref{eq:model-chisq}. 
-      We simulate $\nu=1, 2, 3, 6$ (first to last row), at dimensions $p=10^2, 10^3, 10^4$ (left to right column), for a grid of sparsity levels $\beta$ and signal sizes $r$.
+	\includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_strong_boundary_chi-squared_nu1_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu1_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu1_p10000.eps}
+
+	\includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_strong_boundary_chi-squared_nu2_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu2_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu2_p10000.eps}
+
+	\includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_strong_boundary_chi-squared_nu3_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu3_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu3_p10000.eps}
+
+	\includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_strong_boundary_chi-squared_nu6_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu6_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu6_p10000.eps}
+	\caption{The empirical risks of exact, approximate, and approximate-exact support recovery (left to right) in the chi-squared model \eqref{eq:model-chisq} with Bonferroni's procedure and the Benjamini-Hochberg procedure.
+		We display results as a heatmap for $\nu=1, 2, 3, 6$ (first to last row) at dimension $p=10^4$ (left to right column), for a grid of sparsity levels $\beta$ and signal sizes $r$.
 		The experiments were repeated 1000 times for each sparsity-signal size combination; darker color indicates higher probability of exact support recovery.  
-      Numerical results are in general agreement with the boundaries described in Theorem \ref{thm:chi-squared-exact-boundary}; for large $\nu$'s, the phase transitions take place somewhat above the predicted boundaries.
-      The boundary for the approximate support recovery (Theorem \ref{thm:chi-squared-approx-boundary}) and the detection boundary (see Donoho and Jin (2004)) are plotted for comparison.} 
+		Numerical results are in general agreement with the boundaries described in Theorem \ref{thm:chi-squared-exact-boundary}; for large $\nu$'s, the phase transitions take place somewhat above the predicted boundaries.}
 	\label{fig:phase-simulated-chi-squared}
 \end{figure}
+
+%\begin{figure}
+%      \centering
+%      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu1_p100.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu1_p1000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu1_p10000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu2_p100.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu2_p1000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu2_p10000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu3_p100.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu3_p1000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu3_p10000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu6_p100.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu6_p1000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_phase_diagram_chi-squared_nu6_p10000.eps}
+%      \caption{The empirical probability of exact support recovery of Bonferroni's procedure in the chi-squared model \eqref{eq:model-chisq}. 
+%      We simulate $\nu=1, 2, 3, 6$ (first to last row), at dimensions $p=10^2, 10^3, 10^4$ (left to right column), for a grid of sparsity levels $\beta$ and signal sizes $r$.
+%      The experiments were repeated 1000 times for each sparsity-signal size combination; darker color indicates higher probability of exact support recovery.  
+%      Numerical results are in general agreement with the boundaries described in Theorem \ref{thm:chi-squared-exact-boundary}; for large $\nu$'s, the phase transitions take place somewhat above the predicted boundaries.
+%      The boundary for the approximate support recovery (Theorem \ref{thm:chi-squared-approx-boundary}) and the detection boundary (see Donoho and Jin (2004)) are plotted for comparison.} 
+%      \label{fig:phase-simulated-chi-squared}
+%\end{figure}
 
@@
 The nominal FDR level for the BH procedure is set at $1/(5{\log{p}})$, therefore slowly vanishing, in line with the assumptions in Theorem \ref{thm:chi-squared-approx-boundary}; all other parameters are identical to that in the experiments for exact support recovery.
-Results of the experiments are shown in Figure \ref{fig:one-vs-two-sided-approx_support_recovery} and Figure \ref{fig:phase-simulated-chi-squared-approx-boundary}.
+Results of the experiments are shown in Figure \ref{fig:one-vs-two-sided-approx_support_recovery} and in the middle column of Figure \ref{fig:phase-simulated-chi-squared}.
 
@@
 $$
-and visualize results of the experiments in Figure \ref{fig:phase-simulated-chi-squared-approx-exact-boundary}.
+and visualize results of the experiments in the right column of Figure \ref{fig:phase-simulated-chi-squared}.
 Notice that the BH procedure sets its threshold somewhat higher than the oracle, especially for small $\beta$'s. 
@@
 
-\begin{figure}
-      \centering
-      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu1_p100.eps}
-      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu1_p1000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu1_p10000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu2_p100.eps}
-      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu2_p1000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu2_p10000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu3_p100.eps}
-      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu3_p1000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu3_p10000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu6_p100.eps}
-      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu6_p1000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu6_p10000.eps}
-      \caption{The estimated risk of approximate support recovery $\mathrm{risk}^{\mathrm{A}}$ (see \eqref{eq:risk-approximate}) of the Benjamini-Hochberg procedure in the chi-squared model \eqref{eq:model-chisq}.
-      We simulate $\nu=1, 2, 3, 6$ (first to last row), at dimensions $p=10^2, 10^3, 10^4$ (left to right column), for a grid of sparsity levels $\beta$ and signal sizes $r$.
-      The experiments were repeated 1000 times for each sparsity-signal size combination; darker color indicates higher larger $\mathrm{risk}^{\mathrm{A}}$. 
-      Numerical results are generally in agreement with the boundaries described in Theorem \ref{thm:chi-squared-approx-boundary}; for large $\nu$'s, the phase transitions take place somewhat above the predicted boundaries.
-      The boundary for the exact support recovery problem (Theorem \ref{thm:chi-squared-exact-boundary}) and the detection boundary (see Donoho and Jin (2004)) are plotted for comparison.} 
-      \label{fig:phase-simulated-chi-squared-approx-boundary}
-\end{figure}
-
-\begin{figure}
-      \centering
-      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu1_p100.eps}
-      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu1_p1000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu1_p10000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu2_p100.eps}
-      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu2_p1000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu2_p10000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu3_p100.eps}
-      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu3_p1000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu3_p10000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu6_p100.eps}
-      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu6_p1000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu6_p10000.eps}
-      \caption{The estimated risk of approximate-exact support recovery $\mathrm{risk}^{\mathrm{EA}}$ (see \eqref{eq:risk-approx-exact}) of the Benjamini-Hochberg procedure in the chi-squared model \eqref{eq:model-chisq}.
-      We simulate $\nu=1, 2, 3, 6$ (first to last row), at dimensions $p=10^2, 10^3, 10^4$ (left to right column), for a grid of sparsity levels $\beta$ and signal sizes $r$.
-      The experiments were repeated 1000 times for each sparsity-signal size combination; darker color indicates higher larger $\mathrm{risk}^{\mathrm{EA}}$. 
-      Numerical results are generally in agreement with the boundaries described in Theorem \ref{thm:chi-squared-approx-exact-boundary}; for small $\beta$'s and large $\nu$'s, the phase transitions take place somewhat above the predicted boundaries.
-      Other boundaries in the support recovery and the detection problems are plotted for comparison.} 
-      \label{fig:phase-simulated-chi-squared-approx-exact-boundary}
-\end{figure}
+%
+%\begin{figure}
+%      \centering
+%      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu1_p100.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu1_p1000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu1_p10000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu2_p100.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu2_p1000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu2_p10000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu3_p100.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu3_p1000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu3_p10000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu6_p100.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu6_p1000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu6_p10000.eps}
+%      \caption{The estimated risk of approximate support recovery $\mathrm{risk}^{\mathrm{A}}$ (see \eqref{eq:risk-approximate}) of the Benjamini-Hochberg procedure in the chi-squared model \eqref{eq:model-chisq}.
+%      We simulate $\nu=1, 2, 3, 6$ (first to last row), at dimensions $p=10^2, 10^3, 10^4$ (left to right column), for a grid of sparsity levels $\beta$ and signal sizes $r$.
+%      The experiments were repeated 1000 times for each sparsity-signal size combination; darker color indicates higher larger $\mathrm{risk}^{\mathrm{A}}$. 
+%      Numerical results are generally in agreement with the boundaries described in Theorem \ref{thm:chi-squared-approx-boundary}; for large $\nu$'s, the phase transitions take place somewhat above the predicted boundaries.
+%      The boundary for the exact support recovery problem (Theorem \ref{thm:chi-squared-exact-boundary}) and the detection boundary (see Donoho and Jin (2004)) are plotted for comparison.} 
+%      \label{fig:phase-simulated-chi-squared-approx-boundary}
+%\end{figure}
+%
+%
+%\begin{figure}
+%      \centering
+%      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu1_p100.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu1_p1000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu1_p10000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu2_p100.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu2_p1000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu2_p10000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu3_p100.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu3_p1000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu3_p10000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu6_p100.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu6_p1000.eps}
+%      \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu6_p10000.eps}
+%      \caption{The estimated risk of approximate-exact support recovery $\mathrm{risk}^{\mathrm{EA}}$ (see \eqref{eq:risk-approx-exact}) of the Benjamini-Hochberg procedure in the chi-squared model \eqref{eq:model-chisq}.
+%      We simulate $\nu=1, 2, 3, 6$ (first to last row), at dimensions $p=10^2, 10^3, 10^4$ (left to right column), for a grid of sparsity levels $\beta$ and signal sizes $r$.
+%      The experiments were repeated 1000 times for each sparsity-signal size combination; darker color indicates higher larger $\mathrm{risk}^{\mathrm{EA}}$. 
+%      Numerical results are generally in agreement with the boundaries described in Theorem \ref{thm:chi-squared-approx-exact-boundary}; for small $\beta$'s and large $\nu$'s, the phase transitions take place somewhat above the predicted boundaries.
+%      Other boundaries in the support recovery and the detection problems are plotted for comparison.} 
+%      \label{fig:phase-simulated-chi-squared-approx-exact-boundary}
+%\end{figure}
+%

### 2021-02-04 supplement/other-boundaries.tex
rename files and folders according to the new structure

--- 2020-08-17 4.exact_support_recovery/4.other-boundaries.tex
@@
 The strong classification boundaries extend beyond the AGG models.
-As our analysis in Section \ref{sec:boundary} suggests, all additive error models where the errors have URS maxima demonstrate this phase transition phenomenon under appropriate parametrization of the sparsity and signal sizes.
-We derive explicit boundaries for two additional classes of models under the general form of the additive noise models \eqref{eq:model-additive}, with heavier and lighter tails than the AGG models, respectively.
+As our analysis in Chapter \ref{chap:exact-support-recovery} suggests, all additive error models where the errors have URS maxima exhibit this phase transition phenomenon under appropriate parametrization of the sparsity and signal sizes.
+We derive explicit boundaries for two additional classes of models under the general form of the additive noise models \eqref{eq:model-additive} with 
+{\em heavier} and {\em lighter} tails than the AGG models, respectively.
 

### 2021-03-10 7.GWAS/7.GWAS-phase-transitions.tex
ch 7
i implemented my minor edits to ch 7.  I have 3 paragraphs in BLUE which need to be checked -- pages 97, 102, 105.

--- 2020-08-17 6.GWAS/6.GWAS-phase-transitions.tex
@@
 \end{equation}
-Therefore, if we were to apply FWER-controlling procedures at low nominal levels (say, $5\%$), then the FNR would experience a phase transition in the sense that, if
+Therefore, if we were to apply FWER-controlling procedures at low nominal levels (say, $5\%$), then the FNR would experience a phase transition
+in the following sense.  If the signal size is strong enough, i.e., 
 \begin{equation} \label{eq:power-1-region}
@@
 Sample sizes marked in the figure are adjusted by a factor of $1/2$, to reflect the genetic context where a pair of alleles are measured for every individual at every genomic location.} (referred to as OR-RAF diagrams) in Figure \ref{fig:OR-RAF_GWAS}.
-These parameter values are chosen so that $\log{p}/n$ are roughly constant (around $4.6\times10^{-5}$).
+These parameter values are chosen so that $\log(p)/n$ are roughly constant (around $4.6\times10^{-5}$).
 
@@
 This signal size calls for a sample size of $n = \lambda / w^2 = 2r\log(p)/w^2 \approx 307,011$.
-In a typically GWAS, a pair of alleles are sequenced for every marker location, bringing the required number of subjects in the study to $n/2 \approx 153,509$.
+In a typical GWAS, a pair of alleles are sequenced for every marker location, bringing the required number of subjects in the study to $n/2 \approx 153,509$.
 \end{example}

### 2021-03-10 7.GWAS/7.chi-square.tex
ch 7
i implemented my minor edits to ch 7.  I have 3 paragraphs in BLUE which need to be checked -- pages 97, 102, 105.

@@
 \end{equation}
-where $\beta$ parametrizes the problem sparsity.
+where $S_p:= \{ i\, :\, \lambda(i) >0 \}$ is the {\em signal support} set and  $\beta$ parametrizes the problem {\em sparsity}.
 The closer $\beta$ is to 1, the sparser the support $S_p$; conversely, when $\beta$ is close to 0, the support is dense with many non-null signals.
@@
 
-The first main result characterizes the phase transition phenomenon in the exact support recovery problem under the chi-square model.
+The first main result characterizes the phase transition phenomenon in the exact support recovery problem under the chi-square model.  It parallels
+Theorem \ref{thm:Gaussian-error-exact-boundary}.
 
@@
 characterizes the phase transition of exact support recovery problem.
-Specifically, if $\underline{r} > {{g}}(\beta)$, then Bonferroni's, Sid\'ak's, Holm's, and Hochberg's procedures with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FWER levels all achieve asymptotically exact support recovery in the sense of \eqref{eq:support-recovery-success}.
+Namely, the following two results hold.\\
 
-Conversely, if $\overline{r} < {{g}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, we have $\P[\widehat{S}_p=S_p]\to0$.
+{\rm (i)} If $\underline{r} > {{g}}(\beta)$, then Bonferroni's, Sid\'ak's, Holm's, and Hochberg's procedures with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FWER levels all achieve asymptotically exact support recovery in the sense of \eqref{eq:support-recovery-success}.\\
+
+{\rm (ii)} Conversely, if $\overline{r} < {{g}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, we have $\P[\widehat{S}_p=S_p]\to0$.
 Therefore, in view of Lemma \ref{lemma:risk-exact-recovery-probability}, exact support recovery asymptotically fails for all thresholding procedures in the sense of \eqref{eq:support-recovery-failure}.
@@
 The procedures listed in Theorem \ref{thm:chi-squared-exact-boundary} were reviewed in Section \ref{sec:statistical-procedures}. 
-Proof of the theorem can be found in Section \ref{subsec:proof-chi-squared-exact-boundary}. 
+The proof of the theorem can be found in Section \ref{subsec:proof-chi-squared-exact-boundary}. 
 % The boundary \eqref{eq:exact-boundary-chisquared} is plotted in Figure \ref{fig:phase-chi-squared}.
@@
 \begin{remark} \label{rmk:strong-classification-boundary-2}
-Theorem \ref{thm:chi-squared-exact-boundary} predicts that the asymptotic boundaries are the same for all values of the parameter $\nu$.
-In simulations (Section \ref{sec:numerical}), we find this asymptotic prediction to be quite accurate for $\nu\le3$ even in moderate dimensions ($p=100$). 
-For $\nu>3$, the phase transitions take place somewhat above the boundary ${g}$.
-The behavior is qualitatively similar for the other three phase transitions (see Theorems \ref{thm:chi-squared-exact-approx-boundary}, \ref{thm:chi-squared-approx-boundary}, and \ref{thm:chi-squared-approx-exact-boundary} below).
+Theorem \ref{thm:chi-squared-exact-boundary} predicts that the asymptotic boundaries are the same for all values of the degrees of freedom 
+parameter $\nu$.  In simulations (Section \ref{sec:numerical}), we find this asymptotic prediction to be quite accurate for $\nu\le3$ even in 
+moderate dimensions ($p=100$).  For $\nu>3$, the phase transitions take place somewhat above the boundary ${g}$.
+The behavior is qualitatively similar for the other three phase transitions (see Theorems \ref{thm:chi-squared-exact-approx-boundary}, 
+\ref{thm:chi-squared-approx-boundary}, and \ref{thm:chi-squared-approx-exact-boundary} below).
 \end{remark}
@@
 
-The next theorem describes the phase transition in the exact-approximate support recovery problem.
+The next theorem describes the phase transition in the exact-approximate support recovery problem. Recall also
+Theorem \ref{thm:Gaussian-error-exact-approx-boundary}.
 
@@
 characterizes the phase transition of exact-approximate support recovery problem.
-Specifically, if $\underline{r} > \widetilde{g}(\beta)$, then the procedures listed in Theorem \ref{thm:chi-squared-exact-boundary} with slowly vanishing nominal FWER levels achieve asymptotically exact-approximate support recovery in the sense of \eqref{eq:support-recovery-success}.
+ Namely, the following two results hold.\\
 
-Conversely, if $\overline{r} < \widetilde{g}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, the exact-approximate support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
+{\rm (i)} If $\underline{r} > \widetilde{g}(\beta)$, then the procedures listed in Theorem \ref{thm:chi-squared-exact-boundary} with slowly 
+vanishing nominal FWER levels achieve asymptotically exact-approximate support recovery in the sense of \eqref{eq:support-recovery-success}. \\
+
+{\rm (ii)} Conversely, if $\overline{r} < \widetilde{g}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, the exact-approximate support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
 \end{theorem}
@@
 
-Our third main result characterizes the phase transition phenomenon in the approximate support recovery problem in the chi-square model.
+Our third asymptotic result characterizes the phase transition phenomenon in the approximate support recovery problem in the chi-square model.
+It closely parallels Theorem \ref{thm:Gaussian-error-approx-boundary} for the additive errors model.
 
@@
 \end{equation}
-characterizes the phase transition of approximate support recovery problem.
-Specifically, if $\underline{r} > {h}(\beta)$, then the \ac{BH} procedure $\widehat{S}_p$ (defined in Section \ref{sec:statistical-procedures}) with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FDR levels achieves asymptotically approximate support recovery in the sense of \eqref{eq:support-recovery-success}.
+characterizes the phase transition of approximate support recovery problem. Specifically the following two results hold.\\
 
-Conversely, if $\overline{r} < {h}(\beta)$, then approximate support recovery asymptotically fails in the sense of \eqref{eq:support-recovery-failure} for all thresholding procedures.
+{\rm (i)} If $\underline{r} > {h}(\beta)$, then the \ac{BH} procedure $\widehat{S}_p$ (defined in Section \ref{sec:statistical-procedures}) with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FDR levels achieves asymptotically approximate support recovery in the sense of \eqref{eq:support-recovery-success}.
+\\
+
+{\rm (ii)} Conversely, if $\overline{r} < {h}(\beta)$, then approximate support recovery asymptotically fails in the sense of \eqref{eq:support-recovery-failure} for all thresholding procedures.
 \end{theorem}
@@
 \end{equation}
-characterizes the phase transition of approximate-exact support recovery problem.
-Specifically, if $\underline{r} > \widetilde{h}(\beta)$, then the Benjamini-Hochberg procedure with slowly vanishing nominal FDR levels achieves asymptotically approximate-exact support recovery in the sense of \eqref{eq:support-recovery-success}.
+characterizes the phase transition of approximate-exact support recovery problem. Namely, 
+the following two results hold.\\
 
-Conversely, if $\overline{r} < \widetilde{h}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, the approximate-exact support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
+{\rm (i)} If $\underline{r} > \widetilde{h}(\beta)$, then the Benjamini-Hochberg procedure with slowly vanishing nominal FDR levels achieves asymptotically approximate-exact support recovery in the sense of \eqref{eq:support-recovery-success}.
+\\
+
+{\rm (ii)} Conversely, if $\overline{r} < \widetilde{h}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, the approximate-exact support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
 \end{theorem}
@@
 
-Notice that all phase transitions boundaries are identical to those in the Gaussian additive error model \eqref{eq:model-additive} under one-side alternative.
+Notice that all phase transitions boundaries are identical to those in the Gaussian additive error model \eqref{eq:model-additive} under one-sided alternative.
 We refer readers to Figure \ref{fig:phase-Gaussian-errors} in Section \ref{sec:additive-error-model-boundaries} for a visualization of the results in Theorems \ref{thm:chi-squared-exact-boundary} through \ref{thm:chi-squared-approx-exact-boundary}.
@@
 
-The all four Theorems so far focus only on the idealized models \eqref{eq:model-chisq-Chapter6} where statistics are \emph{independent}.
+All four phase transitions results in Theorems \ref{thm:chi-squared-exact-boundary} through \ref{thm:chi-squared-approx-exact-boundary} 
+focus only on the idealized models \eqref{eq:model-chisq-Chapter6} where the statistics are \emph{independent}.
 Support recovery problems under dependent observations remain to be explored.
-Recall in Chapter \ref{chap:phase-transitions} we showed that the boundary for the exact support recovery problem in the additive error model \eqref{eq:model-additive} continues to hold even under severe dependence and general distributional assumptions.
-We conjecture that similar results would also hold, under classes of dependence structures that are ``not too different from independence'', in the chi-square models.
-As an example, in the GWAS application, dependence among the genetic markers at different locations (known as linkage disequilibrium) decay as a function of their physical distances on the genome \citep{bush2012genome}, resulting in locally dependent test statistics.
+Recall in Chapter \ref{chap:exact-support-recovery} we showed that the boundary for the exact support recovery problem in the additive error model 
+\eqref{eq:model-additive} continues to hold even under {\em severe dependence} and general distributional assumptions.
+We conjecture that the concentration of maxima phenomenon, which is at the heart of the results in Chapter \ref{chap:exact-support-recovery}, will play
+a role and all of the above phase-transition results will continue to hold, under broad dependence conditions in the chi-square models. As an example, 
+in the GWAS application, dependence among the genetic markers at different locations (known as linkage disequilibrium) decay as a function of their physical distances on the genome \citep{bush2012genome}, resulting in locally dependent test statistics.
 It would be of great interest to extend the current theory to cover important dependence structures that arise in such applications.
@@
 % $\mathrm{risk}^{\mathrm{EA}}$ and $\mathrm{risk}^{\mathrm{AE}}$.
-As alluded to in Section \ref{sec:motivation-chisq} in the introduction, we draw explicit comparisons between the one-sided and two-sided alternatives in Gaussian additive error models \eqref{eq:model-additive}.
+As alluded to in Chapter \ref{sec:motivation-chisq} in the introduction, we draw explicit comparisons between the one-sided and two-sided alternatives in Gaussian additive error models \eqref{eq:model-additive}.
 % The exact, and the approximate support recovery problems in the additive error model \eqref{eq:model-additive} under standard Gaussian errors have been studied in \cite{gao2018fundamental} and \cite{arias2017distribution}, respectively.
@@
 
-Comparing Theorems \ref{thm:chi-squared-exact-approx-boundary} to \ref{thm:Gaussian-error-exact-approx-boundary} and Theorems \ref{thm:chi-squared-approx-exact-boundary} to \ref{thm:Gaussian-error-approx-exact-boundary}, we see that the phase transition boundaries under the two types of alternatives are also identical in the exact-approximate and approximate-exact support recovery problems.
+Comparing Theorems \ref{thm:chi-squared-exact-approx-boundary} and \ref{thm:Gaussian-error-exact-approx-boundary} as well as
+ Theorems \ref{thm:chi-squared-approx-exact-boundary} and \ref{thm:Gaussian-error-approx-exact-boundary}, we see that the phase transition boundaries under the two types of alternatives are also identical in the exact-approximate and approximate-exact support recovery problems.
 
@@
 % and Figure \ref{fig:phase-chi-squared} continues to apply.
-This indicates vanishing differences between the difficulties of the one-sided and two-sided alternatives in the Gaussian additive error model \eqref{eq:model-additive}.
-The additional uncertainty in the two-sided alternatives do not call for larger signal sizes in these problems, asymptotically.
+This indicates vanishing differences between the difficulties of the one-sided and two-sided alternatives in the Gaussian additive error model 
+\eqref{eq:model-additive}. The additional uncertainty in the two-sided alternatives does not call for larger signal sizes in these problems, asymptotically.

### 2021-03-10 7.GWAS/7.numerical.tex
ch 7
i implemented my minor edits to ch 7.  I have 3 paragraphs in BLUE which need to be checked -- pages 97, 102, 105.

@@
 We illustrate with simulations the phase transition phenomena in the chi-square model, and compare numerically the required signal sizes in support recovery problems between the two types of alternatives in the additive error model.
+\stilian{These results can provide further guidance to practitioners on when to expect genetic association discoveries.
+They provide also an explanation of the empirically observed phenomenon known as steep part of the power curve
+in statistical genetics \citep{bush2012genome}. }{\fbox{IS this the RIGHT reference?  I could not find the ``steep part of the power curve" anywhere.}}
 % We also demonstrate the fundamental trade-off between odds ratios and relative frequencies in association studies, as outlined in Proposition \ref{prop:signal-size-odds-ratio} and Corollary \ref{cor:signal-size-odds-ratio-conditional-frequency}, using evidence from large-scale genetic studies.
 
-\subsection{Exact support recovery}
+\subsection{Exact support recovery} \label{sec:ch7-exact-support-numerics}
 
@@
 
-Experiments were repeated 1000 times for a grid of signal size values ranging from $r=0$ to $6$, and for dimensions $10^2, 10^3$, and $10^5$.
+The experiments were repeated 1000 times for a grid of signal size values ranging from $r=0$ to $6$, and for dimensions $10^2, 10^3$, and $10^5$.
 Results of the experiments, shown in Figure \ref{fig:one-vs-two-sided-exact_support_recovery}, suggest vanishing difference between difficulties of two-sided vs one-sided alternatives in the additive error models, as well as vanishing difference between the powers of Bonferroni's procedures and the oracle procedures as $p\to\infty$.
@@
 in implementation, we only need to scan the values of observations $t\in\{x(1), \ldots, x(p)\}$. 
-The nominal FDR level for the BH procedure is set at $1/(5{\log{p}})$, therefore slowly vanishing, in line with the assumptions in Theorem \ref{thm:chi-squared-approx-boundary}; all other parameters are identical to that in the experiments for exact support recovery.
-Results of the experiments are shown in Figure \ref{fig:one-vs-two-sided-approx_support_recovery} and in the middle column of Figure \ref{fig:phase-simulated-chi-squared}.
+The nominal FDR level for the BH procedure is set at $1/(5{\log{p}})$, therefore slowly vanishing, in line with the assumptions in Theorem \ref{thm:chi-squared-approx-boundary}; all other parameters are identical to that in the experiments for exact support recovery in
+Section \ref{sec:ch7-exact-support-numerics}.  The results of the experiments are shown in 
+Figure \ref{fig:one-vs-two-sided-approx_support_recovery} and in the middle column of Figure \ref{fig:phase-simulated-chi-squared}.
 
@@
 $$
-and visualize results of the experiments in the right column of Figure \ref{fig:phase-simulated-chi-squared}.
+and visualize the results of the experiments in the right column of Figure \ref{fig:phase-simulated-chi-squared}.
 Notice that the BH procedure sets its threshold somewhat higher than the oracle, especially for small $\beta$'s. 

### 2021-03-10 7.GWAS/7.odds-and-power.tex
ch 7
i implemented my minor edits to ch 7.  I have 3 paragraphs in BLUE which need to be checked -- pages 97, 102, 105.

--- 2021-02-04 6.GWAS/6.odds-and-power.tex
@@
 While ``signal size'' likely sounds foreign to most practitioners, it is intimately linked with the concept of ``effect sizes'' --- or odds ratios --- in association studies, which are frequently estimated and reported in GWAS catalogs.
-We characterize the relationship between the two quantities in the special, but fairly common case of association tests on 2-by-2 contingency tables in Section \ref{sec:odds-and-power}.
+This terminology, in turn, may be alien to some statisticians.
+Here, we aim to clarify
+the two languages.
+
+ %in Section \ref{sec:odds-and-power}.
 
@@
 
+\stilian{Recall the general setup of genetic association testing in Chapter \ref{sec:motivation-chisq}, where one wants to test 
+for the effect (or lack thereof) of a specific gene on the occurrence of a disease.  A randomly drawn individual from the entire population 
+is characterized by a pair $(P,G)$ of binary random variables, where $P$ encodes the phenotype and $G$, the genotype.  For example, in
+the context of a specific study,  by phenotype we mean whether or not the individual has the disease (belongs to the Cases group) or is healthy 
+(Controls group).  The genotype encodes whether or not the gene in question is expressed (Variant 1) or not (Variant 2). 
+Table  \ref{tab:multinomial-counts} in the introduction summarizes the {\em counts} for all phenotype-genotype combinations
+for the individuals in a given study sampled from the population. These counts can be assumed to follow a multinomial distribution, with probabilities 
+given in the following Table \ref{tab:multinomial-probabilites}.  Notice that there are fundamental study design questions here since the counts will 
+depend on the way individuals are recruited in the study.  For example, ``controlling'' the number of Cases or Controls (as opposed to sampling at
+random from the population) will change the theoretical parameters (probabilities) of the multinomial model.  
+These questions will be addressed in Section \ref{sec:optimal-design}  below.
+
+In this section, we characterize the relationship between the aforementioned ``signal size'' and ``odds-ratio'' parameterizations 
+in the special, but fairly common case of association tests on 2-by-2 contingency tables.
+}{\fbox{CHECK PLEASE}}
 Consider a 2-by-2 multinomial distribution with marginal probabilities of phenotypes $(\phi_1, \phi_2)$ and genotypes $(\theta_1, \theta_2)$.
 The \emph{probability} table (as opposed to the table of multinomial \emph{counts} in the introduction) is as follows.
+\begin{table}[h]\label{tab:multinomial-probabilites}
 \begin{center}
@@
     \end{tabular}
+    \caption{Probabilities of the multinomial distribution in a genetic association test. (Compare and contrast with 
+    Table \ref{tab:multinomial-counts}. We have $\E[ O_{ij}] = n\mu_{ij},\ i,j=1,2$, where $n = \sum_{i,j} O_{ij}$.) }
 \end{center}
+\end{table}
+
 The odds ratio (i.e., ``effect size'') is defined as the ratio of the phenotype frequencies between the two genotype variants,
@@
 	Under this parametrization, Relation \eqref{eq:odds-ratio} then becomes
-	\begin{equation} \label{eq:odds-ratio-delta}
+	\begin{align} \label{eq:odds-ratio-delta}
 	\text{R} = \frac{\mu_{11}\mu_{22}}{\mu_{12}\mu_{21}}
-	= \frac{\phi_1\theta_1\phi_2\theta_2 + \delta(\phi_1\theta_1+\phi_2\theta_2)+\delta^2}{\phi_1\theta_1\phi_2\theta_2 - \delta(\phi_1\theta_2+\phi_2\theta_1)+\delta^2},
-	\end{equation}
+	= \frac{\phi_1\theta_1\phi_2\theta_2 + \delta(\phi_1\theta_1+\phi_2\theta_2)+\delta^2}{\phi_1\theta_1\phi_2\theta_2 - \delta(\phi_1\theta_2+\phi_2\theta_1)+\delta^2}
+	= \frac{A +\delta B + \delta^2}{A -\delta C + \delta^2},
+	\end{align}
 	which is one-to-one and increasing in $\delta$ on $(\delta_\mathrm{min}, \delta_\mathrm{max})$.

### 2021-03-10 7.GWAS/7.optimal-design.tex
ch 7
i implemented my minor edits to ch 7.  I have 3 paragraphs in BLUE which need to be checked -- pages 97, 102, 105.

--- 2021-02-01 6.GWAS/6.optimal-design.tex
@@
 \begin{equation} \label{eq:RAF}
-    f := \mu_{21} / \phi_2.
+    f := \mu_{21} / \phi_2 = \mu_{21}/ (1-\phi_1).
 \end{equation}
@@
 	where $D = fR+1-f > 0$.
-	Therefore, he derivative of \eqref{eq:reparametrize-2-by-2-table-3} with respect to $\phi_1$ is
+	Therefore, the derivative of \eqref{eq:reparametrize-2-by-2-table-3} with respect to $\phi_1$ is
 	\begin{equation} \label{eq:signal-size-first-derivative}
@@
 	They share the same expression ${D}/{(D+\sqrt{R})}$, which coincides with \eqref{eq:optimal-design}.
-	Finally, when $D^2=R$, the only root $\phi_1^*=1/2$, which also coincides with \eqref{eq:optimal-design}, is the maximizer of \eqref{eq:reparametrize-2-by-2-table-3}.
+	Finally, when $D^2=R$, the only root $\phi_1^*=1/2$, which also coincides with \eqref{eq:optimal-design}, is the maximizer 
+	of \eqref{eq:reparametrize-2-by-2-table-3}.  \stilian{This is so, in particular, when 
+	$R=1$ and confirms our intuition that the symmetric design is optimal when the odds ratio 
+	equals one.  This is not the only case when symmetrical designs are optimal though. }{\fbox{ Am I CORRECT?}}
 \end{proof}

### 2021-03-10 7.GWAS/GWAS.tex
rename files and folders according to the new structure
ch 7
i implemented my minor edits to ch 7.  I have 3 paragraphs in BLUE which need to be checked -- pages 97, 102, 105.

--- 2021-02-01 6.GWAS/GWAS.tex
@@
-The process of scientific discovery, as famously explained by Richard Faynman, usually starts with guesses in one form or another.
+The process of scientific discovery, as famously explained by Richard Feynman, usually starts with guesses in one form or another.
 The consequences of such guesses are then computed, and compared with experimental results.
-If the predictions disagree with experiment, then our guesses are wrong. ``That is all there is to it''  \citep{feynman2017character}.
+If the predictions disagree with the experiment, then our guesses are wrong. ``That is all there is to it''  \citep{feynman2017character}.
 
-In previous chapters, we delved deep in to the theoretical underpinnings of the phase transition phenomena in high-dimensional multiple testing problems.
+In the previous chapters, we delved deep into the theoretical underpinnings of the phase transition phenomena in high-dimensional multiple testing problems.
 The results are interesting in their own right.
-However, in the spirit of Faynman, we have not discovered any scientific law, but merely worked out mathematical consequences of our postulated models.
+However, in the spirit of Feynman, we have not discovered any scientific law, but merely worked out mathematical consequences of our postulated models.
 In this chapter, our goal is to relate these predictions to real experimental data from the field of genetics, where large-scale simultaneous hypotheses testing problems often arise.
@@
 \end{equation}
-where $\chi_\nu^2\left(\lambda(i)\right)$ is a chi-square distributed random variable with $\nu$ degrees of freedom and non-centrality parameter $\lambda(i)$.
+where $\chi_\nu^2\left(\lambda(i)\right)$ is a chi-square distributed random variable with $\nu>0$ degrees of 
+freedom\footnote{The parameter $\nu$ here should not be confused with the shape parameter of the AGG$(\nu)$ 
+distributions, which will not appear in this chapter.} and non-centrality parameter $\lambda(i)$.
 
@@
 % \ref{thm:chi-squared-exact-boundary}, \ref{thm:chi-squared-exact-approx-boundary}, \ref{thm:chi-squared-approx-boundary}, and \ref{thm:chi-squared-approx-exact-boundary}.
-Under appropriate parametrizations of the signal sizes and sparsity, they establish the phase transitions of support recovery problems in the chi-square model.
+Under appropriate parametrization of the signal sizes and sparsity, we establish the phase transitions of support recovery problems in the chi-square model.
 Remarkably, the degree-of-freedom parameter does not affect the asymptotic boundaries in any of the four support recovery problems.
@@
 % This result, establishing the relationship between sample sizes and signal sizes, is made precise in Section \ref{sec:odds-and-power}.
-As a bonus, we point out an implications of this relationship on optimal study designs for association studies in Section \ref{sec:optimal-design}.
+As a bonus, we point out the implications of this relationship on statistically optimal study designs for association studies in Section \ref{sec:optimal-design}.
 Perhaps surprisingly, our analysis reveals that balanced designs with equal number of cases and controls are often statistically inefficient.
@@
 
-Armed with the results on phase transitions in the chi-square model, and a translation from the language of high-dimenstional statistics to the patois of association screening studies, we finally present in Section \ref{sec:phase-transitions-in-GWAS} the consequences of the phase transitions in \ac{GWAS}, and compare against real experimental data to evaluate the success of our predictions.
+Armed with the results on phase transitions in the chi-square model, and a translation from the language of high-dimenstional statistics to the {\em patois} of association screening studies, we finally present in Section \ref{sec:phase-transitions-in-GWAS} the consequences of the phase transitions in \ac{GWAS}, and compare against real experimental data to evaluate the success of our predictions.
 
 The phase transitions in the chi-square models are demonstrated with numerical simulations in Section \ref{sec:numerical}.
-Proofs are collected in the online Supplement.
+The proofs, which are closely related to those of the results in Chapter \ref{chap:phase-transitions},
+ are collected in Section \ref{sec:supplement:proofs}.
 %in Section \ref{sec:proof-signal-size-odds-ratio}.
@@
 \label{sec:chisq-boundaries}
-\input{6.GWAS/6.chi-square.tex}
+\input{7.GWAS/7.chi-square.tex}
 
@@
 \label{sec:odds-and-power}
-\input{6.GWAS/6.odds-and-power.tex}
+\input{7.GWAS/7.odds-and-power.tex}
 
@@
 \label{sec:optimal-design} 
-\input{6.GWAS/6.optimal-design.tex}
+\input{7.GWAS/7.optimal-design.tex}
 
@@
 \label{sec:phase-transitions-in-GWAS}
-\input{6.GWAS/6.GWAS-phase-transitions.tex}
+\input{7.GWAS/7.GWAS-phase-transitions.tex}
 
@@
 \label{sec:numerical}
-\input{6.GWAS/6.numerical.tex}
+\input{7.GWAS/7.numerical.tex}
 
-\section{Proofs}
-\label{sec:proof-signal-size-odds-ratio}
-\input{6.GWAS/6.proofs-GWAS.tex}
+%\section{Proofs}
+%\label{sec:proof-signal-size-odds-ratio}
+%\input{6.GWAS/6.proofs-GWAS.tex}

### 2021-03-10 reviews/response.tex
Ch 5
Upgraded fromer Prop 5.1 & 5.3 to Thm 5.1 & 5.2, Prop 5.2 became Cor 5.1.

These are THEOREMS!

\documentclass[11pt]{article}
\usepackage{fullpage,amsfonts,amsmath}

\title{Response to the reviews of the manuscript: ``Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference'' by Zheng Gao
and Stilian Stoev submitted to {\em SpringerBriefs Series in Probability and Statistics} }

\begin{document}
 \maketitle

 \section*{Summary of the revision}

 We sincerely thank the managing Editor and the five anonymous referees for their very helpful and constructive suggestions.  We really 
 appreciate the reviewers' time, effort, and thoughtful suggestions, which stimulated us to substantially revise and improve the manuscript.
 We begin with a high-level description of our edits and in the following section we respond to specific points raised by the reviewers.

 \begin{itemize}
  \item {\bf (Summary)} The revised manuscript has now a brief introductory chapter and 6 substantive chapters, 
  which amount to a total of 124 pages. As with the original submission,  Chapter 2 reviews the statistical risks, estimation and testing procedures,
  as well as probability models for the errors used in the rest of the manuscript.  It contains also a high-level summary of our results 
  in the context of the existing literature and some auxiliary facts from probability and extreme value theory.  For convenience of the reader, we 
  have added statements of Slepyan's Lemma and the Sudakov-Fernique inequality (without proofs).

   Chapter 3 provides a panorama of the phase-transition results in the signal detection and support estimation problems for the
   iid Gaussian error model.  Its purpose is to emphasize ideas and provide an accessible account, including references to the state-of-the-art 
   in the literature.  The chapter contains also some new results on the (sub)optimality of some popular statistics, which appear to have been 
   overlooked in the literature (Theorem 3.1).  One main idea  behind the exposition is to systematically present the different types of phase transition 
   results as a function of the chosen statistical risk.

   Chapters 4 through 7 contain the core of our contributions.

   Chapter 4 establishes phase-transitions results for the exact support recovery problem in the additive error model.  The main themes of this 
   chapter are {\em error--dependence} and {\em concentration of maxima}. We establish that the notion of uniform relative stability -- 
   a type of concentration of maxima phenomenon -- is key to characterizing the phase-transition in exact support recovery for the general class 
   of thresholding estimators.

   Chapter 5 begins with a study of the finite-sample (Bayes) optimality and sub-optimality of the threshold-based support estimators.  
   Criteria for the latter are established and certain theoretical results indicate that likelihood thresholding is in general optimal, when the thresholding 
   estimators are sub-optimal.  In the regime when the thresholding estimators are optimal, i.e., for log-concave error densities, our results entail 
   a universal statistical limit for exact support recovery, valid over all estimators (Theorem 5.1).   On the other hand, for the general class of
   thresholding estimators, we obtain minimax characterizations of the phase-transition in exact support recovery, for every fixed error-dependence 
   structure that satisfies mild uniform relative stability condition (Corollary 5.2).

   These finite-sample optimality results are used to obtain a variety of asymptotic minimax optimality results.  Consequently,

    for the large class of
   thresholding estimators. For example, the phase-transition in exact support recovery is shown to  universal among all estimators and  result is obtained for the minimax optimal exact support estimators under 
   log-concave error distributions (

   Under independent 
   errors, criteria for the 
   that the errors can

   We have revised substantially Chapters 4 and 5.

  \item {\bf (Organization)} Following a suggestion of a reviewer ({\bf R2}),  we have included most proofs 
  in the text right after the corresponding claims (theorems, propositions, lemmas).  In the interest of space and to conform with the format of
  the SpringerBriefs series, we no longer include ``Exercise'' sections.

  Last but not least, to better balance the exposition, we decided to divide the previous
  Chapter 4 into two new chapters (now Ch.\ 4, entitled ``Exact Support Recovery Under Dependence'', 
  and Ch.\ 5 ``Bayes and Minimax Optimality'').  In addition to making all chapters more manageable and of about equal length, it exposes more
  clearly our contributions.  The results contained in Chapters 4 and 5 as well as the more probabilistic Chapter 6 and more applied Chapter 7 are 
  original and new contributions to the literature.

 \end{itemize}

 \section*{Responses to specific points raised by the reviewers}
\end{document}

### 2021-03-10 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
Ch 5
Upgraded fromer Prop 5.1 & 5.3 to Thm 5.1 & 5.2, Prop 5.2 became Cor 5.1.

These are THEOREMS!

@@
 
-\begin{proposition} \label{prop:optimal-oracle-procedures}
+\begin{theorem} \label{thm:optimal-oracle-procedures}
 Let the observations $x(i)$, $i=1,\ldots,p$ be as prescribed as in \eqref{eq:signal-distributions-ordered} through \eqref{eq:uniform-ordered}.
@@
 for all $s$ and $p$.
-\end{proposition} 
-\begin{proof}%[Proof of Proposition \ref{prop:optimal-oracle-procedures}]
+\end{theorem} 
+\begin{proof}%[Proof of Proposition \ref{thm:optimal-oracle-procedures}]
 The problem of support recovery can be equivalently stated as a classification problem, where the discrete parameter space is $\mathcal{S} = \{S\subseteq\{1,\ldots,p\}:|S|=s\}$, and the observation $x \in\R^p$ has likelihood $f(x|S)$ indexed by the support set $S$.
@@
 
-We emphasize that under the MLR conditions in Proposition \ref{prop:optimal-oracle-procedures},
+We emphasize that under the MLR conditions in Theorem \ref{thm:optimal-oracle-procedures},
  the oracle thresholding procedures are in fact \emph{finite-sample optimal} in the 
@@
 In this setting, log-concavity of the error densities is \emph{equivalent} to the MLR property (Lemma \ref{lemma:MLR-log-concavity}).
-This, in turn, yields the finite-sample optimality of data thresholding procedures (Proposition \ref{prop:log-concave}).
+This, in turn, yields the finite-sample optimality of data thresholding procedures (Theorem \ref{c:log-concave}).
 
@@
 
-Proposition \ref{prop:optimal-oracle-procedures} and Lemma \ref{lemma:MLR-log-concavity} yield immediately the following.
+Theorem \ref{thm:optimal-oracle-procedures} and Lemma \ref{lemma:MLR-log-concavity} yield immediately the following.
 
-\begin{proposition} \label{prop:log-concave}
+\begin{corollary} \label{c:log-concave}
 Consider the additive error model \eqref{eq:model-additive}, where the $\epsilon(i)$'s are
@@
 finite-sample optimal in terms of Bayes risk in the sense of \eqref{eq:finite-sample-Bayes-optimal}.
-\end{proposition} 
+\end{corollary} 
 \begin{proof} The independence and the fact that the observations have densities implies the absence of 
@@
 and given by $\widehat{S}^* = \{i\, :\, x(i)\ge x_{[s]}\}$.  The result then follows from 
-Proposition \ref{prop:optimal-oracle-procedures} and Lemma \ref{lemma:MLR-log-concavity}.
+Theorem \ref{thm:optimal-oracle-procedures} and Lemma \ref{lemma:MLR-log-concavity}.
 \end{proof}
@@
 \begin{remark}
-Propositions \ref{prop:optimal-oracle-procedures} and \ref{prop:log-concave} show that under MLR (or equivalently, 
+Theorem \ref{thm:optimal-oracle-procedures} and Corollary \ref{c:log-concave} show that under MLR (or equivalently, 
 log-concavity of the errors in additive models), the oracle thresholding procedures are finite-sample optimal even in the case where the signals have different (positive) sizes.
@@
 The generalized Gaussian density $f(x)\propto \exp\{-|x|^\nu/\nu\}$ is log-concave for all $\nu\ge1$.
-Therefore in the additive error model \eqref{eq:model-additive}, according to Proposition \ref{prop:log-concave}, the oracle thresholding procedure is Bayes optimal in the sense of \eqref{eq:finite-sample-Bayes-optimal}.
+Therefore in the additive error model \eqref{eq:model-additive}, according to Corollary \ref{c:log-concave}, the oracle thresholding procedure is Bayes optimal in the sense of \eqref{eq:finite-sample-Bayes-optimal}.
 \end{example}
@@
 
-When the MLR condition in Proposition \ref{prop:optimal-oracle-procedures} is violated, the oracle thresholding 
+When the MLR condition in Theorem \ref{thm:optimal-oracle-procedures} is violated, the oracle thresholding 
 procedures can in fact be sub-optimal (see Example \ref{exmp:suboptimal-data-thresholding} and 
@@
 \end{definition}
-\begin{proposition} \label{prop:likelihood-ratio-thresholding} Any oracle likelihood ratio thresholding 
+\begin{theorem} \label{thm:likelihood-ratio-thresholding} Any oracle likelihood ratio thresholding 
 procedure $\widehat{S}_{\text{LRT}}$ is finite-sample optimal in terms of Bayes risk. That is,
@@
 for all $s$ and $p$, where the infimum on $\widehat{S}$ is taken over all support estimators of size $s$.
-\end{proposition}
+\end{theorem}
 
-\begin{proof}%[Proof of Proposition \ref{prop:likelihood-ratio-thresholding}]
-The proof is analogous to that of Proposition \ref{prop:optimal-oracle-procedures}.
+\begin{proof}%[Proof of Proposition \ref{thm:likelihood-ratio-thresholding}]
+The proof is analogous to that of Theorem \ref{thm:optimal-oracle-procedures}.
 We need to show that
@@
 
-The characterization of optimal likelihood ratio thresholding procedures in Proposition \ref{prop:likelihood-ratio-thresholding} may not always yield practical estimators, as the density of the alternatives, and the number of signals $s$
-are typically unknown. Still, some insights can be gained by virtue of Proposition \ref{prop:likelihood-ratio-thresholding}.
-In particular, when MLR fails (for example, when the errors in model \eqref{eq:model-additive} do not have log-concave densities), data thresholding is sub-optimal.
+The characterization of optimal likelihood ratio thresholding procedures in Theorem \ref{thm:likelihood-ratio-thresholding} may not always yield practical estimators, as the density of the alternatives, and the number of signals $s$
+are typically unknown. Still, some insights can be gained by virtue of Theorem \ref{thm:likelihood-ratio-thresholding}.
+In particular, when MLR fails (for example, when the errors in model \eqref{eq:model-additive} do not have log-concave densities), 
+data thresholding is sub-optimal.
 
@@
 $$
-is decreasing in $x(j)$ on $[K+\delta, \infty)$.  The claim follows from Proposition \ref{prop:likelihood-ratio-thresholding}.
+is decreasing in $x(j)$ on $[K+\delta, \infty)$.  The claim follows from Theorem \ref{thm:likelihood-ratio-thresholding}.
 \end{proof}
@@
 \begin{remark}[{\bf An open problem\!}\,] As we have seen, the thresholding estimators are no longer optimal 
-in the additive model with error-densities heavier than exponential.   Thanks to Proposition 
-\ref{prop:likelihood-ratio-thresholding}, the oracle likelihood thresholding procedures are promising alternatives
+in the additive model with error-densities heavier than exponential.   Thanks to Theorem 
+\ref{thm:likelihood-ratio-thresholding}, the oracle likelihood thresholding procedures are promising alternatives
 that can lead us to practical support estimators.
 
-In the case where the signals have different sizes, however, the argument in the proof of Proposition \ref{prop:likelihood-ratio-thresholding} breaks downs since the signal densities need to be identical for Relation \eqref{eq:likelihood-ratio-thresholding-proof} to hold.
+In the case where the signals have different sizes, however, the argument in the proof of Theorem \ref{thm:likelihood-ratio-thresholding} breaks downs since the signal densities need to be identical for Relation \eqref{eq:likelihood-ratio-thresholding-proof} to hold.
 In such cases, the characterization of the optimal procedure is an open problem.
@@
 Consider the asymptotic Bayes risk as defined in \eqref{eq:Bayes-risk}. The statement for the 
-necessary condition of support recovery in Theorem \ref{thm:necessary}, with the help of Proposition 
-\ref{prop:log-concave}, can be strengthened to include all procedures (in the Bayesian context), regardless 
+necessary condition of support recovery in Theorem \ref{thm:necessary}, with the help of Corollary 
+\ref{c:log-concave}, can be strengthened to include all procedures (in the Bayesian context), regardless 
 of whether they are thresholding or not.
@@
 Consider the additive model \eqref{eq:model-additive} where the $\epsilon_p(i)$'s are independent and identically distributed with log-concave densities in the AGG class. 
-Let the signals be as prescribed in Proposition \ref{prop:log-concave}.
+Let the signals be as prescribed in Corollary \ref{c:log-concave}.
 If the signal sizes fall below the strong classification boundary \eqref{eq:strong-classification-boundary}, 
@@
 \begin{proof}%[Proof of Theorem \ref{thm:necessary-strengthened}]
-When the errors are independent with log-concave density, the oracle thresholding procedure $\widehat{S}^*_p$, by Proposition \ref{prop:log-concave}, minimizes the Bayes risk \eqref{eq:Bayes-risk} among \emph{all} procedures.
+When the errors are independent with log-concave density, the oracle thresholding procedure $\widehat{S}^*_p$, by Corollary \ref{c:log-concave}, minimizes the Bayes risk \eqref{eq:Bayes-risk} among \emph{all} procedures.
 That is,
@@
 Specifically, in such cases the signal classification boundary is universal.
-On the other hand, Proposition \ref{prop:likelihood-ratio-thresholding}, and indeed, Example \ref{exmp:suboptimal-data-thresholding} demonstrate that thresholding procedures are \emph{sub-optimal} for $\text{AGG}(\nu)$ models with $\nu<1$.
+On the other hand, Theorem \ref{thm:likelihood-ratio-thresholding}, and indeed, Example \ref{exmp:suboptimal-data-thresholding} demonstrate that thresholding procedures are \emph{sub-optimal} for $\text{AGG}(\nu)$ models with $\nu<1$.
 Therefore, the optimality of thresholding

### 2021-03-10 reviews/response.tex
response
I added in the folder "reviews" a draft with our responses.  I will be working on it.

@@
  \begin{itemize}
-  \item {\bf (Summary)} The revised manuscript has now a brief introductory chapter and 6 substantive chapters, 
+  \item {\bf (Brief description)} The revised manuscript has now a brief introductory chapter and 6 substantive chapters, 
   which amount to a total of 124 pages. As with the original submission,  Chapter 2 reviews the statistical risks, estimation and testing procedures,
@@
 
-   Chapter 3 provides a panorama of the phase-transition results in the signal detection and support estimation problems for the
+   Chapter 3 provides a panorama of the phase-transition results in the signal detection and support estimation problems for the additive
    iid Gaussian error model.  Its purpose is to emphasize ideas and provide an accessible account, including references to the state-of-the-art 
@@
 
-   Chapters 4 through 7 contain the core of our contributions.
+   Chapters 4 through 7 contain the core of our original contributions.
 
@@
    Chapter 5 begins with a study of the finite-sample (Bayes) optimality and sub-optimality of the threshold-based support estimators.  
-   Criteria for the latter are established and certain theoretical results indicate that likelihood thresholding is in general optimal, when the thresholding 
-   estimators are sub-optimal.  In the regime when the thresholding estimators are optimal, i.e., for log-concave error densities, our results entail 
-   a universal statistical limit for exact support recovery, valid over all estimators (Theorem 5.1).   On the other hand, for the general class of
+   Criteria for the latter are established and certain theoretical results indicate that {\em likelihood thresholding} (as opposed to data thresholding)
+   is in general optimal, when the thresholding estimators are sub-optimal.  In the regime when the thresholding estimators are optimal, i.e., 
+   for log-concave error densities, our results entail 
+   a universal statistical limit in the exact support recovery problem, valid for all estimators (Theorem 5.3).   On the other hand, for the general class of
    thresholding estimators, we obtain minimax characterizations of the phase-transition in exact support recovery, for every fixed error-dependence 
-   structure that satisfies mild uniform relative stability condition (Corollary 5.2).
+   structure that satisfies mild uniform relative stability condition (Corollary 5.3).
 
-   These finite-sample optimality results are used to obtain a variety of asymptotic minimax optimality results.  Consequently,
+   Chapter 6 is nearly unchanged. It is more probabilistic in nature and it provides a complete characterization of the uniform relatively stable (URS) Gaussian 
+   triangular arrays.  This URS condition is the key property, in the lower bound on exact support recovery under dependence in Chpter 4. 
+   These probabilistic results as well as their methods of proof may of independent interest and are accessible to a wider audience of graduate students in statistics.
 
-    for the large class of
-   thresholding estimators.
-For example, the phase-transition in exact support recovery is shown to  universal among all estimators and  result is obtained for the minimax optimal exact support estimators under
-   log-concave error distributions (
-
-   Under independent 
-   errors, criteria for the 
-   that the errors can
-
-   We have revised substantially Chapters 4 and 5.
+   Chapter 7 focuses on an application to genome-wide association studies (GWAS) in statistical genetics.  It is shown that all phase-transition results in the 
+    additive error models of Chapter 3, have their close counterparts for the chi-square models arising naturally in GWAS. To connect these
+    asymptotic results to the practical notions in statistical genetics, we establish the connection between the odds-ratio (effect size) in multinomial 
+    $2\times 2$ models
+    and the signal-size parameter of the corresponding chi-square association test.  This allows us to quantify the statistical power and
+     optimal design questions as well as ultimately explain the role of phase-transitions in the fundamental statistical limits of GWAS.
 

### 2021-03-17 reviews/response.tex
responses
I am almost done with the responses.  Just need to add R4 (the most detailed one :))

@@
 
- \section*{Summary of the revision}
+ \section{Summary of the revision}
 
@@
  appreciate the reviewers' time, effort, and thoughtful suggestions, which stimulated us to substantially revise and improve the manuscript.
- We begin with a high-level description of our edits and in the following section we respond to specific points raised by the reviewers.
+ We begin with a high-level description of our edits and in the following section we respond to some of the more major 
+ specific points raised by the reviewers.  We do not list a large number of smaller edits made to the manuscript.
 
@@
 
+  \item {\bf (Typos, grammar, and style)}  Prompted by criticism of a referee (R2), we have revised the language of the manuscript. 
+  We have corrected a large number of typos, missing articles as well as attempted to make the language more consistent.  For example, 
+  we re-formatted the statements of a large number theorems so that they are more clear and modular.
+
+ \item {\bf (Length and online supplement)} We have softened the manuscript to just under 125 pages. The Appendix section appearing after the 
+ References is meant to become an online supplement should the manuscript be considered for publication.  This Appendix section contains some proofs
+ of phase-transition results stated in Ch.\ 7, which are similar to ones appearing in Ch.\ 3.  Thus, even without the online supplement, not much is lost by
+ not including the Appendix in the printed version.
+
  \end{itemize}
 
- \section*{Responses to specific points raised by the reviewers}
+ \section{Responses to specific points raised by the reviewers}
+
+ \subsection{Reviewer 1 (R1)}
+
+ \begin{itemize}
+  \item {\em I think the topic of this manuscript is excellent and timely. There are few self-contained books on high-dimensional statistics with this sort of twist.}
+
+  We thank the reviewer for the favorable and encouraging assessment.
+
+  \item {\em  The manuscript contains sufficiently new topics especially the application in Chapter 4 to dependent data.
+This is an important topic and has not received as much attention in the high-dimensional literature as it should.
+
+  \centerline{$\cdots$}
+
+  The manuscript is generally well-written and the issues/problems are clearly laid out.
+On the other hand, the writing may be a bit overly concise for which a supplement would be needed in a topics course.
+But the authors seem to be aware of this aspect.}
+
+  Thank you.  Stimulated by your feedback, we have attempted to provide more details and background where necessary.  In the interest of space and to 
+  conform to the format of the SpringerBriefs series, we had to relegate some of the proofs in Chapter 7 (new labeling) to an online supplement.  This still 
+  allowed us to treat carefully the important application to GWAS.  We believe we have also improved the treatment of the exact support recovery topic under 
+  dependence.  As indicated above, we divided the phase-transitions results (under dependence) and the Bayes and minimax optimality results into 
+  two separate chapters (Ch.\ 4 and 5, now).   We have added some more insights to the statements in Ch.\ 3 and Ch.\ 7, as well as some more 
+  background material in Ch.\ 2.  In addition to making the more advanced material better accessible, this case resulted in a balanced chapters, which can be
+  read independently and are better suited for a special topics course.
+
+  \end{itemize}
+
+  \subsection{Reviewer 2 (R2)}
+
+  We really appreciate the reviewer's feedback and suggestions.   We have taken all of them into account while revising the manuscript.
+
+   \begin{itemize}
+
+     \item {\em The book project grew out of the thesis of Z.
+Gao and some related articles.
+The main idea is about concentration of maxima in the sense of a law of large numbers (which is a rather rough result in this context; it could be supplemented by finer results on large deviations of maxima, as used in the context of a.s.
+convergence of maxima; e.g.
+the cited results of Barndorff; Resnick, Tomkins.
+BTW the best results on a.s.
+stability of maxima are due to Klass) and to exploit this fact for various applications.
+}
+
+     Thank you for the references and insights.  
+     Indeed, we use a rather basic relative stability property.  Mathematically, the study of finer large deviations of maxima is of great interest.  Our 
+     main focus, however, is on the situation where the variables could be dependent and possibly very strongly dependent.  To the best of our knowledge, 
+     less is known about almost sure relative stability under dependence.  In the statistical context of exact support recovery, it was more important for us 
+     to be able to deal with nearly arbitrary dependence rather than to have finer results on concentration of maxima.  This is because we establish only
+     asymptotic phase-transition-type results.  It would be of great interest to obtain more precise finite-sample 
+     and/or rate of concentration results. This would require more advanced mathematics beyond the scope of this manuscript.
+
+     \item {\em The manuscript is well written in general and the English is basically ok.
+There are some problems with articles...
+In my opinion, the authors exaggerate their explanations in the first chapters.
+There are repetitions of text and references.
+
+     \centerline{$\cdots$}
+
+     It is not clear whether the authors aim at a textbook or a monograph: some chapters contain exercises, others do not.
+For briefs the text is already too long in the present state.
+The authors could easily extend the manuscript to more than 200 pages, for example by extending the exercises and reorganizing the text.}
+
+     We have thoroughly revised the exposition and fixed most (and hopefully all) typos and grammatical errors.  We have also streamlined the exposition 
+     and tried to ground it.
+
+     As indicated above, we have shortened the manuscript, eliminated the exercises, and cast it into the format of a SpringerBriefs monograph.  We 
+     appreciate the reviewer's suggestions, but we felt that the work is not mature enough to extend to a textbook. At the same time, by balancing the
+     chapter lengths and content, we believe now the manuscript is more appropriate for an auxiliary text in a special topics graduate course on 
+     high-dimensional statistics.
+
+     \item {\em For my taste, the authors take too long to come to the point.
+An example is Chapter 3.
+The authors cite dozens of sources before they come to their own results.
+I think this is the wrong approach.
+The main line of the manuscript should be to present own results.
+The results of others and their relation to those in the book can be discussed anywhere else, e.g.
+in comments after the results, or at the end of a section or chapter.
+It honors the authors that they want to quote correctly and give merit to previous work, but this approach disturbs the flow.}
+
+     We really appreciate the feedback, which made us thoroughly revise the presentation!
+
+     Some results of Chapter 3 are in fact new.  The main philosophy behind Chapters 2 and 3 is to emphasize the (perhaps 
+     overlooked) impact the choice the statistical loss has on the statistical limits in support recovery.    Ch.\ 3 serves the purpose of reviewing 
+     the existing literature, while at the same time providing a unified treatment of phase transitions, suitable for a wider audience.  To emphasize this 
+     role, we have now changed the title of this chapter to ``A panorama of phase transitions''.  Theorem 3.1 both summarizes known as well as presents 
+     some new {\em overlooked} results on the sub-optimality of certain popular statistics.  The other results in Chapter 3 are also closely connected to the 
+    phase-transition results in Chapter 7 on GWAS, which are new.  This allowed us to omit the proofs of the results in Ch.\ 7 (presented in an online
+     supplement) and focus on the discussion of statistical power and optimal design issues, which are very relevant in practice and also novel.
+
+     We agree that the core of our contribution is on the exact support recovery under dependence.  To do justice to these results, as explained above, 
+     we have divided the previous Chapter 4 into two new chapters.  The first part (new Ch.\ 4) highlights the role of relative stability in exact support recovery 
+     under dependence. The new Ch.\ 5, more clearly presents another important contribution on the finite-sample Bayes optimality in 
+     exact support recovery.  These important results were a bit obscured in the previous version of the manuscript.
+
+     We hope that the revision has resulted in a more accessible manuscript, which at the same time more clearly shows our new ideas and results in the
+     context of the existing literature.
+
+     \item {\em Chapter 4-6 are relevant because they illustrate the idea of concentration of maxima for various advanced statistical topics.
+But the writing has several disadvantages...
+For example, Section 6.6.1 does not belong there and should be given in an appendix.
+The property of rapid variation can be introduced in an appendix...}
+
+     Chapter 6 (now Ch.\ 7) has been thoroughly revised and the proofs of phase-transition results similar to the ones in Ch.\ 3 have been omitted.  They
+     will be presented in an online supplement (appearing as the Appendix section after the References).  This 
+     allowed us to emphasize more the novel ideas in this chapter on the parametrization of association tests and the study of their power.
+
+     \item {\em Personally, I do not favor the separation of proofs from the results ... As the manuscript stands now, it reads like a collection of distinct papers. 
+     The authors should think how to organize the results in a more suitable way such that the chapters get linked in a better way.}
+
+     We agree.  All proofs have been incorporated in the text and the manuscript has been thoroughly revised.  As described in a previous point, we have
+     made a number of changes to the organization of the manuscript, where now the chapters are better connected and balanced.
+
+   \end{itemize}
+
+   \subsection{Reviewer 4 (R4)}
+
+   We are very grateful to the reviewer for their exceptionally detailed and helpful feedback.
+
+   \subsection{Reviewer 5 (R5)}
+
+  {\em The book definitely looks interesting and extremely timely. These concentration tools are fundamental for high-dimensional statistics 
+  and we still lack good articles that survey them. This book project fills in this crucial gap.}
+
+  \bigskip
+\noindent   We thank the reviewer for the encouraging assessment!  In our revision we have strived to maintain the balance between reviewing the
+   existing literature and presenting our own work.  
+   %We hope that we have contributed to providing a more complete picture of a dynamic 
+   %research area.
+
 \end{document}

### 2021-03-18 reviews/response.tex
Li & Fithian
Added some comments in Ch 2 and 3 on the contribution of Li and Fithian (2020) moentioned by R4.

Added more details to the response.

WE are almost there!

@@
 \documentclass[11pt]{article}
-\usepackage{fullpage,amsfonts,amsmath}
-
+\usepackage{fullpage,amsfonts,amsmath,hyperref}
+\def\P{{\mathbb P}}
 \title{Response to the reviews of the manuscript: ``Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference'' by Zheng Gao
@@
 
-   We are very grateful to the reviewer for their exceptionally detailed and helpful feedback.
+   We are very grateful to the reviewer for their exceptionally detailed and helpful feedback!  We appreciate the reviewer's encouraging assessment and 
+   important suggestions on improving the manuscript, which have all been taken into account in the present revision.  We respond below only to some
+   of the major points raised but would be happy to provide a more detailed account.
+
+   \begin{enumerate}
+    \item {\em Most existing works assume the constant signal strength, which essen- tially assume that the location parameters are drawn from a two-point distribution...
+However, it is a bit far from realistic from my perspective because the practical case often involves a mixture of strong and weak signals.
+A recent paper by Li 2020 considers the generic distribution of alternative means under appropriate rescaling, and shows the surprising result that the higher criticism test no longer dominates Bonferroni’s method even in the sparse regime $\beta >3/4$.
+It would be more instructive if the paper can start from the more general model to provide a fuller picture.}
+
+    \medskip
+    Thank you.  We were not aware of the interesting and very recent work of Li and Fithian, 2020 (\url{https://arxiv.org/abs/2006.12489}). We wholeheartedly 
+    agree that the set-up proposed my the reviewer is much more realistic.  It is quite interesting and stimulating for us to learn that the Higher Criticism
+    statistic no longer dominates the Bonferonni thresholding procedure.  We have now included brief comments
+    about this very recent development in Chapters 2 and 3.  Since our focus in this manuscript is mostly on the support estimation problem (rather than on the 
+     detection problem), we decided not to pursue this new and important line of research, which may require resolving some new mathematical challenges. 
+     We hope to understand this phenomenon better in the near future.
+
+     \fbox{Zheng, PLEASE CHECK how if I quoted the work of  Li and Fithian in Ch 2 and 3, appropriately.  Thanks!}
+
+    \item {\em The statistical risks for exact-approximate and approximate-exact support recovery look artificial and uninterpretable. 
+    Could you provide further explanations of these two criteria?}
+
+    \fbox{Zheng, need help here?}
+
+        \item {\em In practice, type-I error/FWER/FDR and type-II error/FNER/FNR are typically not equally weighted.
+The former is often worse than the latter.
+Is there any work that considers the asymmetric version like FDR plus a fraction of FNR?
+Does the weighted risk give a fundamentally different phase transition in some regimes?}
+
+        \fbox{Help.}
+
+        \item {\em The uniform relative stability (URS) is type of weak dependence based on the results in Chapter 5. In FDR literature, the statistics are 
+        said to be weakly dependent if 
+        $$
+        \frac{1}{p^2} \sum_{i=1}^n |{\rm Cor}(x_i,x_j)| = o(1),
+        $$
+see e.g. Efron 2007 and Fan 2012. Is there any connection between these two types of weak dependence?}
+
+   \medskip
+   \noindent Indeed, the notion of {\em weak dependence} in its various forms of mixing coefficients and dependence functionals
+    has a long and fruitful history in the study of large-sample limit theorems.  We appreciate this natural question!  There is a fundamental 
+    difference between the notions of weak dependence required to establish the asymptotic behavior of sums and those for maxima.     
+    As a rule, the maxima of dependent variables behave
+   very similarly to the maxima of independent variables even under {\em severe dependence}.  This is in stark contrast with the large-sample 
+   behavior of dependent sums (averages), which have been much more extensively studied in the literature.  We have now
+    clarified and emphasized these differences in several places in the text.
+
+    We provide below some brief comments on the way we understand the differences between the asymptotic behaviors of sums and maxima 
+    under dependence.  This is certainly a big and important subject and the following discussion is just on the level of ideas.
+    The weak dependence condition stated by the referee appears to be tailored to the study of sums rather than maxima.  For example, a 
+    stationary (finite-variance) time-series $\{X_k,\ k\in \mathbb Z\}$ is said to be short-range dependent if
+   $$
+   \sum_{k=1}^\infty |{\rm Cov} (X_{k}, X_0) | <\infty.
+   $$
+   If the latter sum is infinite, the time series is referred to as long-range dependent. For example, consider the Gaussian case, where
+   the time series has a power-law auto-covariance ${\rm Cov}(X_{k}, X_0) \propto k^{-\gamma},\ \ k\to\infty$, for $\gamma \in (0,1)$.  In this long-range
+   dependent regime, it can be shown that, as $n\to\infty$,
+  $$
+  \Big\{ \frac{1}{n^H} \sum_{k=1}^{[nt]} (X_k -\mathbb E X_k) \Big\}_{t\ge 0} \stackrel{f.d.d.}{\longrightarrow} B_H = \{B_H(t),\ t\ge 0\},
+  $$   
+  where $B_H$ is the fractional Brownian motion process -- a Gaussian, stationary increment and  self-similar process with 
+  exponent $H = 1 - \gamma/2 \in (1/2,1)$.  This is in stark contrast with the usual Brownian motion limit which arises 
+  under the {\em weak dependence}.  The behaviors of many sum-based statistics will change dramatically when the dependence switches from
+  short- to long-range.  For more details, see e.g. \cite{----}.
+
+  Shockingly, when considering even most heavily dependent (say Gaussian) stationary time series $\{X_k\}$, the limit behavior of the maxima
+  is no different than had they been iid.  Indeed, the Berman condition
+  $$
+  {\rm Cov}(X_k,X_0) = o (\log k),\ \ \mbox{ as }k\to\infty,
+  $$
+  guarantees in this setting that, as $n\to\infty$,
+  \begin{equation}\label{e:Gumbel}
+  \frac{1}{a_n} \max_{k=1,\cdots,n} X_k - b_n \stackrel{d}{\longrightarrow} Z \sim {\rm Gumbel},
+  \end{equation}
+  where $a_n$ and $b_n$ are {\em the same} scaling and shift sequences as in the case of iid data.  That is, if $X_k^*$ are iid with the same marginal 
+  distribution as the $X_k$'s, then
+  $$
+  \frac{1}{a_n} \max_{k=1,\cdots,n} X_k^* - b_n \stackrel{d}{\longrightarrow} Z,
+  $$
+  where the normalizing constants $a_n$ and $b_n$ as well as the limit $Z$ are the same as in \eqref{e:Gumbel}.
+
+  In particular, the Berman condition holds for Gaussian long-range dependent models!  Thus, even when the traditional notions of weak dependence for
+  sums no longer hold, the dependence is weak enough for the maxima to behave as in the iid setting.
+Please note that in our monograph we need an even weaker notion of dependence since we need only have relative stability, i.e.,
+  $$
+  \frac{1}{a_n} \max_{k=1,\cdots,n} X_k \stackrel{\P}{\longrightarrow} 1,
+  $$
+  as $n\to\infty$.  As shown in the seminal work of Berman (and in a more general situation for triangular arrays in our 
+  Chapter 6), for the latter to hold one needs the auto-covariance to vanish, i.e., 
+  $$
+  {\rm Cov}(X_k,X_0) = o(1),\ \ \ \mbox{ as }k\to\infty.
+  $$
+  We find this to be an important and perhaps somewhat overlooked universality phenomenon showing that light-tailed maxima continue to 
+  concentrate under drastically stronger dependence than we are accustomed to deal with.
+
+   \end{enumerate}
 

### 2021-03-18 3.phase_transitions/3.global-tests.tex
Li & Fithian
Added some comments in Ch 2 and 3 on the contribution of Li and Fithian (2020) moentioned by R4.

Added more details to the response.

WE are almost there!

@@
 It is also known that the max-statistic \eqref{eq:max-statistic} is only efficient when $r>(1+\sqrt{1-\beta})^2$, and is therefore sub-optimal for denser signals where $1/2\le\beta\le 3/4$; see \cite{cai2011optimal}.
+\stilian{This said,  the very recent contribution of \cite{li2020optimality} investigates a more realistic setting where the non-null signal is drawn from a general distribution with tails no lighter than the Gaussian additive error.
+In this, much more practical regime, they show that the max statistic in fact achieves the optimal detection boundary for the entire
+``sparsity'' regime $1/2<\beta<1$.  This surprising new development shows that the high-dimensional testing and inference is an active 
+area of research.}{}
 In contrast, the sum-of-square-type statistics such as $L_2$ was shown in \cite{fan1996test} to be asymptotically powerless when the $L_2$-norm of the signal $\|\mu\|_2^2$ is $o(\sqrt{p})$, or equivalently, when $\beta>1/2$ in our parametrization.
@@
       The \ac{HC} statistic can detect signals in all configurations in the detectable regions.
-      See text and Theorem \ref{thm:detection-optimality}.}
+      See the text and Theorem \ref{thm:detection-optimality}.}
       \label{fig:phase-diagram-signal-detection}

### 2021-03-18 3.phase_transitions/phase_transitions.tex
Li & Fithian
Added some comments in Ch 2 and 3 on the contribution of Li and Fithian (2020) moentioned by R4.

Added more details to the response.

WE are almost there!

@@
 
+\stilian{It should be noted that here we consider only the ``classic'' setting where the non-null signals are constant.  The recent contribution of \cite{li2020optimality}
+investigates a more practical setting where the signals can be drawn from a general distribution with potentially heavier tail than the distribution of the additive
+errors.  This leads to new phenomena such as an improved performance of the max-statistic in the detection problem.  The study of this more general setting
+in both the detection and support recovery problems is an important problem of future research not covered in this monograph.}{}
+
 \section{Sparse signal detection problems}

### 2021-03-18 reviews/response.tex
done!
I think I am done with the responses.  Now I need your help a bit.  Please CHECK ME :-).

@@
 \documentclass[11pt]{article}
-\usepackage{fullpage,amsfonts,amsmath,hyperref}
+\usepackage{fullpage,amsfonts,amsmath,hyperref,natbib}
 \def\P{{\mathbb P}}
+\bibliographystyle{plain}
 \title{Response to the reviews of the manuscript: ``Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference'' by Zheng Gao
@@
     \medskip
-    Thank you.  We were not aware of the interesting and very recent work of Li and Fithian, 2020 (\url{https://arxiv.org/abs/2006.12489}). We wholeheartedly 
-    agree that the set-up proposed my the reviewer is much more realistic.  It is quite interesting and stimulating for us to learn that the Higher Criticism
-    statistic no longer dominates the Bonferonni thresholding procedure.  We have now included brief comments
-    about this very recent development in Chapters 2 and 3.  Since our focus in this manuscript is mostly on the support estimation problem (rather than on the 
-     detection problem), we decided not to pursue this new and important line of research, which may require resolving some new mathematical challenges. 
-     We hope to understand this phenomenon better in the near future.
+    Thank you.  We were not aware of the interesting and very recent work \cite{li2020optimality}
+     of Li and Fithian. We wholeheartedly agree that the set-up proposed my the reviewer is much more realistic.  
+     It is quite interesting and stimulating for us to learn that the Higher Criticism statistic no longer dominates the Bonferonni thresholding procedure.  
+     This changes our general understanding about optimality of the max-statistic.  Although, we are not prepared to contribute more to the subject from 
+     the more general perspective of  \cite{li2020optimality}, we have included brief comments about this very recent development in Chapters 2 and 3.  
+     Since our focus in this manuscript is mostly on the support estimation problem (rather than on the detection problem), we decided not to pursue 
+     this new and important line of research, which may require resolving some new mathematical challenges. We hope to understand this phenomenon 
+     better in the near future.
 
@@
   under the {\em weak dependence}.  The behaviors of many sum-based statistics will change dramatically when the dependence switches from
-  short- to long-range.  For more details, see e.g. \cite{----}.
+  short- to long-range.  For more details, see e.g. \cite{pipiras:taqqu:2017} and the references therein.
 
   Shockingly, when considering even most heavily dependent (say Gaussian) stationary time series $\{X_k\}$, the limit behavior of the maxima
-  is no different than had they been iid.  Indeed, the Berman condition
+  is no different than in the iid case.  Indeed, the Berman condition (cf \cite{berman1964limit,leadbetter2012extremes})
   $$
@@
 Please note that in our monograph we need an even weaker notion of dependence since we need only have relative stability, i.e.,
-  $$
+  \begin{equation}\label{e:RS}
   \frac{1}{a_n} \max_{k=1,\cdots,n} X_k \stackrel{\P}{\longrightarrow} 1,
-  $$
-  as $n\to\infty$.  As shown in the seminal work of Berman (and in a more general situation for triangular arrays in our 
-  Chapter 6), for the latter to hold one needs the auto-covariance to vanish, i.e., 
+  \end{equation}
+  as $n\to\infty$.  As shown in the seminal work of Berman \cite{berman1964limit} and in a more general situation for triangular arrays in our 
+  Chapter 6), for the latter convergence \eqref{e:RS} to hold one merely needs the auto-covariance to vanish, i.e., 
   $$
@@
   $$
-  We find this to be an important and perhaps somewhat overlooked universality phenomenon showing that light-tailed maxima continue to 
-  concentrate under drastically stronger dependence than we are accustomed to deal with.
+  We find this to be an important and perhaps somewhat overlooked universality phenomenon showing that maxima of Gaussians 
+  (and in fact, general light-tailed variables) continue to concentrate under drastically stronger dependence than we are accustomed to deal with 
+  in the case of sums/averages.
+
+   \item {\em This is another line of work that studies the strong dependence structure where the covariance matrix has a factor structure 
+   (eg. Fan 2012). For instance, this includes the equi-correlated case. Are you aware of any results under strong dependence in your context?}
+
+   We thank the reviewer for the important reference to the work of Fan, Xu and Gu \cite{fan:xu:gu:2012}, which we had overlooked.  
+   It can be seen that the {\em weak dependence} condition in their Definition 1, implies our UDD condition (for a correlation matrix).  
+   Therefore, the Gaussian error arrays of the $K_i$-variables in Relation (10) in the latter reference, are URS (uniformly relatively stable).  
+   This suggests that the PFA methodology in \cite{fan:xu:gu:2012} can perhaps be extended to apply to the exact support recovery problem.  
+   That is, one can project on the orthogonal complement of the space spanned by the top$-k$ eigenvectors of the error-covariance.  Then, perhaps 
+   under standard in-coherence conditions, between the  signal and the covariance, the simple Bonferonni thresholding estimator is optimal for exact 
+   support recovery.  We are not aware of many more examples, but hope that the developed general theory applies in many more setting.  We now 
+   include a remark on this important reference.
+
+   \item  {\em The results in Chapter 4 require different dependence structure but some of them are not clearly stated.
+For instance, the results in Section 4.2.2 and 4.2.3 rely on the independence assumption that is stated in the last sentence of the first paragraph in page 59.
+It would be more clear if this assumption can be included in the Propositions and Theorems.}
+
+   Thank you.  Indeed, to clarify and better present the two very distinct themes -- exact support recovery under dependence, on one hand, and 
+   finite-sample Bayes optimality (under independence), we have divided the previous Chapter 4 in two -- the new Chapters 4 and 5. The new
+   Chapter 5 entitled ``Bayes and Minimax Optimality'' now presents the results in a much more organized fashion where the independence 
+   assumptions are clearly stated.
+
+   \item {\em Proposition 4.3 still requires $f_a$ to be MLR, right? If so, please state it.}
+
+   Thank you for the sharp observation.  The previous presentation was not sufficiently clear.  We have now devoted the new Ch.\ 5 to the
+   finite-sample Bayes optimality (and minimax optimality) to better present these topics.  
+   The former Proposition 4.3 appears now as Theorem 5.2.  The MLR property on $f_a$
+   is no longer necessary.  This is because the {\em likelihood ratio theresholding} estimator is defined in such a way (in terms of the likelihood) that
+   the desired monotonicity property is guaranteed.  The MLR property was essential in Theorem 5.1 since there we deal with thresholding (as opposed to
+   likelihood thresholding). The MLR property basically ensures that in the setting of Theorem 5.1, the simple thresholding estimators are in fact of
+   {\em likelihood thresholding} type.  We realize that Theorem 5.2 is a bit too theoretical (i.e., not directly useful in practice since we don't have the 
+   likelihood) but it provides some insights on
+   the general Bayes (sub)optimal support estimation procedures.
+
+\item  {\em Fig 3.2 shows that the exact-approximate support recovery is strictly easier to achieve than the approximate-exact support recovery. 
+Do you have intuition on it?}
+
+\fbox{Help, please! Is it related to the fact that $p\gg p^{1-\beta}$. }
+
+\item {\em The phrase ``exact support recovery''  is used for both the general problem
+(as in the title of Chapter 2), and for the specific criterion risk$^{\rm E}$. This is a bit confusing.}
+
+We have clarified the terminology througout.  In particular, Chapter 2 is a now entitled ``Risks, Procedures, and Error Models''.
 
     \end{enumerate}
+
+We thank the reviewer for pointing a number of typos, which we have corrected.  We respond below to a subset of the minor points
+and comments raised in the report.
+
+\medskip
+\noindent {\bf Typos and other minor comments}
+\begin{itemize}
+ \item [10.] {\em Page 46, ``these Hamming loss-minimax studies naturally amounts to the analysis of the elementary case of iid data,...'' 
+ Is this true? Although the indicators can be dealt with separately but the threshold may depend on the entire dataset as in Holm, 
+ Hochberg, and BH procedures. }
+
+ You are right that our statement was a bit exaggerated and thus perhaps misleading. We have clarified and tempered the language.
+
+ \item[11.]{\em Page 50, ``Intuitively, this is because the maxima of the errors grow at their fastest in the case of independence." Is it true that the maxima of negatively equi-correlated statistics grow slower than that of independent statistics?}
+
+  Thank you for the insightful comment.  Indeed, by Slepian's Lemma, negatively correlated Gaussian variables have smaller maxima (in stochastic order)
+  than iid maxima (with the same marginals).  This difference, however, is negligible asymptotically.  Intuitively, this is due to the fact that while Gaussian
+  vectors can be equi-correlated with correlation $\rho$ that can be arbitrarily close to $1$, this common correlation is bounded below by $-1/(p-1)$,
+  where $p$ is the number of the variables.
+
+  Our choice of words was imprecise. We should have said that the rate of growth of dependent maxima is no faster than in the iid case.  
+  We now clarify this point in the new Remark 2.1 (see Relation (2.41)).
+
+  This general observation is entirely due to the light-tailed (rapidly varying) nature of the marginal distributions.  It applies to error-arrays with arbitrary
+  dependence and the proof involves the union bound and the rapid variation property of the marginal distributions.  Please see Proposition 2.2.
+
+\end{itemize}
 
@@
 
+   \bibliography{../tex/thesis.bib}
+
 \end{document}

### 2021-03-18 4.exact_support_recovery/exact_support_recovery.tex
done!
I think I am done with the responses.  Now I need your help a bit.  Please CHECK ME :-).

@@
 Unfortunately, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and the latter sharp results do not carry over directly to the study of the probability of support recovery or exact support recovery risk.
-More importantly, despite their elegance, these Hamming loss-minimax studies naturally reduce to the analysis of the elementary case of iid data, and is by design blind to non-trivial error-dependence structures.
-This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
+%More importantly, despite their elegance, these Hamming loss-minimax studies often amount to the analysis of the elementary case of iid data, and 
+%unless is by design blind to non-trivial error-dependence structures.
+%This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
+More importantly, since the Hamming loss is the same for both independent and dependent data, typical Hamming loss-minimax studies
+amount to the analysis of the elementary case of iid data. This prevents one from fully exploring the phase transition phenomena under 
+other dependence conditions.
+
 % This is arguably a consequence of the inherent limitation of the Hamming-loss approach. 

### 2021-03-19 reviews/response.tex
response
Corrected some typos.

Still needs some minor work.

@@
   \item {\bf (Brief description)} The revised manuscript has now a brief introductory chapter and 6 substantive chapters, 
-  which amount to a total of 124 pages. As with the original submission,  Chapter 2 reviews the statistical risks, estimation and testing procedures,
+  which amount to a total of 125 pages. As with the original submission,  Chapter 2 reviews the statistical risks, estimation and testing procedures,
   as well as probability models for the errors used in the rest of the manuscript.  It contains also a high-level summary of our results 
@@
    thresholding estimators, we obtain minimax characterizations of the phase-transition in exact support recovery, for every fixed error-dependence 
-   structure that satisfies mild uniform relative stability condition (Corollary 5.3).
+   structure that satisfies the mild uniform relative stability condition (Corollary 5.3).
 
    Chapter 6 is nearly unchanged. It is more probabilistic in nature and it provides a complete characterization of the uniform relatively stable (URS) Gaussian 
-   triangular arrays.  This URS condition is the key property, in the lower bound on exact support recovery under dependence in Chpter 4. 
-   These probabilistic results as well as their methods of proof may of independent interest and are accessible to a wider audience of graduate students in statistics.
+   triangular arrays.  This URS condition is the key property used to establish the lower bound on exact support recovery under dependence in Chapter 4. 
+   These probabilistic results as well as their methods of proof may of independent interest and are presented in a way that should be 
+   accessible to a wider audience of graduate students in statistics.
 
@@
     and the signal-size parameter of the corresponding chi-square association test.  This allows us to quantify the statistical power and
-     optimal design questions as well as ultimately explain the role of phase-transitions in the fundamental statistical limits of GWAS.
+     optimal design questions in a unified manner as well as ultimately explain the role of phase-transitions in the fundamental statistical limits of GWAS.
 
-  \item {\bf (Organization)} Following a suggestion of a reviewer ({\bf R2}),  we have included most proofs 
+  \item {\bf (Organization)} Following a suggestion of a reviewer ({\bf R2}),  we have incorporated most proofs 
   in the text right after the corresponding claims (theorems, propositions, lemmas).  In the interest of space and to conform with the format of
-  the SpringerBriefs series, we no longer include ``Exercise'' sections.
+  the SpringerBriefs series, we no longer include ``Exercises'' sections.
 
@@
   Chapter 4 into two new chapters (now Ch.\ 4, entitled ``Exact Support Recovery Under Dependence'', 
-  and Ch.\ 5 ``Bayes and Minimax Optimality'').  In addition to making all chapters more manageable and of about equal length, it exposes more
-  clearly our contributions.  The results contained in Chapters 4 and 5 as well as the more probabilistic Chapter 6 and more applied Chapter 7 are 
+  and Ch.\ 5 ``Bayes and Minimax Optimality'').  This change, in addition to making all chapters more manageable and of about equal length, 
+  exposes more clearly our contributions.  The results contained in Chapters 4 and 5 as well as the more probabilistic Chapter 6 and more 
+  applied Chapter 7 are 
   original and new contributions to the literature.
 
-  \item {\bf (Typos, grammar, and style)}  Prompted by criticism of a referee (R2), we have revised the language of the manuscript. 
-  We have corrected a large number of typos, missing articles as well as attempted to make the language more consistent.  For example, 
-  we re-formatted the statements of a large number theorems so that they are more clear and modular.
+  \item {\bf (Typos, grammar, and style)}  Prompted by criticism of a referee ({\bf R2}), we have revised the language of the manuscript. 
+  We have corrected a large number of typos, missing articles as well as attempted to make the language more consistent.  In the spirit of
+  making the style more accessible, we re-formatted the statements of a large number theorems so that they are more modular.
 
- \item {\bf (Length and online supplement)} We have softened the manuscript to just under 125 pages. The Appendix section appearing after the 
- References is meant to become an online supplement should the manuscript be considered for publication.  This Appendix section contains some proofs
- of phase-transition results stated in Ch.\ 7, which are similar to ones appearing in Ch.\ 3.  Thus, even without the online supplement, not much is lost by
+ \item {\bf (Length and online supplement)} We have shortened the manuscript to just under 125 pages. The Appendix appearing after the 
+ References is meant to become an online supplement should the manuscript be considered for publication.  The appendix contains some proofs
+ of phase-transition results stated in Ch.\ 7, which are similar to ones appearing in Ch.\ 3.% as well as some phase transition results for lighter and/or
+ %heavier tailed models than the AGG class.  
+ Thus, even without the online supplement, not much is lost by
  not including the Appendix in the printed version.
@@
   two separate chapters (Ch.\ 4 and 5, now).   We have added some more insights to the statements in Ch.\ 3 and Ch.\ 7, as well as some more 
-  background material in Ch.\ 2.  In addition to making the more advanced material better accessible, this case resulted in a balanced chapters, which can be
-  read independently and are better suited for a special topics course.
+  background material in Ch.\ 2.  In addition to making the more advanced material accessible, these changes have improved the balance between
+  the chapters, which can be read independently and are better suited for a special topics course.
 
@@
      overlooked) impact the choice the statistical loss has on the statistical limits in support recovery.    Ch.\ 3 serves the purpose of reviewing 
-     the existing literature, while at the same time providing a unified treatment of phase transitions, suitable for a wider audience.  To emphasize this 
-     role, we have now changed the title of this chapter to ``A panorama of phase transitions''.  Theorem 3.1 both summarizes known as well as presents 
+     the existing literature, while at the same time providing a unified treatment of phase transitions, suitable for an introduction to a wider audience.  
+     To emphasize this  role, we have now changed the title of this chapter to ``A panorama of phase transitions''.  Theorem 3.1 both summarizes known as well as presents 
      some new {\em overlooked} results on the sub-optimality of certain popular statistics.  The other results in Chapter 3 are also closely connected to the 
-    phase-transition results in Chapter 7 on GWAS, which are new.  This allowed us to omit the proofs of the results in Ch.\ 7 (presented in an online
-     supplement) and focus on the discussion of statistical power and optimal design issues, which are very relevant in practice and also novel.
+    phase-transition results in Chapter 7 on GWAS, which are new.  This exposition allowed us to omit the proofs of the results in Ch.\ 7 (presented in an 
+    online supplement) and focus on the discussion of statistical power and optimal design issues, which are very relevant in practice and also novel.
 
      We agree that the core of our contribution is on the exact support recovery under dependence.  To do justice to these results, as explained above, 
-     we have divided the previous Chapter 4 into two new chapters.  The first part (new Ch.\ 4) highlights the role of relative stability in exact support recovery 
-     under dependence. The new Ch.\ 5, more clearly presents another important contribution on the finite-sample Bayes optimality in 
+     we have divided the old Chapter 4 into two new chapters.  The first part (new Ch.\ 4) highlights the role of relative stability in exact support recovery 
+     under dependence. The new Ch.\ 5 more clearly presents another one of our contributions, namely the finite-sample Bayes optimality in 
      exact support recovery.  These important results were a bit obscured in the previous version of the manuscript.
@@
      will be presented in an online supplement (appearing as the Appendix section after the References).  This 
-     allowed us to emphasize more the novel ideas in this chapter on the parametrization of association tests and the study of their power.
+     allowed us to emphasize more clearly the novel ideas in this chapter on the parametrization of association tests and the study of their power.
 
@@
    We are very grateful to the reviewer for their exceptionally detailed and helpful feedback!  We appreciate the reviewer's encouraging assessment and 
-   important suggestions on improving the manuscript, which have all been taken into account in the present revision.  We respond below only to some
-   of the major points raised but would be happy to provide a more detailed account.
+   important suggestions on improving the manuscript, which have all been taken into account in the present revision.  We respond below to only some
+   of the major points raised but we would be happy to provide a more detailed account.
 
    \begin{enumerate}
-    \item {\em Most existing works assume the constant signal strength, which essen- tially assume that the location parameters are drawn from a two-point distribution...
+    \item {\em Most existing works assume the constant signal strength, which essentially assume that the location parameters are drawn from a two-point distribution...
 However, it is a bit far from realistic from my perspective because the practical case often involves a mixture of strong and weak signals.
@@
     Thank you.  We were not aware of the interesting and very recent work \cite{li2020optimality}
-     of Li and Fithian. We wholeheartedly agree that the set-up proposed my the reviewer is much more realistic.  
-     It is quite interesting and stimulating for us to learn that the Higher Criticism statistic no longer dominates the Bonferonni thresholding procedure.  
-     This changes our general understanding about optimality of the max-statistic.  Although, we are not prepared to contribute more to the subject from 
-     the more general perspective of  \cite{li2020optimality}, we have included brief comments about this very recent development in Chapters 2 and 3.  
+     of Li and Fithian. We wholeheartedly agree that the set-up described by the reviewer is much more realistic.  
+     It is quite interesting and stimulating for us to learn that the Higher Criticism statistic no longer dominates the max-type Bonferonni thresholding procedure.  
+     This changed our general understanding about optimality of the max-statistic.  Although, we are not prepared to contribute more to the subject from 
+     the more realistic perspective of  \cite{li2020optimality}, we have quoted this very recent and fascinating development in Chapters 2 and 3.  
      Since our focus in this manuscript is mostly on the support estimation problem (rather than on the detection problem), we decided not to pursue 
-     this new and important line of research, which may require resolving some new mathematical challenges. We hope to understand this phenomenon 
+     this new and interesting line of research, which may require resolving some new mathematical challenges. We hope to understand this phenomenon 
      better in the near future.
@@
   exponent $H = 1 - \gamma/2 \in (1/2,1)$.  This is in stark contrast with the usual Brownian motion limit which arises 
-  under the {\em weak dependence}.  The behaviors of many sum-based statistics will change dramatically when the dependence switches from
+  under the {\em weak dependence}.  The behavior of many sum-based statistics changes dramatically when the dependence switches from
   short- to long-range.  For more details, see e.g. \cite{pipiras:taqqu:2017} and the references therein.
 
-  Shockingly, when considering even most heavily dependent (say Gaussian) stationary time series $\{X_k\}$, the limit behavior of the maxima
+  Shockingly, when considering even most heavily dependent (say long-range dependent) Gaussian
+   stationary time series $\{X_k\}$, the limit behavior of the maxima
   is no different than in the iid case.  Indeed, the Berman condition (cf \cite{berman1964limit,leadbetter2012extremes})
   $$
-  {\rm Cov}(X_k,X_0) = o (\log k),\ \ \mbox{ as }k\to\infty,
+  {\rm Cov}(X_k,X_0) = o \Big(\frac{1}{\log k}\Big),\ \ \mbox{ as }k\to\infty,
   $$
@@
 
-  In particular, the Berman condition holds for Gaussian long-range dependent models!  Thus, even when the traditional notions of weak dependence for
+  In particular, the Berman condition holds for most Gaussian long-range dependent models!  Thus, even when the traditional notions of weak dependence for
   sums no longer hold, the dependence is weak enough for the maxima to behave as in the iid setting.
@@
   We find this to be an important and perhaps somewhat overlooked universality phenomenon showing that maxima of Gaussians 
-  (and in fact, general light-tailed variables) continue to concentrate under drastically stronger dependence than we are accustomed to deal with 
-  in the case of sums/averages.
+  (and perhaps much more broad classes of light-tailed arrays) continue to concentrate under drastically stronger dependence than we are 
+  accustomed to deal with in the case of sums/averages.
 
@@
    under standard in-coherence conditions, between the  signal and the covariance, the simple Bonferonni thresholding estimator is optimal for exact 
-   support recovery.  We are not aware of many more examples, but hope that the developed general theory applies in many more setting.  We now 
-   include a remark on this important reference.
+   support recovery.  We are not aware of many more examples, but hope that the developed general theory applies in many more setting.  
+   %We now include a remark on this important reference.
 
@@
 
-  Thank you for the insightful comment.  Indeed, by Slepian's Lemma, negatively correlated Gaussian variables have smaller maxima (in stochastic order)
+  Thank you for the insightful comment.  Indeed, by Slepian's Lemma, negatively correlated Gaussian variables have larger maxima (in stochastic order)
   than iid maxima (with the same marginals).  This difference, however, is negligible asymptotically.  Intuitively, this is due to the fact that while Gaussian

### 2021-03-19 preamble.tex
.
minor edit

@@
 phase-transition results help explain and quantify a previously observed empirical phenomenon of the so-called {\em steep part of the power 
-curve}  In the last chapter of this work, we detail this application and highlight future theoretical and practical consequences of our work.
+curve}.  In the last chapter of this work, we detail this application and highlight future theoretical and practical consequences of our work.
 

### 2021-04-04 reviews/response.tex
many changes... Chapter 4 intro WIP

@@
  \begin{itemize}
-  \item {\bf (Brief description)} The revised manuscript has now a brief introductory chapter and 6 substantive chapters, 
-  which amount to a total of 125 pages. As with the original submission,  Chapter 2 reviews the statistical risks, estimation and testing procedures,
-  as well as probability models for the errors used in the rest of the manuscript.  It contains also a high-level summary of our results 
-  in the context of the existing literature and some auxiliary facts from probability and extreme value theory.  For convenience of the reader, we 
-  have added statements of Slepyan's Lemma and the Sudakov-Fernique inequality (without proofs).
+%  \item {\bf (Brief description)} The revised manuscript has now a brief introductory chapter and 6 substantive chapters, 
+%  which amount to a total of 125 pages. As with the original submission,  Chapter 2 reviews the statistical risks, estimation and testing procedures,
+%  as well as probability models for the errors used in the rest of the manuscript.  It contains also a high-level summary of our results 
+%  in the context of the existing literature and some auxiliary facts from probability and extreme value theory.  For convenience of the reader, we 
+%  have added statements of Slepyan's Lemma and the Sudakov-Fernique inequality (without proofs).
+%  
+%   Chapter 3 provides a panorama of the phase-transition results in the signal detection and support estimation problems for the additive
+%   iid Gaussian error model.  Its purpose is to emphasize ideas and provide an accessible account, including references to the state-of-the-art 
+%   in the literature.  The chapter contains also some new results on the (sub)optimality of some popular statistics, which appear to have been 
+%   overlooked in the literature (Theorem 3.1).  One main idea  behind the exposition is to systematically present the different types of phase transition 
+%   results as a function of the chosen statistical risk.  
+%   
+%   Chapters 4 through 7 contain the core of our original contributions.  
+%   
+%   Chapter 4 establishes phase-transitions results for the exact support recovery problem in the additive error model.  The main themes of this 
+%   chapter are {\em error--dependence} and {\em concentration of maxima}. We establish that the notion of uniform relative stability -- 
+%   a type of concentration of maxima phenomenon -- is key to characterizing the phase-transition in exact support recovery for the general class 
+%   of thresholding estimators. 
+%   
+%   Chapter 5 begins with a study of the finite-sample (Bayes) optimality and sub-optimality of the threshold-based support estimators.  
+%   Criteria for the latter are established and certain theoretical results indicate that {\em likelihood thresholding} (as opposed to data thresholding)
+%   is in general optimal, when the thresholding estimators are sub-optimal.  In the regime when the thresholding estimators are optimal, i.e., 
+%   for log-concave error densities, our results entail 
+%   a universal statistical limit in the exact support recovery problem, valid for all estimators (Theorem 5.3).   On the other hand, for the general class of
+%   thresholding estimators, we obtain minimax characterizations of the phase-transition in exact support recovery, for every fixed error-dependence 
+%   structure that satisfies the mild uniform relative stability condition (Corollary 5.3).
+%   
+%   Chapter 6 is nearly unchanged. It is more probabilistic in nature and it provides a complete characterization of the uniform relatively stable (URS) Gaussian 
+%   triangular arrays.  This URS condition is the key property used to establish the lower bound on exact support recovery under dependence in Chapter 4. 
+%   These probabilistic results as well as their methods of proof may be of independent interest and are presented in a way that should be 
+%   accessible to a wider audience of graduate students in statistics. 
+%   
+%   Chapter 7 focuses on an application to genome-wide association studies (GWAS) in statistical genetics.  It is shown that all phase-transition results in the 
+%    additive error models of Chapter 3, have their close counterparts for the chi-square models arising naturally in GWAS. To connect these
+%    asymptotic results to the practical notions in statistical genetics, we establish the connection between the odds-ratio (effect size) in multinomial 
+%    $2\times 2$ models
+%    and the signal-size parameter of the corresponding chi-square association test.  This allows us to quantify the statistical power and
+%     optimal design questions in a unified manner as well as ultimately explain the role of phase-transitions in the fundamental statistical limits of GWAS.
+%
 
-   Chapter 3 provides a panorama of the phase-transition results in the signal detection and support estimation problems for the additive
-   iid Gaussian error model.  Its purpose is to emphasize ideas and provide an accessible account, including references to the state-of-the-art 
-   in the literature.  The chapter contains also some new results on the (sub)optimality of some popular statistics, which appear to have been 
-   overlooked in the literature (Theorem 3.1).  One main idea  behind the exposition is to systematically present the different types of phase transition 
-   results as a function of the chosen statistical risk.
+  \item {\bf (Organization)} 
+  The manuscript has been revised substantially to include a brief introductory chapter and 6 substantive chapters, which amount to a total of 125 pages.
+  As with the original submission, Chapter 2 reviews the statistical risks, estimation and testing procedures, as well as probability models for the errors used in the rest of the manuscript.
 
-   Chapters 4 through 7 contain the core of our original contributions.
+  After very careful deliberation, we decided to keep most of the content in Chapter 3, which provides a panorama of the phase-transition results in the signal detection and support estimation problems for the additive iid Gaussian error model.
+  There were some mixed opinions from the reviewers regarding the inclusion of a chapter that paints the landscape in broad strokes and provides references to the state-of-the-art of the literature, at the expense of delaying entirely original contributions.
+  We think that providing an accessible account of the subject of high-dimensional multiple testing would benefit readers who are not already experts in the area, and might just narrowly outweigh the additional patience required on the part of experts before we get to the more exciting material.
+  Details and explanations of the changes we made can be found in the reponse to Reviewer 2 below.
 
-   Chapter 4 establishes phase-transitions results for the exact support recovery problem in the additive error model.  The main themes of this 
-   chapter are {\em error--dependence} and {\em concentration of maxima}. We establish that the notion of uniform relative stability -- 
-   a type of concentration of maxima phenomenon -- is key to characterizing the phase-transition in exact support recovery for the general class 
-   of thresholding estimators.
+  To better balance the exposition, we reorganized Chapter 4 of the previous version of the draft into two new chapters (now Ch.\ 4, entitled ``Exact Support Recovery Under Dependence'',  and Ch.\ 5 ``Bayes and Minimax Optimality'').
+  This change, in addition to making all chapters more manageable and of about equal lengths, exposes more clearly our contributions. 
+  The results contained in Chapters 4 and 5 as well as the more probabilistic Chapter 6 and the more applied Chapter 7 are original contributions to the literature.
 
-   Chapter 5 begins with a study of the finite-sample (Bayes) optimality and sub-optimality of the threshold-based support estimators.  
-   Criteria for the latter are established and certain theoretical results indicate that {\em likelihood thresholding} (as opposed to data thresholding)
-   is in general optimal, when the thresholding estimators are sub-optimal.  In the regime when the thresholding estimators are optimal, i.e., 
-   for log-concave error densities, our results entail 
-   a universal statistical limit in the exact support recovery problem, valid for all estimators (Theorem 5.3).   On the other hand, for the general class of
-   thresholding estimators, we obtain minimax characterizations of the phase-transition in exact support recovery, for every fixed error-dependence 
-   structure that satisfies the mild uniform relative stability condition (Corollary 5.3).
-
-   Chapter 6 is nearly unchanged. It is more probabilistic in nature and it provides a complete characterization of the uniform relatively stable (URS) Gaussian 
-   triangular arrays.  This URS condition is the key property used to establish the lower bound on exact support recovery under dependence in Chapter 4. 
-   These probabilistic results as well as their methods of proof may of independent interest and are presented in a way that should be 
-   accessible to a wider audience of graduate students in statistics.
-
-   Chapter 7 focuses on an application to genome-wide association studies (GWAS) in statistical genetics.  It is shown that all phase-transition results in the 
-    additive error models of Chapter 3, have their close counterparts for the chi-square models arising naturally in GWAS. To connect these
-    asymptotic results to the practical notions in statistical genetics, we establish the connection between the odds-ratio (effect size) in multinomial 
-    $2\times 2$ models
-    and the signal-size parameter of the corresponding chi-square association test.  This allows us to quantify the statistical power and
-     optimal design questions in a unified manner as well as ultimately explain the role of phase-transitions in the fundamental statistical limits of GWAS.
-
-  \item {\bf (Organization)} Following a suggestion of a reviewer ({\bf R2}),  we have incorporated most proofs 
-  in the text right after the corresponding claims (theorems, propositions, lemmas).  In the interest of space and to conform with the format of
-  the SpringerBriefs series, we no longer include ``Exercises'' sections.
-
-  Last but not least, to better balance the exposition, we decided to divide the previous
-  Chapter 4 into two new chapters (now Ch.\ 4, entitled ``Exact Support Recovery Under Dependence'', 
-  and Ch.\ 5 ``Bayes and Minimax Optimality'').  This change, in addition to making all chapters more manageable and of about equal length, 
-  exposes more clearly our contributions.  The results contained in Chapters 4 and 5 as well as the more probabilistic Chapter 6 and more 
-  applied Chapter 7 are 
-  original and new contributions to the literature.
+  Following the suggestion of Reviewer 2 ({\bf R2}),  we have placed most proofs in the text after the corresponding claims (theorems, propositions, lemmas).
+In the interest of space and to conform with the format of the SpringerBriefs series, we no longer include ``Exercises'' sections.
 
   \item {\bf (Typos, grammar, and style)}  Prompted by criticism of a referee ({\bf R2}), we have revised the language of the manuscript. 
-  We have corrected a large number of typos, missing articles as well as attempted to make the language more consistent.  In the spirit of
-  making the style more accessible, we re-formatted the statements of a large number theorems so that they are more modular.
+  We have corrected a number of typos and missing articles.   
+  There have been re-writes throughout the manuscript in order to make the style more consistent.  
+  In trying to make the text more accessible, we re-formatted the statements of most theorems to make them more modular.
 
  \item {\bf (Length and online supplement)} We have shortened the manuscript to just under 125 pages. The Appendix appearing after the 
- References is meant to become an online supplement should the manuscript be considered for publication.  The appendix contains some proofs
- of phase-transition results stated in Ch.\ 7, which are similar to ones appearing in Ch.\ 3.% as well as some phase transition results for lighter and/or
+ References is meant to become an online supplement when the manuscript becomes ready for publication.
+The appendix contains some proofs of phase-transition results stated in Ch.\ 7, which are similar to ones appearing in Ch.\ 3.% as well as some phase transition results for lighter and/or
  %heavier tailed models than the AGG class.  
- Thus, even without the online supplement, not much is lost by
- not including the Appendix in the printed version.
+ Thus, even without the online supplement, not much is lost by not including the Appendix in the printed version.
 
@@
  \subsection{Reviewer 1 (R1)}
+
+ We are grateful for the positive comments and important feedbacks from the reviewer.
 
@@
   two separate chapters (Ch.\ 4 and 5, now).   We have added some more insights to the statements in Ch.\ 3 and Ch.\ 7, as well as some more 
-  background material in Ch.\ 2.  In addition to making the more advanced material accessible, these changes have improved the balance between
-  the chapters, which can be read independently and are better suited for a special topics course.
+  background material in Ch.\ 2.  
+  These changes, in addition to making the more advanced material accessible, should improve the balance between the chapters and make them read better independently, thus making the text better suited for a special topics course.
 
@@
 Gao and some related articles.
-The main idea is about concentration of maxima in the sense of a law of large numbers (which is a rather rough result in this context; it could be supplemented by finer results on large deviations of maxima, as used in the context of a.s.
-convergence of maxima; e.g.
+The main idea is about concentration of maxima in the sense of a law of large numbers (which is a rather rough result in this context; it could be supplemented by finer results on large deviations of maxima, as used in the context of a.s.\ convergence of maxima; e.g.
 the cited results of Barndorff; Resnick, Tomkins.
@@
 
-     We have thoroughly revised the exposition and fixed most (and hopefully all) typos and grammatical errors.  We have also streamlined the exposition 
+     We have thoroughly revised the exposition and fixed hopefully all typos and grammatical errors.  We have also streamlined the exposition 
      and tried to ground it.
@@
      As indicated above, we have shortened the manuscript, eliminated the exercises, and cast it into the format of a SpringerBriefs monograph.  We 
-     appreciate the reviewer's suggestions, but we felt that the work is not mature enough to extend to a textbook. At the same time, by balancing the
-     chapter lengths and content, we believe now the manuscript is more appropriate for an auxiliary text in a special topics graduate course on 
-     high-dimensional statistics.
+     appreciate the reviewer's suggestions on extending the manuscript, but we felt that the work is not mature enough to ne expanded into a longer textbook.
+     In trying to balance the chapter lengths and content, we believe now the manuscript is more appropriate for an auxiliary text in a special topics graduate course on high-dimensional statistics.
 
@@
 
-     We really appreciate the feedback, which made us thoroughly revise the presentation!
+     We really appreciate the feedback, which prompted us to thoroughly revise the presentation.
 
-     Some results of Chapter 3 are in fact new.  The main philosophy behind Chapters 2 and 3 is to emphasize the (perhaps 
-     overlooked) impact the choice the statistical loss has on the statistical limits in support recovery.    Ch.\ 3 serves the purpose of reviewing 
-     the existing literature, while at the same time providing a unified treatment of phase transitions, suitable for an introduction to a wider audience.  
-     To emphasize this  role, we have now changed the title of this chapter to ``A panorama of phase transitions''.  Theorem 3.1 both summarizes known as well as presents 
-     some new {\em overlooked} results on the sub-optimality of certain popular statistics.  The other results in Chapter 3 are also closely connected to the 
-    phase-transition results in Chapter 7 on GWAS, which are new.  This exposition allowed us to omit the proofs of the results in Ch.\ 7 (presented in an 
-    online supplement) and focus on the discussion of statistical power and optimal design issues, which are very relevant in practice and also novel.
+     The main goal of Chapters 2 and 3 is to shed light on the relationships between typical high-dimensional problems and their respective statistical limits. 
+     In particular, Ch.\ 3 reviews the existing literature, and provide a unified treatment of the phase transitions under different loss functions.
+%     To the best of our knowledge, such a unified treatment has not been available before.
+
+     The inclusion of material surrounding Theorem 3.1 seems to be of concern.
+     Indeed, Theorem 3.1 summarizes some known results in the signal detection problem, which may be familiar to experts in the field.
+     On the other hand, Theorem 3.1 also presents some new, previously overlooked results on the sub-optimality of certain popular statistics. 
+     These results are not the most exciting advances in either methodology or theory (and unfortunately will likely not be found in a journal publication because of their perceived lack of novelty).
+Nevertheless, they are natural and practically important questions that needed answers.
+     In addition to these incremental contributions, we think that there is some value in collecting a range of related problems and results in one place.
+This inclusion of a bird's-eye view, however cursory,  would make the text more suitable for an introduction to a wider audience.
+     To emphasize this role, we changed the title of this chapter to ``A panorama of phase transitions''.
+
+%     The results in Chapter 3 are also closely connected to the phase-transition results in Chapter 7 on GWAS. 
+%     This exposition allowed us to omit the proofs of the results in Ch.\ 7 (presented in an online supplement) and focus on the discussion of statistical power and optimal design issues, which are very relevant in practice and also novel.
 
@@
 
-     We hope that the revision has resulted in a more accessible manuscript, which at the same time more clearly shows our new ideas and results in the
-     context of the existing literature.
+     We hope that the revision has resulted in a more accessible manuscript, which at the same time more clearly highlights new ideas and results in the
+     context of existing literature.
 
@@
 
-     Chapter 6 (now Ch.\ 7) has been thoroughly revised and the proofs of phase-transition results similar to the ones in Ch.\ 3 have been omitted.  They
+     Chapter 6 (now Ch.\ 7) has been thoroughly revised. 
+     The proofs of phase-transition results similar to the ones in Ch.\ 3 have been omitted.  They
      will be presented in an online supplement (appearing as the Appendix section after the References).  This 
@@
     \medskip
-    Thank you.  We were not aware of the interesting and very recent work \cite{li2020optimality}
-     of Li and Fithian. We wholeheartedly agree that the set-up described by the reviewer is much more realistic.  
-     It is quite interesting and stimulating for us to learn that the Higher Criticism statistic no longer dominates the max-type Bonferonni thresholding procedure.  
-     This changed our general understanding about optimality of the max-statistic.  Although, we are not prepared to contribute more to the subject from 
-     the more realistic perspective of  \cite{li2020optimality}, we have quoted this very recent and fascinating development in Chapters 2 and 3.  
-     Since our focus in this manuscript is mostly on the support estimation problem (rather than on the detection problem), we decided not to pursue 
-     this new and interesting line of research, which may require resolving some new mathematical challenges. We hope to understand this phenomenon 
-     better in the near future.
+    Thank you.
+We were not aware of the interesting and very recent work \cite{li2020optimality} of Li and Fithian when the first draft was prepared.
+We wholeheartedly agree that the set-up described by the reviewer is much more realistic.
+    It is stimulating for us to learn that the Higher Criticism statistic no longer dominates the max-type Bonferonni thresholding procedure when $1/2<\beta<3/4$, as long as the signals are spread out, even if the noise terms remain Gaussian.
+%    This changed our understanding about optimality of the max-statistic.  
+    We now discuss and reference this recent and fascinating development in Chapters 2 and 3 where appropriate. 
+%    This new development on the spread-out and heavy-tailed signals setting is parallel to the heavy-tailed noise setting that we pursued in this manuscript.
 
-     \fbox{Zheng, PLEASE CHECK how if I quoted the work of  Li and Fithian in Ch 2 and 3, appropriately.  Thanks!}
+    One naturally wonders what happens, e.g., when both signals and noise terms are distributed with regularly-varying tails, and what can be said about the support recovery problems when signals are spread-out.
+    Since our focus in this manuscript is weighted towards support estimation problems rather than the detection problem, we have refrained from discussing more in the direction of the more realistic setting of \cite{li2020optimality}, which would require resolving some new mathematical challenges.
+    We hope to understand this phenomenon better in the near future.
 
@@
 
-    \fbox{Zheng, need help here?}
+    We have edited the following explanation when introducing the asymmetric statistical risks:
+    \begin{quote}
+    $\dots$
+	In applications, however, attitudes towards false discoveries and missed signals are often asymmetric.
+	In the example of GWAS, where the number of candidate locations \$p\$ could be in the millions, and a class imbalance between the number of nulls and signals exists, researchers are typically interested in the marginal (location-wise) power of discovery, while exercising stringent (family-wise) false discovery control.
+	These types of asymmetric considerations, while important in applications, have not been studied theoretically.  
+	For example, the GWAS application motivates the \textbackslash\{\}emph\{exact-approximate\} support recovery risk, which weighs both the family-wise error rate and the marginal power of discovery:
+	$\dots$
+    \end{quote}
+    In fact, we believe that power calculations for GWAS is most natrually interpreted when viewed through the exact-approximate support recovery risk.
+
+    On the other hand, we are not aware of an equally strong motivating application for the approximate-exact support recovery risk. 
+    It is harder to come up with a scenario where we want to weed out a few nulls from a large number of signals, with strong type II control and evaluate marginal type I errors. 
+%    However, if it had been left out, the discussion would not feel complete humanly love for symmetry.
 
@@
 
-        \fbox{Help.}
+    There have been discussions on unequally weighted type I and type II errors.
+For example, the version of asymmetric risk suggested by the reviewer (i.e., $\textrm{FDR} + \lambda\textrm{FNR}$) appeared in Genovese and Wasserman \citep{genovese2002operating} Section 6, although the asymptotic limits were not discussed there.
+
+    The asymptotic limits would not have been different for the weighted risk, so long as $\lambda$ is bounded away from zero and infinity.
+    This is because $\textrm{FDR} + \lambda\textrm{FNR}$ vanishes if and only if both FDR and FNR vanish; conversely, non-vanishing FDR and FNR is equivalent to non-vanishing weighted risk.
+    Therefore, the only (theoretically) interesting weighting of type I and type II errors is combining family-wise error metrics with marginal errors, as in the exact-approximate support recovery risk.
+
+    We have added this comment on risk weighting to the manuscript.
 
@@
 
+    It can be shown that the more restrictive UDD' condition (Definition 6.2 in the new numbering) implies weak dependence as described in Fan et al \cite{fan:xu:gu:2012} (the single sum in the reviewer's comment seems to be a typo),
+    $$
+    \lim_{p\to\infty}\frac{1}{p^2} \sum_{i,j} |\Sigma_p(i,j)| = 0.
+    $$
+    Starting with the assumed permutations $l_p$ of $\{1, . . . , p\}$ in UDD', we have the equality
+    $$
+    \sum_{i,j} |\Sigma_p(i,j)| = \sum_{i,j} |\Sigma_p(i',j')|,
+    $$
+    where $i'= l_p(i)$, $j'= l_p(j)$, since permutations do not affect the sum.
+    By the second assumption of a sequence $r_n\to0$ that bounds the correlations from above, we have
+    $$
+    \frac{1}{p^2} \sum_{i,j} |\Sigma_p(i',j')| \le \frac{1}{p^2} \sum_{i,j} r_{|i-j|} \le \frac{1}{p} \sum_{k=0}^{p-1} r_{k} \to 0.
+    $$
+    Therefore UDD' impies the weak dependence condition.
+
     \medskip
-   \noindent Indeed, the notion of {\em weak dependence} in its various forms of mixing coefficients and dependence functionals
-    has a long and fruitful history in the study of large-sample limit theorems.  We appreciate this natural question!  There is a fundamental 
-    difference between the notions of weak dependence required to establish the asymptotic behavior of sums and those for maxima.     
-    As a rule, the maxima of dependent variables behave
-   very similarly to the maxima of independent variables even under {\em severe dependence}.  This is in stark contrast with the large-sample 
-   behavior of dependent sums (averages), which have been much more extensively studied in the literature.  We have now
-    clarified and emphasized these differences in several places in the text.
+    We can also establish that the UDD/URS condition is no-weaker than the weak dependence condition.
+    We use the same non-UDD example outlined in Example 6.1 (new numbering).
+    Suppose ${\cal E} = \left(\epsilon_p(i)\right)_{i=1}^p$ is Gaussian, and is comprised of $\lfloor p^{1-\beta}\rfloor$ blocks, each of size at least $\lfloor p^\beta \rfloor$.
+Let the elements within each block have correlation 1, and let the elements from different blocks be independent.
+    It follows that 
+    $$
+    \frac{1}{p^2} \sum_{i,j} |\Sigma_p(i,j)| \sim \frac{1}{p^2} (p^{1-\beta})^2 p^{\beta} = p^{-\beta} \to 0,
+    $$
+    and therefore ${\cal E}$ is weakly dependent as defined in \cite{fan:xu:gu:2012}, but not UDD/URS.
 
-    We provide below some brief comments on the way we understand the differences between the asymptotic behaviors of sums and maxima 
-    under dependence.  This is certainly a big and important subject and the following discussion is just on the level of ideas.
-    The weak dependence condition stated by the referee appears to be tailored to the study of sums rather than maxima.  For example, a 
-    stationary (finite-variance) time-series $\{X_k,\ k\in \mathbb Z\}$ is said to be short-range dependent if
-   $$
-   \sum_{k=1}^\infty |{\rm Cov} (X_{k}, X_0) | <\infty.
-   $$
-   If the latter sum is infinite, the time series is referred to as long-range dependent. For example, consider the Gaussian case, where
-   the time series has a power-law auto-covariance ${\rm Cov}(X_{k}, X_0) \propto k^{-\gamma},\ \ k\to\infty$, for $\gamma \in (0,1)$.  In this long-range
-   dependent regime, it can be shown that, as $n\to\infty$,
-  $$
-  \Big\{ \frac{1}{n^H} \sum_{k=1}^{[nt]} (X_k -\mathbb E X_k) \Big\}_{t\ge 0} \stackrel{f.d.d.}{\longrightarrow} B_H = \{B_H(t),\ t\ge 0\},
-  $$   
-  where $B_H$ is the fractional Brownian motion process -- a Gaussian, stationary increment and  self-similar process with 
-  exponent $H = 1 - \gamma/2 \in (1/2,1)$.  This is in stark contrast with the usual Brownian motion limit which arises 
-  under the {\em weak dependence}.  The behavior of many sum-based statistics changes dramatically when the dependence switches from
-  short- to long-range.  For more details, see e.g. \cite{pipiras:taqqu:2017} and the references therein.
+    However, it is not clear to us whether the weak dependence condition is weaker than UDD as well.
+    The comparison is complicated by the fact that the definition of UDD only cares about positive correlations, while the weak dependence condition takes the sum of absolute values of the correlations.
 
-  Shockingly, when considering even most heavily dependent (say long-range dependent) Gaussian
-   stationary time series $\{X_k\}$, the limit behavior of the maxima
-  is no different than in the iid case.  Indeed, the Berman condition (cf \cite{berman1964limit,leadbetter2012extremes})
-  $$
-  {\rm Cov}(X_k,X_0) = o \Big(\frac{1}{\log k}\Big),\ \ \mbox{ as }k\to\infty,
-  $$
-  guarantees in this setting that, as $n\to\infty$,
-  \begin{equation}\label{e:Gumbel}
-  \frac{1}{a_n} \max_{k=1,\cdots,n} X_k - b_n \stackrel{d}{\longrightarrow} Z \sim {\rm Gumbel},
-  \end{equation}
-  where $a_n$ and $b_n$ are {\em the same} scaling and shift sequences as in the case of iid data.  That is, if $X_k^*$ are iid with the same marginal 
-  distribution as the $X_k$'s, then
-  $$
-  \frac{1}{a_n} \max_{k=1,\cdots,n} X_k^* - b_n \stackrel{d}{\longrightarrow} Z,
-  $$
-  where the normalizing constants $a_n$ and $b_n$ as well as the limit $Z$ are the same as in \eqref{e:Gumbel}.
+%   \medskip
+%   \noindent Indeed, the notion of {\em weak dependence} in its various forms of mixing coefficients and dependence functionals
+%    has a long and fruitful history in the study of large-sample limit theorems.  
+%%    We appreciate this natural question!  
+%    There is a fundamental difference between the notions of weak dependence required to establish the asymptotic behavior of sums and those for maxima.     
+%    As a rule, the maxima of dependent variables behave very similarly to the maxima of independent variables even under {\em severe dependence}.
+This is in stark contrast with the large-sample behavior of dependent sums (averages), which have been much more extensively studied in the literature.
+We have now
+%    clarified and emphasized these differences in several places in the text. 
+%    
+%    We provide below some brief comments on the way we understand the differences between the asymptotic behaviors of sums and maxima 
+%    under dependence.  This is certainly a big and important subject and the following discussion is just on the level of ideas.
+%    The weak dependence condition stated by the referee appears to be tailored to the study of sums rather than maxima.  For example, a 
+%    stationary (finite-variance) time-series $\{X_k,\ k\in \mathbb Z\}$ is said to be short-range dependent if
+%   $$
+%   \sum_{k=1}^\infty |{\rm Cov} (X_{k}, X_0) | <\infty.
+%   $$
+%   If the latter sum is infinite, the time series is referred to as long-range dependent. For example, consider the Gaussian case, where
+%   the time series has a power-law auto-covariance ${\rm Cov}(X_{k}, X_0) \propto k^{-\gamma},\ \ k\to\infty$, for $\gamma \in (0,1)$.  In this long-range
+%   dependent regime, it can be shown that, as $n\to\infty$,
+%  $$
+%  \Big\{ \frac{1}{n^H} \sum_{k=1}^{[nt]} (X_k -\mathbb E X_k) \Big\}_{t\ge 0} \stackrel{f.d.d.}{\longrightarrow} B_H = \{B_H(t),\ t\ge 0\},
+%  $$   
+%  where $B_H$ is the fractional Brownian motion process -- a Gaussian, stationary increment and  self-similar process with 
+%  exponent $H = 1 - \gamma/2 \in (1/2,1)$.  This is in stark contrast with the usual Brownian motion limit which arises 
+%  under the {\em weak dependence}.  The behavior of many sum-based statistics changes dramatically when the dependence switches from
+%  short- to long-range.  For more details, see e.g. \cite{pipiras:taqqu:2017} and the references therein.
+%  
+%  Shockingly, when considering even most heavily dependent (say long-range dependent) Gaussian
+%   stationary time series $\{X_k\}$, the limit behavior of the maxima
+%  is no different than in the iid case.  Indeed, the Berman condition (cf \cite{berman1964limit,leadbetter2012extremes})
+%  $$
+%  {\rm Cov}(X_k,X_0) = o \Big(\frac{1}{\log k}\Big),\ \ \mbox{ as }k\to\infty,
+%  $$
+%  guarantees in this setting that, as $n\to\infty$,
+%  \begin{equation}\label{e:Gumbel}
+%  \frac{1}{a_n} \max_{k=1,\cdots,n} X_k - b_n \stackrel{d}{\longrightarrow} Z \sim {\rm Gumbel},
+%  \end{equation}
+%  where $a_n$ and $b_n$ are {\em the same} scaling and shift sequences as in the case of iid data.  That is, if $X_k^*$ are iid with the same marginal 
+%  distribution as the $X_k$'s, then
+%  $$
+%  \frac{1}{a_n} \max_{k=1,\cdots,n} X_k^* - b_n \stackrel{d}{\longrightarrow} Z,
+%  $$
+%  where the normalizing constants $a_n$ and $b_n$ as well as the limit $Z$ are the same as in \eqref{e:Gumbel}.
+%  
+%  In particular, the Berman condition holds for most Gaussian long-range dependent models!  Thus, even when the traditional notions of weak dependence for
+%  sums no longer hold, the dependence is weak enough for the maxima to behave as in the iid setting.
+Please note that in our monograph we need an even weaker notion of dependence since we need only have relative stability, i.e.,
+%  \begin{equation}\label{e:RS}
+%  \frac{1}{a_n} \max_{k=1,\cdots,n} X_k \stackrel{\P}{\longrightarrow} 1,
+%  \end{equation}
+%  as $n\to\infty$.  As shown in the seminal work of Berman \cite{berman1964limit} and in a more general situation for triangular arrays in our 
+%  Chapter 6), for the latter convergence \eqref{e:RS} to hold one merely needs the auto-covariance to vanish, i.e., 
+%  $$
+%  {\rm Cov}(X_k,X_0) = o(1),\ \ \ \mbox{ as }k\to\infty.
+%  $$
+%  We find this to be an important and perhaps somewhat overlooked universality phenomenon showing that maxima of Gaussians 
+%  (and perhaps much more broad classes of light-tailed arrays) continue to concentrate under drastically stronger dependence than we are 
+%  accustomed to deal with in the case of sums/averages.
+%
 
-  In particular, the Berman condition holds for most Gaussian long-range dependent models!  Thus, even when the traditional notions of weak dependence for
-  sums no longer hold, the dependence is weak enough for the maxima to behave as in the iid setting.
-Please note that in our monograph we need an even weaker notion of dependence since we need only have relative stability, i.e.,
-  \begin{equation}\label{e:RS}
-  \frac{1}{a_n} \max_{k=1,\cdots,n} X_k \stackrel{\P}{\longrightarrow} 1,
-  \end{equation}
-  as $n\to\infty$.  As shown in the seminal work of Berman \cite{berman1964limit} and in a more general situation for triangular arrays in our 
-  Chapter 6), for the latter convergence \eqref{e:RS} to hold one merely needs the auto-covariance to vanish, i.e., 
-  $$
-  {\rm Cov}(X_k,X_0) = o(1),\ \ \ \mbox{ as }k\to\infty.
-  $$
-  We find this to be an important and perhaps somewhat overlooked universality phenomenon showing that maxima of Gaussians 
-  (and perhaps much more broad classes of light-tailed arrays) continue to concentrate under drastically stronger dependence than we are 
-  accustomed to deal with in the case of sums/averages.
+    \item {\em This is another line of work that studies the strong dependence structure where the covariance matrix has a factor structure (eg.
+Fan 2012).
+For instance, this includes the equi-correlated case.
+Are you aware of any results under strong dependence in your context?}
 
-   \item {\em This is another line of work that studies the strong dependence structure where the covariance matrix has a factor structure 
-   (eg. Fan 2012). For instance, this includes the equi-correlated case. Are you aware of any results under strong dependence in your context?}
-
-   We thank the reviewer for the important reference to the work of Fan, Xu and Gu \cite{fan:xu:gu:2012}, which we had overlooked.  
-   It can be seen that the {\em weak dependence} condition in their Definition 1, implies our UDD condition (for a correlation matrix).  
-   Therefore, the Gaussian error arrays of the $K_i$-variables in Relation (10) in the latter reference, are URS (uniformly relatively stable).  
-   This suggests that the PFA methodology in \cite{fan:xu:gu:2012} can perhaps be extended to apply to the exact support recovery problem.  
-   That is, one can project on the orthogonal complement of the space spanned by the top$-k$ eigenvectors of the error-covariance.  Then, perhaps 
-   under standard in-coherence conditions, between the  signal and the covariance, the simple Bonferonni thresholding estimator is optimal for exact 
-   support recovery.  We are not aware of many more examples, but hope that the developed general theory applies in many more setting.  
-   %We now include a remark on this important reference.
+    We thank the reviewer for pointing to the interesting methodological work of Fan, Xu and Gu \cite{fan:xu:gu:2012}, which aimed to estimate false discovery proportions for heavily dependent observations.
+    We are not aware of works that discuss optimality or feasibility of support recovery (i.e., multiple testing) problems under such dependence conditions.
+    The results in our text in their current form do easily extend to that of Fan et al., since even the remainder term $K_i$'s in the factor model can be more heavily dependent than under the UDD/URS condition, as discussed in the response to the previous question.
+    Nevertheless, Fan et al provides a glimpse into how heavy dependence (e.g., the equi-correlated case) may be handled, and how theoretical analysis may be carried out.
+We do hope to develop general theory that applies to the more setting.
+%   It can be seen that the {\em weak dependence} condition in their Definition 1, implies our UDD condition (for a correlation matrix).  
+%   Therefore, the Gaussian error arrays of the $K_i$-variables in Relation (10) in the latter reference, are URS (uniformly relatively stable).  
+%   This suggests that the PFA methodology in \cite{fan:xu:gu:2012} can perhaps be extended to apply to the exact support recovery problem.  
+%   That is, one can project on the orthogonal complement of the space spanned by the top$-k$ eigenvectors of the error-covariance.  Then, perhaps 
+%   under standard in-coherence conditions, between the  signal and the covariance, the simple Bonferonni thresholding estimator is optimal for exact 
+%   support recovery.  
+%   We are not aware of many more examples, but hope that the developed general theory applies in many more setting.
 
@@
 
-\item  {\em Fig 3.2 shows that the exact-approximate support recovery is strictly easier to achieve than the approximate-exact support recovery. 
-Do you have intuition on it?}
+    \item  {\em Fig 3.2 shows that the exact-approximate support recovery is strictly easier to achieve than the approximate-exact support recovery. Do you have intuition on it?}
 
-\fbox{Help, please! Is it related to the fact that $p\gg p^{1-\beta}$. }
+    To provide an intuition, consider the distances between the decision boundaries and the means of the null and signal part of the observations, respectively.
+    Controlling the FWER requires setting the decision boundaries approximately 
+    \begin{equation} \label{FWER}
+    \sqrt{2\log{p}}
+    \end{equation}
+    away from zero (mean of nulls), as is well-known in the Bonferroni adjustment.
 
-\item {\em The phrase ``exact support recovery''  is used for both the general problem
-(as in the title of Chapter 2), and for the specific criterion risk$^{\rm E}$. This is a bit confusing.}
+    Controlly FDR, on the other hand, depends on the number of signals present.
+    When there are fewer signals, a FDR-controlling procedure has to be more conservative -- when the number of true signals is small, the number of false discoveries reported along with them has to reduce as well.
+    Consequently, the decision boundary has to be further away from zero as $\beta\to1$.
+    Quantitatively, this distance varies with $\beta$ approximately as
+    \begin{equation} \label{FDR}
+    \sqrt{2\beta\log{p}},
+    \end{equation}
+    with sparser problems requiring a larger separation. 
+    Notice that the distance required for FDR control in an extremely sparse problem ($\beta\to1$) is no different from that of FWER control.
+    For very dense problems ($\beta\to0$), the distance vanishes on the Bonferroni scale.
+
+    Similar to FWER, controlling the family-wise non-discovery rate (FWNR) requires this boundary to be approximately
+    \begin{equation} \label{FWNR}
+    \sqrt{2\log{(p^{1-\beta})}} = \sqrt{2(1-\beta)\log{p}}
+    \end{equation}
+    away from the mean of the signals.
+
+    Finally, controlling false non-discovery ratio (FNR) is similar to FDR control, except the class imbalance reverses -- the null part greatly out numbers the signals.
+    Therefore the separation between the decision boundary and the mean of signals can afford to be small.
+    So small that it vanishes on the Bonferroni scale:
+    \begin{equation} \label{FNR}
+    o\left(\sqrt{2\log{p}}\right).
+    \end{equation}
+
+    Informally, mixing and matching the two distances from nulls \eqref{FWER} and \eqref{FDR} with the two distances from signals \eqref{FWNR} and \eqref{FNR} gives rise to the four boundaries we derive in this text.
+    The fact that exact-approximate support recovery is strictly easier than approximate-exact support recovery is a consequence of \eqref{FWER} + \eqref{FNR} $\le$ \eqref{FDR} + \eqref{FWNR}.
+    But it is ultimately a consequence of the assumption on signal sparsity.
+That is, when there are more nulls than signals, the separation between the signals and the nulls has to be larger for simultaneous FDR and FWNR control.
+    % when the number of nulls is much larger than the number of signals $p\gg p^{1-\beta}$.
+
+    \item {\em The phrase ``exact support recovery''  is used for both the general problem (as in the title of Chapter 2), and for the specific criterion risk$^{\rm E}$. This is a bit confusing.}
 
@@
 
-\end{document}
+\end{document}\grid

### 2021-04-04 3.phase_transitions/3.BH_monotonicity.tex
many changes... Chapter 4 intro WIP

@@
-We make a connection between power of the \ac{BH} procedure and the stochastic ordering of distributions under the alternative.
-This result, though natural, seems new.
+As promised in the previous section, we make a connection between power of the \ac{BH} procedure and the stochastic ordering of distributions under the alternative.
+This natural result seems new.
 
@@
 
-\begin{proof}[Proof of Lemma \ref{lemma:monotonicity-BH-procedure}]
+\begin{proof}[Lemma \ref{lemma:monotonicity-BH-procedure}]
 We first re-express the BH procedure in a different form.

### 2021-04-04 3.phase_transitions/3.global-tests.tex
many changes... Chapter 4 intro WIP

--- 2021-02-04 3.phase_transitions/3.global-tests.tex
@@
 \begin{equation} \label{eq:detection-boundary-large-signals}
-    f(\beta) = 
+    f_{\mathrm{D}}(\beta) = 
     \begin{cases}
@@
 Assume that the non-zero signal sizes are all equal and parameterized as $\sqrt{2{r}\log{p}}$.
-If the signal size parameter $r$ is {\em above} the detection boundary, i.e., $r>f(\beta)$, then the global null 
+If the signal size parameter $r$ is {\em above} the detection boundary, i.e., $r>f_{\mathrm{D}}(\beta)$, then the global null 
 hypothesis $\mu(i)=0$ for all $i=1,\dots,p$ can be distinguished from the alternative as $p\to\infty$ in the sense of \eqref{eq:support-recovery-success} using the likelihood ratio test.
-Otherwise, when the signal sizes fall below the boundary, i.e., $r< f(\beta)$, no test can do better than a
+Otherwise, when the signal sizes fall below the boundary, i.e., $r< f_{\mathrm{D}}(\beta)$, no test can do better than a
 random guess.  We visualize the detection boundary in the upper panel of Figure
@@
 It is also known that the max-statistic \eqref{eq:max-statistic} is only efficient when $r>(1+\sqrt{1-\beta})^2$, and is therefore sub-optimal for denser signals where $1/2\le\beta\le 3/4$; see \cite{cai2011optimal}.
+(Recently, \cite{li2020optimality} showed that in the more general setting where signals themselves are dispersed, the sub-optimality of the max statistic disappears in the detection problem.)
 In contrast, the sum-of-square-type statistics such as $L_2$ was shown in \cite{fan1996test} to be asymptotically powerless when the $L_2$-norm of the signal $\|\mu\|_2^2$ is $o(\sqrt{p})$, or equivalently, when $\beta>1/2$ in our parametrization.
@@
 Notice that the scaling for the signal magnitude $\Delta = \sqrt{2r\log{p}}$ is useful for studying very sparse signals ($\beta>1/2$), but fails to reveal the difficulties of the detection problems when the signals are relatively dense
-($\beta<1/2$).  This is because $f(\beta) = 0,\ \beta\in (0,1/2]$. Thus, a different scaling is needed to study the regime of
+($\beta<1/2$).  This is because $f_{\mathrm{D}}(\beta) = 0,\ \beta\in (0,1/2]$. Thus, a different scaling is needed to study the regime of
 small but dense signals.  In this case, with slight overloading of notation, we parametrize signal sizes as 
@@
 \begin{equation} \label{eq:detection-boundary-small-signals}
-    f_s(\beta) = \beta - 1/2, \quad 0 < \beta \le 1/2.
+    f_{\mathrm{D}'}(\beta) = \beta - 1/2, \quad 0 < \beta \le 1/2.
 \end{equation} 
-Specifically, if $\overline{r}<f_s(\beta)$, the signal detection fails in the sense of \eqref{eq:support-recovery-failure} regardless of the procedures, while the \ac{HC} statistic continues to attain asymptotically perfect detection when $\underline{r}>f_s(\beta)$.
+Specifically, if $\overline{r}<f_{\mathrm{D}'}(\beta)$, the signal detection fails in the sense of \eqref{eq:support-recovery-failure} regardless of the procedures, while the \ac{HC} statistic continues to attain asymptotically perfect detection when $\underline{r}>f_{\mathrm{D}'}(\beta)$.
 We visualize this boundary in the lower panel of Figure \ref{fig:phase-diagram-signal-detection}.
@@
       On the other hand, the max-statistic remains powerful for sparse signals ($\beta>1/2$), and is fully efficient when the problem is very sparse ($\beta\ge3/4$).
-      The \ac{HC} statistic can detect signals in all configurations in the detectable regions.
-      See text and Theorem \ref{thm:detection-optimality}.}
+      The \ac{HC} statistic can detect signals in all configurations in the detectable regions; we explicitly marked the region where signals are only detectable by \ac{HC} among the statistics considered.
+      See the text and Theorem \ref{thm:detection-optimality}.}
       \label{fig:phase-diagram-signal-detection}

### 2021-04-04 4.exact_support_recovery/4.phase_transition_results.tex
many changes... Chapter 4 intro WIP

@@
 \begin{equation} \label{eq:signal-above-boundary}
-    \underline{r} > g(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu,
+    \underline{r} > f_{\mathrm{E}}(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu,
 \end{equation}
@@
 Under Gaussian errors, the particular choice of the thresholding at $t_p = \sqrt{2\log{p}}$ in \eqref{eq:Bonferroni-procedure} corresponds to a Bonferroni's procedure with FWER decreasing at a rate of ${\cal O}((\log{p})^{-1/2})$, and hence Theorem \ref{thm:sufficient} applies.
-By Corollary \ref{cor:FWER-controlling_procedures}, Holm's procedure --- and when the errors are independent, the {\v{S}}id{\'a}k, and Hochberg procedures --- with FWER controlled at $(\log{p})^{-1/2}$ all achieve perfect support recovery provided that $\underline{r}>g(\beta)$.
+By Corollary \ref{cor:FWER-controlling_procedures}, Holm's procedure --- and when the errors are independent, the {\v{S}}id{\'a}k, and Hochberg procedures --- with FWER controlled at $(\log{p})^{-1/2}$ all achieve perfect support recovery provided that $\underline{r}>f_{\mathrm{E}}(\beta)$.
 
@@
 \end{equation}
-for $\underline{r} > g(\beta)$, where $D(F)$ is the collection of all arrays with common marginal $F$, i.e., 
+for $\underline{r} > f_{\mathrm{E}}(\beta)$, where $D(F)$ is the collection of all arrays with common marginal $F$, i.e., 
 \begin{equation} \label{eq:common-marginal-distribution}
@@
     \begin{equation} \label{eq:signal-below-boundary}
-        \overline{r} < g(\beta) = \left(1+(1-\beta)^{1/\nu}\right)^\nu,
+        \overline{r} < f_{\mathrm{E}}(\beta) = \left(1+(1-\beta)^{1/\nu}\right)^\nu,
     \end{equation}
@@
 \begin{remark}[Minding the gap] \label{rmk:gap-between-sufficient-necessary}
-The sufficient condition in Theorem \ref{thm:sufficient} requires that \emph{all} signals be larger than the strong classification boundary $g(\beta)$ in order to achieve exact support recovery \eqref{eq:exact-recovery}, while Theorem \ref{thm:necessary} states that exact support recovery fails (in the sense of \eqref{eq:exact-recovery-failure}) when \emph{all} signal sizes are below the boundary --- the two conditions are \emph{not} complements of each other.
+The sufficient condition in Theorem \ref{thm:sufficient} requires that \emph{all} signals be larger than the strong classification boundary $f_{\mathrm{E}}(\beta)$ in order to achieve exact support recovery \eqref{eq:exact-recovery}, while Theorem \ref{thm:necessary} states that exact support recovery fails (in the sense of \eqref{eq:exact-recovery-failure}) when \emph{all} signal sizes are below the boundary --- the two conditions are \emph{not} complements of each other.
 This gap between the sufficient and necessary conditions on signal sizes, however, may be difficult to bridge.
-Indeed, in general, when signal sizes straddle the boundary $g(\beta)$, either outcome is possible, as we demonstrate in 
+Indeed, in general, when signal sizes straddle the boundary $f_{\mathrm{E}}(\beta)$, either outcome is possible, as we demonstrate in 
 Example \ref{exmp:signals-straddling-the-boundary} below.
@@
 \begin{enumerate}
-    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1+\delta)$ with $|S_p^{(1)}|=|S_p|-1$, $|S_p^{(2)}|=1$, 
-    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1-\delta)g(\beta)$ with $|S_p^{(1)}|=\lfloor|S_p|/2\rfloor$, $|S_p^{(2)}|=|S_p| - |S_p^{(1)}|$.
+    \item $r^{(1)} = (1+\delta)f_{\mathrm{E}}(\beta)$, $r^{(2)} = (1+\delta)$ with $|S_p^{(1)}|=|S_p|-1$, $|S_p^{(2)}|=1$, 
+    \item $r^{(1)} = (1+\delta)f_{\mathrm{E}}(\beta)$, $r^{(2)} = (1-\delta)f_{\mathrm{E}}(\beta)$ with $|S_p^{(1)}|=\lfloor|S_p|/2\rfloor$, $|S_p^{(2)}|=|S_p| - |S_p^{(1)}|$.
 \end{enumerate}
@@
 $$
-By the assumption that signals in $S^{(2)}$ have size parameter $(1-\delta)g(\beta)$, we have
+By the assumption that signals in $S^{(2)}$ have size parameter $(1-\delta)f_{\mathrm{E}}(\beta)$, we have
 \begin{equation}
 \P\left[\max_{j\in S^c}x(j) < \min_{j\in S^{(2)}}x(j)\right]
-= \P\left[ \frac{M_{S^{c}}}{u_p} < \frac{\sqrt{2(1-\delta)g(\beta)\log{p}} - m_{S^{(2)}}}{u_p}\right], 
+= \P\left[ \frac{M_{S^{c}}}{u_p} < \frac{\sqrt{2(1-\delta)f_{\mathrm{E}}(\beta)\log{p}} - m_{S^{(2)}}}{u_p}\right], 
 \end{equation}
@@
 \begin{align*}
-    \frac{\sqrt{2(1-\delta)g(\beta)\log{p}} - m_{S^{(2)}}}{u_p} 
-    &= \sqrt{(1-\delta)g(\beta)} - \frac{m_{S^{(2)}}}{u_{|S^{(2)}|}} \frac{u_{|S^{(2)}|}}{u_p} \\
+    \frac{\sqrt{2(1-\delta)f_{\mathrm{E}}(\beta)\log{p}} - m_{S^{(2)}}}{u_p} 
+    &= \sqrt{(1-\delta)f_{\mathrm{E}}(\beta)} - \frac{m_{S^{(2)}}}{u_{|S^{(2)}|}} \frac{u_{|S^{(2)}|}}{u_p} \\
     &\xrightarrow{\P} \sqrt{(1-\delta)} + \sqrt{1-\beta}(\sqrt{(1-\delta)} - 1) < 1.
@@
 
-Our second comment is on the interplay between thresholding procedures and the dependence class characterized by URS.
+Our second remark is on the restriction to thresholding procedures.
+\begin{remark}
+	we emphasize that the sharp phase transition result just established apply only to the general class of thresholding procedures.
+It is natural to ask if we have left out the other good procedures in this restriction.
+	We will establish in Chapter \ref{chap:optimality} below that in many cases the optimal procedures are in fact thresholding procedures.
+In general, however, thresholding procedures can be sub-optimal, e.g., when the errors have heavy (regularly-varying) tails.
+	We will also demonstrate the absence of a phase transition phenomenon in exact support recovery by thresholding, in Supplement Section \ref{suppsec:heavy-tailed}. 
+\end{remark}
+
+Our final comment is on the interplay between thresholding procedures and the dependence class characterized by URS.
 \begin{remark} \label{rmk:dependence-assumptions}
-Paraphrasing Theorems \ref{thm:sufficient} and \ref{thm:necessary}: 
-if we consider only thresholding procedures, then for a very large class of dependence structures, we cannot improve upon the Bonferroni procedure $\widehat{S}_p^{\text{Bonf}}$. 
+Paraphrasing Theorems \ref{thm:sufficient} and \ref{thm:necessary}: if we consider only thresholding procedures, then for a very large class of dependence structures, we cannot improve upon the Bonferroni procedure $\widehat{S}_p^{\text{Bonf}}$.
 Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we have
@@
     = \begin{cases}
-    \limsup_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 0, & \text{if}\quad \underline{r} > g(\beta),\\
-    \liminf_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 1, & \text{if}\quad \overline{r} < g(\beta)\\
+    \limsup_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 0, & \text{if}\quad \underline{r} > f_{\mathrm{E}}(\beta),\\
+    \liminf_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 1, & \text{if}\quad \overline{r} < f_{\mathrm{E}}(\beta)\\
     \end{cases}
@@
 Therefore, the phase transition behavior is universal in the class of dependence structures characterized by URS.
-For more details, see also Section \ref{sec:minimax}.
+%For more details, see also Section \ref{sec:minimax}.
 \end{remark}
 
-\begin{remark} We emphasize that the restriction to the URS dependence class in Theorem \ref{thm:necessary} is 
-\emph{not} an assumption of convenience. 
-The dependence condition characterized by uniform relative stability is, in fact, the weakest of its kind in the literature.
+The restriction to the URS dependence class in Theorem \ref{thm:necessary} is \emph{not} an assumption of convenience. 
+The dependence condition characterized by uniform relative stability is, in fact, one of the weakest in the literature.
 We will characterize the class URS dependence class in Chapter \ref{chap:URS} below.
-\end{remark}
 
@@
 Notice that the boundary for the signal size parameter is identically $1$ in this dense regime.
-Therefore, if we interpret $\beta = 0$ of the parametrization \eqref{eq:sparsity-parametrized} as $s\sim cp$, where $c\in(0,1)$, then the strong classification boundary \eqref{eq:strong-classification-boundary} may be continuously extended to the left-end point where $g(0)=1$.
+Therefore, if we interpret $\beta = 0$ of the parametrization \eqref{eq:sparsity-parametrized} as $s\sim cp$, where $c\in(0,1)$, then the strong classification boundary \eqref{eq:strong-classification-boundary} may be continuously extended to the left-end point where $f_{\mathrm{E}}(0)=1$.
 \end{remark}

### 2021-04-04 4.exact_support_recovery/exact_support_recovery.tex
many changes... Chapter 4 intro WIP

--- 2021-01-15 4.exact_support_recovery/exact_support_recovery.tex
@@
-We focus on exact support recovery problems in this chapter, and generalize the results we obtained in Chapter \ref{chap:phase-transitions} to additive error models with much relaxed distributional and dependence assumptions.
-Sufficient conditions for exact support recovery \eqref{eq:exact-recovery} are given in 
-Section \ref{subsec:sufficient}.  A very general class of dependence structures characterized by the uniform relative stability concept will 
-be introduced in Section \ref{subsec:URS}, to prepare us for the necessary condition in Section \ref{subsec:necessary}.
-Section \ref{subsec:dense-signals} discusses the dense signal regime, and Section \ref{suppsec:numerical} illustrates the phase transition 
-phenomena with numerical examples.  We begin with an overview of our results in the context of the existing literature.
+We focus on exact support recovery problems in this chapter.
+%Here, we limit ourselves to the general class of thresholding estimators but allow for nearly arbitrary error dependence structure.  
+%Questions on optimality and extensions to other classes of estimators are pursued in Chapter \ref{chap:optimality}.  
+As in Theorem \ref{thm:Gaussian-error-exact-boundary}, in order to study the asymptotic behaviors of $\mathrm{risk}^{\mathrm{E}}$, it is sufficient to establish minimal conditions under which the support sets can be consistently estimated, i.e.,
+\begin{equation} \label{eq:exact-recovery} 
+\P[\widehat{S}_p = S_p] \longrightarrow 1 \quad \text{as } \; p\to\infty, 
+\end{equation}
+where $\widehat{S}_p$ is an estimate of the true support set $S_p$ of a high-dimensional signal vector $\mu_p$ (recall Lemma \ref{lemma:risk-exact-recovery-probability}).
 
-\section{Contributions and related work} Consider the additive error model \eqref{eq:model-additive} with the triangular array of errors,
+To generalize the results we obtained in Chapter \ref{chap:phase-transitions} to additive error models with relaxed distributional and dependence assumptions on the additive error array, described next.
+
+%Sufficient conditions for exact support recovery are given in Section \ref{subsec:sufficient}.  A very general class of 
+%dependence structures characterized by the uniform relative stability concept will be introduced in Section \ref{subsec:URS}, to prepare us 
+%for the necessary condition in Section \ref{subsec:necessary}.
+%Section \ref{subsec:dense-signals} discusses the dense signal regime, and Section \ref{suppsec:numerical} illustrates the phase transition 
+%phenomena with numerical examples.  We begin with an overview of our results in the context of the existing literature.
+
+\section{Generalizations of distributional and dependence assumptions}
+Consider the additive error model \eqref{eq:model-additive} with the triangular array of errors,
 \begin{equation} \label{eq:error-array}
@@
 where the $\epsilon_p(i)$'s have common cumulative distribution function $F(x)=\P[\epsilon_p(i)\le x]$.
-In contrast to the assumptions in Chapter \ref{chap:phase-transitions}, we only require the errors to have common marginal distributions, and allow them to have potentially arbitrary dependence.
+In contrast to the assumptions in Chapter \ref{chap:phase-transitions}, we only require the errors to have common marginal distributions.
 % We will study the role of dependence in support recovery problems in Section \ref{sec:URS}.
@@
 Although our method of analysis applies to all light-tailed error distributions with rapidly varying tails (see Definition \ref{def:rapid-variation}), to be concrete and better convey the main ideas, we will focus on the class of $\mathrm{AGG}(\nu)$ laws (see Definition \ref{def:AGG}).
-Extensions of the results to other error models are presented in Section \ref{suppsec:other-boundaries}.
+Extensions of the results to other classes of error models are presented in Section \ref{suppsec:other-boundaries}.
 
-As in Chapter \ref{chap:phase-transitions}, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector $\mu = \left(\mu(i)\right)_{i=1}^p$ where the sparsity, with a few exceptions which will be explicitly stated, is parametrized as
+This generalized distributional assumption on the error terms call for a suitable change to parametrization of the signal sizes in order to analyze the problem.
+As in Chapter \ref{chap:phase-transitions}, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector $\mu = \left(\mu(i)\right)_{i=1}^p$ where its sparsity, with a few exceptions which will be explicitly stated, is parametrized as
 \begin{equation} \label{eq:sparsity-parametrized}
@@
 with parameters $0 < \underline{r} \le \overline{r} \le +\infty$.
-Notice that the parametrization now depends on the shape of the assumed error distributions $\mathrm{AGG}(\nu)$ through the parameter $\nu$.
-
-According to Lemma \ref{lemma:risk-exact-recovery-probability}, in order to study the asymptotic behaviors of $\mathrm{risk}^{\mathrm{E}}$, it is sufficient to establish minimal conditions under which the support sets can be consistently estimated, i.e.,
-\begin{equation} \label{eq:exact-recovery} 
-    \P[\widehat{S}_p = S_p] \longrightarrow 1 \quad \text{as } \; p\to\infty, 
-\end{equation}
-where $\widehat{S}_p$ is an estimate of the true signal support set $S_p$.
+%The signal sizes now depends on the shape of the assumed error distributions $\mathrm{AGG}(\nu)$ through the parameter $\nu$.
 
@@
 
+Dependence conditions are also relaxed.
 Several authors have studied the support recovery problem in terms of the Hamming loss and obtained minimax optimality results (see, e.g., \cite{ji2012ups, genovese2012comparison, jin2014optimality, butucea2018variable}).
-% We briefly review the recent work by \cite{butucea2018variable}, whose .
-In the special case of Gaussian marginals, \cite{butucea2018variable} showed that the boundary \eqref{eq:strong-classification-boundary-Gaussian} exists in a minimax sense.
-That is, when the errors are \emph{independent} Gaussians, the Hamming loss cannot be made to vanish if the signal sizes fall below the boundary \eqref{eq:strong-classification-boundary-Gaussian} by any procedure.
-Conversely, if signal size falls below, the Hamming loss can be made to vanish with a specific thresholding procedure.
-
-Unfortunately, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and the latter sharp results do not carry over directly to the study of the probability of support recovery or exact support recovery risk.
-More importantly, despite their elegance, these Hamming loss-minimax studies naturally reduce to the analysis of the elementary case of iid data, and is by design blind to non-trivial error-dependence structures.
-This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
-% This is arguably a consequence of the inherent limitation of the Hamming-loss approach. 
-% For practitioners, a minimax statement in the Gaussian case seems to offer little guidance.
-% Indeed, in applications, independence is an exception rather than the rule; Gaussianity of the errors may also be unnecessarily restrictive.
-
-So far in the literature, the role of dependence, and that of the distributional assumptions in model 
-\eqref{eq:model-additive} have remained largely unexplored.
-This chapter offers advances in both directions, and provides a close-to-complete solution of the exact support recovery problem.
-(See also, Chapter \ref{chap:URS}.)
+%% We briefly review the recent work by \cite{butucea2018variable}, whose .
+%In the special case of Gaussian marginals, \cite{butucea2018variable} showed that the boundary \eqref{eq:strong-classification-boundary-Gaussian} exists in a minimax sense.
+%That is, when the errors are \emph{independent} Gaussians, the Hamming loss cannot be made to vanish if the signal sizes are sufficiently small by any procedure. 
+%Conversely, if signal size falls below, the Hamming loss can be made to vanish with a very specific thresholding procedure.
+%
+%However, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and results on the former do not carry over directly to the study of the exact support recovery problem.
+%%More importantly, despite their elegance, these Hamming loss-minimax studies often amount to the analysis of the elementary case of iid data, and 
+%%unless is by design blind to non-trivial error-dependence structures.
+%%This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
+%More importantly, since the Hamming loss is the same for both independent and dependent data, aforementioned Hamming loss-minimax studies amounted to the analysis of the elementary case of iid data. 
+%This prevents one from fully exploring the phase transition phenomena under other dependence conditions.
+%
+%
+%% This is arguably a consequence of the inherent limitation of the Hamming-loss approach. 
+%% For practitioners, a minimax statement in the Gaussian case seems to offer little guidance.
+%% Indeed, in applications, independence is an exception rather than the rule; Gaussianity of the errors may also be unnecessarily restrictive.
+However, so far in the literature, the role of dependence, and that of the distributional assumptions in model \eqref{eq:model-additive} have remained largely unexplored. 
+This chapter offers advances in both directions, and provides a close-to-complete solution of the exact support recovery problem. (See also, Chapter \ref{chap:URS}.)
 We briefly summarize our contributions next.
@@
 \begin{equation} \label{eq:strong-classification-boundary}
-    g(\beta) = g_\nu(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu, \quad \nu>0,
+    f_{\mathrm{E}}(\beta) = f_{\mathrm{E},\nu}(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu, \quad \nu>0,
 \end{equation}
@@
 % under the general distributional assumptions in Section \ref{subsec:set-up}, 
-if the signal sizes are above the boundary (i.e., $\underline{r}> g(\beta)$), the \ac{FWER}-controlling procedures described in Section \ref{sec:statistical-procedures} with appropriately calibrated levels achieve \emph{exact support recovery} as in \eqref{eq:exact-recovery}.
+if the signal sizes are above the boundary (i.e., $\underline{r}> f_{\mathrm{E}}(\beta)$), the \ac{FWER}-controlling procedures described in Section \ref{sec:statistical-procedures} with appropriately calibrated levels achieve \emph{exact support recovery} as in \eqref{eq:exact-recovery}.
 
-Conversely, we show in Theorem \ref{thm:necessary}, that for a surprisingly large class of dependence structures characterized by the concept of \emph{uniform relative stability} (URS, see Definition \ref{def:URS} below), when the signal size is below the boundary  (i.e., $r<g(\beta)$), no thresholding procedure can achieve the asymptotically perfect support recovery \eqref{eq:exact-recovery}.
+Conversely, in Section \ref{subsec:necessary}, we show in Theorem \ref{thm:necessary} that for a surprisingly large class of dependence structures characterized by the concept of \emph{uniform relative stability} (URS, see Definition \ref{def:URS} below), when the signal size is below the boundary  (i.e., $r<f_{\mathrm{E}}(\beta)$), no thresholding procedure can achieve the asymptotically perfect support recovery \eqref{eq:exact-recovery}.
 In fact,
@@
 for all $\widehat{S}_p$ in the form of \eqref{eq:thresholding-procedure}.
+These two results show that the thresholding procedures obey a phase transition phenomenon in a strong, \emph{point-wise} sense over the class of URS dependence structures, and over the class of AGG$(\nu),\ \nu>0$ error distributions.
+%  A transparent characterizations of the dependence conditions under which this result holds will be established in the Chapter \ref{chap:URS} later.
 
-These two results show that the thresholding procedures obey a phase transition phenomenon in a strong, \emph{point-wise} sense over the class of URS dependence structures, and over the class of AGG$(\nu),\ \nu>0$ error distributions.
-The conclusions are fundamentally stronger and more informative than the minimax statements in the literature (see, e.g., \cite{butucea2018variable}).
-The techniques developed in this here are also entirely different from those in \citet{ji2012ups} or \citet{butucea2018variable}, and transparent characterizations of the dependence conditions under which the phase transition type result holds will be established in the Chapter \ref{chap:URS} later.
+%The conclusions are fundamentally stronger and more informative than the minimax statements in the literature (see, e.g., \cite{butucea2018variable}).
+%The techniques developed in this here are also entirely different from those in \citet{ji2012ups} or \citet{butucea2018variable}, and transparent characterizations of the dependence conditions under which the phase transition type result holds will be established in the Chapter \ref{chap:URS} later.
 
@@
 
-\medskip
-The phase transition phenomena for two additional classes of error distributions with either heavier or lighter tails than the AGG distributions will be described in Section \ref{suppsec:other-boundaries}.
-
-\medskip
-To conclude this summary, we emphasize that the sharp phase transition results established in this chapter apply only to
-the general class of thresholding procedures.  In Chapter \ref{chap:optimality}, we characterize the finite-sample Bayes optimal support estimation procedures.
-It will turn out that in many cases the optimal procedures are in fact thresholding procedures.  This will lead to complete phase transition
-results valid for all types of support estimators, for certain classes of error models. In general, however, thresholding procedures
-can be sub-optimal.  This has only recently been noticed by the statistical community in the case when the errors have heavy (regularly-varying) tails. 
-\citet{arias2019detection} discussed the phenomenon in approximate support recovery problems.  In this case, we also demonstrate the absence 
-of a phase transition phenomenon in exact support recovery by thresholding, in Section \ref{suppsec:heavy-tailed}.
+%\medskip
+%Our method of analysis is sufficiently general and can be applied to other error models. 
+%The phase transition phenomena for two additional classes of error distributions with either heavier or lighter tails than the AGG distributions will be described in Section \ref{suppsec:other-boundaries}.
 

### 2021-04-04 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
many changes... Chapter 4 intro WIP

@@
 Let also the errors have common $\text{AGG}(\nu)$ distribution $F$ with parameter $\nu>0$, and $\Theta_p^+$ be as defined in \eqref{eq:minimax-signal-config-over}.
-If $\underline{r}>g(\beta)$, then we have
+If $\underline{r}>f_{\mathrm{E}}(\beta)$, then we have
 \begin{equation} \label{eq:point-wise-minimax-above}
@@
 Let $\cal T$ be the class of thresholding procedures \eqref{eq:thresholding-procedure}. 
-If $\underline{r}<g(\beta)$, then we have
+If $\underline{r}<f_{\mathrm{E}}(\beta)$, then we have
 \begin{equation} \label{eq:point-wise-minimax-below}
@@
 
-For the second statement \eqref{eq:point-wise-minimax-below}, since $\underline{r}<g(\beta)$, we can pick a sequence $\mu^*\in\Theta_p^+(\beta, \underline{r})$ such that $|S_p| = \lfloor p^{1-\beta}\rfloor$, with signals having the same signal size $\mu(i)=(2r\log{p})^{1/\nu}$ for all $i\in S_p$, where $\underline{r}<{r}<g(\beta)$.
-For this particular choice of $\mu^*$ we have $\mu^*\in\Theta_p^-(\beta, \overline{r})$ where $r<\overline{r}<g(\beta)$,
+For the second statement \eqref{eq:point-wise-minimax-below}, since $\underline{r}<f_{\mathrm{E}}(\beta)$, we can pick a sequence $\mu^*\in\Theta_p^+(\beta, \underline{r})$ such that $|S_p| = \lfloor p^{1-\beta}\rfloor$, with signals having the same signal size $\mu(i)=(2r\log{p})^{1/\nu}$ for all $i\in S_p$, where $\underline{r}<{r}<f_{\mathrm{E}}(\beta)$.
+For this particular choice of $\mu^*$ we have $\mu^*\in\Theta_p^-(\beta, \overline{r})$ where $r<\overline{r}<f_{\mathrm{E}}(\beta)$,
 and according to Theorem \ref{thm:necessary}, we obtain $\lim_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \mathbb P[\widehat{S}_p \neq S_p] = 1$, for all dependence structures in the URS class.
@@
 If the signal sizes fall below the strong classification boundary \eqref{eq:strong-classification-boundary}, 
-i.e. $\overline{r}<g(\beta)$, then we have
+i.e. $\overline{r}<f_{\mathrm{E}}(\beta)$, then we have
 \begin{equation} \label{eq:classification-impossible-Bayes}
@@
 \end{align*}
-when $\overline{r}<g(\beta)$, where the last line follows from Theorem \ref{thm:necessary}.
+when $\overline{r}<f_{\mathrm{E}}(\beta)$, where the last line follows from Theorem \ref{thm:necessary}.
 \end{proof}
@@
 Let also $\widehat{S}^{\text{Bonf}}_p$ be Bonferroni's procedure as described in Theorem \ref{thm:sufficient}.
-If $\underline{r}>g(\beta)$, then we have
+If $\underline{r}>f_{\mathrm{E}}(\beta)$, then we have
 \begin{equation} \label{eq:minimax-over-dependence-over}
@@
 \end{equation}
-Further, when $\underline{r}<g(\beta)$, and $F$ has a positive log-concave density $f$, we have
+Further, when $\underline{r}<f_{\mathrm{E}}(\beta)$, and $F$ has a positive log-concave density $f$, we have
 \begin{equation} \label{eq:minimax-over-dependence-under}
@@
     \{\mu\in\mathbb{R}^d:\;|S_p|=\lfloor p^{1-\beta}\rfloor,\;\mu(i)=0\;\text{for all }i\not\in S, \;\text{and}\\
-    &\quad\quad\mu(i) = (\nu{r}\log{p})^{1/\nu}\;\text{for all }i\in S,\;\text{where}\;\underline{r}<r<g(\beta)\},
+    &\quad\quad\mu(i) = (\nu{r}\log{p})^{1/\nu}\;\text{for all }i\in S,\;\text{where}\;\underline{r}<r<f_{\mathrm{E}}(\beta)\},
 \end{align*}

### 2021-04-04 7.GWAS/7.chi-square.tex
many changes... Chapter 4 intro WIP

@@
 \begin{equation} \label{eq:exact-boundary-chisquared}
-    g(\beta) = \left(1 + \sqrt{1-\beta}\right)^2
+    f_{\mathrm{E}}(\beta) = \left(1 + \sqrt{1-\beta}\right)^2
 \end{equation}
@@
 
-{\rm (i)} If $\underline{r} > {{g}}(\beta)$, then Bonferroni's, Sid\'ak's, Holm's, and Hochberg's procedures with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FWER levels all achieve asymptotically exact support recovery in the sense of \eqref{eq:support-recovery-success}.\\
+{\rm (i)} If $\underline{r} > f_{\mathrm{E}}(\beta)$, then Bonferroni's, Sid\'ak's, Holm's, and Hochberg's procedures with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FWER levels all achieve asymptotically exact support recovery in the sense of \eqref{eq:support-recovery-success}.\\
 
-{\rm (ii)} Conversely, if $\overline{r} < {{g}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, we have $\P[\widehat{S}_p=S_p]\to0$.
+{\rm (ii)} Conversely, if $\overline{r} < f_{\mathrm{E}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, we have $\P[\widehat{S}_p=S_p]\to0$.
 Therefore, in view of Lemma \ref{lemma:risk-exact-recovery-probability}, exact support recovery asymptotically fails for all thresholding procedures in the sense of \eqref{eq:support-recovery-failure}.
@@
 \begin{equation} \label{eq:exact-approx-boundary-chisquared}
-    \widetilde{g}(\beta) = 1
+    f_{\mathrm{EA}}(\beta) = 1
 \end{equation}
@@
 
-{\rm (i)} If $\underline{r} > \widetilde{g}(\beta)$, then the procedures listed in Theorem \ref{thm:chi-squared-exact-boundary} with slowly 
+{\rm (i)} If $\underline{r} > f_{\mathrm{EA}}(\beta)$, then the procedures listed in Theorem \ref{thm:chi-squared-exact-boundary} with slowly 
 vanishing nominal FWER levels achieve asymptotically exact-approximate support recovery in the sense of \eqref{eq:support-recovery-success}. \\
 
-{\rm (ii)} Conversely, if $\overline{r} < \widetilde{g}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, the exact-approximate support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
+{\rm (ii)} Conversely, if $\overline{r} < f_{\mathrm{EA}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, the exact-approximate support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
 \end{theorem}
@@
 \begin{equation} \label{eq:approx-boundary-chisquared}
-    h(\beta) = \beta
+    f_{\mathrm{A}}(\beta) = \beta
 \end{equation}
@@
 
-{\rm (i)} If $\underline{r} > {h}(\beta)$, then the \ac{BH} procedure $\widehat{S}_p$ (defined in Section \ref{sec:statistical-procedures}) with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FDR levels achieves asymptotically approximate support recovery in the sense of \eqref{eq:support-recovery-success}.
+{\rm (i)} If $\underline{r} > f_{\mathrm{A}}(\beta)$, then the \ac{BH} procedure $\widehat{S}_p$ (defined in Section \ref{sec:statistical-procedures}) with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FDR levels achieves asymptotically approximate support recovery in the sense of \eqref{eq:support-recovery-success}.
 \\
 
-{\rm (ii)} Conversely, if $\overline{r} < {h}(\beta)$, then approximate support recovery asymptotically fails in the sense of \eqref{eq:support-recovery-failure} for all thresholding procedures.
+{\rm (ii)} Conversely, if $\overline{r} < f_{\mathrm{A}}(\beta)$, then approximate support recovery asymptotically fails in the sense of \eqref{eq:support-recovery-failure} for all thresholding procedures.
 \end{theorem}
@@
 \begin{equation} \label{eq:approx-exact-boundary-chisquared}
-    \widetilde{h}(\beta) = \left(\sqrt{\beta} + \sqrt{1-\beta}\right)^2
+    f_{\mathrm{AE}}(\beta) = \left(\sqrt{\beta} + \sqrt{1-\beta}\right)^2
 \end{equation}
@@
 
-{\rm (i)} If $\underline{r} > \widetilde{h}(\beta)$, then the Benjamini-Hochberg procedure with slowly vanishing nominal FDR levels achieves asymptotically approximate-exact support recovery in the sense of \eqref{eq:support-recovery-success}.
+{\rm (i)} If $\underline{r} > f_{\mathrm{AE}}(\beta)$, then the Benjamini-Hochberg procedure with slowly vanishing nominal FDR levels achieves asymptotically approximate-exact support recovery in the sense of \eqref{eq:support-recovery-success}.
 \\
 
-{\rm (ii)} Conversely, if $\overline{r} < \widetilde{h}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, the approximate-exact support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
+{\rm (ii)} Conversely, if $\overline{r} < f_{\mathrm{AE}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, the approximate-exact support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
 \end{theorem}

### 2021-04-04 7.GWAS/7.numerical.tex
many changes... Chapter 4 intro WIP

@@
 We illustrate with simulations the phase transition phenomena in the chi-square model, and compare numerically the required signal sizes in support recovery problems between the two types of alternatives in the additive error model.
-\stilian{These results can provide further guidance to practitioners on when to expect genetic association discoveries.
-They provide also an explanation of the empirically observed phenomenon known as steep part of the power curve
-in statistical genetics \citep{bush2012genome}. }{\fbox{IS this the RIGHT reference?  I could not find the ``steep part of the power curve" anywhere.}}
+% These results can provide further guidance to practitioners on when to expect genetic association discoveries. 
 % We also demonstrate the fundamental trade-off between odds ratios and relative frequencies in association studies, as outlined in Proposition \ref{prop:signal-size-odds-ratio} and Corollary \ref{cor:signal-size-odds-ratio-conditional-frequency}, using evidence from large-scale genetic studies.

### 2021-04-04 7.GWAS/7.odds-and-power.tex
many changes... Chapter 4 intro WIP

--- 2021-02-04 6.GWAS/6.odds-and-power.tex
@@
 
-In order to do so, we must first connect the concept of ``statistical signal size'' $\lambda$ with some key quantities in association tests.
-While ``signal size'' likely sounds foreign to most practitioners, it is intimately linked with the concept of ``effect sizes'' --- or odds ratios --- in association studies, which are frequently estimated and reported in GWAS catalogs.
-We characterize the relationship between the two quantities in the special, but fairly common case of association tests on 2-by-2 contingency tables in Section \ref{sec:odds-and-power}.
+In order to do so, we must first connect the concept of statistical signal size $\lambda$ with some key quantities in association tests.
+While the term ``signal size'' likely sounds foreign to most practitioners, it is intimately linked with the concept of ``effect sizes'' --- or odds ratios --- in association studies, which are frequently estimated and reported in GWAS catalogs.
+Effect sizes, on the other hand, may be alien to some statisticians.  
+In this section, we aim to bridge the two languages by characterizing the relationship between ``signal size'' and ``odds-ratio'' parameterizations in the special, but fairly common case of association tests on 2-by-2 contingency tables.
+
+ %in Section \ref{sec:odds-and-power}.
 
@@
 
+Recall the general setup of genetic association testing in Section \ref{sec:motivation-chisq}, where one wants to detect the association between genetic variations at a specific location and the occurrence of a disease.
+An individual randomly drawn from the target population will have two (random) characteristics: a phenotype indicating whether the individual has the condition or is healthy (i.e., belonging to the Case group or the Control group), and a genotype that encodes the genetic variation in question.
+Table \ref{tab:multinomial-counts} in the introduction summarizes the {\em counts} for all phenotype-genotype combinations for the individuals in a given study sampled from the population.
+These counts may be assumed to follow a multinomial distribution, with probabilities given in Table \ref{tab:multinomial-probabilites} below. 
+% Notice that there are fundamental study design questions here since the counts will depend on the way individuals are recruited in the study. 
+% For example, ``controlling'' the number of Cases or Controls (as opposed to sampling at random from the population) will change the theoretical parameters (probabilities) of the multinomial model.
+% These questions will be addressed in Section \ref{sec:optimal-design} below.
+
 Consider a 2-by-2 multinomial distribution with marginal probabilities of phenotypes $(\phi_1, \phi_2)$ and genotypes $(\theta_1, \theta_2)$.
 The \emph{probability} table (as opposed to the table of multinomial \emph{counts} in the introduction) is as follows.
+\begin{table}[h]\label{tab:multinomial-probabilites}
 \begin{center}

### 2021-04-04 7.GWAS/GWAS.tex
many changes... Chapter 4 intro WIP

@@
-The process of scientific discovery, as famously explained by Richard Feynman, usually starts with guesses in one form or another.
-The consequences of such guesses are then computed, and compared with experimental results.
-If the predictions disagree with the experiment, then our guesses are wrong. ``That is all there is to it''  \citep{feynman2017character}.
+The process of scientific discovery, as explained by Richard Feynman, usually starts with guesses.
+The consequences of such guesses are then computed and compared with experimental results.
+If the predictions disagree with the experiment then our guesses are wrong. ``That is all there is to it''  \citep{feynman2017character}.
 
@@
 In this chapter, our goal is to relate these predictions to real experimental data from the field of genetics, where large-scale simultaneous hypotheses testing problems often arise.
-From such comparisons, we will demonstrate that the phase transition laws are indeed accurate predictions of some curious phenomena in the real world.
-The accuracy of our predictions will lend credibility to the application of these ``laws of large dimensions'' in actual statistical problems.
+From such comparisons, we will demonstrate that the phase transition laws are indeed reasonable predictions of some curious phenomena in that field.
+The accuracy of our predictions will lend credibility to the application of these ``laws of large dimensions'' in actual applications.
 
@@
 
-We then translate the canonical signal size and sparsity parametrizations into the vernacular of statistical geneticists in Section \ref{sec:odds-and-power}.
+In the second step, we translate the canonical signal size and sparsity parametrizations into the vernacular of statistical geneticists in Section \ref{sec:odds-and-power}.
 % present empirical evidence for the phase transition in the exact-approximate problem using real data from large-scale association studies on breast cancer obtained from the NHGRI-EBI GWAS Catalog \citep{macarthur2016new}.
@@
 We do so by characterizing the relationship between the signal size $\lambda$ and the marginal frequencies, odds ratio, and sample sizes for association tests on 2-by-2 contingency tables. 
-These parameters are more often estimated and reported in \ac{GWAS} than the elusive signal size parameter $\lambda$.
+This is important because these parameters are often estimated and reported in \ac{GWAS}, while we have never seen the elusive signal size parameter $\lambda$ reported.
 % Specifically, the amount of signal, when rare variants are present, is weaker compared to the signal when the marginal distributions are balanced.
@@
 % This result, establishing the relationship between sample sizes and signal sizes, is made precise in Section \ref{sec:odds-and-power}.
-As a bonus, we point out the implications of this relationship on statistically optimal study designs for association studies in Section \ref{sec:optimal-design}.
-Perhaps surprisingly, our analysis reveals that balanced designs with equal number of cases and controls are often statistically inefficient.
+As a bonus, we point out the implications of this relationship on statistically optimal study designs for association studies in Section \ref{sec:optimal-design}:
+perhaps surprisingly, balanced designs with equal number of cases and controls are often statistically inefficient.
 % Practical consequences of these results in power analysis will be illustrated with data examples in Section \ref{sec:phase-transitions-in-GWAS}.
 
-Armed with the results on phase transitions in the chi-square model, and a translation from the language of high-dimenstional statistics to the {\em patois} of association screening studies, we finally present in Section \ref{sec:phase-transitions-in-GWAS} the consequences of the phase transitions in \ac{GWAS}, and compare against real experimental data to evaluate the success of our predictions.
+Armed with the results on phase transitions in the chi-square model, and a translation from the language of high-dimenstional statistics to the patois of association screening studies, we finally present in Section \ref{sec:phase-transitions-in-GWAS} the consequences of the phase transitions in \ac{GWAS}, and compare against real experimental data to evaluate the success of our predictions.
 
 The phase transitions in the chi-square models are demonstrated with numerical simulations in Section \ref{sec:numerical}.
-The proofs, which are closely related to those of the results in Chapter \ref{chap:phase-transitions},
- are collected in Section \ref{sec:supplement:proofs}.
+The proofs, which are closely resemble those of the results in Chapter \ref{chap:phase-transitions}, are collected in Section \ref{sec:supplement:proofs}.
 %in Section \ref{sec:proof-signal-size-odds-ratio}.

### 2021-04-04 supplement/other-boundaries.tex
many changes... Chapter 4 intro WIP

@@
 \begin{equation}\label{eq:altenative-parametrization}
-g(\beta) = \widetilde{g}(\widetilde{\beta}) = 2 - \widetilde{\beta}.
+f_{\mathrm{E}}(\beta) = \widetilde{f}_{\mathrm{E}}(\widetilde{\beta}) = 2 - \widetilde{\beta}.
 \end{equation}
@@
 \overline{\Delta} = \exp{\left\{(\log{p})^{1/\gamma}\right\}}\overline{r}.$$
-If $\underline{r} > \widetilde{g}(\beta) = 2 - \beta$, then Bonferroni's procedure $\widehat{S}_p$ (defined in \eqref{eq:Bonferroni-procedure}) with appropriately calibrated FWER $\alpha\to 0$ achieves asymptotic perfect support recovery, under arbitrary dependence of the errors.
+If $\underline{r} > \widetilde{f}_{\mathrm{E}}(\beta) = 2 - \beta$, then Bonferroni's procedure $\widehat{S}_p$ (defined in \eqref{eq:Bonferroni-procedure}) with appropriately calibrated FWER $\alpha\to 0$ achieves asymptotic perfect support recovery, under arbitrary dependence of the errors.
 
-On the other hand, when the errors are uniformly relatively stable, if $\overline{r} < \widetilde{g}(\beta) = 2 - \beta$, then no thresholding procedure can achieve asymptotic perfect support recovery with positive probability.
+On the other hand, when the errors are uniformly relatively stable, if $\overline{r} < \widetilde{f}_{\mathrm{E}}(\beta) = 2 - \beta$, then no thresholding procedure can achieve asymptotic perfect support recovery with positive probability.
 \end{theorem}
@@
 \overline{\Delta} = \log{\log{p}}^{1/\nu}\overline{r}.$$
-If $\underline{r} > \widetilde{g}(\beta) = 2 - \beta$, then Bonferroni's procedure $\widehat{S}_p$ (defined in \eqref{eq:Bonferroni-procedure}) with appropriately calibrated FWER $\alpha\to 0$ achieves asymptotic perfect support recovery, under arbitrary dependence of the errors.
+If $\underline{r} > \widetilde{f}_{\mathrm{E}}(\beta) = 2 - \beta$, then Bonferroni's procedure $\widehat{S}_p$ (defined in \eqref{eq:Bonferroni-procedure}) with appropriately calibrated FWER $\alpha\to 0$ achieves asymptotic perfect support recovery, under arbitrary dependence of the errors.
 
-On the other hand, when the errors are uniformly relatively stable, if $\overline{r} < \widetilde{g}(\beta) = 2 - \beta$, then no thresholding procedure can achieve asymptotic perfect support recovery with positive probability.
+On the other hand, when the errors are uniformly relatively stable, if $\overline{r} < \widetilde{f}_{\mathrm{E}}(\beta) = 2 - \beta$, then no thresholding procedure can achieve asymptotic perfect support recovery with positive probability.
 \end{theorem}

### 2021-04-04 supplement/proofs-GWAS.tex
rename files and folders according to the new structure
many changes... Chapter 4 intro WIP

--- 2021-02-04 6.GWAS/6.proofs-GWAS.tex
@@
 \label{sec:chi-square-distributions}
-\input{6.GWAS/6.chi-square-distributions.tex}
+\input{./supplement/chi-square-distributions.tex}
 
@@
 
-The condition $\underline{r} > {{g}}(\beta)$ implies, after some algebraic manipulation,
+The condition $\underline{r} > f_{\mathrm{E}}(\beta)$ implies, after some algebraic manipulation,
 $\sqrt{\underline{r}} -\sqrt{1-\beta} > 1$.
@@
 One could in principle obtain the proofs in this section by referencing arguments that have appeared in Chapter \ref{chap:phase-transitions}.
-We choose to present the proof here in full to make this section self-contained.
+We choose to present the proof here in full for completeness.
 
@@
 
-As with the proof of Theorem \ref{thm:chi-squared-approx-boundary}, one could shorten the presentations in this section by 
-referencing arguments in Chapter \ref{chap:phase-transitions}.  Again, we choose to present the proof in full to make this section 
-self-contained.
+As with the proof of Theorem \ref{thm:chi-squared-approx-boundary}, one could shorten the presentations in this section by referencing arguments in Chapter \ref{chap:phase-transitions}.  
+%Again, we choose to present the proof in full to make this section self-contained.
 
@@
 
-Since $\underline{r}>\widetilde{g}(\beta)=1$, we can pick $q$ such that $1<q<\underline{r}$.
+Since $\underline{r}>f_{\mathrm{EA}}(\beta)=1$, we can pick $q$ such that $1<q<\underline{r}$.
 Let $t^* = 2q\log{p}$, we have $t_p<t_p^*$ for large $p$ as in the proof of Theorem \ref{thm:chi-squared-exact-boundary}.
@@
 which holds for any thresholding procedure $\mathcal{R}$ and for arbitrary $u\in\R$.
-By the assumption that $\overline{r}<\widetilde{g}(\beta)=1$, we can pick $q$ such that $\overline{r}<q<1$ and let $u = t^*=2q\log{p}$.
+By the assumption that $\overline{r}<f_{\mathrm{EA}}(\beta)=1$, we can pick $q$ such that $\overline{r}<q<1$ and let $u = t^*=2q\log{p}$.
 By relative stability of chi-squared random variables (Lemma \ref{lemma:rapid-variation-chisq}), we have
@@
 
-By the assumption that $\underline{r}>\widetilde{h}(\beta)=(\sqrt{\beta}+\sqrt{1-\beta})^2$, we have $\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{\beta}$, so we can pick $q>0$, such that 
+By the assumption that $\underline{r}>f_{\mathrm{AE}}(\beta)=(\sqrt{\beta}+\sqrt{1-\beta})^2$, we have $\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{\beta}$, so we can pick $q>0$, such that 
 \begin{equation} \label{eq:approx-exact-boundary-proof-sufficient-2}
@@
 
-By the assumption that $\overline{r}<\widetilde{h}(\beta)=(\sqrt{\beta}+\sqrt{1-\beta})^2$, we can pick a constant $q>0$, such that 
+By the assumption that $\overline{r}<f_{\mathrm{AE}}(\beta)=(\sqrt{\beta}+\sqrt{1-\beta})^2$, we can pick a constant $q>0$, such that 
 \begin{equation} \label{eq:approx-exact-boundary-proof-necessary-2}

### 2021-04-04 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
update chapter 4 intro; update response to R4 minor comments

@@
 In studying support recovery problems, restrictions to the thresholding procedures 
-are sometimes justified by arguing that such procedures are the ``reasonable'' choice for estimating the support set \citep[e.g.,][]{arias2017distribution}.
+are sometimes justified by arguing that such procedures are the ``reasonable'' choice for estimating the support set \citep[see, e.g.,][]{arias2017distribution}.
 We show in this chapter that, perhaps surprisingly, for general error models, thresholding procedures are not always 
@@
 
-\begin{remark}[{\bf An open problem\!}\,] As we have seen, the thresholding estimators are no longer optimal 
+\begin{remark} As we have seen, the thresholding estimators are no longer optimal 
 in the additive model with error-densities heavier than exponential.   Thanks to Theorem 

### 2021-04-04 7.GWAS/GWAS.tex
update chapter 4 intro; update response to R4 minor comments

@@
 The results are interesting in their own right.
-However, in the spirit of Feynman, we have not discovered any scientific law, but merely worked out mathematical consequences of our postulated models.
+However, we have not discovered any scientific law in the spirit of Feynman, but merely worked out mathematical consequences of our postulated models.
 In this chapter, our goal is to relate these predictions to real experimental data from the field of genetics, where large-scale simultaneous hypotheses testing problems often arise.

### 2021-04-04 6.URS/URS.tex
rename files and folders according to the new structure
minor updates to Chapter 5 intro

--- 2021-02-03 5.URS/URS.tex
@@
-Recall that the notion of uniform relative stability (URS) in Definition \ref{def:URS} is the key to the necessary conditions for exact support recovery 
-established in Theorem \ref{thm:necessary}.
+The notion of uniform relative stability (URS) in Definition \ref{def:URS} is the key to the necessary conditions for exact support recovery established in Theorem \ref{thm:necessary}.
 In this chapter, we provide a complete characterization of the class of URS Gaussian arrays in terms of a simple condition on their covariance structure.
@@
 \label{sec:Ramsey}
-\input{5.URS/5.proofs-Ramsey.tex}
+\input{6.URS/6.proofs-Ramsey.tex}
 
@@
 \label{sec:URS=>UDD}
-\input{5.URS/5.proofs-URS-UDD.tex}
+\input{6.URS/6.proofs-URS-UDD.tex}
 
@@
 \label{sec:UDD=>URS}
-\input{5.URS/5.proofs-UDD-URS.tex}
+\input{6.URS/6.proofs-UDD-URS.tex}
 
@@
 \label{sec:URS-numerical}
-\input{5.URS/5.numerical.tex}
+\input{6.URS/6.numerical.tex}

### 2021-04-05 1.intro/introduction.tex
2 more major questions
Pages 5, 25, 47 in the PDF.

The biggest question is if we can relax the parameterization of the support size...

@@
 Focusing on one specific genomic location, the counts of observed genotypes, if two variants are present, can be tabulated as follows.
-% \begin{table}[ht]
-% \centering
+ \begin{table}[ht] \label{tab:multinomial-counts}
+ \centering
 \begin{center}
@@
     \end{tabular}
-    % \caption{Tabulated counts of genotype-phenotype combinations in a genetic association test.}
+     \caption{Tabulated counts of genotype-phenotype combinations in a genetic association test.}
 \end{center}
-% \end{table}
+\end{table}
 Researchers test for associations between the genotypes and phenotypes using, for example, the Pearson chi-square test with statistic
@@
 Both the Gaussianity assumption and the independence assumption are relaxed in Chapter \ref{chap:exact-support-recovery}.
-Established are the necessary and sufficient conditions for exact support recovery in the high-dimensional asymptotic regime.
+Established are the necessary and sufficient conditions for exact support recovery in the high-dimensional asymptotic regime 
+\stilian{for the large class of thresholding procedures.}{}
 This is a major theoretical contribution of our approach, which solves and expands on open problems in the recent literature 
@@
 The latter concept is key to understanding the role played by dependence in the phase transition phenomena of high-dimensional testing problems.
-Using this probabilistic concept, we establish minimax optimality results that hold for a very large class of dependence structures.
+\stilian{
+In Chapter \ref{chap:optimality} we study the universality of the phase-transition phenomenon in exact support recovery.  We do so by first 
+establishing the finite-sample Bayes optimality and sub-optimality of thresholding procedures.
+This, combined with the results from Chapter \ref{chap:exact-support-recovery}, culminates in asymptotic minimax characterizations of the phase transition phenomenon in exact
+support recovery across all procedures and/or for large class of dependence structures.}{}
 

### 2021-04-05 2.background/2.Gaussian-distributions.tex
2 more major questions
Pages 5, 25, 47 in the PDF.

The biggest question is if we can relax the parameterization of the support size...

@@
 {\bf Relative stability.} We first state the relative stability of iid standard Gaussian random variables.  Since the standard Gaussian distribution falls in the 
-class of asymptotically generalized Gaussians (AGG; see Definition \ref{def:AGG}), by Example \ref{exmp:AGG}, we know that the triangular array ${\cal E} = \{\left(\epsilon_p(i)\right)_{i=1}^p, p\in\N\}$ has relatively stable (RS) maxima in the sense of \eqref{eq:RS-condition}, i.e.,
+class of asymptotically generalized Gaussians (AGG; see Definition \ref{def:AGG}), by Example \ref{exmp:AGG}, we know that the triangular array ${\cal E} = \{(\epsilon_p(i))_{i=1}^p, p\in\N\}$ has relatively stable (RS) maxima in the sense of \eqref{eq:RS-condition}, i.e.,
 \begin{equation} \label{eq:relative-stability-Gaussian-maxima}
@@
 \end{theorem}
+
+With these conceptual and technical preparations, we are ready to discuss the high-dimensional signal detection and support recovery problems in the next chapter.

### 2021-04-05 2.background/2.asymptotics.tex
2 more major questions
Pages 5, 25, 47 in the PDF.

The biggest question is if we can relax the parameterization of the support size...

@@
 Recent studies have also focused on the behavior of detection risk \eqref{eq:risk-detection} in dense and scale mixture models \cite{cai2011optimal}, under general distributional assumptions \citep{cai2014optimal, arias2017distribution1}, as well as when the errors are dependent \citep{hall2010innovated}.
-A comprehensive review focusing on the role of \ac{HC} in detection problems can be found in \cite{donoho2015special}.
+A comprehensive review focusing on the role of \ac{HC} in detection problems can be found in \cite{donoho2015special}. The very recent 
+contribution of \cite{li2020optimality} shows exciting new developments on the detection problem in a more realistic regime than the ones previously studied 
+in the literature.  It shows that the max statistic begins to attain the optimal boundary and is on par with \ac{HC} (cf Table 1, therein). 
 Notwithstanding the extensive literature on the detection problem, the performances of simple statistics such as 
@@
 Furthermore, a phase-transition in the exact support recovery problem for thresholding procedures is established under broad dependence conditions on the errors using the concentration of maxima phenomenon (Chapter \ref{chap:exact-support-recovery}).
-We also establish finite-sample Bayes optimality and sub-optimality results for these procedures under independence, and by extension, arrive at minimax optimality results for the exact support recovery problem.
+We also establish finite-sample Bayes optimality and sub-optimality results for these procedures under independence, and by extension, arrive at minimax optimality results for the exact support recovery problem (Chapter \ref{chap:optimality}).
 
@@
 \cite{arias2017distribution} showed that a phase transition exists for  the approximate support recovery risk \eqref{eq:risk-approximate}.
-The \ac{BH} procedure \cite{benjamini1995controlling}, and the Barber-Cand\`es procedure \citep{barber2015controlling} was identified to be asymptotically optimal.
+The \ac{BH} procedure \citep{benjamini1995controlling}, and the Barber-Cand\`es procedure \citep{barber2015controlling} were identified to be asymptotically optimal.
 % \citet{rabinovich2017optimal} further established the rate-optimality of both procedures under the same regime.

### 2021-04-05 3.phase_transitions/3.global-tests.tex
2 more major questions
Pages 5, 25, 47 in the PDF.

The biggest question is if we can relax the parameterization of the support size...

@@
 
-To the best of our knowledge, performance of simple statistics such as $L_1$, $L_2$ norms, and 
+To the best of our knowledge, the performance of simple statistics such as $L_1$, $L_2$ norms, and 
 the sum statistic $T$ in \eqref{eq:sum-statistic} in this weak signal setting have not been reported in the literature. %perhaps due to a perceived lack of novelty. 

### 2021-04-05 3.phase_transitions/phase_transitions.tex
2 more major questions
Pages 5, 25, 47 in the PDF.

The biggest question is if we can relax the parameterization of the support size...

--- 2021-02-01 3.phase_transitions/phase_transitions.tex
@@
 \begin{equation} \label{eq:signal-sparsity-additive}
-    |S_p| = \left\lfloor p^{1-\beta} \right\rfloor, \quad \beta\in(0,1],
+   \stilian{|S_p| \sim p^{1-\beta} }{\mbox{instead of $= \left\lfloor p^{1-\beta} \right\rfloor$ \fbox{CAN WE DO THAT?}}}, \quad \beta\in(0,1],
 \end{equation}
-where $\beta$ parametrizes the problem sparsity.
+where $\beta$ parametrizes the problem sparsity\stilian{, and $\sim$ stands for asymptotic equivalence, i.e., $a_p\sim b_p$ if $a_p/b_p\to 1$, as $p\to\infty$.}{}
 The closer $\beta$ is to 1, the sparser the support $S_p$.  
@@
 
+It should be noted that the ``classical'' setting where all signals are of equal size is not the only one that have been studied. 
+The recent contribution of \cite{li2020optimality} investigates the signal detection problem in a more realistic setting where the signals are drawn from a general and potentially polynomial-tailed distribution.
+The study of such general settings in both detection and support recovery problems is an interesting new direction of research.
+
 \section{Sparse signal detection problems}

### 2021-04-05 4.exact_support_recovery/exact_support_recovery.tex
2 more major questions
Pages 5, 25, 47 in the PDF.

The biggest question is if we can relax the parameterization of the support size...

@@
 %Questions on optimality and extensions to other classes of estimators are pursued in Chapter \ref{chap:optimality}.  
-As in Theorem \ref{thm:Gaussian-error-exact-boundary}, in order to study the asymptotic behaviors of $\mathrm{risk}^{\mathrm{E}}$, it is sufficient to establish minimal conditions under which the support sets can be consistently estimated, i.e.,
+Recall from Lemma \ref{lemma:risk-exact-recovery-probability} that in order to study the asymptotic behaviors of $\mathrm{risk}^{\mathrm{E}}$, it is sufficient to establish minimal conditions under which the support sets can be consistently estimated, i.e.,
 \begin{equation} \label{eq:exact-recovery} 
@@
 \end{equation}
-where $\widehat{S}_p$ is an estimate of the true support set $S_p$ of a high-dimensional signal vector $\mu_p$ (recall Lemma \ref{lemma:risk-exact-recovery-probability}).
+where $\widehat{S}_p$ is an estimate of the true support set $S_p$ of a high-dimensional signal vector $\mu_p$.
 
-To generalize the results we obtained in Chapter \ref{chap:phase-transitions} to additive error models with relaxed distributional and dependence assumptions on the additive error array, described next.
+We will establish minimal conditions such that \eqref{eq:exact-recovery} holds, by generalizing the results we obtained in Chapter \ref{chap:phase-transitions} to additive error models with relaxed distributional and dependence assumptions on the additive error array.
 
@@
 
-This generalized distributional assumption on the error terms call for a suitable change to parametrization of the signal sizes in order to analyze the problem.
-As in Chapter \ref{chap:phase-transitions}, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector $\mu = \left(\mu(i)\right)_{i=1}^p$ where its sparsity, with a few exceptions which will be explicitly stated, is parametrized as
+This generalized distributional assumption on the errors call for a suitable generalization of the signal size parametrization in order to analyze the problem as we did in the previous chapter.
+As before, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector $\mu = \left(\mu(i)\right)_{i=1}^p$ where its sparsity, with a few exceptions which will be explicitly stated, is parametrized as
 \begin{equation} \label{eq:sparsity-parametrized}
@@
 
+ \stilian{\begin{remark}Without much effort, one can relax the above parameterization of the support size in \eqref{eq:sparsity-parametrized} to $|S_p| \sim p^{1-\beta}$ or in fact, to the 
+much more general case of $|S_p|\sim L(p) p^{1-\beta}$, for a slowly varying function $L$.  Going along this path would would naturally lead to
+more sophisticated signal models, which merit independent study.  Here, we opt for simplicity of exposition and thus adopt 
+\eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized}.\end{remark}}
+
 \medskip
 
-Dependence conditions are also relaxed.
+We now turn to the dependence conditions.
 Several authors have studied the support recovery problem in terms of the Hamming loss and obtained minimax optimality results (see, e.g., \cite{ji2012ups, genovese2012comparison, jin2014optimality, butucea2018variable}).
 %% We briefly review the recent work by \cite{butucea2018variable}, whose .
-%In the special case of Gaussian marginals, \cite{butucea2018variable} showed that the boundary \eqref{eq:strong-classification-boundary-Gaussian} exists in a minimax sense.
-%That is, when the errors are \emph{independent} Gaussians, the Hamming loss cannot be made to vanish if the signal sizes are sufficiently small by any procedure. 
-%Conversely, if signal size falls below, the Hamming loss can be made to vanish with a very specific thresholding procedure.
+In the special case of Gaussian marginals, \cite{butucea2018variable} showed that the boundary \eqref{eq:strong-classification-boundary-Gaussian} exists in a minimax sense.
+That is, when the errors are \emph{independent} Gaussians, the Hamming loss cannot be made to vanish if the signal sizes are sufficiently small by any procedure. 
+Conversely, if signal size falls below, the Hamming loss can be made to vanish for some thresholding procedure.
 %
-%However, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and results on the former do not carry over directly to the study of the exact support recovery problem.
+However, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and results on the former do not carry over directly to the study of the exact support recovery problem.
 %%More importantly, despite their elegance, these Hamming loss-minimax studies often amount to the analysis of the elementary case of iid data, and 
@@
 %%This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
-%More importantly, since the Hamming loss is the same for both independent and dependent data, aforementioned Hamming loss-minimax studies amounted to the analysis of the elementary case of iid data. 
-%This prevents one from fully exploring the phase transition phenomena under other dependence conditions.
-%
-%
+More importantly, since Hamming loss decomposes into expectations on individual terms that are not affected by dependence, Hamming loss-minimax studies do not reveal the difference in probability of support recovery between independent and dependent observations.
+This prevents one from fully exploring the phase transition phenomena under other dependence conditions.
 %% This is arguably a consequence of the inherent limitation of the Hamming-loss approach. 
@@
 %% Indeed, in applications, independence is an exception rather than the rule; Gaussianity of the errors may also be unnecessarily restrictive.
-However, so far in the literature, the role of dependence, and that of the distributional assumptions in model \eqref{eq:model-additive} have remained largely unexplored. 
-This chapter offers advances in both directions, and provides a close-to-complete solution of the exact support recovery problem. (See also, Chapter \ref{chap:URS}.)
-We briefly summarize our contributions next.
+As a result, so far in the literature, the role of dependence in model \eqref{eq:model-additive} have remained largely unexplored. 
+%This chapter offers an advances in this direction, and provides a close-to-complete solution of the exact support recovery problem. (See also, Chapter \ref{chap:URS}.)
+%We briefly summarize our contributions next.
 
-\medskip
-In Section \ref{subsec:sufficient}, we study exact support recovery in the sense of \eqref{eq:exact-recovery} directly, under general 
-distributional and dependence assumptions.
-In particular, we describe the phase transition phenomena in the dependent AGG model, under the scaling described in \eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized}.
-Consider the function
+We take a different approach in this text. 
+In particular, we study the exact support recovery problem \eqref{eq:exact-recovery} directly, and show that for thresholding procedures the phase transition phenomena exists {universally} in a large class of dependence structures, and not just in a minimax sense.
+
+In a first step, we show that in the AGG model under \emph{arbitrary} dependence, under the scaling described in \eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized}, the function
 \begin{equation} \label{eq:strong-classification-boundary}
@@
 \end{equation}
-which we refer to as the {\em strong classification boundary}.
-In Theorem \ref{thm:sufficient} we show that, 
-% under the general distributional assumptions in Section \ref{subsec:set-up}, 
-if the signal sizes are above the boundary (i.e., $\underline{r}> f_{\mathrm{E}}(\beta)$), the \ac{FWER}-controlling procedures described in Section \ref{sec:statistical-procedures} with appropriately calibrated levels achieve \emph{exact support recovery} as in \eqref{eq:exact-recovery}.
+demarcates the region of possibility for the exact support recovery problem.
+That is, if the signal sizes are above the boundary (i.e., $\underline{r}> f_{\mathrm{E}}(\beta)$), then \ac{FWER}-controlling procedures with appropriately calibrated levels achieve exact support recovery (Theorem \ref{thm:sufficient} below).
+We refer to \eqref{eq:strong-classification-boundary} as the {\em strong classification boundary}.
 
-Conversely, in Section \ref{subsec:necessary}, we show in Theorem \ref{thm:necessary} that for a surprisingly large class of dependence structures characterized by the concept of \emph{uniform relative stability} (URS, see Definition \ref{def:URS} below), when the signal size is below the boundary  (i.e., $r<f_{\mathrm{E}}(\beta)$), no thresholding procedure can achieve the asymptotically perfect support recovery \eqref{eq:exact-recovery}.
+Conversely, we show that for a surprisingly large class of dependence structures characterized by the concept of \emph{uniform relative stability} (URS, see Definition \ref{def:URS} below), when the signal size is below the boundary  (i.e., $r<f_{\mathrm{E}}(\beta)$), no thresholding procedure can achieve the asymptotically perfect support recovery.
 In fact,
@@
 \end{equation}
-for all $\widehat{S}_p$ in the form of \eqref{eq:thresholding-procedure}.
+for all thresholding procedures (Theorem \ref{thm:necessary} below).
 These two results show that the thresholding procedures obey a phase transition phenomenon in a strong, \emph{point-wise} sense over the class of URS dependence structures, and over the class of AGG$(\nu),\ \nu>0$ error distributions.

### 2021-04-05 4.exact_support_recovery/4.phase_transition_results.tex
Theorem 4.1 and proof
Just tried to introduce the new parameterization of sparsity and it seems to work.

@@
 \begin{align} \label{eq:minimax-signal-config-over}
-    \Theta_p^+(\beta, \underline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|\le\lfloor p^{1-\beta}\rfloor, \nonumber \\
-    &\quad\quad\mu(i)\ge (\nu\underline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\}.
+    \Theta_p^+(\beta, \underline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|\le \stilian{s_p^*}{\lfloor p^{1-\beta}\rfloor}, \nonumber \\
+    &\quad\quad\mu(i)\ge (\nu\underline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\},
 \end{align}
+\stilian{where $s_p^*$ is as in \eqref{eq:sparsity-parametrized-new}.}
 Our first result states that, when $F\in \text{AGG}(\nu)$ with $\nu>0$, regardless of the error dependence structure, (asymptotic) perfect support recovery is achieved by applying Bonferroni's procedure with appropriately calibrated FWER, as long as the minimum signal size $\underline{r}$ is above the strong classification boundary \eqref{eq:strong-classification-boundary}.
@@
 \begin{theorem} \label{thm:sufficient}
-Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.
+Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.  \stilian{if $\beta=1$, assume in addition that the
+slowly varying function in \eqref{eq:sparsity-parametrized-new} is such that
+\begin{equation}\label{e:new-beta=1-condition}
+\ell(p) = o(F(- c\log(p)^{1/\nu})),\ \ \mbox{ for all $c>0$.}
+\end{equation}}{}
 Let $\widehat{S}_p$ be the Bonferroni's procedure \eqref{eq:Bonferroni-procedure} with vanishing FWER $\alpha = \alpha(p) \to 0$, such that %\fbox{slower than any polynomial}
@@
       &= \P\Big[\max_{i\in S}\left(-\epsilon(i)\right) < \underbrace{\left(\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}\right)(\nu\log{p})^{1/\nu}(1+o(1))}_{=:\text{A}} \Big] \nonumber \\
-      &\ge 1 - \lfloor p^{1-\beta} \rfloor \times \overline{F}_-(\text{A}), \label{eq:sufficient-proof-eq2}
+      &\ge 1 - \stilian{\ell(p)p^{1-\beta}}{\lfloor p^{1-\beta} \rfloor} \times \overline{F}_-(\text{A}), \label{eq:sufficient-proof-eq2}
       % &\ge 1 - |S|\times\P\Big[(-\epsilon(1)) \ge \left(\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}\right)(\nu\log{p})^{1/\nu}(1+o(1)) \Big] 
@@
 where $\overline{F}_-(x) = \P[-\epsilon(i)>x]$ is the survival function of the $(-\epsilon(i))$'s.
-Notice that \eqref{eq:sufficient-proof-eq2} follows from the union bound and the assumption that ${|S_p|}\le{\lfloor p^{1-\beta}\rfloor}$. 
+Notice that \eqref{eq:sufficient-proof-eq2} follows from the union bound and the assumption that ${|S_p|}\le \stilian{s_p^*= \ell(p)p^{1-\beta}}{{\lfloor p^{1-\beta}\rfloor}}$. 
 Therefore, the lower bound does not depend on $\mu$ (nor on the error dependence structure), and holds uniformly in the parameter space. In turn, we obtain 
 \begin{equation} \label{eq:exact-supporot-recovery-FWNR}
-    \inf_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \supseteq S_p] \ge 1 - \lfloor p^{1-\beta} \rfloor \times \overline{F}_-(\text{A}).
+    \inf_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \supseteq S_p] \ge 1 - \stilian{\ell(p)p^{1-\beta}}{\lfloor p^{1-\beta} \rfloor} \times \overline{F}_-(\text{A}).
 \end{equation}
@@
 If $\beta=1$, we conclude that the right-hand-side of \eqref{eq:exact-supporot-recovery-FWNR} 
-converges to $1$, since $\text{A}\to+\infty$.
+converges to $1$, \stilian{in view of \eqref{e:new-beta=1-condition} applied with $c \log(p)^{1/\nu}:= A$.}{ since $\text{A}\to+\infty$.}
 
@@
 \begin{equation}
-    \lfloor p^{1-\beta} \rfloor \times \overline{F}_-(\text{A}) \le 
-    \frac{\overline{F}_-\left(\text{B}\times{u_{\lfloor p^{1-\beta}\rfloor}^-}\right)} {\overline{F}_-\left({u_{\lfloor p^{1-\beta}\rfloor}^-}\right)} \label{eq:sufficient-proof-eq3}
+    \stilian{s_p^*}{\lfloor p^{1-\beta} \rfloor} \times \overline{F}_-(\text{A}) \le 
+    \frac{\overline{F}_-\left(\text{B}\times{u_{s_p^*}^-}\right)} {\overline{F}_-\left({u_{s_p^*}}\right)} \label{eq:sufficient-proof-eq3}
     % \P\Big[\frac{\max_{i\in S}(-\epsilon(i))}{u_{|S|}}\frac{u_{|S|}}{u_{\lfloor p^{1-\beta}\rfloor}} < \underbrace{\frac{\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}}{(1-\beta)^{1/\nu}}\left(1+o(1)\right)}_{=:\text{B}}\Big], \label{eq:exact-supporot-recovery-FWNR}
 \end{equation}
-where $\text{B} := {\text{A}}/{u_{\lfloor p^{1-\beta}\rfloor}^-}$.
+where $\text{B} := {\text{A}}/{u_{s_p^*}^-}$.
 
@@
 \begin{equation} \label{eq:sufficient-proof-eq4}
-    u_{\lfloor p^{1-\beta}\rfloor}^- \sim \left(\nu(1-\beta)\log{p}\right)^{1/\nu}
+    u_{s_p^*}^- \equiv u_{\ell(p)p^{1-\beta}}^-\sim \left(\nu(1-\beta)\log{p}\right)^{1/\nu},
 \end{equation}
-and 
+\stilian{where we used the fact that $\log(\ell(p)) = o(\log(p))$. Hence,}{and} 
 \begin{equation*}
-\text{B} = \frac{\text{A}}{u_{\lfloor p^{1-\beta}\rfloor}^-}
+\text{B} = \frac{\text{A}}{u_{s_p^*}^-}
 = \frac{\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}}{(1-\beta)^{1/\nu}}\left(1+o(1)\right) \to c>1
@@
 We end this section with several remarks on the scope and consequences
-of our results. Our first comment is on the signal sizes, and in particular, the gap 
-between the sufficient conditions (Theorem \ref{thm:sufficient}) and the necessary 
+of our results. Our first comment is on the signal sizes, and in particular, on the gap between the sufficient conditions (Theorem \ref{thm:sufficient}) and the necessary 
 conditions (Theorem \ref{thm:necessary}).
@@
 \begin{enumerate}
-    \item $r^{(1)} = (1+\delta)f_{\mathrm{E}}(\beta)$, $r^{(2)} = (1+\delta)$ with $|S_p^{(1)}|=|S_p|-1$, $|S_p^{(2)}|=1$, 
-    \item $r^{(1)} = (1+\delta)f_{\mathrm{E}}(\beta)$, $r^{(2)} = (1-\delta)f_{\mathrm{E}}(\beta)$ with $|S_p^{(1)}|=\lfloor|S_p|/2\rfloor$, $|S_p^{(2)}|=|S_p| - |S_p^{(1)}|$.
+    \item $r^{(1)} = (1+\delta)f_{\mathrm{E}}(\beta)$, $r^{(2)} = (1+\delta)$,  with $|S_p^{(1)}|=|S_p|-1$, $|S_p^{(2)}|=1$, 
+    \item $r^{(1)} = (1+\delta)f_{\mathrm{E}}(\beta)$, $r^{(2)} = (1-\delta)f_{\mathrm{E}}(\beta)$, with $|S_p^{(1)}|=\lfloor|S_p|/2\rfloor$, $|S_p^{(2)}|=|S_p| - |S_p^{(1)}|$.
 \end{enumerate}
@@
 \begin{remark}
-	we emphasize that the sharp phase transition result just established apply only to the general class of thresholding procedures.
-It is natural to ask if we have left out the other good procedures in this restriction.
-	We will establish in Chapter \ref{chap:optimality} below that in many cases the optimal procedures are in fact thresholding procedures.
+	Since the sharp phase transition result just established apply only to the general class of thresholding procedures, it is natural to ask if other good procedures have left out by this restriction.
+	We will establish later in Chapter \ref{chap:optimality} that in many cases the optimal procedures are in fact thresholding procedures.
 In general, however, thresholding procedures can be sub-optimal, e.g., when the errors have heavy (regularly-varying) tails.
@@
 errors \citep{hall2010innovated}. 
-Surprisingly, our results here state that asymptotically, \emph{all} error dependence structures in the large URS class are equally difficult for \emph{thresholding procedures}.
+Surprisingly, our results here state that asymptotically, \emph{all} error dependence structures in the large URS class are equally difficult for {thresholding procedures}.
 Therefore, the phase transition behavior is universal in the class of dependence structures characterized by URS.
@@
 
-The restriction to the URS dependence class in Theorem \ref{thm:necessary} is \emph{not} an assumption of convenience. 
-The dependence condition characterized by uniform relative stability is, in fact, one of the weakest in the literature.
+We emphasize the restriction to the URS dependence class in Theorem \ref{thm:necessary} is {not} an assumption of convenience. 
+The dependence condition characterized by uniform relative stability is in fact one of the weakest in the literature.
 We will characterize the class URS dependence class in Chapter \ref{chap:URS} below.

### 2021-04-05 4.exact_support_recovery/exact_support_recovery.tex
Theorem 4.1 and proof
Just tried to introduce the new parameterization of sparsity and it seems to work.

@@
 This generalized distributional assumption on the errors call for a suitable generalization of the signal size parametrization in order to analyze the problem as we did in the previous chapter.
-As before, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector $\mu = \left(\mu(i)\right)_{i=1}^p$ where its sparsity, with a few exceptions which will be explicitly stated, is parametrized as
+\stilian{As before, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector
+$\mu_p = \left(\mu_p(i)\right)_{i=1}^p$, with support $S_p:= \{i\, :\, \mu_p(i)\not = 0\}$.  The sparsity of $\mu_p$ will be parameterized and quantified
+in terms of a {\em fixed} regularly varying sequence $\{s_p^*\}$ as follows:
+\begin{equation} \label{eq:sparsity-parametrized-new}
+s_p := |S_p| \sim s_p^* := \ell(p) p^{1-\beta},
+\end{equation}
+where $\ell(\cdot)$ is some fixed slowly varying function.
+Recall that a function $\ell$ is slowly varying if $\ell(\lambda t)/\ell(t) \to 1$, as $t\to\infty$, for all $\lambda>0$.
+As before, the fixed exponent $\beta \in (0,1]$ controls the sparsity.}{
+ where its sparsity, with a few exceptions which will be explicitly stated, is parametrized as
 \begin{equation} \label{eq:sparsity-parametrized}
@@
 \end{equation}
-with $0 < \beta \le 1$ fixed.
+with $0 < \beta \le 1$ fixed.}
 

### 2021-04-06 3.phase_transitions/phase_transitions.tex
done
Implemented a more flexible support parameterization in Ch. 4.  All proposed changes are marked in blue. PLEASE REVIEW.

@@
 \begin{equation} \label{eq:signal-sparsity-additive}
-   \stilian{|S_p| \sim p^{1-\beta} }{\mbox{instead of $= \left\lfloor p^{1-\beta} \right\rfloor$ \fbox{CAN WE DO THAT?}}}, \quad \beta\in(0,1],
+   |S_p| = \lfloor p^{1-\beta} \rfloor, \quad \beta\in(0,1],
 \end{equation}
-where $\beta$ parametrizes the problem sparsity\stilian{, and $\sim$ stands for asymptotic equivalence, i.e., $a_p\sim b_p$ if $a_p/b_p\to 1$, as $p\to\infty$.}{}
-The closer $\beta$ is to 1, the sparser the support $S_p$.  
-Conversely, when $\beta$ is close to 0, the support is dense with many non-null signals.
+where $\beta$ parametrizes the problem sparsity.\stilian{A more general parameterization of the support involving a slowly 
+varying function is considered in Chapter \ref{chap:exact-support-recovery}.}{}
+
+The closer $\beta$ to 1, the sparser the support $S_p$. Conversely, when $\beta$ is close to 0, the support is dense with many non-null signals.
 We consider one-sided alternatives \eqref{eq:global-test-one-sided}, and parametrize the range of the non-zero (and perhaps unequal) signals with

### 2021-04-06 4.exact_support_recovery/4.phase_transition_results.tex
done
Implemented a more flexible support parameterization in Ch. 4.  All proposed changes are marked in blue. PLEASE REVIEW.

@@
 \begin{align} \label{eq:minimax-signal-config-over}
-    \Theta_p^+(\beta, \underline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|\le \stilian{s_p^*}{\lfloor p^{1-\beta}\rfloor}, \nonumber \\
+    \Theta_p^+(\beta, \underline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|\le \stilian{s_p^\dagger}{\lfloor p^{1-\beta}\rfloor}, \nonumber \\
     &\quad\quad\mu(i)\ge (\nu\underline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\},
 \end{align}
-\stilian{where $s_p^*$ is as in \eqref{eq:sparsity-parametrized-new}.}
+\stilian{where $s_p^\dagger$ is as in \eqref{eq:sparsity-parametrized-new}.}
 Our first result states that, when $F\in \text{AGG}(\nu)$ with $\nu>0$, regardless of the error dependence structure, (asymptotic) perfect support recovery is achieved by applying Bonferroni's procedure with appropriately calibrated FWER, as long as the minimum signal size $\underline{r}$ is above the strong classification boundary \eqref{eq:strong-classification-boundary}.
@@
 \begin{theorem} \label{thm:sufficient}
-Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.  \stilian{if $\beta=1$, assume in addition that the
+Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.  \stilian{If $\beta=1$, assume in addition that the
 slowly varying function in \eqref{eq:sparsity-parametrized-new} is such that
 \begin{equation}\label{e:new-beta=1-condition}
-\ell(p) = o(F(- c\log(p)^{1/\nu})),\ \ \mbox{ for all $c>0$.}
+\ell(p) = o\Big(1/ F(- c\log(p)^{1/\nu})\Big),\ \ \mbox{ for all $c>0$.}
 \end{equation}}{}
@@
 where $\overline{F}_-(x) = \P[-\epsilon(i)>x]$ is the survival function of the $(-\epsilon(i))$'s.
-Notice that \eqref{eq:sufficient-proof-eq2} follows from the union bound and the assumption that ${|S_p|}\le \stilian{s_p^*= \ell(p)p^{1-\beta}}{{\lfloor p^{1-\beta}\rfloor}}$. 
+Notice that \eqref{eq:sufficient-proof-eq2} follows from the union bound and the assumption 
+that  \stilian{${|S_p|}\le s_p^\dagger= \ell(p)p^{1-\beta}$ in \eqref{eq:minimax-signal-config-over}. }{${|S_p|}\le \lfloor p^{1-\beta}\rfloor$}. 
 Therefore, the lower bound does not depend on $\mu$ (nor on the error dependence structure), and holds uniformly in the parameter space. In turn, we obtain 
@@
 \begin{equation}
-    \stilian{s_p^*}{\lfloor p^{1-\beta} \rfloor} \times \overline{F}_-(\text{A}) \le 
-    \frac{\overline{F}_-\left(\text{B}\times{u_{s_p^*}^-}\right)} {\overline{F}_-\left({u_{s_p^*}}\right)} \label{eq:sufficient-proof-eq3}
+    \stilian{s_p^\dagger}{\lfloor p^{1-\beta} \rfloor} \times \overline{F}_-(\text{A}) \le 
+    \frac{\overline{F}_-\left(\text{B}\times{u_{s_p^\dagger}^-}\right)} {\overline{F}_-\left({u_{s_p^\dagger}}\right)} \label{eq:sufficient-proof-eq3}
     % \P\Big[\frac{\max_{i\in S}(-\epsilon(i))}{u_{|S|}}\frac{u_{|S|}}{u_{\lfloor p^{1-\beta}\rfloor}} < \underbrace{\frac{\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}}{(1-\beta)^{1/\nu}}\left(1+o(1)\right)}_{=:\text{B}}\Big], \label{eq:exact-supporot-recovery-FWNR}
 \end{equation}
-where $\text{B} := {\text{A}}/{u_{s_p^*}^-}$.
+where $\text{B} := {\text{A}}/{u_{s_p^\dagger}^-}$.
 
@@
 \begin{equation} \label{eq:sufficient-proof-eq4}
-    u_{s_p^*}^- \equiv u_{\ell(p)p^{1-\beta}}^-\sim \left(\nu(1-\beta)\log{p}\right)^{1/\nu},
+    u_{s_p^\dagger}^- \equiv u_{\ell(p)p^{1-\beta}}^-\sim \left(\nu(1-\beta)\log{p}\right)^{1/\nu},
 \end{equation}
@@
 \begin{equation*}
-\text{B} = \frac{\text{A}}{u_{s_p^*}^-}
+\text{B} = \frac{\text{A}}{u_{s_p^\dagger}^-}
 = \frac{\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}}{(1-\beta)^{1/\nu}}\left(1+o(1)\right) \to c>1
@@
 \begin{align} \label{eq:minimax-signal-config-under}
-    \Theta_p^-(\beta, \overline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|=\lfloor p^{1-\beta}\rfloor, \nonumber \\
-    &\quad\quad0<\mu(i)\le(\nu\overline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\}.
+    \Theta_p^-(\beta, \overline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }
+    \stilian{|S_p| = \lfloor s_p^\dagger \rfloor}{ |S_p|=\lfloor p^{1-\beta}\rfloor}, \nonumber \\
+    &\quad\quad0<\mu(i)\le(\nu\overline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\},
 \end{align}
+\stilian{where $s_p^\dagger= \ell(p) p^{1-\beta}$ is as in \eqref{eq:sparsity-parametrized-new}.}
 
@@
 $$
-S_p^* = \argmax_{S\subseteq\{1,\ldots,p\}:|S| = \lfloor p^{1-\beta}\rfloor} \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
+S_p^* = \argmax_{S\subseteq\{1,\ldots,p\}:|S| =\stilian{\lfloor s_p^\dagger \rfloor }{\lfloor p^{1-\beta}\rfloor}} \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
 $$
+\stilian{where $s_p^\dagger = \ell(p)p^{1-\beta}$ is the size of the true support set and}{}
 where ties can be broken lexicographically if multiple maximizers exist.
@@
 so that the two random terms in probability \eqref{eq:classification-possible-dependent-proof-2} converge to constants.
-Notice that the second relation in \eqref{eq:classification-possible-dependent-proof-3} holds by URS for any $\beta\in(0,1)$; when $\beta=1$, the relation holds since ${u_{|S^*|}}/{u_p}$ vanishes while $\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight.
+Notice that the second relation in \eqref{eq:classification-possible-dependent-proof-3} holds by URS for any $\beta\in(0,1)$; when $\beta=1$, the relation holds because \stilian{$\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight while $0\le u_{|S^*|}/u_p \le u_{\ell(p)}/u_p \to 0$ since $\ell(p) = o(p)$.
+}{${u_{|S^*|}}/{u_p}$  vanishes while $\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight.}
 
@@
 Paraphrasing Theorems \ref{thm:sufficient} and \ref{thm:necessary}: if we consider only thresholding procedures, then for a very large class of dependence structures, we cannot improve upon the Bonferroni procedure $\widehat{S}_p^{\text{Bonf}}$.
-Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we have
+Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where 
+$\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};\stilian{|S| = \lfloor \ell (p) p^{1-\beta}\rfloor}{|S|=\lfloor p^{1-\beta}\rfloor}\right\}$, we have
 \begin{equation}

### 2021-04-06 4.exact_support_recovery/exact_support_recovery.tex
done
Implemented a more flexible support parameterization in Ch. 4.  All proposed changes are marked in blue. PLEASE REVIEW.

@@
 \stilian{As before, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector
-$\mu_p = \left(\mu_p(i)\right)_{i=1}^p$, with support $S_p:= \{i\, :\, \mu_p(i)\not = 0\}$.  The sparsity of $\mu_p$ will be parameterized and quantified
-in terms of a {\em fixed} regularly varying sequence $\{s_p^*\}$ as follows:
+$\mu_p = \left(\mu_p(i)\right)_{i=1}^p$, with support $S_p:= \{i\, :\, \mu_p(i)\not = 0\}$.
+The sparsity of $\mu_p$  with a few exceptions which will be explicitly stated, is parametrized in terms of a {\em fixed} regularly varying sequence $\{s_p^\dagger\}$ as follows:
 \begin{equation} \label{eq:sparsity-parametrized-new}
-s_p := |S_p| \sim s_p^* := \ell(p) p^{1-\beta},
+ |S_p| =   \lfloor s_p^\dagger \rfloor,\ \ \mbox{ where }\ \ s_p^\dagger := \ell(p) p^{1-\beta},
 \end{equation}
-where $\ell(\cdot)$ is some fixed slowly varying function.
-Recall that a function $\ell$ is slowly varying if $\ell(\lambda t)/\ell(t) \to 1$, as $t\to\infty$, for all $\lambda>0$.
-As before, the fixed exponent $\beta \in (0,1]$ controls the sparsity.}{
+for some fixed slowly varying function $\ell$.  Recall that a function $\ell$ is slowly varying 
+if $\ell(\lambda t)/\ell(t) \to 1$, as $t\to\infty$, for all $\lambda>0$.   As before, the exponent $$0 <\beta \le 1$$ controls the sparsity.}{
  where its sparsity, with a few exceptions which will be explicitly stated, is parametrized as
@@
 
- \stilian{\begin{remark}Without much effort, one can relax the above parameterization of the support size in \eqref{eq:sparsity-parametrized} to $|S_p| \sim p^{1-\beta}$ or in fact, to the 
+\comment{ \stilian{\begin{remark}Without much effort, one can relax the above parameterization of the support size in \eqref{eq:sparsity-parametrized} to $|S_p| \sim p^{1-\beta}$ or in fact, to the 
 much more general case of $|S_p|\sim L(p) p^{1-\beta}$, for a slowly varying function $L$.  Going along this path would would naturally lead to
 more sophisticated signal models, which merit independent study.  Here, we opt for simplicity of exposition and thus adopt 
-\eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized}.\end{remark}}
+\eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized}.\end{remark}}}
 

### 2021-04-07 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
chapter 5 and 7 -- minor edits
I propagated the new support parameterization to Ch 5.  Please CHECK.  I also added a small comment/pointer in Ch. 7 (right after (7.2)) but other than that, did not change anything in Ch. 7.

@@
-In this chapter, we investigate the universality of the phase-transition results on exact support recovery established in
-Chapter \ref{chap:exact-support-recovery}.  Specifically, we would like to know to what extent the signal classification 
-boundary valid for thresholding estimators applies to the best possible support estimators.  The answer to this question 
-will complete the characterization of the fundamental limits in exact support recovery.
+In this chapter, we investigate the universality of the phase-transition results on exact support recovery established in Chapter \ref{chap:exact-support-recovery}.
+Specifically, we would like to know to what extent the strong classification 
+boundary applies to all support estimators, and not just thresholding ones.
+The answer to this question will complete the characterization of the fundamental limits in exact support recovery.
 
-To this end, we begin by characterizing the finite-sample Bayes optimality of the thresholding procedures (Section
-\ref{subsec:optimal-procedure-sub-exponential}). As we will see, the so-called oracle thresholding estimators are in 
-fact finite-sample optimal for many classes of models.  These optimality results allow us to establish 
-powerful minimax formulations of the exact support recovery phase-transition phenomenon showing its universality for all estimators (Theorem \ref{thm:necessary-strengthened}).
+To this end, we begin by characterizing the finite-sample Bayes optimality of the thresholding procedures. 
+As we will see, the so-called oracle thresholding estimators are in fact finite-sample optimal for many classes of models. 
+These optimality results allow us to establish a minimax formulation of the exact support recovery phase-transition phenomenon that covers arbitrary procedures.
 
-Perhaps surprisingly, however, thresholding estimators can be sub-optimal.  This is so for example 
-in the additive noise model with heavier than exponential error densities (Example 
-\ref{exmp:suboptimal-data-thresholding}).   In this case, {\em likelihood ratio
-thresholding} rather than {\em data thresholding} can lead to optimal support estimators
-(Section \ref{subsec:optimal-procedure-super-exponential}).  In such cases, the universality 
-of the exact support recovery boundary remains an open question.
+Perhaps surprisingly, thresholding estimators can be sub-optimal.
+This is so, for example, in the additive noise model when the error tail densities are heavier than exponential. 
+In this case, we will see that {\em likelihood ratio thresholding} rather than {\em data thresholding} are the optimal support estimators.
+%In such cases, the universality of the exact support recovery boundary remains an open question.
 
@@
 Let $\widehat{S}^{\text{Bonf}}$ be the sequence of Bonferroni's procedure described in Theorem \ref{thm:sufficient}. 
-Let also the errors have common $\text{AGG}(\nu)$ distribution $F$ with parameter $\nu>0$, and $\Theta_p^+$ be as defined in \eqref{eq:minimax-signal-config-over}.
+Let also the errors have common $\text{AGG}(\nu)$ distribution $F$ with parameter $\nu>0$, and $\Theta_p^+(\beta,\underline{r})$ be as defined in \eqref{eq:minimax-signal-config-over}.
+\stilian{If $\beta=1$, assume in addition that \eqref{e:new-beta=1-condition} holds.}{}
 If $\underline{r}>f_{\mathrm{E}}(\beta)$, then we have
@@
 
-For the second statement \eqref{eq:point-wise-minimax-below}, since $\underline{r}<f_{\mathrm{E}}(\beta)$, we can pick a sequence $\mu^*\in\Theta_p^+(\beta, \underline{r})$ such that $|S_p| = \lfloor p^{1-\beta}\rfloor$, with signals having the same signal size $\mu(i)=(2r\log{p})^{1/\nu}$ for all $i\in S_p$, where $\underline{r}<{r}<f_{\mathrm{E}}(\beta)$.
-For this particular choice of $\mu^*$ we have $\mu^*\in\Theta_p^-(\beta, \overline{r})$ where $r<\overline{r}<f_{\mathrm{E}}(\beta)$,
-and according to Theorem \ref{thm:necessary}, we obtain $\lim_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \mathbb P[\widehat{S}_p \neq S_p] = 1$, for all dependence structures in the URS class.
+For the second statement \eqref{eq:point-wise-minimax-below}, since $\underline{r}<f_{\mathrm{E}}(\beta)$, we can pick a sequence $\mu^*\in\Theta_p^+(\beta, \underline{r})$ such that \stilian{$|S_p| = \lfloor \ell(p) p^{1-\beta} \rfloor$}{$|S_p| = \lfloor p^{1-\beta}\rfloor$}, with signals having the same signal size $\mu(i)=(2r\log{p})^{1/\nu}$ for all $i\in S_p$, where $\underline{r}<{r}<f_{\mathrm{E}}(\beta)$.
+For this particular choice of $\mu^*$ we have $\mu^*\in\Theta_p^-(\beta, \overline{r})$ (recall \eqref{eq:minimax-signal-config-under}),
+where $r<\overline{r}<f_{\mathrm{E}}(\beta)$, and according to Theorem \ref{thm:necessary}, we obtain 
+$\lim_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \mathbb P[\widehat{S}_p \neq S_p] = 1$, for all dependence structures in the URS class.
 \end{proof}
@@
 Let $D(F)$ be the collection of error arrays with common marginal $F$ as defined in \eqref{eq:common-marginal-distribution} where $F$ is an $\text{AGG}(\nu)$ distribution.
+\stilian{If $\beta=1$, assume in addition that \eqref{e:new-beta=1-condition} holds.}{}
 Let also $\widehat{S}^{\text{Bonf}}_p$ be Bonferroni's procedure as described in Theorem \ref{thm:sufficient}.
@@
     \Theta_p^* &=
-    \{\mu\in\mathbb{R}^d:\;|S_p|=\lfloor p^{1-\beta}\rfloor,\;\mu(i)=0\;\text{for all }i\not\in S, \;\text{and}\\
+    \{\mu\in\mathbb{R}^d:\;|S_p|=\stilian{\lfloor \ell(p)p^{1-\beta} \rfloor}{\lfloor p^{1-\beta}\rfloor},\;\mu(i)=0\;\text{for all }i\not\in S, \;\text{and}\\
     &\quad\quad\mu(i) = (\nu{r}\log{p})^{1/\nu}\;\text{for all }i\in S,\;\text{where}\;\underline{r}<r<f_{\mathrm{E}}(\beta)\},

### 2021-04-07 7.GWAS/7.chi-square.tex
chapter 5 and 7 -- minor edits
I propagated the new support parameterization to Ch 5.  Please CHECK.  I also added a small comment/pointer in Ch. 7 (right after (7.2)) but other than that, did not change anything in Ch. 7.

@@
 \end{equation}
-where $S_p:= \{ i\, :\, \lambda(i) >0 \}$ is the {\em signal support} set and  $\beta$ parametrizes the problem {\em sparsity}.
+where $S_p:= \{ i\, :\, \lambda(i) >0 \}$ is the {\em signal support} set and  $\beta$ parametrizes the problem {\em sparsity}. \stilian{More general
+parameterizations of the support size are possible as in \eqref{eq:sparsity-parametrized-new}. 
+Here, however, for simplicity, we drop the slowly varying term $\ell(\cdot)$. } {}
 The closer $\beta$ is to 1, the sparser the support $S_p$; conversely, when $\beta$ is close to 0, the support is dense with many non-null signals.

### 2021-04-07 4.exact_support_recovery/4.phase_transition_results.tex
added a remark
about the extra condition (4.9) right after the statement of Theorem 4.1.

@@
 \end{theorem}
-\begin{proof}%[Proof of Theorem \ref{thm:sufficient}]
+\stilian{\begin{remark} The seemingly technical condition \eqref{e:new-beta=1-condition} is rather mild.
+It is trivially satisfied if $\ell(p) \sim {\rm const}$.  This condition is only needed in the extremely sparse regime $\beta=1$.
+\end{remark}}{}
+\begin{proof}[Proof of Theorem \ref{thm:sufficient}]
 Throughout the proof, the dependence on $p$ will be suppressed to simplify notations when such omissions do not lead to ambiguity.

### 2021-04-07 4.exact_support_recovery/4.phase_transition_results.tex
simplified a bit
It turns out that we don't need a special condition on the slowly varying function \ell in the case \beta=1.  I just added an argument in the proof of Theorem 4.1 based on Potter bounds.

This simplified the exposition!

Please check, I will carefully check one more time tomorrow.

BTW, I am sure you know, but a safe way to make sure we have no broken references is to examine the log and go page by page through the missing labels.  This is also a way to securely replace all the references to an outdated  equation -- just eliminate its label and go through the errors...

--- 2021-04-06 4.exact_support_recovery/4.phase_transition_results.tex
@@
 \begin{theorem} \label{thm:sufficient}
-Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.  \stilian{If $\beta=1$, assume in addition that the
-slowly varying function in \eqref{eq:sparsity-parametrized-new} is such that
-\begin{equation}\label{e:new-beta=1-condition}
-\ell(p) = o\Big(1/ F(- c\log(p)^{1/\nu})\Big),\ \ \mbox{ for all $c>0$.}
-\end{equation}}{}
+Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.
 Let $\widehat{S}_p$ be the Bonferroni's procedure \eqref{eq:Bonferroni-procedure} with vanishing FWER $\alpha = \alpha(p) \to 0$, such that %\fbox{slower than any polynomial}
@@
 If $\beta=1$, we conclude that the right-hand-side of \eqref{eq:exact-supporot-recovery-FWNR} 
-converges to $1$, \stilian{in view of \eqref{e:new-beta=1-condition} applied with $c \log(p)^{1/\nu}:= A$.}{ since $\text{A}\to+\infty$.}
+converges to $1$. \stilian{ Indeed, since $F\in {\rm AGG}(\mu)$, we have that 
+$$
+\overline{F}_{-}({\rm A}) \le \overline{F}_-(c(\nu \log(p))^{1/\nu}) = {\cal O}( p^{-c'} ),
+$$
+for some $c>c'>0$.  On the other hand, the celebrated Potter bounds for slowly-varying functions \citep[see, e.g.,][]{bingham:goldie:teugels:1987}
+entail $\ell(p) = o(p^{c'})$, for every $c'>0$ and
+hence $\ell(p) \overline{F}_{-}({\rm A}) \to 0$, as $p\to\infty$.}{ since $\text{A}\to+\infty$.}
 
@@
 so that the two random terms in probability \eqref{eq:classification-possible-dependent-proof-2} converge to constants.
-Notice that the second relation in \eqref{eq:classification-possible-dependent-proof-3} holds by URS for any $\beta\in(0,1)$; when $\beta=1$, the relation holds because \stilian{$\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight while $0\le u_{|S^*|}/u_p \le u_{\ell(p)}/u_p \to 0$ since $\ell(p) = o(p)$.
-}{${u_{|S^*|}}/{u_p}$  vanishes while $\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight.}
+Notice that the second relation in \eqref{eq:classification-possible-dependent-proof-3} holds by URS for any $\beta\in(0,1)$; when $\beta=1$, the relation holds because \stilian{$\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight while $0\le u_{|S^*|}/u_p \le u_{\ell(p)}/u_p \to 0$ since $\ell(p) = o(p)$
+by the Potter bounds for slowly varying functions \citep[see, e.g.,][]{bingham:goldie:teugels:1987}. }{${u_{|S^*|}}/{u_p}$  vanishes while $\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight.}
 

### 2021-04-07 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
simplified a bit
It turns out that we don't need a special condition on the slowly varying function \ell in the case \beta=1.  I just added an argument in the proof of Theorem 4.1 based on Potter bounds.

This simplified the exposition!

Please check, I will carefully check one more time tomorrow.

BTW, I am sure you know, but a safe way to make sure we have no broken references is to examine the log and go page by page through the missing labels.  This is also a way to securely replace all the references to an outdated  equation -- just eliminate its label and go through the errors...

@@
 Let also the errors have common $\text{AGG}(\nu)$ distribution $F$ with parameter $\nu>0$, and $\Theta_p^+(\beta,\underline{r})$ be as defined in \eqref{eq:minimax-signal-config-over}. 
-\stilian{If $\beta=1$, assume in addition that \eqref{e:new-beta=1-condition} holds.}{}
 If $\underline{r}>f_{\mathrm{E}}(\beta)$, then we have
@@
 Let $D(F)$ be the collection of error arrays with common marginal $F$ as defined in \eqref{eq:common-marginal-distribution} where $F$ is an $\text{AGG}(\nu)$ distribution.
-\stilian{If $\beta=1$, assume in addition that \eqref{e:new-beta=1-condition} holds.}{}
 Let also $\widehat{S}^{\text{Bonf}}_p$ be Bonferroni's procedure as described in Theorem \ref{thm:sufficient}.

### 2021-04-19 reviews/response.tex

@@
   \item {\bf (Organization)} 
-  The manuscript has been revised substantially to include a brief introductory chapter and 6 substantive chapters, which amount to a total of 125 pages.
+  The manuscript has been revised substantially and now includes a brief introductory chapter and 6 substantive chapters, which amount to a total of 125 pages.
   As with the original submission, Chapter 2 reviews the statistical risks, estimation and testing procedures, as well as probability models for the errors used in the rest of the manuscript.
 
-  After very careful deliberation, we decided to keep most of the content in Chapter 3, which provides a panorama of the phase-transition results in the signal detection and support estimation problems for the additive iid Gaussian error model.
+  After very careful deliberation, we decided to keep a majority of the content in Chapter 3, which provides a panorama of the phase-transition results in the signal detection and support estimation problems for the additive iid Gaussian error model.
   There were some mixed opinions from the reviewers regarding the inclusion of a chapter that paints the landscape in broad strokes and provides references to the state-of-the-art of the literature, at the expense of delaying entirely original contributions.
   We think that providing an accessible account of the subject of high-dimensional multiple testing would benefit readers who are not already experts in the area, and might just narrowly outweigh the additional patience required on the part of experts before we get to the more exciting material.
-  Details and explanations of the changes we made can be found in the reponse to Reviewer 2 below.
+  Details and explanations of the changes we made can be found in the reponse to Reviewer 2 (R2) below.
 
@@
 
-  Following the suggestion of Reviewer 2 ({\bf R2}),  we have placed most proofs in the text after the corresponding claims (theorems, propositions, lemmas).
+  Following the suggestion of R2,  we have placed most proofs in the text after the corresponding claims (theorems, propositions, lemmas).
 In the interest of space and to conform with the format of the SpringerBriefs series, we no longer include ``Exercises'' sections.
 
-  \item {\bf (Typos, grammar, and style)}  Prompted by criticism of a referee ({\bf R2}), we have revised the language of the manuscript. 
-  We have corrected a number of typos and missing articles.   
-  There have been re-writes throughout the manuscript in order to make the style more consistent.  
+  \item {\bf (Typos, grammar, and style)}  Prompted by the suggestions of R2, we have revised the language of the manuscript. 
+  There have been extensive re-writes throughout the manuscript in order to make the content more connected and style more consistent.  
   In trying to make the text more accessible, we re-formatted the statements of most theorems to make them more modular. 
+  We have also corrected typos and missing articles.
 
@@
 	In applications, however, attitudes towards false discoveries and missed signals are often asymmetric.
-	In the example of GWAS, where the number of candidate locations \$p\$ could be in the millions, and a class imbalance between the number of nulls and signals exists, researchers are typically interested in the marginal (location-wise) power of discovery, while exercising stringent (family-wise) false discovery control.
+	In the example of GWAS, where the number of candidate locations $p$ could be in the millions, and a class imbalance between the number of nulls and signals exists, researchers are typically interested in the marginal (location-wise) power of discovery, while exercising stringent (family-wise) false discovery control.
 	These types of asymmetric considerations, while important in applications, have not been studied theoretically.  
-	For example, the GWAS application motivates the \textbackslash\{\}emph\{exact-approximate\} support recovery risk, which weighs both the family-wise error rate and the marginal power of discovery:
+	For example, the GWAS application motivates the \emph{exact-approximate} support recovery risk, which weighs both the family-wise error rate and the marginal power of discovery:
 	$\dots$
     \end{quote}
-    In fact, we believe that power calculations for GWAS is most natrually interpreted when viewed through the exact-approximate support recovery risk.
+    In fact, we believe that power calculations for GWAS are most natrually interpreted when viewed through the exact-approximate support recovery risk.
 
@@
 
-    However, it is not clear to us whether the weak dependence condition is weaker than UDD as well.
+    However, it is not clear to us whether the weak dependence condition is always weaker than UDD.
     The comparison is complicated by the fact that the definition of UDD only cares about positive correlations, while the weak dependence condition takes the sum of absolute values of the correlations.
@@
     We are not aware of works that discuss optimality or feasibility of support recovery (i.e., multiple testing) problems under such dependence conditions.
-    The results in our text in their current form do easily extend to that of Fan et al., since even the remainder term $K_i$'s in the factor model can be more heavily dependent than under the UDD/URS condition, as discussed in the response to the previous question.
+    The results in our text in their current form do not easily extend to that of Fan et al., since even the remainder term $K_i$'s in the factor model can be more heavily dependent than under the UDD/URS condition, as discussed in the response to the previous question.
     Nevertheless, Fan et al provides a glimpse into how heavy dependence (e.g., the equi-correlated case) may be handled, and how theoretical analysis may be carried out.
-We do hope to develop general theory that applies to the more setting.
+We do hope to develop a theory that applies to the more general setting.
 %   It can be seen that the {\em weak dependence} condition in their Definition 1, implies our UDD condition (for a correlation matrix).  
@@
 
-    To provide an intuition, consider the distances between the decision boundaries and the means of the null and signal part of the observations, respectively.
+    To provide some intuition, consider the distances between the decision boundaries and the means of the null and signal part of the observations, respectively.
     Controlling the FWER requires setting the decision boundaries approximately 
@@
 
-    Controlly FDR, on the other hand, depends on the number of signals present.
+    Controlling FDR, on the other hand, depends on the number of signals present.
     When there are fewer signals, a FDR-controlling procedure has to be more conservative -- when the number of true signals is small, the number of false discoveries reported along with them has to reduce as well.
@@
 \begin{itemize}
+	\item [8.] {Page 25, what does the dark-gray area that is below the area marked by
+	``M'' and on the right of the area marked by ``$S, L_1 , L_2$'' correspond to?}
+
+    The area is detectable by the HC statistic. We have made changes to the figure and clarified this in the caption.
+
+	\item [9.] {Chapter 3, the notation $f(\beta), g(\beta), h(\beta), \widetilde{g}(\beta), \widetilde{h}(\beta)$ is hard to memorize. What about $f_P(\beta)$ where $P\in\{\mathrm{D, A, E, AE, EA}\}$?}
+
+	Agreed! We have made changes everywhere in the text.
+
 	 \item [10.] {\em Page 46, ``these Hamming loss-minimax studies naturally amounts to the analysis of the elementary case of iid data,...'' 
@@
 
- You are right that our statement was a bit exaggerated and thus perhaps misleading. We have clarified and tempered the language.
+	% You are right that our statement was a bit exaggerated and thus perhaps misleading.
+	Thank you for the feedback. We have clarified and tempered the language:
+	\begin{quote}
+	 More importantly, since Hamming loss decomposes into expectations on individual terms that are not affected by dependence, Hamming loss-minimax studies do not reveal the difference in probability of support recovery between independent and dependent observations.
+	\end{quote}
+	Our analysis, and e.g. that of Butucea et al \citep{butucea2018variable}, consider all thresholding procedures which include data-dependent procedures that are affected by dependence.
 
@@
     Thank you for the insightful comment.  Indeed, by Slepian's Lemma, negatively correlated Gaussian variables have larger maxima (in stochastic order)
-  than iid maxima (with the same marginals).  This difference, however, is negligible asymptotically.  Intuitively, this is due to the fact that while Gaussian
-  vectors can be equi-correlated with correlation $\rho$ that can be arbitrarily close to $1$, this common correlation is bounded below by $-1/(p-1)$,
-  where $p$ is the number of the variables.
+    than iid maxima (with the same marginals).
+This difference, however, is negligible asymptotically.
+Intuitively, this is due to the fact that while Gaussian vectors can be equi-correlated with correlation $\rho$ that can be arbitrarily close to $1$, this common correlation is bounded below by $-1/(p-1)$, where $p$ is the number of the variables.
 
@@
     dependence and the proof involves the union bound and the rapid variation property of the marginal distributions.  Please see Proposition 2.2.
+
+    \item[12.] {Page 52, scenario 1, $r^{(2)} = (1 + \delta) \implies r^{(2)} = (1 + \delta)g(\beta)$.}
+
+    Thank you for your careful reading of the text! 
+    However this was not a typo -- we wanted to provide an example where signals sizes straddle the boundary but exact support recovery is still achieved. 
+    There is only one signal of size $r^{(2)}$ which corresponds to the required signal size at its sparsity $\beta=1$, i.e., $r^{(2)} = (1 + \delta)g(1)$.
+%    We have changed the expression to
+%    $$r^{(2)} = (1+\delta)f_{\mathrm{E}}(1)$$
+%    for clarification.
 

### 2021-04-19 2.background/2.statistical_risks.tex
updated Ch 4
I updated up to and including Ch 4.2.2.

Hope to finish tomorrow.

@@
 \begin{equation} \label{eq:type-II-error}
-    \alpha(\mathcal{R}) := \P_{\mathcal{H}_0}\left(T()\mathcal{R}(x))=1\right)
+    \alpha(\mathcal{R}) := \P_{\mathcal{H}_0}\left(T(\mathcal{R}(x))=1\right)
     \quad \text{and} \quad
@@
 Notice that all risk metrics introduced so far penalize false discoveries and missed signals somewhat symmetrically --- the approximate support recovery risk combines proportions of errors, the exact support recovery risk combines probabilities of errors, and the Hamming loss increments the risk by one regardless of the types of errors made.
-In applications, however, attitudes towards Type I and Type II errors are often different.
-In the example of GWAS, where the number of candidate locations $p$ could be in the millions, researchers are typically interested in the marginal (location-wise) power of discovery, while exercising stringent (family-wise) false discovery control.
-Such types of asymmetric risks, while important in applications, have not been studied theoretically.  
-This asymmetric consideration, and in particular the GWAS application, prompts us to consider risks that weigh both the family-wise error rate and the marginal power of discovery.
-One such risk metric is what shall be referred to as the \emph{exact-approximate} support recovery risk
+In applications, however, attitudes towards false discoveries and missed signals are often asymmetric.
+In the example of GWAS, where the number of candidate locations $p$ could be in the millions, and a class imbalance between the number of nulls and signals exists, researchers are typically interested in the marginal (location-wise) power of discovery, while exercising stringent (family-wise) false discovery control.
+These types of asymmetric considerations, while important in applications, have not been studied theoretically.  
+For example, the GWAS application motivates the \emph{exact-approximate} support recovery risk, which weighs both the family-wise error rate and the marginal power of discovery:
 \begin{equation} \label{eq:risk-exact-approx}

### 2021-04-19 3.phase_transitions/3.Gaussian-support-recovery.tex

@@
 \begin{equation} \label{eq:strong-classification-boundary-Gaussian}
-    g(\beta) = (1 + (1 - \beta)^{1/2})^2,
+    f_{\mathrm{E}}(\beta) = (1 + (1 - \beta)^{1/2})^2,
 \end{equation}
 for any method of support estimation.
-Conversely, under orthogonal, or near-orthogonal random designs, if $r>g(\beta)$, they showed that the methods they proposed achieve vanishing Hamming loss.
+Conversely, under orthogonal, or near-orthogonal random designs, if $r>f_{\mathrm{E}}(\beta)$, they showed that the methods they proposed achieve vanishing Hamming loss.
 
@@
 
-{\rm (i)} If $\underline{r} > {{g}}(\beta)$, then Bonferroni's, Sid\'ak's, Holm's, and Hochberg's procedures with slowly vanishing  nominal FWER levels 
+{\rm (i)} If $\underline{r} > f_{\mathrm{E}}(\beta)$, then Bonferroni's, Sid\'ak's, Holm's, and Hochberg's procedures with slowly vanishing  nominal FWER levels 
 (as defined in Definition \ref{def:slowly-vanishing}) all achieve asymptotically exact support recovery in the sense of \eqref{eq:support-recovery-success}. \\
 
-{\rm (ii)} Conversely, if $\overline{r} < {{g}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, we have $\P[\widehat{S}_p=S_p]\to0$.
+{\rm (ii)} Conversely, if $\overline{r} < f_{\mathrm{E}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, we have $\P[\widehat{S}_p=S_p]\to0$.
 Therefore, in view of Lemma \ref{lemma:risk-exact-recovery-probability}, exact support recovery asymptotically fails for all thresholding procedures in the sense of \eqref{eq:support-recovery-failure}.
@@
 \begin{equation} \label{eq:approx-boundary-Gaussian}
-    h(\beta) = \beta
+    f_{\mathrm{A}}(\beta) = \beta
 \end{equation}
@@
 
-{\rm (i)} If $\underline{r} > {h}(\beta)$, then the Benjamini-Hochberg procedure (defined in Section \ref{sec:statistical-procedures}) with slowly 
+{\rm (i)} If $\underline{r} > f_{\mathrm{a}}(\beta)$, then the Benjamini-Hochberg procedure (defined in Section \ref{sec:statistical-procedures}) with slowly 
 vanishing nominal FDR levels (as defined in Definition \ref{def:slowly-vanishing}) achieves asymptotically approximate support recovery in the sense of \eqref{eq:support-recovery-success}.\\
@@
 {\rm (ii)}
-Conversely, if $\overline{r} < {h}(\beta)$, then approximate support recovery asymptotically fails in the sense of \eqref{eq:support-recovery-failure} for all thresholding procedures.
+Conversely, if $\overline{r} < f_{\mathrm{a}}(\beta)$, then approximate support recovery asymptotically fails in the sense of \eqref{eq:support-recovery-failure} for all thresholding procedures.
 \end{theorem}
@@
 We now derive two new asymptotic phase transition results for the \emph{asymmetric} statistical risks, \eqref{eq:risk-exact-approx} and \eqref{eq:risk-approx-exact}, in the Gaussian error models.
+As discussed in Section \ref{sec:risks}, the exact-approximate support recovery risk is the natural criteria when considering the marginal power of discovery while controlling for family-wise error rates in applications such as GWAS.
+
+Although there have been discussions of weighted sums of type I and type II errors in the literature (see, e.g., Genovese and Wasserman \citep{genovese2002operating} Section 6, where the authors sought to minimize $\textrm{FDR} + \lambda\textrm{FNR}$), asymptotic limits were not discussed.
+We point out that the asymptotic limits for the unequally-weighted risks are no different from the equally-weighted risk, so long as $\lambda$ is bounded away from zero and infinity.
+This is because $\textrm{FDR} + \lambda\textrm{FNR}$ vanishes if and only if both FDR and FNR vanish; conversely, non-vanishing FDR and FNR is equivalent to non-vanishing weighted sums.
+Therefore, a different phase transition would only arise if we weight the type I and type II errors by combining family-wise error metrics with marginal error rates.
+
 The next theorem describes the phase transition in the exact-approximate support recovery problem.
@@
 \begin{equation} \label{eq:exact-approx-boundary-Gaussian}
-    \widetilde{g}(\beta) = 1
+    f_{\mathrm{EA}}(\beta) = 1
 \end{equation}
@@
 
-{\rm (i)} If $\underline{r} > \widetilde{g}(\beta)$, then the procedures listed in Theorem \ref{thm:Gaussian-error-exact-boundary} with slowly vanishing nominal FWER levels (as defined in Definition \ref{def:slowly-vanishing}) achieve asymptotically exact-approximate support recovery in the sense of \eqref{eq:support-recovery-success}.
+{\rm (i)} If $\underline{r} > f_{\mathrm{EA}}(\beta)$, then the procedures listed in Theorem \ref{thm:Gaussian-error-exact-boundary} with slowly vanishing nominal FWER levels (as defined in Definition \ref{def:slowly-vanishing}) achieve asymptotically exact-approximate support recovery in the sense of \eqref{eq:support-recovery-success}.
 \\
 
-{\rm (ii)} Conversely, if $\overline{r} < \widetilde{g}(\beta)$, then for any thresholding procedure $\widehat{S}$, the exact-approximate support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
+{\rm (ii)} Conversely, if $\overline{r} < f_{\mathrm{EA}}(\beta)$, then for any thresholding procedure $\widehat{S}$, the exact-approximate support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
 \end{theorem}
@@
 
-Since $\underline{r}>\widetilde{g}(\beta)=1$, we can pick $q$ such that $1<q<\underline{r}$.
+Since $\underline{r}>f_{\mathrm{EA}}(\beta)=1$, we can pick $q$ such that $1<q<\underline{r}$.
 Let $t^* = \sqrt{2q\log{p}}$, we know that $t_p<t_p^*$ for large $p$.
@@
 
-By the assumption that $\overline{r}<\widetilde{g}(\beta)=1$, we can pick $q$ such that $\overline{r}<q<1$ and let $u = t^*=\sqrt{2q\log{p}}$ in \eqref{eq:additive-error-exact-approx-boundary-proof-necessary-1}.
+By the assumption that $\overline{r}<f_{\mathrm{EA}}(\beta)=1$, we can pick $q$ such that $\overline{r}<q<1$ and let $u = t^*=\sqrt{2q\log{p}}$ in \eqref{eq:additive-error-exact-approx-boundary-proof-necessary-1}.
 By relative stability of iid Gaussian random variables \eqref{eq:relative-stability-Gaussian-maxima}, we have
@@
 \begin{equation} \label{eq:approx-exact-boundary-Gaussian}
-    \widetilde{h}(\beta) = \left(\sqrt{\beta} + \sqrt{1-\beta}\right)^2
+    f_{\mathrm{AE}}(\beta) = \left(\sqrt{\beta} + \sqrt{1-\beta}\right)^2
 \end{equation}
@@
 
-{\rm (i)} If $\underline{r} > \widetilde{h}(\beta)$, then the Benjamini-Hochberg procedure with slowly vanishing nominal FDR levels (as defined in Definition \ref{def:slowly-vanishing}) achieves asymptotically approximate-exact support recovery in the sense of \eqref{eq:support-recovery-success}.
+{\rm (i)} If $\underline{r} > f_{\mathrm{AE}}(\beta)$, then the Benjamini-Hochberg procedure with slowly vanishing nominal FDR levels (as defined in Definition \ref{def:slowly-vanishing}) achieves asymptotically approximate-exact support recovery in the sense of \eqref{eq:support-recovery-success}.
 \\
 
-{\rm (ii)} Conversely, if $\overline{r} < \widetilde{h}(\beta)$, then for any thresholding procedure $\widehat{S}$, the approximate-exact support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
+{\rm (ii)} Conversely, if $\overline{r} < f_{\mathrm{AE}}(\beta)$, then for any thresholding procedure $\widehat{S}$, the approximate-exact support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
 \end{theorem}
@@
 
-By the assumption that $\underline{r}>\widetilde{h}(\beta)=(\sqrt{\beta}+\sqrt{1-\beta})^2$, we have $\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{\beta}$, so we can pick $q>0$, such that 
+By the assumption that $\underline{r}>f_{\mathrm{AE}}(\beta)=(\sqrt{\beta}+\sqrt{1-\beta})^2$, we have $\sqrt{\underline{r}}-\sqrt{1-\beta}>\sqrt{\beta}$, so we can pick $q>0$, such that 
 \begin{equation} \label{eq:approx-exact-boundary-proof-sufficient-2-Gaussian}
@@
 $$
-f(\beta) < h(\beta) < \widetilde{g}(\beta) < \widetilde{h}(\beta) < g(\beta),
+f_{\mathrm{D}}(\beta) < f_{\mathrm{A}}(\beta) < f_{\mathrm{EA}}(\beta) < f_{\mathrm{AE}}(\beta) < f_{\mathrm{E}}(\beta),
 $$
@@
 Similarly, more stringent criteria for error control (e.g., FWER compared to FDR) require larger signals.
-We can now also compare $\widetilde{g}(\beta)$ and $\widetilde{h}(\beta)$, whose ordering may not be clear from this line of reasoning.
+We can now also compare $f_{\mathrm{EA}}(\beta)$ and $f_{\mathrm{AE}}(\beta)$, whose ordering may not be clear from this line of reasoning.
 
@@
 Our last comment is on the gap between FDR and FWER under sparsity assumptions. 
-Although it is believed that FWER control is sometimes too stringent compared to, say, FDR control in support recovery problems, the fact that all three thresholds (detection, weak, and strong classification) involve the same scaling indicates that the difficulties of the three problems (signal detection, approximate, and exact support recovery) are comparable when signals are very sparse, i.e., when $\beta$ is close to 1.
+Although it is believed that FWER control is sometimes too stringent compared to, say, FDR control in support recovery problems, the fact that all five thresholds involve the same scaling indicates that the difficulties of the problems (signal detection, and the four support recovery problems) are comparable when signals are very sparse, i.e., when $\beta$ is close to 1.
 This is illustrated with the next example.
@@
 we can reduce error standard deviation, and hence boost the signal-to-noise ratio, by a factor of $\sqrt{m}$.
-By the simple calculations above, if $m$ samples are needed to detect (sparse) signals of a certain magnitude, then $3m$ samples will enable approximate support recovery with FDR control, and in fact, $9m$ samples would enable exact support recovery with FWER control.
+By the simple calculations above, if $m$ samples are needed to detect (sparse) signals of a certain magnitude, then $3m$ samples will enable approximate support recovery with false discovery and non-discovery control, and in fact, $9m$ samples would enable exact support recovery with family-wise error rates control.
 \end{example}

### 2021-04-19 3.phase_transitions/phase_transitions.tex

@@
 \begin{equation} \label{eq:signal-sparsity-additive}
-   |S_p| = \lfloor p^{1-\beta} \rfloor, \quad \beta\in(0,1],
+    |S_p| = \left\lfloor p^{1-\beta} \right\rfloor, \quad \beta\in(0,1],
 \end{equation}
-where $\beta$ parametrizes the problem sparsity.\stilian{A more general parameterization of the support involving a slowly 
-varying function is considered in Chapter \ref{chap:exact-support-recovery}.}{}
-
-The closer $\beta$ to 1, the sparser the support $S_p$. Conversely, when $\beta$ is close to 0, the support is dense with many non-null signals.
+where $\beta$ parametrizes the problem sparsity.
+The closer $\beta$ is to 1, the sparser the support $S_p$.  
+Conversely, when $\beta$ is close to 0, the support is dense with many non-null signals.
 We consider one-sided alternatives \eqref{eq:global-test-one-sided}, and parametrize the range of the non-zero (and perhaps unequal) signals with

### 2021-04-19 4.exact_support_recovery/4.phase_transition_results.tex

@@
 \begin{align} \label{eq:minimax-signal-config-over}
-    \Theta_p^+(\beta, \underline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|\le \stilian{s_p^\dagger}{\lfloor p^{1-\beta}\rfloor}, \nonumber \\
-    &\quad\quad\mu(i)\ge (\nu\underline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\},
+    \Theta_p^+(\beta, \underline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|\le\lfloor p^{1-\beta}\rfloor, \nonumber \\
+    &\quad\quad\mu(i)\ge (\nu\underline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\}.
 \end{align}
-\stilian{where $s_p^\dagger$ is as in \eqref{eq:sparsity-parametrized-new}.}
 Our first result states that, when $F\in \text{AGG}(\nu)$ with $\nu>0$, regardless of the error dependence structure, (asymptotic) perfect support recovery is achieved by applying Bonferroni's procedure with appropriately calibrated FWER, as long as the minimum signal size $\underline{r}$ is above the strong classification boundary \eqref{eq:strong-classification-boundary}.
@@
       &= \P\Big[\max_{i\in S}\left(-\epsilon(i)\right) < \underbrace{\left(\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}\right)(\nu\log{p})^{1/\nu}(1+o(1))}_{=:\text{A}} \Big] \nonumber \\
-      &\ge 1 - \stilian{\ell(p)p^{1-\beta}}{\lfloor p^{1-\beta} \rfloor} \times \overline{F}_-(\text{A}), \label{eq:sufficient-proof-eq2}
+      &\ge 1 - \lfloor p^{1-\beta} \rfloor \times \overline{F}_-(\text{A}), \label{eq:sufficient-proof-eq2}
       % &\ge 1 - |S|\times\P\Big[(-\epsilon(1)) \ge \left(\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}\right)(\nu\log{p})^{1/\nu}(1+o(1)) \Big] 
@@
 where $\overline{F}_-(x) = \P[-\epsilon(i)>x]$ is the survival function of the $(-\epsilon(i))$'s.
-Notice that \eqref{eq:sufficient-proof-eq2} follows from the union bound and the assumption 
-that  \stilian{${|S_p|}\le s_p^\dagger= \ell(p)p^{1-\beta}$ in \eqref{eq:minimax-signal-config-over}. }{${|S_p|}\le \lfloor p^{1-\beta}\rfloor$}. 
+Notice that \eqref{eq:sufficient-proof-eq2} follows from the union bound and the assumption that ${|S_p|}\le{\lfloor p^{1-\beta}\rfloor}$. 
 Therefore, the lower bound does not depend on $\mu$ (nor on the error dependence structure), and holds uniformly in the parameter space. In turn, we obtain 
 \begin{equation} \label{eq:exact-supporot-recovery-FWNR}
-    \inf_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \supseteq S_p] \ge 1 - \stilian{\ell(p)p^{1-\beta}}{\lfloor p^{1-\beta} \rfloor} \times \overline{F}_-(\text{A}).
+    \inf_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \supseteq S_p] \ge 1 - \lfloor p^{1-\beta} \rfloor \times \overline{F}_-(\text{A}).
 \end{equation}
@@
 If $\beta=1$, we conclude that the right-hand-side of \eqref{eq:exact-supporot-recovery-FWNR} 
-converges to $1$. \stilian{ Indeed, since $F\in {\rm AGG}(\mu)$, we have that 
-$$
-\overline{F}_{-}({\rm A}) \le \overline{F}_-(c(\nu \log(p))^{1/\nu}) = {\cal O}( p^{-c'} ),
-$$
-for some $c>c'>0$.  On the other hand, the celebrated Potter bounds for slowly-varying functions \citep[see, e.g.,][]{bingham:goldie:teugels:1987}
-entail $\ell(p) = o(p^{c'})$, for every $c'>0$ and
-hence $\ell(p) \overline{F}_{-}({\rm A}) \to 0$, as $p\to\infty$.}{ since $\text{A}\to+\infty$.}
+converges to $1$, since $\text{A}\to+\infty$.
 
@@
 \begin{equation}
-    \stilian{s_p^\dagger}{\lfloor p^{1-\beta} \rfloor} \times \overline{F}_-(\text{A}) \le 
-    \frac{\overline{F}_-\left(\text{B}\times{u_{s_p^\dagger}^-}\right)} {\overline{F}_-\left({u_{s_p^\dagger}}\right)} \label{eq:sufficient-proof-eq3}
+    \lfloor p^{1-\beta} \rfloor \times \overline{F}_-(\text{A}) \le 
+    \frac{\overline{F}_-\left(\text{B}\times{u_{\lfloor p^{1-\beta}\rfloor}^-}\right)} {\overline{F}_-\left({u_{\lfloor p^{1-\beta}\rfloor}^-}\right)} \label{eq:sufficient-proof-eq3}
     % \P\Big[\frac{\max_{i\in S}(-\epsilon(i))}{u_{|S|}}\frac{u_{|S|}}{u_{\lfloor p^{1-\beta}\rfloor}} < \underbrace{\frac{\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}}{(1-\beta)^{1/\nu}}\left(1+o(1)\right)}_{=:\text{B}}\Big], \label{eq:exact-supporot-recovery-FWNR}
 \end{equation}
-where $\text{B} := {\text{A}}/{u_{s_p^\dagger}^-}$.
+where $\text{B} := {\text{A}}/{u_{\lfloor p^{1-\beta}\rfloor}^-}$.
 
@@
 \begin{equation} \label{eq:sufficient-proof-eq4}
-    u_{s_p^\dagger}^- \equiv u_{\ell(p)p^{1-\beta}}^-\sim \left(\nu(1-\beta)\log{p}\right)^{1/\nu},
+    u_{\lfloor p^{1-\beta}\rfloor}^- \sim \left(\nu(1-\beta)\log{p}\right)^{1/\nu}
 \end{equation}
-\stilian{where we used the fact that $\log(\ell(p)) = o(\log(p))$. Hence,}{and} 
+and 
 \begin{equation*}
-\text{B} = \frac{\text{A}}{u_{s_p^\dagger}^-}
+\text{B} = \frac{\text{A}}{u_{\lfloor p^{1-\beta}\rfloor}^-}
 = \frac{\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}}{(1-\beta)^{1/\nu}}\left(1+o(1)\right) \to c>1
@@
 \begin{align} \label{eq:minimax-signal-config-under}
-    \Theta_p^-(\beta, \overline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }
-    \stilian{|S_p| = \lfloor s_p^\dagger \rfloor}{ |S_p|=\lfloor p^{1-\beta}\rfloor}, \nonumber \\
-    &\quad\quad0<\mu(i)\le(\nu\overline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\},
+    \Theta_p^-(\beta, \overline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|=\lfloor p^{1-\beta}\rfloor, \nonumber \\
+    &\quad\quad0<\mu(i)\le(\nu\overline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\}.
 \end{align}
-\stilian{where $s_p^\dagger= \ell(p) p^{1-\beta}$ is as in \eqref{eq:sparsity-parametrized-new}.}
 
@@
 $$
-S_p^* = \argmax_{S\subseteq\{1,\ldots,p\}:|S| =\stilian{\lfloor s_p^\dagger \rfloor }{\lfloor p^{1-\beta}\rfloor}} \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
+S_p^* = \argmax_{S\subseteq\{1,\ldots,p\}:|S| = \lfloor p^{1-\beta}\rfloor} \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
 $$
-\stilian{where $s_p^\dagger = \ell(p)p^{1-\beta}$ is the size of the true support set and}{}
 where ties can be broken lexicographically if multiple maximizers exist.
@@
 so that the two random terms in probability \eqref{eq:classification-possible-dependent-proof-2} converge to constants.
-Notice that the second relation in \eqref{eq:classification-possible-dependent-proof-3} holds by URS for any $\beta\in(0,1)$; when $\beta=1$, the relation holds because \stilian{$\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight while $0\le u_{|S^*|}/u_p \le u_{\ell(p)}/u_p \to 0$ since $\ell(p) = o(p)$
-by the Potter bounds for slowly varying functions \citep[see, e.g.,][]{bingham:goldie:teugels:1987}. }{${u_{|S^*|}}/{u_p}$  vanishes while $\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight.}
+Notice that the second relation in \eqref{eq:classification-possible-dependent-proof-3} holds by URS for any $\beta\in(0,1)$; when $\beta=1$, the relation holds since ${u_{|S^*|}}/{u_p}$ vanishes while $\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight.
 
@@
 Paraphrasing Theorems \ref{thm:sufficient} and \ref{thm:necessary}: if we consider only thresholding procedures, then for a very large class of dependence structures, we cannot improve upon the Bonferroni procedure $\widehat{S}_p^{\text{Bonf}}$.
-Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where 
-$\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};\stilian{|S| = \lfloor \ell (p) p^{1-\beta}\rfloor}{|S|=\lfloor p^{1-\beta}\rfloor}\right\}$, we have
+Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we have
 \begin{equation}

### 2021-04-19 4.exact_support_recovery/exact_support_recovery.tex

--- 2021-04-05 4.exact_support_recovery/exact_support_recovery.tex
@@
 %The signal sizes now depends on the shape of the assumed error distributions $\mathrm{AGG}(\nu)$ through the parameter $\nu$.
-
- \stilian{\begin{remark}Without much effort, one can relax the above parameterization of the support size in \eqref{eq:sparsity-parametrized} to $|S_p| \sim p^{1-\beta}$ or in fact, to the 
-much more general case of $|S_p|\sim L(p) p^{1-\beta}$, for a slowly varying function $L$.  Going along this path would would naturally lead to
-more sophisticated signal models, which merit independent study.  Here, we opt for simplicity of exposition and thus adopt 
-\eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized}.\end{remark}}
 

### 2021-04-19 7.GWAS/7.GWAS-phase-transitions.tex

@@
 
-If we wish to achieve exact-approximate support recovery in the sense of \eqref{eq:support-recovery-success}, Theorem \ref{thm:chi-squared-exact-approx-boundary} predicts that the signal size parameter $r$ has to be at least $\widetilde{g}(\beta)= 1$.
+If we wish to achieve exact-approximate support recovery in the sense of \eqref{eq:support-recovery-success}, Theorem \ref{thm:chi-squared-exact-approx-boundary} predicts that the signal size parameter $r$ has to be at least $f_{\mathrm{EA}}(\beta)= 1$.
 This signal size calls for a sample size of $n = \lambda / w^2 = 2r\log(p)/w^2 \approx 307,011$.

### 2021-04-19 1.intro/introduction.tex
"approve" changes on generalized support set size

@@
 Both the Gaussianity assumption and the independence assumption are relaxed in Chapter \ref{chap:exact-support-recovery}.
-Established are the necessary and sufficient conditions for exact support recovery in the high-dimensional asymptotic regime.
+Established are the necessary and sufficient conditions for exact support recovery in the high-dimensional asymptotic regime for the large class of thresholding procedures.
 This is a major theoretical contribution of our approach, which solves and expands on open problems in the recent literature 
@@
 The latter concept is key to understanding the role played by dependence in the phase transition phenomena of high-dimensional testing problems.
-Using this probabilistic concept, we establish minimax optimality results that hold for a very large class of dependence structures.
+In Chapter \ref{chap:optimality} we study the universality of the phase-transition phenomenon in exact support recovery.  
+We do so by first establishing the finite-sample Bayes optimality and sub-optimality of thresholding procedures.
+This, combined with the results from Chapter \ref{chap:exact-support-recovery}, culminates in asymptotic minimax characterizations of the phase transition phenomenon in exact support recovery across all procedures for a large class of dependence structures.
 

### 2021-04-19 3.phase_transitions/phase_transitions.tex
"approve" changes on generalized support set size

--- 2021-04-06 3.phase_transitions/phase_transitions.tex
@@
 \end{equation}
-where $\beta$ parametrizes the problem sparsity.\stilian{A more general parameterization of the support involving a slowly 
-varying function is considered in Chapter \ref{chap:exact-support-recovery}.}{}
+where $\beta$ parametrizes the problem sparsity.
+A more general parameterization of the support involving a slowly varying function is considered in Chapter \ref{chap:exact-support-recovery}.
 

### 2021-04-19 4.exact_support_recovery/4.phase_transition_results.tex
"approve" changes on generalized support set size

@@
 \begin{align} \label{eq:minimax-signal-config-over}
-    \Theta_p^+(\beta, \underline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|\le\lfloor p^{1-\beta}\rfloor, \nonumber \\
-    &\quad\quad\mu(i)\ge (\nu\underline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\}.
+    \Theta_p^+(\beta, \underline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|\le s_p^\dagger, \nonumber \\
+    &\quad\quad\mu(i)\ge (\nu\underline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\},
 \end{align}
+where $s_p^\dagger$ is as in \eqref{eq:sparsity-parametrized}.
 Our first result states that, when $F\in \text{AGG}(\nu)$ with $\nu>0$, regardless of the error dependence structure, (asymptotic) perfect support recovery is achieved by applying Bonferroni's procedure with appropriately calibrated FWER, as long as the minimum signal size $\underline{r}$ is above the strong classification boundary \eqref{eq:strong-classification-boundary}.
@@
       &= \P\Big[\max_{i\in S}\left(-\epsilon(i)\right) < \underbrace{\left(\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}\right)(\nu\log{p})^{1/\nu}(1+o(1))}_{=:\text{A}} \Big] \nonumber \\
-      &\ge 1 - \lfloor p^{1-\beta} \rfloor \times \overline{F}_-(\text{A}), \label{eq:sufficient-proof-eq2}
+      &\ge 1 - \ell(p)p^{1-\beta} \times \overline{F}_-(\text{A}), \label{eq:sufficient-proof-eq2}
       % &\ge 1 - |S|\times\P\Big[(-\epsilon(1)) \ge \left(\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}\right)(\nu\log{p})^{1/\nu}(1+o(1)) \Big] 
@@
 where $\overline{F}_-(x) = \P[-\epsilon(i)>x]$ is the survival function of the $(-\epsilon(i))$'s.
-Notice that \eqref{eq:sufficient-proof-eq2} follows from the union bound and the assumption that ${|S_p|}\le{\lfloor p^{1-\beta}\rfloor}$. 
+Notice that \eqref{eq:sufficient-proof-eq2} follows from the union bound and the assumption that ${|S_p|}\le s_p^\dagger= \ell(p)p^{1-\beta}$ in \eqref{eq:minimax-signal-config-over}. 
 Therefore, the lower bound does not depend on $\mu$ (nor on the error dependence structure), and holds uniformly in the parameter space. In turn, we obtain 
 \begin{equation} \label{eq:exact-supporot-recovery-FWNR}
-    \inf_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \supseteq S_p] \ge 1 - \lfloor p^{1-\beta} \rfloor \times \overline{F}_-(\text{A}).
+    \inf_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \supseteq S_p] \ge 1 - \ell(p)p^{1-\beta} \times \overline{F}_-(\text{A}).
 \end{equation}
 
-If $\beta=1$, we conclude that the right-hand-side of \eqref{eq:exact-supporot-recovery-FWNR} 
-converges to $1$, since $\text{A}\to+\infty$.
+We first show that the right-hand-side of \eqref{eq:exact-supporot-recovery-FWNR} converges to $1$ when $\beta=1$. 
+Indeed, since $F\in {\rm AGG}(\mu)$, we have, for sufficiently large $p$,
+$$
+\overline{F}_{-}({\rm A}) \le \overline{F}_-(c(\nu \log(p))^{1/\nu}) = {\cal O}( p^{-c'} ),
+$$
+for some $c>c'>0$.
+On the other hand, the celebrated Potter bounds for slowly-varying functions \citep[see, e.g.,][]{bingham:goldie:teugels:1987} entail $\ell(p) = o(p^{c'})$, for every $c'>0$ and hence $\ell(p) \overline{F}_{-}({\rm A}) \to 0$, as $p\to\infty$.
 
@@
 \begin{equation}
-    \lfloor p^{1-\beta} \rfloor \times \overline{F}_-(\text{A}) \le 
-    \frac{\overline{F}_-\left(\text{B}\times{u_{\lfloor p^{1-\beta}\rfloor}^-}\right)} {\overline{F}_-\left({u_{\lfloor p^{1-\beta}\rfloor}^-}\right)} \label{eq:sufficient-proof-eq3}
+    s_p^\dagger \times \overline{F}_-(\text{A}) \le 
+    \frac{\overline{F}_-\left(\text{B}\times{u_{s_p^\dagger}^-}\right)} {\overline{F}_-\left({u_{s_p^\dagger}}\right)} \label{eq:sufficient-proof-eq3}
     % \P\Big[\frac{\max_{i\in S}(-\epsilon(i))}{u_{|S|}}\frac{u_{|S|}}{u_{\lfloor p^{1-\beta}\rfloor}} < \underbrace{\frac{\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}}{(1-\beta)^{1/\nu}}\left(1+o(1)\right)}_{=:\text{B}}\Big], \label{eq:exact-supporot-recovery-FWNR}
 \end{equation}
-where $\text{B} := {\text{A}}/{u_{\lfloor p^{1-\beta}\rfloor}^-}$.
+where $\text{B} := {\text{A}}/{u_{s_p^\dagger}^-}$.
 
-Notice that by assumption, the $-\epsilon(i)$'s are also 
-AGG$(\nu)$ distributed and by Proposition \ref{prop:quantile}, 
-$u_p^{-}:= F_-^{\leftarrow}(1-1/p) \sim (\nu \log(p))^{1/\nu}$,
-as $p\to\infty$. Therefore, we have
+Notice that by assumption, the $-\epsilon(i)$'s are also AGG$(\nu)$ distributed, and by Proposition \ref{prop:quantile}, $u_p^{-}:= F_-^{\leftarrow}(1-1/p) \sim (\nu \log(p))^{1/\nu}$, as $p\to\infty$.
+Therefore, we have
 \begin{equation} \label{eq:sufficient-proof-eq4}
-    u_{\lfloor p^{1-\beta}\rfloor}^- \sim \left(\nu(1-\beta)\log{p}\right)^{1/\nu}
+    u_{s_p^\dagger}^- \equiv u_{\ell(p)p^{1-\beta}}^-\sim \left(\nu(1-\beta)\log{p}\right)^{1/\nu},
 \end{equation}
-and 
+where we used the fact that $\log(\ell(p)) = o(\log(p))$. Hence,
 \begin{equation*}
-\text{B} = \frac{\text{A}}{u_{\lfloor p^{1-\beta}\rfloor}^-}
+\text{B} = \frac{\text{A}}{u_{s_p^\dagger}^-}
 = \frac{\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}}{(1-\beta)^{1/\nu}}\left(1+o(1)\right) \to c>1
@@
 \begin{align} \label{eq:minimax-signal-config-under}
-    \Theta_p^-(\beta, \overline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|=\lfloor p^{1-\beta}\rfloor, \nonumber \\
-    &\quad\quad0<\mu(i)\le(\nu\overline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\}.
+    \Theta_p^-(\beta, \overline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }
+    |S_p| = \lfloor s_p^\dagger \rfloor, \nonumber \\
+    &\quad\quad0<\mu(i)\le(\nu\overline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\},
 \end{align}
+where $s_p^\dagger= \ell(p) p^{1-\beta}$ is as in \eqref{eq:sparsity-parametrized}.
 
@@
 $$
-S_p^* = \argmax_{S\subseteq\{1,\ldots,p\}:|S| = \lfloor p^{1-\beta}\rfloor} \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
+S_p^* = \argmax_{S\subseteq\{1,\ldots,p\}:|S| = \lfloor s_p^\dagger \rfloor} \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
 $$
-where ties can be broken lexicographically if multiple maximizers exist.
+where $s_p^\dagger = \ell(p)p^{1-\beta}$ is the size of the true support set, and 
+ties are broken lexicographically if multiple maximizers exist.
 Then,
@@
 so that the two random terms in probability \eqref{eq:classification-possible-dependent-proof-2} converge to constants.
-Notice that the second relation in \eqref{eq:classification-possible-dependent-proof-3} holds by URS for any $\beta\in(0,1)$; when $\beta=1$, the relation holds since ${u_{|S^*|}}/{u_p}$ vanishes while $\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight.
+Notice that the second relation in \eqref{eq:classification-possible-dependent-proof-3} holds by URS for any $\beta\in(0,1)$.
+When $\beta=1$, the relation holds because $\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight, while $0\le u_{|S^*|}/u_p \le u_{\ell(p)}/u_p \to 0$ since $\ell(p) = o(p)$ by the Potter bounds for slowly varying functions \citep[see, e.g.,][]{bingham:goldie:teugels:1987}.
 
@@
 Paraphrasing Theorems \ref{thm:sufficient} and \ref{thm:necessary}: if we consider only thresholding procedures, then for a very large class of dependence structures, we cannot improve upon the Bonferroni procedure $\widehat{S}_p^{\text{Bonf}}$.
-Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we have
+Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where 
+$\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\}; |S| = \lfloor \ell (p) p^{1-\beta}\rfloor \right\}$, we have
 \begin{equation}

### 2021-04-19 4.exact_support_recovery/exact_support_recovery.tex
"approve" changes on generalized support set size

--- 2021-04-06 4.exact_support_recovery/exact_support_recovery.tex
@@
 This generalized distributional assumption on the errors call for a suitable generalization of the signal size parametrization in order to analyze the problem as we did in the previous chapter.
-\stilian{As before, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector
-$\mu_p = \left(\mu_p(i)\right)_{i=1}^p$, with support $S_p:= \{i\, :\, \mu_p(i)\not = 0\}$.
-The sparsity of $\mu_p$  with a few exceptions which will be explicitly stated, is parametrized in terms of a {\em fixed} regularly varying sequence $\{s_p^\dagger\}$ as follows:
-\begin{equation} \label{eq:sparsity-parametrized-new}
+As before, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector $\mu_p = \left(\mu_p(i)\right)_{i=1}^p$, with support $S_p:= \{i\, :\, \mu_p(i)\not = 0\}$.
+The sparsity of $\mu_p$,  with a few exceptions which will be explicitly stated, is parametrized in terms of a {\em fixed} regularly varying sequence $\{s_p^\dagger\}$ as follows:
+\begin{equation} \label{eq:sparsity-parametrized}
  |S_p| =   \lfloor s_p^\dagger \rfloor,\ \ \mbox{ where }\ \ s_p^\dagger := \ell(p) p^{1-\beta},
 \end{equation}
-for some fixed slowly varying function $\ell$.  Recall that a function $\ell$ is slowly varying 
-if $\ell(\lambda t)/\ell(t) \to 1$, as $t\to\infty$, for all $\lambda>0$.   As before, the exponent $$0 <\beta \le 1$$ controls the sparsity.}{
- where its sparsity, with a few exceptions which will be explicitly stated, is parametrized as
-\begin{equation} \label{eq:sparsity-parametrized}
-   s = |S_p| = \lfloor p^{1 -\beta} \rfloor, % \quad \text{with } 0 < \beta \le 1 \; \text{(fixed)},
-\end{equation}
-with $0 < \beta \le 1$ fixed.}
+for some fixed slowly varying function $\ell$.  
+Recall that a function $\ell$ is slowly varying if $\ell(\lambda t)/\ell(t) \to 1$, as $t\to\infty$, for all $\lambda>0$. 
+As before, the exponent $$0 <\beta \le 1$$ controls the sparsity.
 

### 2021-04-19 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
"approve" changes on generalized support set size

--- 2021-04-07 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
@@
 
-For the second statement \eqref{eq:point-wise-minimax-below}, since $\underline{r}<f_{\mathrm{E}}(\beta)$, we can pick a sequence $\mu^*\in\Theta_p^+(\beta, \underline{r})$ such that \stilian{$|S_p| = \lfloor \ell(p) p^{1-\beta} \rfloor$}{$|S_p| = \lfloor p^{1-\beta}\rfloor$}, with signals having the same signal size $\mu(i)=(2r\log{p})^{1/\nu}$ for all $i\in S_p$, where $\underline{r}<{r}<f_{\mathrm{E}}(\beta)$.
+For the second statement \eqref{eq:point-wise-minimax-below}, since $\underline{r}<f_{\mathrm{E}}(\beta)$, we can pick a sequence $\mu^*\in\Theta_p^+(\beta, \underline{r})$ such that $|S_p| = \lfloor \ell(p) p^{1-\beta} \rfloor$, with signals having the same signal size $\mu(i)=(2r\log{p})^{1/\nu}$ for all $i\in S_p$, where $\underline{r}<{r}<f_{\mathrm{E}}(\beta)$.
 For this particular choice of $\mu^*$ we have $\mu^*\in\Theta_p^-(\beta, \overline{r})$ (recall \eqref{eq:minimax-signal-config-under}),
@@
     \Theta_p^* &=
-    \{\mu\in\mathbb{R}^d:\;|S_p|=\stilian{\lfloor \ell(p)p^{1-\beta} \rfloor}{\lfloor p^{1-\beta}\rfloor},\;\mu(i)=0\;\text{for all }i\not\in S, \;\text{and}\\
+    \{\mu\in\mathbb{R}^d:\;|S_p|=\lfloor \ell(p)p^{1-\beta} \rfloor,\;\mu(i)=0\;\text{for all }i\not\in S, \;\text{and}\\
     &\quad\quad\mu(i) = (\nu{r}\log{p})^{1/\nu}\;\text{for all }i\in S,\;\text{where}\;\underline{r}<r<f_{\mathrm{E}}(\beta)\},

### 2021-04-19 3.phase_transitions/3.global-tests.tex
clean up repo: rename main.tex, remove unused figures, organize directories

@@
       \centering
-      \includegraphics[width=0.7\textwidth]{figures/phase_diagram_signal_detection.eps}
-      \includegraphics[width=0.7\textwidth]{figures/phase_diagram_signal_detection_vanishing_signals.eps}
+      \includegraphics[width=0.7\textwidth]{figures/theoretical_boundaries/phase_diagram_signal_detection.eps}
+      \includegraphics[width=0.7\textwidth]{figures/theoretical_boundaries/phase_diagram_signal_detection_vanishing_signals.eps}
       \caption{The phase diagrams of the sparse signal detection problem. 

### 2021-04-19 4.exact_support_recovery/4.numerical.tex
minor update
clean up repo: rename main.tex, remove unused figures, organize directories

--- 2020-08-17 4.exact_support_recovery/4.numerical.tex
@@
       \centering
-      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_p100.eps}
-      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_p10000.eps}
-      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_Laplace_p100_4.eps}
-      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_Laplace_p10000_4.eps}
-      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_NLC_p100.eps}
-      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_NLC_p10000.eps}
+      \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_p100.eps}
+      \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_p10000.eps}
+      \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_Laplace_p100_4.eps}
+      \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_Laplace_p10000_4.eps}
+      \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_NLC_p100.eps}
+      \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_NLC_p10000.eps}
       \caption{The empirical probability of exact support recovery from numerical experiments, as a function of sparsity level $\beta$ and signal sizes $r$, from Gaussian error models (upper panels), Laplace error models (middle panels), and generalized Gaussian with $\nu=1/2$ (lower panels); darker color indicates higher probability of exact support recovery.

### 2021-04-19 6.URS/6.numerical.tex
clean up repo: rename main.tex, remove unused figures, organize directories

@@
     \centering
-    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR-05_p10000.eps}
-    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR-05_p10000_oracle.eps}
-    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR05_p10000.eps}
-    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR05_p10000_oracle.eps}
-    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR09_p10000.eps}
-    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR09_p10000_oracle.eps}
+    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_AR-05_p10000.eps}
+    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_AR-05_p10000_oracle.eps}
+    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_AR05_p10000.eps}
+    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_AR05_p10000_oracle.eps}
+    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_AR09_p10000.eps}
+    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_AR09_p10000_oracle.eps}
     \caption{The empirical probability of exact support recovery from numerical experiments, as a function of sparsity level $\beta$ and signal sizes $r$.
@@
     \centering
-    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_fGn075_p10000.eps}
-    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_fGn075_p10000_oracle.eps}
-    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_fGn09_p10000.eps}
-    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_fGn09_p10000_oracle.eps}
-    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_block_structure_p10000_agnostic7.eps}
-    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_block_structure_p10000_oracle6.eps}
+    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_fGn075_p10000.eps}
+    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_fGn075_p10000_oracle.eps}
+    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_fGn09_p10000.eps}
+    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_fGn09_p10000_oracle.eps}
+    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_block_structure_p10000_agnostic7.eps}
+    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_block_structure_p10000_oracle6.eps}
     \caption{The empirical probability of exact support recovery from numerical experiments, as a function of sparsity level $\beta$ and signal sizes $r$.

### 2021-04-19 7.GWAS/7.GWAS-phase-transitions.tex
clean up repo: rename main.tex, remove unused figures, organize directories

@@
       \centering
-      \includegraphics[width=0.49\textwidth]{OR-RAF_plots/OR-RAF_p4.png} \includegraphics[width=0.49\textwidth]{OR-RAF_plots/OR-RAF_p1e2.png} \includegraphics[width=0.49\textwidth]{OR-RAF_plots/OR-RAF_p1e6.png} \includegraphics[width=0.49\textwidth]{OR-RAF_plots/OR-RAF_BC_study.png}
+      \includegraphics[width=0.49\textwidth]{figures/OR-RAF_plots/OR-RAF_p4.png}
+      \includegraphics[width=0.49\textwidth]{figures/OR-RAF_plots/OR-RAF_p1e2.png}
+      \includegraphics[width=0.49\textwidth]{figures/OR-RAF_plots/OR-RAF_p1e6.png}
+      \includegraphics[width=0.49\textwidth]{figures/OR-RAF_plots/OR-RAF_BC_study.png}
       \caption{The OR-RAF diagram visualizing the marginal power of discovery in genetic association studies, after applying Bonferroni's procedure with nominal FWER at $5\%$ level.

### 2021-04-19 7.GWAS/7.numerical.tex
clean up repo: rename main.tex, remove unused figures, organize directories

@@
 	\centering
-	\includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_strong_boundary_chi-squared_nu1_p10000.eps}
-    \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu1_p10000.eps}
-    \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu1_p10000.eps}
+	\includegraphics[width=0.32\textwidth]{figures/sim_strong_boundary/simulated_strong_boundary_chi-squared_nu1_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{figures/sim_weak_boundary/simulated_weak_boundary_chi-squared_nu1_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{figures/sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu1_p10000.eps}
 
-	\includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_strong_boundary_chi-squared_nu2_p10000.eps}
-    \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu2_p10000.eps}
-    \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu2_p10000.eps}
+	\includegraphics[width=0.32\textwidth]{figures/sim_strong_boundary/simulated_strong_boundary_chi-squared_nu2_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{figures/sim_weak_boundary/simulated_weak_boundary_chi-squared_nu2_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{figures/sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu2_p10000.eps}
 
-	\includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_strong_boundary_chi-squared_nu3_p10000.eps}
-    \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu3_p10000.eps}
-    \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu3_p10000.eps}
+	\includegraphics[width=0.32\textwidth]{figures/sim_strong_boundary/simulated_strong_boundary_chi-squared_nu3_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{figures/sim_weak_boundary/simulated_weak_boundary_chi-squared_nu3_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{figures/sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu3_p10000.eps}
 
-	\includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_strong_boundary_chi-squared_nu6_p10000.eps}
-    \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu6_p10000.eps}
-    \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu6_p10000.eps}
+	\includegraphics[width=0.32\textwidth]{figures/sim_strong_boundary/simulated_strong_boundary_chi-squared_nu6_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{figures/sim_weak_boundary/simulated_weak_boundary_chi-squared_nu6_p10000.eps}
+    \includegraphics[width=0.32\textwidth]{figures/sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu6_p10000.eps}
 	\caption{The empirical risks of exact, approximate, and approximate-exact support recovery (left to right) in the chi-squared model \eqref{eq:model-chisq} with Bonferroni's procedure and the Benjamini-Hochberg procedure.
@@
       \centering
-      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p100.eps}
-      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p1000.eps}
+      \includegraphics[width=0.32\textwidth]{figures/sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p100.eps}
+      \includegraphics[width=0.32\textwidth]{figures/sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p1000.eps}
       % \includegraphics[width=0.33\textwidth]{sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p10000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p100000.eps}
+      \includegraphics[width=0.32\textwidth]{figures/sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p100000.eps}
       \caption{The empirical probability of exact support recovery of Bonferroni's procedure (solid curves) and the oracle procedure (dashed curves) in the chi-squared model with one degree of freedom (marked `2') in the additive Gaussian error model and under one-sided alternatives (marked `1').
@@
       \centering
-      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p100.eps}
-      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p1000.eps}
-      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p100000.eps}
+      \includegraphics[width=0.32\textwidth]{figures/sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p100.eps}
+      \includegraphics[width=0.32\textwidth]{figures/sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p1000.eps}
+      \includegraphics[width=0.32\textwidth]{figures/sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p100000.eps}
       \caption{The empirical risk of approximate support recovery of Benjamini-Hochberg's procedure (solid curves) and the oracle procedure (dashed curves) in the chi-squared model with one degree of freedom (marked `2') and in the additive Gaussian error model under one-sided alternatives (marked `1').

### 2021-04-19 figures/phase_diagram_Gaussian_ALL_boundaries.R

@@ -1,53 +1,0 @@
-#### Theoretical phase diagram - all known boundaries ####
-
-setEPS()
-postscript("phase_diagram_Gaussian_ALL_boundaries.eps", height = 5, width = 5)
-# png("phase_diagram_chisquared_ALL_boundaries.png", height = 400, width = 400, units = "px")
-plot.ylim <- 4
-beta.seq <- seq(0,1,0.001)
-strong.classification.boundary <- (sqrt(1-beta.seq) + 1)^2
-classification.boundary.FDR_FNDR <- (sqrt(1-beta.seq) + sqrt(beta.seq))^2
-classification.boundary.FWER_FNR <- rep(1, length(beta.seq))
-weak.classification.boundary <- beta.seq
-detection.boundary.bonf <- (1-sqrt(1-beta.seq))^2
-detection.boundary <- detection.boundary.bonf
-detection.boundary[1:(length(beta.seq)/2)] <- 0
-detection.boundary[(length(beta.seq)/2):(length(beta.seq)*3/4)] <- 
-  beta.seq[(length(beta.seq)/2):(length(beta.seq)*3/4)] - 0.5
-par(mar = c(3,3,2,2))
-plot(beta.seq, strong.classification.boundary, type = 'l',
-     xaxs="i", yaxs="i", ylim = c(0,plot.ylim),
-     xlab = expression(beta), ylab = expression(r),
-     las = 1)
-lines(beta.seq, detection.boundary, type = 'l')
-polygon(x = c(beta.seq,rev(beta.seq)),
-        y = c(detection.boundary,rep(0,length(beta.seq))),
-        col = grey(0.0), border = T)
-polygon(x = c(beta.seq,rev(beta.seq)),
-        y = c(detection.boundary,rev(weak.classification.boundary)),
-        col = grey(0.2), border = T)
-polygon(x = c(beta.seq,rev(beta.seq)),
-        y = c(weak.classification.boundary,rev(classification.boundary.FWER_FNR)),
-        col = grey(0.4), border = T)
-polygon(x = c(beta.seq,rev(beta.seq)),
-        y = c(classification.boundary.FWER_FNR,rev(classification.boundary.FDR_FNDR)),
-        col = grey(0.6), border = T)
-polygon(x = c(beta.seq,rev(beta.seq)),
-        y = c(classification.boundary.FDR_FNDR,rev(strong.classification.boundary)),
-        col = grey(0.8), border = T)
[…]

### 2021-04-19 reviews/response.tex
added a note in "response.tex"
I added a small point (page 2) about our more general form of the support.  Hopefully, this will make the reviewers look at it more closely and spot some typos we missed :-) in addition to showing that our results have been improved.

@@
   We have also corrected typos and missing articles.
+
+   \item {\bf (An improvement)} We implemented a small improvement, which broadens the scope of our exact support recovery results.  Specifically, we noticed that 
+   the size of the signal support $|S_p|$  (previously $|S_p| = \lfloor p^{1-\beta}\rfloor$) can be parameterized as
+   $$
+   |S_p| \sim \ell(p)p^{1-\beta},\ \ \mbox{ as }p\to\infty, 
+   $$
+   where $0<\beta\le 1$ and where $\ell(\cdot)$ is a slowly varying function.  This more general parameterization required only minor, cosmetic changes to some
+   proofs in Chapters 4 and 5.
 

### 2021-04-20 figures/chisq_signal_size/Odds-ratio_2by2-tables.R
move preface forward; increase font size figure 7.1, 7.4, 7.5

@@ -1,0 +1,264 @@
+
+OR <- 1.3^(-50:50)
+
+# calculate signal size for a range of odds ratios, given marginal prob.
+lam.finder <- function(p, q) {
+  dmin <- max(-p*q, -(1-p)*(1-q), (1-p)*q-1, (1-q)*p-1)
+  dmax <- min(1-p*q, 1-(1-p)*(1-q), (1-p)*q, (1-q)*p)
+  d <- vector(mode = "numeric", length = 101)
+  d.root.finder <- function(d, OR){(p*q+d)*((1-p)*(1-q)+d)/(p*(1-q)-d)/((1-p)*q-d) - OR}
+  for (i in 1:length(OR)) {
+    solution <- uniroot(f = d.root.finder, lower = dmin, upper = dmax, OR = OR[i])
+    d[i] <- solution$root
+  }
+  lam <- d^2*(1/(p*q) + 1/(p*(1-q)) + 1/((1-p)*q) + 1/((1-p)*(1-q)))
+  return(lam)
+}
+
+
+#### Figure 1: p = 1/2 ####
+
+library(MASS)
+
+setEPS()
+postscript("singal-vs-odds-p05.eps", height = 4, width = 4)
+p <- 1/2
+q <- 1/2
+lam <- lam.finder(p, q)
+par(mar = c(3,3,2,1))
+plot(x = OR, y = lam, log = 'x', type = 'n', las = 1, ylim = c(0,1), xaxt = 'n')
+mtext(text = expression(paste("signal size ", w^2, '= ', lambda/n)), 
+      side = 2, at = 1.1, las = 1, line = -5)
+axis(side = 1, at = 10^seq(-6, 6, 2), 
+     labels = parse(text = paste("10^", seq(-6, 6, 2), sep="")))
+mtext(text = "odds ratio", side = 1, at = 3e5, las = 1, line = 2)
+
+q.vec <- as.character(fractions(1/c(2, 3, 5, 10)))
+for (i in 1:length(q.vec)) {
+  q <- eval(parse(text = q.vec[i]))
+  lam <- lam.finder(p, q)
+  lines(x = OR, y = lam, col = 1, lty = i)
+  text(x = 1e6, y = 0.95*lam[1] - 0.04, pos = 2,
+       labels = bquote(paste(theta[1], " = ", .(q.vec[i]), ", ", phi[1], " = 1/2", sep="")))
+}
+dev.off()
+
+#### Figure 2: p = 1/3 ####
+
+setEPS()
[…]

### 2021-04-20 figures/sim_one-vs-two-sided/Chi-squared_strong_boundary_simulation.R

@@ -1,0 +1,32 @@
+beta <- 0.6
+p.vec <- c(100, 1000, 10000, 100000)
+resolution <- 20
+r.max <- 6
+r.list <- seq(from = r.max/2/resolution, to = r.max - r.max/2/resolution, by = r.max/resolution)
+
+load(file = "strong.boundary.one-vs-two-sided.Rdata")
+
+for (p in p.vec) {
+  setEPS()
+  postscript(paste0("exact_recovery_one-vs-two-sided_beta0", beta*10, 
+                    "_p", format(p, scientific=F),".eps"), height = 3.5, width = 3)
+  par(mar = c(2.8,2.2,1.5,0.5))
+  matplot(t(drop(result.array[,,as.character(p)])), type = 'n', 
+          las = 1, ylim = c(0, 1), x = r.list, col = 1,
+          pch = as.character(c(1,1,2,2)), lty = c(1,2,1,2))
+  theoretical.boundary <- (sqrt(1-beta)+1)^2
+  polygon(x = c(rep(theoretical.boundary, 2), rep(r.max, 2)),
+          y = c(0, 1, 1, 0), col = grey(0.9), border = F)
+  lines(x = rep(theoretical.boundary, 2), y = c(0, 1), lty = 3)
+  abline(h = c(0, 1), lty = 3)
+  matplot(t(drop(result.array[,,as.character(p)])), type = 'b', 
+          las = 1, ylim = c(0, 1), x = r.list, col = 1, add = T,
+          pch = as.character(c(1,1,2,2)), lty = c(1,2,1,2))
+  mtext(text = bquote('signal size' ~ r), side = 1, line = 2, at = 5)
+  mtext(text = 'Prob. exact recovery', side = 2, line = -5.5, at = 1 * 1.1, las = 1)
+  text(x = 4, y = 0.18, pos = 4, labels = bquote(beta ~ '=' ~ .(beta)))
+  # text(x = 4, y = 0.10, pos = 4, labels = paste0("p = ", format(p, scientific=F)))
+  text(x = 4, y = 0.10, pos = 4, labels = bquote("p =" ~ 10^.(log10(p))))
+  dev.off()
+}
+

### 2021-04-20 figures/sim_one-vs-two-sided/Chi-squared_weak_boundary_simulation.R

@@ -1,0 +1,32 @@
+beta <- 0.6
+p.vec <- c(100, 1000, 10000, 100000)
+resolution <- 20
+r.max <- 3
+r.list <- seq(from = r.max/2/resolution, to = r.max - r.max/2/resolution, by = r.max/resolution)
+
+load(file = "weak.boundary.one-vs-two-sided.Rdata")
+
+for (p in p.vec) {
+  setEPS()
+  postscript(paste0("approx_recovery_one-vs-two-sided_beta0", beta*10, 
+                    "_p", format(p, scientific=F),".eps"), height = 3.5, width = 3)
+  par(mar = c(2.8,2.2,1.5,0.5))
+  matplot(t(drop(result.array[,,as.character(p)])), type = 'n', 
+          las = 1, ylim = c(0, 1), x = r.list, col = 1,
+          pch = as.character(c(1,1,2,2)), lty = c(1,2,1,2))
+  theoretical.boundary <- beta
+  polygon(x = c(rep(theoretical.boundary, 2), rep(r.max, 2)),
+          y = c(0, 1, 1, 0), col = grey(0.9), border = F)
+  lines(x = rep(theoretical.boundary, 2), y = c(0, 1), lty = 3)
+  abline(h = c(0, 1), lty = 3)
+  matplot(t(drop(result.array[,,as.character(p)])), type = 'b', 
+          las = 1, ylim = c(0, 1), x = r.list, col = 1, add = T,
+          pch = as.character(c(1,1,2,2)), lty = c(1,2,1,2))
+  mtext(text = bquote('signal size' ~ r), side = 1, line = 2, at = 2.5)
+  mtext(text = 'Risk approx. recovery', side = 2, line = -5.8, at = 1 * 1.1, las = 1)
+  text(x = 2, y = 0.80, pos = 4, labels = bquote(beta ~ '=' ~ .(beta)))
+  # text(x = 2, y = 0.72, pos = 4, labels = paste0("p = ", format(p, scientific=F)))
+  text(x = 2, y = 0.72, pos = 4, labels = bquote("p =" ~ 10^.(log10(p))))
+  dev.off()
+}
+
